### 2018-01-30 paper/abstract.tex
Adds makefiles submodule, paper structure

% What's the problem?
% Why is it a problem? Research gap left by other approaches?
% Why is it important? Why care?
% What's the approach? How to solve the problem?
% What's the findings? How was it evaluated, what are the results, limitations, 
% what remains to be done?

\dots

### 2018-01-31 paper/related.tex
Adds start of Related Work, moves intro to own file

\section{Related work}%
\label{RelatedWork}

\dots

### 2018-02-06 paper/related.tex
one related work line was done
completed user modeling in related works

@@
 
-\dots
+\commentAL{Will need another pass.}
+\paragraph*{Modeling devices' connection and disconnection} 
+% To simulate users' devices participating in a distributed protocol, we build upon existing literature on two topics: 
+% multi-device interaction, and churn in P2P networks. 
+In our experiments, we simulate users' devices participating in a distributed protocol.
+To make this simulation realistic, we based our models on existing literature.
+
+Firstly, fields studies provide \emph{usage and connectivity patterns of users' appliances}.
+Karlson et al. \cite{Karlson_Meyers_Jacobs_Johns_Kane_2009} studied the compared usage of the laptop and smartphone of 16 information workers: 
+they show that their participants use their smartphones very regularly throughout the day to do background tasks (e.g. answering mails or checking their agenda).
+Their laptop is online less often, and is dedicated to the most demanding tasks.
+Wagner et al.
+\cite{Wagner_Rice_Beresford_2013} conducted a thorough data collection on Android devices via an application called Device Analyzer, that collected metrics on movement patterns, connectivity and energy consumption from 16,000 users.
+\commentAL{Conclude: will we use their dataset? Why are these papers useful to us?}
+
+Secondly, several research works point out the emerging trend of \emph{multi-device interaction}.
+A 2012 Google-led study \cite{google2012} stated that the USA are nowadays ``a nation of multi-screeners''.
+People switch their attention toward their phone, laptop, tablet or their television depending on the context.
+M\"uller et al. \cite{Muller_Gove_Webb_Cheang_2015} specifically compared the usage patterns of phones against tablets.
+Jokela et al. \cite{Jokela_Ojala_Olsson_2015} and \cite{google2012} also differentiated sequential and parallel usage of one's multiple devices.
+
+Finally, research in P2P networks observed \cite{Stutzbach_Rejaie_2006} and modeled \cite{Yao_Leonard_Wang_Loguinov_2006} patterns of \emph{churn} (i.e. participants moving in and out of a system).
+
+We make use of these works to establish credible models of user behaviors to evaluate our protocol. 
+Participants can own several devices: their smartphone is always on, but lacks processing power, while their laptop is rarely online, though it contains better hardware, etc.

### 2018-02-13 paper/intro.tex
Adds start of Related Work, moves intro to own file
Adds some text to intro, adds bibsp submodule

--- 2018-01-30 paper/abstract.tex
@@
+\section{Introduction}
+
 % What's the problem?
-% Why is it a problem? Research gap left by other approaches?
-% Why is it important? Why care?
-% What's the approach? How to solve the problem?
-% What's the findings? How was it evaluated, what are the results, limitations, 
-% what remains to be done?
 
-\dots
+It's common nowadays to use a third party, i.e.\ someone else's computer (better 
+known as the Cloud), as an intermediate to share files.
+For instance, it's common for Alice to upload the file to e.g.\ Box, Dropbox or 
+OneDrive and share the link with Bob who can then download it.
+The goal of this work is to design a decentralized, distributed system where 
+Alice can share files \emph{efforlessly} between her own devices, e.g.\ laptop, 
+smartphone and tablet.
+But Alice should also be able to use her smartphone to share a file on her home 
+computer with Bob.
+Since these are Alice's private devices, privacy is essential.
+E.g.\ it would be devastating for Alice's privacy if Bob could stalk her by 
+tracking her devices or discern usage patterns.
+
+% XXX Why is it a problem? Research gap left by other approaches?
+% Why is it important, why care?
+
+\commentDaniel{Summarize here why related work is not enough.}
+
+% XXX What's the approach? How to solve the problem?
+
+We use a purely \ac{P2P} design.
+We first provide \iac{P2P} design connecting Alice's own devices.
+This decreases the risk of third-party behaviour tracking.
+Then we also use \iac{P2P} design to connect Alice's and Bob's devices.
+This requires some more care, in this case Bob can track Alice since his devices 
+are interacting directly with hers.
+
+% XXX What's the findings?
+% How was it evaluated, what are the results, limitations, what remains to be 
+% done?
+
+\commentDaniel{Summarize our results.}

### 2018-02-13 paper/algorithm.tex
Adds WIP on algorithm description

\section{Algorithm}%
\label{Algorithm}

\NewCryptoEntity{\Alice}{A}
\NewCryptoEntity{\Bob}{B}
\NewCryptoEntity{\Carol}{C}
\NewCryptoEntity{\David}{D}

We have several participants: Alice, Bob, Carol and David.
Each of them has a set of devices, \(D_i\) (where \(i\in \{\Alice, \Bob, \Carol, 
  \David\}\)).
We have two protocols to track knowledge: one protocol which is run between the 
devices in \(D_i\) (the Device Swarm Protocol) to keep local knowledge in the 
swarm and another run between different swarms (the Inter-Swarm Protocol) to 
keep global knowledge.
Finally, we have a file-sharing protocol which uses the local and global 
knowledge to coordinate file sharing between devices in different swarms.

\subsection{The Device Swarm Protocol}%
\label{DeviceSwarmProtocol}

A user's devices, \(D_i\), uses the Device Swarm Protocol to coordinate 
themselves.
More specifically, the devices use this protocol to keep the swarm state up to 
date.
The swarm state contains:
\begin{itemize}
  \item A knowledge vector, \(K_i\), encoding a Markov chain to predict online 
    and offline patterns for the various devices to predict when and for how 
    long each device might be available before disappearing again.
  \item A table, \(F_i\times \powerset(D_i)\), mapping a user's files (\(F_i\)) 
    to its devices (\(D_i\)) that store a copy of it.
\end{itemize}

\commentDaniel{What should we reuse from the session-handoff paper?}

\subsection{The Inter-Swarm Protocol}%
\label{InterSwarmProtocol}

All swarms participates in the Inter-Swarm Protocol to coordinate the global 
knowledge needed by the swarms to interact.
More specifically, the global knowledge contains:
\begin{itemize}
  \item A table, \(A\), of available devices.
  \item A key--value store, \(S = \{0, 1\}^\lambda\times \{0, 1\}^*\), mapping 
    fixed-length strings of length \(\lambda\) to arbitrary-length strings.
\end{itemize}

\subsection{File-sharing protocol}

\dots

### 2018-02-13 paper/algorithm.tex
Adds short description of file-sharing protocol
Also changes some notation from previous commit.

@@
 \begin{itemize}
-  \item A knowledge vector, \(K_i\), encoding a Markov chain to predict online 
+  \item A knowledge vector, \(A_i\), encoding a Markov chain to predict online 
     and offline patterns for the various devices to predict when and for how 
     long each device might be available before disappearing again.
-  \item A table, \(F_i\times \powerset(D_i)\), mapping a user's files (\(F_i\)) 
-    to its devices (\(D_i\)) that store a copy of it.
+  \item A table, \(F_i = N_i\times \powerset(D_i)\), mapping a user's file names 
+    (\(N_i\)) to its devices (\(D_i\)) that store a copy of that file.
 \end{itemize}
@@
 \begin{itemize}
-  \item A table, \(A\), of available devices.
+  \item A table, \(R\), of devices available for routing.
   \item A key--value store, \(S = \{0, 1\}^\lambda\times \{0, 1\}^*\), mapping 
@@
 
-\dots
+When Alice wants to transfer a file to Bob, she will find which devices have the 
+file (from \(F_i\)), then predict when any of those devices will be available 
+(from \(A_i\)).
+Then she will construct a probabilistic onion route with her devices as the 
+destinations.
+She will encrypt this route for Bob and transfer it to him, who now can use the 
+onion route to fetch the file.

### 2018-02-13 paper/intro.tex
removed some typos

@@
 
-It's common nowadays to use a third party, i.e.\ someone else's computer (better 
+It is common nowadays to use a third party, i.e.\ someone else's computer (better 
 known as the Cloud), as an intermediate to share files.
-For instance, it's common for Alice to upload the file to e.g.\ Box, Dropbox or 
+For instance, it is common for Alice to upload a file to e.g.\ Box, Dropbox or 
 OneDrive and share the link with Bob who can then download it.
 The goal of this work is to design a decentralized, distributed system where 
-Alice can share files \emph{efforlessly} between her own devices, e.g.\ laptop, 
+Alice can share files \emph{effortlessly} between her own devices, e.g.\ laptop, 
 smartphone and tablet.
@@
 We first provide \iac{P2P} design connecting Alice's own devices.
-This decreases the risk of third-party behaviour tracking.
+This decreases the risk of third-party behavior tracking.
 Then we also use \iac{P2P} design to connect Alice's and Bob's devices.

### 2018-02-13 paper/algorithm.tex

@@
 We have two protocols to track knowledge: one protocol which is run between the 
-devices in \(D_i\) (the Device Swarm Protocol) to keep local knowledge in the 
-swarm and another run between different swarms (the Inter-Swarm Protocol) to 
+devices in \(D_i\) (the Device Swarm Protocol) to gain knowledge on the 
+swarm, and another run between different swarms (the Inter-Swarm Protocol) to 
 keep global knowledge.
 Finally, we have a file-sharing protocol which uses the local and global 
-knowledge to coordinate file sharing between devices in different swarms.
+knowledges to coordinate file sharing between devices in different swarms.
 
@@
 
-A user's devices, \(D_i\), uses the Device Swarm Protocol to coordinate 
+A user's devices, \(D_i\), use the Device Swarm Protocol to coordinate 
 themselves.
@@
     and offline patterns for the various devices to predict when and for how 
-    long each device might be available before disappearing again.
+    long each device might be available before disappearing again;
   \item A table, \(F_i = N_i\times \powerset(D_i)\), mapping a user's file names 
@@
 
-All swarms participates in the Inter-Swarm Protocol to coordinate the global 
+All swarms participate in the Inter-Swarm Protocol to coordinate the global 
 knowledge needed by the swarms to interact.
@@
 \begin{itemize}
-  \item A table, \(R\), of devices available for routing.
+  \item A table, \(R\), of devices available for routing;
   \item A key--value store, \(S = \{0, 1\}^\lambda\times \{0, 1\}^*\), mapping 

### 2018-02-20 paper/algorithm.tex
changed participants names because I wanted to

@@
 
-\NewCryptoEntity{\Alice}{A}
-\NewCryptoEntity{\Bob}{B}
-\NewCryptoEntity{\Carol}{C}
+\NewCryptoEntity{\Alfred}{A}
+\NewCryptoEntity{\Beth}{B}
+\NewCryptoEntity{\Cathy}{C}
 \NewCryptoEntity{\David}{D}
 
-We have several participants: Alice, Bob, Carol and David.
-Each of them has a set of devices, \(D_i\) (where \(i\in \{\Alice, \Bob, \Carol, 
+We have several participants: Alfred, Beth, Cathy and David.
+Each of them has a set of devices, \(D_i\) (where \(i\in \{\Alfred, \Beth, \Cathy, 
   \David\}\)).
@@
 
-When Alice wants to transfer a file to Bob, she will find which devices have the 
+When Alfred wants to transfer a file to Beth, she will find which devices have the 
 file (from \(F_i\)), then predict when any of those devices will be available 
@@
 destinations.
-She will encrypt this route for Bob and transfer it to him, who now can use the 
+She will encrypt this route for Beth and transfer it to him, who now can use the 
 onion route to fetch the file.

### 2018-02-22 paper/algorithm.tex
updated text according to figure

--- 2018-02-13 paper/algorithm.tex
@@
 
-When Alice wants to transfer a file to Bob, she will find which devices have the 
-file (from \(F_i\)), then predict when any of those devices will be available 
-(from \(A_i\)).
-Then she will construct a probabilistic onion route with her devices as the 
-destinations.
-She will encrypt this route for Bob and transfer it to him, who now can use the 
-onion route to fetch the file.
+\begin{figure}[t]
+\centering
+\includegraphics[width=0.8\columnwidth]{figures/schema.pdf}
+\caption{\label{fig:pipeline}Pipeline of the steps undergone by Alfred when he shares a file from his laptop L with Beth.}
+\end{figure}
+
+Figure~\ref{fig:pipeline} depicts the process of a file exchange from Alfred to Beth.
+The file $f$ is initially located on Alfred's laptop $L$, which is potentially offline for now.
+Firstly, Alfred and Beth need to exchange encryption keys and the key $ID_f$ referencing the file on the DHT.
+They do so \emph{out-of-band}, that is using another channel than the one presented here (e.g. bluetooth, email...).
+
+Then, Alfred queries the DHT for devices that will most likely be online at the same time as his laptop $L$.
+To this end, Alfred uses his knowledge on his devices connection patterns $A_i$, along with the DHT's public information on devices connections.
+Once Alfred and the DHT agreed upon a set of peers $(M_1, M_2, M_3)$, their address is put in the DHT at the key $ID_f$ referencing the file of interest.
+
+At the third step, Alfred's laptop $L$ becomes available. 
+Informed of the ongoing file exchange by Alfred's Device Swarm Protocol, $L$ fetches the addresses of $M_1, M_2$ and $M_3$ on the DHT using the key $ID_f$.
+These peers will serve as middle-men: $L$ sends them redundant chunks of $f$ through an onion route (thus remaining anonymous), for Beth to fetch them later.
+
+In the last forth step, Beth fetches the file $f$ using any of her devices.
+To do so, she uses the key $ID_f$ to learn the addresses of $M_1, M_2$ and $M_3$.
+Then, she fetches parts of $f$ from the online middle-men through an onion route.
+Given that $L$ sent redundant chunks to the middle-men, Beth will not need every middle-man to be connected to fetch the whole file.
+Once Beth has completed the download, the key $ID_f$ is flushed on the DHT.
+
+% When Alfred and Beth want to exchange a file owned by Alfred, they first need to exchange their
+
+% When Alfred wants to transfer a file to Beth, she will find which devices have the 
+% file (from \(F_i\)), then predict when any of those devices will be available 
+% (from \(A_i\)).
+% Then she will construct a probabilistic onion route with her devices as the 
+% destinations.
+% She will encrypt this route for Beth and transfer it to him, who now can use the 
+% onion route to fetch the file.

### 2018-02-22 paper/algorithm.tex

--- 2018-02-20 paper/algorithm.tex
@@
 
-We have several participants: Alfred, Beth, Cathy and David.
+We consider several participants: Alfred, Beth, Cathy and David.
 Each of them has a set of devices, \(D_i\) (where \(i\in \{\Alfred, \Beth, \Cathy, 
-  \David\}\)).
-We have two protocols to track knowledge: one protocol which is run between the 
+  \David\}\)), hereafter called their device swarm.
+Our system is composted of two network overlays: one protocol is run between the 
 devices in \(D_i\) (the Device Swarm Protocol) to gain knowledge on the 
@@
 keep global knowledge.
-Finally, we have a file-sharing protocol which uses the local and global 
+Finally, our file-sharing protocol uses the local and global 
 knowledges to coordinate file sharing between devices in different swarms.
@@
 \subsection{File-sharing protocol}
+\label{FileSharingProtocol}
+
+\begin{figure}[t]
+\centering
+\includegraphics[width=0.8\columnwidth]{figures/schema.pdf}
+\caption{\label{fig:pipeline}Pipeline of the steps undergone by Alfred when he shares a file from his laptop L with Beth.}
+\end{figure}
 

### 2018-02-22 paper/algorithm.tex

--- 2018-02-22 paper/algorithm.tex
@@
 
-\NewCryptoEntity{\Alice}{A}
-\NewCryptoEntity{\Bob}{B}
-\NewCryptoEntity{\Carol}{C}
+\NewCryptoEntity{\Alfred}{A}
+\NewCryptoEntity{\Beth}{B}
+\NewCryptoEntity{\Cathy}{C}
 \NewCryptoEntity{\David}{D}
 
-We have several participants: Alice, Bob, Carol and David.
-Each of them has a set of devices, \(D_i\) (where \(i\in \{\Alice, \Bob, \Carol, 
-  \David\}\)).
-We have two protocols to track knowledge: one protocol which is run between the 
+We consider several participants: Alfred, Beth, Cathy and David.
+Each of them has a set of devices, \(D_i\) (where \(i\in \{\Alfred, \Beth, \Cathy, 
+  \David\}\)), hereafter called their device swarm.
+Our system is composted of two network overlays: one protocol is run between the 
 devices in \(D_i\) (the Device Swarm Protocol) to gain knowledge on the 
@@
 \subsection{File-sharing protocol}
+\label{FileSharingProtocol}
 

### 2018-03-07 paper/user-model.tex
created a User Model section

\section{User model} 
\label{sec:user_model}

We consider many users owning several devices, that they freely turn on and off depending on their location and will.
The participants' devices are the only nodes constituting our system; the unreliability of their connectivity has to be taken for granted.

We will first present a model of each user's behavior, that will drive the connection intervals of our system's nodes.

\subsection{A model of the user's behavior}
\label{sub:a_model_of_the_user_s_behavior}

In \name, we take interest in users that own several devices, and wish to privately exchange files with each other.
To the best of our knowledge, no real-world traces of multi-devices usage over several days exist, as would be needed for the experimental evaluation of our system.
For that reason, we propose a user behavioral model having the following features:

\begin{itemize}
	\item Each user owns a variable amount of devices, that can be either mobile or immobile;
	\item The user travels between three ``locations'' according to a simple probabilistic model: her home, her workplace, and outside;
	\item She can act her devices only when she is close to them. For instance, a user cannot shut down her workstation while being home or outside.
\end{itemize}

To this end, we use a Hidden Markov Model (HMM). 
The \emph{hidden} Markovian process dictates the user's progression among the three proposed locations.
The \emph{observable} process emits ``toggle'' actions on the user's devices, based on probabilities associated with each location.
For instance, the probability that the user switches her home computer on or off (i.e. \emph{toggles}) is null while she is at work or outside.

Such a statistical model is overly simplistic (e.g. it does not encapsulate the time or the weekday), but it is on purpose: simplicity is bliss.
Given the lack of real-world data for our testbed, building a more complex and realistic user model would add no value to our proposal: 
our goal is to see devices exhibiting frequent disconnections and reconnections (or \emph{churn}).
Our simple model being able to put extravagant stress on our system, it is sufficient to access \name's resilience.

### 2018-03-14 paper/user-model.tex

@@
 To this end, we use a Hidden Markov Model (HMM). 
-The \emph{hidden} Markovian process dictates the user's progression among the three proposed locations.
-The \emph{observable} process emits ``toggle'' actions on the user's devices, based on probabilities associated with each location.
+The \emph{hidden} Markovian process $S=S_1,\dots,S_T$ dictates the user's progression among the three proposed locations.
+The \emph{observable} process $O=O_1,\dots,O_T$ emits ``toggle'' actions on the user's devices, based on probabilities associated with each location.
 For instance, the probability that the user switches her home computer on or off (i.e. \emph{toggles}) is null while she is at work or outside.
@@
 Given the lack of real-world data for our testbed, building a more complex and realistic user model would add no value to our proposal: 
-our goal is to see devices exhibiting frequent disconnections and reconnections (or \emph{churn}).
+our goal is to see devices exhibiting frequent disconnections and reconnections (also called \emph{churn}).
 Our simple model being able to put extravagant stress on our system, it is sufficient to access \name's resilience.
+
+\subsubsection{Formal definition} % (fold)
+\label{ssub:formal_definition}
+
+\begin{figure}[t]
+\centering
+\vspace{-1em}
+
+$$A =
+\kbordermatrix{
+      & W            & O            & H            \cr
+    W & \sfrac{2}{3} & \sfrac{1}{3} & 0            \cr
+    O & \sfrac{1}{3} & \sfrac{1}{3} & \sfrac{1}{3} \cr
+    H & 0            & \sfrac{1}{3} & \sfrac{2}{3} \\[0.3em]
+}, \;
+B = 
+\kbordermatrix{
+      & W    & O    & H    \cr
+    n & 0.1  & 0.45 & 0.1  \cr
+    p & 0.45 & 0.55 & 0.45 \cr
+    w & 0.45 & 0    & 0    \cr
+    h & 0    & 0    & 0.45 \\[0.3em]
+}$$
+
+\includegraphics[width=0.85\columnwidth]{figures/hmm.pdf}
+\caption{ \label{fig:hmm} Example Hidden Markov Model (HMM) of a user's behavior.}
+\end{figure}
+
+We consider a single user, owning a set of $\mathcal{D}$ devices.
+Time is discretized here, and the user's activity is sequential: she can do zero or one action per ``round''of $T$s.
+A HMM $\lambda_N$, comprising a set of states $\mathcal{S}$ and a set of observable events $\mathcal{O}$, is defined as follows:
+
+$$\text{HMM}:\;\lambda_N=(\Pi, A, B)$$
+
+where 
+\begin{itemize}
+	\item $N$ is the number of states in the system:
+	$N = \left| \mathcal{S} \right|$;
+
+	\item $\Pi=\left\{ \pi_i\right\}_{i\in\mathcal{S}}$ is the initial state distribution:\\
+	$\pi_i=P[S_1=i]$;
+
+	\item $A = \left\{ a_{ij}\right\}_{(i,j)\in\mathcal{S}^2}$ is the transition probability matrix:\\
+	$a_{ij}=P[S_t=j \mid S_{t-1}=i]$;
+
+	\item $B = \left\{ b_{ik}\right\}_{(i,k)\in\mathcal{S}\times\mathcal{O}}$ is the matrix of states conditional densities:
+	$b_{ik} = P[O_t=k \mid S_t = i]$.
+\end{itemize}
+
+In our case, the states are the different locations where the user is susceptible to go.
+We considered the three following locations: $\mathcal{S}=\left\{ \mathit{work}, \mathit{outside}, \mathit{home} \right\}$. 
+There is one action per device $d$ owned by the user, plus a $\mathit{none}$ action when the user does not do anything: 
+$\mathcal{O} = \left\{ \mathit{toggle}_d \right\}_{d\in \mathcal{D}}$.
+$\mathit{toggle}_d$ means that the user turned her device $d$ on or off, depending on the device's previous state.
+
+In figure~\ref{fig:hmm}, we show an example HMM of a user's behavioral HMM, along with its graphical representation (the initial state distribution $\Pi$ was left out for simplicity). 
+The represented user possesses a phone, that she carries around with her, a home computer, that is only accessible from her home, and a workstation, located at her workplace.
+
+\begin{figure}[t]
+\centering
+\includegraphics[width=\columnwidth]{figures/sample_usage.pdf}
+
+\caption{\label{fig:sample_usage}Sample device usage using the previous HMM specifications. 
+%The bottom line reads the HMM's states: \textbf{W}ork, \textbf{O}utside, and \textbf{H}ome, while the dark lines read when the devices (\textbf{h}ome computer, \textbf{p}hone, and \textbf{w}orkstation) are online.
+}
+\end{figure}
+
+\commentAL{Stupid of me to use same abbreviations for toggle and usage events...}
+
+Figure~\ref{fig:sample_usage} plots a sample device usage timeline using the previous model. 
+Each device starts offline; the user can toggle one device per round (or do nothing).
+In this figure, we show the device \emph{usage}, that is a consequence of the $\mathit{toggle}$ events defined by the HMM.
+As a consequence, several devices can be online at the same time, as happens in the figure.
+
+% subsubsection formal_definition (end)

### 2018-03-29 paper/user-model.tex
renamed variables

@@
 	\item The user travels between three ``locations'' according to a simple probabilistic model: her home, her workplace, and outside;
-	\item She can act her devices only when she is close to them. For instance, a user cannot shut down her workstation while being home or outside.
+	\item She can act on her devices only when she is close to them. For instance, a user cannot shut down her workstation while being home or outside.
 \end{itemize}
@@
 To this end, we use a Hidden Markov Model (HMM). 
-The \emph{hidden} Markovian process $S=S_1,\dots,S_T$ dictates the user's progression among the three proposed locations.
-The \emph{observable} process $O=O_1,\dots,O_T$ emits ``toggle'' actions on the user's devices, based on probabilities associated with each location.
-For instance, the probability that the user switches her home computer on or off (i.e. \emph{toggles}) is null while she is at work or outside.
+The \emph{hidden} Markovian process $S=S_1,\dots,S_T$ represents the user's progression among the three proposed locations.
+The \emph{observable} process $O=O_1,\dots,O_T$ reads ``toggle'' actions performed by the user on her devices. The probability of observable events depends on the current location.
+For instance, the probability that the user switches her home computer on or off is null while she is at work or outside.
 
-Such a statistical model is overly simplistic (e.g. it does not encapsulate the time or the weekday), but it is on purpose: simplicity is bliss.
+Such a statistical model is simplistic (e.g. it does not encapsulate date \& time nor location), but it is on purpose: simplicity is bliss.
 Given the lack of real-world data for our testbed, building a more complex and realistic user model would add no value to our proposal: 
@@
       & W    & O    & H    \cr
-    n & 0.1  & 0.45 & 0.1  \cr
-    p & 0.45 & 0.55 & 0.45 \cr
-    w & 0.45 & 0    & 0    \cr
-    h & 0    & 0    & 0.45 \\[0.3em]
+    t_n & 0.1  & 0.45 & 0.1  \cr
+    t_p & 0.45 & 0.55 & 0.45 \cr
+    t_w & 0.45 & 0    & 0    \cr
+    t_h & 0    & 0    & 0.45 \\[0.3em]
 }$$
 
-\includegraphics[width=0.85\columnwidth]{figures/hmm.pdf}
+\includegraphics[width=0.9\columnwidth]{figures/hmm.pdf}
 \caption{ \label{fig:hmm} Example Hidden Markov Model (HMM) of a user's behavior.}
@@
 We considered the three following locations: $\mathcal{S}=\left\{ \mathit{work}, \mathit{outside}, \mathit{home} \right\}$. 
-There is one action per device $d$ owned by the user, plus a $\mathit{none}$ action when the user does not do anything: 
-$\mathcal{O} = \left\{ \mathit{toggle}_d \right\}_{d\in \mathcal{D}}$.
-$\mathit{toggle}_d$ means that the user turned her device $d$ on or off, depending on the device's previous state.
+There is one action per device $d\in\mathcal{D}$, plus a ``none'' action when the user does not do anything: 
+$\mathcal{O} = \left\{ t_d \right\}_{d\in \mathcal{D}} \bigcup \left\{ t_\text{none} \right\}$.
+$t_d$ means that the user turned her device $d$ on or off (i.e. \emph{toggled} it), depending on the device's previous state.
 
@@
 }
+
 \end{figure}
 
-\commentAL{Stupid of me to use same abbreviations for toggle and usage events...}
+Using the toggle events, we compute the device's \emph{connection} events, represented by the multivariate Bernoulli process $C=\left\{ c^{(d)} \right\}_{d\in\mathcal{D}}$. 
+$c^{(d)}_t=1$ (resp. 0) means that the device $d$ was online (resp. offline) at time step $t$.
 
-Figure~\ref{fig:sample_usage} plots a sample device usage timeline using the previous model. 
-Each device starts offline; the user can toggle one device per round (or do nothing).
-In this figure, we show the device \emph{usage}, that is a consequence of the $\mathit{toggle}$ events defined by the HMM.
-As a consequence, several devices can be online at the same time, as happens in the figure.
+We state that every device starts offline, and compute $c^{(d)}_t$ as follows:
+
+$$ \forall d \in \mathcal{D},
+\begin{cases}
+c^{(d)}_t=0 &\text{when } t=0; \\
+c^{(d)}_t=c^{(d)}_{t-1} \oplus \left[ O_t = t_d \right] &\text{when } t>0.
+\end{cases}$$
+
+Figure~\ref{fig:sample_usage}, shows a possible trace of the user's behavior, using the parameters depicted in figure~\ref{fig:hmm}.
+It read the timeline of $c^{(d)}$ for each device $d$.
+On the bottom of the graph, the first letter of the user's location is shown at each time step.
+We see that any number of devices can be connected at the same time.
+
+% Each device starts offline; then, the user either toggles one device per round or does nothing.
+% In this figure, we show the device \emph{usage}, that is a consequence of the $\mathit{toggle}$ events defined by the HMM.
+% As a consequence, several devices can be online at the same time, as happens in the figure.
 

### 2018-04-03 paper/privacy.tex
Pontless commit

\section{Privacy}%
\label{Privacy}

We care about
\dots

### 2018-04-03 paper/user-model.tex
new subsubsection
Changes [Ff]igure~\ref to \[Cc]ref

--- 2018-03-14 paper/user-model.tex
@@
 
-In figure~\ref{fig:hmm}, we show an example HMM of a user's behavioral HMM, along with its graphical representation (the initial state distribution $\Pi$ was left out for simplicity). 
+In \cref{fig:hmm}, we show an example HMM of a user's behavioral HMM, along with its graphical representation (the initial state distribution $\Pi$ was left out for simplicity). 
 The represented user possesses a phone, that she carries around with her, a home computer, that is only accessible from her home, and a workstation, located at her workplace.
@@
 
-Figure~\ref{fig:sample_usage} plots a sample device usage timeline using the previous model. 
+\Cref{fig:sample_usage} plots a sample device usage timeline using the previous model. 
 Each device starts offline; the user can toggle one device per round (or do nothing).

### 2018-04-03 paper/user-model.tex

@@
 The \emph{observable} process $O=O_1,\dots,O_T$ emits ``toggle'' actions on the user's devices, based on probabilities associated with each location.
-For instance, the probability that the user switches her home computer on or off (i.e. \emph{toggles}) is null while she is at work or outside.
+For instance, the probability that the user switches her home computer on or off (\ie \emph{toggles}) is null while she is at work or outside.
 
-Such a statistical model is overly simplistic (e.g. it does not encapsulate the time or the weekday), but it is on purpose: simplicity is bliss.
+Such a statistical model is overly simplistic (\eg it does not encapsulate the time or the weekday), but it is on purpose: simplicity is bliss.
 Given the lack of real-world data for our testbed, building a more complex and realistic user model would add no value to our proposal: 

### 2018-04-04 paper/algorithm.tex
Changes [Ff]igure~\ref to \[Cc]ref
Minor clarification to algorithm section

--- 2018-02-22 paper/algorithm.tex
@@
 
-\NewCryptoEntity{\Alfred}{A}
-\NewCryptoEntity{\Beth}{B}
-\NewCryptoEntity{\Cathy}{C}
+\NewCryptoEntity{\Alice}{A}
+\NewCryptoEntity{\Bob}{B}
+\NewCryptoEntity{\Carol}{C}
 \NewCryptoEntity{\David}{D}
 
-We consider several participants: Alfred, Beth, Cathy and David.
-Each of them has a set of devices, \(D_i\) (where \(i\in \{\Alfred, \Beth, \Cathy, 
+We consider several participants: Alice, Bob, Carol and David.
+Each of them has a set of devices, \(D_i\) (where \(i\in \{\Alice, \Bob, \Carol, 
   \David\}\)), hereafter called their device swarm.
@@
 \begin{itemize}
-  \item A table, \(R\), of devices available for routing;
-  \item A key--value store, \(S = \{0, 1\}^\lambda\times \{0, 1\}^*\), mapping 
+  \item A table, \(R\), of devices available for routing.
+  \item A key--value store, \(S\colon \{0, 1\}^\lambda\to \{0, 1\}^*\), mapping 
     fixed-length strings of length \(\lambda\) to arbitrary-length strings.
+    We will use the notation \(x\mapsto S[x]\).
 \end{itemize}
 
-\subsection{File-sharing protocol}
+\subsection{File-sharing protocol}%
 \label{FileSharingProtocol}
@@
 \includegraphics[width=0.8\columnwidth]{figures/schema.pdf}
-\caption{\label{fig:pipeline}Pipeline of the steps undergone by Alfred when he shares a file from his laptop L with Beth.}
+\caption{\label{fig:pipeline}Pipeline of the steps undergone by Alice when he shares a file from his laptop L with Bob.}
 \end{figure}
 
-When Alfred wants to transfer a file to Beth, she will find which devices have the 
-file (from \(F_i\)), then predict when any of those devices will be available 
-(from \(A_i\)).
-Then she will construct a probabilistic onion route with her devices as the 
-destinations.
-She will encrypt this route for Beth and transfer it to him, who now can use the 
-onion route to fetch the file.
+\Cref{fig:pipeline} depicts the process of a file exchange from Alice to Bob.
+The file $f$ is initially located on Alice's laptop $L$, which is potentially offline for now.
+Firstly, Alice and Bob need to exchange encryption keys and the key $ID_f$ 
+referencing the file on the \ac{DHT}.
+They do so \emph{out-of-band}, that is using another channel than the one 
+presented here (\eg bluetooth, email, \etc).
+
+Then, Alice queries the DHT for devices that will most likely be online at the same time as his laptop $L$.
+To this end, Alice uses his knowledge on his devices connection patterns $A_i$, along with the DHT's public information on devices connections.
+Once Alice and the DHT agreed upon a set of peers $(M_1, M_2, M_3)$, their address is put in the DHT at the key $ID_f$ referencing the file of interest.
+
+At the third step, Alice's laptop $L$ becomes available. 
+Informed of the ongoing file exchange by Alice's Device Swarm Protocol, $L$ fetches the addresses of $M_1, M_2$ and $M_3$ on the DHT using the key $ID_f$.
+These peers will serve as middle-men: $L$ sends them redundant chunks of $f$ through an onion route (thus remaining anonymous), for Bob to fetch them later.
+
+In the last forth step, Bob fetches the file $f$ using any of her devices.
+To do so, she uses the key $ID_f$ to learn the addresses of $M_1, M_2$ and $M_3$.
+Then, she fetches parts of $f$ from the online middle-men through an onion route.
+Given that $L$ sent redundant chunks to the middle-men, Bob will not need every middle-man to be connected to fetch the whole file.
+Once Bob has completed the download, the key $ID_f$ is flushed on the DHT.
+
+% When Alice and Bob want to exchange a file owned by Alice, they first need to exchange their
+
+% When Alice wants to transfer a file to Bob, she will find which devices have the 
+% file (from \(F_i\)), then predict when any of those devices will be available 
+% (from \(A_i\)).
+% Then she will construct a probabilistic onion route with her devices as the 
+% destinations.
+% She will encrypt this route for Bob and transfer it to him, who now can use the 
+% onion route to fetch the file.

### 2018-04-04 paper/algorithm.tex
Adds figures of incremental OR and prob route tree

@@
 
-\begin{figure}[t]
+Alice has a file \(f\) stored on one of her devices and wants to transfer \(f\) 
+to Bob.
+Neither Alice nor Bob care about where \(f\) will be stored, as long as they can 
+access it from any device (\ie the device they are using at the moment).
+Here we will focus on how to get \(f\) from any of Alice's devices to any of 
+Bob's devices.
+When \(f\) is available on any of Bob's devices, Bob can rely on the Device 
+Swarm Protocol (\cref{DeviceSwarmProtocol}) to access it on the device choice.
+
+\begin{figure*}
   \centering
-\includegraphics[width=0.8\columnwidth]{figures/schema.pdf}
-\caption{\label{fig:pipeline}Pipeline of the steps undergone by Alice when he shares a file from his laptop L with Bob.}
-\end{figure}
+  % XXX Replace ProbabilisticRoutes figure
+  \includegraphics{figures/probabilistic-routes-cropped.png}
+  \caption{\label{ProbabilisticRoutes}%
+    Probabilistic routes from Alice to Bob.
+  }
+\end{figure*}
+
+\begin{figure*}
+  \centering
+  % XXX Replace IncrementalOnionRouting figure
+  \includegraphics[height=\textheight]{figures/incremental-onion-routing-cropped.png}
+  \caption{\label{IncrementalOnionRouting}%
+    Overview of incremental onion routing.
+  }
+\end{figure*}
 

### 2018-04-05 paper/user-model.tex

--- 2018-03-29 paper/user-model.tex
@@
 We will first present a model of each user's behavior, that will drive the connection intervals of our system's nodes.
+Then, we will show how devices can predict the future user's behavior given the model.
 
@@
 $t_d$ means that the user turned her device $d$ on or off (i.e. \emph{toggled} it), depending on the device's previous state.
+\commentAL{TODO Rephrase:} We also note $o^{(d)}_t=1$ (resp. 0) when the user toggled (resp. did not toggle) device $d$ at time $t$.
 
@@
 c^{(d)}_t=0 &\text{when } t=0; \\
-c^{(d)}_t=c^{(d)}_{t-1} \oplus \left[ O_t = t_d \right] &\text{when } t>0.
+c^{(d)}_t=c^{(d)}_{t-1} \oplus o^{(d)}_t &\text{when } t>0.
 \end{cases}$$
@@
 % subsubsection formal_definition (end)
+
+\commentAL{Need to explain how devices go from sequence to the HMM at some point. 
+We first define the prediction of behavior from the HMM directly.}
+
+\subsubsection{Predicting future behavior} % (fold)
+\label{ssub:predicting_future_behavior}
+\commentAL{Why we need to make these predictions is not explained yet.}
+Devices want to predict whether they are likely to be connected in the near future.
+This information will be publicly available, and allow routes prediction for the upcoming files exchange.
+
+Given the model $\lambda_N$, the current user's location $S_t$ and the current connection state of the devices $C_t$, we can predict the devices connections in $k$ round $C_{t+k}$.
+
+If the device $d$ is connected at time $t$ (resp.
+disconnected), the probability that $d$ is connected at time $t+k$ is equal to the probability that the user toggles $d$ an even (resp.
+odd) number of times between round $t+1$ and $t+k$:
+
+$$
+P\left[c^{(d)}_{t+k}=1 \mid c^{(d)}_{t}=1 ,S_t \right]= P\left[ \sum\limits_{i\in[\![ 1,k]\!]}o^{(d)}_{t+i} \text{ is even} \mid S_t\right] 
+$$
+
+To compute this probability, one thus need to predict the probability that the user toggles $d$ at each round until $t+k$. This is done recursively:
+
+\begin{multline*}
+P\left[o^{(d)}_{t+i}=1 \mid S_{t} \right] = \\
+\sum\limits_{s \in \mathcal{S}} P\left[ S_{t+1}=s \mid S_t\right] * P\left[o^{(d)}_{t+i}=1 \mid S_{t+1}=s \right]
+\end{multline*}
+
+Knowing that the probability of toggling $d$ during the next round is computed as follows:
+
+\begin{multline*}
+P\left[o^{(d)}_{t+1}= 1 \mid S_{t} \right]=\\
+\sum\limits_{s \in \mathcal{S}} P\left[ S_{t+1}=s \mid S_{t}\right] * P\left[ o^{(d)}_{t+1}=1 \mid S_{t+1}=s\right] 
+\end{multline*}
+
+Finally, we enumerate the set $\mathcal{B}^{(k)}_\text{even}$ (resp.
+$\mathcal{B}^{(k)}_\text{even}$) of sequences of $k$ booleans having an even (resp.
+odd) number of true values, and compute the probability that device $d$ will be connected in $k$ turns, knowing that it is connected (resp.
+disconnected) at time $t$:
+
+\begin{multline*}
+P\left[c^{(d)}_{t+k}=1 \mid c^{(d)}_{t}=1 ,S_t \right]=\\
+\sum\limits_{B \in \mathcal{B}_\text{even}}\sum\limits_{i\in[\![ 1,k]\!]} P\left[o^{(d)}_{t+i}= B\left[i\right] \mid S_{t} \right]
+\end{multline*}
+
+\begin{multline*}
+P\left[c^{(d)}_{t+k}=1 \mid c^{(d)}_{t}=0 ,S_t \right]=\\
+\sum\limits_{B \in \mathcal{B}_\text{odd}}\sum\limits_{i\in[\![ 1,k]\!]} P\left[o^{(d)}_{t+i}= B\left[i\right] \mid S_{t} \right]
+\end{multline*}
+
+% \begin{multline}
+% P\left[o^{(d)}_{t+1}= 1 \mid S_{t} \right]= P\left[o^{(d)}_{t+i+1}= 1 \mid S_{t+i} \right] = \\
+% \sum\limits_{s \in \mathcal{S}} P\left[ S_{t+1}=s \mid S_{t}\right] * P\left[ o^{(d)}_{t+1}=1 \mid S_{t+1}=s\right] \\
+
+% P\left[o^{(d)}_{t+i}=1 \mid S_{t} \right] = \sum\limits_{s \in \mathcal{S}} P\left[ S_{t+1}=s \mid S_t\right] * P\left[o^{(d)}_{t+i}=1 \mid S_{t+1}=s \right]
+% \end{multline}
+
+% Using the matrices notations:
+
+% $$
+% \begin{cases}
+% P\left[o^{(d)}_{t+i+1}=1 \mid S_{t+i} = i\right] = \sum\limits_{j \in \mathcal{S}} a_{ij} * b_{jk}\\
+
+% P\left[o^{(d)}_{t+i}=1 \mid S_{t} = i \right] = \sum\limits_{j \in \mathcal{S}} a_{ij} * P\left[o^{(d)}_{t+i}=1 \mid S_{t+1}=s \right]
+% \end{cases}
+% $$
+
+% subsubsection predicting_future_behavior (end)

### 2018-04-05 paper/algorithm.tex
Adds pointers to GitHub issues

--- 2018-04-04 paper/algorithm.tex
@@
 \begin{itemize}
-  \item A table, \(R\), of devices available for routing.
-  \item A key--value store, \(S\colon \{0, 1\}^\lambda\to \{0, 1\}^*\), mapping 
+  \item A table, \(R\), of devices available for routing;
+  \item A key--value store, \(S = \{0, 1\}^\lambda\times \{0, 1\}^*\), mapping 
     fixed-length strings of length \(\lambda\) to arbitrary-length strings.
-    We will use the notation \(x\mapsto S[x]\).
 \end{itemize}

### 2018-04-05 paper/intro.tex

@@
 
-It is common nowadays to use a third party, i.e.\ someone else's computer (better 
+It is common nowadays to use a third party, \ie someone else's computer (better 
 known as the Cloud), as an intermediate to share files.
-For instance, it is common for Alice to upload a file to e.g.\ Box, Dropbox or 
+For instance, it is common for Alice to upload a file to \eg Box, Dropbox or 
 OneDrive and share the link with Bob who can then download it.
 The goal of this work is to design a decentralized, distributed system where 
-Alice can share files \emph{effortlessly} between her own devices, e.g.\ laptop, 
+Alice can share files \emph{effortlessly} between her own devices, \eg laptop, 
 smartphone and tablet.

### 2018-04-05 paper/related.tex

@@
 Karlson et al. \cite{Karlson_Meyers_Jacobs_Johns_Kane_2009} studied the compared usage of the laptop and smartphone of 16 information workers: 
-they show that their participants use their smartphones very regularly throughout the day to do background tasks (e.g. answering mails or checking their agenda).
+they show that their participants use their smartphones very regularly throughout the day to do background tasks (\eg answering mails or checking their agenda).
 Their laptop is online less often, and is dedicated to the most demanding tasks.
@@
 
-Finally, research in P2P networks observed \cite{Stutzbach_Rejaie_2006} and modeled \cite{Yao_Leonard_Wang_Loguinov_2006} patterns of \emph{churn} (i.e. participants moving in and out of a system).
+Finally, research in P2P networks observed \cite{Stutzbach_Rejaie_2006} and modeled \cite{Yao_Leonard_Wang_Loguinov_2006} patterns of \emph{churn} (\ie participants moving in and out of a system).
 

### 2018-04-05 paper/user-model.tex

@@
 
-% P\left[o^{(d)}_{t+i}=1 \mid S_{t} \right] = \sum\limits_{s \in \mathcal{S}} P\left[ S_{t+1}=s \mid S_t\right] * P\left[o^{(d)}_{t+i}=1 \mid S_{t+1}=s \right]
-% \end{multline}
+\Cref{fig:sample_usage} plots a sample device usage timeline using the previous model. 
+Each device starts offline; the user can toggle one device per round (or do nothing).
+In this figure, we show the device \emph{usage}, that is a consequence of the $\mathit{toggle}$ events defined by the HMM.
+As a consequence, several devices can be online at the same time, as happens in the figure.
 

### 2018-04-10 python/modules/model.py
some work done on working in the system

@@ -3,15 +3,25 @@
 import numpy as np
 import random
 import pomegranate as pg
+import string
 
 STATE_NAME_PREFIX = "s"
 OBSERVATION_NAME_PREFIX = "d"
 
 DEFAULT_STATES_NAME = ["Home", "Outside", "Work"]
+DEFAULT_STATES_NUMBER = len(DEFAULT_STATES_NAME)
+DEFAULT_TRANSITION_MATRIX = \
+    [[0.6, 0.4, 0.],
+     [0.2, 0.6, 0.2],
+     [0.,  0.4, 0.6]]
+
+DEVICES_NUMBER_MIN = 3
+DEVICES_NUMBER_MAX = 10
+
+RANDOM_NAME_SIZE = 16
 
 
 class Model:
-
     def __init__(self):
         self.n_states = 0
         self.n_obs = 0
@@ -21,6 +31,13 @@ class Model:
         self.A = None
         self.B = None
         self.defined = False
+
+    def __str__(self):
+        ret = str(self.__class__) + ': {\n'
+        for k, v in self.__dict__.items():
+            ret += "{}: {}\n".format(k, v)
+        ret += "}"
+        return ret
 
     def set(self, A, B, states=None, observations=None):
         self.A = np.array(A, dtype=np.float64)
@@ -44,7 +61,7 @@ class Model:
 
         self.defined = True
 
-    def sample(self, length=20):
+    def sample(self, length=20, s0=None):
         if not self.defined:
             print("Model is not defined.")
             return None, None
@@ -56,8 +73,15 @@ class Model:
 
         for t in range(length):
             if initial_state:
-                # Random initial state
-                state = random.randint(0, self.n_states-1)
+                if s0 is None:
+                    # Random initial state
+                    state = random.randint(0, self.n_states-1)
+                else:
+                    if s0 < 0 or s0 >= self.n_states:
+                        raise ValueError(
+                            "Out of bounds initial state s0: \
+                             should be in [[0, {}]]".format(self.n_states-1))
+                    state = s0
                 initial_state = False
             else:
                 state = np.random.choice(
@@ -73,7 +97,7 @@ class Model:
 
         return sample_states, sample_obs
 
-    def predict(self, up_to, obs):
+    def predict(self, up_to, obs, s_t=None):
         """Return a <t x s> matrix of the probability
         P[obs is online in t turns | current state is s]
         for all states s and t in [1, up_to].
[…]

### 2018-04-10 paper/related.tex
modifying user model to fit system's improvements

@@
 
-We make use of these works to establish credible models of user behaviors to evaluate our protocol. 
-Participants can own several devices: their smartphone is always on, but lacks processing power, while their laptop is rarely online, though it contains better hardware, etc.
+We take inspiration from these works in order to establish credible models of user behaviors to evaluate our protocol. 
+% Participants can own several devices: their smartphone is always on, but lacks processing power, while their laptop is rarely online, though it contains better hardware, etc.

### 2018-04-10 paper/user-model.tex
modifying user model to fit system's improvements

@@
 We will first present a model of each user's behavior, that will drive the connection intervals of our system's nodes.
-Then, we will show how devices can predict the future user's behavior given the model.
+%Then, we will show how devices can predict the future user's behavior given the model.
 
@@
 
-In \name, we take interest in users that own several devices, and wish to privately exchange files with each other.
+In \name, we take interest in users that own several devices, and wish to privately exchange files with each other without revealing .
 To the best of our knowledge, no real-world traces of multi-devices usage over several days exist, as would be needed for the experimental evaluation of our system.
@@
 \begin{itemize}
-	\item Each user owns a variable amount of devices, that can be either mobile or immobile;
+	\item Each user owns a variable amount of devices. We consider the following device types: mobile, portable, fixed, and server;
 	\item The user travels between three ``locations'' according to a simple probabilistic model: her home, her workplace, and outside;
-	\item She can act on her devices only when she is close to them. For instance, a user cannot shut down her workstation while being home or outside.
+	\item She makes a different use of her devices depending on her location: at home, she will her laptop that at work; she cannot use her workstation at home.
 \end{itemize}
 
-To this end, we use a Hidden Markov Model (HMM). 
-The \emph{hidden} Markovian process $S=S_1,\dots,S_T$ represents the user's progression among the three proposed locations.
-The \emph{observable} process $O=O_1,\dots,O_T$ reads ``toggle'' actions performed by the user on her devices. The probability of observable events depends on the current location.
-For instance, the probability that the user switches her home computer on or off is null while she is at work or outside.
+To this end, we use a Hidden Markov Model (HMM) of order one, with multiple discrete observation processes. 
+The \emph{hidden} Markovian process $S=S_1,\dots,S_T$ represents the user's progression among the three proposed locations up to time step $T$.
+For every device $d$ owned by the user, the \emph{observable} process $O_d=O_{d,1},\dots,O_{d,T}$ reads $d$'s state: it is either online ($o_d$) or offline ($\overline{o_d}$) at each point in time. 
+The probability of observable events depends only on the current location.
+%The \emph{observable} process $O=O_1,\dots,O_T$ reads ``toggle'' actions performed by the user on her devices. The probability of observable events depends on the current location.
+For example, the probability that the user's home computer is on while she is at work is null (in our model, users never forget to turn off their fixed devices before leaving).
 

### 2018-04-11 paper/user-model.tex
rewrote HMM model

@@
 To this end, we use a Hidden Markov Model (HMM) of order one, with multiple discrete observation processes. 
-The \emph{hidden} Markovian process $S=S_1,\dots,S_T$ represents the user's progression among the three proposed locations up to time step $T$.
-For every device $d$ owned by the user, the \emph{observable} process $O_d=O_{d,1},\dots,O_{d,T}$ reads $d$'s state: it is either online ($o_d$) or offline ($\overline{o_d}$) at each point in time. 
-The probability of observable events depends only on the current location.
-%The \emph{observable} process $O=O_1,\dots,O_T$ reads ``toggle'' actions performed by the user on her devices. The probability of observable events depends on the current location.
-For example, the probability that the user's home computer is on while she is at work is null (in our model, users never forget to turn off their fixed devices before leaving).
+The hidden Markovian process $S$ represents the user's locations, while the \emph{observable} process $O=O_1, \dots, \O_T$ represents the connection state of her devices (either connected or disconnected at any point in time).
+% The \emph{hidden} Markovian process $S=S_1,\dots,S_T$ represents the user's progression among the three proposed locations up to time step $T$.
+% For every device $d$ owned by the user, the \emph{observable} process $O_d=O_{d,1},\dots,O_{d,T}$ reads $d$'s state: it is either online ($o_d$) or offline ($\overline{o_d}$) at each point in time.
+$O_t = O_1, \dots, \O_T$ represents the connection of all the user's devices, such that $o_d \in O_t$ means that device $d$ was connected at time $t$.
+
+% The probability of observable events depends only on the current location.
+% For example, the probability that the user's home computer is on while she is at work is null (in our model, users never forget to turn off their fixed devices before leaving).
 
@@
       & W     & O   & H   \cr
-    t_n & 0.1  & 0.45 & 0.1  \cr
-    t_p & 0.45 & 0.55 & 0.45 \cr
-    t_w & 0.45 & 0    & 0    \cr
-    t_h & 0    & 0    & 0.45 \\[0.3em]
+    o_p & 0.7 & 0.6 & 0.8 \cr
+    o_w & 0.7 & 0   & 0   \cr
+    o_h & 0   & 0   & 0.7 \cr
+    o_l & 0.2 & 0.4 & 0.6 \\[0.3em]
 }$$
@@
 We consider a single user, owning a set of $\mathcal{D}$ devices.
-Time is discretized here, and the user's activity is sequential: she can do zero or one action per ``round''of $T$s.
-A HMM $\lambda_N$, comprising a set of states $\mathcal{S}$ and a set of observable events $\mathcal{O}$, is defined as follows:
+Time is discretized, and the devices' observations are independent: Alice can have her laptop and phone connected at the same time.
+The hidden process $S=S_1,\dots,S_T$ is built from an alphabet of states $\mathcal{S}$, while the observable process $O=O_1, \dots, \O_T$ contains events from the alphabet $\mathcal{O}$.
+We define a multivariate HMM $\lambda_N$ as follows:
 
@@
 
-	\item $A = \left\{ a_{ij}\right\}_{(i,j)\in\mathcal{S}^2}$ is the transition probability matrix:\\
-	$a_{ij}=P[S_t=j \mid S_{t-1}=i]$;
+	\item $A = \left\{ a_{i\,j}\right\}_{(i,j)\in\mathcal{S}^2}$ is the state transition matrix:\\
+	$a_{i\,j}=P[S_t=j \mid S_{t-1}=i]$;
 
-	\item $B = \left\{ b_{ik}\right\}_{(i,k)\in\mathcal{S}\times\mathcal{O}}$ is the matrix of states conditional densities:
-	$b_{ik} = P[O_t=k \mid S_t = i]$.
+	\item $B = \left\{ b_{i\,k}\right\}_{(i,k)\in\mathcal{S}\times\mathcal{O}}$ is the matrix of event emission probabilities for each state:
+	$b_{i\,k} = P[ k \in O_t \mid S_t = i]$.
 \end{itemize}
 
-In our case, the states are the different locations where the user is susceptible to go.
-We considered the three following locations: $\mathcal{S}=\left\{ \mathit{work}, \mathit{outside}, \mathit{home} \right\}$. 
-There is one action per device $d\in\mathcal{D}$, plus a ``none'' action when the user does not do anything: 
-$\mathcal{O} = \left\{ t_d \right\}_{d\in \mathcal{D}} \bigcup \left\{ t_\text{none} \right\}$.
-$t_d$ means that the user turned her device $d$ on or off (i.e. \emph{toggled} it), depending on the device's previous state.
-\commentAL{TODO Rephrase:} We also note $o^{(d)}_t=1$ (resp. 0) when the user toggled (resp. did not toggle) device $d$ at time $t$.
+In our case, the states are the different locations where the user is susceptible to go;
+we considered the three following ones: $\mathcal{S}=\left\{ \mathit{work}, \mathit{outside}, \mathit{home} \right\}$. 
+There is one event per device $d$: $\mathcal{O} = \left\{ o_d \right\}_{d\in \mathcal{D}}$.
+Several devices can be connected at the same time, such that $O_t$ is a set, and $o_d \in O_t$ means that device $d$ was connected at time $t$.
+Devices' connection probabilities are independent.
 
 In \cref{fig:hmm}, we show an example HMM of a user's behavioral HMM, along with its graphical representation (the initial state distribution $\Pi$ was left out for simplicity). 
-The represented user possesses a phone, that she carries around with her, a home computer, that is only accessible from her home, and a workstation, located at her workplace.
+The represented user possesses a phone and a laptop, that she carries around with her, a home computer, that is only accessible from her home, and a workstation, located at her workplace.
+She never forgets to turn off her fixed appliances before leaving.
 
@@
 
-\caption{\label{fig:sample_usage}Sample device usage using the previous HMM specifications. 
+\caption{\label{fig:sample_usage}Sample device usages using the previous HMM specifications. 
 %The bottom line reads the HMM's states: \textbf{W}ork, \textbf{O}utside, and \textbf{H}ome, while the dark lines read when the devices (\textbf{h}ome computer, \textbf{p}hone, and \textbf{w}orkstation) are online.
@@
 
-Using the toggle events, we compute the device's \emph{connection} events, represented by the multivariate Bernoulli process $C=\left\{ c^{(d)} \right\}_{d\in\mathcal{D}}$. 
-$c^{(d)}_t=1$ (resp. 0) means that the device $d$ was online (resp. offline) at time step $t$.
+% Using the toggle events, we compute the device's \emph{connection} events, represented by the multivariate Bernoulli process $C=\left\{ c^{(d)} \right\}_{d\in\mathcal{D}}$. 
+% $c^{(d)}_t=1$ (resp. 0) means that the device $d$ was online (resp. offline) at time step $t$.
 
-We state that every device starts offline, and compute $c^{(d)}_t$ as follows:
+% We state that every device starts offline, and compute $c^{(d)}_t$ as follows:
 
-$$ \forall d \in \mathcal{D},
-\begin{cases}
-c^{(d)}_t=0 &\text{when } t=0; \\
-c^{(d)}_t=c^{(d)}_{t-1} \oplus o^{(d)}_t &\text{when } t>0.
-\end{cases}$$
+% $$ \forall d \in \mathcal{D},
+% \begin{cases}
+% c^{(d)}_t=0 &\text{when } t=0; \\
+% c^{(d)}_t=c^{(d)}_{t-1} \oplus o^{(d)}_t &\text{when } t>0.
+% \end{cases}$$
 
 Figure~\ref{fig:sample_usage}, shows a possible trace of the user's behavior, using the parameters depicted in figure~\ref{fig:hmm}. 
-It read the timeline of $c^{(d)}$ for each device $d$.
-On the bottom of the graph, the first letter of the user's location is shown at each time step.
-We see that any number of devices can be connected at the same time.
+It reads the timeline of $o_{d}$ for each device $d$. On the bottom of the graph, the first letter of the user's location is shown at each time step.
+We see that devices connections depend on the user's location, and that any number of devices can be connected at the same time.
 
@@
 
-\commentAL{Need to explain how devices go from sequence to the HMM at some point. 
-We first define the prediction of behavior from the HMM directly.}
-
 \subsubsection{Predicting future behavior} % (fold)
@@
 Devices want to predict whether they are likely to be connected in the near future.
-This information will be publicly available, and allow routes prediction for the upcoming files exchange.
+This information will be publicly available, and will allow routes selection for the  files exchange between users.
 
-Given the model $\lambda_N$, the current user's location $S_t$ and the current connection state of the devices $C_t$, we can predict the devices connections in $k$ round $C_{t+k}$.
-
-If the device $d$ is connected at time $t$ (resp.
-disconnected), the probability that $d$ is connected at time $t+k$ is equal to the probability that the user toggles $d$ an even (resp.
-odd) number of times between round $t+1$ and $t+k$:
+Because devices connections only depend on the users location, we can predict the devices connections in $i$ round $O_{t+i}$ given only the model $\lambda_N$ and the current user's location $S_t$.
+We first compute the probability that a device $d$ will be connected next turn:
 
 $$
-P\left[c^{(d)}_{t+k}=1 \mid c^{(d)}_{t}=1 ,S_t \right]= P\left[ \sum\limits_{i\in[\![ 1,k]\!]}o^{(d)}_{t+i} \text{ is even} \mid S_t\right] 
+P\left[ o_d \in O_{t} \mid S_{t-1} = s \right] = 
+\sum\limits_{s' \in \mathcal{S}} 
+a_{s\,s'} * b_{s'\,o_d}.
 $$
 
-To compute this probability, one thus need to predict the probability that the user toggles $d$ at each round until $t+k$. This is done recursively:
+It is the sum of the probabilities, for each state $s$, that the user switches to $s$ and uses her device.
+Recursively, predicting $i$ turns in advance follows the same logic:
 
 \begin{multline*}
-P\left[o^{(d)}_{t+i}=1 \mid S_{t} \right] = \\
-\sum\limits_{s \in \mathcal{S}} P\left[ S_{t+1}=s \mid S_t\right] * P\left[o^{(d)}_{t+i}=1 \mid S_{t+1}=s \right]
+P\left[ o_d \in O_{t+i} \mid S_{t} = s \right] = \\
+\sum\limits_{s' \in \mathcal{S}}
+P\left[ S_{t+1} = s' \mid S_t = s \right] * 
+P\left[ o_d \in O_{t+i} \mid S_{t+1} = s'\right].
 \end{multline*}
-
-Knowing that the probability of toggling $d$ during the next round is computed as follows:
-
-\begin{multline*}
-P\left[o^{(d)}_{t+1}= 1 \mid S_{t} \right]=\\
-\sum\limits_{s \in \mathcal{S}} P\left[ S_{t+1}=s \mid S_{t}\right] * P\left[ o^{(d)}_{t+1}=1 \mid S_{t+1}=s\right] 
-\end{multline*}
-
-Finally, we enumerate the set $\mathcal{B}^{(k)}_\text{even}$ (resp.
-$\mathcal{B}^{(k)}_\text{even}$) of sequences of $k$ booleans having an even (resp.
-odd) number of true values, and compute the probability that device $d$ will be connected in $k$ turns, knowing that it is connected (resp.
-disconnected) at time $t$:
-
-\begin{multline*}
-P\left[c^{(d)}_{t+k}=1 \mid c^{(d)}_{t}=1 ,S_t \right]=\\
-\sum\limits_{B \in \mathcal{B}_\text{even}}\sum\limits_{i\in[\![ 1,k]\!]} P\left[o^{(d)}_{t+i}= B\left[i\right] \mid S_{t} \right]
-\end{multline*}
-
-\begin{multline*}
-P\left[c^{(d)}_{t+k}=1 \mid c^{(d)}_{t}=0 ,S_t \right]=\\
-\sum\limits_{B \in \mathcal{B}_\text{odd}}\sum\limits_{i\in[\![ 1,k]\!]} P\left[o^{(d)}_{t+i}= B\left[i\right] \mid S_{t} \right]
-\end{multline*}
-
-% \begin{multline}
-% P\left[o^{(d)}_{t+1}= 1 \mid S_{t} \right]= P\left[o^{(d)}_{t+i+1}= 1 \mid S_{t+i} \right] = \\
-% \sum\limits_{s \in \mathcal{S}} P\left[ S_{t+1}=s \mid S_{t}\right] * P\left[ o^{(d)}_{t+1}=1 \mid S_{t+1}=s\right] \\
-
-\Cref{fig:sample_usage} plots a sample device usage timeline using the previous model. 
-Each device starts offline; the user can toggle one device per round (or do nothing).
-In this figure, we show the device \emph{usage}, that is a consequence of the $\mathit{toggle}$ events defined by the HMM.
-As a consequence, several devices can be online at the same time, as happens in the figure.
-
-% Using the matrices notations:
-
-% $$
-% \begin{cases}
-% P\left[o^{(d)}_{t+i+1}=1 \mid S_{t+i} = i\right] = \sum\limits_{j \in \mathcal{S}} a_{ij} * b_{jk}\\
-
-% P\left[o^{(d)}_{t+i}=1 \mid S_{t} = i \right] = \sum\limits_{j \in \mathcal{S}} a_{ij} * P\left[o^{(d)}_{t+i}=1 \mid S_{t+1}=s \right]
-% \end{cases}
-% $$
-
-% subsubsection predicting_future_behavior (end)

### 2018-04-11 paper/algorithm.tex
changed CryptoEntity font

@@
 \NewCryptoEntity{\Carol}{C}
+% Arg, already used \mathcal{D} for the devices set
 \NewCryptoEntity{\David}{D}
 
-We consider several participants: Alice, Bob, Carol and David.
-Each of them has a set of devices, \(D_i\) (where \(i\in \{\Alice, \Bob, \Carol, 
-  \David\}\)), hereafter called their device swarm.
+% We consider several participants: Alice, Bob, Carol and David.
+% Each of them has a set of devices, \(D_i\) (where \(i\in \{\Alice, \Bob, \Carol,\David\}\)), hereafter called their device swarm.
+Alice (\Alice) and Bob (\Bob) want to exchange a file secretly: no participant should learn who sends and receives it, nor its content.
+They participate, along with Carol (\Carol) and David (\David) in the \name network.
+
 Our system is composted of two network overlays: one protocol is run between the 

### 2018-04-11 paper/privacy.tex
changed CryptoEntity font

@@
 
-We care about
-\dots
+\commentAL{``Alice and Bob want to exchange a file secretly: no participant should learn who sends and receives it, nor its content.'' (I put that in the Algorithm section for now, but should come here)}
+
+The solution we consider is strictly \ac{P2P}.
+From a privacy point-of-view, this is, at a first glance, good for privacy: 
+there will be no central provider who can monitor everyone.
+Unfortunately, with \iac{P2P} system, everything that was done in the Cloud 
+before, must now be done in the public.
+This means less privacy for Alice and Bob unless we carefully design the system 
+from a privacy perspective, which is not easy~\cite{DevilInMetadata}.
+Particular to our case, Alice and Bob will rely only on their own devices (\eg 
+smartphones, laptops, tables \etc).
+The online--offline patterns of the devices, which devices has certain files 
+\etc will reveal information about Alice and Bob's behaviour.
+We would like to limit how much of Alice's or Bob's behaviour can be learned by 
+another party.
+
+The first adversary model that we consider is friendly 
+surveillance~\cite{FriendlySurveillance}.
+Since Alice relies only on her own devices, whenever any of those devices must 
+communicate with Bob (\eg to transfer a file), this will reveal information 
+about Alice's behaviour to Bob.
+(In the same way, this will also reveal information about Bob's behaviour to 
+Alice.)
+Alice's goal is to reveal as little of her behaviour to Bob as possible.
+\commentDaniel{%
+  What do we mean by behaviour and what is \enquote{little}? See issue \#15.%
+}
+
+We would also consider what Carol can learn about Alice's and Bob's behaviour.
+Since this is \iac{P2P} system, Carol can participate and maybe Alice and Bob 
+must use Carol in their communication.
+\commentDaniel{%
+  This should be the same problem as for Bob above, it's just that Carol doesn't 
+  communicate with Alice directly.
+  So still issue \#15.%
+}
+
+%The final adversary is a network-wide adversary.
+%We know from \textcite{SystemsForAnonymousCommunication} that it is difficult to 
+%protect oneself from an adversary who can monitor the entire network 
+%(specifically the edges).

### 2018-04-12 paper/algorithm.tex
finished route_success_rate plot
described my new idea

removed big'o'file

--- 2018-04-05 paper/algorithm.tex
@@
 
-\NewCryptoEntity{\Alice}{A}
-\NewCryptoEntity{\Bob}{B}
-\NewCryptoEntity{\Carol}{C}
-\NewCryptoEntity{\David}{D}
+% \NewCryptoEntity{\Alice}{A}
+% \NewCryptoEntity{\Bob}{B}
+% \NewCryptoEntity{\Carol}{C}
+% % Arg, already used \mathcal{D} for the devices set
+% \NewCryptoEntity{\David}{D}
 
-We consider several participants: Alice, Bob, Carol and David.
-Each of them has a set of devices, \(D_i\) (where \(i\in \{\Alice, \Bob, \Carol, 
-  \David\}\)), hereafter called their device swarm.
-Our system is composted of two network overlays: one protocol is run between the 
-devices in \(D_i\) (the Device Swarm Protocol) to gain knowledge on the 
-swarm, and another run between different swarms (the Inter-Swarm Protocol) to 
-keep global knowledge.
-Finally, our file-sharing protocol uses the local and global 
-knowledges to coordinate file sharing between devices in different swarms.
+\newcommand{\Alice}{\ensuremath{\mathscr{A}}}
+\newcommand{\Bob}{\ensuremath{\mathscr{B}}}
 
-\subsection{The Device Swarm Protocol}%
-\label{DeviceSwarmProtocol}
+\newcommand{\localoverlay}{Squad Overlay}
+\newcommand{\globaloverlay}{Global Overlay}
 
-A user's devices, \(D_i\), use the Device Swarm Protocol to coordinate 
-themselves.
-More specifically, the devices use this protocol to keep the swarm state up to 
-date.
-The swarm state contains:
+A set of users $\mathcal{U}$ participate in the \name network.
+Each user $u \in \mathcal{U}$ has a set $\mathcal{D}_u$ of devices that contribute to the system when online.
+Alice and Bob use \name to exchange a file secretly: no participant will learn who sends and receives it, nor its content.
+
+On one hand, a user's devices must exchange information among themselves to learn the user's behavior \commentAL{Can we skip files mapping, pretty please?} and map files to devices.
+We call this part of the protocol the \localoverlay, and present it in section~\ref{local overlay}. 
+On the other hand, user's collectively upload the list of their connected devices and associated future predictions to a Distributed Hash Table (DHT): it serves as a registry of online peers (including connection probabilities for the next turn), and for the routing of files.
+We describe this \globaloverlay in section~\ref{global overlay}. 
+File exchange between two users is enabled by the two previous protocols, and is covered in section~\ref{file exchange}
+
+\subsection{The \localoverlay}%
+\label{local overlay}
+
+A user's devices, \(D_i\), use the \localoverlay to:
+\begin{enumerate}
+	\item Share information about the user's behavior.
+	Devices use it to build a behavioral model and infer their future connection probability;
+	\item Share files location \commentAL{Maybe...}
+\end{enumerate}
+
+\subsubsection{Sharing the user's behavior} % (fold)
+\label{ssub:sharing_the_user_s_behavior}
+
+Each device initially only knows when it is connected. 
+To make a model of the user's behavior, they need to know the whole observation sequence $O$: which device is online at each time step.
+To do so, they employ a probabilistic dissemination protocol, based on previous work from our team \cite{luxey:hal-01704172}.
+This algorithm, called \textsc{Sprinkler}, allows devices to gossip any new connection information to random peers, ensuring that all devices know the full observation sequence with a very high probability.
+\textsc{Sprinkler} has shown resilient to devices churn \cite{luxey:cascade}, and is thus perfectly suited for our purpose, where a user's devices often disconnect and reconnect.
+
+\commentAL{Then we \textbf{maybe} do predictions as \textbf{maybe} shown in section~\ref{sec:user_model}.}
+
+% subsubsection sharing_the_user_s_behavior (end)
+
+\subsubsection{Sharing files location} % (fold)
+\label{ssub:sharing_files_location}
+
+We do stuff and things work.
+
+% subsubsection sharing_files_location (end)
+
+\subsection{The \globaloverlay}%
+\label{global overlay}
+
+% All swarms participate in the Inter-Swarm Protocol to coordinate the global 
+% knowledge needed by the swarms to interact.
+% More specifically, the global knowledge contains:
+% \begin{itemize}
+%   \item A table, \(R\), of devices available for routing;
+%   \item A key--value store, \(S = \{0, 1\}^\lambda\times \{0, 1\}^*\), mapping 
+%     fixed-length strings of length \(\lambda\) to arbitrary-length strings.
+% \end{itemize}
+
+Every device in the system participates in a Distributed Hash Table (DHT) that is used for two purposes:
+\begin{enumerate}
+	\item Providing routing information to nodes during file exchange. This is discussed in-depth in section~\ref{file exchange};
+	\item Listing online devices and their probability of being online next time step.
+\end{enumerate}
+
+Every time a device is online, it sends the following information to the DHT:
 \begin{itemize}
-  \item A knowledge vector, \(A_i\), encoding a Markov chain to predict online 
-    and offline patterns for the various devices to predict when and for how 
-    long each device might be available before disappearing again;
-  \item A table, \(F_i = N_i\times \powerset(D_i)\), mapping a user's file names 
-    (\(N_i\)) to its devices (\(D_i\)) that store a copy of that file.
+	\item the time \commentAL{step?};
+	\item its address;
+	\item its public key;
+	\item the probability that it will still be connected next turn \commentAL{no interest in t+2 and more.}
 \end{itemize}
 
-\commentDaniel{What should we reuse from the session-handoff paper?}
+\commentAL{Cite DHT articles and emphasize their security guarantees.}
 
-\subsection{The Inter-Swarm Protocol}%
-\label{InterSwarmProtocol}
+\subsection{The file exchange}%
+\label{file exchange}
 
-All swarms participate in the Inter-Swarm Protocol to coordinate the global 
-knowledge needed by the swarms to interact.
-More specifically, the global knowledge contains:
-\begin{itemize}
-  \item A table, \(R\), of devices available for routing;
-  \item A key--value store, \(S = \{0, 1\}^\lambda\times \{0, 1\}^*\), mapping 
-    fixed-length strings of length \(\lambda\) to arbitrary-length strings.
-\end{itemize}
+We consider two users, Alice and Bob, such that Alice wants to send a file to Bob secretly.
+They want to keep the file content secret to anybody but them; \name's users should not know who sent a file to whom; and Alice and Bob want to hide their address from one another.
 
-\subsection{File-sharing protocol}%
-\label{FileSharingProtocol}
+In other words, \name must guarantee \emph{sender-receiver anonymity}.
+To achieve this, communications go through onion routes, using rendez-vous points.
+Our approach is tightly based on the Tor seminal paper \cite{Tor}.
 
-\begin{figure}[t]
-\centering
-\includegraphics[width=0.8\columnwidth]{figures/schema.pdf}
-\caption{\label{fig:pipeline}Pipeline of the steps undergone by Alice when he shares a file from his laptop L with Bob.}
-\end{figure}
+\subsubsection{File exchange process} % (fold)
+\label{ssub:file_exchange_process}
 
-\Cref{fig:pipeline} depicts the process of a file exchange from Alice to Bob.
-The file $f$ is initially located on Alice's laptop $L$, which is potentially offline for now.
-Firstly, Alice and Bob need to exchange encryption keys and the key $ID_f$ 
-referencing the file on the \ac{DHT}.
-They do so \emph{out-of-band}, that is using another channel than the one 
-presented here (\eg bluetooth, email, \etc).
+Firstly, Alice and Bob must exchange information out-of-band: an encryption key $ek$ to cipher the file, and an ID $k$ in the DHT pointing to information on how to reach Alice.
 
-Then, Alice queries the DHT for devices that will most likely be online at the same time as his laptop $L$.
-To this end, Alice uses his knowledge on his devices connection patterns $A_i$, along with the DHT's public information on devices connections.
-Once Alice and the DHT agreed upon a set of peers $(M_1, M_2, M_3)$, their address is put in the DHT at the key $ID_f$ referencing the file of interest.
+The device that contains Alice's file \commentAL{I don't like that dependence on the file's location} creates routes to several Introductory Points (IP), chosen at random among connected peers.
+Alice uploads the addresses of her IP to the DHT at the position $k$.
+One of Bob's devices creates routes to several Rendez-Vous points (RV), randomly picked among peers that will be connected in the next time step.
+Bob fetches the addresses of Alice's IP from the DHT.
+Then, he sends a packet containing the addresses of its chosen RV to Alice's IPs.
+The IP nodes forward the packet to Alice's device. 
+Alice chunks her file into pieces of a predefined size, encrypted using $ek$.
 
-At the third step, Alice's laptop $L$ becomes available. 
-Informed of the ongoing file exchange by Alice's Device Swarm Protocol, $L$ fetches the addresses of $M_1, M_2$ and $M_3$ on the DHT using the key $ID_f$.
-These peers will serve as middle-men: $L$ sends them redundant chunks of $f$ through an onion route (thus remaining anonymous), for Bob to fetch them later.
+Starting from the next round, Alice will send all chunks of her file to Bob's RV, that will forward it to Bob.
+Once the file is received, everybody is happy and all routes are killed.
 
-In the last forth step, Bob fetches the file $f$ using any of her devices.
-To do so, she uses the key $ID_f$ to learn the addresses of $M_1, M_2$ and $M_3$.
-Then, she fetches parts of $f$ from the online middle-men through an onion route.
-Given that $L$ sent redundant chunks to the middle-men, Bob will not need every middle-man to be connected to fetch the whole file.
-Once Bob has completed the download, the key $ID_f$ is flushed on the DHT.
+% subsubsection file_exchange_process (end)
 
-% When Alice and Bob want to exchange a file owned by Alice, they first need to exchange their
+\subsubsection{Onion routes in face of churn} % (fold)
+\label{ssub:onion_routes_in_face_of_churn}
 
-% When Alice wants to transfer a file to Bob, she will find which devices have the 
-% file (from \(F_i\)), then predict when any of those devices will be available 
-% (from \(A_i\)).
-% Then she will construct a probabilistic onion route with her devices as the 
-% destinations.
-% She will encrypt this route for Bob and transfer it to him, who now can use the 
-% onion route to fetch the file.
+An onion route between A and B consists of several servers (usually three) that serve as relays, say $r_1, r_2$ and $r_3$. 
+The route will have a fixed order: $A \rightarrow r_1 \rightarrow r_2 \rightarrow r_3 \rightarrow B$.
+Every time data travels through the onion route, it is encrypted---along with its header---with symmetric keys, such that no-one except the sender and the receiver can read its content.
+A node only knows its direct predecessor (that sent the packet) and its direct successor (whose address is the only one readable by it) on the route, such that only the creator of the route (A) knows the destination (B).
+
+Alas, when one node goes down along the way, the route has to be recreated, at least partly.
+Alice will be informed of the crash by the predecessor of the failed node with a control message, using the onion route.
+Then, she will have to select a new connected peer, and ask the predecessor of the failed node to re-establish the route using this new peer.
+This is fine in scenarii where participating servers only fail sporadically.
+But in our setup, where devices disconnection is a certainty, we need a more robust approach.
+
+We select several relays at each point of the route: $R_i=\{r_{i,j}\}$ would be the \emph{set} of possibly disconnected devices that will take the $i^\text{th}$ position in our onion route.
+In traditional onion routing, $r_1$ is the only one knowing the address of $r_2$, because it is written encrypted with its public key in the header.
+Here, every device in the $R_i$ can read the set $R_{i+1}$ in the header, because the symmetric key $sk$ used to encrypt the set $R_{i+1}$ is known to every device in $R_i$.
+The header indeed contains a version of $sk$ for each device $r_{i,j}$, encrypted with its own public key $pk_{r_{i,j}}$.
+
+In the following equation, $S(sk,\texttt{message})$ means that $\texttt{message}$ is encrypted with the symmetric key $sk$, while $P(pk, \texttt{message})$ means that $\texttt{message}$ is encrypted using the public key $pk$.
+Follows the content of the header in our version of the onion routing, considering that $R_i=\{r_{i,1}, r_{i,2}, r_{i,3}\}$, that $pk_{r_{i,j}}$ is $r_{i,j}$'s public key, and that $||$ means concatenation:
+
+$$ P(pk_{r_{i,1}}, sk) || P(pk_{r_{i,2}}, sk) || P(pk_{r_{i,3}}, sk) || S(sk, R_{i+1}) $$
+
+(I read that this is how PGP handles multiple recipients.)
+
+% subsubsection onion_routes_in_face_of_churn (end)
+
+% \begin{figure}[t]
+% \centering
+% \includegraphics[width=0.8\columnwidth]{figures/schema.pdf}
+% \caption{\label{fig:pipeline}Pipeline of the steps undergone by Alice when he shares a file from his laptop L with Bob.}
+% \end{figure}
+
+% \Cref{fig:pipeline} depicts the process of a file exchange from Alice to Bob.
+% The file $f$ is initially located on Alice's laptop $L$, which is potentially offline for now.
+% Firstly, Alice and Bob need to exchange encryption keys and the key $ID_f$ 
+% referencing the file on the \ac{DHT}.
+% They do so \emph{out-of-band}, that is using another channel than the one 
+% presented here (\eg bluetooth, email, \etc).
+
+% Then, Alice queries the DHT for devices that will most likely be online at the same time as his laptop $L$.
+% To this end, Alice uses his knowledge on his devices connection patterns $A_i$, along with the DHT's public information on devices connections.
+% Once Alice and the DHT agreed upon a set of peers $(M_1, M_2, M_3)$, their address is put in the DHT at the key $ID_f$ referencing the file of interest.
+
+% At the third step, Alice's laptop $L$ becomes available. 
+% Informed of the ongoing file exchange by Alice's Device Swarm Protocol, $L$ fetches the addresses of $M_1, M_2$ and $M_3$ on the DHT using the key $ID_f$.
+% These peers will serve as middle-men: $L$ sends them redundant chunks of $f$ through an onion route (thus remaining anonymous), for Bob to fetch them later.
+
+% In the last forth step, Bob fetches the file $f$ using any of her devices.
+% To do so, she uses the key $ID_f$ to learn the addresses of $M_1, M_2$ and $M_3$.
+% Then, she fetches parts of $f$ from the online middle-men through an onion route.
+% Given that $L$ sent redundant chunks to the middle-men, Bob will not need every middle-man to be connected to fetch the whole file.
+% Once Bob has completed the download, the key $ID_f$ is flushed on the DHT.

### 2018-04-12 paper/intro.tex
finished route_success_rate plot
described my new idea

removed big'o'file

@@
 \commentDaniel{Summarize our results.}
+
+\commentAL{The proposal:}We propose \name, a \ac{P2P} system for secret file exchange.
+Using only devices owned by participants, \name creates onion routes that allow two users to exchange a file such that nobody is able to determine the content of the file, nor its source and destination.
+Personal devices, unlike servers, often disconnect from the network.
+To permit reliable file exchange despite the unreliability of the nodes constituting the system, we use devices' knowledge on their owner's behavior to predict future (dis)connections.

### 2018-04-12 paper/user-model.tex
finished route_success_rate plot
described my new idea

removed big'o'file

@@
 We consider a single user, owning a set of $\mathcal{D}$ devices.
-Time is discretized, and the devices' observations are independent: Alice can have her laptop and phone connected at the same time.
+Time is discretized \commentAL{Discretized/synchronous time needs more explanation}.
+Needs, and the devices' observations are independent: Alice can have her laptop and phone connected at the same time.
 The hidden process $S=S_1,\dots,S_T$ is built from an alphabet of states $\mathcal{S}$, while the observable process $O=O_1, \dots, \O_T$ contains events from the alphabet $\mathcal{O}$.
@@
 \label{ssub:predicting_future_behavior}
-\commentAL{Why we need to make these predictions is not explained yet.}
 Devices want to predict whether they are likely to be connected in the near future.
@@
 It is the sum of the probabilities, for each state $s$, that the user switches to $s$ and uses her device.
+\commentAL{Following maybe not needed if we only use $t+1$:}
 Recursively, predicting $i$ turns in advance follows the same logic:
@@
 \end{multline*}
+
+\commentAL{In conclusion: we want more unicorns at the Olympic Games.}
+
+\commentAL{I don't mention prediction yet since I am not sure we get good enough results.}

### 2018-04-15 code/modules/device.py
worked on implem; renamed python folder to code

@@ -1,0 +1,35 @@
+#!/usr/bin/env python3
+
+import numpy as np
+from .peers_view import PeersView
+
+ADDR_SIZE = 12
+
+DEFAULT_GOSSIP_SIZE = 6
+DEFAULT_VIEW_SIZE = 20
+
+
+class Device:
+    def __init__(
+            self, owner, global_view,
+            gossip_size=DEFAULT_GOSSIP_SIZE,
+            view_size=DEFAULT_VIEW_SIZE):
+
+        self.owner = owner
+        self.global_view = global_view
+        self.gossip_size = gossip_size
+        self.view_size = view_size
+        self.peers_view = PeersView(view_size)
+        self.addr = random_string(ADDR_SIZE)
+
+        self.files = []  # ?
+
+    def random_peer_sampling(self):
+        self.peers_view.insert(
+            self.global_view.get_sample(n=self.gossip_size))
+
+
+def random_string(n):
+    ''.join(
+        [random.choice(string.ascii_lowercase+string.digits)
+         for _ in range(n)])

### 2018-04-15 code/modules/peers_view.py

@@ -1,0 +1,40 @@
+#!/usr/bin/env python3
+
+import pandas as pd
+
+COLUMNS = ["t", "addr", "p"]
+
+
+class PeersView:
+    def __init__(self, max_size):
+        self.view = pd.DataFrame(columns=COLUMNS)
+        self.max_size = max_size
+
+    def put(self, t, addr, p, prune=True):
+        self.view = self.view[self.view['addr'] != addr]
+
+        self.view = self.view.append(
+            pd.DataFrame({
+                't': t,
+                'addr': addr,
+                'p': p
+            }, index=[t])
+        )
+
+        self._prune_view()
+
+    def insert(self, items):
+        for item in items:
+            self.put(*item, prune=False)
+
+        self._prune_view()
+
+    def get_sample(self, n=3):
+        if n > self.view.shape[0]:
+            n = self.view.shape[0]
+
+        return self.view.sample(n=n).values
+
+    def _prune_view(self):
+        if self.view.shape[0] > self.max_size:
+            self.view = self.view[self.view.shape[0] - self.max_size:]

### 2018-04-15 code/modules/user.py

@@ -1,0 +1,9 @@
+#!/usr/bin/env python3
+
+import numpy as np
+
+
+class User:
+    def __init__(self):
+        self.devices = None
+        self.model = None

### 2018-04-16 code/modules/device.py
several users

@@ -1,35 +1,51 @@
 #!/usr/bin/env python3
 
-import numpy as np
+# import numpy as np
 from .peers_view import PeersView
+from datetime import timedelta, datetime
+import random
+import string
 
 ADDR_SIZE = 12
 
-DEFAULT_GOSSIP_SIZE = 6
-DEFAULT_VIEW_SIZE = 20
+DEFAULT_GOSSIP_SIZE = 10
+DEFAULT_EXPIRATION_PERIOD = timedelta(seconds=1)
 
 
 class Device:
     def __init__(
-            self, owner, global_view,
+            self, owner, global_view, device_id,
             gossip_size=DEFAULT_GOSSIP_SIZE,
-            view_size=DEFAULT_VIEW_SIZE):
+            expiration_period=DEFAULT_EXPIRATION_PERIOD):
 
         self.owner = owner
         self.global_view = global_view
+        self.device_id = device_id
         self.gossip_size = gossip_size
-        self.view_size = view_size
-        self.peers_view = PeersView(view_size)
+        self.peers_view = PeersView(expiration_period)
         self.addr = random_string(ADDR_SIZE)
+        self.is_online = False
 
         self.files = []  # ?
 
+    def act(self, is_online):
+        self.is_online = is_online
+        if is_online:
+            self.global_view.put(
+                datetime.now(),
+                self.addr,
+                self.owner.get_prediction(self.device_id)
+            )
+            self.random_peer_sampling()
+
     def random_peer_sampling(self):
         self.peers_view.insert(
-            self.global_view.get_sample(n=self.gossip_size))
+            self.global_view.get_sample(
+                n=self.gossip_size,
+                exclude_addr=self.addr))
 
 
 def random_string(n):
-    ''.join(
+    return ''.join(
         [random.choice(string.ascii_lowercase+string.digits)
          for _ in range(n)])

### 2018-04-16 code/modules/peers_view.py

@@ -1,14 +1,16 @@
 #!/usr/bin/env python3
 
 import pandas as pd
+from datetime import timedelta, datetime
 
 COLUMNS = ["t", "addr", "p"]
 
 
 class PeersView:
-    def __init__(self, max_size):
+    def __init__(self, expiration_period=timedelta(seconds=1)):
         self.view = pd.DataFrame(columns=COLUMNS)
-        self.max_size = max_size
+
+        self.expiration_period = expiration_period
 
     def put(self, t, addr, p, prune=True):
         self.view = self.view[self.view['addr'] != addr]
@@ -21,20 +23,35 @@ class PeersView:
             }, index=[t])
         )
 
-        self._prune_view()
+        if prune:
+            self._prune_view()
 
+    # Items is a dataframe
     def insert(self, items):
-        for item in items:
-            self.put(*item, prune=False)
+        if len(items) == 0:
+            return
+        # print("insert:")
+        # print(type(items))
+        # print(items)
+
+        for _, item in items.iterrows():
+            self.put(item['t'], item['addr'], item['p'], prune=False)
 
         self._prune_view()
 
-    def get_sample(self, n=3):
-        if n > self.view.shape[0]:
-            n = self.view.shape[0]
+    def get_sample(self, n=3, exclude_addr=None):
+        view = self.view[self.view['addr'] != exclude_addr]
 
-        return self.view.sample(n=n).values
+        if n > view.shape[0]:
+            n = view.shape[0]
+        if n == 0:
+            return []
+
+        return view.sample(n=n)
 
     def _prune_view(self):
-        if self.view.shape[0] > self.max_size:
-            self.view = self.view[self.view.shape[0] - self.max_size:]
+        # Time-bound
+        expiration_limit = datetime.now() - self.expiration_period
+
+        # print(self.view.index)
+        self.view = self.view[self.view.index >= expiration_limit]

### 2018-04-16 code/modules/user.py

@@ -1,9 +1,34 @@
 #!/usr/bin/env python3
 
 import numpy as np
+from . import model, device
 
 
 class User:
-    def __init__(self):
-        self.devices = None
-        self.model = None
+    def __init__(self, global_view):
+        self.model = model.get_random()
+
+        self.n_devices = self.model.n_obs
+        # Create devices
+        self.devices = [None] * self.n_devices
+        for d_id in range(self.n_devices):
+            self.devices[d_id] = device.Device(self, global_view, d_id)
+
+        self.current_state = None
+        self.state_history = []
+        self.devices_history = []
+
+    def act(self):
+        states, devices = self.model.sample(
+            length=1, previous_state=self.current_state)
+        # Model.sample returns array indexed by time
+        # here we need sample[0] = t+1
+        self.current_state = states[0]
+        self.state_history.append(self.current_state)
+        self.devices_history.append(devices[0])
+
+        for d_id, is_online in enumerate(devices[0]):
+            self.devices[d_id].act(is_online)
+
+    def get_prediction(self, device_id):
+        return self.model.predict(1, device_id, self.current_state)[0]

### 2018-04-17 paper/primitives.tex
Adds primitives section

\section{Primitives}%
\label{Primitives}

The algorithm (\cref{Algorithm}) makes use of several primitives, which we 
describe here.
There is a local prediction oracle (described in \cref{LocalPrediction}) which 
is used by a device to predict its own online behaviour.

\subsection{Local prediction oracle}%
\label{LocalPrediction}

\NewScheme{\LP}{P_L}
\NewAlgorithm{\LNext}{Next}
\NewAlgorithm{\LProb}{Prob}

We have a local prediction oracle, \(\LP\), which provides the following two 
algorithms:
\begin{description}
  \item[\(\LNext\)] Test \dots
  \item[\(\LProb\)] \dots
\end{description}
We will denote these as \(\LP[\LNext]\) and \(\LP[\LProb]\).

\subsection{Global prediction oracle}

### 2018-04-17 paper/algorithm.tex
Fixes Syntastic warnings

@@
 On one hand, a user's devices must exchange information among themselves to learn the user's behavior \commentAL{Can we skip files mapping, pretty please?} and map files to devices.
-We call this part of the protocol the \localoverlay, and present it in section~\ref{local overlay}. 
-On the other hand, user's collectively upload the list of their connected devices and associated future predictions to a Distributed Hash Table (DHT): it serves as a registry of online peers (including connection probabilities for the next turn), and for the routing of files.
-We describe this \globaloverlay in section~\ref{global overlay}. 
-File exchange between two users is enabled by the two previous protocols, and is covered in section~\ref{file exchange}
+We call this part of the protocol the \localoverlay, and present it in 
+\cref{local overlay}. On the other hand, user's collectively upload the list of 
+their connected devices and associated future predictions to a Distributed Hash 
+Table (DHT): it serves as a registry of online peers (including connection 
+probabilities for the next turn), and for the routing of files.
+We describe this \globaloverlay in \cref{global overlay}. File exchange between 
+two users is enabled by the two previous protocols, and is covered in \cref{file 
+  exchange}
 
@@
 	Devices use it to build a behavioral model and infer their future connection probability;
-	\item Share files location \commentAL{Maybe...}
+  \item Share files location \commentAL{Maybe \dots}
 \end{enumerate}
 
-\subsubsection{Sharing the user's behavior} % (fold)
+\subsubsection{Sharing the user's behavior}% (fold)
 \label{ssub:sharing_the_user_s_behavior}
@@
 To make a model of the user's behavior, they need to know the whole observation sequence $O$: which device is online at each time step.
-To do so, they employ a probabilistic dissemination protocol, based on previous work from our team \cite{luxey:hal-01704172}.
+To do so, they employ a probabilistic dissemination protocol, based on previous work from our team~\cite{luxey:hal-01704172}.
 This algorithm, called \textsc{Sprinkler}, allows devices to gossip any new connection information to random peers, ensuring that all devices know the full observation sequence with a very high probability.
-\textsc{Sprinkler} has shown resilient to devices churn \cite{luxey:cascade}, and is thus perfectly suited for our purpose, where a user's devices often disconnect and reconnect.
+\textsc{Sprinkler} has shown resilient to devices churn~\cite{luxey:cascade}, and is thus perfectly suited for our purpose, where a user's devices often disconnect and reconnect.
 
-\commentAL{Then we \textbf{maybe} do predictions as \textbf{maybe} shown in section~\ref{sec:user_model}.}
+\commentAL{Then we \textbf{maybe} do predictions as \textbf{maybe} shown in 
+  \cref{sec:user_model}.}
 
@@
 
-\subsubsection{Sharing files location} % (fold)
+\subsubsection{Sharing files location}% (fold)
 \label{ssub:sharing_files_location}
@@
 \begin{enumerate}
-	\item Providing routing information to nodes during file exchange. This is discussed in-depth in section~\ref{file exchange};
+  \item Providing routing information to nodes during file exchange. This is 
+    discussed in-depth in \cref{file exchange};
 	\item Listing online devices and their probability of being online next time step.
@@
 To achieve this, communications go through onion routes, using rendez-vous points.
-Our approach is tightly based on the Tor seminal paper \cite{Tor}.
+Our approach is tightly based on the Tor seminal paper~\cite{Tor}.
 
-\subsubsection{File exchange process} % (fold)
+\subsubsection{File exchange process}% (fold)
 \label{ssub:file_exchange_process}
@@
 
-\subsubsection{Onion routes in face of churn} % (fold)
+\subsubsection{Onion routes in face of churn}% (fold)
 \label{ssub:onion_routes_in_face_of_churn}

### 2018-04-17 paper/algorithm.tex
Fixes more Syntastic warnings

@@
 
-\newcommand{\localoverlay}{Squad Overlay}
-\newcommand{\globaloverlay}{Global Overlay}
+\newcommand{\localoverlay}{Squad Overlay\xspace}
+\newcommand{\globaloverlay}{Global Overlay\xspace}
 
@@
 We call this part of the protocol the \localoverlay, and present it in 
-\cref{local overlay}. On the other hand, user's collectively upload the list of 
+\cref{local-overlay}. On the other hand, user's collectively upload the list of 
 their connected devices and associated future predictions to a Distributed Hash 
@@
 probabilities for the next turn), and for the routing of files.
-We describe this \globaloverlay in \cref{global overlay}. File exchange between 
+We describe this \globaloverlay in \cref{global-overlay}. File exchange between 
 two users is enabled by the two previous protocols, and is covered in \cref{file 
@@
 \subsection{The \localoverlay}%
-\label{local overlay}
+\label{local-overlay}
 
@@
 \subsection{The \globaloverlay}%
-\label{global overlay}
+\label{global-overlay}
 
@@
   \item Providing routing information to nodes during file exchange. This is 
-    discussed in-depth in \cref{file exchange};
+    discussed in-depth in \cref{file-exchange};
 	\item Listing online devices and their probability of being online next time step.
@@
 \subsection{The file exchange}%
-\label{file exchange}
+\label{file-exchange}
 
@@
 One of Bob's devices creates routes to several Rendez-Vous points (RV), randomly picked among peers that will be connected in the next time step.
-Bob fetches the addresses of Alice's IP from the DHT.
+Bob fetches the addresses of Alice's IP from the \ac{DHT}.
 Then, he sends a packet containing the addresses of its chosen RV to Alice's IPs.
@@
 Follows the content of the header in our version of the onion routing, considering that $R_i=\{r_{i,1}, r_{i,2}, r_{i,3}\}$, that $pk_{r_{i,j}}$ is $r_{i,j}$'s public key, and that $||$ means concatenation:
-
-$$ P(pk_{r_{i,1}}, sk) || P(pk_{r_{i,2}}, sk) || P(pk_{r_{i,3}}, sk) || S(sk, R_{i+1}) $$
+\[
+  P(pk_{r_{i,1}}, sk) || P(pk_{r_{i,2}}, sk) || P(pk_{r_{i,3}}, sk) || S(sk, 
+  R_{i+1})
+\]
 

### 2018-04-17 paper/algorithm.tex
Fixes a broken \cref
Adds figures with algorithmic overviews

@@
 
+\NewScheme{\SPOR}{SPOR}
+\NewAlgorithm{\Send}{Send}
+\NewAlgorithm{\Recv}{Receive}
+
+\NewVariable{\rdv}{rdv}
+\NewAlgorithm{\Enc}{Enc}
+\NewVariable{\pk}{pk}
+\NewAlgorithm{\Fwd}{Forward}
+\NewAlgorithm{\Dec}{Dec}
+\NewVariable{\sk}{sk}
+
+We have the Secure Probabilistic Onion Routing scheme, \SPOR, which provides 
+onion-routed message passing.
+\(\SPOR\) provides two algorithms: \(\SPOR[\Send]\) (\cref{SPORSend}), 
+\(\SPOR[\Fwd]\) (\cref{SPORFwd}) and \(\SPOR[\Recv]\) (\cref{SPORRecv}).
+
+\NewAlgorithm{\ExtendRoute}{ExtendRoute}
+\NewAlgorithm{\GetRouteNode}{GetRouteNode}
+\NewAlgorithm{\GetRandomPeer}{GetRandomPeer}
+
+\begin{figure}
+  \begin{algorithmic}
+    \Require{%
+      $D$ is the set of alternative destination devices,
+      $L$ is the length of the route,
+      $\theta$ is the threshold of probability of failure.%
+    }
+    \Function{\ExtendRoute}{$H, L, \theta$}
+      \If{$L\leq 0$}
+        \State \Return $H$
+      \EndIf
+      \State $D\gets \GetRouteNode[\theta]$
+      \State $H\gets D\concat \Enc[_{\pk_{D}}][H]$
+      \State \Return $\ExtendRoute[H, L-1, \theta]$
+    \EndFunction
+
+    \Function{\GetRouteNode}{$\theta$}
+      \State $D\gets \GetRandomPeer$
+      \While{$\prod_{d\in D} \Pr[d \text{ offline}] > \theta$}
+        \State $D\gets D\cup \GetRandomPeer$
+      \EndWhile
+      \State \Return $D$
+    \EndFunction
+  \end{algorithmic}
+  \caption{%
+    The function \(\ExtendRoute\) extends a route with \(L\) hops and failure 
+    threshold of \(\theta\) for each hop in the route.
+    Thus the probability of failure for the whole route is \(1 - (1 - 
+      \theta)^L\).
+    The function \(\GetRandomPeer\) is any random peer-sampling algorithm.
+  }
+\end{figure}
+
+\begin{figure}
+  \begin{algorithmic}
+    \Require{%
+      $D$ is the set of alternative recipient devices.
+    }
+    \Function{\SPOR[\Recv]}{$D$}
+      \State $H_\rdv\gets \ExtendRoute[D\concat \bot, L, \theta]$
+      \State Give $H_\rdv$ to sender out-of-bound.
+      \State Wait to receive message.
+    \EndFunction
+  \end{algorithmic}
+  \caption{\label{SPORRecv}%
+    The recipient function.%
+  }
+\end{figure}
+
+\begin{figure}
+  \begin{algorithmic}
+    \Require{%
+      $m$ is the message to be sent,
+      $H_\rdv$ is the onion-route given by the recipient (its first node is the 
+      rendez-vous point).
+    }
+    \Function{\SPOR[\Send]}{$m, H_\rdv$}
+    \EndFunction
+  \end{algorithmic}
+  \caption{\label{SPORSend}%
+    The algorithm for creating a probabilistic onion route.
+    \(d\) is the destination address, \(m\) is the message, \(H_\rdv\) is the 
+    header for the rendez-vous point selected by \(d\).%
+  }
+\end{figure}
+
+\begin{figure}
+  \begin{algorithmic}
+    \Require{$\pk, \sk$ is the public--private key-pair of the node.}
+    \Function{\SPOR[\Fwd]}{$C_H$}
+      \State $H\gets \Dec[_\sk][C_H]$
+      \If{$H = \bot$}
+        \State \Return $\bot$
+      \EndIf
+      \State $\{d_i\}\concat H'\gets H$
+      \For{$d\in \{d_i\}$}
+        \Comment{Uniformly randomly chosen}
+        \If{$d\method \Fwd[H'] \neq \bot$}
+          \State \Return $\top$
+        \EndIf
+      \EndFor
+      \State \Return $\bot$
+    \EndFunction
+  \end{algorithmic}
+  \caption{\label{SPORFwd}%
+    The forwarding function for a node in a probabilistic onion route.%
+  }
+\end{figure}
+
 A set of users $\mathcal{U}$ participate in the \name network.
@@
 We describe this \globaloverlay in \cref{global-overlay}. File exchange between 
-two users is enabled by the two previous protocols, and is covered in \cref{file 
-  exchange}
+two users is enabled by the two previous protocols, and is covered in 
+\cref{file-exchange}
 

### 2018-04-18 paper/algorithm.tex
Adds high-level description of SPOR

@@
 \NewAlgorithm{\Send}{Send}
+\NewAlgorithm{\Fwd}{Forward}
 \NewAlgorithm{\Recv}{Receive}
@@
 \NewVariable{\pk}{pk}
-\NewAlgorithm{\Fwd}{Forward}
 \NewAlgorithm{\Dec}{Dec}
@@
 \(\SPOR[\Fwd]\) (\cref{SPORFwd}) and \(\SPOR[\Recv]\) (\cref{SPORRecv}).
+Say Alice (sender) wants to send a message \(m\) to Bob (recipient).
+Bob uses \(\SPOR[\Recv]\) to create a probabilistic onion route \(H_\rdv\) from 
+a rendez-vous point (\(\rdv\) below) to its own device swarm --- all the hops on 
+the route are chosen by Bob uniformly at random.
+Bob gives \(H_\rdv\) to Alice using an out-of-band channel.
+Alice uses \(\SPOR[\Send]\) at some later time to send the message to Bob using 
+any of her devices.
+\(\SPOR[\Send]\) extends the route \(H_\rdv\) with some hops of Alice's 
+choosing, then lets the probabilistic nodes of the route forward the message 
+(using \(\SPOR[\Fwd]\)) through to Bob.
 
@@
     }
-    \Function{\SPOR[\Send]}{$m, H_\rdv$}
+    \Function{\SPOR[\Send]}{$m, \pk_D, H_\rdv$}
+      \State $H\gets \ExtendRoute[H_\rdv, L, \theta]$
+      \State $c_m\gets \Enc[_{\pk_D}][m]$
+      \State $D\concat C_H\gets H_\rdv$
+      \For{$d\in D$}
+        \Comment{Uniformly randomly chosen}
+        \If{$d\method \Fwd[c_m, C_H] \neq \bot$}
+          \State \Return $\top$
+        \EndIf
+      \EndFor
+      \State \Return $\bot$
     \EndFunction
@@
     \Require{$\pk, \sk$ is the public--private key-pair of the node.}
-    \Function{\SPOR[\Fwd]}{$C_H$}
+    \Function{\SPOR[\Fwd]}{$c_m, C_H$}
       \State $H\gets \Dec[_\sk][C_H]$
@@
       \EndIf
-      \State $\{d_i\}\concat H'\gets H$
+      \State $\{d_i\}\concat C_H'\gets H$
       \For{$d\in \{d_i\}$}
         \Comment{Uniformly randomly chosen}
-        \If{$d\method \Fwd[H'] \neq \bot$}
+        \If{$d\method \Fwd[c_m, C_H'] \neq \bot$}
           \State \Return $\top$

### 2018-04-19 paper/algorithm.tex
Adds comment about outdated content
Changes route creation to be "offline at time t" (for predictions)
Clarifies algorithm figures, improves figure texts

@@
     \Require{%
-      $D$ is the set of alternative destination devices,
+      $H$ is a header of the form \(D\concat H'\) or \(D\concat \top\), where 
+      \(D\) is a set of device addresses.
       $L$ is the length of the route,
@@
       \State $D\gets \GetRandomPeer$
-      \While{$\prod_{d\in D} \Pr[d \text{ offline}] > \theta$}
+      \While{$\prod_{d\in D} \Pr[d \text{ offline at time } t] > \theta$}
         \State $D\gets D\cup \GetRandomPeer$
@@
   \end{algorithmic}
-  \caption{%
-    The function \(\ExtendRoute\) extends a route with \(L\) hops and failure 
-    threshold of \(\theta\) for each hop in the route.
-    Thus the probability of failure for the whole route is \(1 - (1 - 
-      \theta)^L\).
+  \caption{\label{ExtendRoute}%
+    The \(\ExtendRoute\) algorithm extends a route \(H\) with \(L\) hops and 
+    failure threshold of \(\theta\) for each hop in the route.
+    Thus the probability of failure for the extension is \(1 - (1 - \theta)^L\).
     The function \(\GetRandomPeer\) is any random peer-sampling algorithm.
@@
 \end{figure}
+
+\NewAlgorithm{\Store}{Store}
 
@@
     \Function{\SPOR[\Recv]}{$D$}
-      \State $H_\rdv\gets \ExtendRoute[D\concat \bot, L, \theta]$
-      \State Give $H_\rdv$ to sender out-of-bound.
-      \State Wait to receive message.
+      \State $H_\rdv\gets \ExtendRoute[D\concat \top, L, \theta]$
+      \State \Return $H_\rdv$
+        \Comment{Give to sender out-of-bound.}
+    \EndFunction
+
+    \Function{\Store}{$c_m$}
+      \State $m\gets \Dec[_{\sk_D}][c_m]$
+      \If{$m = \bot$}
+        \State \Return $\bot$
+      \EndIf
+      \State Store $m$ to disk.
+      \State \Return $\top$
     \EndFunction
@@
   \caption{\label{SPORRecv}%
-    The recipient function.%
+    The \(\SPOR[\Recv]\) algorithm prepares the recipient for receiving a file.
+    It creates a probabilistic onion-route from a rendez-vous point to its own 
+    devices and returns the route to the sender.
+    The \(\Store\) algorithm is used by the local \(\SPOR[\Fwd]\) algorithm to 
+    store messages intended for itself.
   }
@@
       $m$ is the message to be sent,
-      $H_\rdv$ is the onion-route given by the recipient (its first node is the 
-      rendez-vous point).
+      $\pk_D$ is the public-key of the recipient,
+      $H_\rdv$ is the onion-route given by the recipient.
     }
@@
         \Comment{Uniformly randomly chosen}
-        \If{$d\method \Fwd[c_m, C_H] \neq \bot$}
+        \If{$d\method \Fwd[C_H, c_m] \neq \bot$}
           \State \Return $\top$
@@
   \caption{\label{SPORSend}%
-    The algorithm for creating a probabilistic onion route.
-    \(d\) is the destination address, \(m\) is the message, \(H_\rdv\) is the 
-    header for the rendez-vous point selected by \(d\).%
+    The \(\SPOR[\Send]\) algorithm extends the route \(H_\rdv\) (using 
+    \(\ExtendRoute\), \cref{ExtendRoute}) and sends the message \(m\) down the 
+    extended route using the \(\SPOR[\Fwd]\) algorithm (\cref{SPORFwd}).
+    The first node of \(H_\rdv\) is the rendez-vous point selected by the 
+    recipient.
+    \(\pk_D\) is the public key of the recipient.
   }
@@
     \Require{$\pk, \sk$ is the public--private key-pair of the node.}
-    \Function{\SPOR[\Fwd]}{$c_m, C_H$}
+    \Function{\SPOR[\Fwd]}{$C_H, c_m$}
       \State $H\gets \Dec[_\sk][C_H]$
@@
       \State $\{d_i\}\concat C_H'\gets H$
+      \If{$C_H' = \top$}
+        \State \Return $\Store[c_m]$
+      \EndIf
       \For{$d\in \{d_i\}$}
         \Comment{Uniformly randomly chosen}
-        \If{$d\method \Fwd[c_m, C_H'] \neq \bot$}
+        \If{$d\method \Fwd[C_H', c_m] \neq \bot$}
           \State \Return $\top$
@@
   \caption{\label{SPORFwd}%
-    The forwarding function for a node in a probabilistic onion route.%
+    The \(\SPOR[\Fwd]\) algorithm forwards \(c_m\) down the route \(H\), 
+    obtained by decrypting \(C_H\) with the node's associated private key.%
+    The special value \(H = \top\) indicated the end of the route, thus \(c_m\) 
+    is intended for the local node and \(c_m\) is instead sent to disk using 
+    \(\Store\) (\cref{SPORRecv}).%
   }
 \end{figure}
+
+\commentDaniel{Anything below this line should be updated.}
 

### 2018-04-19 paper/algorithm.tex
Writes up text body for SPOR

@@
 \NewAlgorithm{\Recv}{Receive}
-
 \NewVariable{\rdv}{rdv}
-\NewAlgorithm{\Enc}{Enc}
-\NewVariable{\pk}{pk}
-\NewAlgorithm{\Dec}{Dec}
-\NewVariable{\sk}{sk}
 
 We have the Secure Probabilistic Onion Routing scheme, \SPOR, which provides 
-onion-routed message passing.
-\(\SPOR\) provides two algorithms: \(\SPOR[\Send]\) (\cref{SPORSend}), 
+probabilistically onion-routed message passing.
+Instead of providing only one address per hop in the route (as in \eg 
+Tor~\cite{Tor}), \(\SPOR\) provides several alternatives for the next hop 
+depending on their probability of being online.
+To do this, \(\SPOR\) provides stateless algorithms for the onion-routing.
+
+\(\SPOR\) provides three algorithms: \(\SPOR[\Send]\) (\cref{SPORSend}), 
 \(\SPOR[\Fwd]\) (\cref{SPORFwd}) and \(\SPOR[\Recv]\) (\cref{SPORRecv}).
-Say Alice (sender) wants to send a message \(m\) to Bob (recipient).
+Say Alice wants to send a message \(m\) to Bob.
 Bob uses \(\SPOR[\Recv]\) to create a probabilistic onion route \(H_\rdv\) from 
-a rendez-vous point (\(\rdv\) below) to its own device swarm --- all the hops on 
-the route are chosen by Bob uniformly at random.
-Bob gives \(H_\rdv\) to Alice using an out-of-band channel.
+a rendez-vous point to his own device swarm --- all the hops on the route are 
+chosen by Bob uniformly at random.
+Bob gives \(H_\rdv\) to Alice using an out-of-band channel, \eg using his phone.
 Alice uses \(\SPOR[\Send]\) at some later time to send the message to Bob using 
 any of her devices.
-\(\SPOR[\Send]\) extends the route \(H_\rdv\) with some hops of Alice's 
-choosing, then lets the probabilistic nodes of the route forward the message 
-(using \(\SPOR[\Fwd]\)) through to Bob.
+\(\SPOR[\Send]\) extends the route \(H_\rdv\) with some hops of Alice's choosing 
+(uniformly randomly chosen), then starts to forward the message (using 
+\(\SPOR[\Fwd]\)) through the hops on the route to Bob.
+This process is illustrated in \cref{fig:file-exchange}.
+
+\begin{figure}
+  \includegraphics[width=\linewidth]{figures/file_exchange.pdf}
+  \caption{\label{fig:file-exchange}%
+    A schematic of Alice and Bob sending a message using \(\SPOR\).
+  }
+\end{figure}
 
@@
 \NewAlgorithm{\GetRandomPeer}{GetRandomPeer}
+
+\NewAlgorithm{\Enc}{Enc}
+\NewVariable{\pk}{pk}
 
@@
       \(D\) is a set of device addresses.
+      $\pk_D$ is the public key of device set $D$.
       $L$ is the length of the route,
@@
 \NewAlgorithm{\Store}{Store}
+\NewAlgorithm{\Dec}{Dec}
+\NewVariable{\sk}{sk}
 

### 2018-04-19 code/modules/device.py
wip

@@ -1,8 +1,9 @@
 #!/usr/bin/env python3
 
-# import numpy as np
 from .peers_view import PeersView
 from datetime import timedelta, datetime
+import numpy as np
+import pandas as pd
 import random
 import string
 
@@ -10,21 +11,26 @@ ADDR_SIZE = 12
 
 DEFAULT_GOSSIP_SIZE = 10
 DEFAULT_EXPIRATION_PERIOD = timedelta(seconds=1)
+MINIMUM_LAYER_PROBA = 1
 
 
 class Device:
     def __init__(
-            self, owner, global_view, device_id,
+            self, owner, global_view, net, device_id, device_type,
             gossip_size=DEFAULT_GOSSIP_SIZE,
             expiration_period=DEFAULT_EXPIRATION_PERIOD):
 
-        self.owner = owner
-        self.global_view = global_view
-        self.device_id = device_id
-        self.gossip_size = gossip_size
-        self.peers_view = PeersView(expiration_period)
         self.addr = random_string(ADDR_SIZE)
+        self.device_id = device_id
+        self.global_view = global_view
+        self.gossip_size = gossip_size
         self.is_online = False
+        self.net = net
+        self.owner = owner
+        self.peers_view = PeersView(expiration_period)
+        self.type = device_type
+
+        net.add_device(self)
 
         self.files = []  # ?
 
@@ -34,6 +40,7 @@ class Device:
             self.global_view.put(
                 datetime.now(),
                 self.addr,
+                self.type,
                 self.owner.get_prediction(self.device_id)
             )
             self.random_peer_sampling()
@@ -43,6 +50,32 @@ class Device:
             self.global_view.get_sample(
                 n=self.gossip_size,
                 exclude_addr=self.addr))
+
+    def plan_route(self, role):
+        if role == "receiver":
+            # 2 layers planned in advance
+            route = []
+            route.append(self.pick_devices())
+            route.append(self.pick_devices())
+
+        elif role == "sender":
+
+        else:
+            raise ValueError("role should be either 'sender' or 'receiver'")
+
+    def pick_devices(self):
+        view = self.peers_view.view.copy()
+
+        layer = pd.DataFrame()
+        p = 0
+        while p < MINIMUM_LAYER_PROBA:
+            # Pick a device from view without replacement
+            d = view.iloc[np.random.choice(len(view))]
+            layer = layer.append(d)
+            view.drop(d.name, inplace=True)
+            p += d['p']
+
+        return layer
 
 
 def random_string(n):

### 2018-04-19 code/modules/model.py

@@ -245,7 +245,7 @@ def get_random():
             device_type_id = np.random.choice(
                 range(len(devices_type)), p=devices_type_weights)
         device_type = devices_type[device_type_id]
-        picked_devices_type[obs_id] = devices_type
+        picked_devices_type[obs_id] = devices_type[device_type_id]
 
         # Bake probabilities of connection depending on device type
         if device_type == 'mobile':

### 2018-04-19 code/modules/network.py

@@ -1,0 +1,15 @@
+#!/usr/bin/env python3
+
+
+class Network:
+    def __init__(self):
+        self.devices = dict()
+
+    def add_device(self, d):
+        self.devices[d.addr] = d
+
+    def get_device(self, addr):
+        d = self.devices.get(addr)
+        if d is None or not d.is_online:
+            return None
+        return d

### 2018-04-19 code/modules/peers_view.py

@@ -3,7 +3,7 @@
 import pandas as pd
 from datetime import timedelta, datetime
 
-COLUMNS = ["t", "addr", "p"]
+COLUMNS = ["t", "addr", "type", "p"]
 
 
 class PeersView:
@@ -12,13 +12,14 @@ class PeersView:
 
         self.expiration_period = expiration_period
 
-    def put(self, t, addr, p, prune=True):
+    def put(self, t, addr, typ, p, prune=True):
         self.view = self.view[self.view['addr'] != addr]
 
         self.view = self.view.append(
             pd.DataFrame({
                 't': t,
                 'addr': addr,
+                'type': typ,
                 'p': p
             }, index=[t])
         )
@@ -35,7 +36,8 @@ class PeersView:
         # print(items)
 
         for _, item in items.iterrows():
-            self.put(item['t'], item['addr'], item['p'], prune=False)
+            self.put(item['t'], item['addr'],
+                     item['type'], item['p'], prune=False)
 
         self._prune_view()
 
@@ -48,6 +50,19 @@ class PeersView:
             return []
 
         return view.sample(n=n)
+
+    def snapshot(self, additional_columns=None):
+        if additional_columns is None:
+            return self.view
+        elif type(additional_columns) is dict:
+            ret = self.view.copy()
+            for k, v in additional_columns.items():
+                ret[k] = v
+            return ret
+        else:
+            raise ValueError(
+                "additional_columns must be a dict of 'colname' -> 'value' "
+                "to add the to the view")
 
     def _prune_view(self):
         # Time-bound

### 2018-04-19 code/modules/user.py

@@ -5,14 +5,19 @@ from . import model, device
 
 
 class User:
-    def __init__(self, global_view):
+    def __init__(self, global_view, net,
+                 gossip_size=device.DEFAULT_GOSSIP_SIZE):
         self.model = model.get_random()
 
         self.n_devices = self.model.n_obs
         # Create devices
         self.devices = [None] * self.n_devices
+        self.devices_addr = [None] * self.n_devices
         for d_id in range(self.n_devices):
-            self.devices[d_id] = device.Device(self, global_view, d_id)
+            self.devices[d_id] = device.Device(
+                self, global_view, net, d_id,
+                self.model.devices_type[d_id], gossip_size)
+            self.devices_addr[d_id] = self.devices[d_id].addr
 
         self.current_state = None
         self.state_history = []
@@ -25,10 +30,20 @@ class User:
         # here we need sample[0] = t+1
         self.current_state = states[0]
         self.state_history.append(self.current_state)
-        self.devices_history.append(devices[0])
+        devices_state = devices[0]
+        self.devices_history.append(devices_state)
 
-        for d_id, is_online in enumerate(devices[0]):
+        for d_id, is_online in enumerate(devices_state):
             self.devices[d_id].act(is_online)
+
+    def plan_file_exchange(self, route):
+
+    def has_online_devices(self):
+        return self.devices_history[-1].sum() != 0
+
+    def get_online_device(self):
+        return self.devices[np.random.choice(
+            np.where(self.devices_history[-1])[0])]
 
     def get_prediction(self, device_id):
         return self.model.predict(1, device_id, self.current_state)[0]

### 2018-04-19 paper/algorithm.tex
Introduces some subsections in algorithm section

@@
 \NewScheme{\SPOR}{SPOR}
+
+\subsection{\(\SPOR\)}
+
 \NewAlgorithm{\Send}{Send}
@@
 
-\commentDaniel{Anything below this line should be updated.}
+\subsection{Predictions and scheduling}
 
+\commentDaniel{%
+  We must cover how to do \(\Pr[d \text{ offline at time } t]\) as used above 
+  (\cref{ExtendRoute}).%
+}
+
+\commentDaniel{%
+  We must do the scheduling: \ie divide the file \(f\) into \(f_1, \dotsc, f_n\) 
+  and how the size of \(f_i\) relates to transmission time and size of the 
+  timeslot (for the validity of predictions).
+  After that we just do \(\SPOR[\Send]\) on each \(f_i\).%
+}
+
+\subsection{Adrien's old stuff}
+
+\commentDaniel{%
+  Anything below this line should be updated, integrated or removed.%
+}
 A set of users $\mathcal{U}$ participate in the \name network.

### 2018-04-21 code/modules/device.py
route establishment v1

@@ -1,6 +1,6 @@
 #!/usr/bin/env python3
 
-from .peers_view import PeersView
+from . import config, peers_view
 from datetime import timedelta, datetime
 import numpy as np
 import pandas as pd
@@ -17,22 +17,20 @@ MINIMUM_LAYER_PROBA = 1
 class Device:
     def __init__(
             self, owner, global_view, net, device_id, device_type,
-            gossip_size=DEFAULT_GOSSIP_SIZE,
-            expiration_period=DEFAULT_EXPIRATION_PERIOD):
+            conf=config.default):
 
         self.addr = random_string(ADDR_SIZE)
+        self.conf = conf
         self.device_id = device_id
         self.global_view = global_view
-        self.gossip_size = gossip_size
+        self.gossip_size = conf['gossip_size']
         self.is_online = False
         self.net = net
         self.owner = owner
-        self.peers_view = PeersView(expiration_period)
+        self.peers_view = peers_view.PeersView(conf)
         self.type = device_type
 
         net.add_device(self)
-
-        self.files = []  # ?
 
     def act(self, is_online):
         self.is_online = is_online
@@ -51,31 +49,56 @@ class Device:
                 n=self.gossip_size,
                 exclude_addr=self.addr))
 
-    def plan_route(self, role):
+    def build_route(self, role):
         if role == "receiver":
             # 2 layers planned in advance
-            route = []
-            route.append(self.pick_devices())
-            route.append(self.pick_devices())
-
+            n_layers = self.conf['n_layers'] // 2 + 1
         elif role == "sender":
-
+            n_layers = self.conf['n_layers'] // 2
         else:
             raise ValueError("role should be either 'sender' or 'receiver'")
 
-    def pick_devices(self):
+        route = []
         view = self.peers_view.view.copy()
+        for _ in range(n_layers):
+            layer, view = self.build_layer(view)
+            route.append(layer)
+
+        return route
+
+    def build_layer(self, view=None):
+        if view is None:
+            view = self.peers_view.view.copy()
+
+        print("[build_layer] Starting with view of size {} "
+              "and layer_threshold of {}.".format(
+                  view.shape[0], self.conf['layer_threshold']))
 
         layer = pd.DataFrame()
-        p = 0
-        while p < MINIMUM_LAYER_PROBA:
+        p = 1
+        i = 0
+        while p > self.conf['layer_threshold']:
+            if len(view) == 0:
+                print("[build_layer it. {}] "
+                      "No more devices in view: early abort.".format(i))
[…]

### 2018-04-21 code/modules/model.py

@@ -93,8 +93,9 @@ class Model:
             # Each device has an independant probability of being online
             for obs in range(self.n_obs):
                 p_obs_in_state = self.B[state, obs]
-                sample_obs[t, obs] = np.random.choice([False, True],
-                                                      p=[1 - p_obs_in_state, p_obs_in_state])
+                sample_obs[t, obs] = \
+                    np.random.choice([False, True],
+                                     p=[1 - p_obs_in_state, p_obs_in_state])
 
         return sample_states, sample_obs
 
@@ -196,7 +197,8 @@ class Model:
             # Emission probabilities for each state
             print("B:")
             for s_id in range(self.n_states):
-                self.B[s_id, obs_id] = m.states[s_id].distribution.parameters[0][obs]
+                self.B[s_id, obs_id] = \
+                    m.states[s_id].distribution.parameters[0][obs]
                 print(self.B[s_id, obs_id])
             print()
         return
@@ -250,15 +252,15 @@ def get_random():
         # Bake probabilities of connection depending on device type
         if device_type == 'mobile':
             # Mobile is highly available with varying probability
-            p = 0.7 + 0.3 * np.random.sample(n_states)
+            p = 0.6 + 0.4 * np.random.sample(n_states)
         elif device_type == 'portable':
             # Portable is more or less available with varying probability
-            p = 0.2 + 0.6 * np.random.sample(n_states)
+            p = 0.1 + 0.7 * np.random.sample(n_states)
         elif device_type == 'fixed':
             # Fixed is only available in one place ...
             p = np.zeros(n_states, dtype=np.float64)
             # ... with 0.4 to 1 probability
-            p[random.choice([0, 2])] = 0.4 + 0.6 * np.random.sample()
+            p[random.choice([0, 2])] = 0.2 + 0.8 * np.random.sample()
         elif device_type == 'server':
             # Server has high availability regardless of the user's location
             p = [0.9 + 0.1 * np.random.sample()] * n_states

### 2018-04-21 code/modules/network.py

@@ -10,6 +10,6 @@ class Network:
 
     def get_device(self, addr):
         d = self.devices.get(addr)
-        if d is None or not d.is_online:
-            return None
+        if d is None:
+            raise ValueError("{} is not in the nlist of devices.".format(addr))
         return d

### 2018-04-21 code/modules/peers_view.py

@@ -2,17 +2,17 @@
 
 import pandas as pd
 from datetime import timedelta, datetime
+from . import config
 
 COLUMNS = ["t", "addr", "type", "p"]
 
 
 class PeersView:
-    def __init__(self, expiration_period=timedelta(seconds=1)):
+    def __init__(self, conf=config.default):
         self.view = pd.DataFrame(columns=COLUMNS)
+        self.conf = conf
 
-        self.expiration_period = expiration_period
-
-    def put(self, t, addr, typ, p, prune=True):
+    def put(self, t, addr, typ, p):
         self.view = self.view[self.view['addr'] != addr]
 
         self.view = self.view.append(
@@ -24,21 +24,14 @@ class PeersView:
             }, index=[t])
         )
 
-        if prune:
-            self._prune_view()
+        self._prune_view()
 
     # Items is a dataframe
     def insert(self, items):
-        if len(items) == 0:
+        if items is None:
             return
-        # print("insert:")
-        # print(type(items))
-        # print(items)
 
-        for _, item in items.iterrows():
-            self.put(item['t'], item['addr'],
-                     item['type'], item['p'], prune=False)
-
+        self.view = self.view.append(items)
         self._prune_view()
 
     def get_sample(self, n=3, exclude_addr=None):
@@ -47,7 +40,7 @@ class PeersView:
         if n > view.shape[0]:
             n = view.shape[0]
         if n == 0:
-            return []
+            return None
 
         return view.sample(n=n)
 
@@ -66,7 +59,7 @@ class PeersView:
 
     def _prune_view(self):
         # Time-bound
-        expiration_limit = datetime.now() - self.expiration_period
+        expiration_limit = datetime.now() - self.conf['period']
 
         # print(self.view.index)
         self.view = self.view[self.view.index >= expiration_limit]

### 2018-04-21 code/modules/user.py

@@ -1,49 +1,51 @@
 #!/usr/bin/env python3
 
 import numpy as np
-from . import model, device
+from . import model, device, config
 
 
 class User:
-    def __init__(self, global_view, net,
-                 gossip_size=device.DEFAULT_GOSSIP_SIZE):
+    def __init__(self, global_view, net, conf=config.default):
         self.model = model.get_random()
 
-        self.n_devices = self.model.n_obs
         # Create devices
+        self.n_devices = self.model.n_obs
         self.devices = [None] * self.n_devices
         self.devices_addr = [None] * self.n_devices
         for d_id in range(self.n_devices):
             self.devices[d_id] = device.Device(
                 self, global_view, net, d_id,
-                self.model.devices_type[d_id], gossip_size)
+                self.model.devices_type[d_id], conf)
             self.devices_addr[d_id] = self.devices[d_id].addr
 
-        self.current_state = None
-        self.state_history = []
-        self.devices_history = []
+        self.conf = conf
+        self.current_round = None
+
+        self.state_history, self.devices_history = self.model.sample(
+            length=conf['n_rounds'])
 
     def act(self):
-        states, devices = self.model.sample(
-            length=1, previous_state=self.current_state)
-        # Model.sample returns array indexed by time
-        # here we need sample[0] = t+1
-        self.current_state = states[0]
-        self.state_history.append(self.current_state)
-        devices_state = devices[0]
-        self.devices_history.append(devices_state)
+        if self.current_round is None:
+            self.current_round = 0
+        else:
+            self.current_round += 1
 
-        for d_id, is_online in enumerate(devices_state):
+        for d_id, is_online in \
+                enumerate(self.devices_history[self.current_round]):
             self.devices[d_id].act(is_online)
 
-    def plan_file_exchange(self, route):
-
     def has_online_devices(self):
-        return self.devices_history[-1].sum() != 0
+        return self.devices_history[self.current_round].sum() != 0
 
     def get_online_device(self):
-        return self.devices[np.random.choice(
-            np.where(self.devices_history[-1])[0])]
+        return self.devices[
+            np.random.choice(
+                np.where(
+                    self.devices_history[self.current_round]
+                )[0]
+            )
+        ]
 
     def get_prediction(self, device_id):
-        return self.model.predict(1, device_id, self.current_state)[0]
+        return self.model.predict(
+            1, device_id, self.state_history[self.current_round])[0]

### 2018-04-21 code/modules/device.py
got routes experiment results

@@ -34,13 +34,16 @@ class Device:
 
     def act(self, is_online):
         self.is_online = is_online
-        if is_online:
+        if self.is_online:
             self.global_view.put(
                 datetime.now(),
                 self.addr,
                 self.type,
                 self.owner.get_prediction(self.device_id)
             )
+
+    def rps(self):
+        if self.is_online:
             self.random_peer_sampling()
 
     def random_peer_sampling(self):
@@ -48,6 +51,12 @@ class Device:
             self.global_view.get_sample(
                 n=self.gossip_size,
                 exclude_addr=self.addr))
+        # if len(self.peers_view.view) == 0:
+        #     print("Device's RPS returned 0 devices! Global peers view has {}.".format(
+        #         len(self.global_view.view)))
+        #     expiration_limit = datetime.now() - self.conf['period']
+        #     print("Expiration time:", expiration_limit)
+        #     print(self.global_view.view)
 
     def build_route(self, role):
         if role == "receiver":
@@ -58,44 +67,63 @@ class Device:
         else:
             raise ValueError("role should be either 'sender' or 'receiver'")
 
-        route = []
+        # print("[build route] Creating '{}' route with {} layers".format(
+        #     role, n_layers))
+
+        route = [pd.DataFrame() for _ in range(n_layers)]
         view = self.peers_view.view.copy()
-        for _ in range(n_layers):
-            layer, view = self.build_layer(view)
-            route.append(layer)
+
+        converged = False
+        while not converged:
+            converged_layers = [False for _ in range(n_layers)]
+            # Iteratively add one device per layer until converged
+            for l_id in range(n_layers):
+                if len(route[l_id]) > 0:
+                    # Probability that all devices of layer will be offline
+                    p_failure = (1 - route[l_id]['p']).prod()
+                    # layer is converged when p_failure is below threshold
+                    converged_layers[l_id] = \
+                        p_failure < self.conf['layer_threshold']
+
+                    # print("[build route] Layer {} has p_fail={} => {}".format(
+                    #     l_id, p_failure,
+                    #     "converged" if converged_layers[l_id]
+                    #     else "not converged"))
+
+                    # Skip this layer if converged
+                    if converged_layers[l_id]:
+                        continue
+
+                # Else add a node to layer
+
+                # If view is empty, break
+                if len(view) == 0:
+                    print("[build route] No more available nodes: "
+                          "early abort.")
+                    converged = True
[…]

### 2018-04-21 code/modules/user.py

@@ -34,6 +34,10 @@ class User:
                 enumerate(self.devices_history[self.current_round]):
             self.devices[d_id].act(is_online)
 
+    def rps(self):
+        for d in self.devices:
+            d.rps()
+
     def has_online_devices(self):
         return self.devices_history[self.current_round].sum() != 0
 

### 2018-04-22 code/modules/experiment.py
did routes experiments

@@ -1,0 +1,214 @@
+#!/usr/bin/env python3
+
+# import numpy as np
+from datetime import datetime, timedelta
+from modules import config
+from modules.network import Network
+from modules.peers_view import PeersView
+from modules.user import User
+import pandas as pd
+import random
+import threading
+import time
+
+
+def run_experiments_set(N_LAYERS, LAYER_THRESHOLD, N_ROUNDS_SINCE_ROUTE,
+                        N_ROUTES, N_EXPERIMENTS, PERIOD):
+    routes_df = pd.DataFrame()
+    layers_df = pd.DataFrame()
+
+    period = PERIOD
+    total_n_experiments = len(N_LAYERS) * len(LAYER_THRESHOLD)
+
+    t_start = time.perf_counter()
+    total_experiment_id = 1
+    for n_layers in N_LAYERS:
+        for layer_threshold in LAYER_THRESHOLD:
+            experiments = [None] * N_EXPERIMENTS
+            for experiment_id in range(N_EXPERIMENTS):
+                n_users = n_layers * 5
+                conf = {
+                    'gossip_size': 10 * n_layers,
+                    'layer_threshold': layer_threshold,
+                    'minimum_node_availability': 0,
+                    'n_layers': n_layers,  # must be odd
+                    'n_rounds': N_ROUNDS_SINCE_ROUTE + 1,
+                    'n_users': n_layers * 5,
+                    'period': period,
+                }
+
+    #             layers, routes = run_experiment(conf, experiment_id,
+    #                                            N_ROUTES,
+    #                                            N_ROUNDS_SINCE_ROUTE)
+
+                experiments[experiment_id] = Experiment(conf, experiment_id,
+                                                        N_ROUTES,
+                                                        N_ROUNDS_SINCE_ROUTE)
+                experiments[experiment_id].start()
+
+            for experiment in experiments:
+                experiment.join()
+                layers_df = layers_df.append(
+                    experiment.layers_df, ignore_index=True)
+                routes_df = routes_df.append(
+                    experiment.routes_df, ignore_index=True)
+                # not sure about this
+                period = max(period, experiment.period)
+
+            time_spent = timedelta(seconds=time.perf_counter() - t_start)
+            print("[{}] Experiment {}/{} done.".format(
+                time_spent, total_experiment_id, total_n_experiments))
+            total_experiment_id += 1
+
+    return layers_df, routes_df
+
+
[…]

### 2018-04-23 paper/conclusion.tex

\section{Conclusion and Future Work}

\commentAL{To rewrite as real paragraphs} Future work and prospects:
\begin{itemize}
	\item More in-depth knowledge of the user's behavior would allow to predict devices connections farther in the future;
	\item Changing devices' asymmetric keys regularly would increase security.
	Updating keys is easy in \name given the RPS that propagates new information to all nodes.
	However, more reflection would be needed to avoid key updates breaking ongoing communications passing through the devices in question.

\end{itemize}

### 2018-04-24 code/modules/config.py
new implementation

@@ -1,0 +1,14 @@
+#!/usr/bin/env python3
+
+from datetime import timedelta
+
+default = {
+    'gossip_size': 20,
+    'layer_threshold': 0.001,
+    'minimum_node_availability': 0,
+    'n_file_chunks': 10,
+    'n_layers': 3,  # must be odd
+    'n_rounds': 2,
+    'n_users': 20,
+    'period': timedelta(seconds=1),
+}

### 2018-04-24 code/modules/device.py

@@ -1,0 +1,185 @@
+#!/usr/bin/env python3
+
+from . import config, peers_view, file, network
+from .utils import random_string, hash_layer
+from datetime import timedelta, datetime
+import numpy as np
+import pandas as pd
+import random
+
+ADDR_SIZE = 12
+
+
+class Device:
+    def __init__(
+            self, owner, global_view, net, device_id, device_type,
+            conf=config.default):
+
+        self.addr = random_string(ADDR_SIZE)
+        self.conf = conf
+        self.device_id = device_id
+        self.global_view = global_view
+        self.gossip_size = conf['gossip_size']
+        self.is_online = False
+        self.net = net
+        self.owner = owner
+        self.peers_view = peers_view.PeersView(conf)
+        self.type = device_type
+
+        net.add_device(self)
+
+        # File-exchange related
+        self.sending_files = {}
+        self.sending_files_routes = {}
+
+        # maps hash of route's layer -> previously picked device from layer
+        self.connected_to = {}
+
+    def register_to_global_view(self, is_online):
+        self.is_online = is_online
+        if self.is_online:
+            self.global_view.put(
+                datetime.now(),
+                self.addr,
+                self.type,
+                self.owner.get_prediction(self.device_id)
+            )
+
+    def act(self):
+        if not self.is_online:
+            return
+
+        self.random_peer_sampling()
+
+        # TODO: bandwidth
+        for f in self.sending_files:
+            self.send_file_chunk(f)
+
+    def init_file_send(self, H_rdv, file_id):
+        f = file.File(self.conf['n_chunks'])
+
+        self.sending_files[f.id] = f
+
+        route = [None] * self.conf['n_layers']
+        route[:self.conf['n_layers'] // 2] = self.build_route("sender")
+        route[self.conf['n_layers'] // 2:] = H_rdv
+
+        self.sending_files_routes[f.id] = route
+
+    def send_file_chunk(self, f):
+        if f.all_shared():
+            print("[Device.send_file_chunk] file {} already completed".format(
+                f.id))
+            self.complete_file_exchange()
+            return
+
+        self.send(None, self.sending_files_routes[f.id],
+                  network.Message(
+                      typ=network.MessType.CHUNK,
+                      file_id=f.id,
+                      chunk_id=f.select_chunk()
+        ))
+
+    def send(self, src, route, m):
+        if not self.is_online:
+            return
+
+        # Am I the receiver?
[…]

### 2018-04-24 code/modules/file.py

@@ -1,0 +1,31 @@
+#!/usr/bin/env python3
+
+import numpy as np
+
+
+class File:
+    def __init__(self, n_chunks, file_id):
+        self.id = file_id
+        self.n_chunks = n_chunks
+
+        self.shared_chunks = np.array(
+            [False for _ in range(n_chunks)], dtype=np.bool)
+
+    def select_chunk(self):
+        avail_chunks_id = np.argwhere(self.shared_chunks == False).ravel()
+
+        if len(avail_chunks_id) == 0:
+            return None
+
+        return np.random.choice(avail_chunks_id)
+
+    def ack(self, chunk_id):
+        if chunk_id < 0 or chunk_id >= self.n_chunks:
+            raise ValueError(
+                "chunk_id ({}) should be in bounds [0, {}]".format(
+                    chunk_id, self.n_chunks))
+
+        self.shared_chunks[chunk_id] = True
+
+    def all_shared(self):
+        return all(shared_chunks)

### 2018-04-24 code/modules/model.py

@@ -1,0 +1,283 @@
+#!/usr/bin/env python3
+
+import numpy as np
+import random
+import pomegranate as pg
+import string
+
+STATE_NAME_PREFIX = "s"
+OBSERVATION_NAME_PREFIX = "d"
+
+DEFAULT_STATES_NAME = ["Home", "Outside", "Work"]
+DEFAULT_STATES_NUMBER = len(DEFAULT_STATES_NAME)
+DEFAULT_TRANSITION_MATRIX = \
+    [[0.6, 0.4, 0.],
+     [0.2, 0.6, 0.2],
+     [0.,  0.4, 0.6]]
+
+DEVICES_NUMBER_MIN = 3
+DEVICES_NUMBER_MAX = 10
+
+RANDOM_NAME_SIZE = 16
+
+
+class Model:
+    def __init__(self):
+        self.n_states = 0
+        self.n_obs = 0
+
+        self.states = None
+        self.observations = None
+        self.A = None
+        self.B = None
+        self.defined = False
+
+    def __str__(self):
+        ret = str(self.__class__) + ': {\n'
+        for k, v in self.__dict__.items():
+            ret += "{}: {}\n".format(k, v)
+        ret += "}"
+        return ret
+
+    def set(self, A, B, states=None, observations=None):
+        self.A = np.array(A, dtype=np.float64)
+        self.B = np.array(B, dtype=np.float64)
+        self.n_states = self.A.shape[0]
+        self.n_obs = self.B.shape[1]
+        self.init = np.ones(self.n_states, dtype=np.float64)
+        self.init = self.init / self.n_states
+
+        if states is None or len(states) != self.n_states:
+            self.states = [STATE_NAME_PREFIX +
+                           str(i) for i in range(1, self.n_states+1)]
+        else:
+            self.states = states
+
+        if observations is None or len(observations) != self.n_obs:
+            self.observations = [OBSERVATION_NAME_PREFIX +
+                                 str(i) for i in range(1, self.n_obs+1)]
+        else:
+            self.observations = observations
+
+        self.defined = True
+
+    def sample(self, length=20, previous_state=None):
+        if not self.defined:
+            print("Model is not defined.")
+            return None, None
+        if previous_state is not None and \
+                (previous_state < 0 or previous_state >= self.n_states):
+            raise ValueError(
+                "Out of bounds initial state s0: \
+                 should be in [[0, {}]]".format(self.n_states-1))
+
+        initial_state = True
[…]

### 2018-04-24 code/modules/network.py

@@ -1,0 +1,29 @@
+#!/usr/bin/env python3
+
+from enum import Enum
+
+
+class MessType(Enum):
+    CHUNK = 1
+    ACK = 2
+
+
+class Message:
+    def __init__(self, typ, file_id, chunk_id):
+        self.type = typ
+        self.file_id = file_id
+        self.chunk_id = chunk_id
+
+
+class Network:
+    def __init__(self):
+        self.devices = dict()
+
+    def add_device(self, d):
+        self.devices[d.addr] = d
+
+    def get_device(self, addr):
+        d = self.devices.get(addr)
+        if d is None:
+            raise ValueError("{} is not in the list of devices.".format(addr))
+        return d

### 2018-04-24 code/modules/peers_view.py

@@ -1,0 +1,65 @@
+#!/usr/bin/env python3
+
+import pandas as pd
+from datetime import timedelta, datetime
+from . import config
+
+COLUMNS = ["t", "addr", "type", "p"]
+
+
+class PeersView:
+    def __init__(self, conf=config.default):
+        self.view = pd.DataFrame(columns=COLUMNS)
+        self.conf = conf
+
+    def put(self, t, addr, typ, p):
+        self.view = self.view[self.view['addr'] != addr]
+
+        self.view = self.view.append(
+            pd.DataFrame({
+                't': t,
+                'addr': addr,
+                'type': typ,
+                'p': p
+            }, index=[t])
+        )
+
+        self._prune_view()
+
+    # Items is a dataframe
+    def insert(self, items):
+        if items is None:
+            return
+
+        self.view = self.view.append(items)
+        self._prune_view()
+
+    def get_sample(self, n=3, exclude_addr=None):
+        view = self.view[self.view['addr'] != exclude_addr]
+
+        if n > view.shape[0]:
+            n = view.shape[0]
+        if n == 0:
+            return None
+
+        return view.sample(n=n)
+
+    def snapshot(self, additional_columns=None):
+        if additional_columns is None:
+            return self.view
+        elif type(additional_columns) is dict:
+            ret = self.view.copy()
+            for k, v in additional_columns.items():
+                ret[k] = v
+            return ret
+        else:
+            raise ValueError(
+                "additional_columns must be a dict of 'colname' -> 'value' "
+                "to add the to the view")
+
+    def _prune_view(self):
+        # Time-bound
+        expiration_limit = datetime.now() - self.conf['period']
+
+        # print(self.view.index)
+        self.view = self.view[self.view.index >= expiration_limit]

### 2018-04-24 code/modules/user.py

@@ -1,0 +1,81 @@
+#!/usr/bin/env python3
+
+from . import model, device, config, file
+from .utils import random_string
+import numpy as np
+
+
+FILE_ID_SIZE = 10
+
+
+class User:
+    def __init__(self, global_view, net, conf=config.default):
+        self.model = model.get_random()
+
+        # Create devices
+        self.n_devices = self.model.n_obs
+        self.devices = [None] * self.n_devices
+        self.devices_addr = [None] * self.n_devices
+        for d_id in range(self.n_devices):
+            self.devices[d_id] = device.Device(
+                self, global_view, net, d_id,
+                self.model.devices_type[d_id], conf)
+            self.devices_addr[d_id] = self.devices[d_id].addr
+
+        self.conf = conf
+        self.current_round = None
+
+        self.receiving_files = {}
+
+        self.state_history, self.devices_history = self.model.sample(
+            length=conf['n_rounds'])
+
+    def increment_round(self):
+        if self.current_round is None:
+            self.current_round = 0
+        else:
+            self.current_round += 1
+
+    def register_to_global_view(self):
+        for d_id, is_online in \
+                enumerate(self.devices_history[self.current_round]):
+            self.devices[d_id].register_to_global_view(is_online)
+
+    def act(self):
+        for d in self.devices:
+            d.rps()
+
+    def init_file_receive(self, remote_device):
+        d = self.get_online_device()
+
+        H_rdv = d.build_route("receiver")
+        file_id = random_string(FILE_ID_SIZE)
+
+        self.receiving_files[file_id] = file.File(
+            self.conf['n_chunks'], file_id)
+
+        # This exchange is out of band
+        remote_device.init_file_send(H_rdv, file_id)
+
+    def receive_chunk(self, m):
+        self.receiving_files[m.file_id].ack(m.chunk_id)
+
+        if self.receiving_files[m.file_id].all_shared():
+            # Maybe do something else
+            del self.receiving_files[m.file_id]
+
+    def has_online_devices(self):
+        return self.devices_history[self.current_round].sum() != 0
+
+    def get_online_device(self):
+        return self.devices[
+            np.random.choice(
+                np.where(
+                    self.devices_history[self.current_round]
+                )[0]
+            )
+        ]
+
+    def get_prediction(self, device_id):
+        return self.model.predict(
+            1, device_id, self.state_history[self.current_round])[0]

### 2018-04-24 code/modules/utils.py

@@ -1,0 +1,15 @@
+#!/usr/bin/env python3
+
+import random
+import string
+from pandas.util import hash_pandas_object
+
+
+def random_string(n):
+    return ''.join(
+        [random.choice(string.ascii_lowercase+string.digits)
+         for _ in range(n)])
+
+
+def hash_layer(df):
+    return hash_pandas_object(df).sum()

### 2018-04-24 code/routes/experiment.py
new implementation

@@ -2,10 +2,10 @@
 
 # import numpy as np
 from datetime import datetime, timedelta
-from modules import config
-from modules.network import Network
-from modules.peers_view import PeersView
-from modules.user import User
+from . import config
+from .network import Network
+from .peers_view import PeersView
+from .user import User
 import pandas as pd
 import random
 import threading

### 2018-04-24 code/file_exchange/device.py
wip file exchange

@@ -35,7 +35,7 @@ class Device:
         # maps hash of route's layer -> previously picked device from layer
         self.connected_to = {}
 
-    def register_to_global_view(self, is_online):
+    def update_state(self, is_online):
         self.is_online = is_online
         if self.is_online:
             self.global_view.put(
@@ -44,16 +44,6 @@ class Device:
                 self.type,
                 self.owner.get_prediction(self.device_id)
             )
-
-    def act(self):
-        if not self.is_online:
-            return
-
-        self.random_peer_sampling()
-
-        # TODO: bandwidth
-        for f in self.sending_files:
-            self.send_file_chunk(f)
 
     def init_file_send(self, H_rdv, file_id):
         f = file.File(self.conf['n_chunks'])
@@ -128,7 +118,7 @@ class Device:
             self.global_view.get_sample(
                 n=self.gossip_size,
                 exclude_addr=self.addr))
-        # if len(self.peers_view.view) == 0:
+        # if len(self.peers_view.get()) == 0:
         #     print("Device's RPS returned 0 devices!"
         #           " Global peers view has {}.".format(
         #         len(self.global_view.view)))
@@ -145,8 +135,10 @@ class Device:
         else:
             raise ValueError("role should be either 'sender' or 'receiver'")
 
+        self.random_peer_sampling()
+
         route = [pd.DataFrame() for _ in range(n_layers)]
-        view = self.peers_view.view.copy()
+        view = self.peers_view.get().copy()
 
         converged = False
         while not converged:

### 2018-04-24 code/file_exchange/peers_view.py

@@ -3,19 +3,24 @@
 import pandas as pd
 from datetime import timedelta, datetime
 from . import config
+from gevent.lock import Semaphore
 
 COLUMNS = ["t", "addr", "type", "p"]
 
 
 class PeersView:
     def __init__(self, conf=config.default):
-        self.view = pd.DataFrame(columns=COLUMNS)
+        self._view = pd.DataFrame(columns=COLUMNS)
         self.conf = conf
+        self.lock = Semaphore()
 
     def put(self, t, addr, typ, p):
-        self.view = self.view[self.view['addr'] != addr]
+        self.lock.acquire()
+        # Remove previous entry for addr if any
+        self._view = self._view[self._view['addr'] != addr]
 
-        self.view = self.view.append(
+        # Add the new line
+        self._view = self._view.append(
             pd.DataFrame({
                 't': t,
                 'addr': addr,
@@ -24,31 +29,55 @@ class PeersView:
             }, index=[t])
         )
 
-        self._prune_view()
+        # We prune on reads, not writes
+        # self._prune_view()
+        self.lock.release()
 
     # Items is a dataframe
     def insert(self, items):
         if items is None:
             return
 
-        self.view = self.view.append(items)
+        self.lock.acquire()
+        self._view = self._view.append(items)
+
+        # We prune on reads, not writes
+        # self._prune_view()
+        self.lock.release()
+
+    def get(self):
+        self.lock.acquire()
         self._prune_view()
+        ret = self._view.copy()
+        self.lock.release()
+        return ret
 
     def get_sample(self, n=3, exclude_addr=None):
-        view = self.view[self.view['addr'] != exclude_addr]
+        self.lock.acquire()
+        self._prune_view()
+        view = self._view[self._view['addr'] != exclude_addr]
 
         if n > view.shape[0]:
             n = view.shape[0]
         if n == 0:
+            self.lock.release()
             return None
 
-        return view.sample(n=n)
+        # Sample returns a copy of df, not a slice
+        ret = view.sample(n=n)
+        self.lock.release()
+
+        return ret
 
     def snapshot(self, additional_columns=None):
+        self.lock.acquire()
+        self._prune_view()
+        ret = self._view.copy()
+        self.lock.release()
+
         if additional_columns is None:
-            return self.view
+            return ret
         elif type(additional_columns) is dict:
-            ret = self.view.copy()
             for k, v in additional_columns.items():
                 ret[k] = v
             return ret
[…]

### 2018-04-24 code/file_exchange/user.py

@@ -1,15 +1,15 @@
 #!/usr/bin/env python3
 
-from . import model, device, config, file
-from .utils import random_string
+from . import model, device, config, file, utils
 import numpy as np
-
+import gevent
 
 FILE_ID_SIZE = 10
 
 
-class User:
+class User(gevent.Greenlet):
     def __init__(self, global_view, net, conf=config.default):
+        gevent.Greenlet.__init__(self)
         self.model = model.get_random()
 
         # Create devices
@@ -30,26 +30,33 @@ class User:
         self.state_history, self.devices_history = self.model.sample(
             length=conf['n_rounds'])
 
-    def increment_round(self):
-        if self.current_round is None:
-            self.current_round = 0
-        else:
-            self.current_round += 1
+    def loop(self):
+        print("Hello!")
+        while True:
+            # Initial round
+            if self.current_round is None:
+                self.current_round = 0
+            # Break if all rounds done
+            elif self.current_round == self.conf['n_rounds'] - 1:
+                print("Returned")
+                return
+            # Else increment round
+            else:
+                self.current_round += 1
 
-    def register_to_global_view(self):
-        for d_id, is_online in \
-                enumerate(self.devices_history[self.current_round]):
-            self.devices[d_id].register_to_global_view(is_online)
+            # Update devices' state
+            for d_id, is_online in \
+                    enumerate(self.devices_history[self.current_round]):
+                self.devices[d_id].update_state(is_online)
 
-    def act(self):
-        for d in self.devices:
-            d.rps()
+            # Sleep until next round
+            gevent.sleep(self.conf['period'].total_seconds())
 
     def init_file_receive(self, remote_device):
         d = self.get_online_device()
 
         H_rdv = d.build_route("receiver")
-        file_id = random_string(FILE_ID_SIZE)
+        file_id = utils.random_string(FILE_ID_SIZE)
 
         self.receiving_files[file_id] = file.File(
             self.conf['n_chunks'], file_id)

### 2018-04-24 code/file_exchange/utils.py

@@ -5,6 +5,20 @@ import string
 from pandas.util import hash_pandas_object
 
 
+NAMES = ['Cristy', 'Vickey', 'Sherie', 'Delilah', 'Rick', 'Denver', 'Stephany',
+         'Many', 'Sandie', 'Deneen', 'Jesica', 'Newton', 'Maxwell', 'Sherrie',
+         'Beatriz', 'Georgene', 'Herma', 'Mi', 'Bobbi', 'Julianna', 'Reita',
+         'Kandi', 'Karlene', 'Lila', 'Nelly', 'Sibyl', 'Kermit', 'Luke',
+         'Annabel', 'Moira', 'Hassie', 'Hilda', 'Vicki', 'Gloria', 'Kaci',
+         'Dora', 'Gilbert', 'Livia', 'Buffy', 'Demetra', 'Barry', 'Lizzette',
+         'Julius', 'Queen', 'Lyndsey', 'Lucy', 'Garnett',
+         'Lavette', 'Magaly', 'Norene']
+
+
+def random_name():
+    return random.choice(NAMES)
+
+
 def random_string(n):
     return ''.join(
         [random.choice(string.ascii_lowercase+string.digits)

### 2018-04-24 code/file_exchange/user.py
dummy gevent example works

@@ -24,14 +24,18 @@ class User(gevent.Greenlet):
 
         self.conf = conf
         self.current_round = None
+        self.name = utils.random_name()
 
         self.receiving_files = {}
 
         self.state_history, self.devices_history = self.model.sample(
             length=conf['n_rounds'])
 
+    # Overriding Greenlet
+    def _run(self):
+        self.loop()
+
     def loop(self):
-        print("Hello!")
         while True:
             # Initial round
             if self.current_round is None:
@@ -86,3 +90,7 @@ class User(gevent.Greenlet):
     def get_prediction(self, device_id):
         return self.model.predict(
             1, device_id, self.state_history[self.current_round])[0]
+
+    # Overriding Greenlet
+    def __str__(self):
+        return "User({})".format(self.name)

### 2018-04-24 code/file_exchange/config.py
un petit pas pour l'homme, mais un petit pas pour l'humanite

@@ -8,6 +8,8 @@ default = {
     'minimum_node_availability': 0,
     'n_file_chunks': 10,
     'n_layers': 3,  # must be odd
+    'file_size': 11,  # MB
+    'chunk_max_size': 2  # MB, will depend on header size later
     'n_rounds': 2,
     'n_users': 20,
     'period': timedelta(seconds=1),

### 2018-04-24 code/file_exchange/device.py

@@ -45,16 +45,22 @@ class Device:
                 self.owner.get_prediction(self.device_id)
             )
 
-    def init_file_send(self, H_rdv, file_id):
-        f = file.File(self.conf['n_chunks'])
+    def init_file_send(self, H_rdv_forward, H_rdv_backward, f):
+        # route = L_i + ... + L_j
+        route = self.build_route("sender")
+        # forward_route = (L_i + ... + L_j) + (L_RV + L_k + ... + L_l + L_B)
+        forward_route = route + H_rdv_forward
+        # backward_route = (L_l + ... + L_k + L_RV) + (L_j + ... + L_i) + L_A
+        backward_route = H_rdv_backward + \
+            route[::-1] + [self.owner.get_all_devices()]
 
-        self.sending_files[f.id] = f
+        self.sending_files[f.id] = {
+            'file': f,
+            'forward_route': forward_route,
+            'backward_route': backward_route,
+        }
 
-        route = [None] * self.conf['n_layers']
-        route[:self.conf['n_layers'] // 2] = self.build_route("sender")
-        route[self.conf['n_layers'] // 2:] = H_rdv
-
-        self.sending_files_routes[f.id] = route
+        return forward_route, backward_route
 
     def send_file_chunk(self, f):
         if f.all_shared():
@@ -140,38 +146,38 @@ class Device:
         route = [pd.DataFrame() for _ in range(n_layers)]
         view = self.peers_view.get().copy()
 
-        converged = False
-        while not converged:
-            converged_layers = [False for _ in range(n_layers)]
+        converged_layers = [False for _ in range(n_layers)]
+        # Converged when all layers are converged
+        while not all(converged_layers):
             # Iteratively add one device per layer until converged
             for l_id in range(n_layers):
-                if len(route[l_id]) > 0:
-                    # Probability that all devices of layer will be offline
-                    p_failure = (1 - route[l_id]['p']).prod()
-                    # layer is converged when p_failure is below threshold
-                    converged_layers[l_id] = \
-                        p_failure < self.conf['layer_threshold']
+                # Skip this layer if converged
+                if converged_layers[l_id]:
+                    continue
 
-                    # Skip this layer if converged
-                    if converged_layers[l_id]:
-                        continue
-
-                # Else add a node to layer
-
-                # If view is empty, break
+                # If view is empty, exit
                 if len(view) == 0:
-                    print("[build route] No more available nodes: "
-                          "early abort.")
-                    converged = True
                     break
 
-                # Pick a device from view without replacement
[…]

### 2018-04-24 code/file_exchange/file.py

@@ -1,31 +1,77 @@
 #!/usr/bin/env python3
 
+from copy import deepcopy
 import numpy as np
+from .utils import random_string
 
 
+FILE_ID_SIZE = 10
+
+
+# We use this class to represent files to share and files to receive
 class File:
-    def __init__(self, n_chunks, file_id):
-        self.id = file_id
-        self.n_chunks = n_chunks
+    def __init__(self, size, chunk_max_size):
+        self.id = random_string(FILE_ID_SIZE)
+        self.size = size
 
+        # Computing size of chunks
+        self.chunks_size = []
+        while size > 0:
+            chunk_size = min(size, chunk_max_size)
+            size -= chunk_size
+            self.chunks_size.append(chunk_size)
+
+        self.n_chunks = len(self.chunks_size)
+
+        # Chunks either sent or received
+        # uint to count the number of times chunk was sent
         self.shared_chunks = np.array(
-            [False for _ in range(n_chunks)], dtype=np.bool)
+            [0 for _ in range(self.n_chunks)], dtype=np.uint)
+        # Chunks acknowledged (only for sender)
+        self.acked_chunks = self.shared_chunks.astype(np.bool)
 
+    # Used by sender to pick
     def select_chunk(self):
-        avail_chunks_id = np.argwhere(self.shared_chunks == False).ravel()
+        unsent_chunks_id = np.argwhere(self.shared_chunks == 0).ravel()
 
-        if len(avail_chunks_id) == 0:
+        # If there are chunks we did not send yet, pick them
+        if len(unsent_chunks_id) > 0:
+            return np.random.choice(unsent_chunks_id)
+
+        # Get ids of chunks not acked
+        not_acked_chunks_id = np.argwhere(self.acked_chunks == False).ravel()
+
+        # Wooo, all sent and all acknowledged
+        if len(not_acked_chunks_id):
             return None
 
-        return np.random.choice(avail_chunks_id)
+        # If all chunks were sent at least once
+        # Return the chunk_id that was sent the least but did not get an ack
+        for x in unsent_chunks_id.argsort():
+            if x in not_acked_chunks_id:
+                return x
 
-    def ack(self, chunk_id):
+    def shared(self, chunk_id):
         if chunk_id < 0 or chunk_id >= self.n_chunks:
             raise ValueError(
                 "chunk_id ({}) should be in bounds [0, {}]".format(
                     chunk_id, self.n_chunks))
 
[…]

### 2018-04-24 code/file_exchange/user.py

@@ -4,8 +4,6 @@ from . import model, device, config, file, utils
 import numpy as np
 import gevent
 
-FILE_ID_SIZE = 10
-
 
 class User(gevent.Greenlet):
     def __init__(self, global_view, net, conf=config.default):
@@ -26,16 +24,13 @@ class User(gevent.Greenlet):
         self.current_round = None
         self.name = utils.random_name()
 
-        self.receiving_files = {}
+        self.pending_files_info = {}
 
         self.state_history, self.devices_history = self.model.sample(
             length=conf['n_rounds'])
 
     # Overriding Greenlet
     def _run(self):
-        self.loop()
-
-    def loop(self):
         while True:
             # Initial round
             if self.current_round is None:
@@ -48,25 +43,40 @@ class User(gevent.Greenlet):
             else:
                 self.current_round += 1
 
-            # Update devices' state
-            for d_id, is_online in \
-                    enumerate(self.devices_history[self.current_round]):
-                self.devices[d_id].update_state(is_online)
+            self.update_state()
 
             # Sleep until next round
             gevent.sleep(self.conf['period'].total_seconds())
 
+    def update_state(self):
+        # Update devices' state
+        for d_id, is_online in \
+                enumerate(self.devices_history[self.current_round]):
+            self.devices[d_id].update_state(is_online)
+
     def init_file_receive(self, remote_device):
+        if self.current_round is None:
+            raise Error("User must do a first ")
         d = self.get_online_device()
 
-        H_rdv = d.build_route("receiver")
-        file_id = utils.random_string(FILE_ID_SIZE)
+        f = file.File(self.conf['file_size'], self.conf['chunk_max_size'])
 
-        self.receiving_files[file_id] = file.File(
-            self.conf['n_chunks'], file_id)
+        # route = L_RV + L_k + ... + L_l
+        route = d.build_route("receiver")
+        # H_rdv_forward = (L_RV + L_k + ... + L_l) + L_B (my devices)
+        H_rdv_forward = route + [self.get_all_devices()]
+        # H_rdv_backward = (L_l + ... + L_k + L_RV)
+        H_rdv_backward = route[::-1]
 
         # This exchange is out of band
-        remote_device.init_file_send(H_rdv, file_id)
+        forward_route, backward_route = remote_device.init_file_send(
+            H_rdv_forward, H_rdv_backward, f.copy())
+
+        self.sending_files[f.id] = {
+            'file': f,
+            'forward_route': forward_route,
[…]

### 2018-04-24 code/file_exchange/config.py
I think I cracked it, need to finish the code tomorrow

@@ -9,7 +9,7 @@ default = {
     'n_file_chunks': 10,
     'n_layers': 3,  # must be odd
     'file_size': 11,  # MB
-    'chunk_max_size': 2  # MB, will depend on header size later
+    'chunk_max_size': 2,  # MB, will depend on header size later
     'n_rounds': 2,
     'n_users': 20,
     'period': timedelta(seconds=1),

### 2018-04-24 code/file_exchange/device.py

@@ -3,6 +3,8 @@
 from . import config, peers_view, file, network
 from .utils import random_string, hash_layer
 from datetime import timedelta, datetime
+from gevent.queue import Queue
+import gevent
 import numpy as np
 import pandas as pd
 import random
@@ -10,39 +12,93 @@ import random
 ADDR_SIZE = 12
 
 
-class Device:
+class Device(gevent.Greenlet):
     def __init__(
             self, owner, global_view, net, device_id, device_type,
             conf=config.default):
-
+        gevent.Greenlet.__init__(self)
         self.addr = random_string(ADDR_SIZE)
         self.conf = conf
         self.device_id = device_id
         self.global_view = global_view
         self.gossip_size = conf['gossip_size']
-        self.is_online = False
+        self.lock = gevent.lock.Semaphore()
         self.net = net
+        self.online = gevent.event.Event()
         self.owner = owner
         self.peers_view = peers_view.PeersView(conf)
+        self.message_queue = Queue()
         self.type = device_type
 
         net.add_device(self)
 
-        # File-exchange related
+        # Contains only files that this particular device is sending
         self.sending_files = {}
-        self.sending_files_routes = {}
 
         # maps hash of route's layer -> previously picked device from layer
         self.connected_to = {}
 
-    def update_state(self, is_online):
-        self.is_online = is_online
-        if self.is_online:
+    # Overriding Greenlet
+    def _run(self):
+        while True:
+            self.online.wait()
+
+            # sending_files is going to need locks...
+            for f_id, file_info in self.sending_files.items():
+                if file_info['f'].all_acknowledged():
+                    del self.sending_files[f_id]
+                self.send_file_chunk(file_info)
+
+                if not self.is_online():
+                    continue
+
+            # TODO: Add locks!
+            for m in self.message_queue:
+                if m.file_id in self.owner.receiving_files:
+                    file_info = self.owner.receiving_files[m.file_id]
+
+                    if m.type != network.MessType.CHUNK:
+                        print("dafuq?")
+
+                    file_info['f'].shared(m.chunk_id)
+
+                    self.send_file_ack(file_info, m.chunk_id)
+
+                elif m.file_id in self.owner.sending_files:
+                    file_info = self.owner.sending_files[m.file_id]
+
+                    if m.type != network.MessType.ACK:
+                        print("dafuq?")
+
+                    file_info['f'].acknowledged(m.chunk_id)
+
+                    if file_info['f'].all_acknowledged():
[…]

### 2018-04-24 code/file_exchange/file.py

@@ -30,11 +30,11 @@ class File:
         # Chunks acknowledged (only for sender)
         self.acked_chunks = self.shared_chunks.astype(np.bool)
 
-    # Used by sender to pick
+    # Used by sender to pick right chunk to send
     def select_chunk(self):
         unsent_chunks_id = np.argwhere(self.shared_chunks == 0).ravel()
 
-        # If there are chunks we did not send yet, pick them
+        # If there are chunks we did not send yet, pick among them randomly
         if len(unsent_chunks_id) > 0:
             return np.random.choice(unsent_chunks_id)
 
@@ -51,6 +51,8 @@ class File:
             if x in not_acked_chunks_id:
                 return x
 
+    # Receiver: this chunk was received
+    # Sender: this chunk was sent
     def shared(self, chunk_id):
         if chunk_id < 0 or chunk_id >= self.n_chunks:
             raise ValueError(
@@ -59,6 +61,7 @@ class File:
 
         self.shared_chunks[chunk_id] += 1
 
+    # Sender: received ack for this chunk
     def acknowledged(self, chunk_id):
         if chunk_id < 0 or chunk_id >= self.n_chunks:
             raise ValueError(

### 2018-04-24 code/file_exchange/user.py

@@ -1,8 +1,8 @@
 #!/usr/bin/env python3
 
 from . import model, device, config, file, utils
-import numpy as np
 import gevent
+import random
 
 
 class User(gevent.Greenlet):
@@ -14,49 +14,65 @@ class User(gevent.Greenlet):
         self.n_devices = self.model.n_obs
         self.devices = [None] * self.n_devices
         self.devices_addr = [None] * self.n_devices
+        #self.devices_threads = gevent.pool.Group()
         for d_id in range(self.n_devices):
             self.devices[d_id] = device.Device(
                 self, global_view, net, d_id,
                 self.model.devices_type[d_id], conf)
             self.devices_addr[d_id] = self.devices[d_id].addr
+            self.devices[d_id].start()
+            # self.devices_threads.start(self.devices[d_id])
 
         self.conf = conf
         self.current_round = None
         self.name = utils.random_name()
 
-        self.pending_files_info = {}
+        # Any user's device can receive chunks
+        self.receiving_files = {}
+        # Any user's device can receive ACK, but only source can send chunks
+        self.sending_files = {}
+        self.lock = gevent.lock.Semaphore()
 
         self.state_history, self.devices_history = self.model.sample(
             length=conf['n_rounds'])
 
     # Overriding Greenlet
     def _run(self):
-        while True:
-            # Initial round
-            if self.current_round is None:
-                self.current_round = 0
-            # Break if all rounds done
-            elif self.current_round == self.conf['n_rounds'] - 1:
-                print("Returned")
-                return
-            # Else increment round
-            else:
-                self.current_round += 1
-
+        while self.current_round is None or \
+                self.current_round < self.conf['n_rounds'] - 1:
             self.update_state()
 
             # Sleep until next round
             gevent.sleep(self.conf['period'].total_seconds())
 
     def update_state(self):
+        self.lock.acquire()
+        # Initial round
+        if self.current_round is None:
+            self.current_round = 0
+        # Else increment round
+        elif self.current_round < self.conf['n_rounds'] - 1:
+            self.current_round += 1
+        else:
+            self.lock.release()
+            return
+
         # Update devices' state
         for d_id, is_online in \
                 enumerate(self.devices_history[self.current_round]):
-            self.devices[d_id].update_state(is_online)
 
[…]

### 2018-04-25 paper/security-analysis.tex
Adds security analysis section (WIP)

\section{Security analysis}%
\label{SecurityAnalysis}

\dots

### 2018-04-25 paper/building-blocks.tex
Adds building blocks section

\section{Building blocks}%
\label{BuildingBlocks}

\dots

### 2018-04-25 code/file_exchange/config.py
[some of] it works!

@@ -3,13 +3,16 @@
 from datetime import timedelta
 
 default = {
+    'ack_size': 0,  # MB
+    'bandwidth': 10,  # MB/s
+    'chunk_max_size': 2,  # MB, will depend on header size later
+    'file_size': 11,  # MB
     'gossip_size': 20,
+    'header_size': 0.1,  # MB, will depend on #devices/layers later
     'layer_threshold': 0.001,
     'minimum_node_availability': 0,
     'n_file_chunks': 10,
     'n_layers': 3,  # must be odd
-    'file_size': 11,  # MB
-    'chunk_max_size': 2,  # MB, will depend on header size later
     'n_rounds': 2,
     'n_users': 20,
     'period': timedelta(seconds=1),

### 2018-04-25 code/file_exchange/device.py

@@ -2,6 +2,7 @@
 
 from . import config, peers_view, file, network
 from .utils import random_string, hash_layer
+from copy import deepcopy
 from datetime import timedelta, datetime
 from gevent.queue import Queue
 import gevent
@@ -18,7 +19,9 @@ class Device(gevent.Greenlet):
             conf=config.default):
         gevent.Greenlet.__init__(self)
         self.addr = random_string(ADDR_SIZE)
+        self.all_files_sent = True
         self.conf = conf
+        self.death_requested = False
         self.device_id = device_id
         self.global_view = global_view
         self.gossip_size = conf['gossip_size']
@@ -41,52 +44,95 @@ class Device(gevent.Greenlet):
     # Overriding Greenlet
     def _run(self):
         while True:
-            self.online.wait()
+            # Wait until I'm online, with timeout
+            # online.wait(0.1) return True only if online has been set
+            while not self.online.wait(0.1):
+                # Kill the device if death requested
+                if self.death_requested and self.all_files_sent:
+                    return
 
-            # sending_files is going to need locks...
-            for f_id, file_info in self.sending_files.items():
-                if file_info['f'].all_acknowledged():
-                    del self.sending_files[f_id]
-                self.send_file_chunk(file_info)
+            # Kill the device if death requested
+            if self.death_requested and self.all_files_sent:
+                return
 
-                if not self.is_online():
-                    continue
+            # Send file chunks I am currently sharing
+            self.share_files()
 
-            # TODO: Add locks!
-            for m in self.message_queue:
-                if m.file_id in self.owner.receiving_files:
+            # self.lock.acquire()
+            # for f_id, file_info in self.sending_files.items():
+            #     if file_info['f'].all_acknowledged():
+            #         continue
+            #         # We never remove a file from sending_files
+            #         #del self.sending_files[f_id]
+
+            #     self.send_chunk(file_info)
+
+            #     if not self.is_online():
+            #         break
+            # self.lock.release()
+
+            if not self.is_online():
+                continue
+
+            # Treat the messages in the queue
+            while not self.message_queue.empty():
+                m = self.message_queue.get()
+
+                self.lock.acquire()
+                # If my owner requested this file, update file state
+                # and send acknowledgment
+                if m.file_id in self.owner.receiving_files and \
+                        m.type == network.MessType.CHUNK:
+
[…]

### 2018-04-25 code/file_exchange/file.py

@@ -5,7 +5,7 @@ import numpy as np
 from .utils import random_string
 
 
-FILE_ID_SIZE = 10
+FILE_ID_SIZE = 6
 
 
 # We use this class to represent files to share and files to receive
@@ -42,12 +42,12 @@ class File:
         not_acked_chunks_id = np.argwhere(self.acked_chunks == False).ravel()
 
         # Wooo, all sent and all acknowledged
-        if len(not_acked_chunks_id):
+        if len(not_acked_chunks_id) == 0:
             return None
 
         # If all chunks were sent at least once
         # Return the chunk_id that was sent the least but did not get an ack
-        for x in unsent_chunks_id.argsort():
+        for x in self.shared_chunks.argsort():
             if x in not_acked_chunks_id:
                 return x
 

### 2018-04-25 code/file_exchange/network.py

@@ -1,6 +1,28 @@
 #!/usr/bin/env python3
 
 from enum import Enum
+import gevent
+
+
+def emulate_transfer(dst, m, header_size, bandwidth):
+    '''
+    Sleeps the duration of the file transfer ((m.size+header_size)/bandwidth),
+    Drops the packet if dst is offline, else send it to dst.
+
+    dst: device.Device object
+    m: network.Message object
+    header_size: size of the header
+    bandwidth: numeric value in MB/s
+
+    Returns True if m was sent, False otherwise'''
+
+    gevent.sleep((m.size+header_size)/bandwidth)
+
+    if dst.is_online():
+        dst.receive(m)
+        return True
+
+    return False
 
 
 class MessType(Enum):
@@ -9,21 +31,28 @@ class MessType(Enum):
 
 
 class Message:
-    def __init__(self, typ, file_id, chunk_id):
+    def __init__(self, header, typ, file_id, chunk_id, size):
+        self.header = header
         self.type = typ
         self.file_id = file_id
         self.chunk_id = chunk_id
+        self.size = size
 
 
 class Network:
     def __init__(self):
         self.devices = dict()
+        self.lock = gevent.lock.Semaphore()
 
     def add_device(self, d):
+        self.lock.acquire()
         self.devices[d.addr] = d
+        self.lock.release()
 
     def get_device(self, addr):
+        self.lock.acquire()
         d = self.devices.get(addr)
+        self.lock.release()
         if d is None:
             raise ValueError("{} is not in the list of devices.".format(addr))
         return d

### 2018-04-25 code/file_exchange/user.py

@@ -14,14 +14,12 @@ class User(gevent.Greenlet):
         self.n_devices = self.model.n_obs
         self.devices = [None] * self.n_devices
         self.devices_addr = [None] * self.n_devices
-        #self.devices_threads = gevent.pool.Group()
+
         for d_id in range(self.n_devices):
             self.devices[d_id] = device.Device(
                 self, global_view, net, d_id,
                 self.model.devices_type[d_id], conf)
             self.devices_addr[d_id] = self.devices[d_id].addr
-            self.devices[d_id].start()
-            # self.devices_threads.start(self.devices[d_id])
 
         self.conf = conf
         self.current_round = None
@@ -38,12 +36,21 @@ class User(gevent.Greenlet):
 
     # Overriding Greenlet
     def _run(self):
+        # Starting devices greenlets
+        for d in self.devices:
+            d.start()
+
         while self.current_round is None or \
                 self.current_round < self.conf['n_rounds'] - 1:
             self.update_state()
 
             # Sleep until next round
             gevent.sleep(self.conf['period'].total_seconds())
+
+        for d in self.devices:
+            d.please_die()
+        #print(self.name + " is waiting on his devices to die.")
+        gevent.joinall(self.devices)
 
     def update_state(self):
         self.lock.acquire()
@@ -56,6 +63,9 @@ class User(gevent.Greenlet):
         else:
             self.lock.release()
             return
+
+        # print("User {} is at round #{}/{}".format(
+        #     self.name, self.current_round+1, self.conf['n_rounds']))
 
         # Update devices' state
         for d_id, is_online in \
@@ -72,7 +82,9 @@ class User(gevent.Greenlet):
 
         if self.current_round is None:
             self.lock.release()
-            raise Exception("User must do a first ")
+            raise Exception(
+                "User {} must do a first round before exchanging files".format(
+                    self.name))
         d = self.get_online_device()
 
         f = file.File(self.conf['file_size'], self.conf['chunk_max_size'])
@@ -89,7 +101,7 @@ class User(gevent.Greenlet):
             H_rdv_forward, H_rdv_backward, f.copy())
 
         self.receiving_files[f.id] = {
-            'file': f,
+            'f': f,
             'forward_route': forward_route,
             'backward_route': backward_route,
         }
@@ -100,6 +112,12 @@ class User(gevent.Greenlet):
 
[…]

### 2018-04-25 code/file_exchange/utils.py

@@ -3,6 +3,7 @@
 import random
 import string
 from pandas.util import hash_pandas_object
+import gevent
 
 
 NAMES = ['Cristy', 'Vickey', 'Sherie', 'Delilah', 'Rick', 'Denver', 'Stephany',

### 2018-04-25 code/file_exchange/config.py
lala

@@ -11,9 +11,13 @@ default = {
     'header_size': 0.1,  # MB, will depend on #devices/layers later
     'layer_threshold': 0.001,
     'minimum_node_availability': 0,
+    'output_dir': 'outputs/file_exchange/',
+    'do_monitor': True,
     'n_file_chunks': 10,
     'n_layers': 3,  # must be odd
     'n_rounds': 2,
     'n_users': 20,
-    'period': timedelta(seconds=1),
+    'n_file_exchanges': 10,
+    'period': timedelta(seconds=1),  # don't put milliseconds!
+    'send_strategy': 'random',  # 'random' or 'random_connected'
 }

### 2018-04-25 code/file_exchange/device.py

@@ -1,6 +1,6 @@
 #!/usr/bin/env python3
 
-from . import config, peers_view, file, network
+from . import config, peers_view, file, network, monitor
 from .utils import random_string, hash_layer
 from copy import deepcopy
 from datetime import timedelta, datetime
@@ -8,9 +8,13 @@ from gevent.queue import Queue
 import gevent
 import numpy as np
 import pandas as pd
-import random
+import time
+#import random
 
 ADDR_SIZE = 12
+MONITOR_COLUMNS = ['t', 'addr', 'owner',
+                   'file_id', 'chunk_id', 'type',
+                   'sent', 'received', 'forwarded']
 
 
 class Device(gevent.Greenlet):
@@ -26,6 +30,9 @@ class Device(gevent.Greenlet):
         self.global_view = global_view
         self.gossip_size = conf['gossip_size']
         self.lock = gevent.lock.Semaphore()
+        self.monitor = monitor.Monitor(MONITOR_COLUMNS,
+                                       conf['output_dir']+self.addr+'.csv',
+                                       conf['do_monitor'])
         self.net = net
         self.online = gevent.event.Event()
         self.owner = owner
@@ -49,11 +56,11 @@ class Device(gevent.Greenlet):
             while not self.online.wait(0.1):
                 # Kill the device if death requested
                 if self.death_requested and self.all_files_sent:
-                    return
+                    break
 
             # Kill the device if death requested
             if self.death_requested and self.all_files_sent:
-                return
+                break
 
             # Send file chunks I am currently sharing
             self.share_files()
@@ -84,13 +91,23 @@ class Device(gevent.Greenlet):
                 if m.file_id in self.owner.receiving_files and \
                         m.type == network.MessType.CHUNK:
 
+                    self.monitor.put([time.perf_counter(),
+                                      self.addr,
+                                      self.owner.name,
+                                      m.file_id,
+                                      m.chunk_id,
+                                      m.type,
+                                      0,
+                                      m.size+self.conf['header_size'],
+                                      0])
+
                     file_info = self.owner.receiving_files[m.file_id]
                     file_info['f'].shared(m.chunk_id)
 
-                    print("{} (owned by {}) successfully received "
-                          "file {}'s chunk #{}".format(
-                              self.addr, self.owner.name,
-                              m.file_id, m.chunk_id))
+                    # print("{} (owned by {}) successfully received "
+                    #       "file {}'s chunk #{}".format(
+                    #           self.addr, self.owner.name,
[…]

### 2018-04-25 code/file_exchange/network.py

@@ -2,27 +2,42 @@
 
 from enum import Enum
 import gevent
+import random
 
 
-def emulate_transfer(dst, m, header_size, bandwidth):
+def emulate_transfer(header, m, net, conf):
     '''
     Sleeps the duration of the file transfer ((m.size+header_size)/bandwidth),
-    Drops the packet if dst is offline, else send it to dst.
+    Then sends the message m to a connected peer in header or fails.
 
-    dst: device.Device object
-    m: network.Message object
-    header_size: size of the header
-    bandwidth: numeric value in MB/s
+    header: list of potential peers addresses
+    m: the message, a network.Message object
+    net: the Network object, to retrieve Device from address
+    conf: configuration variables (bandwidth and header_size)
 
     Returns True if m was sent, False otherwise'''
 
-    gevent.sleep((m.size+header_size)/bandwidth)
+    gevent.sleep((m.size+conf['header_size'])/conf['bandwidth'])
 
-    if dst.is_online():
-        dst.receive(m)
+    if conf['send_strategy'] == 'random':
+        # 1 - Pick a random device; send if online, fail if offline
+        dst = net.get_device(random.choice(header))
+        if dst.is_online():
+            dst.receive(m)
+            return True
+        return False
+
+    elif conf['send_strategy'] == 'random_connected':
+        # 2 - Pick a random *connected* device and send;
+        # Fails if no connected device
+        devices = [net.get_device(addr) for addr in header]
+        connected_devices = [d for d in devices if d.is_online()]
+        if len(connected_devices) == 0:
+            return False
+        random.choice(connected_devices).receive(m)
         return True
-
-    return False
+    else:
+        raise ValueError("conf['send_strategy'] is not valid.")
 
 
 class MessType(Enum):

### 2018-04-25 code/file_exchange/user.py

@@ -141,29 +141,3 @@ class User(gevent.Greenlet):
     # Overriding Greenlet
     def __str__(self):
         return "User({})".format(self.name)
-
-    # m.file_id in self.receiving_file must be checked by the caller
-    # def receive_chunk(self, d, m):
-    #     # We never remove a file from receiving_files
-    #     self.lock.acquire()
-    #     file_info = self.receiving_files[m.file_id]
-    #     file_info['f'].shared(m.chunk_id)
-    #     self.lock.release()
-
-    #     d.send_ack(file_info, m)
-
-    # def receive_ack(self, m):
-    #     # We never remove a file from receiving_files
-    #     self.lock.acquire()
-    #     self.sending_files[m.file_id]['f'].acknowledged(m.chunk_id)
-    #     self.lock.release()
-
-    # def receive_chunk(self, m):
-    #     self.receiving_files[m.file_id].ack(m.chunk_id)
-
-    #     if self.receiving_files[m.file_id].all_shared():
-    #         # Maybe do something else
-    #         del self.receiving_files[m.file_id]
-
-    # def has_online_devices(self):
-    #     return self.devices_history[self.current_round].sum() != 0

### 2018-04-25 code/file_exchange/utils.py

@@ -12,8 +12,15 @@ NAMES = ['Cristy', 'Vickey', 'Sherie', 'Delilah', 'Rick', 'Denver', 'Stephany',
          'Kandi', 'Karlene', 'Lila', 'Nelly', 'Sibyl', 'Kermit', 'Luke',
          'Annabel', 'Moira', 'Hassie', 'Hilda', 'Vicki', 'Gloria', 'Kaci',
          'Dora', 'Gilbert', 'Livia', 'Buffy', 'Demetra', 'Barry', 'Lizzette',
-         'Julius', 'Queen', 'Lyndsey', 'Lucy', 'Garnett',
-         'Lavette', 'Magaly', 'Norene']
+         'Julius', 'Queen', 'Lyndsey', 'Lucy', 'Garnett', 'Lavette', 'Magaly',
+         'Norene', 'Toshiko', 'Maurita', 'Angelika', 'Ann', 'Bennie',
+         'Randolph', 'Temika', 'Evelyne', 'Bettye', 'Angelita', 'Shawnda',
+         'Magdalen', 'Benjamin', 'Lorine', 'Morgan', 'Tim', 'Elinor', 'Cordia',
+         'Jay', 'Brain', 'Broderick', 'Janise', 'Nadia', 'Delaine', 'Vonnie',
+         'Adaline', 'Leigh', 'Consuelo', 'Janetta', 'Isaura', 'Elvera', 'Jack',
+         'Cristina', 'Charissa', 'Kaylee', 'Britany', 'Jenae', 'Yuriko',
+         'Annelle', 'Twila', 'January', 'Jillian', 'Maximo', 'Daysi', 'Mazie',
+         'Bronwyn', 'Otha', 'Shane', 'Brande', 'Renna']
 
 
 def random_name():

### 2018-04-25 paper/building-blocks.tex
Adds WIP on broadcast encryption building block

@@
 \dots
+
+\subsection{\Aclp*{KEM}}\label{KEM}
+
+\dots
+
+\subsection{\Acl*{BE}}\label{BE}
+
+We will do onion routing with many alternative nodes per hop.
+This means that we encrypt the same message for more than one possible 
+recipient.
+We will employ \iac{BE} scheme to do this.
+More specifically, we are interested in \iac{BE} adapted for \iac{P2P} setting 
+where devices can dynamically join and leave, \ie we do not want too much cost 
+for joining or leaving, \eg from key regeneration.
+We also want some privacy properties, \ie those of \ac{ANOBE}.
+
+\NewScheme{\DBE}{DBE}
+\NewAlgorithm{\DBEsetup}{\DBE\method Setup}
+\NewAlgorithm{\DBEjoin}{\DBE\method Join}
+\NewAlgorithm{\DBEleave}{\DBE\method Leave}
+\NewAlgorithm{\DBEenc}{\DBE\method Enc}
+\NewAlgorithm{\DBEdec}{\DBE\method Dec}
+
+% XXX Deal with self plagiarism here: \cite{PPACinPubFS}
+
+We need a decentralized \ac{BE} scheme, \(\DBE\).
+\(\DBE\) provides the following algorithms:
+\DBEsetup,\allowbreak \DBEjoin,\allowbreak \DBEleave,\allowbreak 
+\DBEenc,\allowbreak \DBEdec.
+
+The \(\DBEsetup\) algorithm generates the global parameters.
+The \(\DBEjoin\) algorithm performs necessary key generation and other 
+operations when a device joins whereas \(\DBEleave\) performs the necessary 
+operations when a device leaves.
+The \(\DBEenc\) algorithm takes a message and a recipient set \(S\) and returns 
+a ciphertext that everyone in \(S\) can decrypt using \(\DBEdec\).
+
+\NewScheme{\ANOBE}{ANOBE}
+\NewAlgorithm{\ANOBEsetup}{\ANOBE\method Setup}
+\NewAlgorithm{\ANOBEkeygen}{\ANOBE\method Keygen}
+
+We can use the \(\ANOBE\) scheme by \textcite{ANOBE} to instantiate our \(\DBE\) 
+scheme.
+We simply have to break \(\ANOBEsetup\) and \(\ANOBEkeygen\) into 
+\(\DBEsetup,\allowbreak \DBEjoin,\allowbreak \DBEleave\).

### 2018-04-26 paper/building-blocks.tex
WIP on broadcast encryption scheme

--- 2018-04-25 paper/building-blocks.tex
@@
 \dots
+
+\subsection{\Aclp*{KEM}}\label{KEM}
+
+\dots
+
+\subsection{\Acl*{BE}}\label{BE}
+
+We will do onion routing with many alternative nodes per hop.
+This means that we encrypt the same message for more than one possible 
+recipient.
+Given this, it is natural to look for a suitable \ac{BE} scheme.
+More specifically, we are interested in \iac{BE} scheme adapted for \iac{P2P} 
+setting, where devices can dynamically join and leave --- \ie we do not want too 
+much cost for joining or leaving, \eg from key regeneration.
+We also want some privacy properties, \eg those of \ac{ANOBE}.
+
+\NewScheme{\ANOBE}{ANOBE}
+\NewAlgorithm{\ANOBEsetup}{\ANOBE\method Setup}
+\NewAlgorithm{\ANOBEjoin}{\ANOBE*\method Join}
+\NewAlgorithm{\ANOBEleave}{\ANOBE*\method Leave}
+\NewAlgorithm{\ANOBEenc}{\ANOBE\method Enc}
+\NewAlgorithm{\ANOBEdec}{\ANOBE\method Dec}
+
+Our \ac{P2P} setting requires something similar to \iac{DBE} scheme.
+However, we want a slightly different definition.
+We say that \iac{BE} scheme is \iac{DeBE} if
+\begin{enumerate}
+  \item the setup is independent from the expected number of users or an upper 
+    bound thereof,
+  \item a new user can join at any time and the already issued decryption keys 
+    can remain the same,
+  \item the previous (public) encryption key can still be used if the newly 
+    joined user is not in the recipient set.
+\end{enumerate}
+Unlike the definition of \textcite{DynamicBroadcastEncryption}, we desire 
+forward secrecy --- in our scenario it makes no sense that new devices can 
+decrypt old ciphertexts.
+We also want to change the restriction on the ciphertext size:
+whereas \textcite{DynamicBroadcastEncryption} require the ciphertext size to be 
+independent from the expected number of users, we want it to be independent of 
+the total number of users --- \ie it can depend on the recipient set.
+In this sense, the trivial \ac{BE} scheme would fulfil our definition, but not 
+the definition of dynamic~\cite{DynamicBroadcastEncryption}.
+
+% XXX Deal with self plagiarism here: \cite{PPACinPubFS}
+
+\(\ANOBE\) provides the following algorithms:
+\ANOBEsetup,\allowbreak \ANOBEjoin,\allowbreak \ANOBEenc,\allowbreak \ANOBEdec.
+
+The \(\ANOBEsetup\) algorithm generates the global parameters.
+The \(\ANOBEjoin\) algorithm performs necessary key generation and other 
+operations when a device joins.
+The \(\ANOBEenc\) algorithm takes a message and a recipient set \(S\) and returns 
+a ciphertext that everyone in \(S\) can decrypt using \(\ANOBEdec\).
+
+\NewScheme{\ANOBE}{ANOBE}
+\NewAlgorithm{\ANOBEsetup}{\ANOBE\method Setup}
+\NewAlgorithm{\ANOBEkeygen}{\ANOBE\method Keygen}
+
+We can use the \(\ANOBE\) scheme by \textcite{ANOBE} to instantiate our 
+decentralized version.
+We simply have to break \(\ANOBEsetup\) and \(\ANOBEkeygen\) into 
+\(\ANOBEsetup,\allowbreak \ANOBEjoin\).
+
+\endinput
+
+\(\ANOBEsetup\) generates a master public key \(MPK = (\S*, \{\PubKey{i}\}_{i\in
+    U})\) and the master secret key \(MSK = \{\PriKey{i}\}_{i\in U}\), where 
+\((\PubKey{i}, \PriKey{i})\rgets \E*[Keygen][1^\lambda]\).
+\(\ANOBE[Keygen][MPK, MSK, i]\) simply returns \(\PriKey{i}\) from \(MSK\).
+
+For encryption, we must first generate a one-time signature key-pair 
+\((\SignKey{}, \VerifKey{})\), then we choose a random permutation \(\pi\colon 
+  R\to R\).
+Next we must encrypt the message \(m\) and the verification key \((m, 
+  \VerifKey{})\) for every user \(i\in R\) in the recipient set \(R\subseteq 
+  U\) under their respective public key, \(c_{i} = \E*[Enc][\PubKey{i}, 
+  m\concat \VerifKey{}]\).
+We let the \ac{ANOBE} ciphertext be the tuple \((\VerifKey{}, C, \sigma)\), 
+where
+\(C = ( c_{\pi(1)}, \ldots, c_{\pi({|S|})})\) and
+\(\sigma = \S*[Sign][\SignKey{}, C ]\).
+Note that the signature does not authenticate the sender, it ties the 
+ciphertext together and is needed for correctness.
+
+\begin{frame}
+  \begin{figure}
+    \begin{algorithmic}
+      \Function{$\ANOBEenc$}{$MPK, m, R$}
+      \Comment{%
+        Recipient set $R$,
+        $m$ to be encrypted.
+      }
+        \State{%
+          $(\SignKey{}, \VerifKey{})\rgets{\S*[Keygen][1^\lambda]}$
+        }
+        \Comment{%
+          Signature key-pair, security parameter $\lambda$
+        }
+        \State{%
+          Choose a random permutation \(\pi\colon R\to R\).
+        }
+
+        \For{$i \in R$}
+          \State{%
+            $c_{i}\gets{ \E*[Enc][\PubKey{i}, m\concat \VerifKey{}] }$
+          }
+        \EndFor{}
+
+        \State{%
+          $C\gets{( c_{\pi(1)}, \ldots, c_{\pi({|S|})} )}$
+        }
+        \State{%
+          $\sigma\gets{ \S*[Sign][\SignKey{}, C] }$
+        }
+        \State{%
+          \Return{$(\VerifKey{}, C, \sigma)$}
+        }
+      \EndFunction{}
+    \end{algorithmic}
+    \caption{%
+      An algorithmic overview of the encryption algorithm in the \ac{ANOBE} 
+      scheme.
+    }\label{EncANOBE}
+  \end{figure}
+\end{frame}
+
+We now have data which would like to decrypt.
+We parse it as \((\VerifKey{}, C, \sigma)\).
+If \(\S*[Verify][\VerifKey{}, C, \sigma ] = 0\), we return \(\bot\) as the 
+verification failed.
+For each \(c\) in \(C\):
+Compute \(M = \E*[Dec][\PriKey{}, c ]\).
+If \(M \neq \bot\) and \(M = (m, \VerifKey{})\), then return \(m\).
+Otherwise, try the next \(c\).
+If there are no more \(c\) to try, then return \(\bot\).
+
+\begin{frame}
+  \begin{figure}
+    \begin{algorithmic}
+      \Function{$\ANOBEdec$}{$MPK, \PriKey{}, C_{\ANOBE}$}
+%      \Comment{%
+%        Private key \(\PriKey{}\),
+%        ciphertext $C_{\ANOBE} = (\VerifKey{}, C, \sigma)$.
+%      }
+
+        \If{$\S*[Verify][\VerifKey{}, C, \sigma ] = 0$}
+          \State{%
+            \Return{$\bot$}
+          }
+        \EndIf{}
+
+        \For{$c\in C$}
+          \State{%
+            $M\gets{\E*[Dec][\PriKey{}, c]}$
+          }
+          \Comment{%
+            Try to decrypt
+          }
+          \If{$M = \bot$}
+            \State{\Return{$\bot$}}
+          \ElsIf{$M = (m, \VerifKey{})$}
+            \State{\Return{m}}
+          \EndIf{}
+        \EndFor{}
+        \State{\Return{$\bot$}}
+      \EndFunction{}
+    \end{algorithmic}
+    \caption{%
+      An algorithmic overview of the decryption algorithm in the \ac{ANOBE} 
+      scheme.
+    }\label{DecANOBE}
+  \end{figure}
+\end{frame}
+
+To decrypt an \ac{ANOBE} ciphertext, we need a trial-and-error decryption 
+procedure to decide if the ciphertext was indeed intended for us.
+This is costly as it makes the decryption function complexity \(O(|S|)\).
+\citet{ANOBE} presented a tag-hint system along with their \ac{ANOBE} scheme.
+The tag-hint system reduced the complexity back to \(O(1)\).
+As this is not relevant for our discussion, we refer the reader to~\cite{ANOBE} 
+but note that it can be used.

### 2018-04-26 paper/algorithm.tex
SPOR: changes Secure to Stateless
Updates SPOR subsection title
Adds use of breqn package

@@
 
-\subsection{\(\SPOR\)}
+\subsection{\(\SPOR\): Stateless Predictive Onion Routing}
 
@@
 
-We have the Secure Probabilistic Onion Routing scheme, \SPOR, which provides 
+We have the Stateless Predictive Onion Routing scheme, \SPOR, which provides 
 probabilistically onion-routed message passing.
@@
 
-We select several relays at each point of the route: $R_i=\{r_{i,j}\}$ would be the \emph{set} of possibly disconnected devices that will take the $i^\text{th}$ position in our onion route.
+We select several relays at each point of the route: $R_i=\{r_{i,j}\}$ would be 
+the \emph{set} of possibly disconnected devices that will take the 
+$i^{\text{th}}$ position in our onion route.
 In traditional onion routing, $r_1$ is the only one knowing the address of $r_2$, because it is written encrypted with its public key in the header.

### 2018-04-26 code/file_exchange/config.py
updated emulate_transfer function

@@ -19,5 +19,6 @@ default = {
     'n_users': 20,
     'n_file_exchanges': 10,
     'period': timedelta(seconds=1),  # don't put milliseconds!
+    'ping_time': 0.1,  # s
     'send_strategy': 'random',  # 'random' or 'random_connected'
 }

### 2018-04-26 code/file_exchange/device.py

@@ -12,7 +12,7 @@ import time
 #import random
 
 ADDR_SIZE = 12
-MONITOR_COLUMNS = ['t', 'addr', 'owner',
+MONITOR_COLUMNS = ['t', 'addr', 'owner', 'current_round',
                    'file_id', 'chunk_id', 'type',
                    'sent', 'received', 'forwarded']
 
@@ -31,7 +31,7 @@ class Device(gevent.Greenlet):
         self.gossip_size = conf['gossip_size']
         self.lock = gevent.lock.Semaphore()
         self.monitor = monitor.Monitor(MONITOR_COLUMNS,
-                                       conf['output_dir']+self.addr+'.csv',
+                                       conf['output_dir'], self.addr,
                                        conf['do_monitor'])
         self.net = net
         self.online = gevent.event.Event()
@@ -94,9 +94,10 @@ class Device(gevent.Greenlet):
                     self.monitor.put([time.perf_counter(),
                                       self.addr,
                                       self.owner.name,
+                                      self.owner.get_current_round(),
                                       m.file_id,
                                       m.chunk_id,
-                                      m.type,
+                                      m.type.value,
                                       0,
                                       m.size+self.conf['header_size'],
                                       0])
@@ -118,9 +119,10 @@ class Device(gevent.Greenlet):
                     self.monitor.put([time.perf_counter(),
                                       self.addr,
                                       self.owner.name,
+                                      self.owner.get_current_round(),
                                       m.file_id,
                                       m.chunk_id,
-                                      m.type,
+                                      m.type.value,
                                       0,
                                       m.size+self.conf['header_size'],
                                       0])
@@ -144,9 +146,10 @@ class Device(gevent.Greenlet):
                     self.monitor.put([time.perf_counter(),
                                       self.addr,
                                       self.owner.name,
+                                      self.owner.get_current_round(),
                                       m.file_id,
                                       m.chunk_id,
-                                      m.type,
+                                      m.type.value,
                                       0,
                                       0,
                                       m.size+self.conf['header_size']])
@@ -246,9 +249,10 @@ class Device(gevent.Greenlet):
                 self.monitor.put([time.perf_counter(),
                                   self.addr,
                                   self.owner.name,
+                                  self.owner.get_current_round(),
                                   m.file_id,
                                   m.chunk_id,
-                                  m.type,
+                                  m.type.value,
                                   m.size+self.conf['header_size'],
                                   0,
                                   0])
@@ -272,9 +276,10 @@ class Device(gevent.Greenlet):
[…]

### 2018-04-26 code/file_exchange/network.py

@@ -7,8 +7,9 @@ import random
 
 def emulate_transfer(header, m, net, conf):
     '''
-    Sleeps the duration of the file transfer ((m.size+header_size)/bandwidth),
-    Then sends the message m to a connected peer in header or fails.
+    Attempts to send m to a node in header.
+    Emulates traffic by sleeping ((m.size+header_size)/bandwidth).
+
 
     header: list of potential peers addresses
     m: the message, a network.Message object
@@ -17,10 +18,10 @@ def emulate_transfer(header, m, net, conf):
 
     Returns True if m was sent, False otherwise'''
 
-    gevent.sleep((m.size+conf['header_size'])/conf['bandwidth'])
-
     if conf['send_strategy'] == 'random':
-        # 1 - Pick a random device; send if online, fail if offline
+        # 1 - Try to send to a random device: we always sleep
+        # Fail if device is offline, else send to dst
+        gevent.sleep((m.size+conf['header_size'])/conf['bandwidth'])
         dst = net.get_device(random.choice(header))
         if dst.is_online():
             dst.receive(m)
@@ -28,12 +29,16 @@ def emulate_transfer(header, m, net, conf):
         return False
 
     elif conf['send_strategy'] == 'random_connected':
-        # 2 - Pick a random *connected* device and send;
-        # Fails if no connected device
+        # 2 - Ping devices to find a random *connected* one.
+        # Fail if no connected device, else send pick device.
         devices = [net.get_device(addr) for addr in header]
+        gevent.sleep(conf['ping_time'])
         connected_devices = [d for d in devices if d.is_online()]
+
         if len(connected_devices) == 0:
             return False
+
+        gevent.sleep((m.size+conf['header_size'])/conf['bandwidth'])
         random.choice(connected_devices).receive(m)
         return True
     else:

### 2018-04-26 code/file_exchange/user.py

@@ -49,7 +49,6 @@ class User(gevent.Greenlet):
 
         for d in self.devices:
             d.please_die()
-        #print(self.name + " is waiting on his devices to die.")
         gevent.joinall(self.devices)
 
     def update_state(self):
@@ -137,6 +136,12 @@ class User(gevent.Greenlet):
 
     def get_online_device(self):
         return random.choice([d for d in self.devices if d.is_online()])
+
+    def get_current_round(self):
+        self.lock.acquire()
+        r = self.current_round
+        self.lock.release()
+        return r
 
     # Overriding Greenlet
     def __str__(self):

### 2018-04-26 paper/building-blocks.tex
Finalizes broadcast encryption section

--- 2018-04-25 paper/building-blocks.tex
@@
 \dots
+
+\subsection{\Aclp*{KEM}}\label{KEM}
+
+\dots
+
+\subsection{\Acl*{BE}}\label{BE}
+
+We will do onion routing with many alternative nodes per hop.
+This means that we encrypt the same message for more than one possible 
+recipient.
+Given this, it is natural to look for a suitable \ac{BE} scheme.
+More specifically, we are interested in \iac{BE} scheme adapted for \iac{P2P} 
+setting, where devices can dynamically join and leave --- \ie we do not want too 
+much cost for joining or leaving, \eg from key regeneration.
+We also want some privacy properties, \eg those of \ac{ANOBE}.
+
+Our \ac{P2P} setting requires something similar to \iac{DBE} scheme.
+However, we want a slightly different definition.
+We say that \iac{BE} scheme is \iac{DeBE} if
+\begin{enumerate}
+  \item the setup is independent from the expected number of users or an upper 
+    bound thereof,
+  \item a new user can join at any time and the already issued decryption keys 
+    can remain the same,
+  \item the previous (public) encryption key can still be used if the newly 
+    joined user is not in the recipient set.
+\end{enumerate}
+Unlike the definition of \textcite{DynamicBroadcastEncryption}, we desire 
+forward secrecy --- in our scenario it makes no sense that new devices can 
+decrypt old ciphertexts.
+We also want to change the restriction on the ciphertext size:
+whereas \textcite{DynamicBroadcastEncryption} require the ciphertext size to be 
+independent from the expected number of users, we want it to be independent of 
+the total number of users --- \ie it can depend on the recipient set.
+In this sense, the trivial \ac{BE} scheme would fulfil our definition, but not 
+the definition of dynamic~\cite{DynamicBroadcastEncryption}.
+
+\NewScheme{\ANOBE}{ANOBE}
+\NewScheme{\DeBE}{DeBE}
+\NewAlgorithm{\DeBEsetup}{\DeBE[Setup]}
+\NewAlgorithm{\DeBEjoin}{\DeBE[Join]}
+\NewAlgorithm{\DeBEenc}{\DeBE[Enc]}
+\NewAlgorithm{\DeBEdec}{\DeBE[Dec]}
+
+Our \ac{DeBE} scheme, \(\DeBE\), provides the following algorithms:
+\(\DeBEsetup, \allowbreak \DeBEjoin, \allowbreak \DeBEenc, \allowbreak 
+  \DeBEdec\).
+We will use the proposed instantiation of \iac{ANOBE} scheme by \textcite{ANOBE} 
+to instantiate our \ac{DeBE} scheme.
+We will simply divide the steps of the \(\ANOBE\) algorithms differently.
+
+\NewVariable{\mpk}{MPK}
+\NewScheme{\Enc}{E}
+\NewScheme{\Sign}{S}
+
+\(\DeBEsetup[\lambda]\): takes the security parameter \(\lambda\) and generates 
+the global parameters for the underlying IND-CCA encryption scheme \(\Enc\) and 
+the one-time signature scheme \(\Sign\).
+It also creates a master public key, \(\mpk = \emptyset\).
+
+\NewVariable{\pk}{pk}
+\NewVariable{\sk}{sk}
+
+\((\pk_i, \sk_i)\gets \DeBEjoin[i]\): generates the public--private key-pair 
+\((\pk_i, \sk_i)\) for device \(i\) when it joins.
+It also adds \(\pk_i\) to \(\mpk\).
+See \cref{DeBEsetup} for an algorithmic overview.
+
+\begin{figure}
+  \begin{algorithmic}
+    \Require{$\Enc$ is an IND-CCA encryption scheme, $\Sign$ is a one-time 
+      signature scheme.}
+
+    \Function{\DeBEsetup}{$\lambda$}
+      \State $\Enc[Setup](\lambda), \Sign[Setup](\lambda)$
+      \State $\mpk\gets \emptyset$
+    \EndFunction
+
+    \Function{\DeBEjoin}{$i$}
+      \State $(\pk_i, \sk_i)\gets \Enc[Keygen]$
+      \State $\mpk\gets \mpk\cup \{\pk_i\}$
+      \State \Return $(\pk_i, \sk_i)$
+    \EndFunction
+  \end{algorithmic}
+  \caption{\label{DeBEsetup}\label{DeBEjoin}%
+    Algorithmic overview of \(\DeBEsetup\) and \(\DeBEjoin\).
+  }
+\end{figure}
+
+\NewVariable{\ssk}{ssk}
+\NewVariable{\vk}{vk}
+
+\((\vk, C, \sigma)\gets \DeBEenc[\mpk, m, S]\):
+takes a message \(m\) and a recipient set \(S\), it then encrypts the message 
+for each recipient's key, signs the tuple of all ciphertexts and returns the 
+verification key, ciphertexts and signature.
+(Note that the signature does not authenticate the sender, it ties the 
+ciphertext together and is needed for correctness, we refer to~\cite{ANOBE} for 
+details.)
+
+\(m\gets \DeBEdec[\mpk, \sk_i, (\vk, C, \sigma)]\):
+takes a ciphertext \((\vk, C, \sigma)\) and tries to decrypt the sub-ciphertexts 
+in \(C\) using the private key \(\sk_i\).
+If one succeeds, that message is returned, otherwise \(\bot\) is returned on 
+failure.
+This trial-and-error decryption is costly as it makes the decryption function 
+complexity \(O(|S|)\).
+\textcite{ANOBE} also presented a tag-hint system along with their \ac{ANOBE} 
+scheme.
+The tag-hint system reduced the complexity back to \(O(1)\).
+As this is not relevant for our discussion, we refer the reader to~\cite{ANOBE} 
+but note that it can be used.
+
+Both \(\DeBEenc\) and \(\DeBEdec\) are the same as in~\cite{ANOBE}.
+The algorithms are illustrated in \cref{DeBEenc,DeBEdec}.
+
+\begin{frame}
+  \begin{figure}
+    \begin{algorithmic}
+      \Require{$\Enc$ is an IND-CCA encryption scheme, $\Sign$ is a one-time 
+        signature scheme.}
+
+      \Function{$\DeBEenc$}{$\mpk, m, S$}
+        \State $(\ssk, \vk)\gets \Sign[Keygen]$
+        \State Choose a random permutation \(\pi\colon S\to S\).
+        \For{$i \in S$}
+          \State $c_i\gets \Enc[Enc](\pk_i, m\concat \vk)$
+        \EndFor
+        \State $C\gets ( c_{\pi(1)}, \dotsc, c_{\pi(|S|)} )$
+        \State $\sigma\gets \Sign[Sign](\ssk, C)$
+        \State \Return $(\vk, C, \sigma)$
+      \EndFunction
+
+      \Function{$\DeBEdec$}{$\mpk, \sk_i, (\vk, C, \sigma)$}
+        \If{$\Sign[Verify](\vk, C, \sigma) = \bot$}
+          \State \Return $\bot$
+        \EndIf
+        \For{$c\in C$}
+          \Comment Trial-and-error decryption
+          \State $M\gets{\Enc[Dec](\sk_i, c)}$
+          \If{$M = \bot$}
+            \State \Return $\bot$
+          \ElsIf{$M = (m, \vk)$}
+            \State \Return $m$
+          \EndIf
+        \EndFor
+        \State \Return $\bot$
+      \EndFunction
+    \end{algorithmic}
+    \caption{\label{DeBEenc}\label{DeBEdec}%
+      An algorithmic overview of the encryption and decryption algorithms in the 
+      \(\DeBE\) scheme, identical to those of \(\ANOBE\).%
+    }
+  \end{figure}
+\end{frame}

### 2018-04-27 paper/building-blocks.tex

@@
 
-\subsection{\Aclp*{KEM}}\label{KEM}
+\subsection{Hybrid encryption}\label{KEM}
 
-\dots
+\Iac{HE} scheme is a combination of \iac{PKE} scheme and \iac{SKE} scheme.
+The \ac{PKE} scheme is used as \iac{KEM} to encrypt a symmetric key for the 
+\ac{SKE} scheme.
+Then the \ac{SKE} scheme is used as \iac{DEM} to encrypt the actual data.
+
+Whenever we use \iac{PKE} scheme, we mean to employ it in \iac{HE} scheme.
 
@@
   \begin{algorithmic}
-    \Require{$\Enc$ is an IND-CCA encryption scheme, $\Sign$ is a one-time 
+    \Require{$\Enc$ is an IND-CCA \ac{PKE} scheme, $\Sign$ is a one-time 
       signature scheme.}
@@
     \begin{algorithmic}
-      \Require{$\Enc$ is an IND-CCA encryption scheme, $\Sign$ is a one-time 
+      \Require{$\Enc$ is an IND-CCA \ac{PKE} scheme, $\Sign$ is a one-time 
         signature scheme.}

### 2018-04-27 code/file_exchange/config.py
interpreting results

@@ -2,16 +2,18 @@
 
 from datetime import timedelta
 
+EXPERIMENT_NAME = 'default'
 default = {
-    'ack_size': 0,  # MB
-    'bandwidth': 10,  # MB/s
-    'chunk_max_size': 2,  # MB, will depend on header size later
-    'file_size': 11,  # MB
+    'ack_size': 0,  # kB
+    'bandwidth': 400,  # kB/s
+    'chunk_max_size': 128,  # kB, will depend on header size later
+    'file_size': 10240,  # kB
     'gossip_size': 20,
-    'header_size': 0.1,  # MB, will depend on #devices/layers later
+    'header_size': 100,  # kB, will depend on #devices/layers later
     'layer_threshold': 0.001,
     'minimum_node_availability': 0,
-    'output_dir': 'outputs/file_exchange/',
+    'experiment_name': EXPERIMENT_NAME,
+    'output_dir': 'data/'+EXPERIMENT_NAME+'/',
     'do_monitor': True,
     'n_file_chunks': 10,
     'n_layers': 3,  # must be odd

### 2018-04-27 code/file_exchange/device.py

@@ -9,12 +9,13 @@ import gevent
 import numpy as np
 import pandas as pd
 import time
-#import random
+# import random
 
 ADDR_SIZE = 12
 MONITOR_COLUMNS = ['t', 'addr', 'owner', 'current_round',
-                   'file_id', 'chunk_id', 'type',
-                   'sent', 'received', 'forwarded']
+                   'file_id', 'chunk_id', 'mess_id', 'type',
+                   'sent', 'received', 'forwarded', 'success',
+                   'messages_in_queue']
 
 
 class Device(gevent.Greenlet):
@@ -31,7 +32,8 @@ class Device(gevent.Greenlet):
         self.gossip_size = conf['gossip_size']
         self.lock = gevent.lock.Semaphore()
         self.monitor = monitor.Monitor(MONITOR_COLUMNS,
-                                       conf['output_dir'], self.addr,
+                                       conf['output_dir'],
+                                       "device_" + self.addr,
                                        conf['do_monitor'])
         self.net = net
         self.online = gevent.event.Event()
@@ -55,28 +57,19 @@ class Device(gevent.Greenlet):
             # online.wait(0.1) return True only if online has been set
             while not self.online.wait(0.1):
                 # Kill the device if death requested
-                if self.death_requested and self.all_files_sent:
+                if self.death_requested and self.all_files_sent and \
+                        self.message_queue.empty():
+                    # if self.death_requested:
                     break
 
             # Kill the device if death requested
-            if self.death_requested and self.all_files_sent:
+            if self.death_requested and self.all_files_sent and \
+                    self.message_queue.empty():
+                # if self.death_requested:
                 break
 
             # Send file chunks I am currently sharing
             self.share_files()
-
-            # self.lock.acquire()
-            # for f_id, file_info in self.sending_files.items():
-            #     if file_info['f'].all_acknowledged():
-            #         continue
-            #         # We never remove a file from sending_files
-            #         #del self.sending_files[f_id]
-
-            #     self.send_chunk(file_info)
-
-            #     if not self.is_online():
-            #         break
-            # self.lock.release()
 
             if not self.is_online():
                 continue
@@ -91,16 +84,7 @@ class Device(gevent.Greenlet):
                 if m.file_id in self.owner.receiving_files and \
                         m.type == network.MessType.CHUNK:
 
-                    self.monitor.put([time.perf_counter(),
-                                      self.addr,
-                                      self.owner.name,
-                                      self.owner.get_current_round(),
-                                      m.file_id,
-                                      m.chunk_id,
[…]

### 2018-04-27 code/file_exchange/monitor.py

@@ -1,0 +1,51 @@
+#!/usr/bin/env python3
+
+import gevent
+import os
+import sys
+import pandas as pd
+
+
+class Monitor:
+    def __init__(self, columns, save_dir, name, do_monitor):
+        self.do_monitor = do_monitor
+        if save_dir is None:
+            self.do_monitor = False
+        if self.do_monitor:
+            self.df = pd.DataFrame(columns=columns)
+            self.save_path = save_dir + name + ".csv"
+            self.lock = gevent.lock.Semaphore()
+            # Better try saving now
+            self.save()
+
+    def save(self):
+        if self.do_monitor:
+            dir_path = os.path.dirname(self.save_path)
+            if not os.path.isdir(dir_path):
+                os.makedirs(dir_path)
+
+            try:
+                self.lock.acquire()
+                self.df.to_csv(self.save_path, index=False)
+                self.lock.release()
+            except:
+                e = sys.exc_info()[0]
+                raise OSError("Could not save to {}: {}".format(
+                    self.save_path, str(e)))
+            # else:
+            #     print("Successfully saved {}. {} lines.".format(
+            #         self.save_path, self.df.shape[0]))
+
+    def put(self, line):
+        if self.do_monitor:
+            if len(line) != len(self.df.columns):
+                print("Columns:", self.df.columns)
+                print("Line:", line)
+                raise ValueError(
+                    "Come back when you learnt to count:"
+                    " invalid columns number")
+
+            new_row = dict(zip(self.df.columns, line))
+            self.lock.acquire()
+            self.df = self.df.append(new_row, ignore_index=True)
+            self.lock.release()

### 2018-04-27 code/file_exchange/network.py

@@ -3,6 +3,7 @@
 from enum import Enum
 import gevent
 import random
+import sys
 
 
 def emulate_transfer(header, m, net, conf):
@@ -50,8 +51,15 @@ class MessType(Enum):
     ACK = 2
 
 
+MAX_MESSAGE_ID = 2**16
+
+
 class Message:
-    def __init__(self, header, typ, file_id, chunk_id, size):
+    def __init__(self, header, typ, file_id, chunk_id, size, m_id=None):
+        if m_id is None:
+            self.id = random.randint(0, MAX_MESSAGE_ID)
+        else:
+            self.id = m_id
         self.header = header
         self.type = typ
         self.file_id = file_id

### 2018-04-27 code/file_exchange/peers_view.py

@@ -1,7 +1,7 @@
 #!/usr/bin/env python3
 
 import pandas as pd
-from datetime import timedelta, datetime
+import time
 from . import config
 from gevent.lock import Semaphore
 
@@ -89,7 +89,8 @@ class PeersView:
     # Must be called inside lock
     def _prune_view(self):
         # Time-bound
-        expiration_limit = datetime.now() - self.conf['period']
+        expiration_limit = \
+            time.perf_counter() - self.conf['period'].total_seconds()
 
         # print(self._view.index)
         self._view = self._view[self._view.index >= expiration_limit]

### 2018-04-27 code/file_exchange/user.py

@@ -1,16 +1,21 @@
 #!/usr/bin/env python3
 
-from . import model, device, config, file, utils
+from . import model, device, config, file, utils, monitor
 import gevent
 import random
+import time
+
+MONITOR_COLUMNS = ['t', 'user', 'current_round']
 
 
 class User(gevent.Greenlet):
     def __init__(self, global_view, net, conf=config.default):
         gevent.Greenlet.__init__(self)
-        self.model = model.get_random()
 
-        # Create devices
+        self.name = utils.random_name()
+
+        # Create model and devices
+        self.model = model.get_random()
         self.n_devices = self.model.n_obs
         self.devices = [None] * self.n_devices
         self.devices_addr = [None] * self.n_devices
@@ -23,7 +28,11 @@ class User(gevent.Greenlet):
 
         self.conf = conf
         self.current_round = None
-        self.name = utils.random_name()
+        self.monitor = monitor.Monitor(
+            MONITOR_COLUMNS,
+            conf['output_dir'],
+            "user_"+self.name,
+            conf['do_monitor'])
 
         # Any user's device can receive chunks
         self.receiving_files = {}
@@ -42,14 +51,23 @@ class User(gevent.Greenlet):
 
         while self.current_round is None or \
                 self.current_round < self.conf['n_rounds'] - 1:
+            t_start = time.perf_counter()
             self.update_state()
 
             # Sleep until next round
-            gevent.sleep(self.conf['period'].total_seconds())
+            gevent.sleep(self.conf['period'].total_seconds() -
+                         (time.perf_counter() - t_start))
+
+            # print("User {}: round #{}/{} in {:.2f}s".format(
+            #     self.name, self.current_round+1,
+            #     self.conf['n_rounds'], time.perf_counter() - t_start))
+
+        self.monitor.save()
 
         for d in self.devices:
             d.please_die()
         gevent.joinall(self.devices)
+        print("User {} is done".format(self.name))
 
     def update_state(self):
         self.lock.acquire()
@@ -63,8 +81,11 @@ class User(gevent.Greenlet):
             self.lock.release()
             return
 
-        # print("User {} is at round #{}/{}".format(
-        #     self.name, self.current_round+1, self.conf['n_rounds']))
+        self.monitor.put([
+            time.perf_counter(),
+            self.name,
+            self.current_round
+        ])
 
         # Update devices' state
         for d_id, is_online in \
@@ -84,12 +105,20 @@ class User(gevent.Greenlet):
[…]

### 2018-04-27 code/file_exchange/utils.py

@@ -7,19 +7,19 @@ import gevent
 
 
 NAMES = ['Cristy', 'Vickey', 'Sherie', 'Delilah', 'Rick', 'Denver', 'Stephany',
-         'Many', 'Sandie', 'Deneen', 'Jesica', 'Newton', 'Maxwell', 'Sherrie',
+         'Many', 'Sandie', 'Deneen', 'Jesica', 'Newton', 'Maxwell', 'Morty',
          'Beatriz', 'Georgene', 'Herma', 'Mi', 'Bobbi', 'Julianna', 'Reita',
          'Kandi', 'Karlene', 'Lila', 'Nelly', 'Sibyl', 'Kermit', 'Luke',
-         'Annabel', 'Moira', 'Hassie', 'Hilda', 'Vicki', 'Gloria', 'Kaci',
+         'Annabel', 'Moira', 'Hassie', 'Gilda', 'Vicki', 'Gloria', 'Kaci',
          'Dora', 'Gilbert', 'Livia', 'Buffy', 'Demetra', 'Barry', 'Lizzette',
          'Julius', 'Queen', 'Lyndsey', 'Lucy', 'Garnett', 'Lavette', 'Magaly',
          'Norene', 'Toshiko', 'Maurita', 'Angelika', 'Ann', 'Bennie',
-         'Randolph', 'Temika', 'Evelyne', 'Bettye', 'Angelita', 'Shawnda',
+         'Randolph', 'Temika', 'Evelyne', 'Betty', 'Athena', 'Shawnda',
          'Magdalen', 'Benjamin', 'Lorine', 'Morgan', 'Tim', 'Elinor', 'Cordia',
-         'Jay', 'Brain', 'Broderick', 'Janise', 'Nadia', 'Delaine', 'Vonnie',
+         'Jay Z', 'Brian', 'Broderick', 'Janise', 'Nadia', 'Delaine', 'Vonnie',
          'Adaline', 'Leigh', 'Consuelo', 'Janetta', 'Isaura', 'Elvera', 'Jack',
-         'Cristina', 'Charissa', 'Kaylee', 'Britany', 'Jenae', 'Yuriko',
-         'Annelle', 'Twila', 'January', 'Jillian', 'Maximo', 'Daysi', 'Mazie',
+         'Cristina', 'Charissa', 'Kaylee', 'Britany', 'Jayne', 'Yuriko',
[…]

### 2018-04-27 paper/abstract.tex
abstract

@@
 
-\dots
+%abstract
+%problem/topic
+This paper presents privacy-preserving file sharing without relying on any third-party storage such as cloud services or peers.
+
+%research gap
+Centralized file-sharing systems, i.e.
+cloud storage such as Dropbox require trust in the service provider and can be monitored.
+P2P file-sharing relies on replicas on other people's machines.
+We are interested in minimizing trust needed in other systems and preserving the user's privacy in terms of data and metadata, i.e.
+what they share with whom and when.
+
+%why now
+Nowadays, many people use multiple devices and it has thus become possible to benefit from p2p technology for one's own devices alone and thus reducing one's exposure to security and privacy vulnerabilities and threats from third parties.
+
+%approach
+We enable onion routing to cope with probabilistic availability of nodes, informed by peer sampling and Hidden Markov Model predictions.
+
+%findings/contributions:
+We benefit from sender-receiver anonymity properties provided by onion routing.
+We show that even a relatively naive prediction model suffices to share files despite unreliable availability of individual nodes.
+The same model can potentially be applied for better informed churn handling in other p2p systems.
+In the case of TOR-like onion routing systems for anonymity, our solution allows the system to include unreliable nodes and take advantage of locality.

### 2018-04-27 paper/abstract.tex
editing in abstract

--- 2018-01-30 paper/abstract.tex
@@
 
-\dots
+%abstract
+%problem/topic
+This paper presents privacy-preserving file sharing without relying on any third-party storage such as cloud services or peers.
+
+%research gap
+Centralized file-sharing systems, i.e.,  cloud storage such as Dropbox, require trust in the service provider and can be monitored.
+Peer-to-peer (P2P) file-sharing relies on replicas on other people's machines.
+We are interested in minimizing trust needed in other systems and preserving the users' privacy in terms of data and metadata, what they share with whom and when.
+
+%why now
+Nowadays, many people use multiple devices and it has thus become possible to benefit from P2P technology for one's own devices alone and thus reducing one's exposure to security and privacy vulnerabilities and threats from third parties.
+
+%approach
+We combine onion routing with probabilistic node selection, informed by peer sampling and Hidden Markov Model predictions for node availability.
+
+%findings/contributions:
+We benefit from sender-receiver anonymity properties provided by onion routing to protect user privacy in decentralized file sharing.
+We show that even a relatively naive prediction model suffices to share files despite unreliable availability of individual nodes.
+The same model can potentially be applied for better informed churn handling in other p2p systems.
+In the case of onion routing systems for anonymity, our solution allows the system to include unreliable nodes and take advantage of locality, neither of which is currently provided in TOR.

### 2018-04-27 paper/abstract.tex
more editing

@@
 %problem/topic
-This paper presents privacy-preserving file sharing without relying on any third-party storage such as cloud services or peers.
-
+This paper presents privacy-preserving file sharing without relying on any third-party storage. 
 %research gap
-Centralized file-sharing systems, i.e.,  cloud storage such as Dropbox, require trust in the service provider and can be monitored.
+Centralized file-sharing systems, e.g.,  cloud storage services such as Dropbox, require trust in the service provider and can be monitored.
 Peer-to-peer (P2P) file-sharing relies on replicas on other people's machines.
-We are interested in minimizing trust needed in other systems and preserving the users' privacy in terms of data and metadata, what they share with whom and when.
-
+We are interested in minimizing the trust needed in other systems and preserving the users' privacy in terms of data and metadata, what they share with whom and when.
 %why now
-Nowadays, many people use multiple devices and it has thus become possible to benefit from P2P technology for one's own devices alone and thus reducing one's exposure to security and privacy vulnerabilities and threats from third parties.
-
+Nowadays, many people use multiple devices and it has thus become possible to benefit from P2P technology for one's own devices alone, thereby reducing one's exposure to security and privacy threats from third parties.
 %approach
 We combine onion routing with probabilistic node selection, informed by peer sampling and Hidden Markov Model predictions for node availability.
-
 %findings/contributions:
@@
 We show that even a relatively naive prediction model suffices to share files despite unreliable availability of individual nodes.
-The same model can potentially be applied for better informed churn handling in other p2p systems.
+The same model can potentially be applied for better-informed churn handling in other p2p systems.
 In the case of onion routing systems for anonymity, our solution allows the system to include unreliable nodes and take advantage of locality, neither of which is currently provided in TOR.

### 2018-04-28 paper/algorithm.tex
Writes up algorithm section, merges relevant parts of Adrien's old stuff

@@
 
-% \NewCryptoEntity{\Alice}{A}
-% \NewCryptoEntity{\Bob}{B}
-% \NewCryptoEntity{\Carol}{C}
-% % Arg, already used \mathcal{D} for the devices set
-% \NewCryptoEntity{\David}{D}
+Alice and Bob each has a set of devices containing their files, \eg a 
+smartphone, laptop and a desktop computer.
+Alice and Bob meet in a café carrying only their smartphones and Alice wants to 
+share a file, \(f\), with Bob.
+Alice's smartphone knows some metadata of \(f\) and that it resides on Alice's 
+desktop computer.
+She gives some metadata about \(f\) to Bob, at least the file size.
+Bob creates an onion route of low-availability devices with some subset of Bob's 
+devices as the destination.
+The layers of the route are chosen such that the probability of all devices 
+being offline at the same time is low.
+Bob gives this route to Alice.
+Alice's smartphone ensures that her desktop computer (containing the file \(f\)) 
+gets the route and the instruction to send \(f\) using this route.
+When Alice's desktop computer receives this instruction it will create the first 
+half of the route and concatenate it with Bob's route, then transfer \(f\) to 
+Bob.
+In this section we will present the details of the necessary algorithms.
 
-\newcommand{\Alice}{\ensuremath{\mathscr{A}}}
-\newcommand{\Bob}{\ensuremath{\mathscr{B}}}
+We have a set of users, \(U\), each user \(u\in U\) has a set of devices, 
+\(D_u\).
+We call \(D_u\) the device swarm of \(u\).
+Alice, \(a\in U\), has a device swarm, \(D_a\), and Bob, \(b\in U\) has a device 
+swarm, \(D_b\).
+We let \(D = \cup_{u\in U} D_u\) be the set of all devices, the global device 
+swarm.
 
-\newcommand{\localoverlay}{Squad Overlay\xspace}
+Without loss of generality, we will use Alice and Bob as examples.
+Each of Alice's (and Bob's) devices will keep track of its own online and 
+offline behaviour.
+They will use a protocol like Sprinkler~\cite{luxey:hal-01704172} to learn about 
+each other's online--offline behaviour.
+\commentDaniel{Is that correct?}
+This allows Alice's device swarm to do internal scheduling.
+
+Each device \(d\in D_a\) will also participate in the global device swarm, 
+\(D\supset D_a\).
+
+\subsection{Adrien's old stuff}
+
+\newcommand{\localoverlay}{Local Overlay\xspace}
 \newcommand{\globaloverlay}{Global Overlay\xspace}
+
+\subsection{The \localoverlay}%
+\label{local-overlay}
+
+A user's devices, \(D_i\), use the \localoverlay to:
+\begin{enumerate}
+	\item Share information about the user's behavior.
+	Devices use it to build a behavioral model and infer their future connection probability;
+  \item Share files location \commentAL{Maybe \dots}
+\end{enumerate}
+
+\subsubsection{Sharing the user's behavior}% (fold)
+\label{ssub:sharing_the_user_s_behavior}
+
+Each device initially only knows when it is connected. 
+To make a model of the user's behavior, they need to know the whole observation sequence $O$: which device is online at each time step.
+To do so, they employ a probabilistic dissemination protocol, 
+\textsc{Sprinkler}~\cite{luxey:hal-01704172}.
+This allows devices to gossip any new connection information to random peers in 
+the local swarm, ensuring that all devices know the full observation sequence 
+with a very high probability.
+\textsc{Sprinkler} has shown resilient to device churn~\cite{luxey:cascade}, and 
+is thus perfectly suited for our purpose, where a user's devices often 
+disconnect and reconnect.
+
+\commentAL{Then we \textbf{maybe} do predictions as \textbf{maybe} shown in 
+  \cref{sec:user_model}.}
+
+% subsubsection sharing_the_user_s_behavior (end)
+
+\subsubsection{Sharing files location}% (fold)
+\label{ssub:sharing_files_location}
+
+We do stuff and things work.
+
+% subsubsection sharing_files_location (end)
+
+\subsection{The \globaloverlay}%
+\label{global-overlay}
+
+Every time a device is online, it participates in the random peer sampling 
+protocol.
+If a device is sampled it provides the following information:
+\begin{itemize}
+  \item its address;
+	\item its public key;
+  \item the probability of being online.
+\end{itemize}
+
+\subsection{The file exchange}%
+\label{file-exchange}
+
+\subsubsection{File exchange process}% (fold)
+\label{ssub:file_exchange_process}
+
+Firstly, Alice and Bob must exchange information out-of-band: an encryption key $ek$ to cipher the file, and an ID $k$ in the DHT pointing to information on how to reach Alice.
+
+\subsection{Random peer sampling and predictions}
+
+\commentDaniel{%
+  We must cover how to do \(\Pr[d \text{ offline at time } t]\) as used in 
+  \cref{ExtendRoute}.
+  This is probably part of getting random peers in the same place.%
+}
+
+\commentDaniel{%
+  What is the probability distribution of the peer sample that we get?
+  Will it be close to uniformly random?%
+}
 
@@
 
-\subsection{Predictions and scheduling}
-
-\commentDaniel{%
-  We must cover how to do \(\Pr[d \text{ offline at time } t]\) as used above 
-  (\cref{ExtendRoute}).%
-}
+\subsection{Scheduling a file transfer}
 
@@
 
-\subsection{Adrien's old stuff}
-
-\commentDaniel{%
-  Anything below this line should be updated, integrated or removed.%
-}
-A set of users $\mathcal{U}$ participate in the \name network.
-Each user $u \in \mathcal{U}$ has a set $\mathcal{D}_u$ of devices that contribute to the system when online.
-Alice and Bob use \name to exchange a file secretly: no participant will learn who sends and receives it, nor its content.
-
-On one hand, a user's devices must exchange information among themselves to learn the user's behavior \commentAL{Can we skip files mapping, pretty please?} and map files to devices.
-We call this part of the protocol the \localoverlay, and present it in 
-\cref{local-overlay}. On the other hand, user's collectively upload the list of 
-their connected devices and associated future predictions to a Distributed Hash 
-Table (DHT): it serves as a registry of online peers (including connection 
-probabilities for the next turn), and for the routing of files.
-We describe this \globaloverlay in \cref{global-overlay}. File exchange between 
-two users is enabled by the two previous protocols, and is covered in 
-\cref{file-exchange}
-
-\subsection{The \localoverlay}%
-\label{local-overlay}
-
-A user's devices, \(D_i\), use the \localoverlay to:
-\begin{enumerate}
-	\item Share information about the user's behavior.
-	Devices use it to build a behavioral model and infer their future connection probability;
-  \item Share files location \commentAL{Maybe \dots}
-\end{enumerate}
-
-\subsubsection{Sharing the user's behavior}% (fold)
-\label{ssub:sharing_the_user_s_behavior}
-
-Each device initially only knows when it is connected. 
-To make a model of the user's behavior, they need to know the whole observation sequence $O$: which device is online at each time step.
-To do so, they employ a probabilistic dissemination protocol, based on previous work from our team~\cite{luxey:hal-01704172}.
-This algorithm, called \textsc{Sprinkler}, allows devices to gossip any new connection information to random peers, ensuring that all devices know the full observation sequence with a very high probability.
-\textsc{Sprinkler} has shown resilient to devices churn~\cite{luxey:cascade}, and is thus perfectly suited for our purpose, where a user's devices often disconnect and reconnect.
-
-\commentAL{Then we \textbf{maybe} do predictions as \textbf{maybe} shown in 
-  \cref{sec:user_model}.}
-
-% subsubsection sharing_the_user_s_behavior (end)
-
-\subsubsection{Sharing files location}% (fold)
-\label{ssub:sharing_files_location}
-
-We do stuff and things work.
-
-% subsubsection sharing_files_location (end)
-
-\subsection{The \globaloverlay}%
-\label{global-overlay}
-
-% All swarms participate in the Inter-Swarm Protocol to coordinate the global 
-% knowledge needed by the swarms to interact.
-% More specifically, the global knowledge contains:
-% \begin{itemize}
-%   \item A table, \(R\), of devices available for routing;
-%   \item A key--value store, \(S = \{0, 1\}^\lambda\times \{0, 1\}^*\), mapping 
-%     fixed-length strings of length \(\lambda\) to arbitrary-length strings.
-% \end{itemize}
-
-Every device in the system participates in a Distributed Hash Table (DHT) that is used for two purposes:
-\begin{enumerate}
-  \item Providing routing information to nodes during file exchange. This is 
-    discussed in-depth in \cref{file-exchange};
-	\item Listing online devices and their probability of being online next time step.
-\end{enumerate}
-
-Every time a device is online, it sends the following information to the DHT:
-\begin{itemize}
-	\item the time \commentAL{step?};
-	\item its address;
-	\item its public key;
-	\item the probability that it will still be connected next turn \commentAL{no interest in t+2 and more.}
-\end{itemize}
-
-\commentAL{Cite DHT articles and emphasize their security guarantees.}
-
-\subsection{The file exchange}%
-\label{file-exchange}
-
-We consider two users, Alice and Bob, such that Alice wants to send a file to Bob secretly.
-They want to keep the file content secret to anybody but them; \name's users should not know who sent a file to whom; and Alice and Bob want to hide their address from one another.
-
-In other words, \name must guarantee \emph{sender-receiver anonymity}.
-To achieve this, communications go through onion routes, using rendez-vous points.
-Our approach is tightly based on the Tor seminal paper~\cite{Tor}.
-
-\subsubsection{File exchange process}% (fold)
-\label{ssub:file_exchange_process}
-
-Firstly, Alice and Bob must exchange information out-of-band: an encryption key $ek$ to cipher the file, and an ID $k$ in the DHT pointing to information on how to reach Alice.
-
-The device that contains Alice's file \commentAL{I don't like that dependence on the file's location} creates routes to several Introductory Points (IP), chosen at random among connected peers.
-Alice uploads the addresses of her IP to the DHT at the position $k$.
-One of Bob's devices creates routes to several Rendez-Vous points (RV), randomly picked among peers that will be connected in the next time step.
-Bob fetches the addresses of Alice's IP from the \ac{DHT}.
-Then, he sends a packet containing the addresses of its chosen RV to Alice's IPs.
-The IP nodes forward the packet to Alice's device. 
-Alice chunks her file into pieces of a predefined size, encrypted using $ek$.
-
-Starting from the next round, Alice will send all chunks of her file to Bob's RV, that will forward it to Bob.
-Once the file is received, everybody is happy and all routes are killed.
-
-% subsubsection file_exchange_process (end)
-
-\subsubsection{Onion routes in face of churn}% (fold)
-\label{ssub:onion_routes_in_face_of_churn}
-
-An onion route between A and B consists of several servers (usually three) that serve as relays, say $r_1, r_2$ and $r_3$. 
-The route will have a fixed order: $A \rightarrow r_1 \rightarrow r_2 \rightarrow r_3 \rightarrow B$.
-Every time data travels through the onion route, it is encrypted---along with its header---with symmetric keys, such that no-one except the sender and the receiver can read its content.
-A node only knows its direct predecessor (that sent the packet) and its direct successor (whose address is the only one readable by it) on the route, such that only the creator of the route (A) knows the destination (B).
-
-Alas, when one node goes down along the way, the route has to be recreated, at least partly.
-Alice will be informed of the crash by the predecessor of the failed node with a control message, using the onion route.
-Then, she will have to select a new connected peer, and ask the predecessor of the failed node to re-establish the route using this new peer.
-This is fine in scenarii where participating servers only fail sporadically.
-But in our setup, where devices disconnection is a certainty, we need a more robust approach.
-
-We select several relays at each point of the route: $R_i=\{r_{i,j}\}$ would be 
-the \emph{set} of possibly disconnected devices that will take the 
-$i^{\text{th}}$ position in our onion route.
-In traditional onion routing, $r_1$ is the only one knowing the address of $r_2$, because it is written encrypted with its public key in the header.
-Here, every device in the $R_i$ can read the set $R_{i+1}$ in the header, because the symmetric key $sk$ used to encrypt the set $R_{i+1}$ is known to every device in $R_i$.
-The header indeed contains a version of $sk$ for each device $r_{i,j}$, encrypted with its own public key $pk_{r_{i,j}}$.
-
-In the following equation, $S(sk,\texttt{message})$ means that $\texttt{message}$ is encrypted with the symmetric key $sk$, while $P(pk, \texttt{message})$ means that $\texttt{message}$ is encrypted using the public key $pk$.
-Follows the content of the header in our version of the onion routing, considering that $R_i=\{r_{i,1}, r_{i,2}, r_{i,3}\}$, that $pk_{r_{i,j}}$ is $r_{i,j}$'s public key, and that $||$ means concatenation:
-\[
-  P(pk_{r_{i,1}}, sk) || P(pk_{r_{i,2}}, sk) || P(pk_{r_{i,3}}, sk) || S(sk, 
-  R_{i+1})
-\]
-
-(I read that this is how PGP handles multiple recipients.)
+\endinput
 

### 2018-04-28 paper/building-blocks.tex

@@
 
-\((\vk, C, \sigma)\gets \DeBEenc[\mpk, m, S]\):
+\((\vk, C, \sigma)\gets \DeBEenc[\mpk, S, m]\):
 takes a message \(m\) and a recipient set \(S\), it then encrypts the message 
@@
 
-      \Function{$\DeBEenc$}{$\mpk, m, S$}
+      \Function{$\DeBEenc$}{$\mpk, S, m$}
         \State $(\ssk, \vk)\gets \Sign[Keygen]$

### 2018-04-28 code/file_exchange/config.py
experiments

@@ -5,21 +5,22 @@ from datetime import timedelta
 EXPERIMENT_NAME = 'default'
 default = {
     'ack_size': 0,  # kB
-    'bandwidth': 400,  # kB/s
-    'chunk_max_size': 128,  # kB, will depend on header size later
-    'file_size': 10240,  # kB
+    'bandwidth': 128,  # kB/s
+    'chunk_max_size': 512,  # kB, will depend on header size later
+    'do_monitor': True,
+    'experiment_id': 0,
+    'experiment_name': EXPERIMENT_NAME,
     'gossip_size': 20,
     'header_size': 100,  # kB, will depend on #devices/layers later
     'layer_threshold': 0.001,
+    'min_file_size': 51200,  # kB
+    'max_file_size': 51200,  # kB
     'minimum_node_availability': 0,
-    'experiment_name': EXPERIMENT_NAME,
-    'output_dir': 'data/'+EXPERIMENT_NAME+'/',
-    'do_monitor': True,
-    'n_file_chunks': 10,
+    'n_file_exchanges': 10,
     'n_layers': 3,  # must be odd
     'n_rounds': 2,
     'n_users': 20,
-    'n_file_exchanges': 10,
+    'output_dir': 'data/'+EXPERIMENT_NAME+'/',
     'period': timedelta(seconds=1),  # don't put milliseconds!
     'ping_time': 0.1,  # s
     'send_strategy': 'random',  # 'random' or 'random_connected'

### 2018-04-28 code/file_exchange/device.py

@@ -12,9 +12,9 @@ import time
 # import random
 
 ADDR_SIZE = 12
-MONITOR_COLUMNS = ['t', 'addr', 'owner', 'current_round',
-                   'file_id', 'chunk_id', 'mess_id', 'type',
-                   'sent', 'received', 'forwarded', 'success',
+MONITOR_COLUMNS = ['t', 'experiment_id', 'addr', 'owner',
+                   'current_round', 'file_id', 'chunk_id', 'mess_id',
+                   'type', 'sent', 'received', 'forwarded', 'success',
                    'messages_in_queue']
 
 
@@ -57,15 +57,11 @@ class Device(gevent.Greenlet):
             # online.wait(0.1) return True only if online has been set
             while not self.online.wait(0.1):
                 # Kill the device if death requested
-                if self.death_requested and self.all_files_sent and \
-                        self.message_queue.empty():
-                    # if self.death_requested:
+                if self.should_die():
                     break
 
             # Kill the device if death requested
-            if self.death_requested and self.all_files_sent and \
-                    self.message_queue.empty():
-                # if self.death_requested:
+            if self.should_die():
                 break
 
             # Send file chunks I am currently sharing
@@ -138,6 +134,11 @@ class Device(gevent.Greenlet):
     def please_die(self):
         self.death_requested = True
 
+    def should_die(self):
+        return self.death_requested
+        # return self.death_requested and self.all_files_sent and \
+        #             self.message_queue.empty()
+
     # Called from the user's greenlet
     def update_state(self, is_online, p):
         # Set Event according to is_online
@@ -155,28 +156,7 @@ class Device(gevent.Greenlet):
                 p
             )
 
-    def init_file_send(self, H_rdv_forward, H_rdv_backward, f):
-        self.lock.acquire()
-        # route = L_i + ... + L_j
-        route = self.build_route("sender")
-        # forward_route = (L_i + ... + L_j) + (L_RV + L_k + ... + L_l + L_B)
-        forward_route = route + H_rdv_forward
-        # backward_route = (L_l + ... + L_k + L_RV) + (L_j + ... + L_i) + L_A
-        backward_route = H_rdv_backward + \
-            route[::-1] + [self.owner.get_all_devices_addr()]
-
-        print("Device {} (owned by {}) will send file {}".format(
-            self.addr, self.owner.name, f.id))
-
-        self.sending_files[f.id] = {
[…]

### 2018-04-28 code/file_exchange/file.py

@@ -3,6 +3,7 @@
 from copy import deepcopy
 import numpy as np
 from .utils import random_string
+import random
 
 
 FILE_ID_SIZE = 6
@@ -10,14 +11,16 @@ FILE_ID_SIZE = 6
 
 # We use this class to represent files to share and files to receive
 class File:
-    def __init__(self, size, chunk_max_size):
+    def __init__(self, conf):
         self.id = random_string(FILE_ID_SIZE)
-        self.size = size
+        self.size = random.randint(
+            conf['min_file_size'], conf['max_file_size'])
 
         # Computing size of chunks
         self.chunks_size = []
+        size = self.size
         while size > 0:
-            chunk_size = min(size, chunk_max_size)
+            chunk_size = min(size, conf['chunk_max_size'])
             size -= chunk_size
             self.chunks_size.append(chunk_size)
 

### 2018-04-28 code/file_exchange/model.py

@@ -255,12 +255,12 @@ def get_random():
             p = 0.6 + 0.4 * np.random.sample(n_states)
         elif device_type == 'portable':
             # Portable is more or less available with varying probability
-            p = 0.1 + 0.7 * np.random.sample(n_states)
+            p = 0.2 + 0.6 * np.random.sample(n_states)
         elif device_type == 'fixed':
             # Fixed is only available in one place ...
             p = np.zeros(n_states, dtype=np.float64)
             # ... with 0.4 to 1 probability
-            p[random.choice([0, 2])] = 0.2 + 0.8 * np.random.sample()
+            p[random.choice([0, 2])] = 0.4 + 0.4 * np.random.sample()
         elif device_type == 'server':
             # Server has high availability regardless of the user's location
             p = [0.9 + 0.1 * np.random.sample()] * n_states

### 2018-04-28 code/file_exchange/user.py

@@ -5,7 +5,7 @@ import gevent
 import random
 import time
 
-MONITOR_COLUMNS = ['t', 'user', 'current_round']
+MONITOR_COLUMNS = ['t', 'experiment_id', 'user', 'current_round']
 
 
 class User(gevent.Greenlet):
@@ -28,6 +28,7 @@ class User(gevent.Greenlet):
 
         self.conf = conf
         self.current_round = None
+        self.death_requested = False
         self.monitor = monitor.Monitor(
             MONITOR_COLUMNS,
             conf['output_dir'],
@@ -49,25 +50,32 @@ class User(gevent.Greenlet):
         for d in self.devices:
             d.start()
 
-        while self.current_round is None or \
-                self.current_round < self.conf['n_rounds'] - 1:
+        while (not self.death_requested) and \
+            (self.current_round is None or
+             self.current_round < self.conf['n_rounds'] - 1):
             t_start = time.perf_counter()
             self.update_state()
 
             # Sleep until next round
+
             gevent.sleep(self.conf['period'].total_seconds() -
                          (time.perf_counter() - t_start))
 
-            # print("User {}: round #{}/{} in {:.2f}s".format(
+            # print("User {}: round #{}/{} in {:.2f}s (die={})".format(
             #     self.name, self.current_round+1,
-            #     self.conf['n_rounds'], time.perf_counter() - t_start))
+            #     self.conf['n_rounds'], time.perf_counter() - t_start,
+            #     self.death_requested))
 
         self.monitor.save()
 
         for d in self.devices:
             d.please_die()
+
         gevent.joinall(self.devices)
-        print("User {} is done".format(self.name))
+        print("User {} is done.".format(self.name))
+
+    def please_die(self):
+        self.death_requested = True
 
     def update_state(self):
         self.lock.acquire()
@@ -83,6 +91,7 @@ class User(gevent.Greenlet):
 
         self.monitor.put([
             time.perf_counter(),
+            self.conf['experiment_id'],
             self.name,
             self.current_round
         ])
@@ -111,7 +120,7 @@ class User(gevent.Greenlet):
             self.lock.release()
             raise Exception("No online devices")
 
-        f = file.File(self.conf['file_size'], self.conf['chunk_max_size'])
+        f = file.File(self.conf)
 
         # route = L_RV + L_k + ... + L_l
         try:
@@ -125,8 +134,13 @@ class User(gevent.Greenlet):
         H_rdv_backward = route[::-1]
 
[…]

### 2018-04-28 code/file_exchange/utils.py

@@ -7,7 +7,7 @@ import gevent
 
 
 NAMES = ['Cristy', 'Vickey', 'Sherie', 'Delilah', 'Rick', 'Denver', 'Stephany',
-         'Many', 'Sandie', 'Deneen', 'Jesica', 'Newton', 'Maxwell', 'Morty',
+         'Many', 'Sandie', 'Daniel', 'Jessica', 'Newton', 'Maxwell', 'Morty',
          'Beatriz', 'Georgene', 'Herma', 'Mi', 'Bobbi', 'Julianna', 'Reita',
          'Kandi', 'Karlene', 'Lila', 'Nelly', 'Sibyl', 'Kermit', 'Luke',
          'Annabel', 'Moira', 'Hassie', 'Gilda', 'Vicki', 'Gloria', 'Kaci',
@@ -16,8 +16,8 @@ NAMES = ['Cristy', 'Vickey', 'Sherie', 'Delilah', 'Rick', 'Denver', 'Stephany',
          'Norene', 'Toshiko', 'Maurita', 'Angelika', 'Ann', 'Bennie',
          'Randolph', 'Temika', 'Evelyne', 'Betty', 'Athena', 'Shawnda',
          'Magdalen', 'Benjamin', 'Lorine', 'Morgan', 'Tim', 'Elinor', 'Cordia',
-         'Jay Z', 'Brian', 'Broderick', 'Janise', 'Nadia', 'Delaine', 'Vonnie',
-         'Adaline', 'Leigh', 'Consuelo', 'Janetta', 'Isaura', 'Elvera', 'Jack',
+         'Jay Z', 'Brian', 'Broderick', 'Janis', 'Nadia', 'Delaine', 'Vonnie',
+         'Adaline', 'Leigh', 'Consuelo', 'Patty', 'Isaura', 'Elvera', 'Jack',
          'Cristina', 'Charissa', 'Kaylee', 'Britany', 'Jayne', 'Yuriko',
          'Annelle', 'Twila', 'January', 'Jillian', 'Jean Panda', 'Daisy', 'Mazie',
          'Bronwyn', 'Otha', 'Shane', 'Brande', 'Renna']

### 2018-04-28 paper/algorithm.tex
Adapts algorithm to building blocks
Incorporated Adrien's old stuff further, disposition

@@
 swarm.
+Without loss of generality, we will use Alice, with device swarm \(D_a\), and 
+Bob, with device swarm \(D_b\), as examples.
 
-Without loss of generality, we will use Alice and Bob as examples.
+\subsection{The local swarm}%
+\label{local-overlay}
+
 Each of Alice's (and Bob's) devices will keep track of its own online and 
@@
 \commentDaniel{Is that correct?}
-This allows Alice's device swarm to do internal scheduling.
-
-Each device \(d\in D_a\) will also participate in the global device swarm, 
-\(D\supset D_a\).
-
-\subsection{Adrien's old stuff}
-
-\newcommand{\localoverlay}{Local Overlay\xspace}
-\newcommand{\globaloverlay}{Global Overlay\xspace}
-
-\subsection{The \localoverlay}%
-\label{local-overlay}
-
-A user's devices, \(D_i\), use the \localoverlay to:
-\begin{enumerate}
-	\item Share information about the user's behavior.
-	Devices use it to build a behavioral model and infer their future connection probability;
-  \item Share files location \commentAL{Maybe \dots}
-\end{enumerate}
+This allows Alice's device swarm to infer a behavioural model for the device 
+swarm and do internal scheduling based on the probability of being online.
 
@@
 
-\subsection{The \globaloverlay}%
-\label{global-overlay}
-
-Every time a device is online, it participates in the random peer sampling 
-protocol.
-If a device is sampled it provides the following information:
-\begin{itemize}
-  \item its address;
-	\item its public key;
-  \item the probability of being online.
-\end{itemize}
-
-\subsection{The file exchange}%
-\label{file-exchange}
-
-\subsubsection{File exchange process}% (fold)
-\label{ssub:file_exchange_process}
-
-Firstly, Alice and Bob must exchange information out-of-band: an encryption key $ek$ to cipher the file, and an ID $k$ in the DHT pointing to information on how to reach Alice.
-
 \subsection{Random peer sampling and predictions}
@@
 }
+
+\NewAlgorithm{\GetRandomPeer}{GetRandomPeer}
+
+Every time a device is online, it participates in the random peer sampling 
+protocol.
+If a device is sampled it provides the following information:
+\begin{itemize}
+  \item its address;
+	\item its public key;
+  \item the probability of being online.
+\end{itemize}
 
@@
 \NewAlgorithm{\GetRouteNode}{GetRouteNode}
-\NewAlgorithm{\GetRandomPeer}{GetRandomPeer}
-
-\NewAlgorithm{\Enc}{Enc}
-\NewVariable{\pk}{pk}
 
@@
       \State $D\gets \GetRouteNode[\theta]$
-      \State $H\gets D\concat \Enc[_{\pk_{D}}][H]$
+      \State $H\gets D\concat \DeBEenc[\mpk, D, H]$
       \State \Return $\ExtendRoute[H, L-1, \theta]$
@@
     \Function{\GetRouteNode}{$\theta$}
-      \State $D\gets \GetRandomPeer$
+      \State $d\gets \GetRandomPeer$
+      \State $D\gets \{d\}$
       \While{$\prod_{d\in D} \Pr[d \text{ offline at time } t] > \theta$}
-        \State $D\gets D\cup \GetRandomPeer$
+        \State $d\gets \GetRandomPeer$
+        \State $D\gets D\cup \{d\}$
       \EndWhile
@@
     \Function{\Store}{$c_m$}
-      \State $m\gets \Dec[_{\sk_D}][c_m]$
+      \State $m\gets \DeBEdec[\mpk, \sk, c_m]$
       \If{$m = \bot$}
@@
     }
-    \Function{\SPOR[\Send]}{$m, \pk_D, H_\rdv$}
+    \Function{\SPOR[\Send]}{$\mpk, D, H_\rdv, m$}
       \State $H\gets \ExtendRoute[H_\rdv, L, \theta]$
-      \State $c_m\gets \Enc[_{\pk_D}][m]$
+      \State $c_m\gets \DeBEenc[\mpk, D, m]$
       \State $D\concat C_H\gets H_\rdv$
@@
     \Function{\SPOR[\Fwd]}{$C_H, c_m$}
-      \State $H\gets \Dec[_\sk][C_H]$
+      \State $H\gets \DeBEdec[\mpk, \sk, C_H]$
       \If{$H = \bot$}
@@
 
-\endinput
+\subsection{The file exchange}%
+\label{file-exchange}
 
-% subsubsection onion_routes_in_face_of_churn (end)
+\subsubsection{File exchange process}% (fold)
+\label{ssub:file_exchange_process}
 
-% \begin{figure}[t]
-% \centering
-% \includegraphics[width=0.8\columnwidth]{figures/schema.pdf}
-% \caption{\label{fig:pipeline}Pipeline of the steps undergone by Alice when he shares a file from his laptop L with Bob.}
-% \end{figure}
-
-% \Cref{fig:pipeline} depicts the process of a file exchange from Alice to Bob.
-% The file $f$ is initially located on Alice's laptop $L$, which is potentially offline for now.
-% Firstly, Alice and Bob need to exchange encryption keys and the key $ID_f$ 
-% referencing the file on the \ac{DHT}.
-% They do so \emph{out-of-band}, that is using another channel than the one 
-% presented here (\eg bluetooth, email, \etc).
-
-% Then, Alice queries the DHT for devices that will most likely be online at the same time as his laptop $L$.
-% To this end, Alice uses his knowledge on his devices connection patterns $A_i$, along with the DHT's public information on devices connections.
-% Once Alice and the DHT agreed upon a set of peers $(M_1, M_2, M_3)$, their address is put in the DHT at the key $ID_f$ referencing the file of interest.
-
-% At the third step, Alice's laptop $L$ becomes available. 
-% Informed of the ongoing file exchange by Alice's Device Swarm Protocol, $L$ fetches the addresses of $M_1, M_2$ and $M_3$ on the DHT using the key $ID_f$.
-% These peers will serve as middle-men: $L$ sends them redundant chunks of $f$ through an onion route (thus remaining anonymous), for Bob to fetch them later.
-
-% In the last forth step, Bob fetches the file $f$ using any of her devices.
-% To do so, she uses the key $ID_f$ to learn the addresses of $M_1, M_2$ and $M_3$.
-% Then, she fetches parts of $f$ from the online middle-men through an onion route.
-% Given that $L$ sent redundant chunks to the middle-men, Bob will not need every middle-man to be connected to fetch the whole file.
-% Once Bob has completed the download, the key $ID_f$ is flushed on the DHT.
+Firstly, Alice and Bob must exchange information out-of-band: an encryption key $ek$ to cipher the file, and an ID $k$ in the DHT pointing to information on how to reach Alice.

### 2018-04-28 paper/algorithm.tex
Renames \GetRouteNode to \CreateOnionLayer
Clarifies data needed from random peers
Changes local-overlay label to local-swarm

@@
 
-\subsection{The local swarm}%
-\label{local-overlay}
+\subsection{Alice's device swarm}%
+\label{local-swarm}
 
@@
 
-\subsection{Random peer sampling and predictions}
+\subsection{The global device swarm and random peer sampling}
 
@@
 \begin{itemize}
-  \item its address;
-	\item its public key;
-  \item the probability of being online.
+  \item its address, \(d\);
+  \item its public key, \(\pk_d\);
+  \item the probability of being online, \(p_d\).
 \end{itemize}
+We will denote this by the following algorithm \((d, \pk_d, p_d)\gets 
+  \GetRandomPeer\), which will be used below.
+The probability of being online, \(p_d\), is inferred as above 
+(\cref{local-swarm}).
 
@@
 
-\subsection{\(\SPOR\): Stateless Predictive Onion Routing}
+\subsection{\(\SPOR\): Stateless Predictive Onion Routing}%
+\label{SPOR}
 
@@
 \NewAlgorithm{\ExtendRoute}{ExtendRoute}
-\NewAlgorithm{\GetRouteNode}{GetRouteNode}
+\NewAlgorithm{\CreateOnionLayer}{CreateOnionLayer}
 
@@
       \EndIf
-      \State $D\gets \GetRouteNode[\theta]$
+      \State $D\gets \CreateOnionLayer[\theta]$
       \State $H\gets D\concat \DeBEenc[\mpk, D, H]$
@@
 
-    \Function{\GetRouteNode}{$\theta$}
-      \State $d\gets \GetRandomPeer$
+    \Function{\CreateOnionLayer}{$\theta$}
+      \State $(d, \pk_d, p_d)\gets \GetRandomPeer$
+      \Comment We use \(d\) as shorthand for this tuple.
       \State $D\gets \{d\}$
-      \While{$\prod_{d\in D} \Pr[d \text{ offline at time } t] > \theta$}
+      \While{$\prod_{d\in D} p_d > \theta$}
         \State $d\gets \GetRandomPeer$
@@
 
-    \Function{\Store}{$c_m$}
+    \Function{\Store}{$m$}
       \State $m\gets \DeBEdec[\mpk, \sk, c_m]$
@@
       $m$ is the message to be sent,
-      $\pk_D$ is the public-key of the recipient,
       $H_\rdv$ is the onion-route given by the recipient.
     }
-    \Function{\SPOR[\Send]}{$\mpk, D, H_\rdv, m$}
+    \Function{\SPOR[\Send]}{$H_\rdv, m$}
       \State $H\gets \ExtendRoute[H_\rdv, L, \theta]$
-      \State $c_m\gets \DeBEenc[\mpk, D, m]$
       \State $D\concat C_H\gets H_\rdv$
@@
         \Comment{Uniformly randomly chosen}
-        \If{$d\method \Fwd[C_H, c_m] \neq \bot$}
+        \If{$d\method \Fwd[C_H, m] \neq \bot$}
           \State \Return $\top$
@@
     recipient.
-    \(\pk_D\) is the public key of the recipient.
   }
@@
     \Require{$\pk, \sk$ is the public--private key-pair of the node.}
-    \Function{\SPOR[\Fwd]}{$C_H, c_m$}
+    \Function{\SPOR[\Fwd]}{$C_H, m$}
       \State $H\gets \DeBEdec[\mpk, \sk, C_H]$
@@
       \If{$C_H' = \top$}
-        \State \Return $\Store[c_m]$
+        \State \Return $\Store[m]$
       \EndIf
@@
         \Comment{Uniformly randomly chosen}
-        \If{$d\method \Fwd[C_H', c_m] \neq \bot$}
+        \If{$d\method \Fwd[C_H', m] \neq \bot$}
           \State \Return $\top$
@@
   \caption{\label{SPORFwd}%
-    The \(\SPOR[\Fwd]\) algorithm forwards \(c_m\) down the route \(H\), 
-    obtained by decrypting \(C_H\) with the node's associated private key.%
+    The \(\SPOR[\Fwd]\) algorithm forwards \(m\) down the route \(H\), obtained 
+    by decrypting \(C_H\) with the node's associated private key.
     The special value \(H = \top\) indicated the end of the route, thus \(c_m\) 
@@
 
-\subsection{Scheduling a file transfer}
+\subsection{Scheduling and transferring a file}%
+\label{file-transfer}
 
@@
 
-\subsection{The file exchange}%
-\label{file-exchange}
+We are interested in transferring large files.
+Every device \(d\in D\) in the global device swarm is only periodically online.
+We will thus divide the data to send into \(n\) smaller chunks (similar to 
+BitTorrent~\cite{BitTorrent}).
+The idea is to choose \(n\) such that each chunk will be small enough to be 
+successfully relayed by a device before it goes offline again.
+The chunk size is empirically determined in \cref{Performance}.
+\commentDaniel{Adrien, is that true?}
 
-\subsubsection{File exchange process}% (fold)
-\label{ssub:file_exchange_process}
-
-Firstly, Alice and Bob must exchange information out-of-band: an encryption key $ek$ to cipher the file, and an ID $k$ in the DHT pointing to information on how to reach Alice.
+As stated above, Alice and Bob exchange some limited data out-of-bound using 
+their smartphones.
+The information they will exchange is the following:
+\begin{enumerate}
+  \item Bob creates an onion route header, \(H_\rdv\), by running 
+    \(\SPOR[\Recv]\) (\cref{SPORRecv}) and gives it to Alice.
+  \item Alice gives Bob number of file chunks, \(n\), and the size of the file 
+    chunks.
+  \item They agree on a file-specific key \(k\) for some (authenticated) 
+    encryption scheme \(\Enc*\).
+\end{enumerate}
+Then Alice encrypts the file \(f\) and receives the ciphertext \(c_f\gets 
+  \Enc*[Enc](k, f)\).
+She then divides \(c_f\) into \(n\) chunks, \(c_f^{(1)}, \dotsc, c_f^{(n)}\), 
+and runs \(\SPOR[\Send](H_\rdv, c_f^{(i)})\) for all \(1\leq i\leq n\) in 
+parallel.
+\commentDaniel{Or shall we do it sequentially?}

### 2018-04-28 paper/algorithm.tex
Removes no-longer-needed comment
Updates some comments

@@
 \commentDaniel{%
-  We must cover how to do \(\Pr[d \text{ offline at time } t]\) as used in 
-  \cref{ExtendRoute}.
-  This is probably part of getting random peers in the same place.%
+  We must cover above how to compute \(p_d\) below, \ie the probability of being 
+  online.
+  We need this for \cref{ExtendRoute}.%
 }
@@
   What is the probability distribution of the peer sample that we get?
-  Will it be close to uniformly random?%
+  Will it be close to uniformly random?
+  I need this for the security analysis.%
 }
@@
 
-\commentDaniel{%
-  We must do the scheduling: \ie divide the file \(f\) into \(f_1, \dotsc, f_n\) 
-  and how the size of \(f_i\) relates to transmission time and size of the 
-  timeslot (for the validity of predictions).
-  After that we just do \(\SPOR[\Send]\) on each \(f_i\).%
-}
-
 We are interested in transferring large files.

### 2018-04-28 paper/security-analysis.tex
Adds things to cover in security analysis

@@
 \dots
+
+The message \(m\) remains the same from hop to hop during the onion routing, 
+hence a global observer can track the message through the network.
+
+We can choose different properties for \(\Enc*\).
+What makes sense is to choose an authenticated encryption 
+scheme~\cite{AuthEncryption}.
+We could also choose a deniable encryption scheme~\cite{DeniableEncryption}, \eg 
+the one by \textcite{OTPKX} which is both deniable and authenticated and 
+provides \ac{DEN-SS}.

### 2018-04-28 paper/file-exchange.tex
added files...

\subsection{The file exchange}

\commentDaniel{%
  We must do the scheduling: \ie divide the file \(f\) into \(f_1, \dotsc, f_n\) 
  and how the size of \(f_i\) relates to transmission time and size of the 
  timeslot (for the validity of predictions).
  After that we just do \(\SPOR[\Send]\) on each \(f_i\).%
}

\subsubsection{File exchange process}% (fold)
\label{ssub:file_exchange_process}

Firstly, Alice and Bob must exchange information out-of-band: an encryption key $ek$ to cipher the file, and an ID $k$ in the DHT pointing to information on how to reach Alice.

### 2018-04-28 paper/global-overlay-design.tex
added files...

--- 2018-04-28 paper/algorithm.tex
@@
-\section{Algorithm}%
-\label{Algorithm}
-
-Alice and Bob each has a set of devices containing their files, \eg a 
-smartphone, laptop and a desktop computer.
-Alice and Bob meet in a café carrying only their smartphones and Alice wants to 
-share a file, \(f\), with Bob.
-Alice's smartphone knows some metadata of \(f\) and that it resides on Alice's 
-desktop computer.
-She gives some metadata about \(f\) to Bob, at least the file size.
-Bob creates an onion route of low-availability devices with some subset of Bob's 
-devices as the destination.
-The layers of the route are chosen such that the probability of all devices 
-being offline at the same time is low.
-Bob gives this route to Alice.
-Alice's smartphone ensures that her desktop computer (containing the file \(f\)) 
-gets the route and the instruction to send \(f\) using this route.
-When Alice's desktop computer receives this instruction it will create the first 
-half of the route and concatenate it with Bob's route, then transfer \(f\) to 
-Bob.
-In this section we will present the details of the necessary algorithms.
-
-We have a set of users, \(U\), each user \(u\in U\) has a set of devices, 
-\(D_u\).
-We call \(D_u\) the device swarm of \(u\).
-Alice, \(a\in U\), has a device swarm, \(D_a\), and Bob, \(b\in U\) has a device 
-swarm, \(D_b\).
-We let \(D = \cup_{u\in U} D_u\) be the set of all devices, the global device 
-swarm.
-Without loss of generality, we will use Alice, with device swarm \(D_a\), and 
-Bob, with device swarm \(D_b\), as examples.
-
-\subsection{The local swarm}%
-\label{local-overlay}
-
-Each of Alice's (and Bob's) devices will keep track of its own online and 
-offline behaviour.
-They will use a protocol like Sprinkler~\cite{luxey:hal-01704172} to learn about 
-each other's online--offline behaviour.
-\commentDaniel{Is that correct?}
-This allows Alice's device swarm to infer a behavioural model for the device 
-swarm and do internal scheduling based on the probability of being online.
-
-\subsubsection{Sharing the user's behavior}% (fold)
-\label{ssub:sharing_the_user_s_behavior}
-
-Each device initially only knows when it is connected. 
-To make a model of the user's behavior, they need to know the whole observation sequence $O$: which device is online at each time step.
-To do so, they employ a probabilistic dissemination protocol, 
-\textsc{Sprinkler}~\cite{luxey:hal-01704172}.
-This allows devices to gossip any new connection information to random peers in 
-the local swarm, ensuring that all devices know the full observation sequence 
-with a very high probability.
-\textsc{Sprinkler} has shown resilient to device churn~\cite{luxey:cascade}, and 
-is thus perfectly suited for our purpose, where a user's devices often 
-disconnect and reconnect.
-
-\commentAL{Then we \textbf{maybe} do predictions as \textbf{maybe} shown in 
-  \cref{sec:user_model}.}
-
-% subsubsection sharing_the_user_s_behavior (end)
-
-\subsubsection{Sharing files location}% (fold)
-\label{ssub:sharing_files_location}
-
-We do stuff and things work.
-
-% subsubsection sharing_files_location (end)
-
-\subsection{Random peer sampling and predictions}
+\subsection{The Global overlay}
 
@@
 \end{itemize}
-
-\NewScheme{\SPOR}{SPOR}
-
-\subsection{\(\SPOR\): Stateless Predictive Onion Routing}
-
-\NewAlgorithm{\Send}{Send}
-\NewAlgorithm{\Fwd}{Forward}
-\NewAlgorithm{\Recv}{Receive}
-\NewVariable{\rdv}{rdv}
-
-We have the Stateless Predictive Onion Routing scheme, \SPOR, which provides 
-probabilistically onion-routed message passing.
-Instead of providing only one address per hop in the route (as in \eg 
-Tor~\cite{Tor}), \(\SPOR\) provides several alternatives for the next hop 
-depending on their probability of being online.
-To do this, \(\SPOR\) provides stateless algorithms for the onion-routing.
-
-\(\SPOR\) provides three algorithms: \(\SPOR[\Send]\) (\cref{SPORSend}), 
-\(\SPOR[\Fwd]\) (\cref{SPORFwd}) and \(\SPOR[\Recv]\) (\cref{SPORRecv}).
-Say Alice wants to send a message \(m\) to Bob.
-Bob uses \(\SPOR[\Recv]\) to create a probabilistic onion route \(H_\rdv\) from 
-a rendez-vous point to his own device swarm --- all the hops on the route are 
-chosen by Bob uniformly at random.
-Bob gives \(H_\rdv\) to Alice using an out-of-band channel, \eg using his phone.
-Alice uses \(\SPOR[\Send]\) at some later time to send the message to Bob using 
-any of her devices.
-\(\SPOR[\Send]\) extends the route \(H_\rdv\) with some hops of Alice's choosing 
-(uniformly randomly chosen), then starts to forward the message (using 
-\(\SPOR[\Fwd]\)) through the hops on the route to Bob.
-This process is illustrated in \cref{fig:file-exchange}.
-
-\begin{figure}
-  \includegraphics[width=\linewidth]{figures/file_exchange.pdf}
-  \caption{\label{fig:file-exchange}%
-    A schematic of Alice and Bob sending a message using \(\SPOR\).
-  }
-\end{figure}
-
-\NewAlgorithm{\ExtendRoute}{ExtendRoute}
-\NewAlgorithm{\GetRouteNode}{GetRouteNode}
-
-\begin{figure}
-  \begin{algorithmic}
-    \Require{%
-      $H$ is a header of the form \(D\concat H'\) or \(D\concat \top\), where 
-      \(D\) is a set of device addresses.
-      $\pk_D$ is the public key of device set $D$.
-      $L$ is the length of the route,
-      $\theta$ is the threshold of probability of failure.%
-    }
-    \Function{\ExtendRoute}{$H, L, \theta$}
-      \If{$L\leq 0$}
-        \State \Return $H$
-      \EndIf
-      \State $D\gets \GetRouteNode[\theta]$
-      \State $H\gets D\concat \DeBEenc[\mpk, D, H]$
-      \State \Return $\ExtendRoute[H, L-1, \theta]$
-    \EndFunction
-
-    \Function{\GetRouteNode}{$\theta$}
-      \State $d\gets \GetRandomPeer$
-      \State $D\gets \{d\}$
-      \While{$\prod_{d\in D} \Pr[d \text{ offline at time } t] > \theta$}
-        \State $d\gets \GetRandomPeer$
-        \State $D\gets D\cup \{d\}$
-      \EndWhile
-      \State \Return $D$
-    \EndFunction
-  \end{algorithmic}
-  \caption{\label{ExtendRoute}%
-    The \(\ExtendRoute\) algorithm extends a route \(H\) with \(L\) hops and 
-    failure threshold of \(\theta\) for each hop in the route.
-    Thus the probability of failure for the extension is \(1 - (1 - \theta)^L\).
-    The function \(\GetRandomPeer\) is any random peer-sampling algorithm.
-  }
-\end{figure}
-
-\NewAlgorithm{\Store}{Store}
-\NewAlgorithm{\Dec}{Dec}
-\NewVariable{\sk}{sk}
-
-\begin{figure}
-  \begin{algorithmic}
-    \Require{%
-      $D$ is the set of alternative recipient devices.
-    }
-    \Function{\SPOR[\Recv]}{$D$}
-      \State $H_\rdv\gets \ExtendRoute[D\concat \top, L, \theta]$
-      \State \Return $H_\rdv$
-        \Comment{Give to sender out-of-bound.}
-    \EndFunction
-
-    \Function{\Store}{$c_m$}
-      \State $m\gets \DeBEdec[\mpk, \sk, c_m]$
-      \If{$m = \bot$}
-        \State \Return $\bot$
-      \EndIf
-      \State Store $m$ to disk.
-      \State \Return $\top$
-    \EndFunction
-  \end{algorithmic}
-  \caption{\label{SPORRecv}%
-    The \(\SPOR[\Recv]\) algorithm prepares the recipient for receiving a file.
-    It creates a probabilistic onion-route from a rendez-vous point to its own 
-    devices and returns the route to the sender.
-    The \(\Store\) algorithm is used by the local \(\SPOR[\Fwd]\) algorithm to 
-    store messages intended for itself.
-  }
-\end{figure}
-
-\begin{figure}
-  \begin{algorithmic}
-    \Require{%
-      $m$ is the message to be sent,
-      $\pk_D$ is the public-key of the recipient,
-      $H_\rdv$ is the onion-route given by the recipient.
-    }
-    \Function{\SPOR[\Send]}{$\mpk, D, H_\rdv, m$}
-      \State $H\gets \ExtendRoute[H_\rdv, L, \theta]$
-      \State $c_m\gets \DeBEenc[\mpk, D, m]$
-      \State $D\concat C_H\gets H_\rdv$
-      \For{$d\in D$}
-        \Comment{Uniformly randomly chosen}
-        \If{$d\method \Fwd[C_H, c_m] \neq \bot$}
-          \State \Return $\top$
-        \EndIf
-      \EndFor
-      \State \Return $\bot$
-    \EndFunction
-  \end{algorithmic}
-  \caption{\label{SPORSend}%
-    The \(\SPOR[\Send]\) algorithm extends the route \(H_\rdv\) (using 
-    \(\ExtendRoute\), \cref{ExtendRoute}) and sends the message \(m\) down the 
-    extended route using the \(\SPOR[\Fwd]\) algorithm (\cref{SPORFwd}).
-    The first node of \(H_\rdv\) is the rendez-vous point selected by the 
-    recipient.
-    \(\pk_D\) is the public key of the recipient.
-  }
-\end{figure}
-
-\begin{figure}
-  \begin{algorithmic}
-    \Require{$\pk, \sk$ is the public--private key-pair of the node.}
-    \Function{\SPOR[\Fwd]}{$C_H, c_m$}
-      \State $H\gets \DeBEdec[\mpk, \sk, C_H]$
-      \If{$H = \bot$}
-        \State \Return $\bot$
-      \EndIf
-      \State $\{d_i\}\concat C_H'\gets H$
-      \If{$C_H' = \top$}
-        \State \Return $\Store[c_m]$
-      \EndIf
-      \For{$d\in \{d_i\}$}
-        \Comment{Uniformly randomly chosen}
-        \If{$d\method \Fwd[C_H', c_m] \neq \bot$}
-          \State \Return $\top$
-        \EndIf
-      \EndFor
-      \State \Return $\bot$
-    \EndFunction
-  \end{algorithmic}
-  \caption{\label{SPORFwd}%
-    The \(\SPOR[\Fwd]\) algorithm forwards \(c_m\) down the route \(H\), 
-    obtained by decrypting \(C_H\) with the node's associated private key.%
-    The special value \(H = \top\) indicated the end of the route, thus \(c_m\) 
-    is intended for the local node and \(c_m\) is instead sent to disk using 
-    \(\Store\) (\cref{SPORRecv}).%
-  }
-\end{figure}
-
-\subsection{Scheduling a file transfer}
-
-\commentDaniel{%
-  We must do the scheduling: \ie divide the file \(f\) into \(f_1, \dotsc, f_n\) 
-  and how the size of \(f_i\) relates to transmission time and size of the 
-  timeslot (for the validity of predictions).
-  After that we just do \(\SPOR[\Send]\) on each \(f_i\).%
-}
-
-\subsection{The file exchange}%
-\label{file-exchange}
-
-\subsubsection{File exchange process}% (fold)
-\label{ssub:file_exchange_process}
-
-Firstly, Alice and Bob must exchange information out-of-band: an encryption key $ek$ to cipher the file, and an ID $k$ in the DHT pointing to information on how to reach Alice.

### 2018-04-28 paper/message-passing.tex
added files...

--- 2018-04-28 paper/algorithm.tex
@@
-\section{Algorithm}%
-\label{Algorithm}
-
-Alice and Bob each has a set of devices containing their files, \eg a 
-smartphone, laptop and a desktop computer.
-Alice and Bob meet in a café carrying only their smartphones and Alice wants to 
-share a file, \(f\), with Bob.
-Alice's smartphone knows some metadata of \(f\) and that it resides on Alice's 
-desktop computer.
-She gives some metadata about \(f\) to Bob, at least the file size.
-Bob creates an onion route of low-availability devices with some subset of Bob's 
-devices as the destination.
-The layers of the route are chosen such that the probability of all devices 
-being offline at the same time is low.
-Bob gives this route to Alice.
-Alice's smartphone ensures that her desktop computer (containing the file \(f\)) 
-gets the route and the instruction to send \(f\) using this route.
-When Alice's desktop computer receives this instruction it will create the first 
-half of the route and concatenate it with Bob's route, then transfer \(f\) to 
-Bob.
-In this section we will present the details of the necessary algorithms.
-
-We have a set of users, \(U\), each user \(u\in U\) has a set of devices, 
-\(D_u\).
-We call \(D_u\) the device swarm of \(u\).
-Alice, \(a\in U\), has a device swarm, \(D_a\), and Bob, \(b\in U\) has a device 
-swarm, \(D_b\).
-We let \(D = \cup_{u\in U} D_u\) be the set of all devices, the global device 
-swarm.
-Without loss of generality, we will use Alice, with device swarm \(D_a\), and 
-Bob, with device swarm \(D_b\), as examples.
-
-\subsection{The local swarm}%
-\label{local-overlay}
-
-Each of Alice's (and Bob's) devices will keep track of its own online and 
-offline behaviour.
-They will use a protocol like Sprinkler~\cite{luxey:hal-01704172} to learn about 
-each other's online--offline behaviour.
-\commentDaniel{Is that correct?}
-This allows Alice's device swarm to infer a behavioural model for the device 
-swarm and do internal scheduling based on the probability of being online.
-
-\subsubsection{Sharing the user's behavior}% (fold)
-\label{ssub:sharing_the_user_s_behavior}
-
-Each device initially only knows when it is connected. 
-To make a model of the user's behavior, they need to know the whole observation sequence $O$: which device is online at each time step.
-To do so, they employ a probabilistic dissemination protocol, 
-\textsc{Sprinkler}~\cite{luxey:hal-01704172}.
-This allows devices to gossip any new connection information to random peers in 
-the local swarm, ensuring that all devices know the full observation sequence 
-with a very high probability.
-\textsc{Sprinkler} has shown resilient to device churn~\cite{luxey:cascade}, and 
-is thus perfectly suited for our purpose, where a user's devices often 
-disconnect and reconnect.
-
-\commentAL{Then we \textbf{maybe} do predictions as \textbf{maybe} shown in 
-  \cref{sec:user_model}.}
-
-% subsubsection sharing_the_user_s_behavior (end)
-
-\subsubsection{Sharing files location}% (fold)
-\label{ssub:sharing_files_location}
-
-We do stuff and things work.
-
-% subsubsection sharing_files_location (end)
-
-\subsection{Random peer sampling and predictions}
-
-\commentDaniel{%
-  We must cover how to do \(\Pr[d \text{ offline at time } t]\) as used in 
-  \cref{ExtendRoute}.
-  This is probably part of getting random peers in the same place.%
-}
-
-\commentDaniel{%
-  What is the probability distribution of the peer sample that we get?
-  Will it be close to uniformly random?%
-}
-
-\NewAlgorithm{\GetRandomPeer}{GetRandomPeer}
-
-Every time a device is online, it participates in the random peer sampling 
-protocol.
-If a device is sampled it provides the following information:
-\begin{itemize}
-  \item its address;
-	\item its public key;
-  \item the probability of being online.
-\end{itemize}
-
 \NewScheme{\SPOR}{SPOR}
 
-\subsection{\(\SPOR\): Stateless Predictive Onion Routing}
+\subsection{Message Passing: Stateless Predictive Onion Routing \(\SPOR\)}
 
@@
 
-    \Function{\GetRouteNode}{$\theta$}
+    \Function{\CreateOnionLayer}{$\theta$}
       \State $d\gets \GetRandomPeer$
@@
 \end{figure}
-
-\subsection{Scheduling a file transfer}
-
-\commentDaniel{%
-  We must do the scheduling: \ie divide the file \(f\) into \(f_1, \dotsc, f_n\) 
-  and how the size of \(f_i\) relates to transmission time and size of the 
-  timeslot (for the validity of predictions).
-  After that we just do \(\SPOR[\Send]\) on each \(f_i\).%
-}
-
-\subsection{The file exchange}%
-\label{file-exchange}
-
-\subsubsection{File exchange process}% (fold)
-\label{ssub:file_exchange_process}
-
-Firstly, Alice and Bob must exchange information out-of-band: an encryption key $ek$ to cipher the file, and an ID $k$ in the DHT pointing to information on how to reach Alice.

### 2018-04-28 paper/design.tex

--- 2018-04-28 paper/algorithm.tex
@@
-\section{Algorithm}%
-\label{Algorithm}
+\section{Design of the \name file exchange system}
+
+\subsection{Outline}
+
+We present a global outline of \name before covering each of its building block in depth in the next subsections.
 
@@
 
-\subsection{The local swarm}%
-\label{local-overlay}
-
-Each of Alice's (and Bob's) devices will keep track of its own online and 
-offline behaviour.
-They will use a protocol like Sprinkler~\cite{luxey:hal-01704172} to learn about 
-each other's online--offline behaviour.
-\commentDaniel{Is that correct?}
-This allows Alice's device swarm to infer a behavioural model for the device 
-swarm and do internal scheduling based on the probability of being online.
-
-\subsubsection{Sharing the user's behavior}% (fold)
-\label{ssub:sharing_the_user_s_behavior}
-
-Each device initially only knows when it is connected. 
-To make a model of the user's behavior, they need to know the whole observation sequence $O$: which device is online at each time step.
-To do so, they employ a probabilistic dissemination protocol, 
-\textsc{Sprinkler}~\cite{luxey:hal-01704172}.
-This allows devices to gossip any new connection information to random peers in 
-the local swarm, ensuring that all devices know the full observation sequence 
-with a very high probability.
-\textsc{Sprinkler} has shown resilient to device churn~\cite{luxey:cascade}, and 
-is thus perfectly suited for our purpose, where a user's devices often 
-disconnect and reconnect.
-
-\commentAL{Then we \textbf{maybe} do predictions as \textbf{maybe} shown in 
-  \cref{sec:user_model}.}
-
-% subsubsection sharing_the_user_s_behavior (end)
-
-\subsubsection{Sharing files location}% (fold)
-\label{ssub:sharing_files_location}
-
-We do stuff and things work.
-
-% subsubsection sharing_files_location (end)
-
-\subsection{Random peer sampling and predictions}
-
-\commentDaniel{%
-  We must cover how to do \(\Pr[d \text{ offline at time } t]\) as used in 
-  \cref{ExtendRoute}.
-  This is probably part of getting random peers in the same place.%
-}
-
-\commentDaniel{%
-  What is the probability distribution of the peer sample that we get?
-  Will it be close to uniformly random?%
-}
-
-\NewAlgorithm{\GetRandomPeer}{GetRandomPeer}
-
-Every time a device is online, it participates in the random peer sampling 
-protocol.
-If a device is sampled it provides the following information:
-\begin{itemize}
-  \item its address;
-	\item its public key;
-  \item the probability of being online.
-\end{itemize}
-
-\NewScheme{\SPOR}{SPOR}
-
-\subsection{\(\SPOR\): Stateless Predictive Onion Routing}
-
-\NewAlgorithm{\Send}{Send}
-\NewAlgorithm{\Fwd}{Forward}
-\NewAlgorithm{\Recv}{Receive}
-\NewVariable{\rdv}{rdv}
-
-We have the Stateless Predictive Onion Routing scheme, \SPOR, which provides 
-probabilistically onion-routed message passing.
-Instead of providing only one address per hop in the route (as in \eg 
-Tor~\cite{Tor}), \(\SPOR\) provides several alternatives for the next hop 
-depending on their probability of being online.
-To do this, \(\SPOR\) provides stateless algorithms for the onion-routing.
-
-\(\SPOR\) provides three algorithms: \(\SPOR[\Send]\) (\cref{SPORSend}), 
-\(\SPOR[\Fwd]\) (\cref{SPORFwd}) and \(\SPOR[\Recv]\) (\cref{SPORRecv}).
-Say Alice wants to send a message \(m\) to Bob.
-Bob uses \(\SPOR[\Recv]\) to create a probabilistic onion route \(H_\rdv\) from 
-a rendez-vous point to his own device swarm --- all the hops on the route are 
-chosen by Bob uniformly at random.
-Bob gives \(H_\rdv\) to Alice using an out-of-band channel, \eg using his phone.
-Alice uses \(\SPOR[\Send]\) at some later time to send the message to Bob using 
-any of her devices.
-\(\SPOR[\Send]\) extends the route \(H_\rdv\) with some hops of Alice's choosing 
-(uniformly randomly chosen), then starts to forward the message (using 
-\(\SPOR[\Fwd]\)) through the hops on the route to Bob.
-This process is illustrated in \cref{fig:file-exchange}.
-
-\begin{figure}
-  \includegraphics[width=\linewidth]{figures/file_exchange.pdf}
-  \caption{\label{fig:file-exchange}%
-    A schematic of Alice and Bob sending a message using \(\SPOR\).
-  }
-\end{figure}
-
-\NewAlgorithm{\ExtendRoute}{ExtendRoute}
-\NewAlgorithm{\GetRouteNode}{GetRouteNode}
-
-\begin{figure}
-  \begin{algorithmic}
-    \Require{%
-      $H$ is a header of the form \(D\concat H'\) or \(D\concat \top\), where 
-      \(D\) is a set of device addresses.
-      $\pk_D$ is the public key of device set $D$.
-      $L$ is the length of the route,
-      $\theta$ is the threshold of probability of failure.%
-    }
-    \Function{\ExtendRoute}{$H, L, \theta$}
-      \If{$L\leq 0$}
-        \State \Return $H$
-      \EndIf
-      \State $D\gets \GetRouteNode[\theta]$
-      \State $H\gets D\concat \DeBEenc[\mpk, D, H]$
-      \State \Return $\ExtendRoute[H, L-1, \theta]$
-    \EndFunction
-
-    \Function{\GetRouteNode}{$\theta$}
-      \State $d\gets \GetRandomPeer$
-      \State $D\gets \{d\}$
-      \While{$\prod_{d\in D} \Pr[d \text{ offline at time } t] > \theta$}
-        \State $d\gets \GetRandomPeer$
-        \State $D\gets D\cup \{d\}$
-      \EndWhile
-      \State \Return $D$
-    \EndFunction
-  \end{algorithmic}
-  \caption{\label{ExtendRoute}%
-    The \(\ExtendRoute\) algorithm extends a route \(H\) with \(L\) hops and 
-    failure threshold of \(\theta\) for each hop in the route.
-    Thus the probability of failure for the extension is \(1 - (1 - \theta)^L\).
-    The function \(\GetRandomPeer\) is any random peer-sampling algorithm.
-  }
-\end{figure}
-
-\NewAlgorithm{\Store}{Store}
-\NewAlgorithm{\Dec}{Dec}
-\NewVariable{\sk}{sk}
-
-\begin{figure}
-  \begin{algorithmic}
-    \Require{%
-      $D$ is the set of alternative recipient devices.
-    }
-    \Function{\SPOR[\Recv]}{$D$}
-      \State $H_\rdv\gets \ExtendRoute[D\concat \top, L, \theta]$
-      \State \Return $H_\rdv$
-        \Comment{Give to sender out-of-bound.}
-    \EndFunction
-
-    \Function{\Store}{$c_m$}
-      \State $m\gets \DeBEdec[\mpk, \sk, c_m]$
-      \If{$m = \bot$}
-        \State \Return $\bot$
-      \EndIf
-      \State Store $m$ to disk.
-      \State \Return $\top$
-    \EndFunction
-  \end{algorithmic}
-  \caption{\label{SPORRecv}%
-    The \(\SPOR[\Recv]\) algorithm prepares the recipient for receiving a file.
-    It creates a probabilistic onion-route from a rendez-vous point to its own 
-    devices and returns the route to the sender.
-    The \(\Store\) algorithm is used by the local \(\SPOR[\Fwd]\) algorithm to 
-    store messages intended for itself.
-  }
-\end{figure}
-
-\begin{figure}
-  \begin{algorithmic}
-    \Require{%
-      $m$ is the message to be sent,
-      $\pk_D$ is the public-key of the recipient,
-      $H_\rdv$ is the onion-route given by the recipient.
-    }
-    \Function{\SPOR[\Send]}{$\mpk, D, H_\rdv, m$}
-      \State $H\gets \ExtendRoute[H_\rdv, L, \theta]$
-      \State $c_m\gets \DeBEenc[\mpk, D, m]$
-      \State $D\concat C_H\gets H_\rdv$
-      \For{$d\in D$}
-        \Comment{Uniformly randomly chosen}
-        \If{$d\method \Fwd[C_H, c_m] \neq \bot$}
-          \State \Return $\top$
-        \EndIf
-      \EndFor
-      \State \Return $\bot$
-    \EndFunction
-  \end{algorithmic}
-  \caption{\label{SPORSend}%
-    The \(\SPOR[\Send]\) algorithm extends the route \(H_\rdv\) (using 
-    \(\ExtendRoute\), \cref{ExtendRoute}) and sends the message \(m\) down the 
-    extended route using the \(\SPOR[\Fwd]\) algorithm (\cref{SPORFwd}).
-    The first node of \(H_\rdv\) is the rendez-vous point selected by the 
-    recipient.
-    \(\pk_D\) is the public key of the recipient.
-  }
-\end{figure}
-
-\begin{figure}
-  \begin{algorithmic}
-    \Require{$\pk, \sk$ is the public--private key-pair of the node.}
-    \Function{\SPOR[\Fwd]}{$C_H, c_m$}
-      \State $H\gets \DeBEdec[\mpk, \sk, C_H]$
-      \If{$H = \bot$}
-        \State \Return $\bot$
-      \EndIf
-      \State $\{d_i\}\concat C_H'\gets H$
-      \If{$C_H' = \top$}
-        \State \Return $\Store[c_m]$
-      \EndIf
-      \For{$d\in \{d_i\}$}
-        \Comment{Uniformly randomly chosen}
-        \If{$d\method \Fwd[C_H', c_m] \neq \bot$}
-          \State \Return $\top$
-        \EndIf
-      \EndFor
-      \State \Return $\bot$
-    \EndFunction
-  \end{algorithmic}
-  \caption{\label{SPORFwd}%
-    The \(\SPOR[\Fwd]\) algorithm forwards \(c_m\) down the route \(H\), 
-    obtained by decrypting \(C_H\) with the node's associated private key.%
-    The special value \(H = \top\) indicated the end of the route, thus \(c_m\) 
-    is intended for the local node and \(c_m\) is instead sent to disk using 
-    \(\Store\) (\cref{SPORRecv}).%
-  }
-\end{figure}
-
-\subsection{Scheduling a file transfer}
-
-\commentDaniel{%
-  We must do the scheduling: \ie divide the file \(f\) into \(f_1, \dotsc, f_n\) 
-  and how the size of \(f_i\) relates to transmission time and size of the 
-  timeslot (for the validity of predictions).
-  After that we just do \(\SPOR[\Send]\) on each \(f_i\).%
-}
-
-\subsection{The file exchange}%
-\label{file-exchange}
-
-\subsubsection{File exchange process}% (fold)
-\label{ssub:file_exchange_process}
-
-Firstly, Alice and Bob must exchange information out-of-band: an encryption key $ek$ to cipher the file, and an ID $k$ in the DHT pointing to information on how to reach Alice.
+\include*{building-blocks}
+\include*{squad-overlay-design}
+\include*{global-overlay-design}
+\include*{message-passing}
+\include*{file-exchange}

### 2018-04-28 paper/squad-overlay-design.tex

--- 2018-04-12 paper/user-model.tex
@@
-\section{User model} 
+\subsection{The Squad overlay} 
 \label{sec:user_model}
 
-We consider many users owning several devices, that they freely turn on and off depending on their location and will.
-The participants' devices are the only nodes constituting our system; the unreliability of their connectivity has to be taken for granted.
+Each of Alice's (and Bob's) devices will keep track of its own online and 
+offline behaviour.
+They will use a protocol like Sprinkler~\cite{luxey:hal-01704172} to learn about 
+each other's online--offline behaviour.
+\commentDaniel{Is that correct?}
+This allows Alice's device swarm to infer a behavioural model for the device 
+swarm and do internal scheduling based on the probability of being online.
 
-We will first present a model of each user's behavior, that will drive the connection intervals of our system's nodes.
-%Then, we will show how devices can predict the future user's behavior given the model.
+\subsubsection{Sharing knowledge} % (fold)
+\label{sub:sharing_knowledge}
 
-\subsection{A model of the user's behavior}
+Each device initially only knows when it is connected. 
+To make a model of the user's behavior, they need to know the whole observation sequence $O$: which device is online at each time step.
+To do so, they employ a probabilistic dissemination protocol, 
+\textsc{Sprinkler}~\cite{luxey:hal-01704172}.
+This allows devices to gossip any new connection information to random peers in 
+the local swarm, ensuring that all devices know the full observation sequence 
+with a very high probability.
+\textsc{Sprinkler} has shown resilient to device churn~\cite{luxey:cascade}, and 
+is thus perfectly suited for our purpose, where a user's devices often 
+disconnect and reconnect.
+
+% subsection sharing_knowledge (end)
+
+\commentAL{The following was the User Model section}
+
+% We consider many users owning several devices, that they freely turn on and off depending on their location and will.
+% The participants' devices are the only nodes constituting our system; the unreliability of their connectivity has to be taken for granted.
+
+% We will first present a model of each user's behavior, that will drive the connection intervals of our system's nodes.
+% %Then, we will show how devices can predict the future user's behavior given the model.
+
+\subsubsection{A model of the user's behavior}
 \label{sub:a_model_of_the_user_s_behavior}

### 2018-04-28 paper/file-exchange.tex

@@
-\subsection{The file exchange}
+\subsection{Scheduling and transferring a file}%
+\label{file-transfer}
 
-\commentDaniel{%
-  We must do the scheduling: \ie divide the file \(f\) into \(f_1, \dotsc, f_n\) 
-  and how the size of \(f_i\) relates to transmission time and size of the 
-  timeslot (for the validity of predictions).
-  After that we just do \(\SPOR[\Send]\) on each \(f_i\).%
-}
+We are interested in transferring large files.
+Every device \(d\in D\) in the global device swarm is only periodically online.
+We will thus divide the data to send into \(n\) smaller chunks (similar to 
+BitTorrent~\cite{BitTorrent}).
+The idea is to choose \(n\) such that each chunk will be small enough to be 
+successfully relayed by a device before it goes offline again.
+The chunk size is empirically determined in \cref{Performance}.
+\commentDaniel{Adrien, is that true?}
 
-\subsubsection{File exchange process}% (fold)
-\label{ssub:file_exchange_process}
-
-Firstly, Alice and Bob must exchange information out-of-band: an encryption key $ek$ to cipher the file, and an ID $k$ in the DHT pointing to information on how to reach Alice.
+As stated above, Alice and Bob exchange some limited data out-of-bound using 
+their smartphones.
+The information they will exchange is the following:
+\begin{enumerate}
+  \item Bob creates an onion route header, \(H_\rdv\), by running 
+    \(\SPOR[\Recv]\) (\cref{SPORRecv}) and gives it to Alice.
+  \item Alice gives Bob number of file chunks, \(n\), and the size of the file 
+    chunks.
+  \item They agree on a file-specific key \(k\) for some (authenticated) 
+    encryption scheme \(\Enc*\).
+\end{enumerate}
+Then Alice encrypts the file \(f\) and receives the ciphertext \(c_f\gets 
+  \Enc*[Enc](k, f)\).
+She then divides \(c_f\) into \(n\) chunks, \(c_f^{(1)}, \dotsc, c_f^{(n)}\), 
+and runs \(\SPOR[\Send](H_\rdv, c_f^{(i)})\) for all \(1\leq i\leq n\) in 
+parallel.
+\commentDaniel{Or shall we do it sequentially?}

### 2018-04-28 paper/message-passing.tex

@@
     \Function{\CreateOnionLayer}{$\theta$}
-      \State $d\gets \GetRandomPeer$
+      \State $(d, \pk_d, p_d)\gets \GetRandomPeer$
+      \Comment We use \(d\) as shorthand for this tuple.
       \State $D\gets \{d\}$
-      \While{$\prod_{d\in D} \Pr[d \text{ offline at time } t] > \theta$}
+      \While{$\prod_{d\in D} p_d > \theta$}
         \State $d\gets \GetRandomPeer$

### 2018-04-28 paper/design.tex
modifyied file names

@@
 
-\subsection{Outline}
-
-We present a global outline of \name before covering each of its building block in depth in the next subsections.
-
-Alice and Bob each has a set of devices containing their files, \eg a 
-smartphone, laptop and a desktop computer.
-Alice and Bob meet in a café carrying only their smartphones and Alice wants to 
-share a file, \(f\), with Bob.
-Alice's smartphone knows some metadata of \(f\) and that it resides on Alice's 
-desktop computer.
-She gives some metadata about \(f\) to Bob, at least the file size.
-Bob creates an onion route of low-availability devices with some subset of Bob's 
-devices as the destination.
-The layers of the route are chosen such that the probability of all devices 
-being offline at the same time is low.
-Bob gives this route to Alice.
-Alice's smartphone ensures that her desktop computer (containing the file \(f\)) 
-gets the route and the instruction to send \(f\) using this route.
-When Alice's desktop computer receives this instruction it will create the first 
-half of the route and concatenate it with Bob's route, then transfer \(f\) to 
-Bob.
-In this section we will present the details of the necessary algorithms.
-
-We have a set of users, \(U\), each user \(u\in U\) has a set of devices, 
-\(D_u\).
-We call \(D_u\) the device swarm of \(u\).
-Alice, \(a\in U\), has a device swarm, \(D_a\), and Bob, \(b\in U\) has a device 
-swarm, \(D_b\).
-We let \(D = \cup_{u\in U} D_u\) be the set of all devices, the global device 
-swarm.
-Without loss of generality, we will use Alice, with device swarm \(D_a\), and 
-Bob, with device swarm \(D_b\), as examples.
-
+\include*{outline-design}
 \include*{building-blocks}
@@
 \include*{global-overlay-design}
-\include*{message-passing}
-\include*{file-exchange}
+\include*{message-passing-design}
+\include*{file-exchange-design}

### 2018-04-28 paper/outline-design.tex
modifyied file names

--- 2018-04-28 paper/algorithm.tex
@@
-\section{Algorithm}%
-\label{Algorithm}
+\subsection{Outline}
+
+We present a global outline of \name before covering each of its building block in depth in the next subsections.
 
@@
 Bob, with device swarm \(D_b\), as examples.
-
-\subsection{The local swarm}%
-\label{local-overlay}
-
-Each of Alice's (and Bob's) devices will keep track of its own online and 
-offline behaviour.
-They will use a protocol like Sprinkler~\cite{luxey:hal-01704172} to learn about 
-each other's online--offline behaviour.
-\commentDaniel{Is that correct?}
-This allows Alice's device swarm to infer a behavioural model for the device 
-swarm and do internal scheduling based on the probability of being online.
-
-\subsubsection{Sharing the user's behavior}% (fold)
-\label{ssub:sharing_the_user_s_behavior}
-
-Each device initially only knows when it is connected. 
-To make a model of the user's behavior, they need to know the whole observation sequence $O$: which device is online at each time step.
-To do so, they employ a probabilistic dissemination protocol, 
-\textsc{Sprinkler}~\cite{luxey:hal-01704172}.
-This allows devices to gossip any new connection information to random peers in 
-the local swarm, ensuring that all devices know the full observation sequence 
-with a very high probability.
-\textsc{Sprinkler} has shown resilient to device churn~\cite{luxey:cascade}, and 
-is thus perfectly suited for our purpose, where a user's devices often 
-disconnect and reconnect.
-
-\commentAL{Then we \textbf{maybe} do predictions as \textbf{maybe} shown in 
-  \cref{sec:user_model}.}
-
-% subsubsection sharing_the_user_s_behavior (end)
-
-\subsubsection{Sharing files location}% (fold)
-\label{ssub:sharing_files_location}
-
-We do stuff and things work.
-
-% subsubsection sharing_files_location (end)
-
-\subsection{Random peer sampling and predictions}
-
-\commentDaniel{%
-  We must cover how to do \(\Pr[d \text{ offline at time } t]\) as used in 
-  \cref{ExtendRoute}.
-  This is probably part of getting random peers in the same place.%
-}
-
-\commentDaniel{%
-  What is the probability distribution of the peer sample that we get?
-  Will it be close to uniformly random?%
-}
-
-\NewAlgorithm{\GetRandomPeer}{GetRandomPeer}
-
-Every time a device is online, it participates in the random peer sampling 
-protocol.
-If a device is sampled it provides the following information:
-\begin{itemize}
-  \item its address;
-	\item its public key;
-  \item the probability of being online.
-\end{itemize}
-
-\NewScheme{\SPOR}{SPOR}
-
-\subsection{\(\SPOR\): Stateless Predictive Onion Routing}
-
-\NewAlgorithm{\Send}{Send}
-\NewAlgorithm{\Fwd}{Forward}
-\NewAlgorithm{\Recv}{Receive}
-\NewVariable{\rdv}{rdv}
-
-We have the Stateless Predictive Onion Routing scheme, \SPOR, which provides 
-probabilistically onion-routed message passing.
-Instead of providing only one address per hop in the route (as in \eg 
-Tor~\cite{Tor}), \(\SPOR\) provides several alternatives for the next hop 
-depending on their probability of being online.
-To do this, \(\SPOR\) provides stateless algorithms for the onion-routing.
-
-\(\SPOR\) provides three algorithms: \(\SPOR[\Send]\) (\cref{SPORSend}), 
-\(\SPOR[\Fwd]\) (\cref{SPORFwd}) and \(\SPOR[\Recv]\) (\cref{SPORRecv}).
-Say Alice wants to send a message \(m\) to Bob.
-Bob uses \(\SPOR[\Recv]\) to create a probabilistic onion route \(H_\rdv\) from 
-a rendez-vous point to his own device swarm --- all the hops on the route are 
-chosen by Bob uniformly at random.
-Bob gives \(H_\rdv\) to Alice using an out-of-band channel, \eg using his phone.
-Alice uses \(\SPOR[\Send]\) at some later time to send the message to Bob using 
-any of her devices.
-\(\SPOR[\Send]\) extends the route \(H_\rdv\) with some hops of Alice's choosing 
-(uniformly randomly chosen), then starts to forward the message (using 
-\(\SPOR[\Fwd]\)) through the hops on the route to Bob.
-This process is illustrated in \cref{fig:file-exchange}.
-
-\begin{figure}
-  \includegraphics[width=\linewidth]{figures/file_exchange.pdf}
-  \caption{\label{fig:file-exchange}%
-    A schematic of Alice and Bob sending a message using \(\SPOR\).
-  }
-\end{figure}
-
-\NewAlgorithm{\ExtendRoute}{ExtendRoute}
-\NewAlgorithm{\GetRouteNode}{GetRouteNode}
-
-\begin{figure}
-  \begin{algorithmic}
-    \Require{%
-      $H$ is a header of the form \(D\concat H'\) or \(D\concat \top\), where 
-      \(D\) is a set of device addresses.
-      $\pk_D$ is the public key of device set $D$.
-      $L$ is the length of the route,
-      $\theta$ is the threshold of probability of failure.%
-    }
-    \Function{\ExtendRoute}{$H, L, \theta$}
-      \If{$L\leq 0$}
-        \State \Return $H$
-      \EndIf
-      \State $D\gets \GetRouteNode[\theta]$
-      \State $H\gets D\concat \DeBEenc[\mpk, D, H]$
-      \State \Return $\ExtendRoute[H, L-1, \theta]$
-    \EndFunction
-
-    \Function{\GetRouteNode}{$\theta$}
-      \State $d\gets \GetRandomPeer$
-      \State $D\gets \{d\}$
-      \While{$\prod_{d\in D} \Pr[d \text{ offline at time } t] > \theta$}
-        \State $d\gets \GetRandomPeer$
-        \State $D\gets D\cup \{d\}$
-      \EndWhile
-      \State \Return $D$
-    \EndFunction
-  \end{algorithmic}
-  \caption{\label{ExtendRoute}%
-    The \(\ExtendRoute\) algorithm extends a route \(H\) with \(L\) hops and 
-    failure threshold of \(\theta\) for each hop in the route.
-    Thus the probability of failure for the extension is \(1 - (1 - \theta)^L\).
-    The function \(\GetRandomPeer\) is any random peer-sampling algorithm.
-  }
-\end{figure}
-
-\NewAlgorithm{\Store}{Store}
-\NewAlgorithm{\Dec}{Dec}
-\NewVariable{\sk}{sk}
-
-\begin{figure}
-  \begin{algorithmic}
-    \Require{%
-      $D$ is the set of alternative recipient devices.
-    }
-    \Function{\SPOR[\Recv]}{$D$}
-      \State $H_\rdv\gets \ExtendRoute[D\concat \top, L, \theta]$
-      \State \Return $H_\rdv$
-        \Comment{Give to sender out-of-bound.}
-    \EndFunction
-
-    \Function{\Store}{$c_m$}
-      \State $m\gets \DeBEdec[\mpk, \sk, c_m]$
-      \If{$m = \bot$}
-        \State \Return $\bot$
-      \EndIf
-      \State Store $m$ to disk.
-      \State \Return $\top$
-    \EndFunction
-  \end{algorithmic}
-  \caption{\label{SPORRecv}%
-    The \(\SPOR[\Recv]\) algorithm prepares the recipient for receiving a file.
-    It creates a probabilistic onion-route from a rendez-vous point to its own 
-    devices and returns the route to the sender.
-    The \(\Store\) algorithm is used by the local \(\SPOR[\Fwd]\) algorithm to 
-    store messages intended for itself.
-  }
-\end{figure}
-
-\begin{figure}
-  \begin{algorithmic}
-    \Require{%
-      $m$ is the message to be sent,
-      $\pk_D$ is the public-key of the recipient,
-      $H_\rdv$ is the onion-route given by the recipient.
-    }
-    \Function{\SPOR[\Send]}{$\mpk, D, H_\rdv, m$}
-      \State $H\gets \ExtendRoute[H_\rdv, L, \theta]$
-      \State $c_m\gets \DeBEenc[\mpk, D, m]$
-      \State $D\concat C_H\gets H_\rdv$
-      \For{$d\in D$}
-        \Comment{Uniformly randomly chosen}
-        \If{$d\method \Fwd[C_H, c_m] \neq \bot$}
-          \State \Return $\top$
-        \EndIf
-      \EndFor
-      \State \Return $\bot$
-    \EndFunction
-  \end{algorithmic}
-  \caption{\label{SPORSend}%
-    The \(\SPOR[\Send]\) algorithm extends the route \(H_\rdv\) (using 
-    \(\ExtendRoute\), \cref{ExtendRoute}) and sends the message \(m\) down the 
-    extended route using the \(\SPOR[\Fwd]\) algorithm (\cref{SPORFwd}).
-    The first node of \(H_\rdv\) is the rendez-vous point selected by the 
-    recipient.
-    \(\pk_D\) is the public key of the recipient.
-  }
-\end{figure}
-
-\begin{figure}
-  \begin{algorithmic}
-    \Require{$\pk, \sk$ is the public--private key-pair of the node.}
-    \Function{\SPOR[\Fwd]}{$C_H, c_m$}
-      \State $H\gets \DeBEdec[\mpk, \sk, C_H]$
-      \If{$H = \bot$}
-        \State \Return $\bot$
-      \EndIf
-      \State $\{d_i\}\concat C_H'\gets H$
-      \If{$C_H' = \top$}
-        \State \Return $\Store[c_m]$
-      \EndIf
-      \For{$d\in \{d_i\}$}
-        \Comment{Uniformly randomly chosen}
-        \If{$d\method \Fwd[C_H', c_m] \neq \bot$}
-          \State \Return $\top$
-        \EndIf
-      \EndFor
-      \State \Return $\bot$
-    \EndFunction
-  \end{algorithmic}
-  \caption{\label{SPORFwd}%
-    The \(\SPOR[\Fwd]\) algorithm forwards \(c_m\) down the route \(H\), 
-    obtained by decrypting \(C_H\) with the node's associated private key.%
-    The special value \(H = \top\) indicated the end of the route, thus \(c_m\) 
-    is intended for the local node and \(c_m\) is instead sent to disk using 
-    \(\Store\) (\cref{SPORRecv}).%
-  }
-\end{figure}
-
-\subsection{Scheduling a file transfer}
-
-\commentDaniel{%
-  We must do the scheduling: \ie divide the file \(f\) into \(f_1, \dotsc, f_n\) 
-  and how the size of \(f_i\) relates to transmission time and size of the 
-  timeslot (for the validity of predictions).
-  After that we just do \(\SPOR[\Send]\) on each \(f_i\).%
-}
-
-\subsection{The file exchange}%
-\label{file-exchange}
-
-\subsubsection{File exchange process}% (fold)
-\label{ssub:file_exchange_process}
-
-Firstly, Alice and Bob must exchange information out-of-band: an encryption key $ek$ to cipher the file, and an ID $k$ in the DHT pointing to information on how to reach Alice.

### 2018-04-28 paper/squad-overlay-design.tex
modifyied file names

@@
 Each of Alice's (and Bob's) devices will keep track of its own online and 
-offline behaviour.
+offline behavior.
 They will use a protocol like Sprinkler~\cite{luxey:hal-01704172} to learn about 
-each other's online--offline behaviour.
+each other's online--offline behavior.
 \commentDaniel{Is that correct?}
-This allows Alice's device swarm to infer a behavioural model for the device 
+This allows Alice's device swarm to infer a behavioral model for the device 
 swarm and do internal scheduling based on the probability of being online.

### 2018-04-28 paper/security-analysis.tex

@@
 
-\dots
+\commentDaniel{Under editing.}
 
@@
 hence a global observer can track the message through the network.
+The same applies if one node occurs more than once in a route, \eg in both 
+Alice's and Bob's part of the route.
+
+Since we have an in-package header, each node on the route can infer its 
+position on the route.
+\commentDaniel{Maybe this can be solved by issue \#33.}
 
 We can choose different properties for \(\Enc*\).
-What makes sense is to choose an authenticated encryption 
+What makes sense is to choose at least an authenticated encryption 
 scheme~\cite{AuthEncryption}.

### 2018-04-28 paper/global-overlay-design.tex

@@
 \begin{itemize}
-  \item its address;
-	\item its public key;
-  \item the probability of being online.
+  \item its address, \(d\);
+  \item its public key, \(\pk_d\);
+  \item the probability of being online, \(p_d\).
 \end{itemize}
+We will denote this by the following algorithm \((d, \pk_d, p_d)\gets 
+  \GetRandomPeer\), which will be used below.
+The probability of being online, \(p_d\), is inferred as above 
+(\cref{local-swarm}).

### 2018-04-28 paper/design.tex
yaaaay, outline figure

--- 2018-04-28 paper/design.tex
@@
 
-\subsection{Outline}
+This section presents the \name protocol in detail.
+Our goal is to enable private and reliable file exchange between users participating in the system, by using their respective devices only.
+
+The privacy objectives of our system require encryption primitives that we first detail in section~\ref{BuildingBlocks}.
+
+The other constituents of \name are summarized in figure~\ref{fig:outline}.
+On top, the devices of each user are circled in gray, and form a user's device squad.
+The squad online members communicate among themselves: they exchange files and messages information, and cooperate to predict the user's future behavior.
+This first protocol is called the \emph{squad overlay} and will be discussed in section~\ref{sec:squad_overlay}.
+%On top we see that each user's devices (shown as clouds) communicate with one another through a dissemination protocol---coined the \emph{squad overlay}---that will be discussed in section~\ref{sec:squad_overlay}.
+Below, we see all devices connected in a random graph: each online device gives information about itself. This \emph{global overlay} will be covered in section~\ref{sec:global_overlay}.
+The information brought by these overlays allows devices to securely and reliably exchange messages between users, as will be explained in section~\ref{sec:message_passing}.
+Given this message passing protocol, users can privately exchange files. We will cover this ultimate goal in section~\ref{sec:file_exchange}.
+
+\begin{figure}[t]
+\centering
+\def\svgwidth{\columnwidth}
+%\input{outline.pdf_tex}
+\import{figures/}{outline.pdf_tex}
+%\includegraphics[width=0.9\columnwidth]{figures/outline.pdf}
+\caption{\label{fig:outline}Outline of \name's components.}
+
+\end{figure}
 

### 2018-04-29 paper/design.tex
introduction of Design

--- 2018-04-28 paper/design.tex
@@
 
-\include*{outline-design}
+This section presents the \name protocol in detail.
+Our goal is to enable private and reliable file exchange between users participating in the system, by using their respective devices only.
+When Alice and Bob, two users of our system, want to exchange a file $f$ through \name; they start by sharing some information out-of-band, e.g. from their smartphones.
+More precisely, they exchange metadata on $f$, encryption keys, and agree upon a Probabilistic Onion Routes (POR).
+PORs are our adaptation of onion routes, allowing secret communication between two entities despite the unreliability of the nodes that will relay their messages.
+From there on, Alice and Bob add the POR information to the headers of their subsequent file exchange messages, such that the file transfer remains secret to anyone but them.
+
+% Alice and Bob each has a set of devices containing their files, \eg a 
+% smartphone, laptop and a desktop computer.
+% Alice and Bob meet in a café carrying only their smartphones and Alice wants to 
+% share a file, \(f\), with Bob.
+% Alice's smartphone knows some metadata of \(f\) and that it resides on Alice's 
+% desktop computer.
+% She gives some metadata about \(f\) to Bob, at least the file size.
+% Bob creates an onion route of low-availability devices with some subset of Bob's 
+% devices as the destination.
+% The layers of the route are chosen such that the probability of all devices 
+% being offline at the same time is low.
+% Bob gives this route to Alice.
+% Alice's smartphone ensures that her desktop computer (containing the file \(f\)) 
+% gets the route and the instruction to send \(f\) using this route.
+% When Alice's desktop computer receives this instruction it will create the first 
+% half of the route and concatenate it with Bob's route, then transfer \(f\) to 
+% Bob.
+% In this section we will present the details of the necessary algorithms.
+
+% We have a set of users, \(U\), each user \(u\in U\) has a set of devices, 
+% \(D_u\).
+% We call \(D_u\) the device swarm of \(u\).
+% Alice, \(a\in U\), has a device swarm, \(D_a\), and Bob, \(b\in U\) has a device 
+% swarm, \(D_b\).
+% We let \(D = \cup_{u\in U} D_u\) be the set of all devices, the global device 
+% swarm.
+% Without loss of generality, we will use Alice, with device swarm \(D_a\), and 
+% Bob, with device swarm \(D_b\), as examples.
+
+The privacy objectives of our system require encryption primitives that we first detail in section~\ref{BuildingBlocks}. The other constituents of \name are depicted in figure~\ref{fig:outline}.
+On top, the devices of each user are circled in gray, and form a user's device squad.
+The squad online members communicate among themselves: they exchange files and messages information, and cooperate to predict the user's future behavior.
+This first protocol is called the \emph{squad overlay} and will be discussed in section~\ref{sec:squad_overlay}.
+%On top we see that each user's devices (shown as clouds) communicate with one another through a dissemination protocol---coined the \emph{squad overlay}---that will be discussed in section~\ref{sec:squad_overlay}.
+Below, we see all devices connected in a random graph: each online device gives information about itself. This \emph{global overlay} will be covered in section~\ref{sec:global_overlay}.
+The information brought by these overlays allows devices to securely and reliably exchange messages between users, as will be explained in section~\ref{sec:message_passing}.
+Given this message passing protocol, users can privately exchange files, as shown in the bottom of the figure. We will cover this ultimate goal in section~\ref{sec:file_exchange}.
+
+\begin{figure}[t]
+\centering
+\def\svgwidth{\columnwidth}
+%\input{outline.pdf_tex}
+\import{figures/}{outline.pdf_tex}
+%\includegraphics[width=0.9\columnwidth]{figures/outline.pdf}
+\caption{\label{fig:outline}Outline of \name's components.}
+
+\end{figure}
+
 \include*{building-blocks}

### 2018-04-29 paper/design.tex
squad overlay being done

@@
 More precisely, they exchange metadata on $f$, encryption keys, and agree upon a Probabilistic Onion Routes (POR).
-PORs are our adaptation of onion routes, allowing secret communication between two entities despite the unreliability of the nodes that will relay their messages.
+PORs are our adaptation of onion routes, allowing secret communication between two entities despite the unreliability of the nodes that relay their messages.
 From there on, Alice and Bob add the POR information to the headers of their subsequent file exchange messages, such that the file transfer remains secret to anyone but them.
@@
 The squad online members communicate among themselves: they exchange files and messages information, and cooperate to predict the user's future behavior.
-This first protocol is called the \emph{squad overlay} and will be discussed in section~\ref{sec:squad_overlay}.
+This first protocol is called the \emph{Squad Overlay} and will be discussed in section~\ref{sec:squad_overlay}.
 %On top we see that each user's devices (shown as clouds) communicate with one another through a dissemination protocol---coined the \emph{squad overlay}---that will be discussed in section~\ref{sec:squad_overlay}.
-Below, we see all devices connected in a random graph: each online device gives information about itself. This \emph{global overlay} will be covered in section~\ref{sec:global_overlay}.
+Below, we see all devices connected in a random graph: each device gives information about itself to random nodes when it is online. 
+This \emph{Global Overlay} will be covered in section~\ref{sec:global_overlay}.
 The information brought by these overlays allows devices to securely and reliably exchange messages between users, as will be explained in section~\ref{sec:message_passing}.

### 2018-04-29 paper/squad-overlay-design.tex
yaaaay, outline figure
squad overlay being done

--- 2018-04-12 paper/user-model.tex
@@
-\section{User model} 
-\label{sec:user_model}
+\subsection{The Squad Overlay} 
+\label{sec:squad_overlay}
 
-We consider many users owning several devices, that they freely turn on and off depending on their location and will.
-The participants' devices are the only nodes constituting our system; the unreliability of their connectivity has to be taken for granted.
+At the root of \name is predictive routing.
+%By sharing information among themselves, a user's devices (her \emph{squad}) can model her behavior.
+Our goal here is that each online device predicts the probability that it stays online in the near future.
+This probability will later be used to create Probabilistic Onion Routes (POR).
+A device's connection depends on the activity of its user; thus, a user's devices (her \emph{squad}) want to predict her future behavior.
 
-We will first present a model of each user's behavior, that will drive the connection intervals of our system's nodes.
-%Then, we will show how devices can predict the future user's behavior given the model.
+In this section, we only take interest in one user (called Alice) and her squad.
 
-\subsection{A model of the user's behavior}
+% Each of Alice's (and Bob's) devices will keep track of its own online and 
+% offline behavior.
+% They will use a protocol like Sprinkler~\cite{luxey:hal-01704172} to learn about 
+% each other's online--offline behavior.
+% \commentDaniel{Is that correct?}
+% This allows Alice's device swarm to infer a behavioral model for the device 
+% swarm and do internal scheduling based on the probability of being online.
+
+\subsubsection{Sharing the user's behavior} % (fold)
+\label{sub:sharing_knowledge}
+
+Online devices want to know whether they are likely to stay online in the near future.
+Taken separately, each device only knows local information: when Alice used it, and maybe mobility information if it is mobile.
+When combining these informations, though, we obtain a sequence of the user's behavior that is far more complete.
+For instance, the probability that Alice uses her home computer and workstation simultaneously is null: these devices are too far apart.
+
+The Squad Overlay leverages on a probabilistic dissemination protocol, \textsc{Sprinkler}~\cite{luxey:hal-01704172}, that does just that: 
+it allows one's devices to inform one another every time the user performs an action (under the condition that no actions are concurrent).
+Previous work in our team~\cite{luxey:cascade} showed that \textsc{Sprinkler} is resilient to devices churn: 
+devices let each other know of what they have missed while offline.
+We thus employ \textsc{Sprinkler} to disseminate the user's activity to its squad.
+
+% Each device initially only knows when it is connected, which is not sufficient to make reliable predictions on whether it is likely to stay online.
+% If they knew the other devices' connection and disconnection times, they 
+% To make a model of the user's behavior, they need to know the whole observation sequence $O$: which device is online at each time step.
+% To do so, they employ a probabilistic dissemination protocol, 
+% \textsc{Sprinkler}~\cite{luxey:hal-01704172}.
+% This allows devices to gossip any new connection information to random peers in 
+% the local swarm, ensuring that all devices know the full observation sequence 
+% with a very high probability.
+% \textsc{Sprinkler} has shown resilient to device churn~\cite{luxey:cascade}, and 
+% is thus perfectly suited for our purpose, where a user's devices often 
+% disconnect and reconnect.
+
+% subsection sharing_knowledge (end)
+
+\subsubsection{Other uses of the Squad Overlay} % (fold)
+\label{ssub:other_uses_of_the_squad_overlay}
+
+In addition to user's behavior, devices firstly share user-chosen files location: when Alice wants to share a file $f$ that resides on her home computer, using her smartphone as the exchange initiator, her smartphone knows where $f$ is located and can create the route accordingly.
+Secondly, each device is also informed of its user's ongoing file transfers.
+
+\name knows two message types (as will be covered in~\ref{sec:file_exchange}): file chunk, and acknowledgment.
+Alice typically wants to receive a file on one particular device; respectively, only one of her devices is interested in acknowledging reception of the file chunks it is sending.
+However, \name allows all squad members to receive messages destined to Alice.
+Thus, the third complementary purpose of the Squad Overlay is to relay messages among the squad: when a message is not destined to the device that received it, the receiver forwards the message to its final destination.
+% We consider many users owning several devices, that they freely turn on and off depending on their location and will.
+% The participants' devices are the only nodes constituting our system; the unreliability of their connectivity has to be taken for granted.
+
+% We will first present a model of each user's behavior, that will drive the connection intervals of our system's nodes.
+% %Then, we will show how devices can predict the future user's behavior given the model.
+
+\subsubsection{A model of the user's behavior}
 \label{sub:a_model_of_the_user_s_behavior}

### 2018-04-29 paper/squad-overlay-design.tex
need a rest

@@
 
-\subsubsection{Other uses of the Squad Overlay} % (fold)
-\label{ssub:other_uses_of_the_squad_overlay}
+% \subsubsection{Other uses of the Squad Overlay} % (fold)
+% \label{ssub:other_uses_of_the_squad_overlay}
 
-In addition to user's behavior, devices firstly share user-chosen files location: when Alice wants to share a file $f$ that resides on her home computer, using her smartphone as the exchange initiator, her smartphone knows where $f$ is located and can create the route accordingly.
-Secondly, each device is also informed of its user's ongoing file transfers.
+\paragraph*{Other uses of the Squad Overlay} In addition to user's behavior, devices use th Squad Overlay for several purposes.
+Firstly, they share files location: when Alice wants to share a file $f$ that resides on her home computer, using her smartphone as the exchange initiator, her smartphone knows where $f$ is located and can create the route accordingly.
+Secondly, each device is also informed of its user's ongoing file transfers (which serves the next purpose).
 
@@
 Thus, the third complementary purpose of the Squad Overlay is to relay messages among the squad: when a message is not destined to the device that received it, the receiver forwards the message to its final destination.
-% We consider many users owning several devices, that they freely turn on and off depending on their location and will.
-% The participants' devices are the only nodes constituting our system; the unreliability of their connectivity has to be taken for granted.
 
-% We will first present a model of each user's behavior, that will drive the connection intervals of our system's nodes.
-% %Then, we will show how devices can predict the future user's behavior given the model.
+\subsubsection{Modeling the user's behavior}
+\label{sub:a_model_of_the_user_s_behavior}
 
-\subsubsection{A model of the user's behavior}
-\label{sub:a_model_of_the_user_s_behavior}
+To model the user's behavior (and predict its future activity), we employ discrete Hidden Markov Models (HMMs) of order one, with multiple discrete observation processes (the devices connection).
 

### 2018-04-29 paper/evaluation.tex
renamed performance into evaluation

\section{Performance evaluation}%
\label{Performance}

\commentDaniel{%
  Some data for Adrien.%
}
\Textcite{ANOBE} proposed using a modified version of \ac{KD-HES}.

\subsection{Evaluation testbed} % (fold)
\label{sub:evaluation_testbed}

\subsubsection{Simulating user behavior} % (fold)
\label{ssub:simulating_user_behavior}

To evaluate \name, we take interest in users owning a variable amount of devices of different types, and frequently switching among them.
To the best of our knowledge, there exists no real-world dataset of the devices connection times of such a user.
We have thus implemented an evaluation testbed where each user's behavior is simulated  according to the following properties:
\begin{itemize}
	\item The user owns a variable amount of devices (3 to 10). We consider the following device types: mobile (e.g. tablet, phone), portable (laptop), fixed (workstation, home computer) and server (such as a NAS, Raspberry Pi or rented appliance);
	\item She can travel between different locations, say her home, her workplace and and outside;
	\item She makes a different use of her devices depending on her location: her home computer will only be accessed at home, while her phone can be accessed everywhere (though she tends to use it the most at home, for instance).
\end{itemize}

We thus model each user with a Hidden Markov Model, as presented in section~\ref{sub:a_model_of_the_user_s_behavior}.
We keep the different possible locations $\mathcal{L}$ to a number of three, and generate different state transition matrices $A$ and emission probability matrices $B$ for each user.

$B_{*, d}$, the probability that device $d$ is used in each location, depends on $d$'s device type:

\begin{itemize}
	\item for each location, every mobile device $d_m$ has a random but high probability of being online: $\forall l \in \mathcal{L}, B_{l, d_m} \in [0.6, 1]$;
	\item a portable device $d_p$ has a much lower probability of being used ($\forall l \in \mathcal{L}, B_{l, d_p} \in [0.2, 0.8]$); 
	\item a fixed appliance $d_f$ has a non-zero probability of usage in only one location: $\exists l \in \mathcal{L}, \forall l' \neq l, B_{l, d_f} \in [0.4, 0.8] \& B_{l, d_f} = 0$
	\item a server $d_s $has a very high probability of working, 
\end{itemize}

\begin{figure}[t]
\centering
\vspace{-1em}

$$A =
\kbordermatrix{
      & W            & O            & H            \cr
    W & \sfrac{2}{3} & \sfrac{1}{3} & 0            \cr
    O & \sfrac{1}{3} & \sfrac{1}{3} & \sfrac{1}{3} \cr
    H & 0            & \sfrac{1}{3} & \sfrac{2}{3} \\[0.3em]
}, \;
B = 
\kbordermatrix{
      & W     & O   & H   \cr
    p & 0.7 & 0.6 & 0.8 \cr
    w & 0.7 & 0   & 0   \cr
    h & 0   & 0   & 0.7 \cr
    l & 0.2 & 0.4 & 0.6 \\[0.3em]
}$$

\includegraphics[width=0.9\columnwidth]{figures/hmm.pdf}
\caption{ \label{fig:hmm} Example Hidden Markov Model (HMM) of a user's behavior.}
\end{figure}

\begin{figure}[t]
\centering
\includegraphics[width=\columnwidth]{figures/sample_usage.pdf}

\caption{\label{fig:sample_usage}Sample device usages using the previous HMM specifications. 
%The bottom line reads the HMM's states: \textbf{W}ork, \textbf{O}utside, and \textbf{H}ome, while the dark lines read when the devices (\textbf{h}ome computer, \textbf{p}hone, and \textbf{w}orkstation) are online.
}

\end{figure}

% subsubsection simulating_user_behavior (end)

% subsection evaluation_testbed (end)

### 2018-04-29 paper/squad-overlay-design.tex
renamed performance into evaluation

@@
 The Squad Overlay leverages on a probabilistic dissemination protocol, \textsc{Sprinkler}~\cite{luxey:hal-01704172}, that does just that: 
-it allows one's devices to inform one another every time the user performs an action (under the condition that no actions are concurrent).
+it allows one's devices to inform one another every time the user performs an action.
 Previous work in our team~\cite{luxey:cascade} showed that \textsc{Sprinkler} is resilient to devices churn: 
@@
 
-To model the user's behavior (and predict its future activity), we employ discrete Hidden Markov Models (HMMs) of order one, with multiple discrete observation processes (the devices connection).
+We need a probabilistic model of the user's behavior to predict its future activity.
+In \name, the only data we collect are the connection times of each device.
+In this section only, we discretize time. 
+We store the connection times in an ever-increasing \emph{sequence} $O=O_1, ..., O_i, ...$ of actions performed at every \emph{round}, that lasts a short period of time $T$. 
+$d \in O_t$ thus means that the device $d$ was online from time $t$ to time $t+T$.
+Our goal is to predict $O_{t+1}$ knowing $O_t$.
 
-In \name, we take interest in users that own several devices, and wish to privately exchange files with each other without revealing .
-To the best of our knowledge, no real-world traces of multi-devices usage over several days exist, as would be needed for the experimental evaluation of our system.
-For that reason, we propose a user behavioral model having the following features:
+To this end, we model the user's behavior as a Hidden Markov Models (HMMs) of order one, with multiple discrete \emph{observable} processes (one per device) stored in $O$. 
+The hidden process $S=S_1, ..., S_i, ...$ represents the user's locations, constituted of a set of $N$ potential locations (e.g. home, work or outside), $N$ being a user-defined parameter.
 
-\begin{itemize}
-	\item Each user owns a variable amount of devices. We consider the following device types: mobile, portable, fixed, and server;
-	\item The user travels between three ``locations'' according to a simple probabilistic model: her home, her workplace, and outside;
-	\item She makes a different use of her devices depending on her location: at home, she will her laptop that at work; she cannot use her workstation at home.
-\end{itemize}
+% In \name, we take interest in users that own several devices, and wish to privately exchange files with each other without revealing .
+% To the best of our knowledge, no real-world traces of multi-devices usage over several days exist, as would be needed for the experimental evaluation of our system.
+% For that reason, we propose a user behavioral model having the following features:
 
-To this end, we use a Hidden Markov Model (HMM) of order one, with multiple discrete observation processes. 
-The hidden Markovian process $S$ represents the user's locations, while the \emph{observable} process $O=O_1, \dots, \O_T$ represents the connection state of her devices (either connected or disconnected at any point in time).
-% The \emph{hidden} Markovian process $S=S_1,\dots,S_T$ represents the user's progression among the three proposed locations up to time step $T$.
-% For every device $d$ owned by the user, the \emph{observable} process $O_d=O_{d,1},\dots,O_{d,T}$ reads $d$'s state: it is either online ($o_d$) or offline ($\overline{o_d}$) at each point in time.
-$O_t = O_1, \dots, \O_T$ represents the connection of all the user's devices, such that $o_d \in O_t$ means that device $d$ was connected at time $t$.
+% \begin{itemize}
+% 	\item Each user owns a variable amount of devices. We consider the following device types: mobile, portable, fixed, and server;
+% 	\item The user travels between three ``locations'' according to a simple probabilistic model: her home, her workplace, and outside;
+% 	\item She makes a different use of her devices depending on her location: at home, she will her laptop that at work; she cannot use her workstation at home.
+% \end{itemize}
 
-% The probability of observable events depends only on the current location.
-% For example, the probability that the user's home computer is on while she is at work is null (in our model, users never forget to turn off their fixed devices before leaving).
+% To this end, we use a Hidden Markov Model (HMM) of order one, with multiple discrete observation processes. 
+% The hidden Markovian process $S$ represents the user's locations, while the \emph{observable} process $O=O_1, \dots, \O_T$ represents the connection state of her devices (either connected or disconnected at any point in time).
 
-Such a statistical model is simplistic (e.g. it does not encapsulate date \& time nor location), but it is on purpose: simplicity is bliss.
-Given the lack of real-world data for our testbed, building a more complex and realistic user model would add no value to our proposal: 
-our goal is to see devices exhibiting frequent disconnections and reconnections (also called \emph{churn}).
-Our simple model being able to put extravagant stress on our system, it is sufficient to access \name's resilience.
+% Such a statistical model is simplistic (e.g. it does not encapsulate date \& time nor location), but it is on purpose: simplicity is bliss.
+% Given the lack of real-world data for our testbed, building a more complex and realistic user model would add no value to our proposal: 
+% our goal is to see devices exhibiting frequent disconnections and reconnections (also called \emph{churn}).
+% Our simple model being able to put extravagant stress on our system, it is sufficient to access \name's resilience.
 
-\subsubsection{Formal definition} % (fold)
-\label{ssub:formal_definition}
+\paragraph*{Formal definition}
 

### 2018-04-29 paper/evaluation.tex
don't add figures twice -- it's cheating

@@
 \begin{itemize}
-	\item The user owns a variable amount of devices (3 to 10).
+	\item The user owns a variable amount of devices.
 We consider the following device types: mobile (e.g.
@@
 We thus model each user with a Hidden Markov Model, as presented in section~\ref{sub:a_model_of_the_user_s_behavior}.
-We keep the different possible locations $\mathcal{L}$ to a number of three, and generate different state transition matrices $A$ and emission probability matrices $B$ for each user.
+We keep the different possible locations $\mathcal{L}$ to $N=3$ and the state transition matrix $A$ to a fixed value (cf figure~\ref{fig:hmm}).
+The number and types of devices per user, along with the matrix of emission probabilities $B$, is determined randomly according to the following rules.
 
+A user always has a phone, plus a random number of 2 to 9 devices whose type is decided by a weighted random choice: each device has 30\% chances of being either mobile, portable, or fixed, and only 10\% probability of being a server.
 $B_{*, d}$, the probability that device $d$ is used in each location, depends on $d$'s device type: 
-
 \begin{itemize}
 	\item for each location, every mobile device $d_m$ has a random but high probability of being online: $\forall l \in \mathcal{L}, B_{l, d_m} \in [0.6, 1]$;
-	\item a portable device $d_p$ has a much lower probability of being used ($\forall l \in \mathcal{L}, B_{l, d_p} \in [0.2, 0.8]$); 
-	\item a fixed appliance $d_f$ has a non-zero probability of usage in only one location: $\exists l \in \mathcal{L}, \forall l' \neq l, B_{l, d_f} \in [0.4, 0.8] \& B_{l, d_f} = 0$
-	\item a server $d_s $has a very high probability of working, 
+	\item a portable device $d_p$ has a much lower probability of being used: $\forall l \in \mathcal{L}, B_{l, d_p} \in [0.2, 0.8]$; 
+	\item a fixed appliance $d_f$ has a non-zero probability of usage in only one location: $\exists l \in \mathcal{L}, B_{l, d_f} \in [0.4, 0.8] \text{ and } \forall l' \neq l, B_{l', d_f} = 0$;
+	\item a server $d_s$ has a very high probability of working, whatever the user's location: $\exists p \in [0.9, 1], \forall l \in \mathcal{L}, B{l, d_s} = p$.
 \end{itemize}
@@
       & W   & O   & H   \cr
-    W & \sfrac{2}{3} & \sfrac{1}{3} & 0            \cr
-    O & \sfrac{1}{3} & \sfrac{1}{3} & \sfrac{1}{3} \cr
-    H & 0            & \sfrac{1}{3} & \sfrac{2}{3} \\[0.3em]
+    W & 0.6 & 0.4 & 0   \cr
+    O & 0.2 & 0.6 & 0.2 \cr
+    H & 0   & 0.4 & 0.6 \\[0.3em]
 }, \;
@@
 
+HMMs being generative probabilistic models, they allow the generation of observation sequence $O$ given the parameters of the model $\lambda_N$.
+Figure~\ref{fig:hmm} shows a possible outcome of the creation of a user's HMM, while figure~\ref{fig:sample_usage} shows an observation sequence $O$ that was generated from the displayed model.
+
+Each round lasts $T=10s$ \commentAL{yes, the user switches places fast} and users start at different times. 
+This way, even though the round's period is fixed, devices enter and leave the system at different points in the continuous time.
+
 \begin{figure}[t]

### 2018-04-29 paper/evaluation.tex

@@
 Each round lasts $T=10s$ \commentAL{yes, the user switches places fast} and users start at different times. 
-This way, even though the round's period is fixed, devices enter and leave the system at different points in the continuous time.
+This way, even though the round period is fixed, devices enter and leave the system at different points in the continuous time.
 
@@
 
+\subsection{Devices' predictions of the user behavior} % (fold)
+\label{sub:devices_predictions_of_the_user_behavior}
+
+% subsection devices_predictions_of_the_user_behavior (end)
+\commentAL{Should evaluate the inference of the model given only the observable sequence. Also show that $P[O_{t+1} | S_t] \simeq P[O_{t+i} | S_t]$}
+
 \end{figure}

### 2018-04-29 paper/squad-overlay-design.tex

@@
 The hidden process $S=S_1, ..., S_i, ...$ represents the user's locations, constituted of a set of $N$ potential locations (e.g. home, work or outside), $N$ being a user-defined parameter.
+A HMM of order one is such that the hidden variable at time $t$, $S_t$, only depends on the hidden variable at $t-1$, $S_{t-1}$.
+The observations at time $t$, $O_t$, depend on the current hidden variable only, $S_t$.
+
+We first formally define our HMM, then show how to predict the future knowing the HMM, then finally present how to infer the model from the observable sequence only.
 
@@
 
-\begin{figure}[t]
-\centering
-\vspace{-1em}
-
-$$A =
-\kbordermatrix{
-      & W            & O            & H            \cr
-    W & \sfrac{2}{3} & \sfrac{1}{3} & 0            \cr
-    O & \sfrac{1}{3} & \sfrac{1}{3} & \sfrac{1}{3} \cr
-    H & 0            & \sfrac{1}{3} & \sfrac{2}{3} \\[0.3em]
-}, \;
-B = 
-\kbordermatrix{
-      & W     & O   & H   \cr
-    o_p & 0.7 & 0.6 & 0.8 \cr
-    o_w & 0.7 & 0   & 0   \cr
-    o_h & 0   & 0   & 0.7 \cr
-    o_l & 0.2 & 0.4 & 0.6 \\[0.3em]
-}$$
-
-\includegraphics[width=0.9\columnwidth]{figures/hmm.pdf}
-\caption{ \label{fig:hmm} Example Hidden Markov Model (HMM) of a user's behavior.}
-\end{figure}
-
-We consider a single user, owning a set of $\mathcal{D}$ devices.
-Time is discretized \commentAL{Discretized/synchronous time needs more explanation}.
+%We consider a single user, owning a set of $\mathcal{D}$ devices.
+%Time is discretized \commentAL{Discretized/synchronous time needs more explanation}.
 Needs, and the devices' observations are independent: Alice can have her laptop and phone connected at the same time.
-The hidden process $S=S_1,\dots,S_T$ is built from an alphabet of states $\mathcal{S}$, while the observable process $O=O_1, \dots, \O_T$ contains events from the alphabet $\mathcal{O}$.
+The hidden process $S=S_1,\dots,S_i, \dots$ is built from an alphabet of states $\mathcal{S}$, while the observable process $O=O_1, \dots, \O_i, \dots$ contains elements from the alphabet $\mathcal{O}$.
 We define a multivariate HMM $\lambda_N$ as follows:
@@
 
-	\item $B = \left\{ b_{i\,k}\right\}_{(i,k)\in\mathcal{S}\times\mathcal{O}}$ is the matrix of event emission probabilities for each state:
+	\item $B = \left\{ b_{i\,k}\right\}_{(i,k)\in\mathcal{S}\times\mathcal{D}}$ is the matrix of event emission probabilities for each state:
 	$b_{i\,k} = P[ k \in O_t \mid S_t = i]$.
@@
 
-In our case, the states are the different locations where the user is susceptible to go;
-we considered the three following ones: $\mathcal{S}=\left\{ \mathit{work}, \mathit{outside}, \mathit{home} \right\}$. 
-There is one event per device $d$: $\mathcal{O} = \left\{ o_d \right\}_{d\in \mathcal{D}}$.
-Several devices can be connected at the same time, such that $O_t$ is a set, and $o_d \in O_t$ means that device $d$ was connected at time $t$.
-Devices' connection probabilities are independent.
+In our case, the states $\mathcal{S}$ are the different locations $\mathcal{L}$ where the user is susceptible to go.
+The events represent the devices connection, hence $\mathcal{O} = \mathcal{D}$, where $\mathcal{D}$ is the set of the user's devices.
+Several devices can be connected at the same time, such that $O_t$ is a set, and $d \in O_t$ means that device $d$ was connected at time $t$. Devices' connection probabilities are independent.
 
-In \cref{fig:hmm}, we show an example HMM of a user's behavioral HMM, along with its graphical representation (the initial state distribution $\Pi$ was left out for simplicity). 
-The represented user possesses a phone and a laptop, that she carries around with her, a home computer, that is only accessible from her home, and a workstation, located at her workplace.
+% In \cref{fig:hmm}, we show an example HMM of a user's behavioral HMM, along with its graphical representation (the initial state distribution $\Pi$ was left out for simplicity). 
+% The represented user possesses a phone and a laptop, that she carries around with her, a home computer, that is only accessible from her home, and a workstation, located at her workplace.
 She never forgets to turn off her fixed appliances before leaving.
 
-\begin{figure}[t]
-\centering
-\includegraphics[width=\columnwidth]{figures/sample_usage.pdf}
+% Figure~\ref{fig:sample_usage}, shows a possible trace of the user's behavior, using the parameters depicted in figure~\ref{fig:hmm}. 
+% It reads the timeline of $o_{d}$ for each device $d$. On the bottom of the graph, the first letter of the user's location is shown at each time step.
+% We see that devices connections depend on the user's location, and that any number of devices can be connected at the same time.
 
-\caption{\label{fig:sample_usage}Sample device usages using the previous HMM specifications. 
-%The bottom line reads the HMM's states: \textbf{W}ork, \textbf{O}utside, and \textbf{H}ome, while the dark lines read when the devices (\textbf{h}ome computer, \textbf{p}hone, and \textbf{w}orkstation) are online.
-}
-
-\end{figure}
-
-% Using the toggle events, we compute the device's \emph{connection} events, represented by the multivariate Bernoulli process $C=\left\{ c^{(d)} \right\}_{d\in\mathcal{D}}$. 
-% $c^{(d)}_t=1$ (resp. 0) means that the device $d$ was online (resp. offline) at time step $t$.
-
-% We state that every device starts offline, and compute $c^{(d)}_t$ as follows:
-
-% $$ \forall d \in \mathcal{D},
-% \begin{cases}
-% c^{(d)}_t=0 &\text{when } t=0; \\
-% c^{(d)}_t=c^{(d)}_{t-1} \oplus o^{(d)}_t &\text{when } t>0.
-% \end{cases}$$
-
-Figure~\ref{fig:sample_usage}, shows a possible trace of the user's behavior, using the parameters depicted in figure~\ref{fig:hmm}. 
-It reads the timeline of $o_{d}$ for each device $d$. On the bottom of the graph, the first letter of the user's location is shown at each time step.
-We see that devices connections depend on the user's location, and that any number of devices can be connected at the same time.
-
-% Each device starts offline; then, the user either toggles one device per round or does nothing.
-% In this figure, we show the device \emph{usage}, that is a consequence of the $\mathit{toggle}$ events defined by the HMM.
-% As a consequence, several devices can be online at the same time, as happens in the figure.
-
-% subsubsection formal_definition (end)
-
-\subsubsection{Predicting future behavior} % (fold)
-\label{ssub:predicting_future_behavior}
-Devices want to predict whether they are likely to be connected in the near future.
-This information will be publicly available, and will allow routes selection for the  files exchange between users.
+\paragraph*{Predicting future behavior} 
+As already stated, devices want to predict whether they are likely to be connected in the near future.
+This information will be publicly available, and will enable the intelligent building of routes.
 
@@
 $$
-P\left[ o_d \in O_{t} \mid S_{t-1} = s \right] = 
+P\left[ d \in O_{t} \mid S_{t-1} = s \right] = 
 \sum\limits_{s' \in \mathcal{S}} 
-a_{s\,s'} * b_{s'\,o_d}.
+a_{s\,s'} * b_{s'\,d}.
 $$
@@
 \begin{multline*}
-P\left[ o_d \in O_{t+i} \mid S_{t} = s \right] = \\
+P\left[ d \in O_{t+i} \mid S_{t} = s \right] = \\
 \sum\limits_{s' \in \mathcal{S}}
 P\left[ S_{t+1} = s' \mid S_t = s \right] * 
-P\left[ o_d \in O_{t+i} \mid S_{t+1} = s'\right].
+P\left[ d \in O_{t+i} \mid S_{t+1} = s'\right].
 \end{multline*}
 
-\commentAL{In conclusion: we want more unicorns at the Olympic Games.}
+We show in section~\ref{sub:devices_predictions_of_the_user_behavior} that $P\left[ d \in O_{t+1} \mid S_{t} = s \right] \simeq P\left[ d \in O_{t+i} \mid S_{t} = s \right]$. 
+For that reason, devices only compute the prediction of their connection at $t+1$, that is considered a good enough estimator of their state ``in the near future''.
 
-\commentAL{I don't mention prediction yet since I am not sure we get good enough results.}
+\paragraph*{Inferring the model from the sequence of observations}

### 2018-04-29 paper/security-analysis.tex
Adds more to security analysis (fixes #34)
Another thing for the security analysis

@@
 \commentDaniel{Under editing.}
+
+Alice wants to prevent Bob from learning which are her devices. Bob is allowed 
+to infer the behaviour of devices in the global device swarm, a file transfer 
+from Alice should not give Bob any information about which devices are Alice's.
+
+We also prevent Carol and David to know that Alice and Bob exchanged a file. 
+They forwarded unknown messages.
 
@@
 
+Since we choose a new key for every file, we have forward secrecy between files.
+\Eg an adversary who compromises either Alice or Bob cannot determine what Alice 
+sent to Bob.
+
 We can choose different properties for \(\Enc*\).

### 2018-04-29 paper/global-overlay-design.tex
yaaaay, outline figure

@@
-\subsection{The Global overlay}
+\subsection{The Global Overlay}
+\label{sec:global_overlay}
 
@@
 \begin{itemize}
-  \item its address, \(d\);
+  \item its address, $@_d$;
   \item its public key, \(\pk_d\);
-  \item the probability of being online, \(p_d\).
+  \item the probability of being online, $p_d=P\left[d \in O_{t+1} | S_t\right] $.
 \end{itemize}
-We will denote this by the following algorithm \((d, \pk_d, p_d)\gets 
-  \GetRandomPeer\), which will be used below.
+We will denote this by the following algorithm $(@_d, \pk_d, p_d)\gets 
+  \GetRandomPeer$, which will be used below.
 The probability of being online, \(p_d\), is inferred as above 
-(\cref{local-swarm}).
+(\ref{sub:a_model_of_the_user_s_behavior}).

### 2018-04-29 paper/related.tex

@@
 \label{RelatedWork}
+
+Cloud services for availability of files on multiple devices and sharing with others, such as Dropbox, Box, or iCloud, require trust in the service provider, at minimum to keep the service running without changes to the terms of service becoming unacceptable.
+Alternatively, users could set up their own cloud using a dedicated server or edge devices such as home gateways.
+This would require devices that users are less likely to already have than laptops or smartphones.
+P2P file sharing has been researched extensively, with respect to aspects such as architecture (starting with the semi-centralized Napster~\cite{napster}), availability and replication~\cite{gnutella, krz}, scalability~\cite{bittorrent}, anonymity~\cite{freenet, Tor}, and distributed hash tables (DHT)~\cite{opendht, can, chord, pastry}.
+In contrast to our work, the main goal was to enable dissemination to many users who do not necessarily know each other in person.
+Here, we focus on sharing files in a more deliberate yet ad-hoc manner, i.e., between users that out-of-band agree to share a file but do not keep it available for anyone else in the future.
+TOR~\cite{Tor}, although not designed for file sharing specifically, comes closest in that respect, but does not address the following aspect.
+
+There is a concern shared with traditional p2p file sharing, namely churn and its effect on availability - here in the narrow context of the set of user devices based on user behavior.
+We thus discuss the related work on predicting user behavior next.
 
@@
 % multi-device interaction, and churn in P2P networks.
+
 In our experiments, we simulate users' devices participating in a distributed protocol.

### 2018-04-29 paper/squad-overlay-design.tex

@@
 We show in section~\ref{sub:devices_predictions_of_the_user_behavior} that $P\left[ d \in O_{t+1} \mid S_{t} = s \right] \simeq P\left[ d \in O_{t+i} \mid S_{t} = s \right]$. 
-For that reason, devices only compute the prediction of their connection at $t+1$, that is considered a good enough estimator of their state ``in the near future''.
+For that reason, devices only compute the prediction of their connection at $t+1$, that is considered a good enough estimator of their connection state ``in the near future''.
 
 \paragraph*{Inferring the model from the sequence of observations}
+
+Given an initial estimate $\lambda_{N}^{(0)}$ of the model, and the sequence of observations $O$, the Baum-Welch algorithm uses Expectation-Maximization to iteratively compute the most likely $S^{(i)}$ and $\lambda_{N}^{(i)}$ until the probability of the observations using the estimated model falls below a predefined threshold: $P[O; \lambda_{N}^{(i)}] < \epsilon$.
+Devices use this algorithm to infer their user's behavioral model from the observations.
+
+It needs an initial model, though, with a predefined number of states $N$. 
+$N$ is given by the user, and we set $\lambda_{N}^{(0)}$ to be a uniform model: probabilities of switching to each location are uniform, and all devices have a probability of being online of 0.5.
+
+Baum-Welch usually requires a lot of data to fit the model $\lambda_N$ that generated $O$.
+Indeed, $P[O; \lambda_{N}^{(i)}] < \epsilon$ does not mean that $\lambda_N \simeq \lambda_N^{(i)}$.
+In our case, we do not care as long as the predictions using the estimated model, $P[O_{t+1} \mid S_t; \lambda_N^{(i)}]$, are close to the ground-truth, $P[O_{t+1} \mid S_t; \lambda_N]$.
+This will be evaluated in section~\ref{sub:devices_predictions_of_the_user_behavior}.

### 2018-04-29 paper/related.tex
related work, bibtex entries

--- 2018-04-10 paper/related.tex
@@
 \label{RelatedWork}
+
+Cloud services for availability of files on multiple devices and sharing with others, such as Dropbox, Box, or iCloud, require trust in the service provider, at minimum to keep the service running without changes to the terms of service that would make them unacceptable.
+Alternatively, users could set up their own cloud using a dedicated server or edge device such as a home gateway.
+This would require equipment that users are less likely to already have than laptops or smartphones.
+
+P2P file sharing has been researched extensively, with respect to aspects such as architecture (starting with the semi-centralized Napster), availability and replication (Gnutella), scalability (Bittorrent~\cite{bittorrent}), anonymity (Freenet~\cite{freenet}, TOR~\cite{Tor}, and distributed hash tables (DHT) such as CAN, Chord, Pastry, and Tapestry (see \cite{dhtchurn} for an overview).
+In contrast to our work, the main goal was to enable dissemination to many users who do not necessarily know each other in person.
+Here, we focus on sharing files in a more deliberate yet ad-hoc manner, i.e., between users that out-of-band agree to share a file but do not keep it available for anyone else in the future.
+TOR~\cite{Tor}, although not designed for file sharing specifically, comes closest in that respect, but does not address the following aspect.
+
+There is a concern shared with traditional p2p file sharing, namely churn~\cite{dhtchurn} and its effect on availability - here in the narrow context of the set of user devices based on user behavior.
+We thus discuss the related work on predicting device availability next.
 

### 2018-04-29 paper/conclusion.tex
conclusion

@@
 
-\commentAL{To rewrite as real paragraphs} Future work and prospects:
-\begin{itemize}
-	\item More in-depth knowledge of the user's behavior would allow to predict devices connections farther in the future;
-	\item Changing devices' asymmetric keys regularly would increase security.
-	Updating keys is easy in \name given the RPS that propagates new information to all nodes.
-	However, more reflection would be needed to avoid key updates breaking ongoing communications passing through the devices in question.
+We presented \(\SPOR\) that, in analogy to their biological
+counterparts, enables dissemination under unfavorable conditions. More
+specifially, the deliberate dissemination of files without using
+storage on third-party devices, be they peers or cloud service
+providers. This constraint results in the unfavorable conditions of
+reduced a-priori availability and therefore unreliable nodes. We build
+resilience to these conditions by using predictive modeling for user
+behavior and the ensuing availability of their devices. From our
+experiments, we find that even suboptimal prediction already results in
+successful file transfer with high probability, though often at low
+speed. More in-depth knowledge of the users' behavior would allow us
+to predict device connectivity farther into the future and thus likely
+improve the throughput. From a security and privacy perspective, we
+were guided by the properties of TOR~\cite{Tor}, which we modified to
+a stateless protocol to accommodate unreliable nodes. While we took
+the first steps toward analyzing the consequences of the modifications
+on security and privacy, more is needed to ensure that the added
+features of unreliable nodes, peer sampling, and the side effect of
+enabling more local TOR routing (for example, keeping routes inside a
+country) does not compromise security. On a related note, it would be
+interesting to adapt the Sphinx~\cite{Sphinx} cryptographic packet
+format to the routing of \(\SPOR\) as a step toward provable security.
 
-\end{itemize}
+% \commentAL{To rewrite as real paragraphs} Future work and prospects:
+% \begin{itemize}
+% 	\item More in-depth knowledge of the user's behavior would allow to predict devices connections farther in the future;
+% 	\item Changing devices' asymmetric keys regularly would increase security.
+% 	Updating keys is easy in \name given the RPS that propagates new information to all nodes.
+% 	However, more reflection would be needed to avoid key updates breaking ongoing communications passing through the devices in question.
+
+% \end{itemize}
+
+% It would be interesting to adapt the Sphinx~\cite{Sphinx} cryptographic packet 
+% format to the routing of \(\SPOR\).
+% Then we could achieve the properties of Sphinx and enjoy provable security.

### 2018-04-29 paper/intro.tex

--- 2018-04-05 paper/intro.tex
@@
 % What's the problem?
+Following the Weiserian vision, nowadays, we are
+evolving in a new era of cooperation and interactions among humans.
+The exponential proliferation of devices connected to the Internet is
+drastically impacting human experience and enhancing human
+interactions \cite{Dearman:2008, Oh:2017, Sohn:2008,Harper08}. It further opens new area of research such as
+\textit{proxemics} applied to ubiquitous computing
+\cite{Marquardt:2011}. Users are evolving in their social space with 
+multiple kinds of computing devices that form a \textit{squad} of users'
+devices. Leveraging on the help of their devices squad, users increase their expectations in
+terms of connectivity and interactions possibilities. For instance, as users bring
+their devices close to one another, they expect to initiate cross
+device interactions \textit{in situ} to share digital content
+\cite{Oh:2017} among devices of their own or with devices 
+from other users. More broadly, users expect to share digital content,
+whatever the content location, from one
+device to another in a seamless manner \cite{Dearman:2008}, as they
+would have done in the old days with an USB key.
 
-It is common nowadays to use a third party, \ie someone else's computer (better 
-known as the Cloud), as an intermediate to share files.
-For instance, it is common for Alice to upload a file to \eg Box, Dropbox or 
-OneDrive and share the link with Bob who can then download it.
-The goal of this work is to design a decentralized, distributed system where 
-Alice can share files \emph{effortlessly} between her own devices, \eg laptop, 
-smartphone and tablet.
-But Alice should also be able to use her smartphone to share a file on her home 
-computer with Bob.
-Since these are Alice's private devices, privacy is essential.
-E.g.\ it would be devastating for Alice's privacy if Bob could stalk her by 
-tracking her devices or discern usage patterns.
+From a technical perspective, one major trend to provide a seamless
+sharing of digital contents among users' devices is to leverage on the
+cloud, which acts as a key enabler for ubiquitous computing. Users' data
+are pushed online, into the cloud with either Dropbox, Google Docs,
+OneDrive, Amazon Drive, etc. to make it accessible anytime,
+anywhere to the users' devices.  In the last decades, a lot of research work has
+emerged to promote the use of this offloading strategy to overcome scarce
+resources of users' devices, and to provide an always-on availability
+\cite{Zhang:2014,Gordon:2012,Chun:2011}. It paves the way of different kind
+of clouds, such as mobile cloud computing, the mobile-edge computing
+and/or the fog computing, that aim to use the nodes from the cloud
+infrastructure that are the closest to end users
+for offloading with an improved quality of service and user experience.
 
-% XXX Why is it a problem? Research gap left by other approaches?
-% Why is it important, why care?
+Hence, the cloud, and its variants constitue a perfect complement
+to perform storage and computation on behalf of the resource
+constrained devices. However, this cloud reliance comes at a price:
+devices become totally tethered to a cloud ecosystem and provider. As
+a direct consequence, users lose the control over their own data as it is
+stored and spanned into multiple foreign data centers. Hence, it becomes difficult at 
+the legal level to assess the privacy, and
+confidentiality delivered to the end users. Further, at the practical
+level, users' data can be harvested on their behalf by either the cloud provider or third parties.
+Data sent by the user can be encrypted, but it is not enough
+\cite{granick_2017, HooffLZZ15}. As stated by a famous quotation from
+NSA: "we kill people based on metadata''. Metadata such as the users'
+location and activity can be still tracked, including the access
+control history revealing what users share with whom and when.
+Users’ devices become tracking and/or monitoring devices that turn to
+be the best spy over users.
 
-\commentDaniel{Summarize here why related work is not enough.}
-
-% XXX What's the approach? How to solve the problem?
-
-We use a purely \ac{P2P} design.
-We first provide \iac{P2P} design connecting Alice's own devices.
-This decreases the risk of third-party behavior tracking.
-Then we also use \iac{P2P} design to connect Alice's and Bob's devices.
-This requires some more care, in this case Bob can track Alice since his devices 
-are interacting directly with hers.
-
-% XXX What's the findings?
-% How was it evaluated, what are the results, limitations, what remains to be 
-% done?
-
-\commentDaniel{Summarize our results.}
+In this paper, we introduce SPORE

### 2018-04-29 paper/conclusion.tex
global overlay explained + other minor

--- 2018-04-23 paper/conclusion.tex
@@
 	Updating keys is easy in \name given the RPS that propagates new information to all nodes.
-	However, more reflection would be needed to avoid key updates breaking ongoing communications passing through the devices in question.
+	However, more reflection would be needed to avoid key updates breaking ongoing communications passing through the devices in question;
+	\item \name is not resilient to Byzantine nodes for now: malicious users could potentially make users pick Predictive Onion Routes that pass through them with a high probability, thus allowing the attacker to learn the file sender and receiver.
+To circumvent this, we would need to employ a secure Random Peer Sampling \cite{Jesi_Montresor_van_Steen_2010}, and prevent devices to lie on their probability of being online.
 

### 2018-04-29 paper/conclusion.tex
edits in conclusion

--- 2018-04-29 paper/conclusion.tex
@@
 
-We presented \(\SPOR\) that, in analogy to their biological
+We presented \(\SPOR\) that, in analogy to its biological
 counterparts, enables dissemination under unfavorable conditions. More
 specifially, the deliberate dissemination of files without using
-storage on third-party devices, be they peers or cloud service
-providers. This constraint results in the unfavorable conditions of
-reduced a-priori availability and therefore unreliable nodes. We build
-resilience to these conditions by using predictive modeling for user
-behavior and the ensuing availability of their devices. From our
-experiments, we find that even suboptimal prediction already results in
-successful file transfer with high probability, though often at low
-speed. More in-depth knowledge of the users' behavior would allow us
-to predict device connectivity farther into the future and thus likely
-improve the throughput. From a security and privacy perspective, we
-were guided by the properties of TOR~\cite{Tor}, which we modified to
-a stateless protocol to accommodate unreliable nodes. While we took
-the first steps toward analyzing the consequences of the modifications
-on security and privacy, more is needed to ensure that the added
-features of unreliable nodes, peer sampling, and the side effect of
-enabling more local TOR routing (for example, keeping routes inside a
-country) does not compromise security. On a related note, it would be
-interesting to adapt the Sphinx~\cite{Sphinx} cryptographic packet
-format to the routing of \(\SPOR\) as a step toward provable security.
+storage on third-party devices, be they peers or servers in the
+cloud. This constraint results in the unfavorable conditions of
+reduced a-priori availability and therefore unreliable nodes for
+routing. We build resilience to these conditions by using predictive
+modeling for user behavior and the ensuing availability of their
+devices. From our experiments, we find that even suboptimal prediction
+already results in successful file transfer with high probability,
+though often at low speed. More in-depth knowledge of the users'
+behavior would allow us to predict device connectivity farther into
+the future and thus likely improve the throughput. From a security and
+privacy perspective, we were guided by the properties of
+TOR~\cite{Tor}, which we modified to a stateless protocol to
+accommodate unreliable nodes. While we took the first steps toward
+analyzing the consequences of the modifications on security and
+privacy, more work is needed to provably ensure that the added feature
+of resilience despite unreliable nodes (supported by peer sampling)
+and the side effect of enabling more local TOR routing (for example,
+keeping routes inside a country) do not compromise security. On a
+related note, it would be interesting to adapt the
+Sphinx~\cite{Sphinx} cryptographic packet format to the routing of
+\(\SPOR\) as a step toward provable security.
 

### 2018-04-29 paper/design.tex

@@
 
+\begin{figure}[t]
+\centering
+\def\svgwidth{\columnwidth}
+%\input{outline.pdf_tex}
+\import{figures/}{outline.pdf_tex}
+%\includegraphics[width=0.9\columnwidth]{figures/outline.pdf}
+\caption{\label{fig:outline}Outline of \name's components.
+Users squads of devices are circled in gray.
+From top to bottom: a user's devices collaborate through the Squad Overlay; online devices globally share information about them to random peers; using the two above overlays allows for the creation or Predictive Onion Routes (PORs) between sets of devices; secure file exchange between users is enabled by PORs.}
+\end{figure}
+
 The privacy objectives of our system require encryption primitives that we first detail in section~\ref{BuildingBlocks}. The other constituents of \name are depicted in figure~\ref{fig:outline}.
@@
 This \emph{Global Overlay} will be covered in section~\ref{sec:global_overlay}.
-The information brought by these overlays allows devices to securely and reliably exchange messages between users, as will be explained in section~\ref{sec:message_passing}.
+The information brought by these overlays allows devices to securely and reliably exchange messages between users by creating Predictive Onion Routes (PORs), as will be explained in section~\ref{sec:message_passing}.
 Given this message passing protocol, users can privately exchange files, as shown in the bottom of the figure. We will cover this ultimate goal in section~\ref{sec:file_exchange}.
-
-\begin{figure}[t]
-\centering
-\def\svgwidth{\columnwidth}
-%\input{outline.pdf_tex}
-\import{figures/}{outline.pdf_tex}
-%\includegraphics[width=0.9\columnwidth]{figures/outline.pdf}
-\caption{\label{fig:outline}Outline of \name's components.}
-
-\end{figure}
 

### 2018-04-29 paper/intro.tex
up

@@
 device to another in a seamless manner \cite{Dearman:2008}, as they
-would have done in the old days with an USB key.
+would have done in the old days with an USB key or with an email.
 
@@
 \cite{Zhang:2014,Gordon:2012,Chun:2011}. It paves the way of different kind
-of clouds, such as mobile cloud computing, the mobile-edge computing
-and/or the fog computing, that aim to use the nodes from the cloud
+of clouds, such as mobile cloud computing, mobile-edge computing
+and/or fog computing, that aim to use the nodes from the cloud
 infrastructure that are the closest to end users
@@
 confidentiality delivered to the end users. Further, at the practical
-level, users' data can be harvested on their behalf by either the cloud provider or third parties.
+level, users' data can be harvested on their behalf, and without their
+consent, by either the cloud provider or third parties.
 Data sent by the user can be encrypted, but it is not enough

### 2018-04-29 paper/conclusion.tex
Expands discussion in conclusion/future work

--- 2018-04-29 paper/conclusion.tex
@@
 	Updating keys is easy in \name given the RPS that propagates new information to all nodes.
-	However, more reflection would be needed to avoid key updates breaking ongoing communications passing through the devices in question;
-	\item \name is not resilient to Byzantine nodes for now: malicious users could potentially make users pick Predictive Onion Routes that pass through them with a high probability, thus allowing the attacker to learn the file sender and receiver.
-To circumvent this, we would need to employ a secure Random Peer Sampling \cite{Jesi_Montresor_van_Steen_2010}, and prevent devices to lie on their probability of being online.
+	However, more reflection would be needed to avoid key updates breaking ongoing communications passing through the devices in question.
 
 \end{itemize}
+
+We see two alternative paths for improving the header.
+First, we might be able to adapt the Sphinx~\cite{Sphinx} cryptographic packet 
+format to the routing of \(\SPOR\).
+Then we could achieve the properties of Sphinx and enjoy provable security.
+
+The second approach would be to use the technique by \textcite{PPACinPubFS}.
+They adapt \(\ANOBE\) in such a way that its ciphertexts decrypt to different 
+things for different recipients.
+This way we could have one ciphertext encrypted for all the alternative nodes 
+--- across layers.
+Then the ciphertext would decrypt to different plaintexts for nodes on different 
+layers in the route.
+This would hide the path length (constant-size ciphertexts by padding) and the 
+position of individual nodes.
+This approach would probably be the easiest, but would probably not provide all 
+the properties from Sphinx (\eg resistance to active tagging attacks and bitwise 
+unlinkability).
+
+We should provide bitwise unlinkability for the message between hops on the 
+route.
+Currently the message (\(m\) in \cref{SPORFwd}) itself remains constant 
+throughout the route and thus constitutes a tag for tracking.
+This problem can be solved by choosing the encryption scheme \(\Enc*\) (used to 
+encrypt the message in \cref{sec:file_exchange}) to have ciphertexts that can be 
+re-randomized, \eg schemes for universal 
+re-encryption~\cite{UniversalReencryption}.
+However, then we must assume that at least one node is honest and actually 
+performs the re-randomization (re-encryption) --- there is no incentive for them 
+to do this, as neither Alice nor Bob can detect it without talking directly to 
+each other to compare the ciphertexts.

### 2018-04-29 paper/conclusion.tex

--- 2018-04-29 paper/conclusion.tex
@@
 % 	Updating keys is easy in \name given the RPS that propagates new information to all nodes.
-% 	However, more reflection would be needed to avoid key updates breaking ongoing communications passing through the devices in question.
+% 	However, more reflection would be needed to avoid key updates breaking ongoing communications passing through the devices in question;
+% 	\item \name is not resilient to Byzantine nodes for now: malicious users could potentially make users pick Predictive Onion Routes that pass through them with a high probability, thus allowing the attacker to learn the file sender and receiver.
+To circumvent this, we would need to employ a secure Random Peer Sampling \cite{Jesi_Montresor_van_Steen_2010}, and prevent devices to lie on their probability of being online.
 
@@
 
-% It would be interesting to adapt the Sphinx~\cite{Sphinx} cryptographic packet 
-% format to the routing of \(\SPOR\).
-% Then we could achieve the properties of Sphinx and enjoy provable security.
+We see two alternative paths for improving the header.
+First, we might be able to adapt the Sphinx~\cite{Sphinx} cryptographic packet 
+format to the routing of \(\SPOR\).
+Then we could achieve the properties of Sphinx and enjoy provable security.
+
+The second approach would be to use the technique by \textcite{PPACinPubFS}.
+They adapt \(\ANOBE\) in such a way that its ciphertexts decrypt to different 
+things for different recipients.
+This way we could have one ciphertext encrypted for all the alternative nodes 
+--- across layers.
+Then the ciphertext would decrypt to different plaintexts for nodes on different 
+layers in the route.
+This would hide the path length (constant-size ciphertexts by padding) and the 
+position of individual nodes.
+This approach would probably be the easiest, but would probably not provide all 
+the properties from Sphinx (\eg resistance to active tagging attacks and bitwise 
+unlinkability).
+
+We should provide bitwise unlinkability for the message between hops on the 
+route.
+Currently the message (\(m\) in \cref{SPORFwd}) itself remains constant 
+throughout the route and thus constitutes a tag for tracking.
+This problem can be solved by choosing the encryption scheme \(\Enc*\) (used to 
+encrypt the message in \cref{sec:file_exchange}) to have ciphertexts that can be 
+re-randomized, \eg schemes for universal 
+re-encryption~\cite{UniversalReencryption}.
+However, then we must assume that at least one node is honest and actually 
+performs the re-randomization (re-encryption) --- there is no incentive for them 
+to do this, as neither Alice nor Bob can detect it without talking directly to 
+each other to compare the ciphertexts.

### 2018-04-29 paper/global-overlay-design.tex

--- 2018-04-28 paper/global-overlay-design.tex
@@
-\subsection{The Global overlay}
+\subsection{The Global Overlay}
+\label{sec:global_overlay}
 
-\commentDaniel{%
-  We must cover how to do \(\Pr[d \text{ offline at time } t]\) as used in 
-  \cref{ExtendRoute}.
-  This is probably part of getting random peers in the same place.%
-}
+\newcommand{\viewsize}{\ensuremath{l_{\text{view}}}}
+\NewAlgorithm{\GetRandomPeer}{RPS()}
 
-\commentDaniel{%
-  What is the probability distribution of the peer sample that we get?
-  Will it be close to uniformly random?%
-}
+To reach this goal, we employ Random Peer Sampling (RPS) \cite{Voulgaris_Gavidia_van_Steen_2005,Jelasity_Voulgaris_Guerraoui_Kermarrec_van_Steen_2007}.
+Essentially, each node maintains a \emph{view} containing \viewsize other devices' descriptors. 
+By periodically exchanging random descriptors with a carefully selected node from its view, RPS allows devices to always have a fairly random sample of the nodes in the system inside their view.
+Due to the RPS's eviction policy, stale descriptors are removed quickly: each device thus knows a random sample of \viewsize connected nodes.
+An RPS descriptor for device $d$ is constituted of the following information:
+\begin{itemize}
+  \item Its address: $@_d$;
+  \item Its public key: \(\pk_d\);
+  \item Its probability of being online in the near future, as provided by the Squad Overlay: $p_d=P\left[d \in O_{t+1} | S_t\right]$.
+\end{itemize}
 
-\NewAlgorithm{\GetRandomPeer}{GetRandomPeer}
+Devices now have all the information they need to establish reliable PORs between two sets of devices.
 
-Every time a device is online, it participates in the random peer sampling 
-protocol.
-If a device is sampled it provides the following information:
-\begin{itemize}
-  \item its address;
-	\item its public key;
-  \item the probability of being online.
-\end{itemize}
+% \commentDaniel{%
+%   What is the probability distribution of the peer sample that we get?
+%   Will it be close to uniformly random?
+%   I need this for the security analysis.%
+% }
+
+% \NewAlgorithm{\GetRandomPeer}{GetRandomPeer}
+
+% Every time a device is online, it participates in the random peer sampling 
+% protocol.
+% If a device is sampled it provides the following information:
+% \begin{itemize}
+%   \item its address, $@_d$;
+%   \item its public key, \(\pk_d\);
+%   \item the probability of being online, $p_d=P\left[d \in O_{t+1} | S_t\right] $.
+% \end{itemize}
+% We will denote this by the following algorithm $(@_d, \pk_d, p_d)\gets 
+%   \GetRandomPeer$, which will be used below.
+% The probability of being online, \(p_d\), is inferred as above 
+% (\ref{sub:a_model_of_the_user_s_behavior}).

### 2018-04-29 paper/conclusion.tex
Moves some discussion from conclusion to security-analysis

@@
 unlinkability).
-
-We should provide bitwise unlinkability for the message between hops on the 
-route.
-Currently the message (\(m\) in \cref{SPORFwd}) itself remains constant 
-throughout the route and thus constitutes a tag for tracking.
-This problem can be solved by choosing the encryption scheme \(\Enc*\) (used to 
-encrypt the message in \cref{sec:file_exchange}) to have ciphertexts that can be 
-re-randomized, \eg schemes for universal 
-re-encryption~\cite{UniversalReencryption}.
-However, then we must assume that at least one node is honest and actually 
-performs the re-randomization (re-encryption) --- there is no incentive for them 
-to do this, as neither Alice nor Bob can detect it without talking directly to 
-each other to compare the ciphertexts.

### 2018-04-29 paper/design.tex
minor

@@
 When Alice and Bob, two users of our system, want to exchange a file $f$ through \name; they start by sharing some information out-of-band, e.g. from their smartphones.
-More precisely, they exchange metadata on $f$, encryption keys, and agree upon a Probabilistic Onion Routes (POR).
+More precisely, they exchange metadata on $f$, encryption keys, and agree upon a Predictive Onion Route (POR).
 PORs are our adaptation of onion routes, allowing secret communication between two entities despite the unreliability of the nodes that relay their messages.
@@
 This \emph{Global Overlay} will be covered in section~\ref{sec:global_overlay}.
-The information brought by these overlays allows devices to securely and reliably exchange messages between users by creating Predictive Onion Routes (PORs), as will be explained in section~\ref{sec:message_passing}.
+The information brought by these overlays allows devices to securely and reliably exchange messages between users by creating PORs, as will be explained in section~\ref{sec:message_passing}.
 Given this message passing protocol, users can privately exchange files, as shown in the bottom of the figure. We will cover this ultimate goal in section~\ref{sec:file_exchange}.

### 2018-04-29 paper/intro.tex
up

@@
 multiple kinds of computing devices that form a \textit{squad} of users'
-devices. Leveraging on the help of their devices squad, users increase their expectations in
-terms of connectivity and interactions possibilities. For instance, as users bring
+devices, named \textit{E-Squad} in the remainder of the
+paper. Leveraging on the help of their \textit{E-Squad}, users increase
+their expectations in terms of connectivity and interactions
+possibilities. For instance, as users bring
 their devices close to one another, they expect to initiate cross
 device interactions \textit{in situ} to share digital content
-\cite{Oh:2017} among devices of their own or with devices 
-from other users. More broadly, users expect to share digital content,
+\cite{Oh:2017} among devices of their own \textit{E-Squad} or with the ones 
+from other users' \textit{E-Squad}. More broadly, users expect to share digital content,
 whatever the content location, from one
@@
 
-Hence, the cloud, and its variants constitue a perfect complement
+Hence, the cloud, and its variants constitute a perfect complement
 to perform storage and computation on behalf of the resource
-constrained devices. However, this cloud reliance comes at a price:
+constrained devices. However, this cloud reliance comes at a strong price:
 devices become totally tethered to a cloud ecosystem and provider. As
@@
 Data sent by the user can be encrypted, but it is not enough
-\cite{granick_2017, HooffLZZ15}. As stated by a famous quotation from
+\cite{granick_2017, HooffLZZ15, HarnikPS10}.  As stated by a famous quotation from
 NSA: "we kill people based on metadata''. Metadata such as the users'
@@
 control history revealing what users share with whom and when.
-Users’ devices become tracking and/or monitoring devices that turn to
+Users’ devices become tracking and/or monitoring \textit{E-Squad} that turn to
 be the best spy over users.
 
-In this paper, we introduce SPORE
+Constructing a system that provides anonymous communication is a very
+challenging issue. The last decades, we have witnessed a
+ huge set of attempts at building privacy preserving and anonymous p2p
+ networks \cite{Clarke:2001, Gnunet2002, Freedman:2002, Nambiar:2006,
+   Rennhard:2002}. They are mainly based on onion
+ routing concepts \cite{Chaum:1981}, with some improvements to perform node
+ discovery in a distributed manner, which are otherwise
+centralized in traditional onion routing schemes. However, due to high
+churn of peer-to-peer networks, performance of these systems is
+discouraging \cite{LeBlond:2013}; churn implies frequent
+reconstruction of routes, which is very expensive.

### 2018-04-29 paper/security-analysis.tex
Expands discussion in conclusion/future work

@@
 
-\commentDaniel{Under editing.}
+\commentDaniel{Under editing.
+  Must move suggestions for fixes to future work.}
 
@@
 position on the route.
-\commentDaniel{Maybe this can be solved by issue \#33.}
 
@@
 
-We can choose different properties for \(\Enc*\).
+We can choose different properties for the encryption scheme, \(\Enc*\), used to 
+encrypt the message \(m\) in in \cref{sec:file_exchange}, depending on what 
+security properties we would like to achieve.
 What makes sense is to choose at least an authenticated encryption 
 scheme~\cite{AuthEncryption}.
+This would give confidentiality and integrity for the message, but if the first 
+and the last node on the route colludes, they can infer that Alice sent a 
+message to Bob.
 We could also choose a deniable encryption scheme~\cite{DeniableEncryption}, \eg 
@@
 provides \ac{DEN-SS}.
+
+If we choose \(\Enc*\) as a universal re-encryption~\cite{UniversalReencryption} 
+scheme (possibly composed with the deniable, authenticated encryption above), 
+then we could also provide bitwise unlinkability for the message between hops on 
+the route.
+(We would also need to modify \(\SPOR[\Fwd]\), \cref{SPORFwd}, to perform the 
+re-encryption of \(m\) before forwarding the message to the next hop.)
+Without universal re-encryption, the message \(m\) itself remains constant 
+throughout the route and thus constitutes a tag for tracking.
+As long as \emph{at least one node on the route is honest} and actually performs 
+the re-encryption --- there is no incentive for them to do this, as neither 
+Alice nor Bob can detect it without talking directly to each other to compare 
+the ciphertexts --- then the link between Alice and Bob is broken.
+(Alice and Bob are, of course, still susceptible to traffic analysis.)

### 2018-04-29 code/file_exchange/model.py
figure updated and code

@@ -151,24 +151,16 @@ class Model:
         for obs_id, obs_sequence in enumerate(sequence.T):
             obs = self.observations[obs_id]
             non_obs = "non_"+obs
-            print("Observation "+obs)
 
             # We bake a sequence with obs and non_obs names
             obs_sequence = [obs if o else non_obs for o in obs_sequence]
-            print("Sequence:")
-            print(obs_sequence)
-
-            print("A:")
-            print(self.A)
-
             states = []
-            print("B:")
+
             for s_id, state_name in enumerate(self.states):
                 obs_uniform_proba = pg.DiscreteDistribution({
                     obs: self.B[s_id, obs_id],
                     non_obs: 1 - self.B[s_id, obs_id]
                 })
-                print(self.B[s_id, obs_id])
                 states.append(pg.State(obs_uniform_proba, name=state_name))
 
             # And define a Pomegranates HMM with states obs and state non_obs
@@ -182,26 +174,20 @@ class Model:
             m.bake()
 
             # Let Pomegranate do the Baum-Welsh fitting
-            print("fitting...")
             m.fit([obs_sequence])
 
             # Incorporate the Pomegranate parameters back into our model
             A = m.dense_transition_matrix()
 
-            print("A:")
-            print(A)
             # Transition matrix
             self.A = A[:self.n_states, :self.n_states]
             # Initial probability
             self.init = A[self.n_states, :self.n_states]
             # Emission probabilities for each state
-            print("B:")
             for s_id in range(self.n_states):
                 self.B[s_id, obs_id] = \
                     m.states[s_id].distribution.parameters[0][obs]
-                print(self.B[s_id, obs_id])
-            print()
-        return
+        return self
 
 
 def get_default_model(observations):

### 2018-04-29 paper/security-analysis.tex
Writes up security analysis
I must write a system and adversary model, then adapt the security
analysis to them.

--- 2018-04-28 paper/security-analysis.tex
@@
 
-\commentDaniel{Under editing.}
+\commentDaniel{Under editing.
+  Must move suggestions for fixes to future work.}
 
-The message \(m\) remains the same from hop to hop during the onion routing, 
-hence a global observer can track the message through the network.
-The same applies if one node occurs more than once in a route, \eg in both 
-Alice's and Bob's part of the route.
+Alice wants to prevent Bob from learning which are her devices.
+Bob is allowed to infer the behaviour of devices in the Global Device Retinue, 
+but a file transfer from Alice should not give Bob any information about which 
+devices are Alice's.
 
-Since we have an in-package header, each node on the route can infer its 
-position on the route.
-\commentDaniel{Maybe this can be solved by issue \#33.}
+Bob constructs \iac{SPOR} route that he gives to Alice.
+This means that Alice does not learn any of Bob's destination devices.
+When Alice starts sending the message, she will not connect directly to the 
+device at the head of the route, since that might be Bob's device.
+Alice will construct her own \ac{SPOR} route.
+Thus Alice's devices are hidden from Bob's observation and vice versa.
 
-We can choose different properties for \(\Enc*\).
+Alice and Bob also want to prevent Carol and David to learn that Alice sent a 
+message to Bob.
+Alice and Bob construct their \ac{SPOR} route by including devices from the 
+Global Device Retinue, which also includes devices from Carol and David.
+If all devices on the route belong to Carol and David, then they can, of course, 
+learn that Alice sent a message to Bob.
+How well they can do if they do not control the entire route, depends on the 
+choice of the encryption scheme \(\Enc*\), used to encrypt the message \(m\) in 
+in \cref{sec:file_exchange}.
+
 What makes sense is to choose at least an authenticated encryption 
 scheme~\cite{AuthEncryption}.
-We could also choose a deniable encryption scheme~\cite{DeniableEncryption}, \eg 
-the one by \textcite{OTPKX} which is both deniable and authenticated and 
-provides \ac{DEN-SS}.
+(We could also choose a deniable encryption scheme~\cite{DeniableEncryption}, 
+\eg the one by \textcite{OTPKX} which is both deniable and authenticated and 
+provides \ac{DEN-SS}.)
+This would give confidentiality (or deniability) and integrity for the message, 
+but if the first and the last node belong to Carol and David, they can infer 
+that Alice sent a message to Bob.
+Note that as our in-package header is designed, each node on the route can infer 
+its position on the route \emph{relative to the destination}.
+(We discuss how to remedy this in \cref{conclusion}.)
+None of the nodes can know if they are the first node or not, unless they 
+collude with the previous node.
+The last node, however, can know for sure that the next hop is the destination, 
+but not who it belongs to.
+
+If we choose \(\Enc*\) as a universal re-encryption~\cite{UniversalReencryption} 
+scheme (possibly composed with the deniable, authenticated encryption above), 
+then we could also provide bitwise unlinkability for the message between hops on 
+the route.
+(We would also need to modify \(\SPOR[\Fwd]\), \cref{SPORFwd}, to perform the 
+re-encryption of \(m\) before forwarding the message to the next hop.)
+Without universal re-encryption, the message \(m\) itself remains constant 
+throughout the route and thus constitutes a tag for tracking.
+As long as \emph{at least one node on the route is honest}, \ie actually 
+performs the re-encryption --- there is no incentive for them to do this, as 
+neither Alice nor Bob can detect cheating without talking directly to each other 
+to compare the ciphertexts --- then the link between Alice and Bob is broken.
+This means that Carol and David must control all nodes on the route to link 
+Alice's transfer to Bob.
+
+Since Alice and Bob choose a new key for every file, we have forward secrecy 
+between files.
+\Eg an adversary who compromises either Alice or Bob cannot determine what Alice 
+sent to Bob, unless it is an ongoing transfer.

### 2018-04-29 paper/intro.tex

@@
 multiple kinds of computing devices that form a \textit{squad} of users'
-devices, named \textit{E-Squad} in the remainder of the
-paper. Leveraging on the help of their \textit{E-Squad}, users increase
+devices, named \squad in the remainder of the
+paper. Leveraging on the help of their \squad, users increase
 their expectations in terms of connectivity and interactions
@@
 device interactions \textit{in situ} to share digital content
-\cite{Oh:2017} among devices of their own \textit{E-Squad} or with the ones 
-from other users' \textit{E-Squad}. More broadly, users expect to share digital content,
+\cite{Oh:2017} among devices of their own \squad or with the ones 
+from other users' \squad. More broadly, users expect to share digital content,
 whatever the content location, from one
@@
 control history revealing what users share with whom and when.
-Users’ devices become tracking and/or monitoring \textit{E-Squad} that turn to
+Users’ devices become tracking and/or monitoring \squad that turn to
 be the best spy over users.
@@
 discouraging \cite{LeBlond:2013}; churn implies frequent
-reconstruction of routes, which is very expensive.
+reconstruction of routes, which is very expensive. In comparison, Tor
+\cite{Dingledine:2004}, one of the most popular anonymous network
+mitigate lack of performances of anonymity at the cost of a
+centralized design through the use of directory
+servers to advertise available trusted nodes to bootstrap Onion
+routes.
+
+In this paper, we introduce \name, Stateless Predictive Onion Routing
+for \squad, a novel approach to perform a decentralized, autonomous,
+and self-organizing file sharing among users' devices while preserving the users’ privacy
+in terms of data and metadata. We leverage on the latest works achieved
+in p2p systems, privacy and anonymity. The originality of our approach come
+from two key aspects. First, we consider proxemics relationships as a key enabler to initiate file
+transfers. Intimate distance among users enable them to share
+routing information out-of-band, e.g. from their
+\squad. Compared to the state of the art on p2p systems, with \name,
+users agree out-of-band to share a file but
+do not keep it available for anyone else in the future. Second, we
+rely on distributed machine learning technics to predict the
+availability of nodes. As such, \name provides optimized onion routes; it avoids routes
+reconstruction under churns.
+
+Our contributions are as follows: \david{please update}
+\begin{itemize}
+\item We showed the effectiveness of \iac{ANOBE} scheme by \textcite{ANOBE} 
+  to build a \ac{DeBE} as required by \name to
+  provide.... 
+\item A \squad overlay 
+\item Model the user’s behavior as a Hidden Markov Models (HMMs)
+\item SPOR provides stateless algorithms for the onion-routing.
+\item An evaluation testbed where each user’s behavior
+\end{itemize}
+
+In the following, we detail \name 's concepts and approach...
+
+% Cashmere: resilient anonymous routing.
+% Route fingerprinting in anonymous communications.
+% Bridging and fingerprinting:
+% Epistemic attacks on route selection
+% Breaking the collusion detection mechanism of morphmix
+% Denial of service or denial of security? How attacks
+% on reliability can compromise anonymity

### 2018-04-29 paper/related.tex
security discussion section

@@
 
-P2P file sharing has been researched extensively, with respect to aspects such as architecture (starting with the semi-centralized Napster), availability and replication (Gnutella), scalability (Bittorrent~\cite{bittorrent}), anonymity (Freenet~\cite{freenet}, TOR~\cite{Tor}, and distributed hash tables (DHT) such as CAN, Chord, Pastry, and Tapestry (see \cite{dhtchurn} for an overview).
+P2P file sharing has been researched extensively, with respect to aspects such as architecture (starting with the semi-centralized Napster), availability and replication (Gnutella), scalability (Bittorrent~\cite{bittorrent}), anonymity (Freenet~\cite{freenet}, TOR~\cite{Tor}), and distributed hash tables (DHT) such as CAN, Chord, Pastry, and Tapestry (see \cite{dhtchurn} for an overview).
 In contrast to our work, the main goal was to enable dissemination to many users who do not necessarily know each other in person.

### 2018-04-29 paper/security-analysis.tex
security discussion section

@@
-\section{Security analysis}%
-\label{SecurityAnalysis}
-
-\commentDaniel{Under editing.
-  Must move suggestions for fixes to future work.}
+\section{Security Discussion}%
+\label{SecurityDiscussion}
 
@@
 sent to Bob, unless it is an ongoing transfer.
+
+% \commentAL{To rewrite as real paragraphs} Future work and prospects:
+% \begin{itemize}
+% 	\item More in-depth knowledge of the user's behavior would allow to predict devices connections farther in the future;
+% 	\item Changing devices' asymmetric keys regularly would increase security.
+% 	Updating keys is easy in \name given the RPS that propagates new information to all nodes.
+% 	However, more reflection would be needed to avoid key updates breaking ongoing communications passing through the devices in question;
+% 	\item \name is not resilient to Byzantine nodes for now: malicious users could potentially make users pick Predictive Onion Routes that pass through them with a high probability, thus allowing the attacker to learn the file sender and receiver.
+To circumvent this, we would need to employ a secure Random Peer Sampling \cite{Jesi_Montresor_van_Steen_2010}, and prevent devices to lie on their probability of being online.
+
+% \end{itemize}
+
+We see two alternative paths for improving the header.
+First, we might be able to adapt the Sphinx~\cite{Sphinx} cryptographic packet 
+format to the routing of \(\SPOR\).
+Then we could achieve the properties of Sphinx and enjoy provable security.
+
+The second approach would be to use the technique by \textcite{PPACinPubFS}.
+They adapt \(\ANOBE\) in such a way that its ciphertexts decrypt to different 
+things for different recipients.
+This way we could have one ciphertext encrypted for all the alternative nodes 
+--- across layers.
+Then the ciphertext would decrypt to different plaintexts for nodes on different 
+layers in the route.
+This would hide the path length (constant-size ciphertexts by padding) and the 
+position of individual nodes.
+This approach would probably be the easiest, but would probably not provide all 
+the properties from Sphinx (\eg resistance to active tagging attacks and bitwise 
+unlinkability).

### 2018-04-29 paper/intro.tex

--- 2018-04-29 paper/intro.tex
@@
 discouraging \cite{LeBlond:2013}; churn implies frequent
-reconstruction of routes, which is very expensive.
+reconstruction of routes, which is very expensive. In comparison, Tor
+\cite{Dingledine:2004}, one of the most popular anonymous network
+mitigate lack of performances of anonymity at the cost of a
+centralized design through the use of directory
+servers to advertise available trusted nodes to bootstrap Onion
+routes.
+
+In this paper, we introduce SPORES, Stateless Predictive Onion Routing
+for E-Squads, a novel approach to perform a decentralized, autonomous, and self-organizing 
+file sharing among users' devices while preserving the users’ privacy
+in terms of data and metadata. The key originality of our approach is
+to consider that users share files in ...
+
+Our contributions are as follows:
+
+% Cashmere: resilient anonymous routing.
+% Route fingerprinting in anonymous communications.
+% Bridging and fingerprinting:
+% Epistemic attacks on route selection
+% Breaking the collusion detection mechanism of morphmix
+% Denial of service or denial of security? How attacks
+% on reliability can compromise anonymity

### 2018-04-29 paper/intro.tex
halfway through intro, continuing. Added a ref for the CIA/NSA quote in adrien, and a macro for my comments.

--- 2018-04-29 paper/intro.tex
@@
 % What's the problem?
-Following the Weiserian vision, nowadays, we are
-evolving in a new era of cooperation and interactions among humans.
-The exponential proliferation of devices connected to the Internet is
+Following Mark Weiser's vision, we are nowadays
+experiencing a new era of cooperation and interactions between humans.
+The exponential proliferation of connected devices is
 drastically impacting human experience and enhancing human
-interactions \cite{Dearman:2008, Oh:2017, Sohn:2008,Harper08}. It further opens new area of research such as
+exchanges~\cite{Dearman:2008, Oh:2017, Sohn:2008,Harper08}. This evolution has opened new areas of research such as
 \textit{proxemics} applied to ubiquitous computing
-\cite{Marquardt:2011}. Users are evolving in their social space with 
-multiple kinds of computing devices that form a \textit{squad} of users'
-devices, named \squad in the remainder of the
-paper. Leveraging on the help of their \squad, users increase
-their expectations in terms of connectivity and interactions
+\cite{Marquardt:2011}. When evolving in their social space, users can today rely on
+multiple kinds of computing devices that form a \textit{personal squad} of connected entities, or \squad as we shall call them in the remainder of the
+paper. Helped by their \squad, users
+have come to expect ever higher levels of connectivity and interaction
 possibilities. For instance, as users bring
-their devices close to one another, they expect to initiate cross
-device interactions \textit{in situ} to share digital content
+their devices close to one another, they expect to be able to initiate cross-device
+interactions \textit{in situ} in order to share digital content
 \cite{Oh:2017} among devices of their own \squad or with the ones 
 from other users' \squad. More broadly, users expect to share digital content,
-whatever the content location, from one
-device to another in a seamless manner \cite{Dearman:2008}, as they
+wherever the content, its sender, or its recipient might be located, from one
+arbitrary device to another in a seamless manner~\cite{Dearman:2008}, as they
 would have done in the old days with an USB key or with an email.
 
-From a technical perspective, one major trend to provide a seamless
-sharing of digital contents among users' devices is to leverage on the
-cloud, which acts as a key enabler for ubiquitous computing. Users' data
-are pushed online, into the cloud with either Dropbox, Google Docs,
-OneDrive, Amazon Drive, etc. to make it accessible anytime,
-anywhere to the users' devices.  In the last decades, a lot of research work has
-emerged to promote the use of this offloading strategy to overcome scarce
-resources of users' devices, and to provide an always-on availability
-\cite{Zhang:2014,Gordon:2012,Chun:2011}. It paves the way of different kind
-of clouds, such as mobile cloud computing, mobile-edge computing
-and/or fog computing, that aim to use the nodes from the cloud
-infrastructure that are the closest to end users
-for offloading with an improved quality of service and user experience.
+This thirst for seamless sharing explains the rise and ongoing popularity
+of personal sharing platforms such as Dropbox, Google Docs,
+OneDrive, Amazon Drive, etc. These solutions are able to share data on any device, between any user, almost
+anytime, anywhere. They achieve this feat by relying heavily on
+remotely hosted cloud services, which have now become a key enabler of ubiquitous ecosystems. 
+% argument: cloud -> danger, 
+%% From a technical perspective, one major trend to provide a seamless
+%% sharing of digital contents among users' devices is to leverage on the
+%% cloud, which acts as a key enabler for ubiquitous computing. Users' data
+%% are pushed online, into the cloud with either Dropbox, Google Docs,
+%% OneDrive, Amazon Drive, etc. to make it accessible anytime,
+%% anywhere to the users' devices.
+%% \commentFT{Removing the following, as seems to be a detour from main argument: \emph{In the last decades, a lot of research work has
+%% emerged to promote the use of this offloading strategy to overcome scarce
+%% resources of users' devices, and to provide an always-on availability
+%% \cite{Zhang:2014,Gordon:2012,Chun:2011}. It paves the way of different kind
+%% of clouds, such as mobile cloud computing, mobile-edge computing
+%% and/or fog computing, that aim to use the nodes from the cloud
+%% infrastructure that are the closest to end users
+%% for offloading with an improved quality of service and user experience.}}
+%% Hence, the cloud, and its variants constitute a perfect complement
+%% to perform storage and computation on behalf of the resource
+%% constrained devices.
+Unfortunately, this reliance on the cloud comes at a strong price: 
+%% users and their devices become totally tethered to the cloud ecosystem and its providers. As
+%% a direct consequence,
+users lose control over their own data, which become distributed over
+multiple data centers, often in foreign jurisdictions, making it difficult for most users to grasp, review, and assess, the privacy, and
+confidentiality guaranties they can expect. In practice, user data hosted in the cloud is routinely harvested, often without explicit
+consent, either by cloud providers or third parties.
 
-Hence, the cloud, and its variants constitute a perfect complement
-to perform storage and computation on behalf of the resource
-constrained devices. However, this cloud reliance comes at a strong price:
-devices become totally tethered to a cloud ecosystem and provider. As
-a direct consequence, users lose the control over their own data as it is
-stored and spanned into multiple foreign data centers. Hence, it becomes difficult at 
-the legal level to assess the privacy, and
-confidentiality delivered to the end users. Further, at the practical
-level, users' data can be harvested on their behalf, and without their
-consent, by either the cloud provider or third parties.
-Data sent by the user can be encrypted, but it is not enough
-\cite{granick_2017, HooffLZZ15, HarnikPS10}.  As stated by a famous quotation from
-NSA: "we kill people based on metadata''. Metadata such as the users'
+Although data encryption is often proposed as a first line of defense for cloud-hosted data, it is unfortunately  insufficient, because it does not protect meta-data information~\cite{granick_2017, HooffLZZ15, HarnikPS10}.
+This turns out to be a critical limitation, as famously emphasized by a former NSA and CIA director: "We kill people based on metadata.''~\cite{NaughtonTheGuardian2016} Metadata such as a user'
 location and activity can be still tracked, including the access
-control history revealing what users share with whom and when.
-Users’ devices become tracking and/or monitoring \squad that turn to
+control history revealing what each user shared with whom and when.
+User devices become tracking and/or monitoring \squad that turn to
 be the best spy over users.

### 2018-04-29 paper/conclusion.tex
Writes up security analysis
I must write a system and adversary model, then adapt the security
analysis to them.

@@
-\section{Conclusion and Future Work}
+\section{Conclusion and Future Work}%
+\label{conclusion}
 
@@
 \(\SPOR\) as a step toward provable security.
-
-% \commentAL{To rewrite as real paragraphs} Future work and prospects:
-% \begin{itemize}
-% 	\item More in-depth knowledge of the user's behavior would allow to predict devices connections farther in the future;
-% 	\item Changing devices' asymmetric keys regularly would increase security.
-% 	Updating keys is easy in \name given the RPS that propagates new information to all nodes.
-% 	However, more reflection would be needed to avoid key updates breaking ongoing communications passing through the devices in question;
-% 	\item \name is not resilient to Byzantine nodes for now: malicious users could potentially make users pick Predictive Onion Routes that pass through them with a high probability, thus allowing the attacker to learn the file sender and receiver.
-To circumvent this, we would need to employ a secure Random Peer Sampling \cite{Jesi_Montresor_van_Steen_2010}, and prevent devices to lie on their probability of being online.
-
-% \end{itemize}
-
-We see two alternative paths for improving the header.
-First, we might be able to adapt the Sphinx~\cite{Sphinx} cryptographic packet 
-format to the routing of \(\SPOR\).
-Then we could achieve the properties of Sphinx and enjoy provable security.
-
-The second approach would be to use the technique by \textcite{PPACinPubFS}.
-They adapt \(\ANOBE\) in such a way that its ciphertexts decrypt to different 
-things for different recipients.
-This way we could have one ciphertext encrypted for all the alternative nodes 
---- across layers.
-Then the ciphertext would decrypt to different plaintexts for nodes on different 
-layers in the route.
-This would hide the path length (constant-size ciphertexts by padding) and the 
-position of individual nodes.
-This approach would probably be the easiest, but would probably not provide all 
-the properties from Sphinx (\eg resistance to active tagging attacks and bitwise 
-unlinkability).

### 2018-04-29 paper/related.tex

--- 2018-04-29 paper/related.tex
@@
 
-P2P file sharing has been researched extensively, with respect to aspects such as architecture (starting with the semi-centralized Napster), availability and replication (Gnutella), scalability (Bittorrent~\cite{bittorrent}), anonymity (Freenet~\cite{freenet}, TOR~\cite{Tor}, and distributed hash tables (DHT) such as CAN, Chord, Pastry, and Tapestry (see \cite{dhtchurn} for an overview).
+Mixnets~\cite{Chaum:198} are perhaps the first solution to turn to for sending content from A to B anonymously.
+In our context, however, they are less suitable due to their reliance on mix servers, the limited protection against statistical inference possible for even a perfect mixnet given the multiple varying sources and destinations of our use case, and the delay they would add due to batching.
+We thus decided for an approach based on onion routing.
+
+P2P file sharing has been researched extensively, with respect to aspects such as architecture (starting with the semi-centralized Napster, then decentralized Gnutella), availability and replication~\cite{replica}, scalability (Bittorrent~\cite{bittorrent}), anonymity (Freenet~\cite{freenet}, TOR~\cite{Tor}), and distributed hash tables (DHT) such as CAN, Chord, Pastry, and Tapestry (see \cite{dhtchurn} for an overview).
 In contrast to our work, the main goal was to enable dissemination to many users who do not necessarily know each other in person.

### 2018-04-29 paper/security-analysis.tex

@@
 its position on the route \emph{relative to the destination}.
-(We discuss how to remedy this in \cref{conclusion}.)
+(We discuss how to remedy this below.)
 None of the nodes can know if they are the first node or not, unless they 
@@
 
+\subsection{Limitations}
+from mails:  - Route fingerprinting in anonymous communications.
+
+It depends on the random peer sampling I suppose. And I have no clue 
+about how that one works. Adrien referred to a paper by Anne-Marie.
+
+If I were to guess, I'd say: if Anne-Marie's RPS protocol is Byzantine 
+fault tolerant, maybe; otherwise, we're most likely screwed.
+
+> - Bridging and fingerprinting: Epistemic attacks on route selection
+
+I'd say the same as above. It's about peer selection.
+
+> - Breaking the collusion detection mechanism of morphmix
+
+We don't do any collusion detection, so I'd say we're vulnerable. We 
+assume we choose nodes uniformly at random, so colluding nodes have 
+uniform probability of success --- but that falls back on the RPS and 
+Anne-Marie's paper. So maybe or screwed.
+
+> - Denial of service or denial of security? How attacks on reliability can
+> compromise anonymity
+
+After just reading the abstract, most likely vulnerable. But thanks to 
+our stateless design we don't have to do retransmission the whole way, 
+as might be the case for active circuits --- only the node who 
+experience the failure going forward will need to retransmit. (Thanks 
+Adrien for insisting on creating a route back for the ACK ;-)) So we 
+might not be in as bad a position as other systems, it'll take more 
+rounds of attack to break it --- but I'm quite sure it will break.
+
+But in general, these all face global and possibly malicious 
+adversaries. We don't have that in our adversary model. If everyone 
+colludes against Alice and Bob in our setting, they're screwed.
+
+It's basically impossible to remain anonymous against the global 
+adversary (statistical inference, paper by Danezis) unless Alice sends a 
+message to everyone whenever she wants to send a message to Bob. 
+Basically the anonymous communication community is converging on methods 
+like Loopix and HORNET --- have enough throughput so that the global 
+adversary is overwhelmed with data. (Tor is too slow.)
+
+\subsection{Future Work}
 % \commentAL{To rewrite as real paragraphs} Future work and prospects:

### 2018-04-29 paper/conclusion.tex
conclusion \name, humble narrative

@@
 
-We presented \(\SPOR\) that, in analogy to its biological
+We presented \name that, in analogy to its biological
 counterparts, enables dissemination under unfavorable conditions. More
@@
 privacy perspective, we were guided by the properties of
-TOR~\cite{Tor}, which we modified to a stateless protocol to
+TOR~\cite{Tor}, which we used to provide a modicum of privacy for this
+first investigation of feasibility of file-sharing between two users'
+squads of devices and modified to a stateless protocol to
 accommodate unreliable nodes. While we took the first steps toward
@@
 and the side effect of enabling more local TOR routing (for example,
-keeping routes inside a country) do not compromise security. On a
+keeping routes inside a country) do not compromise security. Another
+consideration is the nature of the traffic in this scenario and the
+limits of protection against statistical inference. On a
 related note, it would be interesting to adapt the
 Sphinx~\cite{Sphinx} cryptographic packet format to the routing of
-\(\SPOR\) as a step toward provable security.
+\name as a step toward provable security.

### 2018-04-29 paper/message-passing-design.tex
Edits use of \SPOR and \ac{SPOR}

--- 2018-04-28 paper/message-passing.tex
@@
+\subsection{Message Passing through \acl*{SPOR}}%
+\label{sec:message_passing}
+
+We have \iac{SPOR} scheme, which provides probabilistically onion-routed message 
+passing.
+Instead of providing only one address per hop in the route (as in \eg 
+Tor~\cite{Tor} or remailers), \ac{SPOR} provides several alternatives for the 
+next hop depending on their probability of being online.
+To do this, the \ac{SPOR} scheme provides stateless algorithms for the 
+onion-routing.
+
 \NewScheme{\SPOR}{SPOR}
-
-\subsection{Message Passing: Stateless Predictive Onion Routing \(\SPOR\)}
-
 \NewAlgorithm{\Send}{Send}
@@
 
-We have the Stateless Predictive Onion Routing scheme, \SPOR, which provides 
-probabilistically onion-routed message passing.
-Instead of providing only one address per hop in the route (as in \eg 
-Tor~\cite{Tor}), \(\SPOR\) provides several alternatives for the next hop 
-depending on their probability of being online.
-To do this, \(\SPOR\) provides stateless algorithms for the onion-routing.
-
-\(\SPOR\) provides three algorithms: \(\SPOR[\Send]\) (\cref{SPORSend}), 
-\(\SPOR[\Fwd]\) (\cref{SPORFwd}) and \(\SPOR[\Recv]\) (\cref{SPORRecv}).
+The \(\SPOR\) scheme provides three algorithms: \(\SPOR[\Send]\) 
+(\cref{SPORSend}), \(\SPOR[\Fwd]\) (\cref{SPORFwd}) and \(\SPOR[\Recv]\) 
+(\cref{SPORRecv}).
 Say Alice wants to send a message \(m\) to Bob.

### 2018-04-29 paper/design.tex
Replaces some of Adrien's PORs with \acp{SPOR}

@@
 PORs are our adaptation of onion routes, allowing secret communication between two entities despite the unreliability of the nodes that relay their messages.
-From there on, Alice and Bob add the POR information to the headers of their subsequent file exchange messages, such that the file transfer remains secret to anyone but them.
+From there on, Alice and Bob add the \ac{SPOR} route information to the headers 
+of their subsequent file exchange messages, such that the file transfer remains 
+secret to anyone but them.
 
@@
 %\includegraphics[width=0.9\columnwidth]{figures/outline.pdf}
-\caption{\label{fig:outline}Outline of \name's components.
-Users squads of devices are circled in gray.
-From top to bottom: a user's devices collaborate through the Squad Overlay; online devices globally share information about them to random peers; using the two above overlays allows for the creation or Predictive Onion Routes (PORs) between sets of devices; secure file exchange between users is enabled by PORs.}
+\caption{\label{fig:outline}Outline of \name's components. Users squads of 
+  devices are circled in gray. From top to bottom: a user's devices collaborate 
+  through the Squad Overlay; online devices globally share information about 
+  them to random peers; using the two above overlays allows for the creation of 
+  \ac{SPOR} routes between sets of devices; secure file exchange between users 
+  is enabled by \ac{SPOR}.}
 \end{figure}

### 2018-04-29 paper/intro.tex
pass on intro. Contributions still left to do

@@
 interactions \textit{in situ} in order to share digital content
-\cite{Oh:2017} among devices of their own \squad or with the ones 
-from other users' \squad. More broadly, users expect to share digital content,
+\cite{Oh:2017} between devices of their own \squad or with those of other users' \squad. More broadly, users expect to share digital content,
 wherever the content, its sender, or its recipient might be located, from one
@@
 of personal sharing platforms such as Dropbox, Google Docs,
-OneDrive, Amazon Drive, etc. These solutions are able to share data on any device, between any user, almost
+OneDrive, Amazon Drive, etc. These solutions are able to share data between any device, any user, almost
 anytime, anywhere. They achieve this feat by relying heavily on
-remotely hosted cloud services, which have now become a key enabler of ubiquitous ecosystems. 
+\emph{remote cloud services}, which have now become a key enabler of ubiquitous ecosystems. 
 % argument: cloud -> danger, 
@@
 %% a direct consequence,
-users lose control over their own data, which become distributed over
-multiple data centers, often in foreign jurisdictions, making it difficult for most users to grasp, review, and assess, the privacy, and
+users lose control over their own data, which is distributed over
+multiple data centers, often in foreign jurisdictions, making it difficult for most users to grasp, review, and assess the privacy, and
 confidentiality guaranties they can expect. In practice, user data hosted in the cloud is routinely harvested, often without explicit
@@
 
-Although data encryption is often proposed as a first line of defense for cloud-hosted data, it is unfortunately  insufficient, because it does not protect meta-data information~\cite{granick_2017, HooffLZZ15, HarnikPS10}.
-This turns out to be a critical limitation, as famously emphasized by a former NSA and CIA director: "We kill people based on metadata.''~\cite{NaughtonTheGuardian2016} Metadata such as a user'
+Although data encryption is often proposed as a first line of defense for cloud-hosted data, it is unfortunately  insufficient~\cite{granick_2017, HooffLZZ15, HarnikPS10}. Metadata such as a user'
 location and activity can be still tracked, including the access
 control history revealing what each user shared with whom and when. 
+%  because it does not protect meta-data information
+This turns out to be a critical limitation, as famously emphasized by a former NSA and CIA director: "We kill people based on metadata.''~\cite{NaughtonTheGuardian2016} 
 User devices become tracking and/or monitoring \squad that turn to
@@
 
-Constructing a system that provides anonymous communication is a very
-challenging issue. The last decades, we have witnessed a
- huge set of attempts at building privacy preserving and anonymous p2p
- networks \cite{Clarke:2001, Gnunet2002, Freedman:2002, Nambiar:2006,
-   Rennhard:2002}. They are mainly based on onion
- routing concepts \cite{Chaum:1981}, with some improvements to perform node
- discovery in a distributed manner, which are otherwise
-centralized in traditional onion routing schemes. However, due to high
-churn of peer-to-peer networks, performance of these systems is
-discouraging \cite{LeBlond:2013}; churn implies frequent
-reconstruction of routes, which is very expensive. In comparison, Tor
-\cite{Dingledine:2004}, one of the most popular anonymous network
-mitigate lack of performances of anonymity at the cost of a
-centralized design through the use of directory
-servers to advertise available trusted nodes to bootstrap Onion
+Constructing a system that provides fully anonymous content sharing is highly
+challenging. The last two decades have witnessed many attempts at building privacy preserving and anonymous P2P data-sharing
+networks~\cite{Clarke:2001,Gnunet2002,Freedman:2002,Nambiar:2006,Rennhard:2002}.
+These solutions typically leverage \emph{onion
+ routing}~\cite{Chaum:1981}, with some improvements to perform node
+ discovery in a distributed manner, a step that is otherwise
+centralized in traditional onion routing schemes. However, because of the high
+churn typically experienced by P2P networks, the performance of these systems is
+discouraging~\cite{LeBlond:2013}; churn causes routes to be frequently
+reconstructed, which is very expensive. By contrast, Tor
+\cite{Dingledine:2004}, one of the most popular anonymous networks,
+trades lower anonymity guaranties for a much better performance. Tor's lower protection arises from
+a partially centralized design that hinges on a set of \emph{directory
+servers}, which are used to advertise trusted nodes that are available to bootstrap onion
 routes.
 
-In this paper, we introduce \name, Stateless Predictive Onion Routing
-for \squad, a novel approach to perform a decentralized, autonomous,
-and self-organizing file sharing among users' devices while preserving the users’ privacy
-in terms of data and metadata. We leverage on the latest works achieved
-in p2p systems, privacy and anonymity. The originality of our approach come
-from two key aspects. First, we consider proxemics relationships as a key enabler to initiate file
-transfers. Intimate distance among users enable them to share
+In this paper, we demonstrate how good performance can be reconciled with strong privacy protection in data-sharing systems. We present \name{}, a novel fully decentralized, autonomous,
+% approach that provides a 
+and self-organizing file sharing service between the \squad of different users that preserves user privacy
+in terms of both data \emph{and} metadata. Our proposal hinges on two key ideas: \emph{First}, we consider proxemics relationships as a key enabler to initiate file
+transfers. Close distance among users enable them to share
 routing information out-of-band, e.g. from their
-\squad. Compared to the state of the art on p2p systems, with \name,
-users agree out-of-band to share a file but
-do not keep it available for anyone else in the future. Second, we
-rely on distributed machine learning technics to predict the
-availability of nodes. As such, \name provides optimized onion routes; it avoids routes
-reconstruction under churns.
+\squad. In contrast to state-of-the-art P2P systems, users agree in \name out-of-band to share a file, but
+do not keep it available for anyone else in the future. \emph{Second}, we
+rely on distributed machine learning techniques to predict the future
+availability of user devices, and use this ability to implement a \emph{probabilistic predictive onion routing} mechanism.
+The predictive nature of our routing allows us to overcome the inherent fragility of pure P2P data-sharing schemes.
+
+%% In this paper, we introduce \name{}, a novel approach to perform a decentralized, autonomous,
+%% and self-organizing file sharing among users' devices while preserving the users’ privacy
+%% in terms of data and metadata. We leverage on the latest works achieved
+%% in p2p systems, privacy and anonymity. The originality of our approach come
+%% from two key aspects. First, we consider proxemics relationships as a key enabler to initiate file
+%% transfers. Intimate distance among users enable them to share
+%% routing information out-of-band, e.g. from their
+%% \squad. Compared to the state of the art on p2p systems, with \name,
+%% users agree out-of-band to share a file but
+%% do not keep it available for anyone else in the future. Second, we
+%% rely on distributed machine learning technics to predict the
+%% availability of nodes. As such, \name provides optimized onion routes; it avoids routes
+%% reconstruction under churns.
 

### 2018-04-29 paper/squad-overlay-design.tex
up

@@
-\subsection{The Squad Overlay} 
+\subsection{The E-Squad Overlay} 
 \label{sec:squad_overlay}
@@
 %By sharing information among themselves, a user's devices (her \emph{squad}) can model her behavior.
-Our goal here is that each online device predicts the probability that it stays online in the near future.
+Our key objective is to enable each online device to predict its probability to stay online in the near future.
 This probability will later be used to create Probabilistic Onion Routes (POR).
-A device's connection depends on the activity of its user; thus, a user's devices (her \emph{squad}) want to predict her future behavior.
+A device's connection depends on the activity of its user; thus, a user's devices (her \squad}) want to predict her future behavior.
 
@@
 Online devices want to know whether they are likely to stay online in the near future.
+
 Taken separately, each device only knows local information: when Alice used it, and maybe mobility information if it is mobile.
@@
 
-The Squad Overlay leverages on a probabilistic dissemination protocol, \textsc{Sprinkler}~\cite{luxey:hal-01704172}, that does just that: 
+The \squad Overlay leverages on a probabilistic dissemination protocol, \textsc{Sprinkler}~\cite{luxey:hal-01704172}, that does just that: 
 it allows one's devices to inform one another every time the user performs an action.
@@
 devices let each other know of what they have missed while offline.
-We thus employ \textsc{Sprinkler} to disseminate the user's activity to its squad.
+We thus employ \textsc{Sprinkler} to disseminate the user's activity to its \squad.
 
@@
 
-\paragraph*{Other uses of the Squad Overlay} In addition to user's behavior, devices use th Squad Overlay for several purposes.
+\paragraph*{Other uses of the Squad Overlay} In addition to user's behavior, devices use th \squad Overlay for several purposes.
 Firstly, they share files location: when Alice wants to share a file $f$ that resides on her home computer, using her smartphone as the exchange initiator, her smartphone knows where $f$ is located and can create the route accordingly.
@@
 
+\david{the following paragraph is not clear at all }
 \name knows two message types (as will be covered in~\ref{sec:file_exchange}): file chunk, and acknowledgment.
 Alice typically wants to receive a file on one particular device; respectively, only one of her devices is interested in acknowledging reception of the file chunks it is sending.
+\david{what is the relationship with \squad Overlay?}
 However, \name allows all squad members to receive messages destined to Alice.
 Thus, the third complementary purpose of the Squad Overlay is to relay messages among the squad: when a message is not destined to the device that received it, the receiver forwards the message to its final destination.
+\david{and then?}
 

### 2018-04-29 paper/abstract.tex
Fixes blank line bug in abstract
pass on abstract. Tightening up. Also reformatted authors to take less space.

--- 2018-04-27 paper/abstract.tex
@@
 % what remains to be done?
-
+%
 %abstract
 %problem/topic
-This paper presents privacy-preserving file sharing without relying on any third-party storage such as cloud services or peers.
-
+This paper proposes a novel fully-decentralized privacy-preserving file sharing service that eschews any third-party storage or any centralized bootstrapping service.
 %research gap
-Centralized file-sharing systems, i.e.
-cloud storage such as Dropbox require trust in the service provider and can be monitored.
-P2P file-sharing relies on replicas on other people's machines.
-We are interested in minimizing trust needed in other systems and preserving the user's privacy in terms of data and metadata, i.e.
-what they share with whom and when.
-
+Cloud-based file-sharing systems such as Dropbox require trust in the service provider and can be monitored, even when their data is encrypted.
+Private peer-to-peer (P2P) solutions are either particularly inefficient, or must rely on a fixed set of trusted servers for bootstrapping purposes, which limit their level of protection.
+% We are interested in minimizing the trust needed in other systems and preserving the users' privacy in terms of data and metadata, what they share with whom and when.
 %why now
-Nowadays, many people use multiple devices and it has thus become possible to benefit from p2p technology for one's own devices alone and thus reducing one's exposure to security and privacy vulnerabilities and threats from third parties.
-
+% Nowadays, many people use multiple devices and it has thus become possible to benefit from P2P technology for one's own devices alone, thereby reducing one's exposure to security and privacy threats from third parties.
 %approach
-We enable onion routing to cope with probabilistic availability of nodes, informed by peer sampling and Hidden Markov Model predictions.
-
+In this paper, we demonstrate that an efficient and strongly private fully-decentralized data-sharing solution is possible.
+Our proposal combines onion routing with probabilistic node selection, informed by peer sampling and Hidden Markov Model predictions for node availability.
 %findings/contributions:
-We benefit from sender-receiver anonymity properties provided by onion routing.
-We show that even a relatively naive prediction model suffices to share files despite unreliable availability of individual nodes.
-The same model can potentially be applied for better informed churn handling in other p2p systems.
-In the case of TOR-like onion routing systems for anonymity, our solution allows the system to include unreliable nodes and take advantage of locality.
+Our solution benefits from sender-receiver anonymity properties provided by onion routing. %% to protect user privacy in decentralized file sharing.
+We show that even a relatively naive prediction model suffices to share files despite the unreliable availability of individual nodes.
+%% The same model can potentially be applied for better-informed churn handling in other p2p systems.
+In the case of onion routing systems for anonymity,
+Our solution allows the system to include unreliable nodes and take advantage of locality, neither of which is currently provided in TOR.

### 2018-04-29 paper/intro.tex
pass on abstract. Tightening up. Also reformatted authors to take less space.

@@
 interactions \textit{in situ} in order to share digital content
-\cite{Oh:2017} between devices of their own \squad or with those of other users' \squad. More broadly, users expect to share digital content,
+\cite{Oh:2017} between devices of their own \squad or with those of other users' \squad{}\emph{s}. More broadly, users expect to share digital content,
 wherever the content, its sender, or its recipient might be located, from one
@@
 % approach that provides a 
-and self-organizing file sharing service between the \squad of different users that preserves user privacy
+and self-organizing file sharing service between the \squad{}\emph{s} of different users that preserves user privacy
 in terms of both data \emph{and} metadata. Our proposal hinges on two key ideas: \emph{First}, we consider proxemics relationships as a key enabler to initiate file

### 2018-04-29 paper/evaluation.tex

@@
 }
+\end{figure}
 
@@
 
+\subsection{Predictive Onion Routes creation} % (fold)
+\label{sub:predictive_onion_routes_creation}
+
+\begin{figure}
+\centering
+\includegraphics[width=0.8\columnwidth]{figures/nodes_per_layer_vs_theta.pdf}
+\caption{\label{fig:nodes_per_layer_vs_theta}Number of nodes per layer of Predictive Onion Route as a function of the parameter $\theta$ (the maximal probability that all nodes in a layer fail at once).
+We see that the number of nodes exponentially decreases a we relax the $\theta$ constraint.}
 \end{figure}
 
-% subsubsection simulating_user_behavior (end)
-
-% subsection evaluation_testbed (end)
+\begin{figure}
+\includegraphics[width=\columnwidth]{figures/success_rate_vs_t.pdf}
+\caption{\label{fig:success_rate_vs_t}Availability rate of routes as a function of the time since the route establishment, for several values of the parameters $\theta$ (the maximal probability that all nodes in a layer fail at once) and $L$ (the number of layers in the route).}
+\end{figure}

### 2018-04-30 paper/evaluation.tex
details on plots

@@
 
+In figure \ref{fig:nodes_per_layer_vs_theta} and \ref{fig:success_rate_vs_t}, we computed 10 experiments per set of settings.
+$\theta$ is the threshold of the probability that all nodes fail at once: we keep adding nodes to a layer until the layer's probability is below $\theta$. 
+It takes the following values: $[0.1, 0.01, 0.001, 0.0001]$.
+$L$, the number of layers constituting a route, takes the following values: $[3, 5, 7]$.
+The time since route establishment goes from 1 to 10 with  unit step. 
+An experiment consisted in $L*5$ users, where we randomly picked pairs of users to compute 20 routes.
+Hence, each point in figure~\ref{fig:nodes_per_layer_vs_theta} is the average of 3000 layers size; 
+each point in figure~\ref{fig:nodes_per_layer_vs_theta} is the availability rate over 200 routes.
+
 \begin{figure}

### 2018-04-30 paper/system-model.tex
Renames privacy.tex to system-model.tex
Writes up possible very simple system, adversary model

--- 2018-04-03 paper/privacy.tex
@@
-\section{Privacy}%
-\label{Privacy}
+\section{System model, adversary model and desired privacy properties}%
+\label{system-model}
 
-We care about
-\dots
+Our system consists of users' devices.
+Each device can communicate with any other device that it knows the address for.
+We assume that each user has configured its own devices to know which other 
+devices belong to the same user, \ie the \squad.
+Thus the devices only knows the mapping from devices to users for the devices in 
+the own \squad.
+
+Alice wants to share a file with Bob.
+In the cloud setting, she can instruct the cloud service to make one of her 
+files available to Bob.
+This provides some privacy properties which we have to consider when changing 
+the setting to that of \ac{P2P}~\cite{DevilInMetadata}.
+We can see that in this scenario, Alice and Bob are the only ones who learn 
+about Alice sharing a file with Bob (except for the cloud provider).
+We can also see that Alice and Bob learn nothing about each others' devices, \ie 
+they cannot map any device as belonging to each other.
+(Of course, the cloud provider learns this.)
+
+When changing from the cloud setting to \ac{P2P}, we want to keep the privacy 
+that Alice and Bob enjoy but remove the cloud provider to increase privacy 
+further.
+\Ie we want to protect from friendly surveillance~\cite{FriendlySurveillance} in 
+an honest-but-curious setting.
+
+We will not consider a global network adversary, only subsets of colluding 
+parties.
+We know that it is notoriously difficult to achieve security against a global 
+network adversary~\cite{SystemsForAnonymousCommunication}.

### 2018-04-30 paper/security-discussion.tex
Renames security-analysis (file) to security-discussion

--- 2018-04-29 paper/security-analysis.tex
@@
 \section{Security Discussion}%
-\label{SecurityDiscussion}
+\label{security-discussion}
 
-Alice wants to prevent Bob from learning which are her devices.
+Alice wants to prevent Bob from learning which are her devices (as defined in 
+\cref{system-model}).
 Bob is allowed to infer the behaviour of devices in the Global Device Retinue, 
@@
 Thus Alice's devices are hidden from Bob's observation and vice versa.
+If we assume that Alice and Bob can sample their nodes uniformly randomly from 
+the \emph{entire} Global Device Retinue (we will return to this assumption 
+below), then their probability of successful attack is proportional to their 
+size in the network, \ie \(\frac{|D_i|}{|D|}\), for \(i\in \{a,b\}\).
 
 Alice and Bob also want to prevent Carol and David to learn that Alice sent a 
-message to Bob.
+message to Bob (as defined in \cref{system-model}).
 Alice and Bob construct their \ac{SPOR} route by including devices from the 
@@
 How well they can do if they do not control the entire route, depends on the 
-choice of the encryption scheme \(\Enc*\), used to encrypt the message \(m\) in 
-in \cref{sec:file_exchange}.
+choice of the encryption scheme \(\Enc*\), used to encrypt the message \(m\) 
+(see \cref{sec:file_exchange}).
 
@@
 (We discuss how to remedy this below.)
-None of the nodes can know if they are the first node or not, unless they 
-collude with the previous node.
+None of the nodes can know if the previous node is the originator or not, unless 
+they collude with the previous node.
 The last node, however, can know for sure that the next hop is the destination, 
@@
 Alice's transfer to Bob.
+As above, if we assume uniformly random peer sampling, then Carol and David's 
+success probability is proportional to their joint size in the network.
 
-Since Alice and Bob choose a new key for every file, we have forward secrecy 
-between files.
+This means that under the assumption of uniformly random peer sampling, we 
+achieve the properties we outlined in \cref{system-model}.
+Additionally, since Alice and Bob choose a new key for every file, we have 
+forward secrecy between files.
 \Eg an adversary who compromises either Alice or Bob cannot determine what Alice 
@@
 
-\subsection{Limitations}
-from mails:  - Route fingerprinting in anonymous communications.
+\subsection{Limitations}%
+\label{security-limitations}
+from mails:
+
+- Route fingerprinting in anonymous communications.
 
@@
 as might be the case for active circuits --- only the node who 
-experience the failure going forward will need to retransmit. (Thanks 
-Adrien for insisting on creating a route back for the ACK ;-)) So we 
-might not be in as bad a position as other systems, it'll take more 
-rounds of attack to break it --- but I'm quite sure it will break.
+experience the failure going forward will need to retransmit. (Thanks Adrien for 
+insisting on creating a route back for the ACK ;-) So we might not be in as bad 
+a position as other systems, it'll take more rounds of attack to break it --- 
+but I'm quite sure it will break.
 
@@
 \subsection{Future Work}
+%
 % \commentAL{To rewrite as real paragraphs} Future work and prospects:

### 2018-04-30 paper/squad-overlay-design.tex
Bugfix: too many }
evaluation of POR done

@@
 This probability will later be used to create Probabilistic Onion Routes (POR).
-A device's connection depends on the activity of its user; thus, a user's devices (her \squad}) want to predict her future behavior.
+A device's connection depends on the activity of its user; thus, a user's devices (her \squad) want to predict her future behavior.
 
@@
 \paragraph*{Predicting future behavior} 
+\label{para:predicting future behavior}
 As already stated, devices want to predict whether they are likely to be connected in the near future.
@@
 It is the sum of the probabilities, for each state $s$, that the user switches to $s$ and uses her device.
-\commentAL{Following maybe not needed if we only use $t+1$:}
 Recursively, predicting $i$ turns in advance follows the same logic:
@@
 
-We show in section~\ref{sub:devices_predictions_of_the_user_behavior} that $P\left[ d \in O_{t+1} \mid S_{t} = s \right] \simeq P\left[ d \in O_{t+i} \mid S_{t} = s \right]$. 
-For that reason, devices only compute the prediction of their connection at $t+1$, that is considered a good enough estimator of their connection state ``in the near future''.
+We show in section~\label{sub:predictive_onion_routes_creation} that the prediction of their availability at $t+1$ is a good enough estimator of their connection state at $t+i$.
+For that reason, devices only share $P\left[ d \in O_{t+1} \mid S_{t} = s \right]$ with other devices for PORs creation.
 

### 2018-04-30 code/routes/device.py

@@ -58,6 +58,22 @@ class Device:
         #     print("Expiration time:", expiration_limit)
         #     print(self.global_view.view)
 
+    def build_random_route(self, nodes_per_layer):
+        n_layers = len(nodes_per_layer)
+        route = [pd.DataFrame() for _ in range(n_layers)]
+        view = self.peers_view.view.copy()
+
+        for l_id in range(n_layers):
+            while len(route[l_id]) < nodes_per_layer[l_id]:
+                if len(view) == 0:
+                    raise Exception("Damn, son")
+                # Pick a device from view without replacement
+                d = view.iloc[np.random.choice(len(view))]
+                route[l_id] = route[l_id].append(d)
+                view.drop(d.name, inplace=True)
+
+        return route
+
     def build_route(self, role):
         if role == "receiver":
             # 2 layers planned in advance

### 2018-04-30 paper/message-passing-design.tex
Adds frames around figures
up

@@
-\subsection{Message Passing through \acl*{SPOR}}%
+\NewScheme{\SPOR}{SPOR}
+
+\subsection{Message Passing through Predictive Onion Routes (PORs)}
 \label{sec:message_passing}
 
-We have \iac{SPOR} scheme, which provides probabilistically onion-routed message 
-passing.
-Instead of providing only one address per hop in the route (as in \eg 
-Tor~\cite{Tor} or remailers), \ac{SPOR} provides several alternatives for the 
-next hop depending on their probability of being online.
-To do this, the \ac{SPOR} scheme provides stateless algorithms for the 
-onion-routing.
-
-\NewScheme{\SPOR}{SPOR}
 \NewAlgorithm{\Send}{Send}
@@
 
-The \(\SPOR\) scheme provides three algorithms: \(\SPOR[\Send]\) 
-(\cref{SPORSend}), \(\SPOR[\Fwd]\) (\cref{SPORFwd}) and \(\SPOR[\Recv]\) 
+\david{each protocol should be explained individually}
+
+In contrast to Tor~\cite{Tor} that provides only one address per hop
+in the route, \name provides for each layer of the onion several
+alternatives for the next hop in the route depending on their
+probability of being online. To implement our  probabilistic
+predictive onion routing mechanism, \name defined three different algorithms to
+receive, send and forward messages among users' \squad. For instance,
+if Alice wants to send a message \(m\) to Bob, Bob uses the
+\(\SPOR[\Recv]\) algorithm (See \cref{SPORRecv}) to create a probabilistic onion route \(H_\rdv\) from
+ a rendez-vous point to its own devices from its \squad --- all the hops on the route are 
+chosen by Bob uniformly at random from the RPS. \(\SPOR[\Recv]\)
+returns the \(H_\rdv\) that Bob gives to Alice using an
+out-of-band channel, \eg using one device of its \squad.
+PORs have \(L\) layers, and for each layer the number of
+alternatives nodes depends of a failure threshold \(\theta\). 
+As long as \(\theta\) is not exceeded, alternatives nodes are added in
+\(H_\rdv\) as depicted in \cref{ExtendRoute}. Thus the probability of
+failure for the extension is \(1 - (1 - \theta)^L\).
+
+Once Alice get the \(H_\rdv\), Alice uses \(\SPOR[\Send]\) at some
+later time to send the message to Bob using any of her devices from
+its \squad (See \cref{SPORSend}). First, \(\SPOR[\Send]\) extends the route
+\(H_\rdv\) with some hops of Alice's choosing (uniformly randomly
+chosen). Second, \(\SPOR[\Send]\) extracts from the onion the first
+layer, which contained the overall
+possible rendez-vous points $D$ selected by the recipient (i.e. Bob).
+One device from $D$ is randomly chosen, and the \(\SPOR[\Fwd]\)
+sub-function is called as long as the message forwarding to one node of
+the next layer is not successful. Along the path, each node decrypts
+in sequence the different layer with the current node’s private key. 
+The end of the route is reached when special value \(H_\rdv = \top\) is
+encountered. Consequently the ciphered message \(c_m\) is then stored
+in the disk of the local node through the \(\Store\) sub function 
 (\cref{SPORRecv}).
-Say Alice wants to send a message \(m\) to Bob.
-Bob uses \(\SPOR[\Recv]\) to create a probabilistic onion route \(H_\rdv\) from 
-a rendez-vous point to his own device swarm --- all the hops on the route are 
-chosen by Bob uniformly at random.
-Bob gives \(H_\rdv\) to Alice using an out-of-band channel, \eg using his phone.
-Alice uses \(\SPOR[\Send]\) at some later time to send the message to Bob using 
-any of her devices.
-\(\SPOR[\Send]\) extends the route \(H_\rdv\) with some hops of Alice's choosing 
-(uniformly randomly chosen), then starts to forward the message (using 
-\(\SPOR[\Fwd]\)) through the hops on the route to Bob.
-This process is illustrated in \cref{fig:file-exchange}.
+
+\david{the use of DeBE algorithms must be explicitly explained here}
+
+%The special value \(H = \top\) indicated the end of the route, thus \(c_m\) 
+%    is intended for the local node and \(c_m\) is instead sent to disk using 
+%    \(\Store\) (\cref{SPORRecv}).%
+
+%The SPOR.Forward algorithm forwards m down the route H, obtained by
+%decrypting CH with the node’s associated private key. The special
+%value H = ⊤ indicated the end of the route, thus cm is intended for
+%the local node and cm is instead sent to disk using Store
+
+%extends the route \(H_\rdv\) (using 
+ %   \(\ExtendRoute\), \cref{ExtendRoute}) and sends the message \(m\) down the 
+  %  extended route using the \(\SPOR[\Fwd]\) algorithm (\cref{SPORFwd}).
+   % The first node of \(H_\rdv\) is the rendez-vous point selected by the 
+    %recipient.
+
+%It creates a probabilistic onion-route from a rendez-vous point to its own 
+%    devices and returns the route to the sender.
 
@@
 \begin{figure}
-  \begin{algorithmic}
+
+  \framebox{\begin{minipage}{0.96\linewidth}
+  \begin{algorithmic}[1]
     \Require{%
@@
     \EndFunction
-
+  \vspace{0.3em}
     \Function{\CreateOnionLayer}{$\theta$}
       \State $(d, \pk_d, p_d)\gets \GetRandomPeer$
-      \Comment We use \(d\) as shorthand for this tuple.
-      \State $D\gets \{d\}$
+      \State $D\gets \{(d, \pk_d, p_d)\}$
       \While{$\prod_{d\in D} p_d > \theta$}
-        \State $d\gets \GetRandomPeer$
-        \State $D\gets D\cup \{d\}$
+        \State $(d, \pk_d, p_d)\gets \GetRandomPeer$
+        \State $D\gets D\cup \{(d, \pk_d, p_d)\}$
       \EndWhile
@@
   \end{algorithmic}
+  \end{minipage}}
   \caption{\label{ExtendRoute}%
-    The \(\ExtendRoute\) algorithm extends a route \(H\) with \(L\) hops and 
-    failure threshold of \(\theta\) for each hop in the route.
-    Thus the probability of failure for the extension is \(1 - (1 - \theta)^L\).
-    The function \(\GetRandomPeer\) is any random peer-sampling algorithm.
+    \scriptsize
+    The \(\ExtendRoute\) algorithm extends a route \(H\)
   }
@@
 \begin{figure}
+  \framebox{\begin{minipage}{0.96\linewidth}
   \begin{algorithmic}
@@
     \EndFunction
-
-    \Function{\Store}{$m$}
-      \State $m\gets \DeBEdec[\mpk, \sk, c_m]$
-      \If{$m = \bot$}
-        \State \Return $\bot$
-      \EndIf
-      \State Store $m$ to disk.
-      \State \Return $\top$
-    \EndFunction
   \end{algorithmic}
+  \end{minipage}}
   \caption{\label{SPORRecv}%
+\scriptsize
     The \(\SPOR[\Recv]\) algorithm prepares the recipient for receiving a file.
-    It creates a probabilistic onion-route from a rendez-vous point to its own 
-    devices and returns the route to the sender.
-    The \(\Store\) algorithm is used by the local \(\SPOR[\Fwd]\) algorithm to 
-    store messages intended for itself.
   }
@@
   \end{algorithmic}
+  \end{minipage}}
   \caption{\label{SPORSend}%
-    The \(\SPOR[\Send]\) algorithm extends the route \(H_\rdv\) (using 
-    \(\ExtendRoute\), \cref{ExtendRoute}) and sends the message \(m\) down the 
-    extended route using the \(\SPOR[\Fwd]\) algorithm (\cref{SPORFwd}).
-    The first node of \(H_\rdv\) is the rendez-vous point selected by the 
-    recipient.
+    \scriptsize
+    The \(\SPOR[\Send]\) algorithm 
   }
@@
     \EndFunction
+    \Function{\Store}{$m$}
+      \State $m\gets \DeBEdec[\mpk, \sk, c_m]$
+      \If{$m = \bot$}
+        \State \Return $\bot$
+      \EndIf
+      \State Store $m$ to disk.
+      \State \Return $\top$
+    \EndFunction
   \end{algorithmic}
+  \end{minipage}}
   \caption{\label{SPORFwd}%

### 2018-04-30 paper/evaluation.tex

@@
 
+\subsubsection{Experimental parameters} % (fold)
+\label{ssub:experimental_parameters}
+
+In the following, we perform two types of experiments: figures~\ref{fig:nodes_per_layer_vs_theta} and \ref{fig:success_rate_vs_t} illustrate the establishment of PORs, while the next ones measure file transfer.
+
+Figures \ref{fig:nodes_per_layer_vs_theta} and \ref{fig:success_rate_vs_t} come from the same data, with 10 experiments per set of settings.
+$\theta$ is the threshold of the probability that all nodes fail at once: we keep adding nodes to a layer until the layer's probability is below $\theta$. 
+It takes the following values: $[0.1, 0.01, 0.001, 0.0001]$.
+$L$, the number of layers constituting a route, takes the following values: $[3, 5, 7]$.
+The time since route establishment goes from 1 to 10 with  unit step.
+It is measured in time periods $T$, the interval at which users change the connection state of their devices.
+An experiment consisted in $L*5$ users, where we randomly picked pairs of users to compute 20 routes.
+Hence, each point in figure~\ref{fig:nodes_per_layer_vs_theta} is the average of 3000 layers size; 
+each point in figure~\ref{fig:nodes_per_layer_vs_theta} is the availability rate over 200 routes.
+
 \subsection{Devices' predictions of the user behavior} % (fold)
@@
 
+\commentAL{Will probably ditch that}
+
 % subsection devices_predictions_of_the_user_behavior (end)
-\commentAL{Should evaluate the inference of the model given only the observable sequence. Also show that $P[O_{t+1} | S_t] \simeq P[O_{t+i} | S_t]$}
+%\commentAL{Should evaluate the inference of the model given only the observable sequence. Also show that $P[O_{t+1} | S_t] \simeq P[O_{t+i} | S_t]$}
 
@@
 
-In figure \ref{fig:nodes_per_layer_vs_theta} and \ref{fig:success_rate_vs_t}, we computed 10 experiments per set of settings.
-$\theta$ is the threshold of the probability that all nodes fail at once: we keep adding nodes to a layer until the layer's probability is below $\theta$. 
-It takes the following values: $[0.1, 0.01, 0.001, 0.0001]$.
-$L$, the number of layers constituting a route, takes the following values: $[3, 5, 7]$.
-The time since route establishment goes from 1 to 10 with  unit step. 
-An experiment consisted in $L*5$ users, where we randomly picked pairs of users to compute 20 routes.
-Hence, each point in figure~\ref{fig:nodes_per_layer_vs_theta} is the average of 3000 layers size; 
-each point in figure~\ref{fig:nodes_per_layer_vs_theta} is the availability rate over 200 routes.
-
-\begin{figure}
+\begin{figure}[t]
 \centering
 \includegraphics[width=0.8\columnwidth]{figures/nodes_per_layer_vs_theta.pdf}
-\caption{\label{fig:nodes_per_layer_vs_theta}Number of nodes per layer of Predictive Onion Route as a function of the parameter $\theta$ (the maximal probability that all nodes in a layer fail at once).
-We see that the number of nodes exponentially decreases a we relax the $\theta$ constraint.}
+\caption{\label{fig:nodes_per_layer_vs_theta}Number of nodes per layer of POR as a function of the parameter $\theta$ (the maximal probability that all nodes in a layer fail at once).
+We see that the number of nodes logarithmically decreases as we relax the $\theta$ constraint.}
 \end{figure}
 
-\begin{figure}
+We first measure the influence of the parameter $\theta$ on the number of nodes per layer in figure~\ref{fig:nodes_per_layer_vs_theta}, by displaying average and standard deviation of the number of nodes for $\theta=[10^{-4}, 10^{-3}, 10^{-2}, 10^{-1}]$ (the other experiment parameters are listed in section~\ref{ssub:experimental_parameters}).
+As we can see, the number of devices per layer logarithmically decreases as we relax the constraint on the layer's availability.
+The mean required number of devices per layer is reasonable: between 2 and 6.
+Still, the number of nodes per layer is very variable: at $\theta=10^{-4}$, values range from 2 to 11, with a standard deviation of 1.44.
+
+\begin{figure}[t]
 \includegraphics[width=\columnwidth]{figures/success_rate_vs_t.pdf}
@@
 \end{figure}
+
+We now study the influence of the parameters on the future availability of the routes in figure~\ref{fig:success_rate_vs_t}.
+We consider a route available if at least one node per layer is online at this time.
+The plots reads the mean availability of routes as a function of the time since the route's establishment, for every couple of parameters $(\theta, L)$.
+First of all, we observe that time has a negligible impact on the availability of routes. 
+This shows, as was stated in section~\ref{para:predicting future behavior}, that the prediction that devices make of behavior at $t+1$ is a good enough estimator for $t+i$.
+We also see that $\theta$ has a big impact on the availability average, and variability.
+Still, $\theta\in[10^-4, 10^-3]$ allows highly available routes with an average availability of 100\% and 99.5\% respectively.
+Combined with the results from figure~\ref{fig:nodes_per_layer_vs_theta}, it means that routes will need an average of 5-6 devices per layer to be highly available.
+Finally, increasing $L$ logically hinders the results when using low-availability layers.
+
+We showed that creating reliable onion routes using a backbone of unreliable nodes is feasible by using predictive algorithms.
+The counterpart is that messages header size grows \commentAL{How does it grow? Quadratically, exponentially?} with the number of layers and the number of devices per layer.
+Considering that most onion routing solutions use a statically defined message size to avoid information leakage, this means that a more reliable onion route comes at the cost of an increased network traffic.
+
+\subsection{File transfer} % (fold)
+\label{sub:file_transfer}
+
+\commentAL{Git-noobiness removed my data: it has to compute again overnight.}
+
+% subsection file_transfer (end)

### 2018-04-30 paper/message-passing-design.tex
up

@@
 sub-function is called as long as the message forwarding to one node of
-the next layer is not successful. Along the path, each node decrypts
+the next layer is not successful (See \cref{SPORFwd}). Along the path, each node decrypts
 in sequence the different layer with the current node’s private key. 

### 2018-04-30 paper/message-passing-design.tex
up

@@
 layer, which contained the overall
-possible rendez-vous points $D$ selected by the recipient (i.e. Bob).
+possible rendez-vous points $D$ previously selected by the recipient (i.e. Bob).
 One device from $D$ is randomly chosen, and the \(\SPOR[\Fwd]\)

### 2018-04-30 paper/security-discussion.tex
Writes up security discussion

@@
 \label{security-limitations}
-from mails:
 
-- Route fingerprinting in anonymous communications.
+Many attacks against anonymous communications systems target the peer sampling 
+mechanism, \eg~\cite{%
+  RouteFingerprinting,%
+  EpistemicAttacksOnRouteSelection,%
+}.
+So, even if our system is secure in theory, it will not be secure in practice 
+unless the random peer sampling algorithm returns peers chosen uniformly 
+randomly from the entire Global Device Retinue.
 
-It depends on the random peer sampling I suppose. And I have no clue 
-about how that one works. Adrien referred to a paper by Anne-Marie.
+To prevent attacks on the random peer sampling, some systems have employed 
+techniques to detect colluding nodes, \eg~\cite{%
+  SecurePeerSampling,%
+  MorphMix,%
+}.
+However, as is the case of~\cite{MorphMix}, these can be 
+broken~\cite{BreakingMorphMix}.
 
-If I were to guess, I'd say: if Anne-Marie's RPS protocol is Byzantine 
-fault tolerant, maybe; otherwise, we're most likely screwed.
-
-> - Bridging and fingerprinting: Epistemic attacks on route selection
-
-I'd say the same as above. It's about peer selection.
-
-> - Breaking the collusion detection mechanism of morphmix
-
-We don't do any collusion detection, so I'd say we're vulnerable. We 
-assume we choose nodes uniformly at random, so colluding nodes have 
-uniform probability of success --- but that falls back on the RPS and 
-Anne-Marie's paper. So maybe or screwed.
-
-> - Denial of service or denial of security? How attacks on reliability can
-> compromise anonymity
-
-After just reading the abstract, most likely vulnerable. But thanks to 
-our stateless design we don't have to do retransmission the whole way, 
-as might be the case for active circuits --- only the node who 
-experience the failure going forward will need to retransmit. (Thanks Adrien for 
-insisting on creating a route back for the ACK ;-) So we might not be in as bad 
-a position as other systems, it'll take more rounds of attack to break it --- 
-but I'm quite sure it will break.
-
-But in general, these all face global and possibly malicious 
-adversaries. We don't have that in our adversary model. If everyone 
-colludes against Alice and Bob in our setting, they're screwed.
-
-It's basically impossible to remain anonymous against the global 
-adversary (statistical inference, paper by Danezis) unless Alice sends a 
-message to everyone whenever she wants to send a message to Bob. 
-Basically the anonymous communication community is converging on methods 
-like Loopix and HORNET --- have enough throughput so that the global 
-adversary is overwhelmed with data. (Tor is too slow.)
+There are also other types of attacks, \eg denial of service attacks that can 
+lead to the adversary learning more from the system~\cite{DenialOfSecurity}.
+It is difficult to say to what extent our system might be vulnerable to this 
+type of attack without a deeper analysis.
+Unfortunately this is outside the scope of this study.
+However, we hypothesize that our stateless and redundant design might have some 
+advantages, \eg no control messages sent back from where the error happened to 
+the source.
+But these advantages will only postpone the success of the attack, eventually 
+even our protocol must resend.
 
@@
 
+One thing that we can directly improve is the header.
 We see two alternative paths for improving the header.
@@
 format to the routing of \(\SPOR\).
-Then we could achieve the properties of Sphinx and enjoy provable security.
+Then we could achieve the properties of Sphinx, \eg preventing the last node to 
+learn the destination, and enjoy provable security.
 
@@
 This approach would probably be the easiest, but would probably not provide all 
-the properties from Sphinx (\eg resistance to active tagging attacks and bitwise 
-unlinkability).
+the properties from Sphinx (\eg resistance to active tagging attacks).

### 2018-04-30 paper/global-overlay-design.tex
Replaces some of Adrien's PORs with \acp{SPOR}

@@
 
-To reach this goal, we employ Random Peer Sampling (RPS) \cite{Voulgaris_Gavidia_van_Steen_2005,Jelasity_Voulgaris_Guerraoui_Kermarrec_van_Steen_2007}.
+To reach this goal \david{which one?}, we employ Random Peer Sampling (RPS) \cite{Voulgaris_Gavidia_van_Steen_2005,Jelasity_Voulgaris_Guerraoui_Kermarrec_van_Steen_2007}.
 Essentially, each node maintains a \emph{view} containing \viewsize other devices' descriptors. 

### 2018-04-30 paper/squad-overlay-design.tex

@@
-\subsection{The E-Squad Overlay} 
+\subsection{The \squad Overlay} 
 \label{sec:squad_overlay}
@@
 
-In this section, we only take interest in one user (called Alice) and her squad.
+In this section, we only take interest in one user (called Alice) and her \squad.
 
@@
 
-\paragraph*{Other uses of the Squad Overlay} In addition to user's behavior, devices use th \squad Overlay for several purposes.
+\paragraph*{Other uses of the \squad Overlay} In addition to user's behavior, devices use th \squad Overlay for several purposes.
 Firstly, they share files location: when Alice wants to share a file $f$ that resides on her home computer, using her smartphone as the exchange initiator, her smartphone knows where $f$ is located and can create the route accordingly.
 Secondly, each device is also informed of its user's ongoing file transfers (which serves the next purpose).
+Finally, because devices can receive messages on behalf of their fellow squad members to ensure reception despite the proper recipient being offline, 
+one's devices can forward messages among the \squad.
 
-\david{the following paragraph is not clear at all }
-\name knows two message types (as will be covered in~\ref{sec:file_exchange}): file chunk, and acknowledgment.
-Alice typically wants to receive a file on one particular device; respectively, only one of her devices is interested in acknowledging reception of the file chunks it is sending.
+% \david{the following paragraph is not clear at all }
+% \name knows two message types (as will be covered in~\ref{sec:file_exchange}): file chunk, and acknowledgment.
+% Alice typically wants to receive a file on one particular device; respectively, only one of her devices is interested in acknowledging reception of the file chunks it is sending.
 \david{what is the relationship with \squad Overlay?}
-However, \name allows all squad members to receive messages destined to Alice.
-Thus, the third complementary purpose of the Squad Overlay is to relay messages among the squad: when a message is not destined to the device that received it, the receiver forwards the message to its final destination.
-\david{and then?}
+% However, \name allows all \squad members to receive messages destined to Alice.
+% Thus, the third complementary purpose of the \Squad Overlay is to relay messages among the squad: when a message is not destined to the device that received it, the receiver forwards the message to its final destination.
+% \david{and then?}
 

### 2018-04-30 paper/related.tex
edits in related work, removing Retinue from sec discussion

@@
 
-Mixnets~\cite{Chaum:198} are perhaps the first solution to turn to for sending content from A to B anonymously.
+Mixnets~\cite{Chaum:1981} are perhaps the first solution to turn to for sending content from A to B anonymously.
 In our context, however, they are less suitable due to their reliance on mix servers, the limited protection against statistical inference possible for even a perfect mixnet given the multiple varying sources and destinations of our use case, and the delay they would add due to batching.
@@
 There is a concern shared with traditional p2p file sharing, namely churn~\cite{dhtchurn} and its effect on availability - here in the narrow context of the set of user devices based on user behavior.
-We thus discuss the related work on predicting device availability next.
+We thus discuss the related work on predicting device availability next, though to the best of our knowledge we are the first to make use of such predictions to cope with churn in interoperating sets of user devices.
 
-\commentAL{Will need another pass.}
-\paragraph*{Modeling devices' connection and disconnection} 
+%\commentAL{Will need another pass.}
+%\paragraph*{Modeling devices' connection and disconnection} 
 % To simulate users' devices participating in a distributed protocol, we build upon existing literature on two topics: 
@@
 
-In our experiments, we simulate users' devices participating in a distributed protocol.
-To make this simulation realistic, we based our models on existing literature.
-
-Firstly, fields studies provide \emph{usage and connectivity patterns of users' appliances}.
-Karlson et al. \cite{Karlson_Meyers_Jacobs_Johns_Kane_2009} studied the compared usage of the laptop and smartphone of 16 information workers: 
-they show that their participants use their smartphones very regularly throughout the day to do background tasks (\eg answering mails or checking their agenda).
+%In our experiments, we simulate users' devices participating in a distributed protocol. We base our modeling of devices' online availability on existing literature such as the following.  
+Field studies provide \emph{usage and connectivity patterns of users' appliances}.
+Karlson et al.
+\cite{Karlson_Meyers_Jacobs_Johns_Kane_2009} studied the compared usage of the laptop and smartphone of 16 information workers and show that their participants use their smartphones very regularly throughout the day to do background tasks (\eg answering mails or checking their agenda).
 Their laptop is online less often, and is dedicated to the most demanding tasks.
@@
 \cite{Wagner_Rice_Beresford_2013} conducted a thorough data collection on Android devices via an application called Device Analyzer, that collected metrics on movement patterns, connectivity and energy consumption from 16,000 users.
-\commentAL{Conclude: will we use their dataset? Why are these papers useful to us?}
-
-Secondly, several research works point out the emerging trend of \emph{multi-device interaction}.
+%\commentAL{Conclude: will we use their dataset? Why are these papers useful to us?}
+Several works point out the emerging trend of \emph{multi-device interaction}.
 A 2012 Google-led study \cite{google2012} stated that the USA are nowadays ``a nation of multi-screeners''.
@@
 Jokela et al. \cite{Jokela_Ojala_Olsson_2015} and \cite{google2012} also differentiated sequential and parallel usage of one's multiple devices.
-
-Finally, research in P2P networks observed \cite{Stutzbach_Rejaie_2006} and modeled \cite{Yao_Leonard_Wang_Loguinov_2006} patterns of \emph{churn} (\ie participants moving in and out of a system).
-
+Research in P2P networks observed \cite{Stutzbach_Rejaie_2006} and modeled \cite{Yao_Leonard_Wang_Loguinov_2006} patterns of \emph{churn} (\ie participants moving in and out of a system).
 We take inspiration from these works in order to establish credible models of user behaviors to evaluate our protocol. 

### 2018-04-30 paper/global-overlay-design.tex
lala

--- 2018-04-29 paper/global-overlay-design.tex
@@
 
-\newcommand{\viewsize}{\ensuremath{l_{\text{view}}}}
-\NewAlgorithm{\GetRandomPeer}{RPS()}
+\newcommand{\viewsize}{\ensuremath{l_{\text{view}}\xspace}}
+\newcommand{\view}{\ensuremath{\mathcal{V}_{\text{RPS}}\xspace}}
+\NewAlgorithm{\GetRandomPeer}{random descriptor from \view}
+
+To create PORs, devices need to know the address, encryption key, and probability of remaining available of some nodes in the system, to pick them as relays on the route.
 
 To reach this goal, we employ Random Peer Sampling (RPS) \cite{Voulgaris_Gavidia_van_Steen_2005,Jelasity_Voulgaris_Guerraoui_Kermarrec_van_Steen_2007}.
-Essentially, each node maintains a \emph{view} containing \viewsize other devices' descriptors. 
-By periodically exchanging random descriptors with a carefully selected node from its view, RPS allows devices to always have a fairly random sample of the nodes in the system inside their view.
-Due to the RPS's eviction policy, stale descriptors are removed quickly: each device thus knows a random sample of \viewsize connected nodes.
-An RPS descriptor for device $d$ is constituted of the following information:
+Essentially, each node maintains a view \view containing \viewsize other devices' descriptors. 
+This view is periodically updated as follows: a device $d$ pops the oldest descriptor $d'$ from its view, then swaps a predefined number of $l$ elements from \view with $d'$.
+Both devices add a descriptor for themselves to the view exchange.
+If $d'$ was offline, its descriptor is simply removed from the $d$'s view, but \view is otherwise not updated.
+
+This allows for two things: firstly, each device's view contains a constantly changing random sample of the whole set of devices;
+secondly, offline nodes get removed from one's view fairly fast---we can say that a \view contains \emph{mostly} descriptors of online devices.
+
+In \name, an RPS descriptor for device $d$ is constituted of the following information:
 \begin{itemize}
-  \item Its address: $@_d$;
+  \item Its address: $d$;
   \item Its public key: \(\pk_d\);
@@
 
-Devices now have all the information they need to establish reliable PORs between two sets of devices.
+Devices now have all the information they need to establish reliable PORs.
 

### 2018-04-30 paper/squad-overlay-design.tex
lala

@@
 
-We show in section~\label{sub:predictive_onion_routes_creation} that the prediction of their availability at $t+1$ is a good enough estimator of their connection state at $t+i$.
-For that reason, devices only share $P\left[ d \in O_{t+1} \mid S_{t} = s \right]$ with other devices for PORs creation.
+We show in section~\ref{sub:predictive_onion_routes_creation} that the prediction of devices' availability at $t+1$ is a good enough estimator of their connection state at $t+i$.
+For that reason, devices only compute and publish $P\left[ d \in O_{t+1} \mid S_{t} = s \right]$.
 

### 2018-04-30 code/routes/device.py

@@ -89,6 +89,9 @@ class Device:
         route = [pd.DataFrame() for _ in range(n_layers)]
         view = self.peers_view.view.copy()
 
+        if len(view) == 0:
+            raise("Dayum")
+
         converged = False
         while not converged:
             converged_layers = [False for _ in range(n_layers)]

### 2018-04-30 paper/security-discussion.tex

@@
 \cref{system-model}).
-Bob is allowed to infer the behaviour of devices in the Global Device Retinue, 
+Bob is allowed to infer the behaviour of devices in the global set, % Global Device Retinue, 
 but a file transfer from Alice should not give Bob any information about which 
@@
 If we assume that Alice and Bob can sample their nodes uniformly randomly from 
-the \emph{entire} Global Device Retinue (we will return to this assumption 
+the \emph{entire} global set of devices %Global Device Retinue 
+(we will return to this assumption 
 below), then their probability of successful attack is proportional to their 
@@
 Alice and Bob construct their \ac{SPOR} route by including devices from the 
-Global Device Retinue, which also includes devices from Carol and David.
+global set %Global Device Retinue
+, which also includes devices from Carol and David.
 If all devices on the route belong to Carol and David, then they can, of course, 
@@
 unless the random peer sampling algorithm returns peers chosen uniformly 
-randomly from the entire Global Device Retinue.
+randomly from the entire global set. %Global Device Retinue.
 
@@
 \subsection{Future Work}
-%
-% \commentAL{To rewrite as real paragraphs} Future work and prospects:
-% \begin{itemize}
-% 	\item More in-depth knowledge of the user's behavior would allow to predict devices connections farther in the future;
-% 	\item Changing devices' asymmetric keys regularly would increase security.
-% 	Updating keys is easy in \name given the RPS that propagates new information to all nodes.
-% 	However, more reflection would be needed to avoid key updates breaking ongoing communications passing through the devices in question;
-% 	\item \name is not resilient to Byzantine nodes for now: malicious users could potentially make users pick Predictive Onion Routes that pass through them with a high probability, thus allowing the attacker to learn the file sender and receiver.
-To circumvent this, we would need to employ a secure Random Peer Sampling \cite{Jesi_Montresor_van_Steen_2010}, and prevent devices to lie on their probability of being online.
-
-% \end{itemize}
 

### 2018-04-30 paper/system-model.tex
up

--- 2018-04-03 paper/privacy.tex
@@
-\section{Privacy}%
-\label{Privacy}
+\section{System model, adversary model and desired privacy properties}%
+\label{system-model}
 
-We care about
-\dots
+\name is a distributed system made of users' devices. 
+Each device can communicate with any other device that it knows the
+address for. All devices belonging to one user
+ know which other devices belong to the same user, \ie the \squad.
+Thus the devices from an \squad only knows the mapping from devices to users for the devices in 
+the \squad it belongs to.
+
+\paragraph*{In the cloud setting} if Alice wants to share a file with
+Bob, she picks up and pushes one of her files, from one of her devices, to the cloud
+provider, to make it available to Bob that will thereafter get it from
+one of its devices. The use of the cloud provider as a third party
+provides two main privacy properties, which we have to consider when
+changing the setting to that of \ac{P2P}~\cite{DevilInMetadata}:
+\begin{itemize}
+\item Alice and Bob are the only ones who learn 
+about Alice sharing a file with Bob, except for the cloud provider.
+\item Alice and Bob learn nothing about each others' devices, \ie 
+they cannot map any device as belonging to each other, except for the
+cloud provider that learn it.
+\end{itemize}
+
+\paragraph*{In the \name setting} when changing from the cloud setting
+to \ac{P2P}, we want to keep the privacy that Alice and Bob already
+enjoyed through the cloud provider, and go a step further by removing 
+cloud provider that may act as a spy. However, this increased privacy
+should not be done to the benefit of the user's friends that may
+become the most powerful potential attackers, and act
+as an adversary type of friends.
+In this context, in \name, we want to protect users from friendly
+surveillance~\cite{FriendlySurveillance} in an honest-but-curious setting.
+
+However, we will not consider a global network adversary, only subsets of colluding 
+parties. We know that it is notoriously difficult to achieve security against a global 
+network adversary~\cite{SystemsForAnonymousCommunication}.

### 2018-04-30 paper/intro.tex
typo in intro

--- 2018-04-29 paper/intro.tex
@@
 interactions \textit{in situ} in order to share digital content
-\cite{Oh:2017} between devices of their own \squad or with those of other users' \squad. More broadly, users expect to share digital content,
+\cite{Oh:2017} between devices of their own \squad or with those of other users' \squad{}s. More broadly, users expect to share digital content,
 wherever the content, its sender, or its recipient might be located, from one
@@
 This turns out to be a critical limitation, as famously emphasized by a former NSA and CIA director: "We kill people based on metadata.''~\cite{NaughtonTheGuardian2016} 
-User devices become tracking and/or monitoring \squad that turn to
+User devices become tracking and/or monitoring \squad{}s that turn to
 be the best spy over users.
@@
 % approach that provides a 
-and self-organizing file sharing service between the \squad of different users that preserves user privacy
+and self-organizing file sharing service between the \squad{}s of different users that preserves user privacy
 in terms of both data \emph{and} metadata. Our proposal hinges on two key ideas: \emph{First}, we consider proxemics relationships as a key enabler to initiate file

### 2018-04-30 paper/message-passing-design.tex
lala
algo

@@
-\NewScheme{\SPOR}{SPOR}
+\NewScheme{\SPOR}{SPORES}
 
@@
 
-\NewAlgorithm{\Send}{Send}
 \NewAlgorithm{\Fwd}{Forward}
-\NewAlgorithm{\Recv}{Receive}
+\NewAlgorithm{\Send}{BuildRouteSender}
+\NewAlgorithm{\Recv}{BuildRouteReceiver}
+\NewAlgorithm{\ExtendRoute}{ExtendRoute}
+\NewAlgorithm{\CreateOnionLayer}{CreateOnionLayer}
+\NewAlgorithm{\Dec}{Dec}
+\NewAlgorithm{\Store}{Store}
+\NewVariable{\sk}{sk}
 \NewVariable{\rdv}{rdv}
+\NewVariable{\LRV}{\mathcal{L_{RV}}\xspace}
+\NewVariable{\Hsend}{\mathcal{H}_{\text{send}}\begin{algorithmic}[1]}
+\NewVariable{\Hrec}{\mathcal{H}_{\text{rec}}\begin{algorithmic}[1]}
+\NewVariable{\Hforward}{\mathcal{H}_{\text{forward}}\begin{algorithmic}[1]}
+\NewVariable{\Hbackward}{\mathcal{H}_{\text{backward}}\begin{algorithmic}[1]}
+\NewVariable{\Hsendforward}{\mathcal{H}_{\text{send forward}}\begin{algorithmic}[1]}
+\NewVariable{\Hsendbackward}{\mathcal{H}_{\text{send backward}}\begin{algorithmic}[1]}
+\NewVariable{\Hrecforward}{\mathcal{H}_{\text{rec forward}}\begin{algorithmic}[1]}
+\NewVariable{\Hrecbackward}{\mathcal{H}_{\text{rec backward}}\begin{algorithmic}[1]}
 
@@
 
+The principle of onion routing à la Tor~\cite{Tor} is to put nodes relaying messages between a source and a destination.
+By employing encryption layers, a relay doesn't know where it is situated on the message's path. 
+It only knows who gave him the message, and where to send it to.
+
 In contrast to Tor~\cite{Tor} that provides only one address per hop
-in the route, \name provides for each layer of the onion several
-alternatives for the next hop in the route depending on their
-probability of being online. To implement our  probabilistic
-predictive onion routing mechanism, \name defined three different algorithms to
-receive, send and forward messages among users' \squad. For instance,
-if Alice wants to send a message \(m\) to Bob, Bob uses the
-\(\SPOR[\Recv]\) algorithm (See \cref{SPORRecv}) to create a probabilistic onion route \(H_\rdv\) from
- a rendez-vous point to its own devices from its \squad --- all the hops on the route are 
-chosen by Bob uniformly at random from the RPS. \(\SPOR[\Recv]\)
-returns the \(H_\rdv\) that Bob gives to Alice using an
+in the route, \name provides, for each layer of the onion, several
+alternative nodes for the next hop in the route depending on their
+probability of being online. 
+We call our modified onion routes Probabilistic Onion Routes or PORs.
+
+Another difference from Tor, where connections are established by all nodes in the route, \name is stateless: the route's ends (the sender Alice and receiver Bob) cooperate to create the headers containing all the necessary routing information for future communication between Alice and Bob.
+In that regard, two headers are required: $\Hforward$ to route packets from Alice to Bob, and $\Hbackward$ for packets from Bob to Alice.
+
+To implement our predictive onion routing mechanism, \name is thus split in two algorithms: the route building one, and the message routing one.
+Figure~\ref{fig:file-exchange} shows the process of the route creation until the first exchange of a file chunk from Alice to Bob.
+Bob uses the backward route to send acknowledgments back to Alice.
+
+\begin{figure}[t]
+  \includegraphics[width=\linewidth]{figures/file_exchange.pdf}
+  \caption{\label{fig:file-exchange}A schematic of the creation and usage of PORs between Alice and Bob's e-squads.}
+\end{figure}
+
+\subsubsection{Building routes} 
+\label{ssub:building_routes}
+
+When Alice wants to send a file to Bob, they first have to call the route building algorithm, and to exchange relevant information out of band (e.g. using mail, or their phones' bluetooth connection).
+They create a route of $L$ layers, a configuration parameter that must be odd. We introduce $l=(L-1)/2$.
+Bob (the receiver) initiates the route creation. 
+He randomly chooses nodes to constitute a rendez-vous layer \LRV, and nodes to constitute $l$ layers from \LRV to his \squad. 
+We come back on layer creation below.
+He crafts a layered encrypted header (more details below) to \LRV (excluded) to his squad (included), that we will call \Hrecforward.
+He also crafts his part of the header for the backward route, \Hrecbackward: it contains the route from Bob's \squad (excluded) to \LRV (included).
+
+Bob sends \Hrecforward and the descriptors of the \LRV nodes to Alice.
+Alice still has her part of the route to create: like Bob, she randomly picks nodes to constitutes $l$ layers from her \squad to \LRV.
+
+\paragraph*{Layer creation}
+
+\paragraph*{Header preparation}
+
+\begin{figure}[t]
+  %\framebox{\begin{minipage}{0.96\linewidth}
+  \begin{algorithmic}[1]
+    % \Require{%
+    %   $D$ is the set of alternative recipient devices.
+    % }
+    \Function{\Recv}{$D$}
+      \State $H_\rdv\gets \ExtendRoute[D\concat \top, L, \theta]$
+      \State \Return $H_\rdv$
+        \Comment{Give to sender out-of-bound.}
+    \EndFunction
+  \end{algorithmic}
+  %\end{minipage}}
+
+  \vspace{0.3em}
+  %\framebox{\begin{minipage}{0.96\linewidth}
+  \begin{algorithmic}[1]
+    % \Require{%
+    %   $m$ is the message to be sent,
+    %   $H_\rdv$ is the onion-route given by the recipient.
+    % }
+    \Function{\Send}{$H_\rdv, m$}
+      \State $H\gets \ExtendRoute[H_\rdv, L, \theta]$
+      \State $D\concat C_H\gets H_\rdv$
+      \For{$d\in D$}
+        \Comment{Uniformly randomly chosen}
+        \If{$d\method \Fwd[C_H, m] \neq \bot$}
+          \State \Return $\top$
+        \EndIf
+      \EndFor
+      \State \Return $\bot$
+    \EndFunction
+  \end{algorithmic}
+  %\end{minipage}}
+
+  \vspace{0.3em}
+  %\framebox{\begin{minipage}{0.96\linewidth}
+  \begin{algorithmic}[1]
+    % \Require{%
+    %   $H$ is a header of the form \(D\concat H'\) or \(D\concat \top\), where 
+    %   \(D\) is a set of device addresses.
+    %   $\pk_D$ is the public key of device set $D$.
+    %   $L$ is the length of the route,
+    %   $\theta$ is the threshold of probability of failure.%
+    % }
+    \Function{\ExtendRoute}{$H, L, \theta$}
+      \If{$L\leq 0$}
+        \State \Return $H$
+      \EndIf
+      \State $D\gets \CreateOnionLayer[\theta]$
+      \State $H\gets D\concat \DeBEenc[\mpk, D, H]$
+      \State \Return $\ExtendRoute[H, L-1, \theta]$
+    \EndFunction
+  \vspace{0.3em}
+    \Function{\CreateOnionLayer}{$\theta$}
+      \State $(d, \pk_d, p_d)\gets \GetRandomPeer$
+      \State $D\gets \{(d, \pk_d, p_d)\}$
+      \While{$\prod_{d\in D} p_d > \theta$}
+        \State $(d, \pk_d, p_d)\gets \GetRandomPeer$
+        \State $D\gets D\cup \{(d, \pk_d, p_d)\}$
+      \EndWhile
+      \State \Return $D$
+    \EndFunction
+  \end{algorithmic}
+  %\end{minipage}}
+  \caption{\label{fig:route building algo}The route building algorithm}
+\end{figure}
+
+\subsubsection{Routing messages}
+\label{ssub:routing_messages}
+
+\begin{figure}[t]
+  %\framebox{\begin{minipage}{0.96\linewidth}
+  \begin{algorithmic}[1]
+    %\Require{$\pk, \sk$ is the public--private key-pair of the node.}
+    \Function{\SPOR[\Fwd]}{$C_H, m$}
+      \State $H\gets \DeBEdec[\mpk, \sk, C_H]$
+      \If{$H = \bot$}
+        \State \Return $\bot$
+      \EndIf
+      \State $\{d_i\}\concat C_H'\gets H$
+      \If{$C_H' = \top$}
+        \State \Return $\Store[m]$
+      \EndIf
+      \For{$d\in \{d_i\}$}
+        \Comment{Uniformly randomly chosen}
+        \If{$d\method \Fwd[C_H', m] \neq \bot$}
+          \State \Return $\top$
+        \EndIf
+      \EndFor
+      \State \Return $\bot$
+    \EndFunction
+  \end{algorithmic}
+
+  \begin{algorithmic}[1]
+    \Function{\Store}{$m$}
+      \State $m\gets \DeBEdec[\mpk, \sk, c_m]$
+      \If{$m = \bot$}
+        \State \Return $\bot$
+      \EndIf
+      \State Store $m$ to disk.
+      \State \Return $\top$
+    \EndFunction
+  \end{algorithmic}
+  %\end{minipage}}
+  \caption{\label{SPORFwd}%
+    The \(\SPOR[\Fwd]\) algorithm forwards \(m\) down the route \(H\), obtained 
+    by decrypting \(C_H\) with the node's associated private key.
+    The special value \(H = \top\) indicated the end of the route, thus \(c_m\) 
+    is intended for the local node and \(c_m\) is instead sent to disk using 
+    \(\Store\) (\cref{SPORRecv}).%
+  }
+\end{figure}
+
+For instance, if Alice wants to send a message \(m\) to Bob, they are both going to perform a part of the building algorithm.
+Bob uses the \(\SPOR[\Recv]\) function (See \cref{SPORRecv}) to create a probabilistic onion route $\mathcal{H_B}$ from
+ a rendez-vous (RV) layer $\mathcal{L_{RV}}$ to its own devices from its \squad---all the hops on the route are 
+chosen by Bob uniformly at random from the Global Overlay.
+ \(\SPOR[\Recv]\)
+returns $\mathcal{H_B}$ and  that Bob gives to Alice using an
 out-of-band channel, \eg using one device of its \squad.
@@
 %    devices and returns the route to the sender.
-
-\begin{figure}
-  \includegraphics[width=\linewidth]{figures/file_exchange.pdf}
-  \caption{\label{fig:file-exchange}%
-    A schematic of Alice and Bob sending a message using \(\SPOR\).
-  }
-\end{figure}
-
-\NewAlgorithm{\ExtendRoute}{ExtendRoute}
-\NewAlgorithm{\CreateOnionLayer}{CreateOnionLayer}
-
-\begin{figure}
-
-  \framebox{\begin{minipage}{0.96\linewidth}
-  \begin{algorithmic}[1]
-    \Require{%
-      $H$ is a header of the form \(D\concat H'\) or \(D\concat \top\), where 
-      \(D\) is a set of device addresses.
-      $\pk_D$ is the public key of device set $D$.
-      $L$ is the length of the route,
-      $\theta$ is the threshold of probability of failure.%
-    }
-    \Function{\ExtendRoute}{$H, L, \theta$}
-      \If{$L\leq 0$}
-        \State \Return $H$
-      \EndIf
-      \State $D\gets \CreateOnionLayer[\theta]$
-      \State $H\gets D\concat \DeBEenc[\mpk, D, H]$
-      \State \Return $\ExtendRoute[H, L-1, \theta]$
-    \EndFunction
-  \vspace{0.3em}
-    \Function{\CreateOnionLayer}{$\theta$}
-      \State $(d, \pk_d, p_d)\gets \GetRandomPeer$
-      \State $D\gets \{(d, \pk_d, p_d)\}$
-      \While{$\prod_{d\in D} p_d > \theta$}
-        \State $(d, \pk_d, p_d)\gets \GetRandomPeer$
-        \State $D\gets D\cup \{(d, \pk_d, p_d)\}$
-      \EndWhile
-      \State \Return $D$
-    \EndFunction
-  \end{algorithmic}
-  \end{minipage}}
-  \caption{\label{ExtendRoute}%
-    \scriptsize
-    The \(\ExtendRoute\) algorithm extends a route \(H\)
-  }
-\end{figure}
-
-\NewAlgorithm{\Store}{Store}
-\NewAlgorithm{\Dec}{Dec}
-\NewVariable{\sk}{sk}
-
-\begin{figure}
-  \framebox{\begin{minipage}{0.96\linewidth}
-  \begin{algorithmic}
-    \Require{%
-      $D$ is the set of alternative recipient devices.
-    }
-    \Function{\SPOR[\Recv]}{$D$}
-      \State $H_\rdv\gets \ExtendRoute[D\concat \top, L, \theta]$
-      \State \Return $H_\rdv$
-        \Comment{Give to sender out-of-bound.}
-    \EndFunction
-  \end{algorithmic}
-  \end{minipage}}
-  \caption{\label{SPORRecv}%
-\scriptsize
-    The \(\SPOR[\Recv]\) algorithm prepares the recipient for receiving a file.
-  }
-\end{figure}
-
-\begin{figure}
-  \framebox{\begin{minipage}{0.96\linewidth}
-  \begin{algorithmic}
-    \Require{%
-      $m$ is the message to be sent,
-      $H_\rdv$ is the onion-route given by the recipient.
-    }
-    \Function{\SPOR[\Send]}{$H_\rdv, m$}
-      \State $H\gets \ExtendRoute[H_\rdv, L, \theta]$
-      \State $D\concat C_H\gets H_\rdv$
-      \For{$d\in D$}
-        \Comment{Uniformly randomly chosen}
-        \If{$d\method \Fwd[C_H, m] \neq \bot$}
-          \State \Return $\top$
-        \EndIf
-      \EndFor
-      \State \Return $\bot$
-    \EndFunction
-  \end{algorithmic}
-  \end{minipage}}
-  \caption{\label{SPORSend}%
-    \scriptsize
-    The \(\SPOR[\Send]\) algorithm 
-  }
-\end{figure}
-
-\begin{figure}
-  \framebox{\begin{minipage}{0.96\linewidth}
-  \begin{algorithmic}
-    \Require{$\pk, \sk$ is the public--private key-pair of the node.}
-    \Function{\SPOR[\Fwd]}{$C_H, m$}
-      \State $H\gets \DeBEdec[\mpk, \sk, C_H]$
-      \If{$H = \bot$}
-        \State \Return $\bot$
-      \EndIf
-      \State $\{d_i\}\concat C_H'\gets H$
-      \If{$C_H' = \top$}
-        \State \Return $\Store[m]$
-      \EndIf
-      \For{$d\in \{d_i\}$}
-        \Comment{Uniformly randomly chosen}
-        \If{$d\method \Fwd[C_H', m] \neq \bot$}
-          \State \Return $\top$
-        \EndIf
-      \EndFor
-      \State \Return $\bot$
-    \EndFunction
-    \Function{\Store}{$m$}
-      \State $m\gets \DeBEdec[\mpk, \sk, c_m]$
-      \If{$m = \bot$}
-        \State \Return $\bot$
-      \EndIf
-      \State Store $m$ to disk.
-      \State \Return $\top$
-    \EndFunction
-  \end{algorithmic}
-  \end{minipage}}
-  \caption{\label{SPORFwd}%
-    The \(\SPOR[\Fwd]\) algorithm forwards \(m\) down the route \(H\), obtained 
-    by decrypting \(C_H\) with the node's associated private key.
-    The special value \(H = \top\) indicated the end of the route, thus \(c_m\) 
-    is intended for the local node and \(c_m\) is instead sent to disk using 
-    \(\Store\) (\cref{SPORRecv}).%
-  }
-\end{figure}

### 2018-04-30 paper/squad-overlay-design.tex
up

@@
 
-At the root of \name is predictive routing.
+At the root of \name is predictive routing, based on the concept of Probabilistic Onion Routes (POR).
+To create PORs, as a device's availability strongly depends on the activity of its owner,
+ a user's devices (her \squad) must predict the future behavior of their owner. 
+However, one device, belonging to an \squad, can only predict its probability to stay online in the near future
+if it has a global knowledge of the user behavior over the other devices of the \squad it belongs to.
+To reach this aim, \name relies on a \squad overlay to share the user's behavior among devices of its \squad.
+
 %By sharing information among themselves, a user's devices (her \emph{squad}) can model her behavior.
-Our key objective is to enable each online device to predict its probability to stay online in the near future.
-This probability will later be used to create Probabilistic Onion Routes (POR).
-A device's connection depends on the activity of its user; thus, a user's devices (her \squad) want to predict her future behavior.
 
-In this section, we only take interest in one user (called Alice) and her \squad.
+%In this section, we only take interest in one user (called Alice) and her \squad.
 
@@
 
-Online devices want to know whether they are likely to stay online in the near future.
-
-Taken separately, each device only knows local information: when Alice used it, and maybe mobility information if it is mobile.
-When combining these informations, though, we obtain a sequence of the user's behavior that is far more complete.
-For instance, the probability that Alice uses her home computer and workstation simultaneously is null: these devices are too far apart.
-
-The \squad Overlay leverages on a probabilistic dissemination protocol, \textsc{Sprinkler}~\cite{luxey:hal-01704172}, that does just that: 
+%Online devices want to know whether they are likely to stay online in the near future.
+taken separately, each device only knows local information such as when its user used it, and potentially mobility information if it is handheld device.
+When combining all these local observations, each device can obtain a refined model of the user’s behavior to predict its future activity in an accurate manner.
+To build this sequence of observations,
+%a sequence of the user's behavior that is far more complete.
+%For instance, the probability that Alice uses her home computer and workstation simultaneously is null: these devices are too far apart.
+the \squad overlay leverages on a probabilistic dissemination protocol, \textsc{Sprinkler}~\cite{luxey:hal-01704172}.
 it allows one's devices to inform one another every time the user performs an action.
-Previous work in our team~\cite{luxey:cascade} showed that \textsc{Sprinkler} is resilient to devices churn: 
+In our previous work~\cite{luxey:cascade}, we showed that \textsc{Sprinkler} is resilient to devices churn: 
 devices let each other know of what they have missed while offline.
@@
 
-\paragraph*{Other uses of the \squad Overlay} In addition to user's behavior, devices use th \squad Overlay for several purposes.
+\paragraph*{Other uses of the \squad Overlay} In addition to user's behavior, devices use the \squad overlay for several purposes.
 Firstly, they share files location: when Alice wants to share a file $f$ that resides on her home computer, using her smartphone as the exchange initiator, her smartphone knows where $f$ is located and can create the route accordingly.
@@
 
-We need a probabilistic model of the user's behavior to predict its future activity.
-In \name, the only data we collect are the connection times of each device.
+we need a probabilistic model of the user's behavior to predict its future activity.
+In \name, the only data we collect are the availability times of each device.
 In this section only, we discretize time. 
-We store the connection times in an ever-increasing \emph{sequence} $O=O_1, ..., O_i, ...$ of actions performed at every \emph{round}, that lasts a short period of time $T$. 
+We store the availability times in an ever-increasing \emph{sequence} $O=O_1, ..., O_i, ...$ of actions performed at every \emph{round}, that lasts a short period of time $T$. 
 $d \in O_t$ thus means that the device $d$ was online from time $t$ to time $t+T$.
@@
 In our case, the states $\mathcal{S}$ are the different locations $\mathcal{L}$ where the user is susceptible to go.
-The events represent the devices connection, hence $\mathcal{O} = \mathcal{D}$, where $\mathcal{D}$ is the set of the user's devices.
-Several devices can be connected at the same time, such that $O_t$ is a set, and $d \in O_t$ means that device $d$ was connected at time $t$. Devices' connection probabilities are independent.
+The events represent the devices availability, hence $\mathcal{O} = \mathcal{D}$, where $\mathcal{D}$ is the set of the user's devices.
+Several devices can be available at the same time, such that $O_t$ is a set, and $d \in O_t$ means that device $d$ was available at time $t$. Devices' availability probabilities are independent.
 
@@
 \label{para:predicting future behavior}
-As already stated, devices want to predict whether they are likely to be connected in the near future.
-This information will be publicly available, and will enable the intelligent building of routes.
+As already stated, devices want to predict whether they are likely to be available in the near future.
+This information will be publicly available to enable the intelligent building of routes.
 
-Because devices connections only depend on the users location, we can predict the devices connections in $i$ round $O_{t+i}$ given only the model $\lambda_N$ and the current user's location $S_t$.
-We first compute the probability that a device $d$ will be connected next turn:
+Because devices availability only depend on the users location, we can predict the devices availability in $i$ round $O_{t+i}$ given only the model $\lambda_N$ and the current user's location $S_t$.
+We first compute the probability that a device $d$ will be available next turn:
 
@@
 
-We show in section~\ref{sub:predictive_onion_routes_creation} that the prediction of devices' availability at $t+1$ is a good enough estimator of their connection state at $t+i$.
+We show in section~\ref{sub:predictive_onion_routes_creation} that the prediction of devices' availability at $t+1$ is a good enough estimator of their availability state at $t+i$.
 For that reason, devices only compute and publish $P\left[ d \in O_{t+1} \mid S_{t} = s \right]$.

### 2018-04-30 paper/squad-overlay-design.tex
up

@@
 we need a probabilistic model of the user's behavior to predict its future activity.
-In \name, the only data we collect are the availability times of each device.
-In this section only, we discretize time. 
+In \name, the only data we collect and share, through the \squad overlay, are the availability times of each device among a \squad.
+In our model, time is discretized, i.e. users periodically change the availability stated of their devices in a predefined period.
 We store the availability times in an ever-increasing \emph{sequence} $O=O_1, ..., O_i, ...$ of actions performed at every \emph{round}, that lasts a short period of time $T$. 

### 2018-04-30 paper/message-passing-design.tex
this compiles

@@
 \NewAlgorithm{\ExtendRoute}{ExtendRoute}
-\NewAlgorithm{\CreateOnionLayer}{CreateOnionLayer}
+\NewAlgorithm{\CreateOnionLayer}{CreateLayer}
 \NewAlgorithm{\Dec}{Dec}
@@
 \NewVariable{\LRV}{\mathcal{L_{RV}}\xspace}
-\NewVariable{\Hsend}{\mathcal{H}_{\text{send}}\begin{algorithmic}[1]}
-\NewVariable{\Hrec}{\mathcal{H}_{\text{rec}}\begin{algorithmic}[1]}
-\NewVariable{\Hforward}{\mathcal{H}_{\text{forward}}\begin{algorithmic}[1]}
-\NewVariable{\Hbackward}{\mathcal{H}_{\text{backward}}\begin{algorithmic}[1]}
-\NewVariable{\Hsendforward}{\mathcal{H}_{\text{send forward}}\begin{algorithmic}[1]}
-\NewVariable{\Hsendbackward}{\mathcal{H}_{\text{send backward}}\begin{algorithmic}[1]}
-\NewVariable{\Hrecforward}{\mathcal{H}_{\text{rec forward}}\begin{algorithmic}[1]}
-\NewVariable{\Hrecbackward}{\mathcal{H}_{\text{rec backward}}\begin{algorithmic}[1]}
+\NewVariable{\Hsend}{\mathcal{H}_{\text{send}}\xspace}
+\NewVariable{\Hrec}{\mathcal{H}_{\text{rec}}\xspace}
+\NewVariable{\Hforward}{\mathcal{H}_{\text{forward}}\xspace}
+\NewVariable{\Hbackward}{\mathcal{H}_{\text{backward}}\xspace}
+\NewVariable{\Hsendforward}{\mathcal{H}_{\text{send forward}}\xspace}
+\NewVariable{\Hsendbackward}{\mathcal{H}_{\text{send backward}}\xspace}
+\NewVariable{\Hrecforward}{\mathcal{H}_{\text{rec forward}}\xspace}
+\NewVariable{\Hrecbackward}{\mathcal{H}_{\text{rec backward}}\xspace}
 
@@
 Another difference from Tor, where connections are established by all nodes in the route, \name is stateless: the route's ends (the sender Alice and receiver Bob) cooperate to create the headers containing all the necessary routing information for future communication between Alice and Bob.
-In that regard, two headers are required: $\Hforward$ to route packets from Alice to Bob, and $\Hbackward$ for packets from Bob to Alice.
+In that regard, two headers are required: \Hforward to route packets from Alice to Bob, and \Hbackward for packets from Bob to Alice.
 
@@
 Figure~\ref{fig:file-exchange} shows the process of the route creation until the first exchange of a file chunk from Alice to Bob.
-Bob uses the backward route to send acknowledgments back to Alice.
+Alice uses the forward route to send file chunks to Bob, while Bob uses the backward route to send acknowledgments back to Alice.
 
@@
 Alice still has her part of the route to create: like Bob, she randomly picks nodes to constitutes $l$ layers from her \squad to \LRV.
+She also build two headers: \Hsendforward contains the route from her \squad (excluded) to \LRV (included), while \Hsendbackward contains the route from \LRV (excluded) to her \squad (included).
+Alice finally sends \Hsendbackward back to Bob: he is going to need it to sends acknowledgments back to Alice.
 
@@
     % }
-    \Function{\Recv}{$D$}
-      \State $H_\rdv\gets \ExtendRoute[D\concat \top, L, \theta]$
-      \State \Return $H_\rdv$
-        \Comment{Give to sender out-of-bound.}
+    \Function{\Recv}{sender}
+      \State $\LRV \gets \CreateOnionLayer()$
+      \State layers $\gets [\,]$
+      % \While{len(layers) $ < l$}
+      %   \State layers.append(\CreateOnionLayer())
+      % \EndWhile
+      % \State \Hrecforward \gets properly encrypted layers
+      % \State \Hrecbackward \gets properly encrypted layers
+      % \State \Hsendforward \gets sender.\Send(\Hrecforward, \LRV)
+      % \State \Hbackward \gets \Hrecbackward || \Hsendbackward
+      % \State $H_\rdv\gets \ExtendRoute[D\concat \top, L, \theta]$
+      % \State \Return $H_\rdv$
+      %   \Comment{Give to sender out-of-bound.}
     \EndFunction
@@
     % }
-    \Function{\ExtendRoute}{$H, L, \theta$}
+    \Function{\ExtendRoute}{$\mathcal{H}, l$}
       \If{$L\leq 0$}
@@
   \vspace{0.3em}
-    \Function{\CreateOnionLayer}{$\theta$}
+    \Function{\CreateOnionLayer}{\null}
       \State $(d, \pk_d, p_d)\gets \GetRandomPeer$

### 2018-04-30 paper/message-passing-design.tex
finished writing build route, lacks encryption
lala

@@
 \NewAlgorithm{\Fwd}{Forward}
-\NewAlgorithm{\Send}{BuildRouteSender}
-\NewAlgorithm{\Recv}{BuildRouteReceiver}
+\NewAlgorithm{\Send}{BuildRouteS}
+\NewAlgorithm{\Recv}{BuildRouteR}
 \NewAlgorithm{\ExtendRoute}{ExtendRoute}
@@
 \NewVariable{\Hrec}{\mathcal{H}_{\text{rec}}\xspace}
-\NewVariable{\Hforward}{\mathcal{H}_{\text{forward}}\xspace}
-\NewVariable{\Hbackward}{\mathcal{H}_{\text{backward}}\xspace}
-\NewVariable{\Hsendforward}{\mathcal{H}_{\text{send forward}}\xspace}
-\NewVariable{\Hsendbackward}{\mathcal{H}_{\text{send backward}}\xspace}
-\NewVariable{\Hrecforward}{\mathcal{H}_{\text{rec forward}}\xspace}
-\NewVariable{\Hrecbackward}{\mathcal{H}_{\text{rec backward}}\xspace}
+\NewVariable{\Hforward}{\mathcal{H}_f \xspace}
+\NewVariable{\Hbackward}{\mathcal{H}_b \xspace}
+\NewVariable{\Hsendforward}{\mathcal{H}_{\text{send f}}\xspace}
+\NewVariable{\Hsendbackward}{\mathcal{H}_{\text{send b}}\xspace}
+\NewVariable{\Hrecforward}{\mathcal{H}_{\text{rec f}}\xspace}
+\NewVariable{\Hrecbackward}{\mathcal{H}_{\text{rec b}}\xspace}
+%\NewVariable{\nfilechunks}{\#\text{chunks}}
 
@@
 They create a route of $L$ layers, a configuration parameter that must be odd. We introduce $l=(L-1)/2$.
-Bob (the receiver) initiates the route creation. 
+
+Bob (the receiver) initiates the route creation by calling the \Recv function displayed in figure~\ref{fig:route building algo}
 He randomly chooses nodes to constitute a rendez-vous layer \LRV, and nodes to constitute $l$ layers from \LRV to his \squad. 
@@
 
-Bob sends \Hrecforward and the descriptors of the \LRV nodes to Alice.
-Alice still has her part of the route to create: like Bob, she randomly picks nodes to constitutes $l$ layers from her \squad to \LRV.
-She also build two headers: \Hsendforward contains the route from her \squad (excluded) to \LRV (included), while \Hsendbackward contains the route from \LRV (excluded) to her \squad (included).
-Alice finally sends \Hsendbackward back to Bob: he is going to need it to sends acknowledgments back to Alice.
+Bob then sends \Hrecforward and the descriptors of the \LRV nodes to Alice, by calling Alice's \Send function (also in figure~\ref{fig:route building algo}).
+like Bob, Alice randomly picks nodes to constitutes $l$ layers from her \squad to \LRV.
+She also builds two encrypted headers: \Hsendforward contains the route from her \squad (excluded) to \LRV (included), while \Hsendbackward contains the route from \LRV (excluded) to her \squad (included).
+Alice finally sends \Hsendbackward back to Bob.
+
+Back to Bob's \Recv
 
 \paragraph*{Layer creation}
+
+The
 
@@
       \State layers $\gets [\,]$
-      % \While{len(layers) $ < l$}
-      %   \State layers.append(\CreateOnionLayer())
-      % \EndWhile
-      % \State \Hrecforward \gets properly encrypted layers
-      % \State \Hrecbackward \gets properly encrypted layers
-      % \State \Hsendforward \gets sender.\Send(\Hrecforward, \LRV)
-      % \State \Hbackward \gets \Hrecbackward || \Hsendbackward
-      % \State $H_\rdv\gets \ExtendRoute[D\concat \top, L, \theta]$
+      \While{len(layers) $ < l$}
+        \State layers.append(\CreateOnionLayer())
+      \EndWhile
+      \State $\Hrecforward \gets$ properly encrypted layers
+      \State $\Hrecbackward \gets$ properly encrypted layers
+
+      \Comment{Out-of-band exchange}
+      \State $\Hsendbackward \gets$ sender.\Send(\Hrecforward, \LRV)
+
+      \State $\Hbackward \gets \Hrecbackward \concat \Hsendbackward$
+      %\State $H_\rdv\gets \ExtendRoute[D\concat \top, L, \theta]$
       % \State \Return $H_\rdv$
@@
     % }
-    \Function{\Send}{$H_\rdv, m$}
-      \State $H\gets \ExtendRoute[H_\rdv, L, \theta]$
-      \State $D\concat C_H\gets H_\rdv$
-      \For{$d\in D$}
-        \Comment{Uniformly randomly chosen}
-        \If{$d\method \Fwd[C_H, m] \neq \bot$}
-          \State \Return $\top$
-        \EndIf
-      \EndFor
-      \State \Return $\bot$
+    \Function{\Send}{\Hrecforward, \LRV}
+      \State layers $\gets [\,]$
+      \While{len(layers) $ < l$}
+        \State layers.append(\CreateOnionLayer())
+      \EndWhile
+      \State $\Hsendforward \gets$ properly encrypted layers
+      \State $\Hsendbackward \gets$ properly encrypted layers
+      \State $\Hforward \gets \Hsendforward \concat \Hrecforward$
+      \State \Return \Hsendbackward
+
+      % \State $H\gets \ExtendRoute[H_\rdv, L, \theta]$
+      % \State $D\concat C_H\gets H_\rdv$
+      % \For{$d\in D$}
+      %   \Comment{Uniformly randomly chosen}
+      %   \If{$d\method \Fwd[C_H, m] \neq \bot$}
+      %     \State \Return $\top$
+      %   \EndIf
+      % \EndFor
+      % \State \Return $\bot$
     \EndFunction
@@
 
+  % \vspace{0.3em}
+  % %\framebox{\begin{minipage}{0.96\linewidth}
+  % \begin{algorithmic}[1]
+  %   % \Require{%
+  %   %   $H$ is a header of the form \(D\concat H'\) or \(D\concat \top\), where 
+  %   %   \(D\) is a set of device addresses.
+  %   %   $\pk_D$ is the public key of device set $D$.
+  %   %   $L$ is the length of the route,
+  %   %   $\theta$ is the threshold of probability of failure.%
+  %   % }
+  %   \Function{\ExtendRoute}{$\mathcal{H}, l$}
+  %     \If{$L\leq 0$}
+  %       \State \Return $H$
+  %     \EndIf
+  %     \State $D\gets \CreateOnionLayer[\theta]$
+  %     \State $H\gets D\concat \DeBEenc[\mpk, D, H]$
+  %     \State \Return $\ExtendRoute[H, L-1, \theta]$
+  %   \EndFunction
+  % \end{algorithmic}
+
   \vspace{0.3em}
-  %\framebox{\begin{minipage}{0.96\linewidth}
+
   \begin{algorithmic}[1]
-    % \Require{%
-    %   $H$ is a header of the form \(D\concat H'\) or \(D\concat \top\), where 
-    %   \(D\) is a set of device addresses.
-    %   $\pk_D$ is the public key of device set $D$.
-    %   $L$ is the length of the route,
-    %   $\theta$ is the threshold of probability of failure.%
-    % }
-    \Function{\ExtendRoute}{$\mathcal{H}, l$}
-      \If{$L\leq 0$}
-        \State \Return $H$
-      \EndIf
-      \State $D\gets \CreateOnionLayer[\theta]$
-      \State $H\gets D\concat \DeBEenc[\mpk, D, H]$
-      \State \Return $\ExtendRoute[H, L-1, \theta]$
-    \EndFunction
-  \vspace{0.3em}
     \Function{\CreateOnionLayer}{\null}
       \State $(d, \pk_d, p_d)\gets \GetRandomPeer$
-      \State $D\gets \{(d, \pk_d, p_d)\}$
-      \While{$\prod_{d\in D} p_d > \theta$}
+      \State $\mathcal{L}\gets \{(d, \pk_d, p_d)\}$
+      \While{$\prod_{d\in \mathcal{L}} p_d > \theta$}
         \State $(d, \pk_d, p_d)\gets \GetRandomPeer$
-        \State $D\gets D\cup \{(d, \pk_d, p_d)\}$
+        \State $\mathcal{L}\gets \mathcal{L}\cup \{(d, \pk_d, p_d)\}$
       \EndWhile
-      \State \Return $D$
+      \State \Return $\mathcal{L}$
     \EndFunction

### 2018-04-30 paper/message-passing-design.tex
removed comments

@@
 She also builds two encrypted headers: \Hsendforward contains the route from her \squad (excluded) to \LRV (included), while \Hsendbackward contains the route from \LRV (excluded) to her \squad (included).
+Alice now ha the full forward header \Hforward, as shown on line~\ref{hforward}
 Alice finally sends \Hsendbackward back to Bob.
 
-Back to Bob's \Recv
+Back to \Recv function: Bob has the full backward header $\Hbackward$, as shown on line~\ref{hbackward}.
 
 \paragraph*{Layer creation}
+The function \CreateOnionLayer() iteratively add random nodes (from the RPS's view \view) until the product $\prod_{d\in \mathcal{L}} (1 - p_d)$ falls below $\theta$.
+$(1 - p_d)$ is the probability that a device $d$ will be offline; the product is the probability that all devices on layer $\mathcal{L}$ fall offline at the same time.
 
-The
-
-\paragraph*{Header preparation}
+%\paragraph*{Header preparation}
 
@@
 
-      \State $\Hbackward \gets \Hrecbackward \concat \Hsendbackward$
+      \State $\Hbackward \gets \Hrecbackward \concat \Hsendbackward$ \label{hbackward}
       %\State $H_\rdv\gets \ExtendRoute[D\concat \top, L, \theta]$
@@
       \State $\Hsendbackward \gets$ properly encrypted layers
-      \State $\Hforward \gets \Hsendforward \concat \Hrecforward$
+      \State $\Hforward \gets \Hsendforward \concat \Hrecforward$ \label{hforward}
       \State \Return \Hsendbackward
@@
       \State $\mathcal{L}\gets \{(d, \pk_d, p_d)\}$
-      \While{$\prod_{d\in \mathcal{L}} p_d > \theta$}
+      \While{$\prod_{d\in \mathcal{L}} (1 - p_d) \geq \theta$}
         \State $(d, \pk_d, p_d)\gets \GetRandomPeer$

### 2018-04-30 paper/system-model.tex
Updates bibsp again, fixes Sonja's comment in sys model

@@
 Each device can communicate with any other device that it knows the
-address for. All devices belonging to one user
+address for (\eg using the Internet). All devices belonging to one user
  know which other devices belong to the same user, \ie the \squad.
@@
 the \squad it belongs to.
+We also assume that the users can exchange some limited amounts of data 
+out-of-band, \ie through some other channel than the network just mentioned (\eg 
+using \ac{NFC}).
 

### 2018-04-30 paper/file-exchange-design.tex
yaaaay, outline figure
removed unbound references to article

--- 2018-04-28 paper/file-exchange.tex
@@
 \subsection{Scheduling and transferring a file}%
-\label{file-transfer}
+\label{sec:file_exchange}
 
@@
   \item Bob creates an onion route header, \(H_\rdv\), by running 
-    \(\SPOR[\Recv]\) (\cref{SPORRecv}) and gives it to Alice.
+    \([\Recv]\) %(\cref{SPORRecv}) 
+    and gives it to Alice.
   \item Alice gives Bob number of file chunks, \(n\), and the size of the file 
@@
 She then divides \(c_f\) into \(n\) chunks, \(c_f^{(1)}, \dotsc, c_f^{(n)}\), 
-and runs \(\SPOR[\Send](H_\rdv, c_f^{(i)})\) for all \(1\leq i\leq n\) in 
+and runs \([\Send](H_\rdv, c_f^{(i)})\) for all \(1\leq i\leq n\) in 
 parallel.

### 2018-04-30 paper/message-passing-design.tex
removed unbound references to article

@@
 
+Once Alice get the \(H_\rdv\), Alice uses \([\Send]\) at some
+later time to send the message to Bob using any of her devices from
+its \squad.% (See \cref{SPORSend}). 
+First, \([\Send]\) extends the route
+\(H_\rdv\) with some hops of Alice's choosing (uniformly randomly
+chosen). Second, \([\Send]\) extracts from the onion the first
+layer, which contained the overall
+possible rendez-vous points $D$ previously selected by the recipient (i.e. Bob).
+One device from $D$ is randomly chosen, and the \([\Fwd]\)
+sub-function is called as long as the message forwarding to one node of
+the next layer is not successful.% (See \cref{SPORFwd}). 
+Along the path, each node decrypts
+in sequence the different layer with the current node’s private key. 
+The end of the route is reached when special value \(H_\rdv = \top\) is
+encountered. Consequently the ciphered message \(c_m\) is then stored
+in the disk of the local node through the \(\Store\) sub function.%(\cref{SPORRecv}).
+
+\david{the use of DeBE algorithms must be explicitly explained here}
+
 \begin{figure}[t]
@@
     %\Require{$\pk, \sk$ is the public--private key-pair of the node.}
-    \Function{\SPOR[\Fwd]}{$C_H, m$}
+    \Function{[\Fwd]}{$C_H, m$}
       \State $H\gets \DeBEdec[\mpk, \sk, C_H]$
@@
   \caption{\label{SPORFwd}%
-    The \(\SPOR[\Fwd]\) algorithm forwards \(m\) down the route \(H\), obtained 
+    The \([\Fwd]\) algorithm forwards \(m\) down the route \(H\), obtained 
     by decrypting \(C_H\) with the node's associated private key.
@@
     is intended for the local node and \(c_m\) is instead sent to disk using 
-    \(\Store\) (\cref{SPORRecv}).%
+    \(\Store\).% (\cref{SPORRecv}).%
   }
@@
 
-For instance, if Alice wants to send a message \(m\) to Bob, they are both going to perform a part of the building algorithm.
-Bob uses the \(\SPOR[\Recv]\) function (See \cref{SPORRecv}) to create a probabilistic onion route $\mathcal{H_B}$ from
- a rendez-vous (RV) layer $\mathcal{L_{RV}}$ to its own devices from its \squad---all the hops on the route are 
-chosen by Bob uniformly at random from the Global Overlay.
- \(\SPOR[\Recv]\)
-returns $\mathcal{H_B}$ and  that Bob gives to Alice using an
-out-of-band channel, \eg using one device of its \squad.
-PORs have \(L\) layers, and for each layer the number of
-alternatives nodes depends of a failure threshold \(\theta\). 
-As long as \(\theta\) is not exceeded, alternatives nodes are added in
-\(H_\rdv\) as depicted in \cref{ExtendRoute}. Thus the probability of
-failure for the extension is \(1 - (1 - \theta)^L\).
+% For instance, if Alice wants to send a message \(m\) to Bob, they are both going to perform a part of the building algorithm.
+% Bob uses the \([\Recv]\) function (See \cref{SPORRecv}) to create a probabilistic onion route $\mathcal{H_B}$ from
+%  a rendez-vous (RV) layer $\mathcal{L_{RV}}$ to its own devices from its \squad---all the hops on the route are 
+% chosen by Bob uniformly at random from the Global Overlay.
+%  \(\SPOR[\Recv]\)
+% returns $\mathcal{H_B}$ and  that Bob gives to Alice using an
+% out-of-band channel, \eg using one device of its \squad.
+% PORs have \(L\) layers, and for each layer the number of
+% alternatives nodes depends of a failure threshold \(\theta\). 
+% As long as \(\theta\) is not exceeded, alternatives nodes are added in
+% \(H_\rdv\) as depicted in \cref{ExtendRoute}. Thus the probability of
+% failure for the extension is \(1 - (1 - \theta)^L\).
 
-Once Alice get the \(H_\rdv\), Alice uses \(\SPOR[\Send]\) at some
-later time to send the message to Bob using any of her devices from
-its \squad (See \cref{SPORSend}). First, \(\SPOR[\Send]\) extends the route
-\(H_\rdv\) with some hops of Alice's choosing (uniformly randomly
-chosen). Second, \(\SPOR[\Send]\) extracts from the onion the first
-layer, which contained the overall
-possible rendez-vous points $D$ previously selected by the recipient (i.e. Bob).
-One device from $D$ is randomly chosen, and the \(\SPOR[\Fwd]\)
-sub-function is called as long as the message forwarding to one node of
-the next layer is not successful (See \cref{SPORFwd}). Along the path, each node decrypts
-in sequence the different layer with the current node’s private key. 
-The end of the route is reached when special value \(H_\rdv = \top\) is
-encountered. Consequently the ciphered message \(c_m\) is then stored
-in the disk of the local node through the \(\Store\) sub function 
-(\cref{SPORRecv}).
-
-\david{the use of DeBE algorithms must be explicitly explained here}
+% Once Alice get the \(H_\rdv\), Alice uses \(\SPOR[\Send]\) at some
+% later time to send the message to Bob using any of her devices from
+% its \squad (See \cref{SPORSend}). First, \(\SPOR[\Send]\) extends the route
+% \(H_\rdv\) with some hops of Alice's choosing (uniformly randomly
+% chosen). Second, \(\SPOR[\Send]\) extracts from the onion the first
+% layer, which contained the overall
+% possible rendez-vous points $D$ previously selected by the recipient (i.e. Bob).
+% One device from $D$ is randomly chosen, and the \(\SPOR[\Fwd]\)
+% sub-function is called as long as the message forwarding to one node of
+% the next layer is not successful (See \cref{SPORFwd}). Along the path, each node decrypts
+% in sequence the different layer with the current node’s private key. 
+% The end of the route is reached when special value \(H_\rdv = \top\) is
+% encountered. Consequently the ciphered message \(c_m\) is then stored
+% in the disk of the local node through the \(\Store\) sub function 
+% (\cref{SPORRecv}).
 

### 2018-04-30 paper/intro.tex
up

@@
 
-In this paper, we demonstrate how good performance can be reconciled with strong privacy protection in data-sharing systems. We present \name{}, a novel fully decentralized, autonomous,
+In this paper, we demonstrate how good performance can be reconciled
+with strong privacy protection in data-sharing systems. We present
+\name{}, a novel fully decentralized, autonomous,
+
 % approach that provides a 
@@
 
-Our contributions are as follows: \david{please update}
+Our contributions are as follows: 
 \begin{itemize}
-\item We showed the effectiveness of \iac{ANOBE} scheme by \textcite{ANOBE} 
-  to build a \ac{DeBE} as required by \name to
-  provide.... 
-\item A \squad overlay 
-\item Model the user’s behavior as a Hidden Markov Models (HMMs)
-\item SPOR provides stateless algorithms for the onion-routing.
-\item An evaluation testbed where each user’s behavior
+\item We have designed \name, a novel fully decentralized, autonomous,
+and self-organizing file sharing service among users based on a novel
+concept named Probabilistic Onion Routes (POR), which combines onion routing with
+probabilistic node selection, informed by random peer sampling and
+Hidden Markov Model predictions for node availability. 
+\item  We have demonstrated the successfulness of our approach. Even
+  suboptimal prediction results in successful file transfer with high
+  probability. 
 \end{itemize}
 
-In the following, we detail \name 's concepts and approach...
-
+In the following, in Section~\ref{system-model}, we introduce the
+adversary model the desired privacy properties of \name. Section~\ref{design}
+introduce the design of our proposed solution. Section~\ref{Performance}
+evaluates the proposed approach. In Section~\ref{security-discussion}, we lead a security discussion
+about advantages, shortcomings of our approach.
+Finally, Section~\ref{conclusion} discusses future work and conclusions.
 % Cashmere: resilient anonymous routing.

### 2018-04-30 paper/system-model.tex
up

--- 2018-04-30 paper/system-model.tex
@@
 provider, to make it available to Bob that will thereafter get it from
-one of its devices. The use of the cloud provider as a third party
+one of its devices. The use of the cloud provider, as a third party,
 provides two main privacy properties, which we have to consider when

### 2018-04-30 paper/intro.tex
up

@@
 In the following, in Section~\ref{system-model}, we introduce the
-adversary model the desired privacy properties of \name. Section~\ref{design}
-introduce the design of our proposed solution. Section~\ref{Performance}
+adversary model and the desired privacy properties of \name. Section~\ref{design}
+introduces the design of our proposed solution. Section~\ref{Performance}
 evaluates the proposed approach. In Section~\ref{security-discussion}, we lead a security discussion
-about advantages, shortcomings of our approach.
+about advantages, and shortcomings of our approach.
 Finally, Section~\ref{conclusion} discusses future work and conclusions.

### 2018-04-30 paper/file-exchange-design.tex
minor

@@
 She then divides \(c_f\) into \(n\) chunks, \(c_f^{(1)}, \dotsc, c_f^{(n)}\), 
-and runs \([\Send](H_\rdv, c_f^{(i)})\) for all \(1\leq i\leq n\) in 
+and runs \(\Send(H_\rdv, c_f^{(i)})\) for all \(1\leq i\leq n\) in 
 parallel.

### 2018-04-30 paper/message-passing-design.tex
minor

@@
 \(H_\rdv\) with some hops of Alice's choosing (uniformly randomly
-chosen). Second, \([\Send]\) extracts from the onion the first
+chosen). Second, \(\Send\) extracts from the onion the first
 layer, which contained the overall
 possible rendez-vous points $D$ previously selected by the recipient (i.e. Bob).
-One device from $D$ is randomly chosen, and the \([\Fwd]\)
+One device from $D$ is randomly chosen, and the \(\Fwd\)
 sub-function is called as long as the message forwarding to one node of
@@
     %\Require{$\pk, \sk$ is the public--private key-pair of the node.}
-    \Function{[\Fwd]}{$C_H, m$}
+    \Function{\Fwd}{$C_H, m$}
       \State $H\gets \DeBEdec[\mpk, \sk, C_H]$
@@
   \caption{\label{SPORFwd}%
-    The \([\Fwd]\) algorithm forwards \(m\) down the route \(H\), obtained 
+    The \(\Fwd\) algorithm forwards \(m\) down the route \(H\), obtained 
     by decrypting \(C_H\) with the node's associated private key.

### 2018-04-30 paper/message-passing-design.tex
readded comments

@@
 \NewVariable{\Hrec}{\mathcal{H}_{\text{rec}}\xspace}
-\NewVariable{\Hforward}{\mathcal{H}_f \xspace}
-\NewVariable{\Hbackward}{\mathcal{H}_b \xspace}
+\NewVariable{\Hforward}{\mathcal{H}_f\xspace}
+\NewVariable{\Hbackward}{\mathcal{H}_b\xspace}
 \NewVariable{\Hsendforward}{\mathcal{H}_{\text{send f}}\xspace}
@@
 %\NewVariable{\nfilechunks}{\#\text{chunks}}
-
-\david{each protocol should be explained individually}
 
@@
 \paragraph*{Layer creation}
-The function \CreateOnionLayer() iteratively add random nodes (from the RPS's view \view) until the product $\prod_{d\in \mathcal{L}} (1 - p_d)$ falls below $\theta$.
+The function \CreateOnionLayer() iteratively adds random nodes (from the RPS's view \view) until the product $\prod_{d\in \mathcal{L}} (1 - p_d)$ falls below $\theta$.
 $(1 - p_d)$ is the probability that a device $d$ will be offline; the product is the probability that all devices on layer $\mathcal{L}$ fall offline at the same time.

### 2018-04-30 paper/message-passing-design.tex
experiments and text

@@
 
-%\paragraph*{Header preparation}
+\begin{table}[t]
+\resizebox{\columnwidth}{!}{
+\begin{tabular}{lp{0.9\linewidth}}
+\toprule
+\multicolumn{2}{c}{\textbf{Parameters of the algorithm}} \\
+\midrule
+$\theta$ & Stopping criterion for the layers creation: maximum authorized  probability that all devices in a layer fail at once. \\
+$L$      & Number of layers in a Predictive Onion Route. \\
+$l = (L-1)/2$ & Number of layers (excluding $\LRV$) created by each end of the route. \\
+\bottomrule
+\end{tabular}
+}
+\label{tab:parameters}
+\end{table}
+
+\paragraph*{Header preparation} \commentAL{TODO}
 
@@
 
-Once Alice get the \(H_\rdv\), Alice uses \([\Send]\) at some
+Once Alice get the \(H_\rdv\), Alice uses \(\Send\) at some
 later time to send the message to Bob using any of her devices from
 its \squad.% (See \cref{SPORSend}). 
-First, \([\Send]\) extends the route
+First, \(\Send\) extends the route
 \(H_\rdv\) with some hops of Alice's choosing (uniformly randomly

### 2018-04-30 code/file_exchange/file.py

@@ -6,7 +6,7 @@ from .utils import random_string
 import random
 
 
-FILE_ID_SIZE = 6
+FILE_ID_SIZE = 12
 
 
 # We use this class to represent files to share and files to receive

### 2018-04-30 code/file_exchange/network.py

@@ -51,7 +51,7 @@ class MessType(Enum):
     ACK = 2
 
 
-MAX_MESSAGE_ID = 2**16
+MAX_MESSAGE_ID = 2**63
 
 
 class Message:

### 2018-04-30 paper/design.tex
up
wrote a bit and experiments are undergoing

--- 2018-04-29 paper/design.tex
@@
 \section{Design of the \name file exchange system}
-
+\label{design}
 This section presents the \name protocol in detail.
@@
 This \emph{Global Overlay} will be covered in section~\ref{sec:global_overlay}.
-The information brought by these overlays allows devices to securely and reliably exchange messages between users by creating PORs, as will be explained in section~\ref{sec:message_passing}.
-Given this message passing protocol, users can privately exchange files, as shown in the bottom of the figure. We will cover this ultimate goal in section~\ref{sec:file_exchange}.
+The information brought by these overlays allows devices to securely and reliably exchange messages between users by creating PORs, thus enabling file exchange between users, as will be explained in section~\ref{sec:message_passing}.
+%Given this message passing protocol, users can privately exchange files, as shown in the bottom of the figure. We will cover this ultimate goal in section~\ref{sec:file_exchange}.
 
@@
 \include*{message-passing-design}
-\include*{file-exchange-design}
+%\include*{file-exchange-design}

### 2018-04-30 paper/message-passing-design.tex
wrote a bit and experiments are undergoing

@@
 \NewVariable{\Hrecbackward}{\mathcal{H}_{\text{rec b}}\xspace}
+\NewVariable{\datakey}{k_{\text{data}}\xspace}
 %\NewVariable{\nfilechunks}{\#\text{chunks}}
+
+\david{the use of DeBE algorithms must be explicitly explained in this section}
 
@@
 
-When Alice wants to send a file to Bob, they first have to call the route building algorithm, and to exchange relevant information out of band (e.g. using mail, or their phones' bluetooth connection).
+\commentAL{A symmetric key \datakey should be exchanged during this step, to encrypt the data}
+
+When Alice wants to send a file $f$ to Bob, they first have to call the route building algorithm, and to exchange relevant information out of band (e.g.
+using mail, or their phones' bluetooth connection).
 They create a route of $L$ layers, a configuration parameter that must be odd. We introduce $l=(L-1)/2$.
@@
 
-Once Alice get the \(H_\rdv\), Alice uses \(\Send\) at some
-later time to send the message to Bob using any of her devices from
-its \squad.% (See \cref{SPORSend}). 
-First, \(\Send\) extends the route
-\(H_\rdv\) with some hops of Alice's choosing (uniformly randomly
-chosen). Second, \(\Send\) extracts from the onion the first
-layer, which contained the overall
-possible rendez-vous points $D$ previously selected by the recipient (i.e. Bob).
-One device from $D$ is randomly chosen, and the \(\Fwd\)
-sub-function is called as long as the message forwarding to one node of
-the next layer is not successful.% (See \cref{SPORFwd}). 
-Along the path, each node decrypts
-in sequence the different layer with the current node’s private key. 
-The end of the route is reached when special value \(H_\rdv = \top\) is
-encountered. Consequently the ciphered message \(c_m\) is then stored
-in the disk of the local node through the \(\Store\) sub function.%(\cref{SPORRecv}).
-
-\david{the use of DeBE algorithms must be explicitly explained here}
+% Alice uses \(\Send\) at some
+% later time to send the message to Bob using any of her devices from
+% its \squad.% (See \cref{SPORSend}). 
+% First, \(\Send\) extends the route
+% \(H_\rdv\) with some hops of Alice's choosing (uniformly randomly
+% chosen). Second, \(\Send\) extracts from the onion the first
+% layer, which contained the overall
+% possible rendez-vous points $D$ previously selected by the recipient (i.e. Bob).
+% One device from $D$ is randomly chosen, and the \(\Fwd\)
+% sub-function is called as long as the message forwarding to one node of
+% the next layer is not successful.% (See \cref{SPORFwd}). 
+% Along the path, each node decrypts
+% in sequence the different layer with the current node’s private key. 
+% The end of the route is reached when special value \(H_\rdv = \top\) is
+% encountered. Consequently the ciphered message \(c_m\) is then stored
+% in the disk of the local node through the \(\Store\) sub function.%(\cref{SPORRecv}).
 
@@
 \end{figure}
+
+\subsubsection{Exchanging a file} % (fold)
+\label{ssub:exchanging_a_file}
+
+% subsubsection exchanging_a_file (end)
+\newcommand{\messagesize}{\ensuremath{s_m}}
+\newcommand{\filesize}{\ensuremath{s_f}}
+\newcommand{\headersize}{\ensuremath{s_{\mathcal{H}}}}
+
+Once Alice get the \Hforward, she can start sending her file $f$ to Bob. 
+To do so, she chunks it to pieces, and iteratively send the chunks to Bob, that replies with an acknowledgment (ACK) for that chunk.
+Once all chunks have been acknowledged, Alice sends an empty message to Bob, signifying transfer termination.
+
+To prevent \name from message size analysis attacks, the messages have a fixed size \messagesize.
+As shown in the previous section~\ref{ssub:building_routes}, headers have a variable size \headersize per route (but \Hforward remains constant once the POR is established).
+For this reason, file chunks have a fixed size per session: $\filesize = \messagesize - \headersize$.
+
+A message payload is composed of the following information:
+
+\begin{itemize}
+  \item An identifier for the file;
+  \item The chunk ID, that identifies its position in $f$;
+  \item The file chunk;
+  \item An error correction code (e.g. a SHA-1 hash of the chunk, à la BitTorrent\cite{bt_bep3}).
+\end{itemize}
+
+Payloads are encoded using \datakey that was shared between Alice and Bob during route creation \commentAL{Not done}.
+
+% We are interested in transferring large files.
+% Every device \(d\in D\) in the global device swarm is only periodically online.
+% We will thus divide the data to send into \(n\) smaller chunks (similar to 
+% BitTorrent~\cite{BitTorrent}).
+% The idea is to choose \(n\) such that each chunk will be small enough to be 
+% successfully relayed by a device before it goes offline again.
+% The chunk size is empirically determined in \cref{Performance}.
+% \commentDaniel{Adrien, is that true?}
+
+% As stated above, Alice and Bob exchange some limited data out-of-bound using 
+% their smartphones.
+% The information they will exchange is the following:
+% \begin{enumerate}
+%   \item Bob creates an onion route header, \(H_\rdv\), by running 
+%     \([\Recv]\) %(\cref{SPORRecv}) 
+%     and gives it to Alice.
+%   \item Alice gives Bob number of file chunks, \(n\), and the size of the file 
+%     chunks.
+%   \item They agree on a file-specific key \(k\) for some (authenticated) 
+%     encryption scheme \(\Enc*\).
+% \end{enumerate}
+% Then Alice encrypts the file \(f\) and receives the ciphertext \(c_f\gets 
+%   \Enc*[Enc](k, f)\).
+% She then divides \(c_f\) into \(n\) chunks, \(c_f^{(1)}, \dotsc, c_f^{(n)}\), 
+% and runs \(\Send(H_\rdv, c_f^{(i)})\) for all \(1\leq i\leq n\) in 
+% parallel.
+% \commentDaniel{Or shall we do it sequentially?}
 

### 2018-05-01 code/file_exchange/config.py
code

@@ -23,5 +23,4 @@ default = {
     'output_dir': 'data/'+EXPERIMENT_NAME+'/',
     'period': timedelta(seconds=1),  # don't put milliseconds!
     'ping_time': 0.1,  # s
-    'send_strategy': 'random',  # 'random' or 'random_connected'
 }

### 2018-05-01 code/file_exchange/device.py

@@ -291,14 +291,14 @@ class Device(gevent.Greenlet):
             raise ValueError("role should be either 'sender' or 'receiver'")
 
         self.random_peer_sampling()
-
-        route = [pd.DataFrame() for _ in range(n_layers)]
-        view = self.peers_view.get().copy()
-
+        view = self.peers_view.get()
         if len(view) == 0:
             raise Exception("The view is empty")
 
+        route = [pd.DataFrame() for _ in range(n_layers)]
         converged_layers = [False for _ in range(n_layers)]
+        minimum_probability = self.conf['minimum_node_availability']
+
         # Converged when all layers are converged
         while not all(converged_layers):
             # Iteratively add one device per layer until converged
@@ -307,15 +307,27 @@ class Device(gevent.Greenlet):
                 if converged_layers[l_id]:
                     continue
 
-                # If view is empty, exit
-                if len(view) == 0:
+                # We only pick the devices having a proba > minimum_probability
+                most_probable_devices = view[view['p'] >=
+                                             minimum_probability]
+
+                # If most_probable_devices is empty
+                if len(most_probable_devices) == 0:
+                    # Increase minimum_probability and break
+                    minimum_probability = max(0, minimum_probability-0.1)
                     break
 
                 # Add a node to layer
-                # By picking a device from view without replacement
-                d = view.iloc[np.random.choice(len(view))]
-                route[l_id] = route[l_id].append(d)
+                # By picking a device from most_probable_devices
+                # without replacement (we drop d from the view)
+                d = most_probable_devices.iloc[np.random.choice(
+                    len(most_probable_devices))].copy()
                 view.drop(d.name, inplace=True)
+
+                # Let the node report the minimum_probability
+                d['minimum_probability'] = minimum_probability
+                # And append
+                route[l_id] = route[l_id].append(d)
 
                 # Probability that all devices of layer will be offline
                 p_failure = (1 - route[l_id]['p']).prod()

### 2018-05-01 paper/related.tex

@@
 In our context, however, they are less suitable due to their reliance on mix servers, the limited protection against statistical inference possible for even a perfect mixnet given the multiple varying sources and destinations of our use case, and the delay they would add due to batching.
-We thus decided for an approach based on onion routing.
+We thus decided for an approach based on onion routing, which also entails sender-receiver anonymity.
 
-P2P file sharing has been researched extensively, with respect to aspects such as architecture (starting with the semi-centralized Napster, then decentralized Gnutella), availability and replication~\cite{replica}, scalability (Bittorrent~\cite{bittorrent}), anonymity (Freenet~\cite{freenet}, TOR~\cite{Tor}), and distributed hash tables (DHT) such as CAN, Chord, Pastry, and Tapestry (see \cite{dhtchurn} for an overview).
+P2P file sharing has been researched extensively, with respect to aspects such as architecture (starting with the semi-centralized Napster, then decentralized Gnutella), availability and replication~\cite{replica}, scalability (Bittorrent~\cite{bittorrent}), anonymity (Freenet~\cite{Clarke:2001}, TOR~\cite{Tor}), and distributed hash tables (DHT) such as CAN, Chord, Pastry, and Tapestry (see \cite{dhtchurn} for an overview).
 In contrast to our work, the main goal was to enable dissemination to many users who do not necessarily know each other in person.

### 2018-05-01 paper/squad-overlay-design.tex

@@
 if it has a global knowledge of the user behavior over the other devices of the \squad it belongs to.
-To reach this aim, \name relies on a \squad overlay to share the user's behavior among devices of its \squad.
+To reach this aim, \name relies on a overlay, named thereafter the \squad overlay, to share the user's behavior among devices of its \squad.
 
@@
 %Online devices want to know whether they are likely to stay online in the near future.
-taken separately, each device only knows local information such as when its user used it, and potentially mobility information if it is handheld device.
-When combining all these local observations, each device can obtain a refined model of the user’s behavior to predict its future activity in an accurate manner.
-To build this sequence of observations,
+taken separately, each device can only get local observations, such as when its user used it, and mobility information if it is a handheld device.
+If all these local observations can be combined, a device can infer a refined model of the user’s behavior to predict its future activity in an accurate manner.
+To build such a sequence of observations,
 %a sequence of the user's behavior that is far more complete.
@@
 In \name, the only data we collect and share, through the \squad overlay, are the availability times of each device among a \squad.
-In our model, time is discretized, i.e. users periodically change the availability stated of their devices in a predefined period.
+In our model, time is discretized, i.e. users periodically change the state availability of their devices in a predefined period.
 We store the availability times in an ever-increasing \emph{sequence} $O=O_1, ..., O_i, ...$ of actions performed at every \emph{round}, that lasts a short period of time $T$. 
@@
 In our case, we do not care as long as the predictions using the estimated model, $P[O_{t+1} \mid S_t; \lambda_N^{(i)}]$, are close to the ground-truth, $P[O_{t+1} \mid S_t; \lambda_N]$.
-This will be evaluated in section~\ref{sub:devices_predictions_of_the_user_behavior}.
+%This will be evaluated in section~\ref{sub:devices_predictions_of_the_user_behavior}.

### 2018-05-01 paper/system-model.tex

@@
  know which other devices belong to the same user, \ie the \squad.
-Thus the devices from an \squad only knows the mapping from devices to users for the devices in 
-the \squad it belongs to.
-We also assume that the users can exchange some limited amounts of data 
+Thus, the devices from an \squad only know the mapping from devices to users for the devices in 
+the \squad they belong to.
+We also assume that users can exchange some limited amounts of data 
 out-of-band, \ie through some other channel than the network just mentioned (\eg 
@@
 enjoyed through the cloud provider, and go a step further by removing 
-cloud provider that may act as a spy. However, this increased privacy
+the cloud provider that may act as a spy. However, this increased privacy
 should not be done to the benefit of the user's friends that may

### 2018-05-01 paper/security-discussion.tex
Adds discussion on needed privacy of RPS scheme

@@
 
+Finally, we would also need the random peer sampling to be privacy preserving.
+Consider the following scenario.
+Alice requests a set of peers, say \(\{d_1, \dotsc, d_n\}\).
+If \(d_i\) interacts in each sampling operation resulting in \(d_i\) being in 
+the sample, then \(d_i\) can generate a new public key \(\pk_d^{(j)}\) for each 
+sample \(j\).
+This means that, if Alice sampled \(d_i\), she knows the public key 
+\(\pk_i^{(j)}\), and if \(d_i\) knows it is included in Alice's sample, then it 
+will also know a route belongs to Alice whenever \(\pk_i^{(j)}\) is used to 
+encrypt the header.
+\Ie every node on Alice's route would know that Alice is either the source or 
+the destination.
+When running the protocol, Alice only creates one part of the route and Bob 
+creates the other.
+This means that no device knows both ends of the route unless they collude.
+
 \subsection{Future Work}

### 2018-05-02 paper/evaluation.tex
removed sections
wrote a bit and experiments are undergoing
added figure

@@
 
-\subsection{Devices' predictions of the user behavior} % (fold)
-\label{sub:devices_predictions_of_the_user_behavior}
+% \subsection{Devices' predictions of the user behavior} % (fold)
+% \label{sub:devices_predictions_of_the_user_behavior}
 
-\commentAL{Will probably ditch that}
+% Adios, section
 
-% subsection devices_predictions_of_the_user_behavior (end)
 %\commentAL{Should evaluate the inference of the model given only the observable sequence. Also show that $P[O_{t+1} | S_t] \simeq P[O_{t+i} | S_t]$}
@@
 \caption{\label{fig:nodes_per_layer_vs_theta}Number of nodes per layer of POR as a function of the parameter $\theta$ (the maximal probability that all nodes in a layer fail at once).
-We see that the number of nodes logarithmically decreases as we relax the $\theta$ constraint.}
+The number of nodes logarithmically decreases as we relax the $\theta$ constraint.}
 \end{figure}
@@
 
-\commentAL{Git-noobiness removed my data: it has to compute again overnight.}
+\begin{figure}[t]
+\centering
+\includegraphics[width=0.9\columnwidth]{figures/transfer_time_vs_size.pdf}
+
+\caption{\label{fig:transfer_time_vs_size}Files' transfer time as a function of their size, along with a log-linear regression of the same data.}
+\end{figure}
 

### 2018-05-02 paper/message-passing-design.tex
new figure

@@
 \begin{figure}[t]
-  \includegraphics[width=\linewidth]{figures/file_exchange.pdf}
+  \includegraphics[width=\linewidth]{figures/file_exchange_v2.pdf}
   \caption{\label{fig:file-exchange}A schematic of the creation and usage of PORs between Alice and Bob's e-squads.}
@@
 \newcommand{\messagesize}{\ensuremath{s_m}}
-\newcommand{\filesize}{\ensuremath{s_f}}
+\newcommand{\filesize}{\ensuremath{s_{fc}}
 \newcommand{\headersize}{\ensuremath{s_{\mathcal{H}}}}
@@
 
-To prevent \name from message size analysis attacks, the messages have a fixed size \messagesize.
-As shown in the previous section~\ref{ssub:building_routes}, headers have a variable size \headersize per route (but \Hforward remains constant once the POR is established).
-For this reason, file chunks have a fixed size per session: $\filesize = \messagesize - \headersize$.
+\commentAL{Is it good?}
+In \name, whole messages, headers and file chunks are considered having a fixed size.
+In reality, the message size \messagesize is indeed fixed to prevent \name from message size analysis attacks,
+but the header size \headersize is variable, depending on the number of layers and the number of devices per layer.
+File chunks would then have a size  inversely proportional to \headersize : $\filesize = \messagesize - \headersize$.
+
+% To prevent \name from message size analysis attacks, the messages have a fixed size \messagesize.
+% As shown in the previous section~\ref{ssub:building_routes}, headers have a variable size \headersize per route (but \Hforward remains constant once the POR is established).
+% For this reason, file chunks have a fixed size per session: $\filesize = \messagesize - \headersize$.
 

### 2018-05-02 paper/building-blocks.tex
Adds frames around figures
up

@@
-\section{Building blocks}%
+\subsection{Building blocks}%
 \label{BuildingBlocks}
 
-\dots
+\NewScheme{\ANOBE}{ANOBE}
+\NewScheme{\DeBE}{DeBE}
+\NewAlgorithm{\DeBEsetup}{\DeBE[Setup]}
+\NewAlgorithm{\DeBEjoin}{\DeBE[Join]}
+\NewAlgorithm{\DeBEenc}{\DeBE[Enc]}
+\NewAlgorithm{\DeBEdec}{\DeBE[Dec]}
 
-\subsection{Hybrid encryption}\label{KEM}
+\paragraph*{Hybrid encryption}\label{KEM}
 
@@
 
-\subsection{\Acl*{BE}}\label{BE}
+\paragraph*{\Acl*{BE}}\label{BE}
 
-We will do onion routing with many alternative nodes per hop.
-This means that we encrypt the same message for more than one possible 
-recipient.
-Given this, it is natural to look for a suitable \ac{BE} scheme.
-More specifically, we are interested in \iac{BE} scheme adapted for \iac{P2P} 
+\begin{figure}[t]
+\centering
+  \includegraphics[scale=.20]{figures/pors2.pdf}
+  \caption{\label{fig:por} Group Onion Routing}
+\end{figure}
+
+in \name, we do onion routing with many
+alternative nodes per hop. This means that we encrypt the same message
+for more than one possible recipient for each onion layer (See
+Figure~\ref{fig:por},\ding{182}, \ding{183}, \ding{184}).
+%  Although each node
+% has a private and public key, for performances reasons, we want to avoid 
+% to encrypt a message multiple times for each onion layer. For instance,
+% according to Figure~\ref{fig:por},\ding{182}, \ding{183}, \ding{184},
+% we want to avoid to encrypt a
+% message $n$ times in layer $\mathcal{L}_1$, $m$ times in layer
+% $\mathcal{L}_2$ and $k$ times in layer $\mathcal{L}_3$.
+
+To encrypt
+messages in such a way that only legitimate nodes of a
+layer can decrypt them, we leverage on \ac{BE} scheme.
+More specifically, we are interested in \iac{BE} scheme adapted to \iac{P2P} 
 setting, where devices can dynamically join and leave --- \ie we do not want too 
 much cost for joining or leaving, \eg from key regeneration. 
-We also want some privacy properties, \eg those of \ac{ANOBE}.
-
-Our \ac{P2P} setting requires something similar to \iac{DBE} scheme.
+In \name, we require something similar to \iac{DBE} scheme
+\cite{DynamicBroadcastEncryption}.
 However, we want a slightly different definition.
@@
 \end{enumerate}
-Unlike the definition of \textcite{DynamicBroadcastEncryption}, we desire 
-forward secrecy --- in our scenario it makes no sense that new devices can 
-decrypt old ciphertexts.
-We also want to change the restriction on the ciphertext size:
-whereas \textcite{DynamicBroadcastEncryption} require the ciphertext size to be 
-independent from the expected number of users, we want it to be independent of 
-the total number of users --- \ie it can depend on the recipient set.
-In this sense, the trivial \ac{BE} scheme would fulfil our definition, but not 
-the definition of dynamic~\cite{DynamicBroadcastEncryption}.
 
-\NewScheme{\ANOBE}{ANOBE}
-\NewScheme{\DeBE}{DeBE}
-\NewAlgorithm{\DeBEsetup}{\DeBE[Setup]}
-\NewAlgorithm{\DeBEjoin}{\DeBE[Join]}
-\NewAlgorithm{\DeBEenc}{\DeBE[Enc]}
-\NewAlgorithm{\DeBEdec}{\DeBE[Dec]}
+% Unlike the definition of \textcite{DynamicBroadcastEncryption}, we desire 
+% forward secrecy --- in our scenario it makes no sense that new devices can 
+% decrypt old ciphertexts.
+% We also want to change the restriction on the ciphertext size:
+% whereas \textcite{DynamicBroadcastEncryption} require the ciphertext size to be 
+% independent from the expected number of users, we want it to be independent of 
+% the total number of users --- \ie it can depend on the recipient set.
 
-Our \ac{DeBE} scheme, \(\DeBE\), provides the following algorithms:
-\(\DeBEsetup, \allowbreak \DeBEjoin, \allowbreak \DeBEenc, \allowbreak 
-  \DeBEdec\).
-We will use the proposed instantiation of \iac{ANOBE} scheme by \textcite{ANOBE} 
-to instantiate our \ac{DeBE} scheme.
-We will simply divide the steps of the \(\ANOBE\) algorithms differently.
+% In this sense, the trivial \ac{BE} scheme would fulfil our definition, but not 
+% the definition of dynamic~\cite{DynamicBroadcastEncryption}.
+
+To this end, we use the proposed instantiation of \iac{ANOBE} scheme 
+to instantiate our own scheme, named \ac{DeBE}. 
+In \ac{DeBE}, we simply divide the
+steps of the \(\ANOBE\) algorithms differently to suit our
+aforementioned requirements. Nevertheless, we are reusing 
+both the encryption and decryption algorithms from \cite{ANOBE} to 
+encrypt messages which can only be decrypted by a predefined group of
+nodes. As a result, our \ac{DeBE} scheme provides among others these algorithms:
+\(\DeBEenc, \allowbreak \DeBEdec\) as illustrated in
+\cref{DeBEenc}\footnote{For lack of space reasons, we do not introduce the other
+algorithms of our \ac{DeBE} scheme}.
 
@@
 
-\(\DeBEsetup[\lambda]\): takes the security parameter \(\lambda\) and generates 
-the global parameters for the underlying IND-CCA encryption scheme \(\Enc\) and 
-the one-time signature scheme \(\Sign\).
-It also creates a master public key, \(\mpk = \emptyset\).
+% \(\DeBEsetup[\lambda]\): takes the security parameter \(\lambda\) and generates 
+% the global parameters for the underlying IND-CCA encryption scheme \(\Enc\) and 
+% the one-time signature scheme \(\Sign\).
+% It also creates a master public key, \(\mpk = \emptyset\).
 
@@
 
-\((\pk_i, \sk_i)\gets \DeBEjoin[i]\): generates the public--private key-pair 
-\((\pk_i, \sk_i)\) for device \(i\) when it joins.
-It also adds \(\pk_i\) to \(\mpk\).
-See \cref{DeBEsetup} for an algorithmic overview.
+% \((\pk_i, \sk_i)\gets \DeBEjoin[i]\): generates the public--private key-pair 
+% \((\pk_i, \sk_i)\) for device \(i\) when it joins.
+% It also adds \(\pk_i\) to \(\mpk\).
+% See \cref{DeBEsetup} for an algorithmic overview.
 
-\begin{figure}
-  \begin{algorithmic}
-    \Require{$\Enc$ is an IND-CCA \ac{PKE} scheme, $\Sign$ is a one-time 
-      signature scheme.}
+% \begin{figure}
+%   \framebox{\begin{minipage}{0.96\linewidth}
+%   \begin{algorithmic}
+%     \Require{$\Enc$ is an IND-CCA \ac{PKE} scheme, $\Sign$ is a one-time 
+%       signature scheme.}
 
-    \Function{\DeBEsetup}{$\lambda$}
-      \State $\Enc[Setup](\lambda), \Sign[Setup](\lambda)$
-      \State $\mpk\gets \emptyset$
-    \EndFunction
+%     \Function{\DeBEsetup}{$\lambda$}
+%       \State $\Enc[Setup](\lambda), \Sign[Setup](\lambda)$
+%       \State $\mpk\gets \emptyset$
+%     \EndFunction
 
-    \Function{\DeBEjoin}{$i$}
-      \State $(\pk_i, \sk_i)\gets \Enc[Keygen]$
-      \State $\mpk\gets \mpk\cup \{\pk_i\}$
-      \State \Return $(\pk_i, \sk_i)$
-    \EndFunction
-  \end{algorithmic}
-  \caption{\label{DeBEsetup}\label{DeBEjoin}%
-    Algorithmic overview of \(\DeBEsetup\) and \(\DeBEjoin\).
-  }
-\end{figure}
+%     \Function{\DeBEjoin}{$i$}
+%       \State $(\pk_i, \sk_i)\gets \Enc[Keygen]$
+%       \State $\mpk\gets \mpk\cup \{\pk_i\}$
+%       \State \Return $(\pk_i, \sk_i)$
+%     \EndFunction
+%   \end{algorithmic}
+%   \end{minipage}}
+%   \caption{\label{DeBEsetup}\label{DeBEjoin}%
+%     Algorithmic overview of \(\DeBEsetup\) and \(\DeBEjoin\).
+%   }
+% \end{figure}
 
@@
 
-\((\vk, C, \sigma)\gets \DeBEenc[\mpk, S, m]\):
-takes a message \(m\) and a recipient set \(S\), it then encrypts the message 
-for each recipient's key, signs the tuple of all ciphertexts and returns the 
-verification key, ciphertexts and signature.
-(Note that the signature does not authenticate the sender, it ties the 
-ciphertext together and is needed for correctness, we refer to~\cite{ANOBE} for 
-details.)
+\((\vk, C, \sigma)\gets \DeBEenc[\mpk, S, D, E, m]\):
+takes as input: a message \(m\), a recipient set \(D\),  a one-time signature
+scheme \(S\), an IND-CCA \ac{PKE} scheme \(E\), and the public keys
+set \(MPK\) that contains the public key of each recipient in the set
+\(D\), such as $MPK=\sum_{i=1}^{n} pk_i$. The message $m$ is encrypted 
+for each recipient's key, then the resulting tuple is
+signed.  Finally,the tuple of all ciphertexts, the
+verification key, and signature \footnote{The signature
+does not authenticate the sender, it ties the ciphertext together and
+is needed for correctness, we refer to~\cite{ANOBE} for  details} is returned.
 
-\(m\gets \DeBEdec[\mpk, \sk_i, (\vk, C, \sigma)]\):
+\(m\gets \DeBEdec[\sk_i, (\vk, C, \sigma)]\):
 takes a ciphertext \((\vk, C, \sigma)\) and tries to decrypt the sub-ciphertexts 
@@
 
-Both \(\DeBEenc\) and \(\DeBEdec\) are the same as in~\cite{ANOBE}.
-The algorithms are illustrated in \cref{DeBEenc,DeBEdec}.
-
-\begin{frame}
 \begin{figure}
-    \begin{algorithmic}
-      \Require{$\Enc$ is an IND-CCA \ac{PKE} scheme, $\Sign$ is a one-time 
-        signature scheme.}
-
-      \Function{$\DeBEenc$}{$\mpk, S, m$}
+  \framebox{\begin{minipage}{0.96\linewidth}
+  \begin{algorithmic}[1]
+    \Function{$\DeBEenc$}{$\mpk, S, D, E, m$}
       \State $(\ssk, \vk)\gets \Sign[Keygen]$
-        \State Choose a random permutation \(\pi\colon S\to S\).
-        \For{$i \in S$}
+      \State Choose a random permutation \(\pi\colon D\to D\).
+      \For{$i \in D$}
         \State $c_i\gets \Enc[Enc](\pk_i, m\concat \vk)$
@@
   \end{algorithmic}
+  \end{minipage}}
   \caption{\label{DeBEenc}\label{DeBEdec}%
@@
 \end{figure}
-\end{frame}

### 2018-05-02 paper/intro.tex
up

--- 2018-04-30 paper/intro.tex
@@
 
-Our contributions are as follows: \david{please update}
-\begin{itemize}
-\item We showed the effectiveness of \iac{ANOBE} scheme by \textcite{ANOBE} 
-  to build a \ac{DeBE} as required by \name to
-  provide.... 
-\item A \squad overlay 
-\item Model the user’s behavior as a Hidden Markov Models (HMMs)
-\item SPOR provides stateless algorithms for the onion-routing.
-\item An evaluation testbed where each user’s behavior
-\end{itemize}
+% Our contributions are as follows: 
+% \begin{itemize}
+% \item We have designed \name, a novel fully decentralized, autonomous,
+% and self-organizing file sharing service among users based on a novel
+% concept named Probabilistic Onion Routes (POR), which combines onion routing with
+% probabilistic node selection, informed by random peer sampling and
+% Hidden Markov Model predictions for node availability. 
+% \item  We have demonstrated the successfulness of our approach. Even
+%   suboptimal prediction results in successful file transfer with high
+%   probability. 
+% \end{itemize}
 
-In the following, we detail \name 's concepts and approach...
+In the following, in Section~\ref{system-model}, we introduce the
+adversary model, and the desired privacy properties of \name. In Section~\ref{design}
+we introduce the design of our approach, to then, in Section~\ref{Performance},
+evaluate its performances. Finally, in Section~\ref{security-discussion}, we lead a security discussion
+about advantages, and shortcomings of our approach to conclude in
+Section~\ref{conclusion}.
 

### 2018-05-02 paper/message-passing-design.tex
up

--- 2018-04-30 paper/message-passing-design.tex
@@
-\NewScheme{\SPOR}{SPORES}
+\NewScheme{\SPOR}{SPOR}
 
@@
 
+\NewAlgorithm{\Send}{Send}
 \NewAlgorithm{\Fwd}{Forward}
-\NewAlgorithm{\Send}{BuildRouteS}
-\NewAlgorithm{\Recv}{BuildRouteR}
-\NewAlgorithm{\ExtendRoute}{ExtendRoute}
-\NewAlgorithm{\CreateOnionLayer}{CreateLayer}
-\NewAlgorithm{\Dec}{Dec}
-\NewAlgorithm{\Store}{Store}
-\NewVariable{\sk}{sk}
+\NewAlgorithm{\Recv}{Receive}
 \NewVariable{\rdv}{rdv}
-\NewVariable{\LRV}{\mathcal{L_{RV}}\xspace}
-\NewVariable{\Hsend}{\mathcal{H}_{\text{send}}\xspace}
-\NewVariable{\Hrec}{\mathcal{H}_{\text{rec}}\xspace}
-\NewVariable{\Hforward}{\mathcal{H}_f\xspace}
-\NewVariable{\Hbackward}{\mathcal{H}_b\xspace}
-\NewVariable{\Hsendforward}{\mathcal{H}_{\text{send f}}\xspace}
-\NewVariable{\Hsendbackward}{\mathcal{H}_{\text{send b}}\xspace}
-\NewVariable{\Hrecforward}{\mathcal{H}_{\text{rec f}}\xspace}
-\NewVariable{\Hrecbackward}{\mathcal{H}_{\text{rec b}}\xspace}
-%\NewVariable{\nfilechunks}{\#\text{chunks}}
 
-The principle of onion routing à la Tor~\cite{Tor} is to put nodes relaying messages between a source and a destination.
-By employing encryption layers, a relay doesn't know where it is situated on the message's path. 
-It only knows who gave him the message, and where to send it to.
+\david{each protocol should be explained individually}
 
 In contrast to Tor~\cite{Tor} that provides only one address per hop
-in the route, \name provides, for each layer of the onion, several
-alternative nodes for the next hop in the route depending on their
-probability of being online. 
-We call our modified onion routes Probabilistic Onion Routes or PORs.
+in the route, \name provides for each layer of the onion several
+alternatives for the next hop in the route depending on their
+probability of being online. To implement our  probabilistic
+predictive onion routing mechanism, \name defined three different algorithms to
+receive, send and forward messages among users' \squad. For instance,
+if Alice wants to send a message \(m\) to Bob, Bob uses the
+\(\SPOR[\Recv]\) algorithm (See \cref{SPORRecv}) to create a probabilistic onion route \(H_\rdv\) from
+ a rendez-vous point to its own devices from its \squad --- all the hops on the route are 
+chosen by Bob uniformly at random from the RPS. \(\SPOR[\Recv]\)
+returns the \(H_\rdv\) that Bob gives to Alice using an
+out-of-band channel, \eg using one device of its \squad.
+PORs have \(L\) layers, and for each layer the number of
+alternatives nodes depends of a failure threshold \(\theta\). 
+As long as \(\theta\) is not exceeded, alternatives nodes are added in
+\(H_\rdv\) as depicted in \cref{ExtendRoute}. Thus the probability of
+failure for the extension is \(1 - (1 - \theta)^L\).
 
-Another difference from Tor, where connections are established by all nodes in the route, \name is stateless: the route's ends (the sender Alice and receiver Bob) cooperate to create the headers containing all the necessary routing information for future communication between Alice and Bob.
-In that regard, two headers are required: \Hforward to route packets from Alice to Bob, and \Hbackward for packets from Bob to Alice.
+\NewAlgorithm{\Store}{Store}
 
-To implement our predictive onion routing mechanism, \name is thus split in two algorithms: the route building one, and the message routing one.
-Figure~\ref{fig:file-exchange} shows the process of the route creation until the first exchange of a file chunk from Alice to Bob.
-Alice uses the forward route to send file chunks to Bob, while Bob uses the backward route to send acknowledgments back to Alice.
-
-\begin{figure}[t]
-  \includegraphics[width=\linewidth]{figures/file_exchange.pdf}
-  \caption{\label{fig:file-exchange}A schematic of the creation and usage of PORs between Alice and Bob's e-squads.}
-\end{figure}
-
-\subsubsection{Building routes} 
-\label{ssub:building_routes}
-
-When Alice wants to send a file to Bob, they first have to call the route building algorithm, and to exchange relevant information out of band (e.g. using mail, or their phones' bluetooth connection).
-They create a route of $L$ layers, a configuration parameter that must be odd. We introduce $l=(L-1)/2$.
-
-Bob (the receiver) initiates the route creation by calling the \Recv function displayed in figure~\ref{fig:route building algo}
-He randomly chooses nodes to constitute a rendez-vous layer \LRV, and nodes to constitute $l$ layers from \LRV to his \squad. 
-We come back on layer creation below.
-He crafts a layered encrypted header (more details below) to \LRV (excluded) to his squad (included), that we will call \Hrecforward.
-He also crafts his part of the header for the backward route, \Hrecbackward: it contains the route from Bob's \squad (excluded) to \LRV (included).
-
-Bob then sends \Hrecforward and the descriptors of the \LRV nodes to Alice, by calling Alice's \Send function (also in figure~\ref{fig:route building algo}).
-like Bob, Alice randomly picks nodes to constitutes $l$ layers from her \squad to \LRV.
-She also builds two encrypted headers: \Hsendforward contains the route from her \squad (excluded) to \LRV (included), while \Hsendbackward contains the route from \LRV (excluded) to her \squad (included).
-Alice now ha the full forward header \Hforward, as shown on line~\ref{hforward}
-Alice finally sends \Hsendbackward back to Bob.
-
-Back to \Recv function: Bob has the full backward header $\Hbackward$, as shown on line~\ref{hbackward}.
-
-\paragraph*{Layer creation}
-The function \CreateOnionLayer() iteratively adds random nodes (from the RPS's view \view) until the product $\prod_{d\in \mathcal{L}} (1 - p_d)$ falls below $\theta$.
-$(1 - p_d)$ is the probability that a device $d$ will be offline; the product is the probability that all devices on layer $\mathcal{L}$ fall offline at the same time.
-
-\begin{table}[t]
-\resizebox{\columnwidth}{!}{
-\begin{tabular}{lp{0.9\linewidth}}
-\toprule
-\multicolumn{2}{c}{\textbf{Parameters of the algorithm}} \\
-\midrule
-$\theta$ & Stopping criterion for the layers creation: maximum authorized  probability that all devices in a layer fail at once. \\
-$L$      & Number of layers in a Predictive Onion Route. \\
-$l = (L-1)/2$ & Number of layers (excluding $\LRV$) created by each end of the route. \\
-\bottomrule
-\end{tabular}
-}
-\label{tab:parameters}
-\end{table}
-
-\paragraph*{Header preparation} \commentAL{TODO}
-
-\begin{figure}[t]
-  %\framebox{\begin{minipage}{0.96\linewidth}
-  \begin{algorithmic}[1]
-    % \Require{%
-    %   $D$ is the set of alternative recipient devices.
-    % }
-    \Function{\Recv}{sender}
-      \State $\LRV \gets \CreateOnionLayer()$
-      \State layers $\gets [\,]$
-      \While{len(layers) $ < l$}
-        \State layers.append(\CreateOnionLayer())
-      \EndWhile
-      \State $\Hrecforward \gets$ properly encrypted layers
-      \State $\Hrecbackward \gets$ properly encrypted layers
-
-      \Comment{Out-of-band exchange}
-      \State $\Hsendbackward \gets$ sender.\Send(\Hrecforward, \LRV)
-
-      \State $\Hbackward \gets \Hrecbackward \concat \Hsendbackward$ \label{hbackward}
-      %\State $H_\rdv\gets \ExtendRoute[D\concat \top, L, \theta]$
-      % \State \Return $H_\rdv$
-      %   \Comment{Give to sender out-of-bound.}
-    \EndFunction
-  \end{algorithmic}
-  %\end{minipage}}
-
-  \vspace{0.3em}
-  %\framebox{\begin{minipage}{0.96\linewidth}
-  \begin{algorithmic}[1]
-    % \Require{%
-    %   $m$ is the message to be sent,
-    %   $H_\rdv$ is the onion-route given by the recipient.
-    % }
-    \Function{\Send}{\Hrecforward, \LRV}
-      \State layers $\gets [\,]$
-      \While{len(layers) $ < l$}
-        \State layers.append(\CreateOnionLayer())
-      \EndWhile
-      \State $\Hsendforward \gets$ properly encrypted layers
-      \State $\Hsendbackward \gets$ properly encrypted layers
-      \State $\Hforward \gets \Hsendforward \concat \Hrecforward$ \label{hforward}
-      \State \Return \Hsendbackward
-
-      % \State $H\gets \ExtendRoute[H_\rdv, L, \theta]$
-      % \State $D\concat C_H\gets H_\rdv$
-      % \For{$d\in D$}
-      %   \Comment{Uniformly randomly chosen}
-      %   \If{$d\method \Fwd[C_H, m] \neq \bot$}
-      %     \State \Return $\top$
-      %   \EndIf
-      % \EndFor
-      % \State \Return $\bot$
-    \EndFunction
-  \end{algorithmic}
-  %\end{minipage}}
-
-  % \vspace{0.3em}
-  % %\framebox{\begin{minipage}{0.96\linewidth}
-  % \begin{algorithmic}[1]
-  %   % \Require{%
-  %   %   $H$ is a header of the form \(D\concat H'\) or \(D\concat \top\), where 
-  %   %   \(D\) is a set of device addresses.
-  %   %   $\pk_D$ is the public key of device set $D$.
-  %   %   $L$ is the length of the route,
-  %   %   $\theta$ is the threshold of probability of failure.%
-  %   % }
-  %   \Function{\ExtendRoute}{$\mathcal{H}, l$}
-  %     \If{$L\leq 0$}
-  %       \State \Return $H$
-  %     \EndIf
-  %     \State $D\gets \CreateOnionLayer[\theta]$
-  %     \State $H\gets D\concat \DeBEenc[\mpk, D, H]$
-  %     \State \Return $\ExtendRoute[H, L-1, \theta]$
-  %   \EndFunction
-  % \end{algorithmic}
-
-  \vspace{0.3em}
-
-  \begin{algorithmic}[1]
-    \Function{\CreateOnionLayer}{\null}
-      \State $(d, \pk_d, p_d)\gets \GetRandomPeer$
-      \State $\mathcal{L}\gets \{(d, \pk_d, p_d)\}$
-      \While{$\prod_{d\in \mathcal{L}} (1 - p_d) \geq \theta$}
-        \State $(d, \pk_d, p_d)\gets \GetRandomPeer$
-        \State $\mathcal{L}\gets \mathcal{L}\cup \{(d, \pk_d, p_d)\}$
-      \EndWhile
-      \State \Return $\mathcal{L}$
-    \EndFunction
-  \end{algorithmic}
-  %\end{minipage}}
-  \caption{\label{fig:route building algo}The route building algorithm}
-\end{figure}
-
-\subsubsection{Routing messages}
-\label{ssub:routing_messages}
-
-Once Alice get the \(H_\rdv\), Alice uses \(\Send\) at some
+Once Alice get the \(H_\rdv\), Alice uses \(\SPOR[\Send]\) at some
 later time to send the message to Bob using any of her devices from
-its \squad.% (See \cref{SPORSend}). 
-First, \(\Send\) extends the route
+its \squad (See \cref{SPORSend}). First, \(\SPOR[\Send]\) extends the route
 \(H_\rdv\) with some hops of Alice's choosing (uniformly randomly
-chosen). Second, \(\Send\) extracts from the onion the first
+chosen). Second, \(\SPOR[\Send]\) extracts from the onion the first
 layer, which contained the overall
 possible rendez-vous points $D$ previously selected by the recipient (i.e. Bob).
-One device from $D$ is randomly chosen, and the \(\Fwd\)
+One device from $D$ is randomly chosen, and the \(\SPOR[\Fwd]\)
 sub-function is called as long as the message forwarding to one node of
-the next layer is not successful.% (See \cref{SPORFwd}). 
-Along the path, each node decrypts
+the next layer is not successful (See \cref{SPORFwd}). Along the path, each node decrypts
 in sequence the different layer with the current node’s private key. 
@@
 encountered. Consequently the ciphered message \(c_m\) is then stored
-in the disk of the local node through the \(\Store\) sub function.%(\cref{SPORRecv}).
+in the disk of the local node through the \(\Store\) sub function 
+(\cref{SPORRecv}).
 
 \david{the use of DeBE algorithms must be explicitly explained here}
-
-\begin{figure}[t]
-  %\framebox{\begin{minipage}{0.96\linewidth}
-  \begin{algorithmic}[1]
-    %\Require{$\pk, \sk$ is the public--private key-pair of the node.}
-    \Function{\Fwd}{$C_H, m$}
-      \State $H\gets \DeBEdec[\mpk, \sk, C_H]$
-      \If{$H = \bot$}
-        \State \Return $\bot$
-      \EndIf
-      \State $\{d_i\}\concat C_H'\gets H$
-      \If{$C_H' = \top$}
-        \State \Return $\Store[m]$
-      \EndIf
-      \For{$d\in \{d_i\}$}
-        \Comment{Uniformly randomly chosen}
-        \If{$d\method \Fwd[C_H', m] \neq \bot$}
-          \State \Return $\top$
-        \EndIf
-      \EndFor
-      \State \Return $\bot$
-    \EndFunction
-  \end{algorithmic}
-
-  \begin{algorithmic}[1]
-    \Function{\Store}{$m$}
-      \State $m\gets \DeBEdec[\mpk, \sk, c_m]$
-      \If{$m = \bot$}
-        \State \Return $\bot$
-      \EndIf
-      \State Store $m$ to disk.
-      \State \Return $\top$
-    \EndFunction
-  \end{algorithmic}
-  %\end{minipage}}
-  \caption{\label{SPORFwd}%
-    The \(\Fwd\) algorithm forwards \(m\) down the route \(H\), obtained 
-    by decrypting \(C_H\) with the node's associated private key.
-    The special value \(H = \top\) indicated the end of the route, thus \(c_m\) 
-    is intended for the local node and \(c_m\) is instead sent to disk using 
-    \(\Store\).% (\cref{SPORRecv}).%
-  }
-\end{figure}
-
-% For instance, if Alice wants to send a message \(m\) to Bob, they are both going to perform a part of the building algorithm.
-% Bob uses the \([\Recv]\) function (See \cref{SPORRecv}) to create a probabilistic onion route $\mathcal{H_B}$ from
-%  a rendez-vous (RV) layer $\mathcal{L_{RV}}$ to its own devices from its \squad---all the hops on the route are 
-% chosen by Bob uniformly at random from the Global Overlay.
-%  \(\SPOR[\Recv]\)
-% returns $\mathcal{H_B}$ and  that Bob gives to Alice using an
-% out-of-band channel, \eg using one device of its \squad.
-% PORs have \(L\) layers, and for each layer the number of
-% alternatives nodes depends of a failure threshold \(\theta\). 
-% As long as \(\theta\) is not exceeded, alternatives nodes are added in
-% \(H_\rdv\) as depicted in \cref{ExtendRoute}. Thus the probability of
-% failure for the extension is \(1 - (1 - \theta)^L\).
-
-% Once Alice get the \(H_\rdv\), Alice uses \(\SPOR[\Send]\) at some
-% later time to send the message to Bob using any of her devices from
-% its \squad (See \cref{SPORSend}). First, \(\SPOR[\Send]\) extends the route
-% \(H_\rdv\) with some hops of Alice's choosing (uniformly randomly
-% chosen). Second, \(\SPOR[\Send]\) extracts from the onion the first
-% layer, which contained the overall
-% possible rendez-vous points $D$ previously selected by the recipient (i.e. Bob).
-% One device from $D$ is randomly chosen, and the \(\SPOR[\Fwd]\)
-% sub-function is called as long as the message forwarding to one node of
-% the next layer is not successful (See \cref{SPORFwd}). Along the path, each node decrypts
-% in sequence the different layer with the current node’s private key. 
-% The end of the route is reached when special value \(H_\rdv = \top\) is
-% encountered. Consequently the ciphered message \(c_m\) is then stored
-% in the disk of the local node through the \(\Store\) sub function 
-% (\cref{SPORRecv}).
 
@@
 %    devices and returns the route to the sender.
+
+\begin{figure}
+  \includegraphics[width=\linewidth]{figures/file_exchange.pdf}
+  \caption{\label{fig:file-exchange}%
+    A schematic of Alice and Bob sending a message using \(\SPOR\).
+  }
+\end{figure}
+
+\NewAlgorithm{\ExtendRoute}{ExtendRoute}
+\NewAlgorithm{\CreateOnionLayer}{CreateOnionLayer}
+
+\begin{figure}
+
+  \framebox{\begin{minipage}{0.96\linewidth}
+  \begin{algorithmic}[1]
+    \Require{%
+      $H$ is a header of the form \(D\concat H'\) or \(D\concat \top\), where 
+      \(D\) is a set of device addresses.
+      $\pk_D$ is the public key of device set $D$.
+      $L$ is the length of the route,
+      $\theta$ is the threshold of probability of failure.%
+    }
+    \Function{\ExtendRoute}{$H, L, \theta$}
+      \If{$L\leq 0$}
+        \State \Return $H$
+      \EndIf
+      \State $D\gets \CreateOnionLayer[\theta]$
+      \State $H\gets D\concat \DeBEenc[\mpk, D, H]$
+      \State \Return $\ExtendRoute[H, L-1, \theta]$
+    \EndFunction
+  \vspace{0.3em}
+    \Function{\CreateOnionLayer}{$\theta$}
+      \State $(d, \pk_d, p_d)\gets \GetRandomPeer$
+      \State $D\gets \{(d, \pk_d, p_d)\}$
+      \While{$\prod_{d\in D} p_d > \theta$}
+        \State $(d, \pk_d, p_d)\gets \GetRandomPeer$
+        \State $D\gets D\cup \{(d, \pk_d, p_d)\}$
+      \EndWhile
+      \State \Return $D$
+    \EndFunction
+  \end{algorithmic}
+  \end{minipage}}
+  \caption{\label{ExtendRoute}%
+    \scriptsize
+    The \(\ExtendRoute\) algorithm extends a route \(H\)
+  }
+\end{figure}
+
+\NewAlgorithm{\Dec}{Dec}
+\NewVariable{\sk}{sk}
+
+\begin{figure}
+  \framebox{\begin{minipage}{0.96\linewidth}
+  \begin{algorithmic}
+    \Require{%
+      $D$ is the set of alternative recipient devices.
+    }
+    \Function{\SPOR[\Recv]}{$D$}
+      \State $H_\rdv\gets \ExtendRoute[D\concat \top, L, \theta]$
+      \State \Return $H_\rdv$
+        \Comment{Give to sender out-of-bound.}
+    \EndFunction
+  \end{algorithmic}
+  \end{minipage}}
+  \caption{\label{SPORRecv}%
+\scriptsize
+    The \(\SPOR[\Recv]\) algorithm prepares the recipient for receiving a file.
+  }
+\end{figure}
+
+\begin{figure}
+  \framebox{\begin{minipage}{0.96\linewidth}
+  \begin{algorithmic}
+    \Require{%
+      $m$ is the message to be sent,
+      $H_\rdv$ is the onion-route given by the recipient.
+    }
+    \Function{\SPOR[\Send]}{$H_\rdv, m$}
+      \State $H\gets \ExtendRoute[H_\rdv, L, \theta]$
+      \State $D\concat C_H\gets H_\rdv$
+      \For{$d\in D$}
+        \Comment{Uniformly randomly chosen}
+        \If{$d\method \Fwd[C_H, m] \neq \bot$}
+          \State \Return $\top$
+        \EndIf
+      \EndFor
+      \State \Return $\bot$
+    \EndFunction
+  \end{algorithmic}
+  \end{minipage}}
+  \caption{\label{SPORSend}%
+    \scriptsize
+    The \(\SPOR[\Send]\) algorithm 
+  }
+\end{figure}
+
+\begin{figure}
+  \framebox{\begin{minipage}{0.96\linewidth}
+  \begin{algorithmic}
+    \Require{$\pk, \sk$ is the public--private key-pair of the node.}
+    \Function{\SPOR[\Fwd]}{$C_H, m$}
+      \State $H\gets \DeBEdec[\mpk, \sk, C_H]$
+      \If{$H = \bot$}
+        \State \Return $\bot$
+      \EndIf
+      \State $\{d_i\}\concat C_H'\gets H$
+      \If{$C_H' = \top$}
+        \State \Return $\Store[m]$
+      \EndIf
+      \For{$d\in \{d_i\}$}
+        \Comment{Uniformly randomly chosen}
+        \If{$d\method \Fwd[C_H', m] \neq \bot$}
+          \State \Return $\top$
+        \EndIf
+      \EndFor
+      \State \Return $\bot$
+    \EndFunction
+    \Function{\Store}{$m$}
+      \State $m\gets \DeBEdec[\mpk, \sk, c_m]$
+      \If{$m = \bot$}
+        \State \Return $\bot$
+      \EndIf
+      \State Store $m$ to disk.
+      \State \Return $\top$
+    \EndFunction
+  \end{algorithmic}
+  \end{minipage}}
+  \caption{\label{SPORFwd}%
+    The \(\SPOR[\Fwd]\) algorithm forwards \(m\) down the route \(H\), obtained 
+    by decrypting \(C_H\) with the node's associated private key.
+    The special value \(H = \top\) indicated the end of the route, thus \(c_m\) 
+    is intended for the local node and \(c_m\) is instead sent to disk using 
+    \(\Store\) (\cref{SPORRecv}).%
+  }
+\end{figure}

### 2018-05-02 paper/evaluation.tex
new figure
minor

@@
 
-\commentDaniel{%
-  Some data for Adrien.%
-}
-\Textcite{ANOBE} proposed using a modified version of \ac{KD-HES}.
+In the following, we present the evaluation results of \name. 
+We first give precisions on the evaluation testbed and parameters in section~\ref{sub:evaluation_testbed}, before evaluating the PORs creation  in section~\ref{sub:predictive_onion_routes_creation}, to conclude with an overall evaluation of the file transfer performance in section~\ref{sub:file_transfer}.
 
@@
 \includegraphics[width=0.9\columnwidth]{figures/hmm.pdf}
-\caption{ \label{fig:hmm} Example Hidden Markov Model (HMM) of a user's behavior.}
+\vspace{2ex}
+\includegraphics[width=\columnwidth]{figures/sample_usage.pdf}
+
+\caption{\label{fig:hmm} Example Hidden Markov Model (HMM) of a user's behavior: on top are the HMM parameters, on the middle is a visual representation of the model, and on the bottom is a sample output from the model.}
 \end{figure}
@@
 HMMs being generative probabilistic models, they allow the generation of observation sequence $O$ given the parameters of the model $\lambda_N$.
-Figure~\ref{fig:hmm} shows a possible outcome of the creation of a user's HMM, while figure~\ref{fig:sample_usage} shows an observation sequence $O$ that was generated from the displayed model.
+Figure~\ref{fig:hmm} shows a possible outcome of the creation of a user's HMM $\lambda_N$, its graphical representation, along with a sample observation sequence $O$ output from the model $\lambda_N$.
 
-Each round lasts $T=10s$ \commentAL{yes, the user switches places fast} and users start at different times. 
+Each round lasts $T=10s$ and users start at different times. 
 This way, even though the round period is fixed, devices enter and leave the system at different points in the continuous time.
-
-\begin{figure}[t]
-\centering
-\includegraphics[width=\columnwidth]{figures/sample_usage.pdf}
-
-\caption{\label{fig:sample_usage}Sample device usages using the previous HMM specifications. 
-%The bottom line reads the HMM's states: \textbf{W}ork, \textbf{O}utside, and \textbf{H}ome, while the dark lines read when the devices (\textbf{h}ome computer, \textbf{p}hone, and \textbf{w}orkstation) are online.
-}
-\end{figure}
 
@@
 
-In the following, we perform two types of experiments: figures~\ref{fig:nodes_per_layer_vs_theta} and \ref{fig:success_rate_vs_t} illustrate the establishment of PORs, while the next ones measure file transfer.
+In the following, we perform two types of experiments: 
+section~\ref{sub:predictive_onion_routes_creation} evaluates the establishment of PORs, while section~\ref{sub:file_transfer} handles file transfer.
+For that reason, they used different parameter sets.
 
+\paragraph*{PORs creation}
 Figures \ref{fig:nodes_per_layer_vs_theta} and \ref{fig:success_rate_vs_t} come from the same data, with 10 experiments per set of settings.
-$\theta$ is the threshold of the probability that all nodes fail at once: we keep adding nodes to a layer until the layer's probability is below $\theta$. 
-It takes the following values: $[0.1, 0.01, 0.001, 0.0001]$.
+$\theta$, the threshold of the probability that all nodes fail at once (cf. \ref{ssub:building_routes}), takes the following values: $[0.1, 0.01, 0.001, 0.0001]$.
 $L$, the number of layers constituting a route, takes the following values: $[3, 5, 7]$.
@@
 As we can see, the number of devices per layer logarithmically decreases as we relax the constraint on the layer's availability.
-The mean required number of devices per layer is reasonable: between 2 and 6.
+The mean number of devices per layer lies between 2 and 6.
 Still, the number of nodes per layer is very variable: at $\theta=10^{-4}$, values range from 2 to 11, with a standard deviation of 1.44.
@@
 This shows, as was stated in section~\ref{para:predicting future behavior}, that the prediction that devices make of behavior at $t+1$ is a good enough estimator for $t+i$.
-We also see that $\theta$ has a big impact on the availability average, and variability.
-Still, $\theta\in[10^-4, 10^-3]$ allows highly available routes with an average availability of 100\% and 99.5\% respectively.
+We also see that $\theta$ has a big impact on the mean availability and its variability.
+Still, $\theta\in\{10^-4, 10^-3\}$ allows highly available routes with an average availability of 100\% and 99.5\% respectively.
 Combined with the results from figure~\ref{fig:nodes_per_layer_vs_theta}, it means that routes will need an average of 5-6 devices per layer to be highly available.
@@
 
+\\
 We showed that creating reliable onion routes using a backbone of unreliable nodes is feasible by using predictive algorithms.
-The counterpart is that messages header size grows \commentAL{How does it grow? Quadratically, exponentially?} with the number of layers and the number of devices per layer.
-Considering that most onion routing solutions use a statically defined message size to avoid information leakage, this means that a more reliable onion route comes at the cost of an increased network traffic.
+The counterpart is that messages header size grows with the number of layers and the number of devices per layer.
 
-\subsection{File transfer} % (fold)
+Considering that most onion routing solutions use a statically defined message size to avoid information leakage, a bigger header means less space for the payload in each message.
+The more reliable the route, the bigger the number of messages per file.
+There is a trade-off between route reliability and network traffic.
+
+\subsection{File transfer time} % (fold)
 \label{sub:file_transfer}

### 2018-05-02 paper/message-passing-design.tex
minor

--- 2018-05-02 paper/message-passing-design.tex
@@
 \begin{figure}[t]
-  \includegraphics[width=\linewidth]{figures/file_exchange_v2.pdf}
+  \includegraphics[width=\linewidth]{figures/file_exchange.pdf}
   \caption{\label{fig:file-exchange}A schematic of the creation and usage of PORs between Alice and Bob's e-squads.}
@@
 
-      % \State $H\gets \ExtendRoute[H_\rdv, L, \theta]$
-      % \State $D\concat C_H\gets H_\rdv$
-      % \For{$d\in D$}
-      %   \Comment{Uniformly randomly chosen}
-      %   \If{$d\method \Fwd[C_H, m] \neq \bot$}
-      %     \State \Return $\top$
-      %   \EndIf
-      % \EndFor
-      % \State \Return $\bot$
+      \STATE $H\gets \ExtendRoute[H_\rdv, L, \theta]$
+      \State $D\concat C_H\gets H_\rdv$
+      \For{$d\in D$}
+        \Comment{Uniformly randomly chosen}
+        \If{$d\method \Fwd[C_H, m] \neq \bot$}
+          \State \Return $\top$
+        \EndIf
+      \EndFor
+      \State \Return $\bot$
     \EndFunction
@@
   % %\framebox{\begin{minipage}{0.96\linewidth}
-  % \begin{algorithmic}[1]
-  %   % \Require{%
-  %   %   $H$ is a header of the form \(D\concat H'\) or \(D\concat \top\), where 
-  %   %   \(D\) is a set of device addresses.
-  %   %   $\pk_D$ is the public key of device set $D$.
-  %   %   $L$ is the length of the route,
-  %   %   $\theta$ is the threshold of probability of failure.%
-  %   % }
-  %   \Function{\ExtendRoute}{$\mathcal{H}, l$}
-  %     \If{$L\leq 0$}
-  %       \State \Return $H$
-  %     \EndIf
-  %     \State $D\gets \CreateOnionLayer[\theta]$
-  %     \State $H\gets D\concat \DeBEenc[\mpk, D, H]$
-  %     \State \Return $\ExtendRoute[H, L-1, \theta]$
-  %   \EndFunction
-  % \end{algorithmic}
+  \begin{algorithmic}[1]
+    \Require{%
+      $H$ is a header of the form \(D\concat H'\) or \(D\concat \top\), where 
+      \(D\) is a set of device addresses.
+      $\pk_D$ is the public key of device set $D$.
+      $L$ is the length of the route,
+      $\theta$ is the threshold of probability of failure.%
+    }
+    \Function{\ExtendRoute}{$\mathcal{H}, l$}
+      \If{$L\leq 0$}
+        \State \Return $H$
+      \EndIf
+      \State $D\gets \CreateOnionLayer[\theta]$
+      \State $H\gets D\concat \DeBEenc[\mpk, D, H]$
+      \State \Return $\ExtendRoute[H, L-1, \theta]$
+    \EndFunction
+  \end{algorithmic}
 
@@
 \newcommand{\messagesize}{\ensuremath{s_m}}
-\newcommand{\filesize}{\ensuremath{s_{fc}}
+\newcommand{\filesize}{\ensuremath{s_{fc}}}
 \newcommand{\headersize}{\ensuremath{s_{\mathcal{H}}}}
@@
 
-\commentAL{Is it good?}
 In \name, whole messages, headers and file chunks are considered having a fixed size.

### 2018-05-02 paper/message-passing-design.tex
minor

--- 2018-05-02 paper/message-passing-design.tex
@@
 Once all chunks have been acknowledged, Alice sends an empty message to Bob, signifying transfer termination.
-
-\commentAL{Is it good?}
-In \name, whole messages, headers and file chunks are considered having a fixed size.
-In reality, the message size \messagesize is indeed fixed to prevent \name from message size analysis attacks,
-but the header size \headersize is variable, depending on the number of layers and the number of devices per layer.
-File chunks would then have a size  inversely proportional to \headersize : $\filesize = \messagesize - \headersize$.
 

### 2018-05-02 paper/message-passing-design.tex

--- 2018-05-02 paper/message-passing-design.tex
@@
 
-In \name, whole messages, headers and file chunks are considered having a fixed size.
-In reality, the message size \messagesize is indeed fixed to prevent \name from message size analysis attacks,
-but the header size \headersize is variable, depending on the number of layers and the number of devices per layer.
-File chunks would then have a size  inversely proportional to \headersize : $\filesize = \messagesize - \headersize$.
-
 % To prevent \name from message size analysis attacks, the messages have a fixed size \messagesize.

### 2018-05-02 paper/evaluation.tex
eval

@@
 
-% \subsection{Devices' predictions of the user behavior} % (fold)
-% \label{sub:devices_predictions_of_the_user_behavior}
-
-% Adios, section
-
-%\commentAL{Should evaluate the inference of the model given only the observable sequence. Also show that $P[O_{t+1} | S_t] \simeq P[O_{t+i} | S_t]$}
+\paragraph*{File exchange}
+In section~\ref{sub:file_transfer}, we fix the routes' creation parameters: $\theta=10^-3$, $L=3$.
+The number of users is set to 20, and the number of file exchange per experiment to 10.
+We use a constant file chunk size of 512kB, a constant header size of 100kB, and a constant bandwidth per link of 128kB/s.
 

### 2018-05-02 paper/evaluation.tex
it compiles
figure and eval

@@
 Finally, increasing $L$ logically hinders the results when using low-availability layers.
+\\
 
-\\
 We showed that creating reliable onion routes using a backbone of unreliable nodes is feasible by using predictive algorithms.
@@
 
+\newcommand{\fsize}{\ensuremath{s_f}}
+
+To assess the efficiency of \name, we did several file exchanges with fixed parameters and a random file size $\fsize\in [5\text{MB}, 500\text{MB}]$. 
+By performing 20 experiments using the parameters described in \ref{ssub:experimental_parameters}, we obtained traces for 200 file exchanges.
+
 \begin{figure}[t]
@@
 \caption{\label{fig:transfer_time_vs_size}Files' transfer time as a function of their size, along with a log-linear regression of the same data.}
+
 \end{figure}

### 2018-05-02 paper/message-passing-design.tex
I want the v2 of file exchange
it compiles
up

@@
 
+\NewAlgorithm{\Send}{Send}
 \NewAlgorithm{\Fwd}{Forward}
-\NewAlgorithm{\Send}{BuildRouteS}
-\NewAlgorithm{\Recv}{BuildRouteR}
-\NewAlgorithm{\ExtendRoute}{ExtendRoute}
-\NewAlgorithm{\CreateOnionLayer}{CreateLayer}
-\NewAlgorithm{\Dec}{Dec}
-\NewAlgorithm{\Store}{Store}
-\NewVariable{\sk}{sk}
+\NewAlgorithm{\Recv}{Receive}
 \NewVariable{\rdv}{rdv}
-\NewVariable{\LRV}{\mathcal{L_{RV}}\xspace}
-\NewVariable{\Hsend}{\mathcal{H}_{\text{send}}\xspace}
-\NewVariable{\Hrec}{\mathcal{H}_{\text{rec}}\xspace}
-\NewVariable{\Hforward}{\mathcal{H}_f\xspace}
-\NewVariable{\Hbackward}{\mathcal{H}_b\xspace}
-\NewVariable{\Hsendforward}{\mathcal{H}_{\text{send f}}\xspace}
-\NewVariable{\Hsendbackward}{\mathcal{H}_{\text{send b}}\xspace}
-\NewVariable{\Hrecforward}{\mathcal{H}_{\text{rec f}}\xspace}
-\NewVariable{\Hrecbackward}{\mathcal{H}_{\text{rec b}}\xspace}
-\NewVariable{\datakey}{k_{\text{data}}\xspace}
-%\NewVariable{\nfilechunks}{\#\text{chunks}}
-
-\david{the use of DeBE algorithms must be explicitly explained in this section}
-
-The principle of onion routing à la Tor~\cite{Tor} is to put nodes relaying messages between a source and a destination.
-By employing encryption layers, a relay doesn't know where it is situated on the message's path. 
-It only knows who gave him the message, and where to send it to.
 
 In contrast to Tor~\cite{Tor} that provides only one address per hop
-in the route, \name provides, for each layer of the onion, several
-alternative nodes for the next hop in the route depending on their
-probability of being online. 
-We call our modified onion routes Probabilistic Onion Routes or PORs.
+in the route, \name provides for each layer of the onion several
+alternatives for the next hop in the route depending on their
+probability of being online. We call our modified onion routes
+Probabilistic Onion Routes or PORs.
 
-Another difference from Tor, where connections are established by all nodes in the route, \name is stateless: the route's ends (the sender Alice and receiver Bob) cooperate to create the headers containing all the necessary routing information for future communication between Alice and Bob.
-In that regard, two headers are required: \Hforward to route packets from Alice to Bob, and \Hbackward for packets from Bob to Alice.
+Another difference from Tor, where connections are established by all
+nodes in the route, \name is stateless. The sender
+Alice and receiver Bob cooperate to create the headers containing all
+the necessary routing information for future communication between
+Alice and Bob. In that regard, we use two PORs: one to route packets from Alice to
+Bob, and one for packets acknowledgement from Bob to Alice (See
+Fig.~\ref{fig:file-exchange}~\ding{184}). We defined some fixed
+parameters such as $L$, the number of layers in a POR, and
+$\theta$, the stopping criterion for the layers creation, i.e the
+maximum authorized  probability that all devices in a layer fail at
+once.
 
-To implement our predictive onion routing mechanism, \name is thus split in two algorithms: the route building one, and the message routing one.
-Figure~\ref{fig:file-exchange} shows the process of the route creation until the first exchange of a file chunk from Alice to Bob.
-Alice uses the forward route to send file chunks to Bob, while Bob uses the backward route to send acknowledgments back to Alice.
+To implement our  probabilistic
+predictive onion routing mechanism, \name defined two different algorithms to
+receive, send messages among users' \squad. For instance,
+if Alice wants to send a message \(m\) to Bob, Bob uses the
+\([Recv]\) algorithm (See \cref{SPORRecv}) to create a probabilistic onion route \(H_{Bob}\) from
+ a set of rendez-vous point to its own devices from its \squad --- all the hops on the route are 
+chosen by Bob uniformly at random from its RPS (\view).
+ \([Recv]\) returns the \(H_{Bob}\).
+PORs have \(L\) layers, and for each layer the number of
+alternatives nodes depends of a failure threshold \(\theta\). 
+As long as \(\theta\) is not exceeded, alternatives nodes are added in
+\(H_{Bob}\) as depicted in \cref{ExtendRoute}. Thus the probability of
+failure for the extension is \(1 - (1 - \theta)^L\). In a similar
+manner, Alice create an onion route \(H_{Alice}\) to enable Bob to
+acknowledge its messages. Bob and Alice exchange then their calculated
+PORs (i.e. H_{Bob} andH_{Alice}), using an
+out-of-band channel, \eg using one device of their \squad (See
+Fig.~\ref{fig:file-exchange}~\ding{182}).
 
-\begin{figure}[t]
-  \includegraphics[width=\linewidth]{figures/file_exchange.pdf}
-  \caption{\label{fig:file-exchange}A schematic of the creation and usage of PORs between Alice and Bob's e-squads.}
-\end{figure}
+\NewAlgorithm{\Store}{Store}
 
-\subsubsection{Building routes} 
-\label{ssub:building_routes}
-
-\commentAL{A symmetric key \datakey should be exchanged during this step, to encrypt the data}
-
-When Alice wants to send a file $f$ to Bob, they first have to call the route building algorithm, and to exchange relevant information out of band (e.g.
-using mail, or their phones' bluetooth connection).
-They create a route of $L$ layers, a configuration parameter that must be odd. We introduce $l=(L-1)/2$.
-
-Bob (the receiver) initiates the route creation by calling the \Recv function displayed in figure~\ref{fig:route building algo}
-He randomly chooses nodes to constitute a rendez-vous layer \LRV, and nodes to constitute $l$ layers from \LRV to his \squad. 
-We come back on layer creation below.
-He crafts a layered encrypted header (more details below) to \LRV (excluded) to his squad (included), that we will call \Hrecforward.
-He also crafts his part of the header for the backward route, \Hrecbackward: it contains the route from Bob's \squad (excluded) to \LRV (included).
-
-Bob then sends \Hrecforward and the descriptors of the \LRV nodes to Alice, by calling Alice's \Send function (also in figure~\ref{fig:route building algo}).
-like Bob, Alice randomly picks nodes to constitutes $l$ layers from her \squad to \LRV.
-She also builds two encrypted headers: \Hsendforward contains the route from her \squad (excluded) to \LRV (included), while \Hsendbackward contains the route from \LRV (excluded) to her \squad (included).
-Alice now ha the full forward header \Hforward, as shown on line~\ref{hforward}
-Alice finally sends \Hsendbackward back to Bob.
-
-Back to \Recv function: Bob has the full backward header $\Hbackward$, as shown on line~\ref{hbackward}.
-
-\paragraph*{Layer creation}
-The function \CreateOnionLayer() iteratively adds random nodes (from the RPS's view \view) until the product $\prod_{d\in \mathcal{L}} (1 - p_d)$ falls below $\theta$.
-$(1 - p_d)$ is the probability that a device $d$ will be offline; the product is the probability that all devices on layer $\mathcal{L}$ fall offline at the same time.
-
-\begin{table}[t]
-\resizebox{\columnwidth}{!}{
-\begin{tabular}{lp{0.9\linewidth}}
-\toprule
-\multicolumn{2}{c}{\textbf{Parameters of the algorithm}} \\
-\midrule
-$\theta$ & Stopping criterion for the layers creation: maximum authorized  probability that all devices in a layer fail at once. \\
-$L$      & Number of layers in a Predictive Onion Route. \\
-$l = (L-1)/2$ & Number of layers (excluding $\LRV$) created by each end of the route. \\
-\bottomrule
-\end{tabular}
-}
-\label{tab:parameters}
-\end{table}
-
-\paragraph*{Header preparation} \commentAL{TODO}
-
-\begin{figure}[t]
-  %\framebox{\begin{minipage}{0.96\linewidth}
-  \begin{algorithmic}[1]
-    % \Require{%
-    %   $D$ is the set of alternative recipient devices.
-    % }
-    \Function{\Recv}{sender}
-      \State $\LRV \gets \CreateOnionLayer()$
-      \State layers $\gets [\,]$
-      \While{len(layers) $ < l$}
-        \State layers.append(\CreateOnionLayer())
-      \EndWhile
-      \State $\Hrecforward \gets$ properly encrypted layers
-      \State $\Hrecbackward \gets$ properly encrypted layers
-
-      \Comment{Out-of-band exchange}
-      \State $\Hsendbackward \gets$ sender.\Send(\Hrecforward, \LRV)
-
-      \State $\Hbackward \gets \Hrecbackward \concat \Hsendbackward$ \label{hbackward}
-      %\State $H_\rdv\gets \ExtendRoute[D\concat \top, L, \theta]$
-      % \State \Return $H_\rdv$
-      %   \Comment{Give to sender out-of-bound.}
-    \EndFunction
-  \end{algorithmic}
-  %\end{minipage}}
-
-  \vspace{0.3em}
-  %\framebox{\begin{minipage}{0.96\linewidth}
-  \begin{algorithmic}[1]
-    % \Require{%
-    %   $m$ is the message to be sent,
-    %   $H_\rdv$ is the onion-route given by the recipient.
-    % }
-    \Function{\Send}{\Hrecforward, \LRV}
-      \State layers $\gets [\,]$
-      \While{len(layers) $ < l$}
-        \State layers.append(\CreateOnionLayer())
-      \EndWhile
-      \State $\Hsendforward \gets$ properly encrypted layers
-      \State $\Hsendbackward \gets$ properly encrypted layers
-      \State $\Hforward \gets \Hsendforward \concat \Hrecforward$ \label{hforward}
-      \State \Return \Hsendbackward
-
-      \STATE $H\gets \ExtendRoute[H_\rdv, L, \theta]$
-      \State $D\concat C_H\gets H_\rdv$
-      \For{$d\in D$}
-        \Comment{Uniformly randomly chosen}
-        \If{$d\method \Fwd[C_H, m] \neq \bot$}
-          \State \Return $\top$
-        \EndIf
-      \EndFor
-      \State \Return $\bot$
-    \EndFunction
-  \end{algorithmic}
-  %\end{minipage}}
-
-  % \vspace{0.3em}
-  % %\framebox{\begin{minipage}{0.96\linewidth}
-  \begin{algorithmic}[1]
-    \Require{%
-      $H$ is a header of the form \(D\concat H'\) or \(D\concat \top\), where 
-      \(D\) is a set of device addresses.
-      $\pk_D$ is the public key of device set $D$.
-      $L$ is the length of the route,
-      $\theta$ is the threshold of probability of failure.%
-    }
-    \Function{\ExtendRoute}{$\mathcal{H}, l$}
-      \If{$L\leq 0$}
-        \State \Return $H$
-      \EndIf
-      \State $D\gets \CreateOnionLayer[\theta]$
-      \State $H\gets D\concat \DeBEenc[\mpk, D, H]$
-      \State \Return $\ExtendRoute[H, L-1, \theta]$
-    \EndFunction
-  \end{algorithmic}
-
-  \vspace{0.3em}
-
-  \begin{algorithmic}[1]
-    \Function{\CreateOnionLayer}{\null}
-      \State $(d, \pk_d, p_d)\gets \GetRandomPeer$
-      \State $\mathcal{L}\gets \{(d, \pk_d, p_d)\}$
-      \While{$\prod_{d\in \mathcal{L}} (1 - p_d) \geq \theta$}
-        \State $(d, \pk_d, p_d)\gets \GetRandomPeer$
-        \State $\mathcal{L}\gets \mathcal{L}\cup \{(d, \pk_d, p_d)\}$
-      \EndWhile
-      \State \Return $\mathcal{L}$
-    \EndFunction
-  \end{algorithmic}
-  %\end{minipage}}
-  \caption{\label{fig:route building algo}The route building algorithm}
-\end{figure}
-
-\subsubsection{Routing messages}
-\label{ssub:routing_messages}
-
-% Alice uses \(\Send\) at some
-% later time to send the message to Bob using any of her devices from
-% its \squad.% (See \cref{SPORSend}). 
-% First, \(\Send\) extends the route
-% \(H_\rdv\) with some hops of Alice's choosing (uniformly randomly
-% chosen). Second, \(\Send\) extracts from the onion the first
-% layer, which contained the overall
-% possible rendez-vous points $D$ previously selected by the recipient (i.e. Bob).
-% One device from $D$ is randomly chosen, and the \(\Fwd\)
-% sub-function is called as long as the message forwarding to one node of
-% the next layer is not successful.% (See \cref{SPORFwd}). 
-% Along the path, each node decrypts
-% in sequence the different layer with the current node’s private key. 
-% The end of the route is reached when special value \(H_\rdv = \top\) is
-% encountered. Consequently the ciphered message \(c_m\) is then stored
-% in the disk of the local node through the \(\Store\) sub function.%(\cref{SPORRecv}).
-
-\begin{figure}[t]
-  %\framebox{\begin{minipage}{0.96\linewidth}
-  \begin{algorithmic}[1]
-    %\Require{$\pk, \sk$ is the public--private key-pair of the node.}
-    \Function{\Fwd}{$C_H, m$}
-      \State $H\gets \DeBEdec[\mpk, \sk, C_H]$
-      \If{$H = \bot$}
-        \State \Return $\bot$
-      \EndIf
-      \State $\{d_i\}\concat C_H'\gets H$
-      \If{$C_H' = \top$}
-        \State \Return $\Store[m]$
-      \EndIf
-      \For{$d\in \{d_i\}$}
-        \Comment{Uniformly randomly chosen}
-        \If{$d\method \Fwd[C_H', m] \neq \bot$}
-          \State \Return $\top$
-        \EndIf
-      \EndFor
-      \State \Return $\bot$
-    \EndFunction
-  \end{algorithmic}
-
-  \begin{algorithmic}[1]
-    \Function{\Store}{$m$}
-      \State $m\gets \DeBEdec[\mpk, \sk, c_m]$
-      \If{$m = \bot$}
-        \State \Return $\bot$
-      \EndIf
-      \State Store $m$ to disk.
-      \State \Return $\top$
-    \EndFunction
-  \end{algorithmic}
-  %\end{minipage}}
-  \caption{\label{SPORFwd}%
-    The \(\Fwd\) algorithm forwards \(m\) down the route \(H\), obtained 
-    by decrypting \(C_H\) with the node's associated private key.
-    The special value \(H = \top\) indicated the end of the route, thus \(c_m\) 
-    is intended for the local node and \(c_m\) is instead sent to disk using 
-    \(\Store\).% (\cref{SPORRecv}).%
-  }
-\end{figure}
-
-\subsubsection{Exchanging a file} % (fold)
-\label{ssub:exchanging_a_file}
-
-% subsubsection exchanging_a_file (end)
-\newcommand{\messagesize}{\ensuremath{s_m}}
-\newcommand{\filesize}{\ensuremath{s_{fc}}}
-\newcommand{\headersize}{\ensuremath{s_{\mathcal{H}}}}
-
-Once Alice get the \Hforward, she can start sending her file $f$ to Bob. 
-To do so, she chunks it to pieces, and iteratively send the chunks to Bob, that replies with an acknowledgment (ACK) for that chunk.
-Once all chunks have been acknowledged, Alice sends an empty message to Bob, signifying transfer termination.
-
-% To prevent \name from message size analysis attacks, the messages have a fixed size \messagesize.
-% As shown in the previous section~\ref{ssub:building_routes}, headers have a variable size \headersize per route (but \Hforward remains constant once the POR is established).
-% For this reason, file chunks have a fixed size per session: $\filesize = \messagesize - \headersize$.
-
-A message payload is composed of the following information:
-
-\begin{itemize}
-  \item An identifier for the file;
-  \item The chunk ID, that identifies its position in $f$;
-  \item The file chunk;
-  \item An error correction code (e.g. a SHA-1 hash of the chunk, à la BitTorrent\cite{bt_bep3}).
-\end{itemize}
-
-Payloads are encoded using \datakey that was shared between Alice and Bob during route creation \commentAL{Not done}.
-
-% We are interested in transferring large files.
-% Every device \(d\in D\) in the global device swarm is only periodically online.
-% We will thus divide the data to send into \(n\) smaller chunks (similar to 
-% BitTorrent~\cite{BitTorrent}).
-% The idea is to choose \(n\) such that each chunk will be small enough to be 
-% successfully relayed by a device before it goes offline again.
-% The chunk size is empirically determined in \cref{Performance}.
-% \commentDaniel{Adrien, is that true?}
-
-% As stated above, Alice and Bob exchange some limited data out-of-bound using 
-% their smartphones.
-% The information they will exchange is the following:
-% \begin{enumerate}
-%   \item Bob creates an onion route header, \(H_\rdv\), by running 
-%     \([\Recv]\) %(\cref{SPORRecv}) 
-%     and gives it to Alice.
-%   \item Alice gives Bob number of file chunks, \(n\), and the size of the file 
-%     chunks.
-%   \item They agree on a file-specific key \(k\) for some (authenticated) 
-%     encryption scheme \(\Enc*\).
-% \end{enumerate}
-% Then Alice encrypts the file \(f\) and receives the ciphertext \(c_f\gets 
-%   \Enc*[Enc](k, f)\).
-% She then divides \(c_f\) into \(n\) chunks, \(c_f^{(1)}, \dotsc, c_f^{(n)}\), 
-% and runs \(\Send(H_\rdv, c_f^{(i)})\) for all \(1\leq i\leq n\) in 
-% parallel.
-% \commentDaniel{Or shall we do it sequentially?}
-
-% For instance, if Alice wants to send a message \(m\) to Bob, they are both going to perform a part of the building algorithm.
-% Bob uses the \([\Recv]\) function (See \cref{SPORRecv}) to create a probabilistic onion route $\mathcal{H_B}$ from
-%  a rendez-vous (RV) layer $\mathcal{L_{RV}}$ to its own devices from its \squad---all the hops on the route are 
-% chosen by Bob uniformly at random from the Global Overlay.
-%  \(\SPOR[\Recv]\)
-% returns $\mathcal{H_B}$ and  that Bob gives to Alice using an
-% out-of-band channel, \eg using one device of its \squad.
-% PORs have \(L\) layers, and for each layer the number of
-% alternatives nodes depends of a failure threshold \(\theta\). 
-% As long as \(\theta\) is not exceeded, alternatives nodes are added in
-% \(H_\rdv\) as depicted in \cref{ExtendRoute}. Thus the probability of
-% failure for the extension is \(1 - (1 - \theta)^L\).
-
-% Once Alice get the \(H_\rdv\), Alice uses \(\SPOR[\Send]\) at some
-% later time to send the message to Bob using any of her devices from
-% its \squad (See \cref{SPORSend}). First, \(\SPOR[\Send]\) extends the route
-% \(H_\rdv\) with some hops of Alice's choosing (uniformly randomly
-% chosen). Second, \(\SPOR[\Send]\) extracts from the onion the first
-% layer, which contained the overall
-% possible rendez-vous points $D$ previously selected by the recipient (i.e. Bob).
-% One device from $D$ is randomly chosen, and the \(\SPOR[\Fwd]\)
-% sub-function is called as long as the message forwarding to one node of
-% the next layer is not successful (See \cref{SPORFwd}). Along the path, each node decrypts
-% in sequence the different layer with the current node’s private key. 
-% The end of the route is reached when special value \(H_\rdv = \top\) is
-% encountered. Consequently the ciphered message \(c_m\) is then stored
-% in the disk of the local node through the \(\Store\) sub function 
-% (\cref{SPORRecv}).
+Once Alice get the \(H_{Bob}\), Alice uses \([Send]\) at some
+later time to send the message to Bob using any of her devices from
+its \squad (See \cref{SPORSend}). First, \([Send]\) extends the route
+\(H_{Bob}\) with some hops of Alice's choosing (uniformly randomly
+chosen). Second, \([Send]\) extracts from the onion the first
+layer, which contained the overall
+possible rendez-vous points $D$ previously selected by the recipient (i.e. Bob).
+One device from $D$ is randomly chosen, and the \([Fwd]\)
+sub-function is called as long as the message forwarding to one node of
+the next layer is not successful (See \cref{SPORFwd}). Along the path, each node decrypts
+in sequence the different layer with the current node’s private key. 
+The end of the route is reached when special value \(H_{Bob} = \top\) is
+encountered. Consequently the ciphered message \(c_m\) is then stored
+in the disk of the local node through the \([Store]\) sub function 
+(\cref{SPORRecv}).
 
@@
 %    devices and returns the route to the sender.
+
+\begin{figure}[t]
+\center
+  \includegraphics[scale=.55]{figures/file_exchange_v2.pdf}
+  \caption{\label{fig:file-exchange}A schematic of the creation and usage of PORs between Alice and Bob's e-squads.}
+\end{figure}
+
+\NewAlgorithm{\ExtendRoute}{ExtendRoute}
+\NewAlgorithm{\CreateOnionLayer}{CreateOnionLayer}
+
+    % \Require{%
+    %   $H$ is a header of the form \(D\concat H'\) or \(D\concat \top\), where 
+    %   \(D\) is a set of device addresses.
+    %   $\pk_D$ is the public key of device set $D$.
+    % }
+
+\begin{figure}
+
+  \framebox{\begin{minipage}{0.96\linewidth}
+  \begin{algorithmic}[1]
+\scriptsize
+    \Function{\ExtendRoute}{$H, L$}
+      \If{$L\leq 0$}
+        \State \Return $H$
+      \EndIf
+      \State $D\gets \CreateOnionLayer[]$
+      \State $H\gets D\concat \DeBEenc[\mpk, D, H]$
+      \State \Return $\ExtendRoute[H, L-1, \theta]$
+    \EndFunction
+  \vspace{0.3em}
+    \Function{\CreateOnionLayer}{}
+      \State $(d, \pk_d, p_d)\gets \GetRandomPeer$
+      \State $D\gets \{(d, \pk_d, p_d)\}$
+      \While{$\prod_{d\in D} p_d > \theta$}
+        \State $(d, \pk_d, p_d)\gets \GetRandomPeer$
+        \State $D\gets D\cup \{(d, \pk_d, p_d)\}$
+      \EndWhile
+      \State \Return $D$
+    \EndFunction
+  \end{algorithmic}
+  \end{minipage}}
+  \caption{\label{ExtendRoute}%
+    \scriptsize
+    The \(\ExtendRoute\) algorithm extends a route \(H\)
+  }
+\end{figure}
+
+\NewAlgorithm{\Dec}{Dec}
+\NewVariable{\sk}{sk}
+
+\begin{figure}
+  \framebox{\begin{minipage}{0.96\linewidth}
+  \begin{algorithmic}
+    \Require{%
+      $D$ is the set of alternative recipient devices.
+    }
+    \Function{[\Recv]}{$D$}
+      \State $H_\rdv\gets \ExtendRoute[D\concat \top, L, \theta]$
+      \State \Return $H_\rdv$
+        \Comment{Give to sender out-of-bound.}
+    \EndFunction
+  \end{algorithmic}
+  \end{minipage}}
+  \caption{\label{SPORRecv}%
+\scriptsize
+    The \(\SPOR[\Recv]\) algorithm prepares the recipient for receiving a file.
+  }
+\end{figure}
+
+\begin{figure}
+  \framebox{\begin{minipage}{0.96\linewidth}
+  \begin{algorithmic}
+    \Require{%
+      $m$ is the message to be sent,
+      $H$ is the onion-route given by the recipient.
+    }
+    \Function{[\Send]}{$H,m$}
+      \State $H\gets \ExtendRoute[H_\rdv, L, \theta]$
+      \State $D\concat C_H\gets H_\rdv$
+      \For{$d\in D$}
+        \Comment{Uniformly randomly chosen}
+        \If{$d\method \Fwd[C_H, m] \neq \bot$}
+          \State \Return $\top$
+        \EndIf
+      \EndFor
+      \State \Return $\bot$
+    \EndFunction
+  \end{algorithmic}
+  \end{minipage}}
+  \caption{\label{SPORSend}%
+    \scriptsize
+    The \(\SPOR[\Send]\) algorithm 
+  }
+\end{figure}
+
+\begin{figure}
+  \framebox{\begin{minipage}{0.96\linewidth}
+  \begin{algorithmic}
+    \Require{$\pk, \sk$ is the public--private key-pair of the node.}
+    \Function{\SPOR[\Fwd]}{$C_H, m$}
+      \State $H\gets \DeBEdec[\mpk, \sk, C_H]$
+      \If{$H = \bot$}
+        \State \Return $\bot$
+      \EndIf
+      \State $\{d_i\}\concat C_H'\gets H$
+      \If{$C_H' = \top$}
+        \State \Return $\Store[m]$
+      \EndIf
+      \For{$d\in \{d_i\}$}
+        \Comment{Uniformly randomly chosen}
+        \If{$d\method \Fwd[C_H', m] \neq \bot$}
+          \State \Return $\top$
+        \EndIf
+      \EndFor
+      \State \Return $\bot$
+    \EndFunction
+    \Function{\Store}{$m$}
+      \State $m\gets \DeBEdec[\mpk, \sk, c_m]$
+      \If{$m = \bot$}
+        \State \Return $\bot$
+      \EndIf
+      \State Store $m$ to disk.
+      \State \Return $\top$
+    \EndFunction
+  \end{algorithmic}
+  \end{minipage}}
+  \caption{\label{SPORFwd}%
+    The \(\SPOR[\Fwd]\) algorithm forwards \(m\) down the route \(H\), obtained 
+    by decrypting \(C_H\) with the node's associated private key.
+    The special value \(H = \top\) indicated the end of the route, thus \(c_m\) 
+    is intended for the local node and \(c_m\) is instead sent to disk using 
+    \(\Store\) (\cref{SPORRecv}).%
+  }
+\end{figure}

### 2018-05-02 paper/evaluation.tex

@@
 \vspace{-1em}
-
+\footnotesize
+\centering
 $$A =
@@
 
-\includegraphics[width=0.9\columnwidth]{figures/hmm.pdf}
+\includegraphics[width=0.65\columnwidth]{figures/hmm.pdf}
 \vspace{2ex}
-\includegraphics[width=\columnwidth]{figures/sample_usage.pdf}
+\includegraphics[width=0.9\columnwidth]{figures/sample_usage.pdf}
 
@@
 \centering
-\includegraphics[width=0.8\columnwidth]{figures/nodes_per_layer_vs_theta.pdf}
+\includegraphics[width=0.7\columnwidth]{figures/nodes_per_layer_vs_theta.pdf}
 \caption{\label{fig:nodes_per_layer_vs_theta}Number of nodes per layer of POR as a function of the parameter $\theta$ (the maximal probability that all nodes in a layer fail at once).
@@
 \begin{figure}[t]
-\includegraphics[width=\columnwidth]{figures/success_rate_vs_t.pdf}
+\includegraphics[width=0.9\columnwidth]{figures/success_rate_vs_t.pdf}
 \caption{\label{fig:success_rate_vs_t}Availability rate of routes as a function of the time since the route establishment, for several values of the parameters $\theta$ (the maximal probability that all nodes in a layer fail at once) and $L$ (the number of layers in the route).}
@@
 
-\newcommand{\fsize}{\ensuremath{s_f}}
-
-To assess the efficiency of \name, we did several file exchanges with fixed parameters and a random file size $\fsize\in [5\text{MB}, 500\text{MB}]$. 
+To assess the efficiency of \name, we did several file exchanges with fixed parameters and a random file size between 5MB and 500MB.
 By performing 20 experiments using the parameters described in \ref{ssub:experimental_parameters}, we obtained traces for 200 file exchanges.
+All files reached their destination successfully.
 
@@
 \centering
-\includegraphics[width=0.9\columnwidth]{figures/transfer_time_vs_size.pdf}
+\includegraphics[width=0.7\columnwidth]{figures/transfer_time_vs_size.pdf}
 
 \caption{\label{fig:transfer_time_vs_size}Files' transfer time as a function of their size, along with a log-linear regression of the same data.}
-
 \end{figure}
 
+Figure~\ref{fig:transfer_time_vs_size} shows the results of this experiment: it plots the transfer time as a function of the file size.
+File size is binned into 20 bins, making the series of points representing the average transfer time per bin with standard deviation bars.
+We fitted a log-linear regression to this plot, displayed as a curve.
+It shows that transfer time increases less fast that the file size.
+
+Absolute time values are meaningless here: our system was evaluated on a single machine and on a single process.
+The code execution was not parallel, and only one device was executing at any point in time.
+
+Still, we investigated the message transmission.
+In this simulation, 145172 chunks were sent, and 141276 ACKs were received: 6.00\% of the chunks were lost in transit.
+A chunk took an average of 56s $\pm$ 36s to reach its destination, while ACKs to 48s $\pm$ 33s to do so.
+This is explained mostly by devices falling offline between the time they receive a message and the time they forward it.
+
+We now understand the log-linear curve and it's big initial slope: messages spend a long time in transit, but sending messages in parallel does not impact this time.
+Even small files thus need a lot of time to transfer, while bigger files do not suffer more than small files from the messages delay.
+\\
+
+Overall, we succeeded in creating a reliable and secure file transfer protocol over an underlying network of unreliable, low-end devices.
+Its performance could be enhanced by taking interest in bottlenecks in the messages transmission, i.e. scheduling messages in a similar predictive manner as we planned routes creation.
+
 % subsection file_transfer (end)

### 2018-05-02 paper/evaluation.tex
a

@@
 \paragraph*{PORs creation}
-Figures \ref{fig:nodes_per_layer_vs_theta} and \ref{fig:success_rate_vs_t} come from the same data, with 10 experiments per set of settings.
+Figure \ref{fig:success_rate_vs_t} come from the same data, with 10 experiments per set of settings.
 $\theta$, the threshold of the probability that all nodes fail at once (cf. \ref{ssub:building_routes}), takes the following values: $[0.1, 0.01, 0.001, 0.0001]$.
@@
 An experiment consisted in $L*5$ users, where we randomly picked pairs of users to compute 20 routes.
-Hence, each point in figure~\ref{fig:nodes_per_layer_vs_theta} is the average of 3000 layers size; 
-each point in figure~\ref{fig:nodes_per_layer_vs_theta} is the availability rate over 200 routes.
+Hence, each point on the top of figure~\ref{fig:nodes_per_layer_vs_theta} is the average of 3000 layers size; 
+each point on the bottom is the availability rate over 200 routes.
 
@@
 
-\begin{figure}[t]
-\centering
-\includegraphics[width=0.7\columnwidth]{figures/nodes_per_layer_vs_theta.pdf}
-\caption{\label{fig:nodes_per_layer_vs_theta}Number of nodes per layer of POR as a function of the parameter $\theta$ (the maximal probability that all nodes in a layer fail at once).
-The number of nodes logarithmically decreases as we relax the $\theta$ constraint.}
-\end{figure}
-
-We first measure the influence of the parameter $\theta$ on the number of nodes per layer in figure~\ref{fig:nodes_per_layer_vs_theta}, by displaying average and standard deviation of the number of nodes for $\theta=[10^{-4}, 10^{-3}, 10^{-2}, 10^{-1}]$ (the other experiment parameters are listed in section~\ref{ssub:experimental_parameters}).
+We first measure the influence of the parameter $\theta$ on the number of nodes per layer on the top of figure~\ref{fig:success_rate_vs_t}, by displaying average and standard deviation of the number of nodes for $\theta=[10^{-4}, 10^{-3}, 10^{-2}, 10^{-1}]$ (the other experiment parameters are listed in section~\ref{ssub:experimental_parameters}).
 As we can see, the number of devices per layer logarithmically decreases as we relax the constraint on the layer's availability.
@@
 \begin{figure}[t]
+\centering
+\includegraphics[width=0.7\columnwidth]{figures/nodes_per_layer_vs_theta.pdf}
+\vspace{2ex}
 \includegraphics[width=0.9\columnwidth]{figures/success_rate_vs_t.pdf}
-\caption{\label{fig:success_rate_vs_t}Availability rate of routes as a function of the time since the route establishment, for several values of the parameters $\theta$ (the maximal probability that all nodes in a layer fail at once) and $L$ (the number of layers in the route).}
+\caption{\label{fig:success_rate_vs_t}On top: Number of nodes per layer of POR as a function of the parameter $\theta$ (the maximal probability that all nodes in a layer fail at once).
+The number of nodes logarithmically decreases as we relax the $\theta$ constraint.
+On bottom: Availability rate of routes as a function of the time since the route establishment, for several values of the parameters $\theta$ (the maximal probability that all nodes in a layer fail at once) and $L$ (the number of layers in the route).}
 \end{figure}

### 2018-05-02 paper/evaluation.tex
fig

@@
 
-\includegraphics[width=0.65\columnwidth]{figures/hmm.pdf}
-\vspace{2ex}
+%\includegraphics[width=0.65\columnwidth]{figures/hmm.pdf}
+%\vspace{2ex}
 \includegraphics[width=0.9\columnwidth]{figures/sample_usage.pdf}
 
-\caption{\label{fig:hmm} Example Hidden Markov Model (HMM) of a user's behavior: on top are the HMM parameters, on the middle is a visual representation of the model, and on the bottom is a sample output from the model.}
+\caption{\label{fig:hmm} Example Hidden Markov Model (HMM) of a user's behavior: on top are the HMM parametersand on the bottom is a sample output from the model.}
 \end{figure}
@@
 HMMs being generative probabilistic models, they allow the generation of observation sequence $O$ given the parameters of the model $\lambda_N$.
-Figure~\ref{fig:hmm} shows a possible outcome of the creation of a user's HMM $\lambda_N$, its graphical representation, along with a sample observation sequence $O$ output from the model $\lambda_N$.
+Figure~\ref{fig:hmm} shows a possible outcome of the creation of a user's HMM $\lambda_N$ along with a sample observation sequence $O$ output from the model $\lambda_N$.
 
@@
 \includegraphics[width=0.7\columnwidth]{figures/nodes_per_layer_vs_theta.pdf}
-\vspace{2ex}
+\vspace{1ex}
 \includegraphics[width=0.9\columnwidth]{figures/success_rate_vs_t.pdf}

### 2018-05-02 paper/message-passing-design.tex
up

@@
 
+% <<<<<<< HEAD
+%   \framebox{\begin{minipage}{0.96\linewidth}
+% =======
+%       \State $H\gets \ExtendRoute[H_\rdv, L, \theta]$
+%       \State $D\concat C_H\gets H_\rdv$
+%       \For{$d\in D$}
+%         \Comment{Uniformly randomly chosen}
+%         \If{$d\method \Fwd[C_H, m] \neq \bot$}
+%           \State \Return $\top$
+%         \EndIf
+%       \EndFor
+%       \State \Return $\bot$
+%     \EndFunction
+%   \end{algorithmic}
+%   %\end{minipage}}
+
+%   % \vspace{0.3em}
+%   % %\framebox{\begin{minipage}{0.96\linewidth}
+% >>>>>>> 028fcc4225628a4b1d8b1b48a64b7975d11021ab
 \framebox{\begin{minipage}{0.96\linewidth}
@@
   \begin{algorithmic}
+\scriptsize
     \Require{%
@@
     \Function{[\Send]}{$H,m$}
-      \State $H\gets \ExtendRoute[H_\rdv, L, \theta]$
+      \State $H\gets \ExtendRoute[H, L, \theta]$
       \State $D\concat C_H\gets H_\rdv$
@@
   \begin{algorithmic}
-    \Require{$\pk, \sk$ is the public--private key-pair of the node.}
+\scriptsize
+    \Require{$\sk$ is the private key-pair of the current node.}
     \Function{\SPOR[\Fwd]}{$C_H, m$}
@@
   \caption{\label{SPORFwd}%
-    The \(\SPOR[\Fwd]\) algorithm forwards \(m\) down the route \(H\), obtained 
-    by decrypting \(C_H\) with the node's associated private key.
-    The special value \(H = \top\) indicated the end of the route, thus \(c_m\) 
-    is intended for the local node and \(c_m\) is instead sent to disk using 
-    \(\Store\) (\cref{SPORRecv}).%
+    The \(\SPOR[\Fwd]\) algorithm forwards \(m\) down the route \(H\).%
   }

### 2018-05-02 paper/related.tex
up

@@
 %In our experiments, we simulate users' devices participating in a distributed protocol. We base our modeling of devices' online availability on existing literature such as the following.  
-Field studies provide \emph{usage and connectivity patterns of users' appliances}.
+% Field studies provide \emph{usage and connectivity patterns of users' appliances}.
 Karlson et al.
@@
 \cite{Wagner_Rice_Beresford_2013} conducted a thorough data collection on Android devices via an application called Device Analyzer, that collected metrics on movement patterns, connectivity and energy consumption from 16,000 users.
-%\commentAL{Conclude: will we use their dataset? Why are these papers useful to us?}
-Several works point out the emerging trend of \emph{multi-device interaction}.
-A 2012 Google-led study \cite{google2012} stated that the USA are nowadays ``a nation of multi-screeners''.
+% %\commentAL{Conclude: will we use their dataset? Why are these papers useful to us?}
+% Several works point out the emerging trend of \emph{multi-device interaction}.
+% A 2012 Google-led study \cite{google2012} stated that the USA are nowadays ``a nation of multi-screeners''.
 People switch their attention toward their phone, laptop, tablet or their television depending on the context.
-M\"uller et al. \cite{Muller_Gove_Webb_Cheang_2015} specifically compared the usage patterns of phones against tablets.
-Jokela et al. \cite{Jokela_Ojala_Olsson_2015} and \cite{google2012} also differentiated sequential and parallel usage of one's multiple devices.
-Research in P2P networks observed \cite{Stutzbach_Rejaie_2006} and modeled \cite{Yao_Leonard_Wang_Loguinov_2006} patterns of \emph{churn} (\ie participants moving in and out of a system).
-We take inspiration from these works in order to establish credible models of user behaviors to evaluate our protocol. 
+% M\"uller et al. \cite{Muller_Gove_Webb_Cheang_2015} specifically compared the usage patterns of phones against tablets.
+% Jokela et al. \cite{Jokela_Ojala_Olsson_2015} and \cite{google2012} also differentiated sequential and parallel usage of one's multiple devices.
+% Research in P2P networks observed \cite{Stutzbach_Rejaie_2006} and modeled \cite{Yao_Leonard_Wang_Loguinov_2006} patterns of \emph{churn} (\ie participants moving in and out of a system).
+% We take inspiration from these works in order to establish credible models of user behaviors to evaluate our protocol. 
 % Participants can own several devices: their smartphone is always on, but lacks processing power, while their laptop is rarely online, though it contains better hardware, etc.

### 2018-05-02 paper/message-passing-design.tex
up
merge algo

@@
 if Alice wants to send a message \(m\) to Bob, Bob uses the
-\([Recv]\) algorithm (See \cref{SPORRecv}) to create a probabilistic onion route \(H_{Bob}\) from
+\([Recv]\) algorithm (See \cref{SPORFwd}) to create a probabilistic onion route \(H_{Bob}\) from
  a set of rendez-vous point to its own devices from its \squad --- all the hops on the route are 
@@
 later time to send the message to Bob using any of her devices from
-its \squad (See \cref{SPORSend}). First, \([Send]\) extends the route
+its \squad (See \cref{SPORFwd}). First, \([Send]\) extends the route
 \(H_{Bob}\) with some hops of Alice's choosing (uniformly randomly
@@
 in the disk of the local node through the \([Store]\) sub function 
-(\cref{SPORRecv}).
+(\cref{SPORFwd}).
 
@@
 %    is intended for the local node and \(c_m\) is instead sent to disk using 
-%    \(\Store\) (\cref{SPORRecv}).%
+%    \(\Store\) (\cref{SPORFwd}).%
 
@@
 
-    % \Require{%
-    %   $H$ is a header of the form \(D\concat H'\) or \(D\concat \top\), where 
-    %   \(D\) is a set of device addresses.
-    %   $\pk_D$ is the public key of device set $D$.
-    % }
-
 \begin{figure}
-
-% <<<<<<< HEAD
-%   \framebox{\begin{minipage}{0.96\linewidth}
-% =======
-%       \State $H\gets \ExtendRoute[H_\rdv, L, \theta]$
-%       \State $D\concat C_H\gets H_\rdv$
-%       \For{$d\in D$}
-%         \Comment{Uniformly randomly chosen}
-%         \If{$d\method \Fwd[C_H, m] \neq \bot$}
-%           \State \Return $\top$
-%         \EndIf
-%       \EndFor
-%       \State \Return $\bot$
-%     \EndFunction
-%   \end{algorithmic}
-%   %\end{minipage}}
-
-%   % \vspace{0.3em}
-%   % %\framebox{\begin{minipage}{0.96\linewidth}
-% >>>>>>> 028fcc4225628a4b1d8b1b48a64b7975d11021ab
 \framebox{\begin{minipage}{0.96\linewidth}
@@
     }
-    \Function{[\Recv]}{$D$}
+    \Function{\Recv}{$D$}
       \State $H_\rdv\gets \ExtendRoute[D\concat \top, L, \theta]$
@@
   \end{algorithmic}
-  \end{minipage}}
-  \caption{\label{SPORRecv}%
-\scriptsize
-    The \(\SPOR[\Recv]\) algorithm prepares the recipient for receiving a file.
-  }
-\end{figure}
-
-\begin{figure}
-  \framebox{\begin{minipage}{0.96\linewidth}
+  %\end{minipage}}
+%   \caption{\label{SPORFwd}%
+% \scriptsize
+%     The \(\Recv\) algorithm prepares the recipient for receiving a file.
+%   }
+  %\framebox{\begin{minipage}{0.96\linewidth}
   \begin{algorithmic}
@@
     }
-    \Function{[\Send]}{$H,m$}
+    \Function{\Send}{$H,m$}
       \State $H\gets \ExtendRoute[H, L, \theta]$
@@
   \end{algorithmic}
-  \end{minipage}}
-  \caption{\label{SPORSend}%
-    \scriptsize
-    The \(\SPOR[\Send]\) algorithm 
-  }
-\end{figure}
-
-\begin{figure}
-  \framebox{\begin{minipage}{0.96\linewidth}
+  %\end{minipage}}
+  % \caption{\label{SPORFwd}%
+  %   \scriptsize
+  %   The \(\Recv\), \(\Send\) and \(\Fwd\) algorithms.
+  % }
+ % \framebox{\begin{minipage}{0.96\linewidth}
   \begin{algorithmic}
@@
     \Require{$\sk$ is the private key-pair of the current node.}
-    \Function{\SPOR[\Fwd]}{$C_H, m$}
+    \Function{\Fwd}{$C_H, m$}
       \State $H\gets \DeBEdec[\mpk, \sk, C_H]$
@@
   \caption{\label{SPORFwd}%
-    The \(\SPOR[\Fwd]\) algorithm forwards \(m\) down the route \(H\).%
+    \scriptsize
+    The \(\Recv\) (prepares the recipient for receiving a file), \(\Send\) and \(\Fwd\) (forwards \(m\) down the route \(H\)) algorithms.
   }

### 2018-05-02 paper/security-discussion.tex
final

@@
 How well they can do if they do not control the entire route, depends on the 
-choice of the encryption scheme \(\Enc*\), used to encrypt the message \(m\) 
-(see \cref{sec:file_exchange}).
+choice of the encryption scheme \(\Enc*\), used to encrypt the message \(m\). 
+%(see \cref{sec:file_exchange}).
 
@@
 (We could also choose a deniable encryption scheme~\cite{DeniableEncryption}, 
-\eg the one by \textcite{OTPKX} which is both deniable and authenticated and 
-provides \ac{DEN-SS}.)
+\eg \cite{OTPKX} which is authenticated and provides deniability under
+surveillance-state attacks.) %is both deniable and authenticated and  provides \ac{DEN-SS}.)
 This would give confidentiality (or deniability) and integrity for the message, 
@@
 sent to Bob, unless it is an ongoing transfer.
-
-\subsection{Limitations}%
+\\
+%\subsection{Limitations}%
 \label{security-limitations}
@@
 
-\subsection{Future Work}
+% \subsection{Future Work}
 
-One thing that we can directly improve is the header.
-We see two alternative paths for improving the header.
-First, we might be able to adapt the Sphinx~\cite{Sphinx} cryptographic packet 
-format to the routing of \(\SPOR\).
-Then we could achieve the properties of Sphinx, \eg preventing the last node to 
-learn the destination, and enjoy provable security.
+% One part that we can directly improve is the header.
+% We see two alternative paths for improving the header.
+% First, we might be able to adapt the Sphinx~\cite{Sphinx} cryptographic packet 
+% format to the routing of \(\SPOR\).
+% Then we could achieve the properties of Sphinx, \eg preventing the last node to 
+% learn the destination, and enjoy provable security.
 
-The second approach would be to use the technique by \textcite{PPACinPubFS}.
-They adapt \(\ANOBE\) in such a way that its ciphertexts decrypt to different 
-things for different recipients.
-This way we could have one ciphertext encrypted for all the alternative nodes 
---- across layers.
-Then the ciphertext would decrypt to different plaintexts for nodes on different 
-layers in the route.
-This would hide the path length (constant-size ciphertexts by padding) and the 
-position of individual nodes.
-This approach would probably be the easiest, but would probably not provide all 
-the properties from Sphinx (\eg resistance to active tagging attacks).
+% The second approach would be to use the technique by \textcite{PPACinPubFS}.
+% They adapt \(\ANOBE\) in such a way that its ciphertexts decrypt to different 
+% things for different recipients.
+% This way we could have one ciphertext encrypted for all the alternative nodes 
+% --- across layers.
+% Then the ciphertext would decrypt to different plaintexts for nodes on different 
+% layers in the route.
+% This would hide the path length (constant-size ciphertexts by padding) and the 
+% position of individual nodes.
+% This approach would probably be the easiest, but would probably not provide all 
+% the properties from Sphinx (\eg resistance to active tagging attacks).

### 2018-05-02 paper/abstract.tex
m

@@
 In the case of onion routing systems for anonymity,
-Our solution allows the system to include unreliable nodes and take advantage of locality, neither of which is currently provided in TOR.
+Our solution allows the system to include unreliable nodes, without dedicated relays, %take advantage of locality, 
+neither of which is currently the case in TOR.

### 2018-05-02 paper/intro.tex
m

--- 2018-04-30 paper/intro.tex
@@
 This turns out to be a critical limitation, as famously emphasized by a former NSA and CIA director: "We kill people based on metadata.''~\cite{NaughtonTheGuardian2016} 
-User devices become tracking and/or monitoring \squad{}s that turn to
-be the best spy over users.
+User devices become tracking and/or monitoring \squad{}s that turn out
+to be the best spy over users.
 
@@
 and self-organizing file sharing service between the \squad{}s of different users that preserves user privacy
-in terms of both data \emph{and} metadata. Our proposal hinges on two key ideas: \emph{First}, we consider proxemics relationships as a key enabler to initiate file
+in terms of both data \emph{and} metadata. Our proposal hinges on two
+key ideas: \emph{First},  the recent advances of smartphones and other
+mobile devices enable e-squads and it has thus
+become possible to benefit from P2P technology for one's own devices
+alone, thereby reducing one's exposure to security and privacy threats
+from third parties. Relatedly, we consider proxemics relationships as a key enabler to initiate file
 transfers. Close distance among users enable them to share
@@
 rely on distributed machine learning techniques to predict the future
-availability of user devices, and use this ability to implement a \emph{probabilistic predictive onion routing} mechanism.
-The predictive nature of our routing allows us to overcome the inherent fragility of pure P2P data-sharing schemes.
+availability of user devices, and use this ability to implement a
+\emph{probabilistic predictive onion routing} mechanism. The
+predictive nature of our routing, exploited in a stateless way, allows us to overcome the inherent
+fragility of pure P2P data-sharing schemes.
 

### 2018-05-02 paper/message-passing-design.tex
m

@@
 chosen by Bob uniformly at random from its RPS (\view).
- \([Recv]\) returns the \(H_{Bob}\).
+ %\([Recv]\) returns the \(H_{Bob}\).
 PORs have \(L\) layers, and for each layer the number of
@@
 acknowledge its messages. Bob and Alice exchange then their calculated
-PORs (i.e. H_{Bob} andH_{Alice}), using an
+PORs (i.e. H_{Bob} and H_{Alice}), using an
 out-of-band channel, \eg using one device of their \squad (See
@@
 layer, which contained the overall
-possible rendez-vous points $D$ previously selected by the recipient (i.e. Bob).
+possible alternative nodes $D$.
 One device from $D$ is randomly chosen, and the \([Fwd]\)
@@
 in sequence the different layer with the current node’s private key. 
-The end of the route is reached when special value \(H_{Bob} = \top\) is
+The end of the route is reached when the special value \(H_{Bob} = \top\) is
 encountered. Consequently the ciphered message \(c_m\) is then stored
@@
 (\cref{SPORFwd}).
+
+In a way similar, once Bob get the \(H_{Alice}\), Bob uses \([Send]\) at some
+later time to acknowledge messages sent by Alice using any of his devices from
+its\squad.
 

### 2018-06-29 paper/related.tex
Fixes warnings for references

@@
 
-P2P file sharing has been researched extensively, with respect to aspects such as architecture (starting with the semi-centralized Napster, then decentralized Gnutella), availability and replication~\cite{replica}, scalability (Bittorrent~\cite{bittorrent}), anonymity (Freenet~\cite{Clarke:2001}, TOR~\cite{Tor}), and distributed hash tables (DHT) such as CAN, Chord, Pastry, and Tapestry (see \cite{dhtchurn} for an overview).
+P2P file sharing has been researched extensively, with respect to aspects such as architecture (starting with the semi-centralized Napster, then decentralized Gnutella), availability and replication~\cite{replica}, scalability (Bittorrent~\cite{bittorrent-incentives}), anonymity (Freenet~\cite{Clarke:2001}, TOR~\cite{Tor}), and distributed hash tables (DHT) such as CAN, Chord, Pastry, and Tapestry (see \cite{dhtchurn} for an overview).
 In contrast to our work, the main goal was to enable dissemination to many users who do not necessarily know each other in person.

### 2018-06-29 paper/abstract.tex
pass on abstract - trying to streamline argument, and polish transitions

--- 2018-04-29 paper/abstract.tex
@@
+% -*- tex-main-file: "contents.tex" compile-command: "pdflatex p2p-private-cloud.tex" ispell-dictionary: "american" -*-
 % What's the problem?
@@
 %problem/topic
-This paper proposes a novel fully-decentralized privacy-preserving file sharing service that eschews any third-party storage or any centralized bootstrapping service.
+This paper proposes a novel private file sharing service tat avoids any third-party storage or centralized bootstrapping service.
 %research gap
-Cloud-based file-sharing systems such as Dropbox require trust in the service provider and can be monitored, even when their data is encrypted.
-Private peer-to-peer (P2P) solutions are either particularly inefficient, or must rely on a fixed set of trusted servers for bootstrapping purposes, which limit their level of protection.
+Our solution, which adopts a fully decentralized design, overcomes the limitations of cloud file-sharing systems such as Dropbox, which require trust in the service provider and can be monitored, even when their data is encrypted.
+Our proposal also goes beyond existing private peer-to-peer (P2P) solutions that are either particularly inefficient, or must rely on a fixed set of trusted servers for bootstrapping purposes, which limits their level of protection.
 % We are interested in minimizing the trust needed in other systems and preserving the users' privacy in terms of data and metadata, what they share with whom and when.
@@
 %approach
-In this paper, we demonstrate that an efficient and strongly private fully-decentralized data-sharing solution is possible.
-Our proposal combines onion routing with probabilistic node selection, informed by peer sampling and Hidden Markov Model predictions for node availability.
+In this paper, we demonstrate that a fully-decentralized data-sharing solution that is  both efficient and strongly private is possible.
+\commentFT{Trying to highlight POR, as likely to be catch people's attention, and contribute to the paper's long-term interest.} At the core of our proposal lies a novel probabilistic onion routing protocol called POR, which exploits decentralized peer sampling, and a probabilistic model of node availability.
+\commentFT{Sharing node availability information freely could potentially disclose private information.
+We might want to discuss this risk somewhere in the paper.}
+% Our proposal combines onion routing with probabilistic node selection, informed by peer sampling and Hidden Markov Model predictions for node availability.
 %findings/contributions:
-Our solution benefits from sender-receiver anonymity properties provided by onion routing. %% to protect user privacy in decentralized file sharing.
-We show that even a relatively naive prediction model suffices to share files despite the unreliable availability of individual nodes.
+The resulting solution is fully decentralized, provides sender-receiver anonymity, and can deliver competitive performance in spite of unreliable nodes.
+%% to protect user privacy in decentralized file sharing.
+% We show that even a relatively naive prediction model suffices to share files despite the unreliable availability of individual nodes.
 %% The same model can potentially be applied for better-informed churn handling in other p2p systems.
 In the case of onion routing systems for anonymity,
-Our solution allows the system to include unreliable nodes and take advantage of locality, neither of which is currently provided in TOR.
+\commentFT{Using transient to avoid repeating unreliable.}
+This design makes it possible to exploit transient nodes, without dedicated relays, %take advantage of locality, 
+neither of which is currently the case in TOR.

### 2018-06-29 paper/intro.tex
pass on introduction, with some inlined comments

--- 2018-04-30 paper/intro.tex
@@
+% -*- tex-main-file: "contents.tex" compile-command: "pdflatex p2p-private-cloud.tex" ispell-dictionary: "american" -*-
+
 \section{Introduction}
@@
 % What's the problem?
-Following Mark Weiser's vision, we are nowadays
-experiencing a new era of cooperation and interactions between humans.
-The exponential proliferation of connected devices is
-drastically impacting human experience and enhancing human
-exchanges~\cite{Dearman:2008, Oh:2017, Sohn:2008,Harper08}. This evolution has opened new areas of research such as
-\textit{proxemics} applied to ubiquitous computing
-\cite{Marquardt:2011}. When evolving in their social space, users can today rely on
-multiple kinds of computing devices that form a \textit{personal squad} of connected entities, or \squad as we shall call them in the remainder of the
-paper. Helped by their \squad, users
-have come to expect ever higher levels of connectivity and interaction
-possibilities. For instance, as users bring
+
+Fulfilling Mark Weiser's vision, we now rely on a increasing number of personal digital devices for many everyday tasks.
+These devices form a \textit{personal squad} of connected entities (or \emph{\squad} as we shall call them in the remainder of the
+paper), that users rely on for their everyday interactions with the material and digital world, and with their fellow humans.
+The growing importance of these \squad{}s is profoundly modifying how we live~\cite{Dearman:2008, Oh:2017, Sohn:2008,Harper08}, and has opened new areas of research such as \textit{proxemics}, the study of proximity-based interactions in a world of ubiquitous computing
+\cite{Marquardt:2011}.
+%% we are nowadays
+%% experiencing a new era of cooperation and interactions between humans.
+%% The exponential proliferation of connected devices is
+%% drastically impacting human experience and enhancing human
+%% exchanges~\cite{Dearman:2008, Oh:2017, Sohn:2008,Harper08}. This evolution has opened new areas of research such as
+%% \textit{proxemics} applied to ubiquitous computing
+%% \cite{Marquardt:2011}. 
+%% When evolving in their social space, users can today rely on
+%% multiple kinds of computing devices that form a \textit{personal squad} of connected entities, or \squad as we shall call them in the remainder of the
+%% paper.
+Supported by their \squad, users
+have come to expect always-on connectivity, along with advanced interaction
+capabilities. For instance, as users bring
 their devices close to one another, they expect to be able to initiate cross-device
 interactions \textit{in situ} in order to share digital content
-\cite{Oh:2017} between devices of their own \squad or with those of other users' \squad{}s. More broadly, users expect to share digital content,
+\cite{Oh:2017} between devices of their own \squad or with those of other users' \squad{}s. More broadly, users want to be able to share digital content seamlessly,
 wherever the content, its sender, or its recipient might be located, from one
-arbitrary device to another in a seamless manner~\cite{Dearman:2008}, as they
-would have done in the old days with an USB key or with an email.
+arbitrary device to another~\cite{Dearman:2008}, as they
+would have a few years ago with an USB key or an email.
 
@@
 of personal sharing platforms such as Dropbox, Google Docs,
-OneDrive, Amazon Drive, etc. These solutions are able to share data between any device, any user, almost
+OneDrive, Amazon Drive, etc. These solutions allow users to share data between any device, with anyone, almost
 anytime, anywhere. They achieve this feat by relying heavily on
@@
 Although data encryption is often proposed as a first line of defense for cloud-hosted data, it is unfortunately  insufficient~\cite{granick_2017, HooffLZZ15, HarnikPS10}. Metadata such as a user'
-location and activity can be still tracked, including the access
-control history revealing what each user shared with whom and when. 
+location and activity can still be tracked, including access
+control histories, thus revealing what each user shared with whom and when. 
 %  because it does not protect meta-data information
-This turns out to be a critical limitation, as famously emphasized by a former NSA and CIA director: "We kill people based on metadata.''~\cite{NaughtonTheGuardian2016} 
-User devices become tracking and/or monitoring \squad{}s that turn to
-be the best spy over users.
+The exposure of metadata seriously weakens user privacy, as famously emphasized by a former NSA and CIA director: "\emph{We kill people based on metadata.}''~\cite{NaughtonTheGuardian2016} 
+In this model, user devices, masquerading as allies, get turned into tracking and/or monitoring \squad{}s, and serve as highly efficient spies over their owners.
 
-Constructing a system that provides fully anonymous content sharing is highly
-challenging. The last two decades have witnessed many attempts at building privacy preserving and anonymous P2P data-sharing
+Constructing a system that provides fully anonymous content sharing while avoiding the above pitfalls is unfortunately highly
+challenging. The last two decades have witnessed many attempts at building privacy-preserving and anonymous P2P data-sharing
 networks~\cite{Clarke:2001,Gnunet2002,Freedman:2002,Nambiar:2006,Rennhard:2002}.
@@
 centralized in traditional onion routing schemes. However, because of the high
-churn typically experienced by P2P networks, the performance of these systems is
-discouraging~\cite{LeBlond:2013}; churn causes routes to be frequently
-reconstructed, which is very expensive. By contrast, Tor
+churn typically experienced by P2P networks, the performance of these systems has been
+discouraging~\cite{LeBlond:2013}; churn causes routes to disappear and be
+reconstructed frequently, which is particularly costly. By contrast, Tor
 \cite{Dingledine:2004}, one of the most popular anonymous networks,
@@
 \name{}, a novel fully decentralized, autonomous,
-
 % approach that provides a 
 and self-organizing file sharing service between the \squad{}s of different users that preserves user privacy
-in terms of both data \emph{and} metadata. Our proposal hinges on two key ideas: \emph{First}, we consider proxemics relationships as a key enabler to initiate file
-transfers. Close distance among users enable them to share
+in terms of both data \emph{and} metadata. \commentFT{Moving to 3 ideas, to highlight proxemics in its own right} Our proposal hinges on three
+key ideas: \emph{First}, the emergence of \emph{\squad{}s}, the set of connected devices owned and used by one user, 
+%% the recent advances of smartphones and other
+%% mobile devices enable e-squads and it has thus
+%% become possible to
+makes it possible to apply P2P technology to one's own devices
+alone, thereby reducing one's exposure to security and privacy threats
+from third parties. \emph{Second}, we consider \emph{proxemics relationships} as a key enabler to initiate file
+transfers. Physical proximity allow users to share
 routing information out-of-band, e.g. from their
-\squad. In contrast to state-of-the-art P2P systems, users agree in \name out-of-band to share a file, but
-do not keep it available for anyone else in the future. \emph{Second}, we
-rely on distributed machine learning techniques to predict the future
-availability of user devices, and use this ability to implement a \emph{probabilistic predictive onion routing} mechanism.
-The predictive nature of our routing allows us to overcome the inherent fragility of pure P2P data-sharing schemes.
+\squad. \commentFT{I did not get what 'from their \squad' mean.} In contrast to state-of-the-art P2P systems, users agree in \name out-of-band to share a file, but
+do not keep it available for anyone else in the future. \emph{Third}, we
+exploit distributed machine learning techniques to predict the future
+availability of user devices, and use this ability to implement a
+\emph{probabilistic predictive onion routing} (POR) mechanism. The
+predictive nature of our routing, exploited in a stateless way, allows us to overcome the inherent fragility of pure P2P data-sharing schemes.
 

### 2018-06-30 paper/security-discussion.tex
Reverts 25a8deeb4339f5fd3215b78a21e3b7500ddb735f security-discussion.tex

--- 2018-05-01 paper/security-discussion.tex
@@
 
-One thing that we can directly improve is the header.
+One part that we can directly improve is the header.
 We see two alternative paths for improving the header.

### 2018-07-02 paper/message-passing-design.tex
Reverts most commits back to a696eb796a72fde7c449c1ec6e8973a5f129363a message-passing-design.tex

--- 2018-05-02 paper/message-passing-design.tex
@@
 
+\david{each protocol should be explained individually}
+
 In contrast to Tor~\cite{Tor} that provides only one address per hop
@@
 alternatives for the next hop in the route depending on their
-probability of being online. We call our modified onion routes
-Probabilistic Onion Routes or PORs.
-
-Another difference from Tor, where connections are established by all
-nodes in the route, \name is stateless. The sender
-Alice and receiver Bob cooperate to create the headers containing all
-the necessary routing information for future communication between
-Alice and Bob. In that regard, we use two PORs: one to route packets from Alice to
-Bob, and one for packets acknowledgement from Bob to Alice (See
-Fig.~\ref{fig:file-exchange}~\ding{184}). We defined some fixed
-parameters such as $L$, the number of layers in a POR, and
-$\theta$, the stopping criterion for the layers creation, i.e the
-maximum authorized  probability that all devices in a layer fail at
-once.
-
-To implement our  probabilistic
-predictive onion routing mechanism, \name defined two different algorithms to
-receive, send messages among users' \squad. For instance,
+probability of being online. To implement our  probabilistic
+predictive onion routing mechanism, \name defined three different algorithms to
+receive, send and forward messages among users' \squad. For instance,
 if Alice wants to send a message \(m\) to Bob, Bob uses the
-\([Recv]\) algorithm (See \cref{SPORFwd}) to create a probabilistic onion route \(H_{Bob}\) from
- a set of rendez-vous point to its own devices from its \squad --- all the hops on the route are 
-chosen by Bob uniformly at random from its RPS (\view).
- \([Recv]\) returns the \(H_{Bob}\).
+\(\SPOR[\Recv]\) algorithm (See \cref{SPORRecv}) to create a probabilistic onion route \(H_\rdv\) from
+ a rendez-vous point to its own devices from its \squad --- all the hops on the route are 
+chosen by Bob uniformly at random from the RPS. \(\SPOR[\Recv]\)
+returns the \(H_\rdv\) that Bob gives to Alice using an
+out-of-band channel, \eg using one device of its \squad.
 PORs have \(L\) layers, and for each layer the number of
@@
 As long as \(\theta\) is not exceeded, alternatives nodes are added in
-\(H_{Bob}\) as depicted in \cref{ExtendRoute}. Thus the probability of
-failure for the extension is \(1 - (1 - \theta)^L\). In a similar
-manner, Alice create an onion route \(H_{Alice}\) to enable Bob to
-acknowledge its messages. Bob and Alice exchange then their calculated
-PORs (i.e. H_{Bob} andH_{Alice}), using an
-out-of-band channel, \eg using one device of their \squad (See
-Fig.~\ref{fig:file-exchange}~\ding{182}).
+\(H_\rdv\) as depicted in \cref{ExtendRoute}. Thus the probability of
+failure for the extension is \(1 - (1 - \theta)^L\).
 
@@
 
-Once Alice get the \(H_{Bob}\), Alice uses \([Send]\) at some
+Once Alice get the \(H_\rdv\), Alice uses \(\SPOR[\Send]\) at some
 later time to send the message to Bob using any of her devices from
-its \squad (See \cref{SPORFwd}). First, \([Send]\) extends the route
-\(H_{Bob}\) with some hops of Alice's choosing (uniformly randomly
-chosen). Second, \([Send]\) extracts from the onion the first
+its \squad (See \cref{SPORSend}). First, \(\SPOR[\Send]\) extends the route
+\(H_\rdv\) with some hops of Alice's choosing (uniformly randomly
+chosen). Second, \(\SPOR[\Send]\) extracts from the onion the first
 layer, which contained the overall
 possible rendez-vous points $D$ previously selected by the recipient (i.e. Bob).
-One device from $D$ is randomly chosen, and the \([Fwd]\)
+One device from $D$ is randomly chosen, and the \(\SPOR[\Fwd]\)
 sub-function is called as long as the message forwarding to one node of
@@
 in sequence the different layer with the current node’s private key. 
-The end of the route is reached when special value \(H_{Bob} = \top\) is
+The end of the route is reached when special value \(H_\rdv = \top\) is
 encountered. Consequently the ciphered message \(c_m\) is then stored
-in the disk of the local node through the \([Store]\) sub function 
-(\cref{SPORFwd}).
+in the disk of the local node through the \(\Store\) sub function 
+(\cref{SPORRecv}).
+
+\david{the use of DeBE algorithms must be explicitly explained here}
 
@@
 %    is intended for the local node and \(c_m\) is instead sent to disk using 
-%    \(\Store\) (\cref{SPORFwd}).%
+%    \(\Store\) (\cref{SPORRecv}).%
 
@@
 
-\begin{figure}[t]
-\center
-  \includegraphics[scale=.55]{figures/file_exchange_v2.pdf}
-  \caption{\label{fig:file-exchange}A schematic of the creation and usage of PORs between Alice and Bob's e-squads.}
+\begin{figure}
+  \includegraphics[width=\linewidth]{figures/file_exchange_v2.pdf}
+  \caption{\label{fig:file-exchange}%
+    A schematic of Alice and Bob sending a message using \(\SPOR\).
+  }
 \end{figure}
@@
 \begin{figure}
+
   \framebox{\begin{minipage}{0.96\linewidth}
   \begin{algorithmic}[1]
-\scriptsize
-    \Function{\ExtendRoute}{$H, L$}
+    \Require{%
+      $H$ is a header of the form \(D\concat H'\) or \(D\concat \top\), where 
+      \(D\) is a set of device addresses.
+      $\pk_D$ is the public key of device set $D$.
+      $L$ is the length of the route,
+      $\theta$ is the threshold of probability of failure.%
+    }
+    \Function{\ExtendRoute}{$H, L, \theta$}
       \If{$L\leq 0$}
@@
       \EndIf
-      \State $D\gets \CreateOnionLayer[]$
+      \State $D\gets \CreateOnionLayer[\theta]$
       \State $H\gets D\concat \DeBEenc[\mpk, D, H]$
@@
   \vspace{0.3em}
-    \Function{\CreateOnionLayer}{}
+    \Function{\CreateOnionLayer}{$\theta$}
       \State $(d, \pk_d, p_d)\gets \GetRandomPeer$
@@
   \begin{algorithmic}
-\scriptsize
     \Require{%
@@
     }
-    \Function{\Recv}{$D$}
+    \Function{\SPOR[\Recv]}{$D$}
       \State $H_\rdv\gets \ExtendRoute[D\concat \top, L, \theta]$
@@
   \end{algorithmic}
-  %\end{minipage}}
-%   \caption{\label{SPORFwd}%
-% \scriptsize
-%     The \(\Recv\) algorithm prepares the recipient for receiving a file.
-%   }
-  %\framebox{\begin{minipage}{0.96\linewidth}
+  \end{minipage}}
+  \caption{\label{SPORRecv}%
+\scriptsize
+    The \(\SPOR[\Recv]\) algorithm prepares the recipient for receiving a file.
+  }
+\end{figure}
+
+\begin{figure}
+  \framebox{\begin{minipage}{0.96\linewidth}
   \begin{algorithmic}
-\scriptsize
     \Require{%
       $m$ is the message to be sent,
-      $H$ is the onion-route given by the recipient.
+      $H_\rdv$ is the onion-route given by the recipient.
     }
-    \Function{\Send}{$H,m$}
-      \State $H\gets \ExtendRoute[H, L, \theta]$
+    \Function{\SPOR[\Send]}{$H_\rdv, m$}
+      \State $H\gets \ExtendRoute[H_\rdv, L, \theta]$
       \State $D\concat C_H\gets H_\rdv$
@@
   \end{algorithmic}
-  %\end{minipage}}
-  % \caption{\label{SPORFwd}%
-  %   \scriptsize
-  %   The \(\Recv\), \(\Send\) and \(\Fwd\) algorithms.
-  % }
- % \framebox{\begin{minipage}{0.96\linewidth}
+  \end{minipage}}
+  \caption{\label{SPORSend}%
+    \scriptsize
+    The \(\SPOR[\Send]\) algorithm 
+  }
+\end{figure}
+
+\begin{figure}
+  \framebox{\begin{minipage}{0.96\linewidth}
   \begin{algorithmic}
-\scriptsize
-    \Require{$\sk$ is the private key-pair of the current node.}
-    \Function{\Fwd}{$C_H, m$}
+    \Require{$\pk, \sk$ is the public--private key-pair of the node.}
+    \Function{\SPOR[\Fwd]}{$C_H, m$}
       \State $H\gets \DeBEdec[\mpk, \sk, C_H]$
@@
   \caption{\label{SPORFwd}%
-    \scriptsize
-    The \(\Recv\) (prepares the recipient for receiving a file), \(\Send\) and \(\Fwd\) (forwards \(m\) down the route \(H\)) algorithms.
+    The \(\SPOR[\Fwd]\) algorithm forwards \(m\) down the route \(H\), obtained 
+    by decrypting \(C_H\) with the node's associated private key.
+    The special value \(H = \top\) indicated the end of the route, thus \(c_m\) 
+    is intended for the local node and \(c_m\) is instead sent to disk using 
+    \(\Store\) (\cref{SPORRecv}).%
   }

### 2018-07-02 paper/sphinxes.tex
Adds WIP on Sphinxes

\section{Sphinxes: the Sphinx header format for multi-node layers}%
\label{Sphinxes}

\Textcite{Sphinx} designed \iac{UC} secure message format for mixes.

### 2018-07-03 paper/message-passing-design.tex
Reverts commits to get full captions again
Reverts until 729819c2cfaa59eb7dcb8ff19cfb6000dfaad2fd

@@
 
-\david{each protocol should be explained individually}
+We have the Stateless Predictive Onion Routing scheme, \SPOR, which provides 
+probabilistically onion-routed message passing.
+Instead of providing only one address per hop in the route (as in \eg 
+Tor~\cite{Tor}), \(\SPOR\) provides several alternatives for the next hop 
+depending on their probability of being online.
+To do this, \(\SPOR\) provides stateless algorithms for the onion-routing.
 
-In contrast to Tor~\cite{Tor} that provides only one address per hop
-in the route, \name provides for each layer of the onion several
-alternatives for the next hop in the route depending on their
-probability of being online. To implement our  probabilistic
-predictive onion routing mechanism, \name defined three different algorithms to
-receive, send and forward messages among users' \squad. For instance,
-if Alice wants to send a message \(m\) to Bob, Bob uses the
-\(\SPOR[\Recv]\) algorithm (See \cref{SPORRecv}) to create a probabilistic onion route \(H_\rdv\) from
- a rendez-vous point to its own devices from its \squad --- all the hops on the route are 
-chosen by Bob uniformly at random from the RPS. \(\SPOR[\Recv]\)
-returns the \(H_\rdv\) that Bob gives to Alice using an
-out-of-band channel, \eg using one device of its \squad.
-PORs have \(L\) layers, and for each layer the number of
-alternatives nodes depends of a failure threshold \(\theta\). 
-As long as \(\theta\) is not exceeded, alternatives nodes are added in
-\(H_\rdv\) as depicted in \cref{ExtendRoute}. Thus the probability of
-failure for the extension is \(1 - (1 - \theta)^L\).
-
-\NewAlgorithm{\Store}{Store}
-
-Once Alice get the \(H_\rdv\), Alice uses \(\SPOR[\Send]\) at some
-later time to send the message to Bob using any of her devices from
-its \squad (See \cref{SPORSend}). First, \(\SPOR[\Send]\) extends the route
-\(H_\rdv\) with some hops of Alice's choosing (uniformly randomly
-chosen). Second, \(\SPOR[\Send]\) extracts from the onion the first
-layer, which contained the overall
-possible rendez-vous points $D$ previously selected by the recipient (i.e. Bob).
-One device from $D$ is randomly chosen, and the \(\SPOR[\Fwd]\)
-sub-function is called as long as the message forwarding to one node of
-the next layer is not successful (See \cref{SPORFwd}). Along the path, each node decrypts
-in sequence the different layer with the current node’s private key. 
-The end of the route is reached when special value \(H_\rdv = \top\) is
-encountered. Consequently the ciphered message \(c_m\) is then stored
-in the disk of the local node through the \(\Store\) sub function 
-(\cref{SPORRecv}).
-
-\david{the use of DeBE algorithms must be explicitly explained here}
-
-%The special value \(H = \top\) indicated the end of the route, thus \(c_m\) 
-%    is intended for the local node and \(c_m\) is instead sent to disk using 
-%    \(\Store\) (\cref{SPORRecv}).%
-
-%The SPOR.Forward algorithm forwards m down the route H, obtained by
-%decrypting CH with the node’s associated private key. The special
-%value H = ⊤ indicated the end of the route, thus cm is intended for
-%the local node and cm is instead sent to disk using Store
-
-%extends the route \(H_\rdv\) (using 
- %   \(\ExtendRoute\), \cref{ExtendRoute}) and sends the message \(m\) down the 
-  %  extended route using the \(\SPOR[\Fwd]\) algorithm (\cref{SPORFwd}).
-   % The first node of \(H_\rdv\) is the rendez-vous point selected by the 
-    %recipient.
-
-%It creates a probabilistic onion-route from a rendez-vous point to its own 
-%    devices and returns the route to the sender.
+\(\SPOR\) provides three algorithms: \(\SPOR[\Send]\) (\cref{SPORSend}), 
+\(\SPOR[\Fwd]\) (\cref{SPORFwd}) and \(\SPOR[\Recv]\) (\cref{SPORRecv}).
+Say Alice wants to send a message \(m\) to Bob.
+Bob uses \(\SPOR[\Recv]\) to create a probabilistic onion route \(H_\rdv\) from 
+a rendez-vous point to his own device swarm --- all the hops on the route are 
+chosen by Bob uniformly at random.
+Bob gives \(H_\rdv\) to Alice using an out-of-band channel, \eg using his phone.
+Alice uses \(\SPOR[\Send]\) at some later time to send the message to Bob using 
+any of her devices.
+\(\SPOR[\Send]\) extends the route \(H_\rdv\) with some hops of Alice's choosing 
+(uniformly randomly chosen), then starts to forward the message (using 
+\(\SPOR[\Fwd]\)) through the hops on the route to Bob.
+This process is illustrated in \cref{fig:file-exchange}.
 
@@
     \EndFunction
-  \vspace{0.3em}
+
     \Function{\CreateOnionLayer}{$\theta$}
@@
   \caption{\label{ExtendRoute}%
-    \scriptsize
-    The \(\ExtendRoute\) algorithm extends a route \(H\)
+    The \(\ExtendRoute\) algorithm extends a route \(H\) with \(L\) hops and 
+    failure threshold of \(\theta\) for each hop in the route.
+    Thus the probability of failure for the extension is \(1 - (1 - \theta)^L\).
+    The function \(\GetRandomPeer\) is any random peer-sampling algorithm.
   }
@@
 
+\NewAlgorithm{\Store}{Store}
 \NewAlgorithm{\Dec}{Dec}
@@
   \caption{\label{SPORRecv}%
-\scriptsize
     The \(\SPOR[\Recv]\) algorithm prepares the recipient for receiving a file.
+    It creates a probabilistic onion-route from a rendez-vous point to its own 
+    devices and returns the route to the sender.
   }
@@
   \caption{\label{SPORSend}%
-    \scriptsize
-    The \(\SPOR[\Send]\) algorithm 
+    The \(\SPOR[\Send]\) algorithm extends the route \(H_\rdv\) (using 
+    \(\ExtendRoute\), \cref{ExtendRoute}) and sends the message \(m\) down the 
+    extended route using the \(\SPOR[\Fwd]\) algorithm (\cref{SPORFwd}).
+    The first node of \(H_\rdv\) is the rendez-vous point selected by the 
+    recipient.
   }
@@
     \EndFunction
+
     \Function{\Store}{$m$}
@@
     is intended for the local node and \(c_m\) is instead sent to disk using 
-    \(\Store\) (\cref{SPORRecv}).%
+    \(\Store\).%
   }

### 2018-07-04 paper/system-model.tex
system model, properties, adversary model

@@
 out-of-band, \ie through some other channel than the network just mentioned (\eg 
-using \ac{NFC}).
+using \ac{NFC} or QR codes).
+
+%system model: explain e-squad, contrast with cloud
+
+%adversary model: remove provider, compensate, results in same as in sphinxOR/Tor?  friends?
+
+%properties: cam/lys: correctness, integrity, security (wrap, indistinguishability) - do not want friends to learn 1) which devices are ours 2)  their availability (assumption: RPS, not lookup)
+
+We first describe a simple model of data sharing via cloud storage to
+highlight desirable privacy properties and then map them to our provider-less
+setting. We then add privacy properties and adversary models for onion
+routing to cover network traffic analysis.
 
@@
 Bob, she picks up and pushes one of her files, from one of her devices, to the cloud
-provider, to make it available to Bob that will thereafter get it from
-one of its devices. The use of the cloud provider, as a third party,
+provider, to make it available to Bob to download to
+one of his devices. The use of the cloud provider, as a third party,
 provides two main privacy properties, which we have to consider when
@@
 \begin{itemize}
-\item Alice and Bob are the only ones who learn 
+\item Alice and Bob are the only ones \sonja{narrow down to users?} who learn 
 about Alice sharing a file with Bob, except for the cloud provider.
 \item Alice and Bob learn nothing about each others' devices, \ie 
-they cannot map any device as belonging to each other, except for the
-cloud provider that learn it.
+they cannot map any device as belonging to each other or draw
+inferences from their behavior. The cloud
+provider, however, can learn this. \sonja{expand to other users?}
 \end{itemize}
 
-\paragraph*{In the \name setting} when changing from the cloud setting
-to \ac{P2P}, we want to keep the privacy that Alice and Bob already
-enjoyed through the cloud provider, and go a step further by removing 
-the cloud provider that may act as a spy. However, this increased privacy
-should not be done to the benefit of the user's friends that may
-become the most powerful potential attackers, and act
-as an adversary type of friends.
-In this context, in \name, we want to protect users from friendly
-surveillance~\cite{FriendlySurveillance} in an honest-but-curious setting.
+\paragraph*{In the \ac{P2P} setting} we want to keep the privacy that
+Alice and Bob already enjoyed thanks to the cloud provider functioning
+as a gatekeeper toward each other and other users. We go a step
+further by removing the cloud provider that may draw inferences from
+metadata even when the data itself is encrypted. Removing the provider
+also removes the gatekeeping which needs to be compensated for to
+protect users from friendly surveillance~\cite{FriendlySurveillance}
+by peers (other \name users including Alice and Bob)\sonja{removed: in
+  an honest-but-curious setting}. We give the definitions for the
+security and privacy properties of \name in Section~\ref{security-discussion}.
 
-However, we will not consider a global network adversary, only subsets of colluding 
-parties. We know that it is notoriously difficult to achieve security against a global 
-network adversary~\cite{SystemsForAnonymousCommunication}.
+\paragraph*{In the \name setting} we combine the requirements from
+the \ac{P2P} setting with those from onion routing for anonymity.
+Camenisch and Lysianskaya \cite{} define security properties for onion
+routing: correctness, integrity, security (wrap resistance,
+indistinguishability). These properties cover the concerns about
+revealing to others that Alice shares a file with Bob in the first
+place. In \name, we additionally derive the property of
+device-unlinkability from the \ac{P2P} requirements, meaning that
+using \name does not reveal the \squad a device belongs to nor the
+owner and can thus not infer anything about a user's behavior such as
+being online.
+
+\paragraph*{Adversary model} we share the model by Tor \cite{} and
+Sphinx \cite{}: the adversary has complete control over some part of
+the network as well as some of the nodes. We not consider a passive
+global network adversary, against which it is notoriously difficult to
+achieve security~\cite{SystemsForAnonymousCommunication}.

### 2018-07-04 paper/sphinxes.tex
Adds CLOnionRouting
Changes Sphinxes title to include "Extended for Sets"

@@
-\section{Sphinxes: the Sphinx header format for multi-node layers}%
+\section{Sphinxes: the Sphinx header format Extended for Sets of nodes}%
 \label{Sphinxes}
 
-\Textcite{Sphinx} designed \iac{UC} secure message format for mixes.
+\Textcite{Sphinx} designed \iac{UC} secure message format for mixes based on 
+the formal definitions of \textcite{CLOnionRouting}.

### 2018-07-04 paper/sphinxes.tex
Adds beginning of Sphinx description

--- 2018-07-02 paper/sphinxes.tex
@@
-\section{Sphinxes: the Sphinx header format for multi-node layers}%
+\section{Sphinxes: the Sphinx header format Extended for Sets of nodes}%
 \label{Sphinxes}
@@
 \Textcite{Sphinx} designed \iac{UC} secure message format for mixes.
+Since it is \ac{UC} secure, it provably implements an ideal onion routing 
+functionality.
+\Ie, it provides bitwise unlinkability on the forward route, hides the path 
+length, makes replies indistinguishable from forward messages and resists 
+tagging attacks.
+It is also compact with only 224 bytes of header for a five-hop path with 
+128-bit security.
+Sphinx only provides one node per onion layer, in this section we extend Sphinx 
+to Sphinxes, which allows for multiple nodes per onion layer.
+
+\subsection{The Sphinx header format}
+
+\NewVariable{\sk}{sk}
+\NewVariable{\pk}{pk}
+
+Each node \(n\) in the system has a public-key pair: private key \(\sk_n\in 
+  \ZZ_q^*\) and public key \(\pk_n = g^{\sk_n}\in G\), where \(g\) generates a 
+group \(G\) of prime order \(q\).
+
+The Sphinx header is a triple \((\alpha_1, \beta_1, \gamma_1)\), where 
+\(\alpha_1\) is \iac{DHKE} exponent (\(g^x\)), \(\beta_1\) is the encrypted 
+routing data and \(\gamma_1\) is \iac{MAC} for \(\beta_1\).
+The payload data, \(\delta\), is treated separately from the header.
+
+The first node in the path, with keys \((\pk_1, \sk_1)\), will compute the 
+shared secret \(s_1 = \alpha_1^{\sk_1}\), \ie complete the \ac{DHKE} round.
+Since \(\pk_1\) is an authenticated key, the sender can be sure that only this 
+particular node can process the first layer of the onion.
+
+The derived shared secret \(s_1\) is then used to derive various keys.
+One of them is the key for the \ac{MAC} (\(gamma_1\)) to verify the integrity 
+of the header (\(\beta_1\)).
+If \(\beta_1\) is correct, another key is derived from \(s_1\) to decrypt 
+\(\beta_1\).
+
+\subsection{The Sphinxes extension}
+
+\dots

### 2018-07-05 paper/sphinxes.tex
Adds that Sphinx is called Sphinx
Completes overview of Sphinx

@@
 
-\Textcite{Sphinx} designed \iac{UC} secure message format for mixes.
+\Textcite{Sphinx} designed \iac{UC} secure message format for mixes, called 
+Sphinx.
 Since it is \ac{UC} secure, it provably implements an ideal onion routing 
@@
 
-\subsection{The Sphinx header format}
+\subsection{Overview of the Sphinx header format}
+
+We will now give an overview of the Sphinx header format.
+The idea is not to give a detailed description of Sphinx, but to to give the 
+reader enough understanding of Sphinx to understand the changes we make to 
+achieve Sphinxes.
+For a more detailed understanding of Sphinx, we refer the reader to the 
+excellent description in the original Sphinx paper~\cite{Sphinx}.
 
@@
 
-Each node \(n\) in the system has a public-key pair: private key \(\sk_n\in 
-  \ZZ_q^*\) and public key \(\pk_n = g^{\sk_n}\in G\), where \(g\) generates a 
-group \(G\) of prime order \(q\).
+Each node \(n\) in the system has a long-term public-key pair: private key 
+\(\sk_n\in \ZZ_q^*\) and public key \(\pk_n = g^{\sk_n}\in G\), where \(g\) 
+generates a group \(G\) of prime order \(q\).
 
-The Sphinx header is a triple \((\alpha_1, \beta_1, \gamma_1)\), where 
-\(\alpha_1\) is \iac{DHKE} exponent (\(g^x\)), \(\beta_1\) is the encrypted 
-routing data and \(\gamma_1\) is \iac{MAC} for \(\beta_1\).
+The Sphinx header (for the first node) is a triple \((\alpha_1, \beta_1, 
+  \gamma_1)\), where \(\alpha_1\) is \iac{DHKE} exponent (\(g^x\), where \(x\) 
+is a short-term secret chosen randomly for each header), \(\beta_1\) is the 
+encrypted routing data and \(\gamma_1\) is \iac{MAC} for \(\beta_1\).
 The payload data, \(\delta\), is treated separately from the header.
@@
 If \(\beta_1\) is correct, another key is derived from \(s_1\) to decrypt 
-\(\beta_1\).
+\(\beta_1\) (padded with zeroes to keep the length constant) to get 
+\(d_2\concat \gamma_2\concat \beta_2\), where \(d_2\) is the address of the 
+second node in the path.
+
+Finally, \(\alpha_1\) is blinded into \(\alpha_2\) with a key derived from 
+\(s_1\).
+Then the triple \((\alpha_2, \beta_2, \gamma_2)\) are sent to the node with 
+address \(d_2\).
+
+When node \(n\) discovers \(d_{n+1} = *\) it knows that the message is intended 
+for itself and thus stops the forwarding.
 

### 2018-07-05 paper/sphinxes.tex
Changes the explanation of how to keep constant size

@@
 If \(\beta_1\) is correct, another key is derived from \(s_1\) to decrypt 
-\(\beta_1\) (padded with zeroes to keep the length constant) to get 
-\(d_2\concat \gamma_2\concat \beta_2\), where \(d_2\) is the address of the 
-second node in the path.
+\(\beta_1\) to get \(d_2\concat \gamma_2\concat \beta_2\), where \(d_2\) is the 
+address of the second node in the path.
+
+We note that \(\beta_i\) is encrypted using a stream cipher.
+Thus we can append zeroes before decryption to keep the ciphertext length 
+constant.
+Since we append \emph{before} decryption, those appended zeroes will look 
+completely random to the next node, thus the position on the path is hidden.
 

### 2018-07-05 paper/sphinxes.tex
Adds Sphinxes extension description

@@
 
-\subsection{The Sphinxes extension}
+\subsection{The Sphinxes extension for sets of nodes}
 
-\dots
+\NewAlgorithm{\Enc}{Enc}
+
+We will now extend Sphinx: instead of providing only \(d_{i+1}\) in 
+\(\beta_i\), we will have a set \(\{d_{i+1}^{(0)}, \dotsc, d_{i+1}^{(m)}\}\) of 
+\(m\) alternative next nodes.
+This means that all \(m\) nodes must be able to compute the same shared secret 
+\(s_{i+1}\).
+We do this by adding one layer of indirection.
+
+In Sphinx we denoted the public key for layer \(i\) as \(\pk_i\).
+Since we have \(m\) alternative nodes with different keys, let us denote them 
+by \(\pk_i^{(1)}, \dotsc, \pk_i^{(m)}\).
+
+We extend the header to a quadruple \((\alpha_i, C_i, \beta_i, \gamma_i)\), 
+where \(\alpha_i, \beta_i, \gamma_i\) are the same as before.
+We let the shared secret \(s_i\) be chosen uniformly randomly instead of being 
+computed as \(\alpha_i^{\sk_i}\).
+We now compute one shared secret per alternative node, \ie \(s_i^{(j)} = 
+  \alpha_i^{\sk_i^{(j)}}\) for \(1\leq j\leq m\).
+Then \(C_i = c_i^{(1)}\concat \dotsb\concat c_i^{(m)}\) is the concatenation of 
+ciphertexts \(c_i^{(j)} = \Enc[_{s_i^{(j)}}][s_i]\), where \(\Enc\) is 
+\iac{SKE} algorithm and each ciphertext contains the shared secret \(s_i\) 
+encrypted under the individual keys \(s_i^{(j)}\).

### 2018-07-05 paper/sphinxes.tex
Adds trial-and-error decryption to Sphinxes description

@@
 encrypted under the individual keys \(s_i^{(j)}\).
+
+When a node receives this new header, it will compute \(s_i^{(j)}\gets 
+  \alpha_i^{\sk_i^{(j)}}\).
+Then, it will try to decrypt each ciphertext component \(c_i^{(k)}\) of \(C_i\) 
+to get \(\hat s_i\).
+If \iac{MAC} key that successfully verifies \(\beta_i\) using \(\gamma_i\) can 
+be derived from \(\hat s_i\), then the node knows that \(\hat s_i = s_i\).

### 2018-07-05 paper/sphinxes.tex
Adds draft figure of OR-POR difference
Makes Sphinxes a subsection of the design section

@@
-\section{Sphinxes: the Sphinx header format Extended for Sets of nodes}%
+\subsection{Sphinxes: the Sphinx header format Extended for Sets of nodes}%
 \label{Sphinxes}
@@
 to Sphinxes, which allows for multiple nodes per onion layer.
+(See \cref{fig:OR-POR}.)
 
-\subsection{Overview of the Sphinx header format}
+\begin{figure}
+  \includegraphics[width=\linewidth]{figures/OR-POR.png}
+  \caption{\label{fig:OR-POR}%
+    Illustration of the conceptual difference to traditional onion routing and 
+    mixing.
+  }
+\end{figure}
+
+\subsubsection{Overview of the Sphinx header format}
 
@@
 
-\subsection{The Sphinxes extension for sets of nodes}
+\subsubsection{The Sphinxes extension for sets of nodes}
 
@@
 be derived from \(\hat s_i\), then the node knows that \(\hat s_i = s_i\).
+
+\subsubsection{Sphinxes algorithms}

### 2018-07-05 paper/system-model.tex
pass on section 2

@@
+% -*- tex-main-file: "contents.tex" compile-command: "pdflatex -halt-on-error p2p-private-cloud.tex > /dev/null" ispell-dictionary: "american" -*-
+
 \section{System model, adversary model and desired privacy properties}%
@@
 
-\name is a distributed system made of users' devices. 
-Each device can communicate with any other device that it knows the
-address for (\eg using the Internet). All devices belonging to one user
- know which other devices belong to the same user, \ie the \squad.
-Thus, the devices from an \squad only know the mapping from devices to users for the devices in 
-the \squad they belong to.
+\name provides private and fully decentralized file sharing service by exploiting 
+%% is a distributed system made of
+users' devices. 
+We assume any two devices can communicate with one another as soon as one knows the address of the other (\eg using the Internet, \changeFT{possibly extended with NAT traversal techniques}).
+The devices owned by the same user (this user's \squad) know of each other.
+%Thus, the devices from an \squad only know the mapping from devices to users for the devices in 
+% the \squad they belong to.
 We also assume that users can exchange some limited amounts of data 
@@
 
-We first describe a simple model of data sharing via cloud storage to
-highlight desirable privacy properties and then map them to our provider-less
-setting. We then add privacy properties and adversary models for onion
-routing to cover network traffic analysis.
+In the following, we first describe \changeFT{how file sharing typically occurs when users rely on a cloud storage provider. We use this simple use case}
+%a simple model of data sharing via cloud storage
+to
+highlight some of the desirable privacy properties of a file sharing service, before mapping them into our \changeFT{fully decentralized (a.k.a P2P)}
+context. 
+We finally consider the additional privacy properties required to protect users from  network traffic analysis, which we propose to address through onion
+routing, and detail our adversary model.
+\commentFT{I wasn't sure how to position onion routing: to me it is more a solution than a problem specification, and since we are describing what we want here (spec./problem space) I wasn't sure how much to highlight onion routing (solution space).} \commentFT{Terminology: Do we use both `fully decentralized' and `P2P', or do we favor one over the other?}
 
-\paragraph*{In the cloud setting} if Alice wants to share a file with
-Bob, she picks up and pushes one of her files, from one of her devices, to the cloud
-provider, to make it available to Bob to download to
-one of his devices. The use of the cloud provider, as a third party,
-provides two main privacy properties, which we have to consider when
-changing the setting to that of \ac{P2P}~\cite{DevilInMetadata}:
+% We then add privacy properties and adversary models for onion
+% routing to cover network traffic analysis.
+
+\subsection{File sharing through a cloud storage provider}
+\commentFT{Moving to subsections, to better highlight structure}
+
+When sharing a file with Bob through a cloud provider, Alice only needs to upload this file from one of her devices to the cloud, and \changeFT{share a link to this file with Bob}.
+Bob in turn can download this file through the transmitted link onto one of his devices.
+
+The use of the cloud provider, as a third party,
+provides two main privacy properties, which we \changeFT{should preserve} when
+moving to a \ac{P2P}~\cite{DevilInMetadata} setting:
 \begin{itemize}
-\item Alice and Bob are the only ones \sonja{narrow down to users?} who learn 
-about Alice sharing a file with Bob, except for the cloud provider.
-\item Alice and Bob learn nothing about each others' devices, \ie 
-they cannot map any device as belonging to each other or draw
-inferences from their behavior. The cloud
-provider, however, can learn this. \sonja{expand to other users?}
+\item Except for the cloud provider, Alice and Bob are the only \changeFT{users} who learn 
+about Alice sharing a file with Bob. \sonja{narrow down to users?} \commentFT{Changed to users: we could also use entities/participants}
+\item
+  The composition and behavior of Alice and Bob's \squad remain hidden to each other, and to other users.
+I.e.
+Alice does not learn which devices Bob owns or uses, let alone how Bob uses them, and reciprocally.
+%%   Alice and Bob learn nothing about each others' devices, \ie 
+%% they cannot map any device as belonging to each other or draw
+%% inferences from their behavior.
+The cloud provider, however, \changeFT{knows this information}. \sonja{expand to other users?} \commentFT{Done}
 \end{itemize}
 
-\paragraph*{In the \ac{P2P} setting} we want to keep the privacy that
-Alice and Bob already enjoyed thanks to the cloud provider functioning
-as a gatekeeper toward each other and other users. We go a step
-further by removing the cloud provider that may draw inferences from
-metadata even when the data itself is encrypted. Removing the provider
-also removes the gatekeeping which needs to be compensated for to
-protect users from friendly surveillance~\cite{FriendlySurveillance}
-by peers (other \name users including Alice and Bob)\sonja{removed: in
-  an honest-but-curious setting}. We give the definitions for the
-security and privacy properties of \name in Section~\ref{security-discussion}.
+\subsection{Moving to a P2P environment}
+A private P2P file sharing solution should retain
+%% We want to keep
+the privacy that
+Alice and Bob already enjoy when a cloud provider functions
+as a gatekeeper towards each other and other users.
+\changeFT{Eschewing a cloud provider, as we propose to do, removes the privacy risks associated with a central brokering entity,}
+% We go a step further by removing the cloud provider that may draw inferences from metadata even when the data itself is encrypted.
+%Unfortunately, removing the cloud provider
+\changeFT{but} also removes the gatekeeping a cloud provider provides, \changeFT{and exposes} users to friendly surveillance~\cite{FriendlySurveillance}
+by other peers (other \name users including Alice and Bob). \sonja{removed: in
+  an honest-but-curious setting}
+\commentFT{Removed, as did not fit with the flow, but probably needed somewhere: `We give the definitions for the
+security and privacy properties of \name in Section~\ref{security-discussion}.'} \changeFT{In particular other users might collude to observe some of the traffic, and gain knowledge regarding Alice's and Bob's interactions, the devices they own, and how they use them.}
 
-\paragraph*{In the \name setting} we combine the requirements from
-the \ac{P2P} setting with those from onion routing for anonymity.
-Camenisch and Lysianskaya \cite{} define security properties for onion
-routing: correctness, integrity, security (wrap resistance,
+%\subsection{Protecting against network traffic analysis in \name}
+\subsection{The privacy properties and adversary model of \name}
+
+Friendly surveillance can be mitigated by ensuring security properties typically associated with onion routing \cite{[Camenisch and Lysianskaya]}{}: 
+% We combine the requirements from
+% the \ac{P2P} setting with those from onion routing for anonymity.
+% Camenisch and Lysianskaya \cite{} define security properties for onion
+% routing:
+correctness, integrity, security (wrap resistance,
 indistinguishability). These properties cover the concerns about
@@
 
-\paragraph*{Adversary model} we share the model by Tor \cite{} and
+\paragraph*{Adversary model} To assess our approach, we use the adversary model assumed by by Tor \cite{} and
 Sphinx \cite{}: the adversary has complete control over some part of

### 2018-07-05 paper/simpleSPOR.tex

\onecolumn
\section{Simple SPOR, differences to TOR}
\begin{verbatim}
Names: source S, destination D, intermediate node (set) I, rendezvous point R, file f, secret symmetric key k_s, threshold t,  a node's public key for ANOBE k_p_j

Simple Tor:
1) S: get I from directory
2) set up circuit (via key agreements with each I_i)
3) send/receive in circuit via onion (constructed by encrypting packet for each layer, next hop outermost)

Simple SPOR:

out of band:
1) S tells D: want to send f, metadata(f)
2) D tells S: here's the onion_D(R_D) (path from R_D to D)
Onion(R_D, Onion(I_1, Onion(I_2, Onion(D, payload))))
3) agreement on k_s to encrypt f

To construct an onion:

1)  get I from random peer sampling (request until P(all nodes in set I_i down)<t)
2)  get keys for all nodes in I
3) for each I_i, encrypt for all nodes in I_i, using k_p_j
3) for each I_i, choose 1 node (at random) to send to

File sharing:
1) out of band communication
2) S creates onion for path from R_S to S:
Onion(R_S, Onion(I_1, Onion(I_2, Onion(S, payload))))

3) S creates onion for path to R_D, thus path from S to D

Onion(S, Onion(I_1, Onion(I_2, Onion(R_D, Onion(I_1, Onion(I_2, Onion(D, payload)))))))

4) S uses 3) to send payload 2) (path R_S to S) to D

5) S sends enc_k_s(f) to D, as payload in 3)

6) D creates onion for path from D to R_S, thus path from D to S

Onion(D, Onion(I_1, Onion(I_2, Onion(R_S, Onion(I_1, Onion(I_2, Onion(S, payload)))))))

7) D sends acknowledgment to S along (as payload in) 5) upon receipt of f

Web browsing:

1) last node before web server W (exit node) is treated as R_S

2) S creates onion for path from exit to S
Onion(R_S, Onion(I_1, Onion(I_2, Onion(S, payload))))

3) S creates onion for path from S to W via exit
Onion(S, Onion(I_1, Onion(I_2, Onion(R_S, Onion(W, payload)))))

4) S sends 2) along (as payload in) 3), with http request for server

Note: need to figure out how Tor sends both return onion and request, then do the same here.

5) R_S forwards http request to W, via http(s)/TCP

6) W responds to R_S

7) R_S forwards response to S as payload to 2). (R_S keeps 2) as W is not part of SPOR)

Assumptions/questions:
- choice of t, based on what? Will be informed by performance analysis.

- set of peers for RPS, all peers in the world or possible restrictions. Restrictions possible by FilteredView but loss of security (more predictable, vulnerable to Sibyl)

- RPS gives ID(=address?), public key (ANOBE), probability of availability. Note: take into account Sibyl attacks. Probility of availability currently average, but could be different [1], etc. Problem with public key by RPS is what authentication we can achieve. \Eg 
can Mallory change the public key corresponding to some other node's 
address and thus man-in-the-middle that node? I think this is also 
reduced to the RPS we use.

- metadata(f) is size, digest. Note: possibly only digest.[2]

- only one ack upon whole file receipt, time-outs for retry at S and D. [2]

- time-outs derived from file size, availability? Adrien: This is a problem I want to address. When does S starts resending chunks that it already shared? This has a great impact on the network cost of the overall file exchange.

- TCP between hops (S to I_1 ... to D). Reason: joint probability for loss too high for UDP and maybe we want the chunk size larger than UDP can handle in one package.

- web browsing not stateless at exit node, even possible

- ANOBE encrypts for all, non-recipients get nonsense. But here we only encrypt for set of nodes in I_i. Note: current plan to use Sphinx and modify it to allow sets of nodes (encryption from ANOBE)

Comparison between Tor and SPOR:
- SPOR file sharing similar to Tor hidden service
- Tor web browsing similar to Spor
- Tor stateful (circuits), SPOR stateless
- SPOR layers are sets of nodes, Tor layers are single nodes.
- SPOR allows for parallelism (bottlenecks only at S and D). Whereas Tor bottlenecks at the node in the circuit with the lowest 
bandwidth.
- Tor infrastracture, SPOR decentralized
- SPOR allows any node intor relay directory. Anyone can enter. Then they receive different ranks based on "good behaviour". They also monitor the nodes and kick out suspicious nodes.
- SPOR chooses routes informed by availability prediction to minimize churn (prevention)
- SPOR can do local repairs (future work?) to cope with churn (detection, response, recovery). Already now: if node not available, choose another from the set to send to. Problem in current version if node is available but then crashes. [3]
- SPOR can limit location, e.g. within a country? Would help with availability and uniform distribution of chosen nodes again due to lack of a-priori differences in availability in same time zone.
- Tor sender anonymity, SPOR file sharing sender-receiver anonymity (ID of device, not user as there's out-of-band communication), but the more fair analogy is probably with hidden services, where there should be sender-receiver anonymity also in Tor. Only sender anonymity when SPOR is used for web browsing.

[1] Adrien: Using a vector introduces discrete time, which I would prefer to avoid.
And our prediction model won't produce significantly different results
for P(online at t+1) and P(online at T+infinity). I was thus thinking of
using only P(online at t+1) as a general "P(online in the future)"
predictor. A better prediction model would be future work (not our
point: just plug your own prediction model).

[2]
Daniel: We could let the digest be the digest of each chunk. Then we get the ordering of the chunks as well. (\Ie the metadata is equivalent to a torrent file.) Then the ack could be a bitmap of which chunks are received. This is good for efficiency but opens up for attacks. However, the damage of this is not as bad as for mixes (or Tor), since the retransmission will *probably* not take the same route.
Adrien: We take inspiration from BitTorrent. They chunk files in fixed-size
pieces, make a SHA1 hash of each piece, and a hash of the previous
hashes. This is all we need to share. We can even share it in-band,
during your point 4) in file-sharing. Thus, we only need to exchange a
file identifier out of band.

[3] from Daniel's mail. (remark by Sonja: I don't know what the original v. current versions are)
Our local repairs are more limited when we have onion_D for acks. Then 
acks must be handled on a S--D basis.

Consider node I_i successfully transfers the chunk to I_{i+1}. Now 
I_{i+1} crashes before transferring the chunk to I_{i+2}. I_i cannot 
detect this, it must be detected by and solved by S and D.

With the original design I_i would detect this and resend the chunk to 
I_{i+1}'. In this case, I_i would also resend the chunk if I_{i+1} 
crashed after *successfully* transferring the chunk to I_{i+2}. So D 
would end up with receiving two copies of the chunk.

I still think that the original design is better from a privacy 
perspective as it hides S a bit more. The new design makes S and D more 
visible as any retransmission will force them to take action.

Adrien: We do handle repair. If I_{i} is down, there was a t (parameter)
probability that it would happen. This shouldn't last long, since t lies
around 10^-3. We don't change the route once it's created; it is crafted
for reliability from the ground up.

\end{verbatim}

### 2018-07-05 paper/message-passing-design.tex
Changes \SPOR to \POR

@@
-\NewScheme{\SPOR}{SPOR}
+\NewScheme{\POR}{POR}
 
@@
 
-We have the Stateless Predictive Onion Routing scheme, \SPOR, which provides 
+We have the Stateless Predictive Onion Routing scheme, \POR, which provides 
 probabilistically onion-routed message passing.
 Instead of providing only one address per hop in the route (as in \eg 
-Tor~\cite{Tor}), \(\SPOR\) provides several alternatives for the next hop 
+Tor~\cite{Tor}), \(\POR\) provides several alternatives for the next hop 
 depending on their probability of being online.
-To do this, \(\SPOR\) provides stateless algorithms for the onion-routing.
+To do this, \(\POR\) provides stateless algorithms for the onion-routing.
 
-\(\SPOR\) provides three algorithms: \(\SPOR[\Send]\) (\cref{SPORSend}), 
-\(\SPOR[\Fwd]\) (\cref{SPORFwd}) and \(\SPOR[\Recv]\) (\cref{SPORRecv}).
+\(\POR\) provides three algorithms: \(\POR[\Send]\) (\cref{SPORSend}), 
+\(\POR[\Fwd]\) (\cref{SPORFwd}) and \(\POR[\Recv]\) (\cref{SPORRecv}).
 Say Alice wants to send a message \(m\) to Bob.
-Bob uses \(\SPOR[\Recv]\) to create a probabilistic onion route \(H_\rdv\) from 
+Bob uses \(\POR[\Recv]\) to create a probabilistic onion route \(H_\rdv\) from 
 a rendez-vous point to his own device swarm --- all the hops on the route are 
@@
 Bob gives \(H_\rdv\) to Alice using an out-of-band channel, \eg using his phone.
-Alice uses \(\SPOR[\Send]\) at some later time to send the message to Bob using 
+Alice uses \(\POR[\Send]\) at some later time to send the message to Bob using 
 any of her devices.
-\(\SPOR[\Send]\) extends the route \(H_\rdv\) with some hops of Alice's choosing 
+\(\POR[\Send]\) extends the route \(H_\rdv\) with some hops of Alice's choosing 
 (uniformly randomly chosen), then starts to forward the message (using 
-\(\SPOR[\Fwd]\)) through the hops on the route to Bob.
+\(\POR[\Fwd]\)) through the hops on the route to Bob.
 This process is illustrated in \cref{fig:file-exchange}.
@@
   \caption{\label{fig:file-exchange}%
-    A schematic of Alice and Bob sending a message using \(\SPOR\).
+    A schematic of Alice and Bob sending a message using \(\POR\).
   }
@@
     }
-    \Function{\SPOR[\Recv]}{$D$}
+    \Function{\POR[\Recv]}{$D$}
       \State $H_\rdv\gets \ExtendRoute[D\concat \top, L, \theta]$
@@
   \caption{\label{SPORRecv}%
-    The \(\SPOR[\Recv]\) algorithm prepares the recipient for receiving a file.
+    The \(\POR[\Recv]\) algorithm prepares the recipient for receiving a file.
     It creates a probabilistic onion-route from a rendez-vous point to its own 
@@
     }
-    \Function{\SPOR[\Send]}{$H_\rdv, m$}
+    \Function{\POR[\Send]}{$H_\rdv, m$}
       \State $H\gets \ExtendRoute[H_\rdv, L, \theta]$
@@
   \caption{\label{SPORSend}%
-    The \(\SPOR[\Send]\) algorithm extends the route \(H_\rdv\) (using 
+    The \(\POR[\Send]\) algorithm extends the route \(H_\rdv\) (using 
     \(\ExtendRoute\), \cref{ExtendRoute}) and sends the message \(m\) down the 
-    extended route using the \(\SPOR[\Fwd]\) algorithm (\cref{SPORFwd}).
+    extended route using the \(\POR[\Fwd]\) algorithm (\cref{SPORFwd}).
     The first node of \(H_\rdv\) is the rendez-vous point selected by the 
@@
     \Require{$\pk, \sk$ is the public--private key-pair of the node.}
-    \Function{\SPOR[\Fwd]}{$C_H, m$}
+    \Function{\POR[\Fwd]}{$C_H, m$}
       \State $H\gets \DeBEdec[\mpk, \sk, C_H]$
@@
   \caption{\label{SPORFwd}%
-    The \(\SPOR[\Fwd]\) algorithm forwards \(m\) down the route \(H\), obtained 
+    The \(\POR[\Fwd]\) algorithm forwards \(m\) down the route \(H\), obtained 
     by decrypting \(C_H\) with the node's associated private key.

### 2018-07-10 paper/message-passing-design.tex
Minor updates to Sphinxes
Adds needed \NewScheme's for compilation
Simplifying onion route algorithms following discussion with David

--- 2018-07-02 paper/message-passing-design.tex
@@
+% -*- tex-main-file: "contents.tex" compile-command: "pdflatex -halt-on-error p2p-private-cloud.tex > /dev/null" ispell-dictionary: "american" -*-
+
 \NewScheme{\SPOR}{SPOR}
@@
 \NewAlgorithm{\Recv}{Receive}
-\NewVariable{\rdv}{rdv}
-
-\david{each protocol should be explained individually}
+\NewVariable{\rdv}{\mathit{rdv}}
 
@@
 alternatives for the next hop in the route depending on their
-probability of being online. To implement our  probabilistic
-predictive onion routing mechanism, \name defined three different algorithms to
-receive, send and forward messages among users' \squad. For instance,
+probability of being online. We call our modified onion routes
+Probabilistic Onion Routes or PORs.
+
+Another difference from Tor, where connections are established by all
+nodes in the route, \name is stateless. The sender
+Alice and receiver Bob cooperate to create the headers containing all
+the necessary routing information for future communication between
+Alice and Bob. In that regard, we use two PORs: one to route packets from Alice to
+Bob, and one for packets acknowledgement from Bob to Alice (See
+Fig.~\ref{fig:file-exchange}~\ding{184}). We defined some fixed
+parameters such as $L$, the number of layers in a POR, and
+$\theta$, the stopping criterion for the layers creation, i.e the
+maximum authorized  probability that all devices in a layer fail at
+once.
+
+To implement our  probabilistic
+predictive onion routing mechanism, \name defined two different algorithms to
+receive, send messages among users' \squad. For instance,
 if Alice wants to send a message \(m\) to Bob, Bob uses the
-\(\SPOR[\Recv]\) algorithm (See \cref{SPORRecv}) to create a probabilistic onion route \(H_\rdv\) from
- a rendez-vous point to its own devices from its \squad --- all the hops on the route are 
-chosen by Bob uniformly at random from the RPS. \(\SPOR[\Recv]\)
-returns the \(H_\rdv\) that Bob gives to Alice using an
-out-of-band channel, \eg using one device of its \squad.
+\([Recv]\) algorithm (See \cref{SPORFwd}) to create a probabilistic onion route \(H_{Bob}\) from
+ a set of rendez-vous point to its own devices from its \squad --- all the hops on the route are 
+chosen by Bob uniformly at random from its RPS (\view).
+ %\([Recv]\) returns the \(H_{Bob}\).
 PORs have \(L\) layers, and for each layer the number of
@@
 As long as \(\theta\) is not exceeded, alternatives nodes are added in
-\(H_\rdv\) as depicted in \cref{ExtendRoute}. Thus the probability of
-failure for the extension is \(1 - (1 - \theta)^L\).
+\(H_{Bob}\) as depicted in \cref{ExtendRoute}. Thus the probability of
+failure for the extension is \(1 - (1 - \theta)^L\). In a similar
+manner, Alice create an onion route \(H_{Alice}\) to enable Bob to
+acknowledge its messages. Bob and Alice exchange then their calculated
+PORs (i.e. H_{Bob} and H_{Alice}), using an
+out-of-band channel, \eg using one device of their \squad (See
+Fig.~\ref{fig:file-exchange}~\ding{182}).
 
@@
 
-Once Alice get the \(H_\rdv\), Alice uses \(\SPOR[\Send]\) at some
+Once Alice get the \(H_{Bob}\), Alice uses \([Send]\) at some
 later time to send the message to Bob using any of her devices from
-its \squad (See \cref{SPORSend}). First, \(\SPOR[\Send]\) extends the route
-\(H_\rdv\) with some hops of Alice's choosing (uniformly randomly
-chosen). Second, \(\SPOR[\Send]\) extracts from the onion the first
+its \squad (See \cref{SPORFwd}). First, \([Send]\) extends the route
+\(H_{Bob}\) with some hops of Alice's choosing (uniformly randomly
+chosen). Second, \([Send]\) extracts from the onion the first
 layer, which contained the overall
-possible rendez-vous points $D$ previously selected by the recipient (i.e. Bob).
-One device from $D$ is randomly chosen, and the \(\SPOR[\Fwd]\)
+possible alternative nodes $D$.
+One device from $D$ is randomly chosen, and the \([Fwd]\)
 sub-function is called as long as the message forwarding to one node of
@@
 in sequence the different layer with the current node’s private key. 
-The end of the route is reached when special value \(H_\rdv = \top\) is
+The end of the route is reached when the special value \(H_{Bob} = \top\) is
 encountered. Consequently the ciphered message \(c_m\) is then stored
-in the disk of the local node through the \(\Store\) sub function 
-(\cref{SPORRecv}).
+in the disk of the local node through the \([Store]\) sub function 
+(\cref{SPORFwd}).
 
-\david{the use of DeBE algorithms must be explicitly explained here}
+In a way similar, once Bob get the \(H_{Alice}\), Bob uses \([Send]\) at some
+later time to acknowledge messages sent by Alice using any of his devices from
+its\squad.
 
@@
 
-\begin{figure}
-  \includegraphics[width=\linewidth]{figures/file_exchange_v2.pdf}
-  \caption{\label{fig:file-exchange}%
-    A schematic of Alice and Bob sending a message using \(\SPOR\).
-  }
+\begin{figure}[t]
+\center
+  \includegraphics[scale=.55]{figures/file_exchange_v2.pdf}
+  \caption{\label{fig:file-exchange}A schematic of the creation and usage of PORs between Alice and Bob's e-squads.}
 \end{figure}
@@
 
-\begin{figure}
+\NewAlgorithm{\Dec}{Dec}
+\NewVariable{\sk}{sk}
 
+\begin{figure}[tbh]
   \framebox{\begin{minipage}{0.96\linewidth}
   \begin{algorithmic}[1]
+    \footnotesize
+    %\scriptsize
     \Require{%
-      $H$ is a header of the form \(D\concat H'\) or \(D\concat \top\), where 
-      \(D\) is a set of device addresses.
-      $\pk_D$ is the public key of device set $D$.
-      $L$ is the length of the route,
-      $\theta$ is the threshold of probability of failure.%
+      $D$ is the set of alternative recipient devices.
     }
+    \Function{\Recv}{$D$}
+      \State $H_\rdv\gets \ExtendRoute[D\concat \changeBisFT{\DeBEenc[\mpk, D, \top]}, L, \theta]$
+      \State \Return $H_\rdv$
+        \Comment{Give to sender out-of-bound.}
+    \EndFunction
+    \vspace{0.3em}
+    \Require{%
+      $m$, the message, and
+      $H_\rdv$, the onion route to the recipient
+    }
+    \Function{\Send}{$H_\rdv,m$}
+      \State $H\gets \ExtendRoute[H_\rdv, L, \theta]$
+      \State $D\concat C_H\gets H$  \changeBisFT{\Comment{Grabbing first hop}}
+      \For{$d\in D$}
+        \Comment{Uniformly randomly chosen}
+        % FT10Jul18: \Fwd is now an asynchronous RPS, so no return value
+        \State \changeBisFT{$d\method \Fwd[C_H, m]$ \Comment{Asynchronous RPC}}
+        %\If{$d\method \Fwd[C_H, m] \neq \bot$}
+        %  \State \Return $\top$
+        %\EndIf
+      \EndFor
+      %\State \Return $\bot$
+    \EndFunction
+    \vspace{0.3em}
+    \Require{$\sk$ is the private key-pair of the current node.}
+    \Function{\Fwd}{$C_H, m$}
+      \State $H\gets \DeBEdec[\mpk, \sk, C_H]$
+      % FT10Jul18: the \bot and \top return values do not seem to be
+      % used, so dropping them
+      \If{\changeBisFT{$H = \top$}}
+        \changeBisFT{\Comment{End of the route, the current node $\in D$}}
+        \State \changeBisFT{$\Store[m]$}
+      \Else
+        \State $\{d_i\}\concat C_H'\gets H$ \changeBisFT{\Comment{Grabbing next hop}}
+        %\If{$C_H' = \top$}
+        %  \State \Return $\Store[m]$
+        %\EndIf
+        \For{$d\in \{d_i\}$}
+          \Comment{Uniformly randomly chosen}
+          % FT10Jul18: \Fwd is now an asynchronous RPS, so no return value
+          \State \changeBisFT{$d\method \Fwd[C_H, m]$ \Comment{Asynchronous RPC}}
+          %\If{$d\method \Fwd[C_H, m] \neq \bot$}
+          %  \State \Return $\top$
+          %\EndIf
+        \EndFor
+      \EndIf
+%      \State \Return $\bot$
+    \EndFunction
+    \Function{\Store}{$m$}
+      \State $\changeBisFT{m_{\mathrm{clear}}}\gets \DeBEdec[\mpk, \sk, \changeBisFT{m}]$
+      %% \If{$m = \bot$}
+      %%   \State \Return $\bot$
+      %% \EndIf
+      \State Store $\changeBisFT{m_{\mathrm{clear}}}$ to disk.
+%      \State \Return %$\top$
+    \EndFunction
+  \end{algorithmic}
+  \end{minipage}}
+  \caption{\label{SPORFwd}%
+    \scriptsize
+    The \(\Recv\) (prepares the recipient for receiving a file), \(\Send\) and \(\Fwd\) (forwards \(m\) down the route \(H\)) algorithms.
+  }
+\end{figure}
+
+\begin{figure}[tbh]
+\framebox{\begin{minipage}{0.96\linewidth}
+  \begin{algorithmic}[1]
+\footnotesize
+%\scriptsize
     \Function{\ExtendRoute}{$H, L, \theta$}
@@
       \EndIf
-      \State $D\gets \CreateOnionLayer[\theta]$
+      \State $D\gets \CreateOnionLayer[]$
       \State $H\gets D\concat \DeBEenc[\mpk, D, H]$
@@
   \vspace{0.3em}
-    \Function{\CreateOnionLayer}{$\theta$}
+    \Function{\CreateOnionLayer}{}
       \State $(d, \pk_d, p_d)\gets \GetRandomPeer$
@@
 \end{figure}
-
-\NewAlgorithm{\Dec}{Dec}
-\NewVariable{\sk}{sk}
-
-\begin{figure}
-  \framebox{\begin{minipage}{0.96\linewidth}
-  \begin{algorithmic}
-    \Require{%
-      $D$ is the set of alternative recipient devices.
-    }
-    \Function{\SPOR[\Recv]}{$D$}
-      \State $H_\rdv\gets \ExtendRoute[D\concat \top, L, \theta]$
-      \State \Return $H_\rdv$
-        \Comment{Give to sender out-of-bound.}
-    \EndFunction
-  \end{algorithmic}
-  \end{minipage}}
-  \caption{\label{SPORRecv}%
-\scriptsize
-    The \(\SPOR[\Recv]\) algorithm prepares the recipient for receiving a file.
-  }
-\end{figure}
-
-\begin{figure}
-  \framebox{\begin{minipage}{0.96\linewidth}
-  \begin{algorithmic}
-    \Require{%
-      $m$ is the message to be sent,
-      $H_\rdv$ is the onion-route given by the recipient.
-    }
-    \Function{\SPOR[\Send]}{$H_\rdv, m$}
-      \State $H\gets \ExtendRoute[H_\rdv, L, \theta]$
-      \State $D\concat C_H\gets H_\rdv$
-      \For{$d\in D$}
-        \Comment{Uniformly randomly chosen}
-        \If{$d\method \Fwd[C_H, m] \neq \bot$}
-          \State \Return $\top$
-        \EndIf
-      \EndFor
-      \State \Return $\bot$
-    \EndFunction
-  \end{algorithmic}
-  \end{minipage}}
-  \caption{\label{SPORSend}%
-    \scriptsize
-    The \(\SPOR[\Send]\) algorithm 
-  }
-\end{figure}
-
-\begin{figure}
-  \framebox{\begin{minipage}{0.96\linewidth}
-  \begin{algorithmic}
-    \Require{$\pk, \sk$ is the public--private key-pair of the node.}
-    \Function{\SPOR[\Fwd]}{$C_H, m$}
-      \State $H\gets \DeBEdec[\mpk, \sk, C_H]$
-      \If{$H = \bot$}
-        \State \Return $\bot$
-      \EndIf
-      \State $\{d_i\}\concat C_H'\gets H$
-      \If{$C_H' = \top$}
-        \State \Return $\Store[m]$
-      \EndIf
-      \For{$d\in \{d_i\}$}
-        \Comment{Uniformly randomly chosen}
-        \If{$d\method \Fwd[C_H', m] \neq \bot$}
-          \State \Return $\top$
-        \EndIf
-      \EndFor
-      \State \Return $\bot$
-    \EndFunction
-    \Function{\Store}{$m$}
-      \State $m\gets \DeBEdec[\mpk, \sk, c_m]$
-      \If{$m = \bot$}
-        \State \Return $\bot$
-      \EndIf
-      \State Store $m$ to disk.
-      \State \Return $\top$
-    \EndFunction
-  \end{algorithmic}
-  \end{minipage}}
-  \caption{\label{SPORFwd}%
-    The \(\SPOR[\Fwd]\) algorithm forwards \(m\) down the route \(H\), obtained 
-    by decrypting \(C_H\) with the node's associated private key.
-    The special value \(H = \top\) indicated the end of the route, thus \(c_m\) 
-    is intended for the local node and \(c_m\) is instead sent to disk using 
-    \(\Store\) (\cref{SPORRecv}).%
-  }
-\end{figure}

### 2018-07-10 paper/message-passing-design.tex
WIP editing of algorithms

--- 2018-07-05 paper/message-passing-design.tex
@@
-\NewScheme{\POR}{POR}
+\NewScheme{\SPOR}
 
-\subsection{Message Passing through Predictive Onion Routes (PORs)}
+\subsection{\Acfp*{SPOR}}%
 \label{sec:message_passing}
@@
 
-We have the Stateless Predictive Onion Routing scheme, \POR, which provides 
-probabilistically onion-routed message passing.
-Instead of providing only one address per hop in the route (as in \eg 
-Tor~\cite{Tor}), \(\POR\) provides several alternatives for the next hop 
-depending on their probability of being online.
-To do this, \(\POR\) provides stateless algorithms for the onion-routing.
+We now describe a protocol \ac{SPOR}, which uses the \ac{POR} of Sphinxes to 
+transfer large messages from a source to a destination.
+We provide the following algorithms:
+\begin{itemize}
+  \item \(\SPOR[\Send]\) (\cref{SPORSend}).
+  \item \(\SPOR[\Fwd]\) (\cref{SPORFwd}).
+  \item \(\SPOR[\Recv]\) (\cref{SPORRecv}).
+\end{itemize}
 
-\(\POR\) provides three algorithms: \(\POR[\Send]\) (\cref{SPORSend}), 
-\(\POR[\Fwd]\) (\cref{SPORFwd}) and \(\POR[\Recv]\) (\cref{SPORRecv}).
-Say Alice wants to send a message \(m\) to Bob.
-Bob uses \(\POR[\Recv]\) to create a probabilistic onion route \(H_\rdv\) from 
-a rendez-vous point to his own device swarm --- all the hops on the route are 
-chosen by Bob uniformly at random.
-Bob gives \(H_\rdv\) to Alice using an out-of-band channel, \eg using his phone.
-Alice uses \(\POR[\Send]\) at some later time to send the message to Bob using 
-any of her devices.
-\(\POR[\Send]\) extends the route \(H_\rdv\) with some hops of Alice's choosing 
-(uniformly randomly chosen), then starts to forward the message (using 
-\(\POR[\Fwd]\)) through the hops on the route to Bob.
-This process is illustrated in \cref{fig:file-exchange}.
-
-\begin{figure}
-  \includegraphics[width=\linewidth]{figures/file_exchange_v2.pdf}
-  \caption{\label{fig:file-exchange}%
-    A schematic of Alice and Bob sending a message using \(\POR\).
-  }
-\end{figure}
-
-\NewAlgorithm{\ExtendRoute}{ExtendRoute}
-\NewAlgorithm{\CreateOnionLayer}{CreateOnionLayer}
-
-\begin{figure}
-
-  \framebox{\begin{minipage}{0.96\linewidth}
-  \begin{algorithmic}[1]
-    \Require{%
-      $H$ is a header of the form \(D\concat H'\) or \(D\concat \top\), where 
-      \(D\) is a set of device addresses.
-      $\pk_D$ is the public key of device set $D$.
-      $L$ is the length of the route,
-      $\theta$ is the threshold of probability of failure.%
-    }
-    \Function{\ExtendRoute}{$H, L, \theta$}
-      \If{$L\leq 0$}
-        \State \Return $H$
-      \EndIf
-      \State $D\gets \CreateOnionLayer[\theta]$
-      \State $H\gets D\concat \DeBEenc[\mpk, D, H]$
-      \State \Return $\ExtendRoute[H, L-1, \theta]$
-    \EndFunction
-
-    \Function{\CreateOnionLayer}{$\theta$}
-      \State $(d, \pk_d, p_d)\gets \GetRandomPeer$
-      \State $D\gets \{(d, \pk_d, p_d)\}$
-      \While{$\prod_{d\in D} p_d > \theta$}
-        \State $(d, \pk_d, p_d)\gets \GetRandomPeer$
-        \State $D\gets D\cup \{(d, \pk_d, p_d)\}$
-      \EndWhile
-      \State \Return $D$
-    \EndFunction
-  \end{algorithmic}
-  \end{minipage}}
-  \caption{\label{ExtendRoute}%
-    The \(\ExtendRoute\) algorithm extends a route \(H\) with \(L\) hops and 
-    failure threshold of \(\theta\) for each hop in the route.
-    Thus the probability of failure for the extension is \(1 - (1 - \theta)^L\).
-    The function \(\GetRandomPeer\) is any random peer-sampling algorithm.
-  }
-\end{figure}
+Say that Alice wants to send a message \(m\) to Bob.
+Bob runs the \(\SPOR[\Recv]\) algorithm and Alice runs the \(\SPOR[\Send]\) 
+algorithm.
+Bob (\ie \(\SPOR[\Recv]\)) creates a reply header using \(\CreateRe\) and gives 
+the output to Alice (\ie \(\SPOR[\Send]\)) out-of-band.
+At a later point, Alice creates a forward header using \(\CreateFwd\), attaches 
+the message \(m\) as payload and sends the package to the first node, \ie 
+invokes the \(\SPOR[\Fwd]\) algorithm on the first node (\eg as a remote 
+procedure call).
+The node will then process the package and in turn forward the package to the 
+next node, if itself is not the final destination.
 
@@
 \end{figure}
+
+\subsection{\Acf*{SPORES}}
+
+\dots
+
+To create a probabilistic onion route \(H_\rdv\) from a rendez-vous point to 
+his own device swarm --- all the hops on the route are chosen by Bob uniformly 
+at random.
+Bob gives \(H_\rdv\) to Alice using an out-of-band channel, \eg using his phone.
+Alice uses \(\SPOR[\Send]\) at some later time to send the message to Bob using 
+any of her devices.
+\(\SPOR[\Send]\) extends the route \(H_\rdv\) with some hops of Alice's 
+choosing (uniformly randomly chosen), then starts to forward the message (using 
+\(\SPOR[\Fwd]\)) through the hops on the route to Bob.
+This process is illustrated in \cref{fig:file-exchange}.
+
+\begin{figure}
+  \includegraphics[width=\linewidth]{figures/file_exchange_v2.pdf}
+  \caption{\label{fig:file-exchange}%
+    A schematic of Alice and Bob sending a message using \(\SPORES\).
+    \ding{1} illustrates the layer of the headers that Alice and Bob create.
+    In \ding{2}, Alice and Bob exchange the headers out-of-band.
+    In \ding{3}, Alice and Bob use two \ac{SPOR} routes, one for messages and 
+    one for acknowledgements.
+  }
+\end{figure}

### 2018-07-10 paper/sphinxes.tex
Starts adding Sphinxes algorithms
Minor updates to Sphinxes
WIP editing of algorithms

@@
 
-We will now extend Sphinx: instead of providing only \(d_{i+1}\) in 
-\(\beta_i\), we will have a set \(\{d_{i+1}^{(0)}, \dotsc, d_{i+1}^{(m)}\}\) of 
-\(m\) alternative next nodes.
+We will now extend Sphinx to do \ac{POR}: instead of providing only \(d_{i+1}\) 
+in \(\beta_i\), we will have a set \(\{d_{i+1}^{(0)}, \dotsc, d_{i+1}^{(m)}\}\) 
+of \(m\) alternative next nodes.
 This means that all \(m\) nodes must be able to compute the same shared secret 
@@
 
-\subsubsection{Sphinxes algorithms}
+\subsubsection{Sphinxes algorithms and \acf*{POR}}
+
+\NewScheme{\Sphinxes}{Sphxs}
+\NewAlgorithm{\CreateHeader}{\Sphinxes[CreateHeader]}
+\NewAlgorithm{\CreateFwd}{\Sphinxes[CreateFwd]}
+\NewAlgorithm{\CreateRe}{\Sphinxes[CreateReply]}
+\NewAlgorithm{\WrapRe}{\Sphinxes[WrapReply]}
+\NewAlgorithm{\Process}{\Sphinxes[Process]}
+
+Sphinxes provides the following algorithms:
+\begin{itemize}
+  \item \(\CreateHeader\) creates a header, this is a modification of that of 
+    Sphinx~\cite[\S 3.2]{Sphinx};
+  \item \(\CreateFwd\) creates a forward message, this is identical to that of 
+    Sphinx~\cite[\S 3.3]{Sphinx};
+  \item \(\CreateRe\) creates a single-use reply block, it is the same as in 
+    Sphinx~\cite[\S 3.4]{Sphinx} except that it also outputs the necessary keys 
+    to wrap it;
+  \item \(\WrapRe\) is used to wrap a given single-use reply block; finally
+  \item \(\Process\) is the algorithm for processing incoming messages, the 
+    processing is identical to Sphinx~\cite[\S 3.6, \S 3.7]{Sphinx} but uses a 
+    different interface.
+\end{itemize}
+
+\NewAlgorithm{\ExtendRoute}{ExtendRoute}
+\NewAlgorithm{\CreateOnionLayer}{CreateOnionLayer}
+
+\begin{figure}
+  \framebox{\begin{minipage}{0.96\linewidth}
+  \begin{algorithmic}[1]
+    \Require{%
+      $H$ is a header of the form \(D\concat H'\) or \(D\concat \top\), where 
+      \(D\) is a set of device addresses.
+      $\pk_D$ is the public key of device set $D$.
+      $L$ is the length of the route,
+      $\theta$ is the threshold of probability of failure.%
+    }
+    \Function{\ExtendRoute}{$H, L, \theta$}
+      \If{$L\leq 0$}
+        \State \Return $H$
+      \EndIf
+      \State $D\gets \CreateOnionLayer[\theta]$
+      \State $H\gets D\concat \DeBEenc[\mpk, D, H]$
+      \State \Return $\ExtendRoute[H, L-1, \theta]$
+    \EndFunction
+
+    \Function{\CreateOnionLayer}{$\theta$}
+      \State $(d, \pk_d, p_d)\gets \GetRandomPeer$
+      \State $D\gets \{(d, \pk_d, p_d)\}$
+      \While{$\prod_{d\in D} p_d > \theta$}
+        \State $(d, \pk_d, p_d)\gets \GetRandomPeer$
+        \State $D\gets D\cup \{(d, \pk_d, p_d)\}$
+      \EndWhile
+      \State \Return $D$
+    \EndFunction
+  \end{algorithmic}
+  \end{minipage}}
+  \caption{\label{ExtendRoute}%
+    The \(\ExtendRoute\) algorithm extends a route \(H\) with \(L\) hops and 
+    failure threshold of \(\theta\) for each hop in the route.
+    Thus the probability of failure for the extension is \(1 - (1 - \theta)^L\).
+    The function \(\GetRandomPeer\) is any random peer-sampling algorithm.
+  }
+\end{figure}

### 2018-07-11 paper/sphinxes.tex
Adds more WIP on Sphinxes

--- 2018-07-05 paper/sphinxes.tex
@@
 
-\NewVariable{\sk}{sk}
-\NewVariable{\pk}{pk}
+\NewVariable{\sk}{x}
+\NewVariable{\pk}{X}
 
@@
 
-\subsubsection{Sphinxes algorithms}
+\subsubsection{Sphinxes algorithms and \acf*{POR}}
+
+\NewScheme{\Sphinxes}{POR}
+\NewAlgorithm{\CreateHeader}{\Sphinxes[CreateHeader]}
+\NewAlgorithm{\WrapHeader}{\Sphinxes[WrapHeader]}
+\NewAlgorithm{\AttachPayload}{\Sphinxes[AttachPayload]}
+\NewAlgorithm{\Process}{\Sphinxes[Process]}
+
+Sphinxes provides the following algorithms:
+\begin{itemize}
+  \item \(\CreateHeader\) creates a header, this is a modification of that of 
+    Sphinx~\cite[\S 3.2, \S 3.4]{Sphinx}.
+  \item \(\WrapHeader\) is used to wrap a given single-use reply block given 
+    the proper keys.
+  \item \(\AttachPayload\) attaches a payload to the header, \ie makes it 
+    sendable.
+    This is what Sphinx~\cite[\S 3.3]{Sphinx} calls a forward message.
+  \item \(\Process\) is the algorithm for processing incoming messages, the 
+    processing is identical to Sphinx~\cite[\S 3.6, \S 3.7]{Sphinx} but uses a 
+    different interface.
+\end{itemize}
+
+\NewVariable{\G}{\mathcal{G}}
+\NewVariable{\mac}{\mu}
+\NewVariable{\prg}{\rho}
+\NewVariable{\prp}{\pi}
+\NewVariable{\hash}{h}
+%\NewVariable{\tag}{\tau}
+\NewVariable{\blind}{b}
+\NewVariable{\N}{\mathcal{N}}
+\NewVariable{\D}{\mathcal{D}}
+
+We will synchronize our detailed descriptions with that of 
+Sphinx~\cite{Sphinx}, hence we will use the following notation:
+\begin{itemize}
+  \item \(\kappa\) is the security parameter.
+    The adversary must thus do about \(2^\kappa\) work to break the security.
+
+  \item \(r\) is the maximum number of nodes (\ie equivalent to the number of 
+    layers) that a message will traverse before reaching its destination.
+
+  \item \(\G\) is a prime-order cyclic group satisfying the \ac{DH} assumption.
+
+  \item \(\mac\colon \bin^\kappa\times \bin^*\to \bin^\kappa\) is \iac{MAC}.
+    It can be instantiated as \eg SHA256-HMAC-128.
+
+  \item \(\prg\colon \bin^\kappa\to \bin^{(2r+3)\kappa}\) is \iac{PRG}.
+    It can be instantiated as any block cipher in counter mode.
+
+  \item \(\prp\colon \bin^\kappa\times \bin^{l_\prp} \to \bin^{l_\prp}\) is 
+    \iac{PRP}.
+    It can be instantiated using the LIONESS block cipher~\cite{LIONESS}.
+
+  \item \(\hash_\mac, \hash_\prg, \hash_\prp\) are all distinct hash functions 
+    of the form \(\bin^\kappa\to \bin^\kappa\).
+    They are used as key-derivation functions.
+
+  \item \(\hash_\tau\colon \G^*\to \bin^{2\kappa}\) is used to identify 
+    previously seen elements of \(\G^*\).
+
+  \item \(\hash_\blind\colon \G^*\times \G^*\to \ZZ_q^*\) is used to compute 
+    blinding factors.
+    All the hash functions can be instantiated with truncated versions of hash 
+    functions from the SHA-2 and -3 families.
+
+  \item \(\N\subset \bin^\kappa\) is a set of node identifiers.
+    Each node \(n\in \N\) has a private key \(\sk_n\in \ZZ_q^*\) and a public 
+    key \(\pk_n = g^{\sk_n}\in \G^*\).
+    We assume that the identifier--public-key pairs, \((n, \pk_n)\), are 
+    distributed.
+    (Sphinx made a difference between nodes and destinations, \ie the set 
+    \(\D\) such that \(\D\cap \N = \emptyset\) and \(\D\cup \N\) is prefix 
+    free, see~\cite{Sphinx} for details.
+    We could do the same adoption, but we do not need that for the purposes of 
+    this paper.)
+    We let \(*\in \N\) be the special identifier of the null node.
+
+  \item \(0_x\) denotes \(x\) zeroes.
+    \(s_{[a..b]}\) denotes all bits from the \(a\)th bit to the \(b\)th of the 
+    bit string \(s\).
+\end{itemize}
+
+\NewAlgorithm{\ComputeKeys}{ComputeKeys}
+\NewAlgorithm{\ComputePadding}{ComputePadding}
+
+The \(\CreateHeader\) algorithm is based on that of Sphinx~\cite[\S 
+3.2]{Sphinx}.
+
+\Cref{fig:CreateHeader} summarizes the algorithm.
+
+We reveal the maximum number of alternatives per layer.
+But we do this in ordinary \ac{OR} too, since there is only one node per layer.
+
+First we generate all the needed keys.
+
+\begin{figure}
+  \framebox{\begin{minipage}{0.96\linewidth}
+  \begin{algorithmic}[1]
+    \Require{%
+      $I\in \bin^\kappa$ is an identifier.
+      $L = \{N_0, \dotsc, N_\nu\}$ such that $N_i, N_j\subset \N$, $N_i\cap N_j 
+      = \emptyset\}$ for $i\neq j$, and $\nu+1 = |L| \leq r$.
+      $N_\nu$ is the destination.
+    }
+    \Function{\CreateHeader}{$I, L$}
+      \State $w_L\gets \max_{N\in L} |N|$
+      \Comment{Maximum width of a layer, \ie alternative nodes.}
+      \State $w_H\gets (2w_L+2)$
+      \Comment{Header width:
+        layer nodes' ciphertexts and addresses ($2w_L\kappa$),
+        address of next node ($\kappa$),
+        \ac{MAC} ($\kappa$).}
+      \State $(\alpha_0, s_0, C_0, b_0), \dotsc, (\alpha_\nu, s_\nu, C_\nu, 
+      b_\nu)\gets \ComputeKeys[L, w_L]$
+      \State $\phi_1, \dotsc, \phi_\nu\gets \ComputePadding[\{s_1, \dotsc, 
+      s_\nu\}, w_H]$
+      \State $\alpha \gets \alpha_\nu$
+      \State $C\gets C_\nu$
+      \State $\beta \gets
+      \left\{\left\{N_\nu\concat
+          I\concat
+          0_{(2w_L(r-\nu)+2)\kappa}\right\} \oplus
+        \prg(\hash_\prg(s_\nu)_{[0..(2w_L(r-\nu)+3)\kappa-1]}\right\}\concat 
+      \phi_\nu$
+      \Comment{$\beta_\nu$}
+      \State $\gamma \gets $
+      \Comment{$\gamma_\nu$}
+      \For{$\nu-1\leq i\leq 1$}
+        \State $(\alpha, C, \beta, \gamma) \gets
+          \WrapHeader[i, (\alpha, \beta, \gamma), \alpha_i, s_i, C_i, N_{i+1}, 
+          w_L]$
+      \EndFor
+    \EndFunction
+
+    \Function{\WrapHeader}{$i, (\alpha_{i+1}, \beta_{i+1}, \gamma_{i+1}), 
+      \alpha_i, s_i, C_i, N_{i+1}, w_L$}
+      \If{$i < 1$}
+        \Return $\bot$
+      \EndIf
+      \State $\beta_i \gets \{N_{i+1}, \concat \gamma_{i+1}\concat 
+      (\beta_{i+1})_{[0..(w_L r-1)\kappa -1]}\}$
+      \State $\gamma_i \gets \mac(\hash_\mac(s_i), \beta_i)$
+      \Return $i-1, (\alpha_i, C_i, \beta_i, \gamma_i)$
+    \EndFunction
+  \end{algorithmic}
+  \end{minipage}}
+  \caption{\label{fig:CreateHeader}%
+    \dots
+  }
+\end{figure}
+
+\begin{figure}
+  \framebox{\begin{minipage}{0.96\linewidth}
+  \begin{algorithmic}[1]
+    \Function{\ComputeKeys}{$L = \{L_1, \dotsc, L_l\}, w_L$}
+      \State $\sk\rgets \ZZ_q^*, \pk\gets g^\sk$
+      \State $\alpha_0\gets \pk$
+      \State $s_0\rgets \bin^\kappa$
+      \Comment{Differs from Sphinx.}
+      \For{$1\leq i\leq |N_0|$}
+        \State $s_0^{(i)}\gets \pk_{n_i}^\sk$, where $n_i\in |N_0|$.
+        \State $c_0^{(i)}\gets \Enc[_{s_0^{(i)}}][s_0]$
+      \EndFor
+      \For{$|N_0|+1\leq i\leq w_L$}
+        \State $c_0^{(i)}\rgets \bin^\kappa$
+      \EndFor
+      \State $C_0\gets (c_0^{(1)}, \dotsc, c_0^{(w)})$
+      \State $b_0\gets \hash_\blind(\alpha_0, s_0)$
+      \Comment{Same as Sphinx.}
+      \For{$1\leq i < \nu$}
+        \State Compute $(\alpha_i, C_i, \beta_i, \gamma_i)$ as follows.
+        \State $\alpha_i = \pk^{b_{i-1}}$
+        \State $s_i\rgets \bin^\kappa$
+        \Comment{Differs from Sphinx.}
+        \For{$1\leq j\leq |N_i|$}
+          \State $s_i^{(j)}\gets \pk_{n_j}^\sk$, where $n_j\in |N_i|$.
+          \State $c_i^{(j)}\gets \Enc[_{s_i^{(j)}}][s_i]$
+        \EndFor
+        \For{$|N_i|+1\leq i\leq w_L$}
+          \State $c_0^{(i)}\rgets \bin^\kappa$
+        \EndFor
+        \State $C_i\gets (c_i^{(1)}, \dotsc, c_i^{(w)})$
+        \Comment{Same as Sphinx.}
+        \State $b_i\gets \hash_\blind(\alpha_i, s_i)$
+      \EndFor
+      \State \Return $(\alpha_0, s_0, C_0, b_0), \dotsc, (\alpha_\nu, s_\nu, 
+      C_\nu, b_\nu)$
+    \EndFunction
+  \end{algorithmic}
+  \end{minipage}}
+  \caption{\label{fig:SphinxesKeys}%
+    \dots
+  }
+\end{figure}
+
+\begin{figure}
+  \framebox{\begin{minipage}{0.96\linewidth}
+  \begin{algorithmic}[1]
+    \Function{\ComputePadding}{$\{s_1, \dotsc, s_\nu\}, w_H$}
+      \State $\phi_1\gets \epsilon$
+      \Comment{$\epsilon$ is the empty string.}
+      \For{$2\leq i\leq \nu$}
+        \State $\phi_i = \{ \phi_{i-1}\concat 0_{w_H} \} \oplus
+          \{ \prg(\hash_\prg(s_{i-1}))_{[(w_H(r-i+1)+3)\kappa..(w_H 
+            r+3)\kappa-1]} \}$
+      \EndFor
+      \State \Return $\phi_1, \dotsc, \phi_\nu$
+    \EndFunction
+  \end{algorithmic}
+  \end{minipage}}
+  \caption{\label{fig:SphinxesPadding}%
+    \dots
+  }
+\end{figure}

### 2018-07-11 paper/message-passing-design.tex
Makes sphinxes branch compile

@@
-\NewScheme{\SPOR}
+\NewScheme{\SPOR}{SPOR}
+\NewScheme{\POR}{POR}
 
@@
 algorithm.
-Bob (\ie \(\SPOR[\Recv]\)) creates a reply header using \(\CreateRe\) and gives 
-the output to Alice (\ie \(\SPOR[\Send]\)) out-of-band.
-At a later point, Alice creates a forward header using \(\CreateFwd\), attaches 
-the message \(m\) as payload and sends the package to the first node, \ie 
-invokes the \(\SPOR[\Fwd]\) algorithm on the first node (\eg as a remote 
-procedure call).
+Bob (\ie \(\SPOR[\Recv]\)) creates a reply header using \(\CreateHeader\) and 
+gives the output to Alice (\ie \(\SPOR[\Send]\)) out-of-band.
+At a later point, Alice extends the route using \(\WrapHeader\), attaches the 
+message \(m\) as payload (\(\AttachPayload\)) and sends the package to the 
+first node, \ie invokes the \(\SPOR[\Fwd]\) algorithm on the first node.
 The node will then process the package and in turn forward the package to the 
@@
 \NewVariable{\sk}{sk}
+\NewAlgorithm{\ExtendRoute}{ExtendRoute}
 
@@
   \caption{\label{fig:file-exchange}%
-    A schematic of Alice and Bob sending a message using \(\SPORES\).
+    A schematic of Alice and Bob sending a message using \name.
     \ding{1} illustrates the layer of the headers that Alice and Bob create.

### 2018-07-11 paper/sphinxes.tex
Sphinxes: index at zero, shortens comments, wide figures

@@
 \Cref{fig:CreateHeader} summarizes the algorithm.
+\(w_L\) is the maximum width of a layer, \ie alternative nodes.
+\(w_H\) is the header width:
+layer nodes' ciphertexts and addresses ($2w_L\kappa$),
+address of next node ($\kappa$),
+\ac{MAC} ($\kappa$).
 
@@
 
-\begin{figure}
+\begin{figure*}
   \framebox{\begin{minipage}{0.96\linewidth}
   \begin{algorithmic}[1]
-    \Require{%
-      $I\in \bin^\kappa$ is an identifier.
-      $L = \{N_0, \dotsc, N_\nu\}$ such that $N_i, N_j\subset \N$, $N_i\cap N_j 
-      = \emptyset\}$ for $i\neq j$, and $\nu+1 = |L| \leq r$.
-      $N_\nu$ is the destination.
-    }
     \Function{\CreateHeader}{$I, L$}
       \State $w_L\gets \max_{N\in L} |N|$
-      \Comment{Maximum width of a layer, \ie alternative nodes.}
+      \Comment{Layer width}
       \State $w_H\gets (2w_L+2)$
-      \Comment{Header width:
-        layer nodes' ciphertexts and addresses ($2w_L\kappa$),
-        address of next node ($\kappa$),
-        \ac{MAC} ($\kappa$).}
+      \Comment{Header width}
       \State $(\alpha_0, s_0, C_0, b_0), \dotsc, (\alpha_\nu, s_\nu, C_\nu, 
       b_\nu)\gets \ComputeKeys[L, w_L]$
-      \State $\phi_1, \dotsc, \phi_\nu\gets \ComputePadding[\{s_1, \dotsc, 
+      \State $\phi_0, \dotsc, \phi_\nu\gets \ComputePadding[\{s_0, \dotsc, 
       s_\nu\}, w_H]$
@@
       \Comment{$\beta_\nu$}
-      \State $\gamma \gets $
+      \State $\gamma \gets \mac(\hash_\mac(s_\nu), \beta)$
       \Comment{$\gamma_\nu$}
@@
       \EndFor
+      \State \Return $(\alpha, C, \beta, \gamma)$
     \EndFunction
@@
       \alpha_i, s_i, C_i, N_{i+1}, w_L$}
-      \If{$i < 1$}
+      \If{$i < 0$}
         \Return $\bot$
@@
       \State $\gamma_i \gets \mac(\hash_\mac(s_i), \beta_i)$
-      \Return $i-1, (\alpha_i, C_i, \beta_i, \gamma_i)$
+      \State \Return $i-1, (\alpha_i, C_i, \beta_i, \gamma_i)$
     \EndFunction
@@
     \dots
+      $I\in \bin^\kappa$ is an identifier.
+      $L = \{N_0, \dotsc, N_\nu\}$ such that $N_i, N_j\subset \N$, $N_i\cap N_j 
+      = \emptyset\}$ for $i\neq j$, and $\nu+1 = |L| \leq r$.
+      $N_\nu$ is the destination.
   }
-\end{figure}
+\end{figure*}
 
-\begin{figure}
+\begin{figure*}
   \framebox{\begin{minipage}{0.96\linewidth}
   \begin{algorithmic}[1]
-    \Function{\ComputeKeys}{$L = \{L_1, \dotsc, L_l\}, w_L$}
+    \Function{\ComputeKeys}{$L = \{L_0, \dotsc, L_l\}, w_L$}
       \State $\sk\rgets \ZZ_q^*, \pk\gets g^\sk$
@@
       \State $s_0\rgets \bin^\kappa$
-      \Comment{Differs from Sphinx.}
       \For{$1\leq i\leq |N_0|$}
@@
       \State $b_0\gets \hash_\blind(\alpha_0, s_0)$
-      \Comment{Same as Sphinx.}
       \For{$1\leq i < \nu$}
@@
         \State $s_i\rgets \bin^\kappa$
-        \Comment{Differs from Sphinx.}
         \For{$1\leq j\leq |N_i|$}
@@
         \State $C_i\gets (c_i^{(1)}, \dotsc, c_i^{(w)})$
-        \Comment{Same as Sphinx.}
         \State $b_i\gets \hash_\blind(\alpha_i, s_i)$
@@
   }
-\end{figure}
+\end{figure*}
 
-\begin{figure}
+\begin{figure*}
   \framebox{\begin{minipage}{0.96\linewidth}
   \begin{algorithmic}[1]
-    \Function{\ComputePadding}{$\{s_1, \dotsc, s_\nu\}, w_H$}
-      \State $\phi_1\gets \epsilon$
+    \Function{\ComputePadding}{$\{s_0, \dotsc, s_\nu\}, w_H$}
+      \State $\phi_0\gets \epsilon$
       \Comment{$\epsilon$ is the empty string.}
-      \For{$2\leq i\leq \nu$}
+      \For{$1\leq i\leq \nu$}
         \State $\phi_i = \{ \phi_{i-1}\concat 0_{w_H} \} \oplus
-          \{ \prg(\hash_\prg(s_{i-1}))_{[(w_H(r-i+1)+3)\kappa..(w_H 
+          \{ \prg(\hash_\prg(s_{i-1}))_{[(w_H(r-i)+3)\kappa..(w_H 
             r+3)\kappa-1]} \}$
       \EndFor
-      \State \Return $\phi_1, \dotsc, \phi_\nu$
+      \State \Return $\phi_0, \dotsc, \phi_\nu$
     \EndFunction
@@
   }
-\end{figure}
+\end{figure*}

### 2018-07-12 paper/sphinxes.tex
WIP on Sphinxes

@@
 \begin{itemize}
-  \item \(\CreateHeader\) creates a header, this is a modification of that of 
-    Sphinx~\cite[\S 3.2, \S 3.4]{Sphinx}.
-  \item \(\WrapHeader\) is used to wrap a given single-use reply block given 
-    the proper keys.
-  \item \(\AttachPayload\) attaches a payload to the header, \ie makes it 
-    sendable.
+  \item \(\CreateHeader\) creates an extendible header.
+    It outputs a header with space left for a few layers and the needed keys to 
+    add additional layers.
+
+  \item \(\WrapHeader\) is used to wrap a given header using the proper keys.
+
+  \item \(\AttachPayload\) attaches a payload to the header using the proper 
+    keys.
     This is what Sphinx~\cite[\S 3.3]{Sphinx} calls a forward message.
+
   \item \(\Process\) is the algorithm for processing incoming messages, the 
@@
 
+\paragraph*{The \(\CreateHeader\) algorithm}
+
 \NewAlgorithm{\ComputeKeys}{ComputeKeys}
@@
 
-The \(\CreateHeader\) algorithm is based on that of Sphinx~\cite[\S 
-3.2]{Sphinx}.
+This algorithm creates a header for \iac{POR}.
+It takes as input a unique identifier \(I\in \bin^\kappa\) and a set of layers 
+\(L = \{N_0, \dotsc, N_\nu\}\) such that \(\nu+1\leq r\).
 

### 2018-07-12 paper/sphinxes.tex
Sphinxes: Changes figures to column and footnotesize
Bugfix: \mathit on greek letters made letters look weird

@@
 \NewVariable{\G}{\mathcal{G}}
-\NewVariable{\mac}{\mu}
-\NewVariable{\prg}{\rho}
-\NewVariable{\prp}{\pi}
+\NewVariable*{\mac}{\mu}
+\NewVariable*{\prg}{\rho}
+\NewVariable*{\prp}{\pi}
 \NewVariable{\hash}{h}
@@
 \NewVariable{\D}{\mathcal{D}}
+\NewVariable*{\nullnode}{\varepsilon}
+\NewVariable{\rdvnode}{*}
 
@@
     this paper.)
-    We let \(*\in \N\) be the special identifier of the null node.
+    We have two special node identifiers:
+    \(\nullnode\in \N\) is the null-node identifier, indicating an empty 
+    address.
+    \(\rdvnode\in \N\) is the rendezvous-node identifier, indicating that the 
+    current node is a rendezvous node and that the payload is \iac{POR} route 
+    to forward.
 
@@
 
-\begin{figure*}
+\begin{figure}
   \framebox{\begin{minipage}{0.96\linewidth}
+  \footnotesize
   \begin{algorithmic}[1]
@@
   }
-\end{figure*}
+\end{figure}
 
-\begin{figure*}
+\begin{figure}
   \framebox{\begin{minipage}{0.96\linewidth}
+  \footnotesize
   \begin{algorithmic}[1]
@@
   }
-\end{figure*}
+\end{figure}

### 2018-07-13 paper/message-passing-design.tex
Sphinxes: completes CreateHeader, fixes POR algorithm names

@@
 algorithm.
-Bob (\ie \(\SPOR[\Recv]\)) creates a reply header using \(\CreateHeader\) and 
+Bob (\ie \(\SPOR[\Recv]\)) creates a reply header using \(\CreateReply\) and 
 gives the output to Alice (\ie \(\SPOR[\Send]\)) out-of-band.
-At a later point, Alice extends the route using \(\WrapHeader\), attaches the 
-message \(m\) as payload (\(\AttachPayload\)) and sends the package to the 
-first node, \ie invokes the \(\SPOR[\Fwd]\) algorithm on the first node.
-The node will then process the package and in turn forward the package to the 
-next node, if itself is not the final destination.
+At a later point, Alice attaches a message \(m\) to the reply header (using 
+\(\AttachPayload\), creates a forward header using \(\CreateFwd\) and attaches 
+the reply header as payload (\(\AttachPayload\)) to the forward header.
+Then she send this packet to the first node, \ie invokes the \(\SPOR[\Fwd]\) 
+algorithm on the first node.
+The node will then process the header and in turn forward the packet to the 
+next node.
+When a node receives a packet where the nodes of the next layer is 
+\(\{\rdvnode\}\), it will parse they payload as a packet to be forwarded.
+When a node receives a packet where the nodes of the next layer is 
+\(\{\nullnode\}\), then it knows that it is the intended recipient.
 

### 2018-07-13 paper/sphinxes.tex
Sphinxes: completes CreateHeader, fixes POR algorithm names

@@
 \NewAlgorithm{\CreateHeader}{\Sphinxes[CreateHeader]}
-\NewAlgorithm{\WrapHeader}{\Sphinxes[WrapHeader]}
+\NewAlgorithm{\CreateReply}{\Sphinxes[CreateReply]}
+\NewAlgorithm{\CreateFwd}{\Sphinxes[CreateForward]}
 \NewAlgorithm{\AttachPayload}{\Sphinxes[AttachPayload]}
@@
 \begin{itemize}
-  \item \(\CreateHeader\) creates an extendible header.
-    It outputs a header with space left for a few layers and the needed keys to 
-    add additional layers.
+  \item \(\CreateHeader\) creates a header.
 
-  \item \(\WrapHeader\) is used to wrap a given header using the proper keys.
+  \item \(\CreateReply\) constructs a header to be used for replies.
+
+  \item \(\CreateFwd\) constructs a header to be used for forward messages.
 
@@
 %\NewVariable{\tag}{\tau}
+\NewVariable{\secret}{s}
 \NewVariable{\blind}{b}
@@
 This algorithm creates a header for \iac{POR}.
-It takes as input a unique identifier \(I\in \bin^\kappa\) and a set of layers 
-\(L = \{N_0, \dotsc, N_\nu\}\) such that \(\nu+1\leq r\).
+It is identical to that of Sphinx~\cite[\S 3.2]{Sphinx} except that we use a 
+set of addresses and keys for each layer instead of only one address and key.
+Also, we do not distinguish between addresses of destinations and routers.
 
-\Cref{fig:CreateHeader} summarizes the algorithm.
-\(w_L\) is the maximum width of a layer, \ie alternative nodes.
-\(w_H\) is the header width:
-layer nodes' ciphertexts and addresses ($2w_L\kappa$),
-address of next node ($\kappa$),
-\ac{MAC} ($\kappa$).
+The algorithm takes as input a unique identifier \(I\in \bin^\kappa\) and a set 
+of layers \(L = \{L_0, \dotsc, L_\nu\}\) such that \(\nu+1\leq r\).
+The last layer, \(L_\nu\), should be either \(\{\nullnode\}\) or 
+\(\{\rdvnode\}\) to terminate the routing.
 
-We reveal the maximum number of alternatives per layer.
-But we do this in ordinary \ac{OR} too, since there is only one node per layer.
+We let \(w_L = \max_{N\in L}|N|\) be the maximum width of a layer, \ie the 
+number of alternative nodes in the layer with the most alternative nodes.
+We let \(w_H = 2w_L+1\) be the header width:
+each layer must accommodate the layer nodes' ciphertexts and addresses, \ie  
+\(2w_L\) elements of \(\kappa\) bits,
+and the \ac{MAC}, \ie one element of \(\kappa\) bits.
+(Note that we reveal the maximum number of alternatives per layer, but this is 
+no different from ordinary \ac{OR} where there is a constant one node per 
+layer.)
 
 First we generate all the needed keys.
-
-\begin{figure}
-  \framebox{\begin{minipage}{0.96\linewidth}
-  \footnotesize
-  \begin{algorithmic}[1]
-    \Function{\CreateHeader}{$I, L$}
-      \State $w_L\gets \max_{N\in L} |N|$
-      \Comment{Layer width}
-      \State $w_H\gets (2w_L+2)$
-      \Comment{Header width}
-      \State $(\alpha_0, s_0, C_0, b_0), \dotsc, (\alpha_\nu, s_\nu, C_\nu, 
-      b_\nu)\gets \ComputeKeys[L, w_L]$
-      \State $\phi_0, \dotsc, \phi_\nu\gets \ComputePadding[\{s_0, \dotsc, 
-      s_\nu\}, w_H]$
-      \State $\alpha \gets \alpha_\nu$
-      \State $C\gets C_\nu$
-      \State $\beta \gets
-      \left\{\left\{N_\nu\concat
-          I\concat
-          0_{(2w_L(r-\nu)+2)\kappa}\right\} \oplus
-        \prg(\hash_\prg(s_\nu)_{[0..(2w_L(r-\nu)+3)\kappa-1]}\right\}\concat 
-      \phi_\nu$
-      \Comment{$\beta_\nu$}
-      \State $\gamma \gets \mac(\hash_\mac(s_\nu), \beta)$
-      \Comment{$\gamma_\nu$}
-      \For{$\nu-1\leq i\leq 1$}
-        \State $(\alpha, C, \beta, \gamma) \gets
-          \WrapHeader[i, (\alpha, \beta, \gamma), \alpha_i, s_i, C_i, N_{i+1}, 
-          w_L]$
-      \EndFor
-      \State \Return $(\alpha, C, \beta, \gamma)$
-    \EndFunction
-
-    \Function{\WrapHeader}{$i, (\alpha_{i+1}, \beta_{i+1}, \gamma_{i+1}), 
-      \alpha_i, s_i, C_i, N_{i+1}, w_L$}
-      \If{$i < 0$}
-        \Return $\bot$
-      \EndIf
-      \State $\beta_i \gets \{N_{i+1}, \concat \gamma_{i+1}\concat 
-      (\beta_{i+1})_{[0..(w_L r-1)\kappa -1]}\}$
-      \State $\gamma_i \gets \mac(\hash_\mac(s_i), \beta_i)$
-      \State \Return $i-1, (\alpha_i, C_i, \beta_i, \gamma_i)$
-    \EndFunction
-  \end{algorithmic}
-  \end{minipage}}
-  \caption{\label{fig:CreateHeader}%
-    \dots
-      $I\in \bin^\kappa$ is an identifier.
-      $L = \{N_0, \dotsc, N_\nu\}$ such that $N_i, N_j\subset \N$, $N_i\cap N_j 
-      = \emptyset\}$ for $i\neq j$, and $\nu+1 = |L| \leq r$.
-      $N_\nu$ is the destination.
-  }
-\end{figure}
+We compute \(\nu+1\) tuples
+\begin{align*}
+  \alpha_0 &\gets g^\sk,
+  & \secret_0 &\gets \bin^\kappa,
+  & \blind_0 &\gets \hash_\blind(\alpha_0, \secret_0) \\
+  \alpha_1 &\gets g^{\sk\blind_0},
+  & \secret_1 &\gets \bin^\kappa,
+  & \blind_1 &\gets \hash_\blind(\alpha_1, \secret_1) \\
+  &\vdots &&\vdots && \vdots \\
+  \alpha_\nu &\gets g^{\sk \blind_0\dotsb \blind_{\nu-1}},
+  & \secret_\nu &\gets \bin^\kappa,
+  & \blind_\nu &\gets \hash_\blind(\alpha_\nu, s_\nu).
+\end{align*}
+In addition, we compute
+\begin{align*}
+  \secret_0^{(0)} &\gets \pk_{n_0^{(0)}}^\sk,
+  & \dotsc, &
+  & \secret_0^{(|L_0|-1)} &\gets \pk_{n_0^{(|L_0|-1)}}^\sk \\
+  \secret_1^{(0)} &\gets \pk_{n_1^{(0)}}^{\sk \blind_0},
+  & \dotsc, &
+  & \secret_1^{(|L_1|-1)} &\gets \pk_{n_1^{(|L_1|-1)}}^{\sk \blind_0} \\
+  & \vdots &&& \vdots \\
+  \secret_\nu^{(0)} &\gets \pk_{n_\nu^{(0)}}^{\sk \blind_0\dotsb 
+    \blind_{\nu-1}},
+  & \dotsc, &
+  & \secret_\nu^{(|L_\nu|-1)} &\gets \pk_{n_\nu^{(|L_\nu|-1)}}^{\sk 
+    \blind_0\dotsb \blind_{\nu-1}}.
+\end{align*}
+We note that a node \(n_i^{(j)}\) can compute \(s_i^{(j)}\) since \[
+  s_i^{(j)} = \pk_{n_i^{(j)}}^{\sk \blind_0\dotsb \blind_{i-1}} = 
+  \alpha_i^{\sk_{n_i^{(j)}}}.
+\]
+We then construct the ciphertexts
+\begin{align*}
+  C_0 &= \prp'\left(\hash_{\prp'}\left(s_0^{(0)}\right), s_0\right)
+  \concat \dotsb
+  \concat \prp'\left(\hash_{\prp'}\left(s_0^{(|L_0|-1)}\right), s_0\right) \\
+  C_1 &= \prp'\left(\hash_{\prp'}\left(s_1^{(0)}\right), s_1\right)
+  \concat \dotsb
+  \concat \prp'\left(\hash_{\prp'}\left(s_1^{(|L_1|-1)}\right), s_1\right) \\
+  & \vdots \\
+  C_\nu &= \prp'\left(\hash_{\prp'}\left(s_\nu^{(0)}\right), s_\nu\right)
+  \concat \dotsb
+  \concat \prp'\left(\hash_{\prp'}\left(s_\nu^{(|L_\nu|-1)}\right) 
+    s_\nu\right).
+\end{align*}
+and pad them to equal length with uniformly random bits, \ie length \(w_L = 
+  \max_{i\in \{0, \dotsc, \nu\}} |C_i|\), where \(|C_i|\) denotes the length in 
+bits (each ciphertext is \(\kappa\) bits).
+These computations are summarized in \cref{fig:SphinxesKeys}.
+\commentDaniel{We can probably comment out the figure.}
 
@@
   \caption{\label{fig:SphinxesKeys}%
-    \dots
+    A function computing the keys for all nodes on all layers of a route.
+    \(L = \{L_i\}_i\) is the set of layers and each \(L_i\) is a set of the 
+    nodes on that layer.
+    \(w_L = \max_{L_i\in L} |L_i|\) is the maximum layer width, \ie the number 
+    of nodes in the layer with most nodes.
   }
 \end{figure}
+
+Next we need to compute the padding \(\phi_i\) for each layer \(i\).
+We must do this is to predict the padding introduced at each layer so that we 
+can compute the correct \acp{MAC} (\(\gamma_i\)).
+The padding for the outmost layer (layer 0) is the empty string, thus \(\phi_0 
+  \gets \epsilon\).
+Then, for layers \(1\leq i\leq \nu\), we get
+\begin{multline*}
+  \phi_i\gets \left\{\phi_{i-1}\concat 0_{w_H\kappa}\right\}\oplus \\
+  \left\{\prg\left(\hash_\prg\left(s_{i-1}\right)\right)_{[(w_H(r-i)+3)\kappa..(2r+3)\kappa-1]}\right\}.
+\end{multline*}
+These computations are summarized in \cref{fig:SphinxesPadding}.
+\commentDaniel{We can probably remove the figure.}
 
@@
   \caption{\label{fig:SphinxesPadding}%
-    \dots
+    A function computing the needed padding.
+    \(\{s_i\}_i\) is the set of keys for the layers.
+    \(w_H\) is the width of the header at each layer, \ie everything that must 
+    be removed and compensated by padding.
   }
 \end{figure}
+
+Next we will use the above computations to compute the mix headers \(M_i = 
+  (\alpha_i, \beta_i, \gamma_i)\).
+\(\alpha_i\) was computed above, so we will compute \(\beta_i\) and 
+\(\gamma_i\).
+We must compute \(\beta_i\) in reverse order.
+We let \(\beta_{\nu+1} = I\concat 0_{(w_H r-1)\kappa}\), then, for \(\nu\leq 
+  i\leq 0\), we let
+\begin{align*}
+  \beta_i &\gets \left\{L_{i+1}\concat \gamma_{i+1}\concat 
+    (\beta_{i+1})_{[0..(w_H r-1)\kappa-1]}\right\}, \\
+  \gamma_i &\gets \mac\left( \hash_\mac\left(s_i\right), \beta_i \right).
+\end{align*}
+The algorithm \(\CreateHeader\) is summarized in \cref{fig:CreateHeader}.
+\commentDaniel{We can probably remove the figure.}
+
+\begin{figure}
+  \framebox{\begin{minipage}{0.96\linewidth}
+  \footnotesize
+  \begin{algorithmic}[1]
+    \Function{\CreateHeader}{$I, L = \{L_i\}_i$}
+      \State $w_L\gets \max_{L_i\in L} |L_i|$
+      \Comment{Layer width}
+      \State $w_H\gets (2w_L+1)$
+      \Comment{Header width}
+      \State $(\alpha_0, s_0, C_0, b_0), \dotsc, (\alpha_\nu, s_\nu, C_\nu, 
+      b_\nu)\gets \ComputeKeys[L, w_L]$
+      \State $\phi_0, \dotsc, \phi_\nu\gets \ComputePadding[\{s_0, \dotsc, 
+      s_\nu\}, w_H]$
+      \State $\alpha \gets \alpha_\nu$
+      \State $C\gets C_\nu$
+      \State $\beta \gets
+        \left\{\left\{L_\nu\concat
+            I\concat
+            0_{(2w_L(r-\nu)+2)\kappa}\right\} \oplus
+          \prg(\hash_\prg(s_\nu)_{[0..(2w_L(r-\nu)+3)\kappa-1]}\right\}\concat 
+        \phi_\nu$
+      \Comment{$\beta_\nu$}
+      \State $\gamma \gets \mac(\hash_\mac(s_\nu), \beta)$
+      \Comment{$\gamma_\nu$}
+      \For{$\nu-1\leq i\leq 0$}
+          \State $\beta_i \gets \{L_{i+1}, \concat \gamma_{i+1}\concat 
+          (\beta_{i+1})_{[0..(w_L r-1)\kappa -1]}\}$
+          \State $\gamma_i \gets \mac(\hash_\mac(s_i), \beta_i)$
+      \EndFor
+      \State \Return $(\alpha, C, \beta, \gamma), \{s_0, \dotsc, s_\nu\}$
+    \EndFunction
+  \end{algorithmic}
+  \end{minipage}}
+  \caption{\label{fig:CreateHeader}%
+    \dots
+      $I\in \bin^\kappa$ is an identifier.
+      $L = \{L_0, \dotsc, L_\nu\}$ such that $L_i, L_j\subset \N$, $L_i\cap L_j 
+      = \emptyset\}$ for $i\neq j$, and $\nu+1 = |L| \leq r$.
+      $L_\nu$ is the destination.
+  }
+\end{figure}
+
+\paragraph*{The \(\CreateReply\) algorithm}
+
+\dots
+
+\paragraph*{The \(\CreateFwd\) algorithm}
+
+\dots
+
+\paragraph*{The \(\AttachPayload\) algorithm}
+
+\dots
+
+\paragraph*{The \(\Process\) algorithm}
+
+\dots

### 2018-07-13 paper/security-discussion.tex
Makes sphinxes branch compile
WIP on Sphinxes
Adds comment to security discussion

--- 2018-05-02 paper/security-discussion.tex
@@
 % the properties from Sphinx (\eg resistance to active tagging attacks).
+
+\commentDaniel{We need to prove that our POR still fulfil the CL definition of 
+  OR.
+  Since they formalize and idealize ordinary OR we need to see that our changes 
+  still work.}
+
+\commentDaniel{Retransmission is not captured in the CL OR-model, that's fine 
+  since packets are dropped.
+  We must capture the behaviour that if the adversary interrupts transmission, 
+  we will try to send to another node.
+  We can probably fix this by outputting all nodes in the next layer in the 
+  ideal model.}

### 2018-07-13 paper/sphinxes.tex
Sphinxes: adds CreateReply, UseReply, CreateFwd

@@
 \NewAlgorithm{\CreateHeader}{\Sphinxes[CreateHeader]}
+\NewAlgorithm{\CreateFwd}{\Sphinxes[CreateForward]}
 \NewAlgorithm{\CreateReply}{\Sphinxes[CreateReply]}
-\NewAlgorithm{\CreateFwd}{\Sphinxes[CreateForward]}
-\NewAlgorithm{\AttachPayload}{\Sphinxes[AttachPayload]}
-\NewAlgorithm{\Process}{\Sphinxes[Process]}
+\NewAlgorithm{\UseReply}{\Sphinxes[UseReply]}
+\NewAlgorithm{\ProcessHeader}{\Sphinxes[ProcessHeader]}
 
@@
 
+  \item \(\CreateFwd\) constructs a header to be used for forward messages.
+
   \item \(\CreateReply\) constructs a header to be used for replies.
 
-  \item \(\CreateFwd\) constructs a header to be used for forward messages.
+  \item \(\UseReply\) takes a reply header and attaches a message.
 
-  \item \(\AttachPayload\) attaches a payload to the header using the proper 
-    keys.
-    This is what Sphinx~\cite[\S 3.3]{Sphinx} calls a forward message.
-
-  \item \(\Process\) is the algorithm for processing incoming messages, the 
-    processing is identical to Sphinx~\cite[\S 3.6, \S 3.7]{Sphinx} but uses a 
-    different interface.
+  \item \(\ProcessHeader\) is the algorithm for processing incoming messages, 
+    the processing is identical to Sphinx~\cite[\S 3.6, \S 3.7]{Sphinx} but 
+    uses a different interface.
 \end{itemize}
@@
 
+\paragraph*{The \(\CreateFwd\) algorithm}
+
+This algorithm computes a forward header with a message to be delivered to the 
+destination.
+It takes as input a sequence, \(L = \{L_0, \dotsc, L_\nu\}\), of node sets, 
+such that \(\nu+1\leq r\) and \(L_\nu\) is either \(\{\nullnode\}\) or 
+\(\{\rdvnode\}\), and a message \(m\).
+(\Ie \(L_{\nu-1}\) is the final destination.)
+
+It first runs \(\CreateHeader\) with \(I = 0_\kappa\) to compute a mix header 
+\(M_0\) and the keys \(s_i\) for each layer \(i\).
+Then, for \(\nu\leq i\leq 0\), it will compute
+\begin{equation*}
+  \delta_i = \prp\left(
+    \hash_\prp\left(s_i\right),
+    \delta_{i+1}\right),
+\end{equation*}
+where \(\delta_{\nu+1}\) is the message \(m\).
+
 \paragraph*{The \(\CreateReply\) algorithm}
 
-\dots
+This algorithm prepares a header that can be used for anonymous replies.
+It takes as input a sequence, \(L = \{L_0, \dotsc, L_\nu\}\), of node sets, 
+such that \(\nu+1\leq r\), \(L_\nu\) is either \(\{\nullnode\}\) or 
+\(\{\rdvnode\}\) and \(L_{\nu-1}\) is the set of own addresses.
 
-\paragraph*{The \(\CreateFwd\) algorithm}
+It first runs \(\CreateHeader\) with \(I\rgets \bin^\kappa\) to compute a mix 
+header \(M_0\) and the keys \(s_i\) for each layer \(i\).
+It chooses uniformly randomly a key \(\tilde k\rgets \bin^\kappa\).
+Finally, it returns
+\(I\),
+the tuple of keys \((\tilde k, \hash_\prp(s_0), \dotsc, \hash_\prp(s_\nu))\),
+and \((L_0, M_0, \tilde k)\).
+
+The tuple of keys must be stored in a local table indexed by \(I\).
+The tuple \((L_0, M_0, \tilde k)\) should be given to the sender who wants to 
+use the anonymous reply.
+
+\paragraph*{The \(\UseReply\) algorithm}
+
+This algorithm takes a reply header \((L_0, M_0, \tilde k)\) and a message 
+\(m\) as input.
+It then returns \((M_0, \prp(\tilde k, m))\) which should be sent to any node 
+in \(L_0\).
+
+\paragraph*{The \(\ProcessHeader\) algorithm}
 
 \dots
-
-\paragraph*{The \(\AttachPayload\) algorithm}
-
-\dots
-
-\paragraph*{The \(\Process\) algorithm}
-
-\dots

### 2018-07-13 paper/sphinxes.tex
Sphinxes: fixes so that layers are constant-width

@@
 
-  \item \(r\) is the maximum number of nodes (\ie equivalent to the number of 
-    layers) that a message will traverse before reaching its destination.
+  \item \(r\) is the maximum number of layers (hops, nodes) that a message will 
+    traverse before reaching its destination.
+    Further, let \(w_L\) be the maximum width of a layer, \ie the maximum 
+    number of alternative nodes on a layer.
 
@@
 
-We let \(w_L = \max_{N\in L}|N|\) be the maximum width of a layer, \ie the 
-number of alternative nodes in the layer with the most alternative nodes.
+Remember that \(w_L\) is the maximum width of a layer, \ie the number of 
+alternative nodes in the layer.
 We let \(w_H = 2w_L+1\) be the header width:
@@
 and the \ac{MAC}, \ie one element of \(\kappa\) bits.
-(Note that we reveal the maximum number of alternatives per layer, but this is 
-no different from ordinary \ac{OR} where there is a constant one node per 
-layer.)
 
@@
 \end{align*}
-and pad them to equal length with uniformly random bits, \ie length \(w_L = 
-  \max_{i\in \{0, \dotsc, \nu\}} |C_i|\), where \(|C_i|\) denotes the length in 
-bits (each ciphertext is \(\kappa\) bits).
+and pad them to \(w_L\kappa\) bits with uniformly random bits.
 These computations are summarized in \cref{fig:SphinxesKeys}.
@@
   \begin{algorithmic}[1]
-    \Function{\CreateHeader}{$I, L = \{L_i\}_i$}
-      \State $w_L\gets \max_{L_i\in L} |L_i|$
-      \Comment{Layer width}
+    \Function{\CreateHeader}{$I, L = \{L_i\}_i, w_L$}
       \State $w_H\gets (2w_L+1)$
-      \Comment{Header width}
       \State $(\alpha_0, s_0, C_0, b_0), \dotsc, (\alpha_\nu, s_\nu, C_\nu, 

### 2018-07-13 paper/message-passing-design.tex
Sphinxes: adds CreateReply, UseReply, CreateFwd
Sphinxes: minor edits

@@
 
-We now describe a protocol \ac{SPOR}, which uses the \ac{POR} of Sphinxes to 
-transfer large messages from a source to a destination.
+We now describe a protocol \ac{SPOR}, which uses Sphinxes to transfer large 
+messages from a source to a destination.
 We provide the following algorithms:
@@
 At a later point, Alice attaches a message \(m\) to the reply header (using 
-\(\AttachPayload\), creates a forward header using \(\CreateFwd\) and attaches 
-the reply header as payload (\(\AttachPayload\)) to the forward header.
+\(\UseReply\), creates a forward header using \(\CreateFwd\) with the prepared 
+reply header as payload.
 Then she send this packet to the first node, \ie invokes the \(\SPOR[\Fwd]\) 

### 2018-07-13 paper/sphinxes.tex
Sphinxes: minor edits
Sphinxes: removes figures

@@
 
-  \item \(\ProcessHeader\) is the algorithm for processing incoming messages, 
-    the processing is identical to Sphinx~\cite[\S 3.6, \S 3.7]{Sphinx} but 
-    uses a different interface.
+  \item \(\ProcessHeader\) is the algorithm for processing incoming messages.
 \end{itemize}
@@
 and pad them to \(w_L\kappa\) bits with uniformly random bits.
-These computations are summarized in \cref{fig:SphinxesKeys}.
-\commentDaniel{We can probably comment out the figure.}
-
-\begin{figure}
-  \framebox{\begin{minipage}{0.96\linewidth}
-  \footnotesize
-  \begin{algorithmic}[1]
-    \Function{\ComputeKeys}{$L = \{L_0, \dotsc, L_l\}, w_L$}
-      \State $\sk\rgets \ZZ_q^*, \pk\gets g^\sk$
-      \State $\alpha_0\gets \pk$
-      \State $s_0\rgets \bin^\kappa$
-      \For{$1\leq i\leq |N_0|$}
-        \State $s_0^{(i)}\gets \pk_{n_i}^\sk$, where $n_i\in |N_0|$.
-        \State $c_0^{(i)}\gets \Enc[_{s_0^{(i)}}][s_0]$
-      \EndFor
-      \For{$|N_0|+1\leq i\leq w_L$}
-        \State $c_0^{(i)}\rgets \bin^\kappa$
-      \EndFor
-      \State $C_0\gets (c_0^{(1)}, \dotsc, c_0^{(w)})$
-      \State $b_0\gets \hash_\blind(\alpha_0, s_0)$
-      \For{$1\leq i < \nu$}
-        \State Compute $(\alpha_i, C_i, \beta_i, \gamma_i)$ as follows.
-        \State $\alpha_i = \pk^{b_{i-1}}$
-        \State $s_i\rgets \bin^\kappa$
-        \For{$1\leq j\leq |N_i|$}
-          \State $s_i^{(j)}\gets \pk_{n_j}^\sk$, where $n_j\in |N_i|$.
-          \State $c_i^{(j)}\gets \Enc[_{s_i^{(j)}}][s_i]$
-        \EndFor
-        \For{$|N_i|+1\leq i\leq w_L$}
-          \State $c_0^{(i)}\rgets \bin^\kappa$
-        \EndFor
-        \State $C_i\gets (c_i^{(1)}, \dotsc, c_i^{(w)})$
-        \State $b_i\gets \hash_\blind(\alpha_i, s_i)$
-      \EndFor
-      \State \Return $(\alpha_0, s_0, C_0, b_0), \dotsc, (\alpha_\nu, s_\nu, 
-      C_\nu, b_\nu)$
-    \EndFunction
-  \end{algorithmic}
-  \end{minipage}}
-  \caption{\label{fig:SphinxesKeys}%
-    A function computing the keys for all nodes on all layers of a route.
-    \(L = \{L_i\}_i\) is the set of layers and each \(L_i\) is a set of the 
-    nodes on that layer.
-    \(w_L = \max_{L_i\in L} |L_i|\) is the maximum layer width, \ie the number 
-    of nodes in the layer with most nodes.
-  }
-\end{figure}
 
@@
 \end{multline*}
-These computations are summarized in \cref{fig:SphinxesPadding}.
-\commentDaniel{We can probably remove the figure.}
-
-\begin{figure}
-  \framebox{\begin{minipage}{0.96\linewidth}
-  \footnotesize
-  \begin{algorithmic}[1]
-    \Function{\ComputePadding}{$\{s_0, \dotsc, s_\nu\}, w_H$}
-      \State $\phi_0\gets \epsilon$
-      \Comment{$\epsilon$ is the empty string.}
-      \For{$1\leq i\leq \nu$}
-        \State $\phi_i = \{ \phi_{i-1}\concat 0_{w_H} \} \oplus
-          \{ \prg(\hash_\prg(s_{i-1}))_{[(w_H(r-i)+3)\kappa..(w_H 
-            r+3)\kappa-1]} \}$
-      \EndFor
-      \State \Return $\phi_0, \dotsc, \phi_\nu$
-    \EndFunction
-  \end{algorithmic}
-  \end{minipage}}
-  \caption{\label{fig:SphinxesPadding}%
-    A function computing the needed padding.
-    \(\{s_i\}_i\) is the set of keys for the layers.
-    \(w_H\) is the width of the header at each layer, \ie everything that must 
-    be removed and compensated by padding.
-  }
-\end{figure}
 
@@
 \end{align*}
-The algorithm \(\CreateHeader\) is summarized in \cref{fig:CreateHeader}.
-\commentDaniel{We can probably remove the figure.}
-
-\begin{figure}
-  \framebox{\begin{minipage}{0.96\linewidth}
-  \footnotesize
-  \begin{algorithmic}[1]
-    \Function{\CreateHeader}{$I, L = \{L_i\}_i, w_L$}
-      \State $w_H\gets (2w_L+1)$
-      \State $(\alpha_0, s_0, C_0, b_0), \dotsc, (\alpha_\nu, s_\nu, C_\nu, 
-      b_\nu)\gets \ComputeKeys[L, w_L]$
-      \State $\phi_0, \dotsc, \phi_\nu\gets \ComputePadding[\{s_0, \dotsc, 
-      s_\nu\}, w_H]$
-      \State $\alpha \gets \alpha_\nu$
-      \State $C\gets C_\nu$
-      \State $\beta \gets
-        \left\{\left\{L_\nu\concat
-            I\concat
-            0_{(2w_L(r-\nu)+2)\kappa}\right\} \oplus
-          \prg(\hash_\prg(s_\nu)_{[0..(2w_L(r-\nu)+3)\kappa-1]}\right\}\concat 
-        \phi_\nu$
-      \Comment{$\beta_\nu$}
-      \State $\gamma \gets \mac(\hash_\mac(s_\nu), \beta)$
-      \Comment{$\gamma_\nu$}
-      \For{$\nu-1\leq i\leq 0$}
-          \State $\beta_i \gets \{L_{i+1}, \concat \gamma_{i+1}\concat 
-          (\beta_{i+1})_{[0..(w_L r-1)\kappa -1]}\}$
-          \State $\gamma_i \gets \mac(\hash_\mac(s_i), \beta_i)$
-      \EndFor
-      \State \Return $(\alpha, C, \beta, \gamma), \{s_0, \dotsc, s_\nu\}$
-    \EndFunction
-  \end{algorithmic}
-  \end{minipage}}
-  \caption{\label{fig:CreateHeader}%
-    \dots
-      $I\in \bin^\kappa$ is an identifier.
-      $L = \{L_0, \dotsc, L_\nu\}$ such that $L_i, L_j\subset \N$, $L_i\cap L_j 
-      = \emptyset\}$ for $i\neq j$, and $\nu+1 = |L| \leq r$.
-      $L_\nu$ is the destination.
-  }
-\end{figure}
 

### 2018-07-15 paper/sphinxes.tex
Sphinxes: updates figure text
Sphinxes: adds missing C to header

@@
   \caption{\label{fig:OR-POR}%
-    Illustration of the conceptual difference to traditional onion routing and 
-    mixing.
+    Illustration of the conceptual difference between traditional onion routing 
+    and mixing (top) and \ac{POR} (bottom).
   }
@@
 We must compute \(\beta_i\) in reverse order.
-We let \(\beta_{\nu+1} = I\concat 0_{(w_H r-1)\kappa}\), then, for \(\nu\leq 
-  i\leq 0\), we let
+We let \(\beta_{\nu} = I\concat 0_{(w_H r-1)\kappa}\), then, for \(\nu < i\leq 
+  0\), we let
 \begin{align*}
-  \beta_i &\gets \left\{L_{i+1}\concat \gamma_{i+1}\concat 
+  \beta_i &\gets \left\{L_{i+1}\concat C_{i+1}\concat \gamma_{i+1}\concat 
     (\beta_{i+1})_{[0..(w_H r-1)\kappa-1]}\right\}, \\

### 2018-07-15 paper/sphinxes.tex
Sphinxes: adds processing algorithm

@@
 
-\dots
+\NewVariable{\ProcessMessage}{ProcessMessage}
+
+The algorithm takes as input a header \((M, \delta)\), where \(M = (\alpha, C, 
+  \beta, \gamma)\in \G^*\times (\bin^\kappa)^{w_L} \times \bin^{(w_H 
+    r+1)\kappa}\times bin^\kappa\times \bin^{l_\prp}\), and an auxiliary 
+function \(\ProcessMessage\) which processes messages destined to itself.
+Let \(\sk\) be the node's private key.
+
+First, it computes the key \(s_i^{(j)}\gets \alpha^\sk\).
+Then it trial-and-error decrypts every \(c_k\) in \(C = c_0\concat 
+  \dotsb\concat c_{w_L-1}\) (\(0\leq k< w_L\)) to \(\hat s_i\gets \prp^{\prime 
+    -1}\left(s_i^{(j)}, c_k\right)\).
+If \(\gamma = \mac\left(\hat s_i, \beta\right)\), then \(\hat s_i = s_i\) is 
+correct.
+If the \ac{MAC} does not verify correctly for any key, then the algorithm 
+aborts.
+
+If the \ac{MAC} computed correctly, compute \(t\gets \hash_\tau(s_i)\).
+If \(t\) is already in the table of seen packets, drop the packet.
+Otherwise, add \(t\) to the table and decrypt \(\beta\):
+\begin{equation*}
+  L'\concat C'\concat \gamma'\concat \beta'\gets \{\beta\concat 0_{w_H 
+    \kappa}\}
+  \oplus \prg(\hash_\prg(s_i))
+\end{equation*}
+
+If \(L' = \{\nullnode\}\), the packet is addressed to the current node.
+Parse the first \(\kappa\) bits of \(\beta'\) as an identifier \(I\).
+Pass \((I, \delta)\) to the \(\ProcessMessage\) algorithm.
+
+If \(L' = \{\rdvnode\}\), the packet payload contains another Sphinxes packet 
+to be forwarded.
+Decrypt the payload \(\delta\) to get the mix packet \((M', \delta')\gets 
+  \prp^{-1}(\hash_\prp(s_i), \delta)\).
+Run the \(\ProcessHeader\) algorithm with \((M', \delta')\) and 
+\(\ProcessMessage\) as input.
+
+Otherwise. \(\beta'\) should be forwarded to \(L'\).
+Compute the blinding factor \(b\gets \hash_\blind(\alpha, s_i)\) and let 
+\(\alpha'\gets \alpha^b\).
+Send \((\alpha', C', \beta', \gamma')\) to \(L'\).

### 2018-07-15 paper/message-passing-design.tex
WIP on SPOR section (fixes #46)

@@
 \NewScheme{\SPOR}{SPOR}
-\NewScheme{\POR}{POR}
 
@@
 
-\NewAlgorithm{\Send}{Send}
-\NewAlgorithm{\Fwd}{Forward}
-\NewAlgorithm{\Recv}{Receive}
-\NewVariable{\rdv}{rdv}
-
-We now describe a protocol \ac{SPOR}, which uses Sphinxes to transfer large 
-messages from a source to a destination.
-We provide the following algorithms:
-\begin{itemize}
-  \item \(\SPOR[\Send]\) (\cref{SPORSend}).
-  \item \(\SPOR[\Fwd]\) (\cref{SPORFwd}).
-  \item \(\SPOR[\Recv]\) (\cref{SPORRecv}).
-\end{itemize}
-
 Say that Alice wants to send a message \(m\) to Bob.
-Bob runs the \(\SPOR[\Recv]\) algorithm and Alice runs the \(\SPOR[\Send]\) 
-algorithm.
-Bob (\ie \(\SPOR[\Recv]\)) creates a reply header using \(\CreateReply\) and 
-gives the output to Alice (\ie \(\SPOR[\Send]\)) out-of-band.
-At a later point, Alice attaches a message \(m\) to the reply header (using 
+Bob creates a reply header using \(\CreateReply\) and gives the output to Alice 
+over an out-of-band channel.
+We assume that \(m\) is either unavailable when the channel is used or too 
+large to successfully send over the channel directly.
+At a later point, Alice attaches a message \(m\) to the reply header using 
 \(\UseReply\), creates a forward header using \(\CreateFwd\) with the prepared 
 reply header as payload.
-Then she send this packet to the first node, \ie invokes the \(\SPOR[\Fwd]\) 
-algorithm on the first node.
+Then she sends this packet to the first node, which processes it using 
+\(\ProcessHeader\).
 The node will then process the header and in turn forward the packet to the 
 next node.
-When a node receives a packet where the nodes of the next layer is 
-\(\{\rdvnode\}\), it will parse they payload as a packet to be forwarded.
-When a node receives a packet where the nodes of the next layer is 
-\(\{\nullnode\}\), then it knows that it is the intended recipient.
+At some point the message will reach Alice who identifies the message as the 
+one expected to come from Bob.
+In this section we will focus on how Alice and Bob choose the nodes that they 
+provide to \(\CreateReply\) and \(\CreateFwd\).
+
+There are many uses of Sphinxes, many criteria that can be used to select the 
+nodes in each layer.
+We will focus on maximizing availability when routing in a network with high 
+churn.
+But one could equally well select nodes to maximize, \eg, bandwidth.
+We now describe a protocol, \ac{SPOR}, which uses Sphinxes to transfer messages 
+from a source to a destination over a network of nodes with high churn.
 

### 2018-07-15 paper/message-passing-design.tex
Updates the message massing section (WIP)

@@
 one expected to come from Bob.
-In this section we will focus on how Alice and Bob choose the nodes that they 
-provide to \(\CreateReply\) and \(\CreateFwd\).
-
-There are many uses of Sphinxes, many criteria that can be used to select the 
-nodes in each layer.
-We will focus on maximizing availability when routing in a network with high 
-churn.
-But one could equally well select nodes to maximize, \eg, bandwidth.
-We now describe a protocol, \ac{SPOR}, which uses Sphinxes to transfer messages 
-from a source to a destination over a network of nodes with high churn.
-
-\NewAlgorithm{\Store}{Store}
-\NewAlgorithm{\Dec}{Dec}
-\NewVariable{\sk}{sk}
-\NewAlgorithm{\ExtendRoute}{ExtendRoute}
-
-\begin{figure}
-  \framebox{\begin{minipage}{0.96\linewidth}
-  \begin{algorithmic}
-    \Require{%
-      $D$ is the set of alternative recipient devices.
-    }
-    \Function{\POR[\Recv]}{$D$}
-      \State $H_\rdv\gets \ExtendRoute[D\concat \top, L, \theta]$
-      \State \Return $H_\rdv$
-        \Comment{Give to sender out-of-bound.}
-    \EndFunction
-  \end{algorithmic}
-  \end{minipage}}
-  \caption{\label{SPORRecv}%
-    The \(\POR[\Recv]\) algorithm prepares the recipient for receiving a file.
-    It creates a probabilistic onion-route from a rendez-vous point to its own 
-    devices and returns the route to the sender.
-  }
-\end{figure}
-
-\begin{figure}
-  \framebox{\begin{minipage}{0.96\linewidth}
-  \begin{algorithmic}
-    \Require{%
-      $m$ is the message to be sent,
-      $H_\rdv$ is the onion-route given by the recipient.
-    }
-    \Function{\POR[\Send]}{$H_\rdv, m$}
-      \State $H\gets \ExtendRoute[H_\rdv, L, \theta]$
-      \State $D\concat C_H\gets H_\rdv$
-      \For{$d\in D$}
-        \Comment{Uniformly randomly chosen}
-        \If{$d\method \Fwd[C_H, m] \neq \bot$}
-          \State \Return $\top$
-        \EndIf
-      \EndFor
-      \State \Return $\bot$
-    \EndFunction
-  \end{algorithmic}
-  \end{minipage}}
-  \caption{\label{SPORSend}%
-    The \(\POR[\Send]\) algorithm extends the route \(H_\rdv\) (using 
-    \(\ExtendRoute\), \cref{ExtendRoute}) and sends the message \(m\) down the 
-    extended route using the \(\POR[\Fwd]\) algorithm (\cref{SPORFwd}).
-    The first node of \(H_\rdv\) is the rendez-vous point selected by the 
-    recipient.
-  }
-\end{figure}
-
-\begin{figure}
-  \framebox{\begin{minipage}{0.96\linewidth}
-  \begin{algorithmic}
-    \Require{$\pk, \sk$ is the public--private key-pair of the node.}
-    \Function{\POR[\Fwd]}{$C_H, m$}
-      \State $H\gets \DeBEdec[\mpk, \sk, C_H]$
-      \If{$H = \bot$}
-        \State \Return $\bot$
-      \EndIf
-      \State $\{d_i\}\concat C_H'\gets H$
-      \If{$C_H' = \top$}
-        \State \Return $\Store[m]$
-      \EndIf
-      \For{$d\in \{d_i\}$}
-        \Comment{Uniformly randomly chosen}
-        \If{$d\method \Fwd[C_H', m] \neq \bot$}
-          \State \Return $\top$
-        \EndIf
-      \EndFor
-      \State \Return $\bot$
-    \EndFunction
-
-    \Function{\Store}{$m$}
-      \State $m\gets \DeBEdec[\mpk, \sk, c_m]$
-      \If{$m = \bot$}
-        \State \Return $\bot$
-      \EndIf
-      \State Store $m$ to disk.
-      \State \Return $\top$
-    \EndFunction
-  \end{algorithmic}
-  \end{minipage}}
-  \caption{\label{SPORFwd}%
-    The \(\POR[\Fwd]\) algorithm forwards \(m\) down the route \(H\), obtained 
-    by decrypting \(C_H\) with the node's associated private key.
-    The special value \(H = \top\) indicated the end of the route, thus \(c_m\) 
-    is intended for the local node and \(c_m\) is instead sent to disk using 
-    \(\Store\).%
-  }
-\end{figure}
-
-\subsection{\Acf*{SPORES}}
-
-\dots
-
-To create a probabilistic onion route \(H_\rdv\) from a rendez-vous point to 
-his own device swarm --- all the hops on the route are chosen by Bob uniformly 
-at random.
-Bob gives \(H_\rdv\) to Alice using an out-of-band channel, \eg using his phone.
-Alice uses \(\SPOR[\Send]\) at some later time to send the message to Bob using 
-any of her devices.
-\(\SPOR[\Send]\) extends the route \(H_\rdv\) with some hops of Alice's 
-choosing (uniformly randomly chosen), then starts to forward the message (using 
-\(\SPOR[\Fwd]\)) through the hops on the route to Bob.
-This process is illustrated in \cref{fig:file-exchange}.
+(This process is illustrated in \cref{fig:file-exchange}.)
+Now we will focus on how Alice and Bob choose the nodes that they provide to 
+\(\CreateReply\) and \(\CreateFwd\).
 
@@
 \end{figure}
+
+There are many uses of Sphinxes, many criteria that can be used to select the 
+nodes in each layer.
+We will focus on maximizing availability when routing in a network with high 
+churn, but one could equally well select nodes to maximize, \eg, bandwidth.
+We now describe a protocol, \ac{SPOR}, which uses Sphinxes to transfer messages 
+from a source to a destination over a network of nodes with high churn.
+
+\commentDaniel{We should describe how to do this selection using a prediction 
+  oracle, then we provide a prediction oracle later.}
+
+\subsection{\Acf*{SPORES}}
+
+Above we made the usual assumption that Alice and Bob are represented by one 
+device each.
+Nowadays this is not the case: they both have multiple devices.
+This means that Bob can receive Alice's message \(m\) on several alternative 
+devices.
+This might not be that problematic, so we will modify our scenario slightly:
+The message \(m\) that Alice wants to send to Bob is too large to successfully 
+pass every layer of the route.
+\Eg each device goes offline and back online every \(t\) time units, the 
+bandwidth is \(w\) size units per time unit and the message is \(l\) size 
+units; if \(l\geq t w\), then the message \(m\) can never be delivered as any 
+device will go offline before relaying it to the next node.
+The natural solution is to split \(m\) into \(n\) parts, \(m_0, \dotsc, m_n\), 
+where \(l/n\leq w t\).
+The problem now is that \(m_i\) and \(m_j\) (\(i\neq j\)) might end up on 
+different devices.
+
+\commentDaniel{We should discuss this problem and outline our solution.}

### 2018-07-16 paper/security-discussion.tex
WIP on security discussion, makes it compile

@@
 
+\paragraph*{Security of Sphinxes}
+
+\dots
+
+\paragraph*{Security of \acs*{SPOR}}
+
 Alice wants to prevent Bob from learning which are her devices (as defined in 
 \cref{system-model}).
-Bob is allowed to infer the behaviour of devices in the global set, % Global Device Retinue, 
+Bob is allowed to infer the behaviour of devices in the global set,
+% Global Device Retinue, 
 but a file transfer from Alice should not give Bob any information about which 
@@
 Bob constructs \iac{SPOR} route that he gives to Alice.
-This means that Alice does not learn any of Bob's destination devices.
+Due to the properties that Sphinxes inherits from Sphinx, this means that Alice 
+does not learn any of Bob's destination devices.
 When Alice starts sending the message, she will not connect directly to the 
@@
 the route.
-(We would also need to modify \(\SPOR[\Fwd]\), \cref{SPORFwd}, to perform the 
-re-encryption of \(m\) before forwarding the message to the next hop.)
+%(We would also need to modify \(\SPOR[\Fwd]\), \cref{SPORFwd}, to perform the 
+%re-encryption of \(m\) before forwarding the message to the next hop.)
 Without universal re-encryption, the message \(m\) itself remains constant 

### 2018-07-16 paper/sphinxes.tex
Sphinxes: clarifies the random selection of the next node
Removes ref to LIONESS (fixes #48)
Adds \prp' and \hash_{\prp'} to list of primitives

@@
   \item \(\prp\colon \bin^\kappa\times \bin^{l_\prp} \to \bin^{l_\prp}\) is 
-    \iac{PRP}.
-    It can be instantiated using the LIONESS block cipher~\cite{LIONESS}.
+    \iac{PRP} used to encrypt the payload data.
+    \(l_\prp\) is the maximum length of the payload.
+    (Shorter payloads are assumed to be properly padded.)
 
-  \item \(\hash_\mac, \hash_\prg, \hash_\prp\) are all distinct hash functions 
-    of the form \(\bin^\kappa\to \bin^\kappa\).
+  \item \(\prp'\colon \bin^\kappa\times \bin^\kappa\times \bin^\kappa\) is 
+    another \ac{PRP}.
+    It is used to encapsulate keys.
+
+  \item \(\hash_\mac, \hash_\prg, \hash_\prp. \hash_{\prp'}\) are all distinct 
+    hash functions of the form \(\bin^\kappa\to \bin^\kappa\).
     They are used as key-derivation functions.
@@
 \(\alpha'\gets \alpha^b\).
-Send \((\alpha', C', \beta', \gamma')\) to \(L'\).
+Choose a node \(n\rgets L'\) uniformly at random.
+Send \((\alpha', C', \beta', \gamma')\) to \(n\).
+If sending to \(n\) fails, choose another node from \(L'\) uniformly at random.
+If all nodes in \(L'\) fails, the algorithm fails.

### 2018-07-16 paper/related.tex
started adding to related work, with p2p storage, p2p onion routing, etc.

@@
 \label{RelatedWork}
+
+As a whole, \name is related to but differs from the following concepts: storage and sharing (cloud, P2P file sharing, P2P storage),  mixnets, and onion routing (with infrastructure or P2P).
 
@@
 
-Mixnets~\cite{Chaum:1981} are perhaps the first solution to turn to for sending content from A to B anonymously.
-In our context, however, they are less suitable due to their reliance on mix servers, the limited protection against statistical inference possible for even a perfect mixnet given the multiple varying sources and destinations of our use case, and the delay they would add due to batching.
-We thus decided for an approach based on onion routing, which also entails sender-receiver anonymity.
+There have been several attempts at P2P storage, mostly for backup. Wuala, Farsite, Nebulostore.
+\sonja{will expand and cite}
 
@@
 
-There is a concern shared with traditional p2p file sharing, namely churn~\cite{dhtchurn} and its effect on availability - here in the narrow context of the set of user devices based on user behavior.
+There is a concern shared with traditional P2P file sharing, namely churn~\cite{dhtchurn} and its effect on availability - here in the narrow context of the set of user devices based on user behavior.
 We thus discuss the related work on predicting device availability next, though to the best of our knowledge we are the first to make use of such predictions to cope with churn in interoperating sets of user devices.
+
+Mixnets~\cite{Chaum:1981} are perhaps the first solution to turn to for sending content from A to B anonymously.
+In our context, however, they are less suitable due to their reliance on mix servers, the limited protection against statistical inference possible for even a perfect mixnet given the multiple varying sources and destinations of our use case, and the delay they would add due to batching.
+We thus decided for an approach based on onion routing, which also entails sender-receiver anonymity.
+
+Onion routing, with infrastructure and governance (Tor) and without (I2P), are geared toward web browsing. \sonja{will expand and cite}
+
+\sonja*{include some on Modeling devices' connection and disconnection}
 

### 2018-07-16 paper/design.tex
fig
Removes no-longer-needed building-blocks.tex
Revert "Removes no-longer-needed building-blocks.tex"
This reverts commit 3df1ce56ed39870f643f26e4addb2865992f00ab.
Revert "Revert "Removes no-longer-needed building-blocks.tex""
This reverts commit 0e7094c6269f84c38fd505739131958cc5b14360.
comments with placeholders for intentions

@@
 \label{design}
+\sonja{will frame and structure A) squad overlay (prediction) B)
+  global overlay (RPS) C) sphinxes (incl. sphinx, onion routing in
+  general) D) SPOR and SPORES E) encryption (hybrid, payload, header)
+  if not included earlier F) out-of-band}
+\sonja{remove/update references to building blocks, POR}
+
 This section presents the \name protocol in detail.
@@
 \centering
-\def\svgwidth{\columnwidth}
+\def\svgwidth{0.8\columnwidth}
 %\input{outline.pdf_tex}
@@
 
-\include*{building-blocks}
 \include*{squad-overlay-design}
 \include*{global-overlay-design}
+\include*{sphinxes}
 \include*{message-passing-design}

### 2018-07-16 paper/squad-overlay-design.tex
Changes disposition of design

@@
-\subsection{The \squad Overlay} 
+\subsection{\Acf*{SPORES}}
 \label{sec:squad_overlay}
+
+Above we made the usual assumption that Alice and Bob are represented by one 
+device each.
+Nowadays this is not the case: they both have multiple devices.
+This means that Bob can receive Alice's message \(m\) on several alternative 
+devices.
+This might not be that problematic, so we will modify our scenario slightly:
+The message \(m\) that Alice wants to send to Bob is too large to successfully 
+pass every layer of the route.
+\Eg each device goes offline and back online every \(t\) time units, the 
+bandwidth is \(w\) size units per time unit and the message is \(l\) size 
+units; if \(l\geq t w\), then the message \(m\) can never be delivered as any 
+device will go offline before relaying it to the next node.
+The natural solution is to split \(m\) into \(n\) parts, \(m_0, \dotsc, m_n\), 
+where \(l/n\leq w t\).
+The problem now is that \(m_i\) and \(m_j\) (\(i\neq j\)) might end up on 
+different devices.
+
+\commentDaniel{We should discuss this problem and outline our solution.}
+\commentDaniel{We must edit what's below, it's as before.}
 

### 2018-07-16 paper/security-discussion.tex
adding to discussion, section on alternatives, related work framing
Adds security discussion of Sphinxes

@@
 
-\dots
+There are two changes that we have made that must be analysed.
+We changed the key agreement from a pure \ac{DHKE}, \ie based on the \ac{DH} 
+assumption, to one containing an indirection.
+We also changed from the classical \ac{OR} of a fixed path with one node per 
+layer to \ac{POR} with several nodes per layer.
+
+The confidentiality of the key previously rested entirely on the \ac{DH} 
+assumption (\(\alpha\) in the header).
+Now it also rests on the security of the \ac{PRP} \(\prp'\) (\(C\) in the 
+header).
+The integrity is still reduced to the security of the \ac{MAC} \(\mac\) 
+(\(\gamma\) in the header).
+
+The second change is that we use several nodes per layer as opposed to only 
+one.
+The proofs of Sphinx rests on the results of \textcite{CLOnionRouting}, which 
+are results for ordinary \ac{OR} with only one node per layer.
+As long as we output all the nodes in the next layer, the proofs should not 
+change.
+We note that this is actually quite natural as a malicious adversary can drop 
+any incoming traffic to a router and wait for the timeout and retransmission to 
+the next node.
+As such, the adversary can learn all nodes in the layer.
+
+With these arguments, we believe that Sphinxes inherits the \ac{UC} security 
+properties of Sphinx, however, this should be formally analysed.
 
@@
   ideal model.}
+
+\sonja{Failure, exception handling, such as reordered chunks, chunks
+  on different devices, squad devices going offline during transfer}
+
+\section{Alternatives}%
+\label{Alternatives}
+
+\subsection{Stateful \name}
+\subsection{Beyond file exchange} web browsing, hidden services,
+interaction and collaboration.
+\subsection{Other predictions} time of day?

### 2018-07-17 paper/system-model.tex
Fixes #47: Adds ref to CLOnionRouting

@@
 
-\name provides private and fully decentralized file sharing service by exploiting 
+\name provides a private and fully decentralized file sharing service by exploiting 
 %% is a distributed system made of
@@
 
-Friendly surveillance can be mitigated by ensuring security properties typically associated with onion routing \cite{[Camenisch and Lysianskaya]}{}: 
+Friendly surveillance can be mitigated by ensuring security properties 
+typically associated with onion routing \cite{CLOnionRouting}: 
 % We combine the requirements from
 % the \ac{P2P} setting with those from onion routing for anonymity.
-% Camenisch and Lysianskaya \cite{} define security properties for onion
-% routing:
+% Camenisch and Lysianskaya \cite{CLOnionRouting} define security properties 
+% for onion routing:
 correctness, integrity, security (wrap resistance,

### 2018-07-17 paper/security-discussion.tex
Removes treated comments in security discussion

@@
 sent to Bob, unless it is an ongoing transfer.
-\\
-%\subsection{Limitations}%
+
+\paragraph*{Limitations}%
 \label{security-limitations}
@@
 
-\commentDaniel{We need to prove that our POR still fulfil the CL definition of 
-  OR.
-  Since they formalize and idealize ordinary OR we need to see that our changes 
-  still work.}
-
-\commentDaniel{Retransmission is not captured in the CL OR-model, that's fine 
-  since packets are dropped.
-  We must capture the behaviour that if the adversary interrupts transmission, 
-  we will try to send to another node.
-  We can probably fix this by outputting all nodes in the next layer in the 
-  ideal model.}
-
 \sonja{Failure, exception handling, such as reordered chunks, chunks

### 2018-07-17 paper/security-discussion.tex
WIP adapts SPOR security discussion

@@
 
-Bob constructs \iac{SPOR} route that he gives to Alice.
+Bob constructs a Sphinxes route that he gives to Alice.
 Due to the properties that Sphinxes inherits from Sphinx, this means that Alice 
@@
 When Alice starts sending the message, she will not connect directly to the 
-device at the head of the route, since that might be Bob's device.
-Alice will construct her own \ac{SPOR} route.
+device at the head of the route, since that device might be under Bob's 
+control.
+Instead, Alice will construct her own Sphinxes route.
 Thus Alice's devices are hidden from Bob's observation and vice versa.
-If we assume that Alice and Bob can sample their nodes uniformly randomly from 
-the \emph{entire} global set of devices %Global Device Retinue 
-(we will return to this assumption 
-below), then their probability of successful attack is proportional to their 
-size in the network, \ie \(\frac{|D_i|}{|D|}\), for \(i\in \{a,b\}\).
+This assumes that Alice and Bob can sample their nodes uniformly randomly from 
+the \emph{entire} global set of devices.
+If this is true, the probability of successful attack is proportional to the 
+adversary's size in the network, \ie \(\frac{|D_i|}{|D|}\).
+The adversary must be present on each layer and be selected on the first layer 
+(which is lower-bounded by \(\frac{1}{w_L}\)) --- since after that the 
+adversary can select its own nodes in the next layer instead of uniformly at 
+random.
 

### 2018-07-17 paper/message-passing-design.tex

@@
-\NewScheme{\SPOR}{SPOR}
-
-\subsection{\Acfp*{SPOR}}%
-\label{sec:message_passing}
-
-Say that Alice wants to send a message \(m\) to Bob.
-Bob creates a reply header using \(\CreateReply\) and gives the output to Alice 
-over an out-of-band channel.
-We assume that \(m\) is either unavailable when the channel is used or too 
-large to successfully send over the channel directly.
-At a later point, Alice attaches a message \(m\) to the reply header using 
-\(\UseReply\), creates a forward header using \(\CreateFwd\) with the prepared 
-reply header as payload.
-Then she sends this packet to the first node, which processes it using 
-\(\ProcessHeader\).
-The node will then process the header and in turn forward the packet to the 
-next node.
-At some point the message will reach Alice who identifies the message as the 
-one expected to come from Bob.
-(This process is illustrated in \cref{fig:file-exchange}.)
-Now we will focus on how Alice and Bob choose the nodes that they provide to 
-\(\CreateReply\) and \(\CreateFwd\).
-
-\begin{figure}
-  \includegraphics[width=\linewidth]{figures/file_exchange_v2.pdf}
-  \caption{\label{fig:file-exchange}%
-    A schematic of Alice and Bob sending a message using \name.
-    \ding{1} illustrates the layer of the headers that Alice and Bob create.
-    In \ding{2}, Alice and Bob exchange the headers out-of-band.
-    In \ding{3}, Alice and Bob use two \ac{SPOR} routes, one for messages and 
-    one for acknowledgements.
-  }
-\end{figure}
-
-There are many uses of Sphinxes, many criteria that can be used to select the 
-nodes in each layer.
-We will focus on maximizing availability when routing in a network with high 
-churn, but one could equally well select nodes to maximize, \eg, bandwidth.
-We now describe a protocol, \ac{SPOR}, which uses Sphinxes to transfer messages 
-from a source to a destination over a network of nodes with high churn.
-
-\commentDaniel{We should describe how to do this selection using a prediction 
-  oracle, then we provide a prediction oracle later.}
-
-\subsection{\Acf*{SPORES}}
-
-Above we made the usual assumption that Alice and Bob are represented by one 
-device each.
-Nowadays this is not the case: they both have multiple devices.
-This means that Bob can receive Alice's message \(m\) on several alternative 
-devices.
-This might not be that problematic, so we will modify our scenario slightly:
-The message \(m\) that Alice wants to send to Bob is too large to successfully 
-pass every layer of the route.
-\Eg each device goes offline and back online every \(t\) time units, the 
-bandwidth is \(w\) size units per time unit and the message is \(l\) size 
-units; if \(l\geq t w\), then the message \(m\) can never be delivered as any 
-device will go offline before relaying it to the next node.
-The natural solution is to split \(m\) into \(n\) parts, \(m_0, \dotsc, m_n\), 
-where \(l/n\leq w t\).
-The problem now is that \(m_i\) and \(m_j\) (\(i\neq j\)) might end up on 
-different devices.
-
-\commentDaniel{We should discuss this problem and outline our solution.}
+% -*- tex-main-file: "contents.tex" compile-command: "pdflatex -halt-on-error p2p-private-cloud.tex > /dev/null" ispell-dictionary: "american" -*-

### 2018-07-17 paper/design.tex
Changes disposition of design
Adds comments to design section

@@
   if not included earlier F) out-of-band}
+\commentDaniel{I suggest the following structure:
+  A) Sphinxes
+  B) SPOR (global overlay)
+  C) SPORES (local overlay).
+  My original idea was to make Sphinxes its own section before the design 
+  section instead of a subsection in the design section.}
 \sonja{remove/update references to building blocks, POR}
+\commentDaniel{I removed the building blocks subsection entirely.}
 
@@
 
+\include*{sphinxes}
+\include*{global-overlay-design}
 \include*{squad-overlay-design}
-\include*{global-overlay-design}
-\include*{sphinxes}
-\include*{message-passing-design}
 %\include*{file-exchange-design}

### 2018-07-17 paper/design.tex
Fixes Syntastic warnings

@@
-\section{Design of the \name file exchange system}
+\section{Design of the \name file transfer system}%
 \label{design}
-\sonja{will frame and structure A) squad overlay (prediction) B)
-  global overlay (RPS) C) sphinxes (incl. sphinx, onion routing in
-  general) D) SPOR and SPORES E) encryption (hybrid, payload, header)
-  if not included earlier F) out-of-band}
+\sonja{will frame and structure (A) squad overlay (prediction) (B)
+  global overlay (RPS) (C) sphinxes (incl.\ sphinx, onion routing in
+  general) (D) SPOR and SPORES (E) encryption (hybrid, payload, header)
+  if not included earlier (F) out-of-band}
 \commentDaniel{I suggest the following structure:
-  A) Sphinxes
-  B) SPOR (global overlay)
-  C) SPORES (local overlay).
+  (A) Sphinxes
+  (B) SPOR (global overlay)
+  (C) SPORES (local overlay).
   My original idea was to make Sphinxes its own section before the design 
@@
 Our goal is to enable private and reliable file exchange between users participating in the system, by using their respective devices only.
-When Alice and Bob, two users of our system, want to exchange a file $f$ through \name; they start by sharing some information out-of-band, e.g. from their smartphones.
+When Alice and Bob, two users of our system, want to exchange a file $f$ 
+through \name; they start by sharing some information out-of-band, \eg from 
+their smartphones.
 More precisely, they exchange metadata on $f$, encryption keys, and agree upon a Predictive Onion Route (POR).
@@
 
-The privacy objectives of our system require encryption primitives that we first detail in section~\ref{BuildingBlocks}. The other constituents of \name are depicted in figure~\ref{fig:outline}.
+The privacy objectives of our system require encryption primitives that we 
+first detail in \cref{BuildingBlocks}. The other constituents of \name are 
+depicted in \cref{fig:outline}.
 On top, the devices of each user are circled in gray, and form a user's device squad.
 The squad online members communicate among themselves: they exchange files and messages information, and cooperate to predict the user's future behavior.
-This first protocol is called the \emph{Squad Overlay} and will be discussed in section~\ref{sec:squad_overlay}.
+This first protocol is called the \emph{Squad Overlay} and will be discussed in 
+\cref{sec:squad_overlay}.
 %On top we see that each user's devices (shown as clouds) communicate with one another through a dissemination protocol---coined the \emph{squad overlay}---that will be discussed in section~\ref{sec:squad_overlay}.
-Below, we see all devices connected in a random graph: each device gives information about itself to random nodes when it is online. 
-This \emph{Global Overlay} will be covered in section~\ref{sec:global_overlay}.
-The information brought by these overlays allows devices to securely and reliably exchange messages between users by creating PORs, thus enabling file exchange between users, as will be explained in section~\ref{sec:message_passing}.
+Below, we see all devices connected in a random graph: each device gives 
+information about itself to random nodes when it is online. This \emph{Global 
+  Overlay} will be covered in \cref{sec:global_overlay}.
+The information brought by these overlays allows devices to securely and 
+reliably exchange messages between users by creating PORs, thus enabling file 
+exchange between users, as will be explained in \cref{sec:message_passing}.
 %Given this message passing protocol, users can privately exchange files, as shown in the bottom of the figure. We will cover this ultimate goal in section~\ref{sec:file_exchange}.

### 2018-07-18 paper/conclusion.tex
Moves Adrien's old future work back to conclusion
It's not security, so I'll put it back where it was until we know where
it should be.

@@
 of resilience despite unreliable nodes (supported by peer sampling)
-and the side effect of enabling more local TOR routing (for example,
-keeping routes inside a country) do not compromise security. Another
+does 
+%and the side effect of enabling more local TOR routing (for example,
+%keeping routes inside a country) do 
+not compromise security. Another
 consideration is the nature of the traffic in this scenario and the
-limits of protection against statistical inference. On a
-related note, it would be interesting to adapt the
-Sphinx~\cite{Sphinx} cryptographic packet format to the routing of
-\name as a step toward provable security.
+limits of protection against statistical inference. 
+%On a related note, it would be interesting to adapt the
+%Sphinx~\cite{Sphinx} cryptographic packet format to the routing of \name as a step toward provable security.
+
+%
+% \commentAL{To rewrite as real paragraphs} Future work and prospects:
+% \begin{itemize}
+% 	\item More in-depth knowledge of the user's behavior would allow to predict devices connections farther in the future;
+% 	\item Changing devices' asymmetric keys regularly would increase security.
+% 	Updating keys is easy in \name given the RPS that propagates new information to all nodes.
+% 	However, more reflection would be needed to avoid key updates breaking ongoing communications passing through the devices in question;
+% 	\item \name is not resilient to Byzantine nodes for now: malicious users could potentially make users pick Predictive Onion Routes that pass through them with a high probability, thus allowing the attacker to learn the file sender and receiver.
+To circumvent this, we would need to employ a secure Random Peer Sampling \cite{Jesi_Montresor_van_Steen_2010}, and prevent devices to lie on their probability of being online.
+
+% \end{itemize}

### 2018-07-18 paper/design.tex

@@
 
-This section presents the \name protocol in detail.
+This section presents the different parts of the system in detail.
+We align the presentation of the system with the taxonomy of 
+\textcite{RoutingSurveyAnonymousProtocols}.
+They categorize anonymous communication protocols using the following 
+categories:
+\begin{description}
+  \item[Network structure]
+    This describes the characteristics of the anonymous relays, the connections 
+    between them and the underlying topology.
+
+  \item[Routing information]
+    This describes the network information available to entities deciding on 
+    the route of an anonymous connection.
+
+  \item[Communication model]
+    This describes the entities that make the routing decisions and how they 
+    make these decisions.
+\end{description}
+
+We first describe Sphinxes, which is an adaptation of the Sphinx~\cite{Sphinx} 
+mix-header format.
+This affects very few parts of the taxonomy above.
+
 Our goal is to enable private and reliable file exchange between users participating in the system, by using their respective devices only.

### 2018-07-18 paper/evaluation.tex

@@
 Figure \ref{fig:success_rate_vs_t} come from the same data, with 10 experiments per set of settings.
-$\theta$, the threshold of the probability that all nodes fail at once (cf. \ref{ssub:building_routes}), takes the following values: $[0.1, 0.01, 0.001, 0.0001]$.
+$\theta$, the threshold of the probability that all nodes fail at once, takes the following values: $[0.1, 0.01, 0.001, 0.0001]$.
 $L$, the number of layers constituting a route, takes the following values: $[3, 5, 7]$.
@@
 An experiment consisted in $L*5$ users, where we randomly picked pairs of users to compute 20 routes.
-Hence, each point on the top of figure~\ref{fig:nodes_per_layer_vs_theta} is the average of 3000 layers size; 
+Hence, each point on the top of figure~\ref{fig:success_rate_vs_t} is the average of 3000 layers size; 
 each point on the bottom is the availability rate over 200 routes.
@@
 Still, $\theta\in\{10^-4, 10^-3\}$ allows highly available routes with an average availability of 100\% and 99.5\% respectively.
-Combined with the results from figure~\ref{fig:nodes_per_layer_vs_theta}, it means that routes will need an average of 5-6 devices per layer to be highly available.
+Combined with the results from figure~\ref{fig:success_rate_vs_t}, it means that routes will need an average of 5-6 devices per layer to be highly available.
 Finally, increasing $L$ logically hinders the results when using low-availability layers.

### 2018-07-18 paper/global-overlay-design.tex
algo
Adds missing \pk

@@
-\subsection{The Global Overlay}
+\NewScheme{\SPOR}{SPOR}
+
+\subsection{\Acfp*{SPOR}}%
 \label{sec:global_overlay}
+\label{sec:message_passing}
+
+Say that Alice wants to send a message \(m\) to Bob.
+Bob creates a reply header using \(\CreateReply\) and gives the output to Alice 
+over an out-of-band channel.
+We assume that \(m\) is either unavailable when the channel is used or too 
+large to successfully send over the channel directly.
+At a later point, Alice attaches a message \(m\) to the reply header using 
+\(\UseReply\), creates a forward header using \(\CreateFwd\) with the prepared 
+reply header as payload.
+Then she sends this packet to the first node, which processes it using 
+\(\ProcessHeader\).
+The node will then process the header and in turn forward the packet to the 
+next node.
+At some point the message will reach Alice who identifies the message as the 
+one expected to come from Bob.
+(This process is illustrated in \cref{fig:file-exchange}.)
+Now we will focus on how Alice and Bob choose the nodes that they provide to 
+\(\CreateReply\) and \(\CreateFwd\).
+
+\begin{figure}
+  \includegraphics[width=\linewidth]{figures/file_exchange_v2.pdf}
+  \caption{\label{fig:file-exchange}%
+    A schematic of Alice and Bob sending a message using \name.
+    \ding{1} illustrates the layer of the headers that Alice and Bob create.
+    In \ding{2}, Alice and Bob exchange the headers out-of-band.
+    In \ding{3}, Alice and Bob use two \ac{SPOR} routes, one for messages and 
+    one for acknowledgements.
+  }
+\end{figure}
+
+There are many uses of Sphinxes, many criteria that can be used to select the 
+nodes in each layer.
+We will focus on maximizing availability when routing in a network with high 
+churn, but one could equally well select nodes to maximize, \eg, bandwidth.
+We now describe a protocol, \ac{SPOR}, which uses Sphinxes to transfer messages 
+from a source to a destination over a network of nodes with high churn.
+
+\commentDaniel{We should describe how to do this selection using a prediction 
+  oracle, then we provide a prediction oracle later.}
+\commentDaniel{The stuff below is just as before, it must be edited.}
 
@@
 \newcommand{\view}{\ensuremath{\mathcal{V}_{\text{RPS}}\xspace}}
-\NewAlgorithm{\GetRandomPeer}{random descriptor from \view}
+\NewAlgorithm{\GetRandomPeer}{\text{random descriptor from }\view}
 
@@
 secondly, offline nodes get removed from one's view fairly fast---we can say that a \view contains \emph{mostly} descriptors of online devices.
+
+\NewVariable{\pk}{pk}
 

### 2018-07-18 paper/intro.tex

@@
 The exposure of metadata seriously weakens user privacy, as famously emphasized by a former NSA and CIA director: "\emph{We kill people based on metadata.}''~\cite{NaughtonTheGuardian2016} 
-In this model, user devices, masquerading as allies, get turned into tracking and/or monitoring \squad{}s, and serve as highly efficient spies over their owners.
+In this model, user devices, masquerading as allies, get turned into %% tracking and/or monitoring \squad{}s, and serve as
+highly efficient spies over their owners.
 

### 2018-07-18 paper/related.tex

@@
 
-As a whole, \name is related to but differs from the following concepts: storage and sharing (cloud, P2P file sharing, P2P storage),  mixnets, and onion routing (with infrastructure or P2P).
+\name is designed to allow a user, say Alice,  to deliberately exchange files stored on any device of her e-squad with a specific other user, Bob, represented by any device belonging to his e-squad, without using any provider or storage other than on Alice or Bob's respective e-squads.
+As a whole, \name is related to but thus differs from the following concepts: storage and sharing (cloud, P2P file sharing, P2P storage),  mixnets, and onion routing (with infrastructure or P2P).
 

### 2018-07-19 paper/design.tex
WIP on design

@@
 They categorize anonymous communication protocols using the following 
-categories:
+categories (see \cite[Table 1]{RoutingSurveyAnonymousProtocols}):
 \begin{description}
@@
     between them and the underlying topology.
+    The subcategories are
+    \begin{enumerate*}
+      \item network topology,
+      \item connection type (direction, synchronization),
+      \item symmetry (node roles, node topology for routing, decentralization).
+    \end{enumerate*}
 
@@
     the route of an anonymous connection.
+    The subcategories are
+    \begin{enumerate*}
+      \item network view necessary for making routing decisions,
+      \item triggers for routing information updates.
+    \end{enumerate*}
 
@@
     make these decisions.
+    The subcategories are
+    \begin{enumerate*}
+      \item routing type (who selects nodes per route),
+      \item scheduling (traffic prioritization),
+      \item node selection (determinism, selection set, selection probability).
+    \end{enumerate*}
+
+  \item[Performance]
+    This describes things like latency and communication mode.
+    The subcategories are
+    \begin{enumerate*}
+      \item protocol latency,
+      \item communication mode (connection- or message-based).
+    \end{enumerate*}
 \end{description}
 
-We first describe Sphinxes, which is an adaptation of the Sphinx~\cite{Sphinx} 
-mix-header format.
-This affects very few parts of the taxonomy above.
+We first describe Sphinxes (\cref{Sphinxes}), which is an adaptation of the 
+Sphinx~\cite{Sphinx} mix-header format.
+This means that we inherit some properties from Sphinx and due to being only a 
+header format, it only imposes some restrictions in the above categories.
+Sphinxes provides, just as Sphinx, source-routed (communication model), 
+unidirectional (network structure), message-based (performance) communication.
+As such, it relies on a flat routing-topology (network structure) with fair 
+scheduling (communication model) --- as all packets are indistinguishable they 
+must be processed on a first-in-first-out basis.
+Sphinxes also introduces some probability to the node selection, but this is 
+only a probabilistic selection among already selected nodes and only 
+interesting against passive adversaries (an active adversary can learn the 
+entire set).
 
-Our goal is to enable private and reliable file exchange between users participating in the system, by using their respective devices only.
+Sphinxes does \emph{not} introduce any restrictions on whether the network 
+topology must be fully connected or not, be asynchronous (as in Tor) or 
+synchronous (as in mix-nets), whether node selection must be uniformly random 
+or not.
+Just as Sphinx, it can be used in many different settings.
+
+Next, we describe the \ac{SPOR} protocol (\cref{SPOR}).
+
+Our goal is to enable private and reliable file exchange between users 
+participating in the system, by using their respective devices only.
 When Alice and Bob, two users of our system, want to exchange a file $f$ 

### 2018-07-19 paper/file-exchange-design.tex
merge algo
Finalizes editing of design

@@
-\subsection{Scheduling and transferring a file}%
+\subsection{Transferring files over \acs{SPORES}}%
 \label{sec:file_exchange}
 
-We are interested in transferring large files.
-Every device \(d\in D\) in the global device swarm is only periodically online.
-We will thus divide the data to send into \(n\) smaller chunks (similar to 
-BitTorrent~\cite{BitTorrent}).
-The idea is to choose \(n\) such that each chunk will be small enough to be 
-successfully relayed by a device before it goes offline again.
-The chunk size is empirically determined in \cref{Performance}.
-\commentDaniel{Adrien, is that true?}
-
-As stated above, Alice and Bob exchange some limited data out-of-bound using 
-their smartphones.
-The information they will exchange is the following:
-\begin{enumerate}
-  \item Bob creates an onion route header, \(H_\rdv\), by running 
-    \([\Recv]\) %(\cref{SPORRecv}) 
-    and gives it to Alice.
-  \item Alice gives Bob number of file chunks, \(n\), and the size of the file 
-    chunks.
-  \item They agree on a file-specific key \(k\) for some (authenticated) 
-    encryption scheme \(\Enc*\).
-\end{enumerate}
-Then Alice encrypts the file \(f\) and receives the ciphertext \(c_f\gets 
-  \Enc*[Enc](k, f)\).
-She then divides \(c_f\) into \(n\) chunks, \(c_f^{(1)}, \dotsc, c_f^{(n)}\), 
-and runs \(\Send(H_\rdv, c_f^{(i)})\) for all \(1\leq i\leq n\) in 
-parallel.
-\commentDaniel{Or shall we do it sequentially?}
+We will now show how to build a file transferring service on top of 
+\ac{SPORES}.

### 2018-07-19 paper/global-overlay-design.tex
WIP on design
WIP edits in global-overlay-design.tex

@@
 
-\subsection{\Acfp*{SPOR}}%
-\label{sec:global_overlay}
-\label{sec:message_passing}
+\subsection{\Acf*{SPOR}}%
+\label{SPOR}%
+\label{sec:global_overlay}%
+\label{sec:message_passing}%
 
@@
     A schematic of Alice and Bob sending a message using \name.
-    \ding{1} illustrates the layer of the headers that Alice and Bob create.
-    In \ding{2}, Alice and Bob exchange the headers out-of-band.
-    In \ding{3}, Alice and Bob use two \ac{SPOR} routes, one for messages and 
+    \ding{182} illustrates the layer of the headers that Alice and Bob create.
+    In \ding{183}, Alice and Bob exchange the headers out-of-band.
+    In \ding{184}, Alice and Bob use two \ac{SPOR} routes, one for messages and 
     one for acknowledgements.
@@
 
+\NewAlgorithm{\GetRandomPeer}{GetRandomPeer}
+
+We assume that there is an algorithm \(\GetRandomPeer\) which returns one 
+uniformly randomly selected node.
+Each such node includes
+\begin{itemize}
+  \item the node's identifier (address), \(d\);
+  \item the node's public key, \(\pk_d\);
+  \item the node's probability of being online in the near future, \(p_d = 
+      \Pr\left(d \in O_{t+1} | S_t\right)\).
+\end{itemize}
+
 \commentDaniel{We should describe how to do this selection using a prediction 
@@
 
-To reach this goal, we employ Random Peer Sampling (RPS) \cite{Voulgaris_Gavidia_van_Steen_2005,Jelasity_Voulgaris_Guerraoui_Kermarrec_van_Steen_2007}.
+To reach this goal, we employ Random Peer Sampling (RPS)~\cite{Voulgaris_Gavidia_van_Steen_2005,Jelasity_Voulgaris_Guerraoui_Kermarrec_van_Steen_2007}.
 Essentially, each node maintains a view \view containing \viewsize other devices' descriptors. 
@@
 
-In \name, an RPS descriptor for device $d$ is constituted of the following information:
-\begin{itemize}
-  \item Its address: $d$;
-  \item Its public key: \(\pk_d\);
-  \item Its probability of being online in the near future, as provided by the Squad Overlay: $p_d=P\left[d \in O_{t+1} | S_t\right]$.
-\end{itemize}
-
-Devices now have all the information they need to establish reliable PORs.
-
 % \commentDaniel{%
@@
 % }
-
-% \NewAlgorithm{\GetRandomPeer}{GetRandomPeer}
 

### 2018-07-19 paper/design.tex

@@
 
+Our goal is to enable private and reliable file exchange between users 
+participating in the system, by using their respective devices only.
+When Alice and Bob, two users of our system, want to exchange a file \(f\) 
+through \name; they start by sharing some information out-of-band, \eg from 
+their smartphones.
+More precisely, they exchange metadata on \(f\), encryption keys, and exchange 
+use-once reply mix-headers.
+They use these reply headers to transfer the file contents of \(f\) over a 
+network of unreliable nodes while also achieving privacy.
+
+\begin{figure}[t]
+  \centering
+  \def\svgwidth{0.8\columnwidth}
+  \import{figures/}{outline.pdf_tex}
+  \caption{\label{fig:outline}%
+    \commentDaniel{We must adapt this figure to the text.}
+    Outline of \name's components. Users squads of devices are circled in gray. 
+    From top to bottom: a user's devices collaborate through the Squad Overlay 
+    (\cref{sec:squad_overlay}); online devices globally share information about 
+    them to random peers (\cref{sec:global_overlay}); using the two above 
+    overlays allows for the creation of \ac{SPOR} between sets of devices. 
+    These protocols enables secure file transfer between users 
+    (\cref{SPORES}).}
+\end{figure}
+
 This section presents the different parts of the system in detail.
@@
 They categorize anonymous communication protocols using the following 
-categories (see \cite[Table 1]{RoutingSurveyAnonymousProtocols}):
+categories (see~\cite[Table 1]{RoutingSurveyAnonymousProtocols}):
 \begin{description}
@@
 Next, we describe the \ac{SPOR} protocol (\cref{SPOR}).
+This focuses on the node selection, \ie adds node selection on top of Sphinxes.
+The \ac{SPOR} protocol assumes a source of random nodes, \eg through 
+\ac{RPS}~\cite[\eg][]{} or \iac{DHT} based scheme~\cite[\eg][]{}.
+Each node must be associated with a public key and some availability 
+prediction.
+\Ac{SPOR} selects nodes for a route uniformly randomly and uses the 
+availability to maximize the availability of the entire route, \ie across 
+layers.
+As \ac{SPOR} assumes this source of random nodes, the network view (routing 
+information) of each node depends on this source of random nodes, as does the 
+fact of how decentralized the scheme becomes and whether the network toppology 
+is fully, mostly or partly connected (network structure).
+As \ac{SPOR} is designed, it selects nodes uniformly among all the nodes 
+(communication model, node selection) that the source of random nodes provides.
+Thus, ultimately, these also depends on the source of random nodes.
 
-Our goal is to enable private and reliable file exchange between users 
-participating in the system, by using their respective devices only.
-When Alice and Bob, two users of our system, want to exchange a file $f$ 
-through \name; they start by sharing some information out-of-band, \eg from 
-their smartphones.
-More precisely, they exchange metadata on $f$, encryption keys, and agree upon a Predictive Onion Route (POR).
-PORs are our adaptation of onion routes, allowing secret communication between two entities despite the unreliability of the nodes that relay their messages.
-From there on, Alice and Bob add the POR information to the headers of their subsequent file exchange messages, such that the file transfer remains secret to anyone but them.
+Finally, we describe the complete \ac{SPORES} protocol (\cref{SPORES}).
+\Ac{SPORES} adds an e-squad protocol to \ac{SPOR}.
+This protocol provides provides each device in the e-squad of a user with 
+prediction of its own and the other devices' availability.
+This availability can then be used by the devices in the e-squad to participate 
+as nodes for the routing of \ac{SPOR}, \ie making it \iac{P2P} system (network 
+structure).
 
-% Alice and Bob each has a set of devices containing their files, \eg a 
-% smartphone, laptop and a desktop computer.
-% Alice and Bob meet in a café carrying only their smartphones and Alice wants to 
-% share a file, \(f\), with Bob.
-% Alice's smartphone knows some metadata of \(f\) and that it resides on Alice's 
-% desktop computer.
-% She gives some metadata about \(f\) to Bob, at least the file size.
-% Bob creates an onion route of low-availability devices with some subset of Bob's 
-% devices as the destination.
-% The layers of the route are chosen such that the probability of all devices 
-% being offline at the same time is low.
-% Bob gives this route to Alice.
-% Alice's smartphone ensures that her desktop computer (containing the file \(f\)) 
-% gets the route and the instruction to send \(f\) using this route.
-% When Alice's desktop computer receives this instruction it will create the first 
-% half of the route and concatenate it with Bob's route, then transfer \(f\) to 
-% Bob.
-% In this section we will present the details of the necessary algorithms.
-
-% We have a set of users, \(U\), each user \(u\in U\) has a set of devices, 
-% \(D_u\).
-% We call \(D_u\) the device swarm of \(u\).
-% Alice, \(a\in U\), has a device swarm, \(D_a\), and Bob, \(b\in U\) has a device 
-% swarm, \(D_b\).
-% We let \(D = \cup_{u\in U} D_u\) be the set of all devices, the global device 
-% swarm.
-% Without loss of generality, we will use Alice, with device swarm \(D_a\), and 
-% Bob, with device swarm \(D_b\), as examples.
-
-\begin{figure}[t]
-\centering
-\def\svgwidth{0.8\columnwidth}
-%\input{outline.pdf_tex}
-\import{figures/}{outline.pdf_tex}
-%\includegraphics[width=0.9\columnwidth]{figures/outline.pdf}
-\caption{\label{fig:outline}Outline of \name's components.
-Users squads of devices are circled in gray.
-From top to bottom: a user's devices collaborate through the Squad Overlay; online devices globally share information about them to random peers; using the two above overlays allows for the creation or Predictive Onion Routes (PORs) between sets of devices; secure file exchange between users is enabled by PORs.}
-\end{figure}
-
-The privacy objectives of our system require encryption primitives that we 
-first detail in \cref{BuildingBlocks}. The other constituents of \name are 
-depicted in \cref{fig:outline}.
-On top, the devices of each user are circled in gray, and form a user's device squad.
-The squad online members communicate among themselves: they exchange files and messages information, and cooperate to predict the user's future behavior.
-This first protocol is called the \emph{Squad Overlay} and will be discussed in 
-\cref{sec:squad_overlay}.
-%On top we see that each user's devices (shown as clouds) communicate with one another through a dissemination protocol---coined the \emph{squad overlay}---that will be discussed in section~\ref{sec:squad_overlay}.
-Below, we see all devices connected in a random graph: each device gives 
-information about itself to random nodes when it is online. This \emph{Global 
-  Overlay} will be covered in \cref{sec:global_overlay}.
-The information brought by these overlays allows devices to securely and 
-reliably exchange messages between users by creating PORs, thus enabling file 
-exchange between users, as will be explained in \cref{sec:message_passing}.
-%Given this message passing protocol, users can privately exchange files, as shown in the bottom of the figure. We will cover this ultimate goal in section~\ref{sec:file_exchange}.
+\Ac{SPORES} also allows the e-squad to act as one autonomous system, rather 
+than several.
+In particular, the devices will exchange information so that one device can 
+receive an expected message on the behalf of another device, \eg while it is 
+offline.
 
@@
 \include*{squad-overlay-design}
-%\include*{file-exchange-design}
+\include*{file-exchange-design}

### 2018-07-21 paper/design.tex
Points out that Sohinxes is a bounded random walk

@@
 header format, it only imposes some restrictions in the above categories.
-Sphinxes provides, just as Sphinx, source-routed (communication model), 
-unidirectional (network structure), message-based (performance) communication.
-As such, it relies on a flat routing-topology (network structure) with fair 
+Sphinxes provides, just as Sphinx, unidirectional (network structure), 
+message-based (performance) communication.
+But unlike Sphinx, Sphinxes is hybrid source-hop-by-hop routed (communication 
+model),
+Sphinxes relies on a flat routing-topology (network structure) with fair 
 scheduling (communication model) --- as all packets are indistinguishable they 

### 2018-07-21 paper/security-discussion.tex
Points out that Sohinxes is a bounded random walk

@@
 \label{security-discussion}
+
+\sonja{will add some framing about us composing and modifying parts that
+  have security proofs for their original and individual versions and needing to evaluate the resulting schemes}
+
+\commentDaniel{Predecessor attacks: random walk protocols has the problem that 
+  the adversary can see the initiator (statistically) more often than the other 
+  nodes, and can thus identify the 
+  source~\cite{RoutingSurveyAnonymousProtocols}.
+  Our protocol is a \enquote{bounded} random walk, \ie within limits.}
 

### 2018-07-21 paper/global-overlay-design.tex
Describes assumed GetRandomNode

@@
 
-\NewAlgorithm{\GetRandomPeer}{GetRandomPeer}
-
-We assume that there is an algorithm \(\GetRandomPeer\) which returns one 
-uniformly randomly selected node.
-Each such node includes
+\((d, \pk_d, \avail_d)\gets \GetRandomNode\): We assume that there is an 
+algorithm \(\GetRandomNode\) which returns a tuple \((d, \pk_d, \avail_d)\) of 
+one uniformly randomly selected node, where.
 \begin{itemize}
-  \item the node's identifier (address), \(d\);
-  \item the node's public key, \(\pk_d\);
-  \item the node's probability of being online in the near future, \(p_d = 
-      \Pr\left(d \in O_{t+1} | S_t\right)\).
+  \item \(d\) is the node's identifier (address);
+  \item \(\pk_d\) is the node's public key;
+  \item \(\avail_d(t)\) is the node's probability of being online as a function 
+    of time.
 \end{itemize}
+The \(\GetRandomNode\) algorithm can be instantiated using \eg
+Octopus~\cite{Octopus}.
+But even a solution like Tor's authoritative directory servers would work,
 
@@
 \newcommand{\view}{\ensuremath{\mathcal{V}_{\text{RPS}}\xspace}}
-\NewAlgorithm{\GetRandomPeer}{\text{random descriptor from }\view}
+\NewAlgorithm{\GetRandomNode}{\text{random descriptor from }\view}
 
@@
 % We will denote this by the following algorithm $(@_d, \pk_d, p_d)\gets 
-%   \GetRandomPeer$, which will be used below.
+%   \GetRandomNode$, which will be used below.
 % The probability of being online, \(p_d\), is inferred as above 

### 2018-07-21 paper/security-discussion.tex
Fixes Syntastic warning

@@
 (We could also choose a deniable encryption scheme~\cite{DeniableEncryption}, 
-\eg \cite{OTPKX} which is authenticated and provides deniability under
+\eg~\cite{OTPKX} which is authenticated and provides deniability under
 surveillance-state attacks.) %is both deniable and authenticated and  provides \ac{DEN-SS}.)

### 2018-07-21 paper/design.tex
Renames global-overlay-design to spor

@@
     (\cref{sec:squad_overlay}); online devices globally share information about 
-    them to random peers (\cref{sec:global_overlay}); using the two above 
+    them to random peers (\cref{sec:SPOR}); using the two above 
     overlays allows for the creation of \ac{SPOR} between sets of devices. 
@@
 \include*{sphinxes}
-\include*{global-overlay-design}
+\include*{spor}
 \include*{squad-overlay-design}

### 2018-07-21 paper/spor.tex
Renames global-overlay-design to spor
Writes up SPOR

--- 2018-07-21 paper/global-overlay-design.tex
@@
 \label{SPOR}%
-\label{sec:global_overlay}%
+\label{sec:SPOR}%
 \label{sec:message_passing}%
@@
 But even a solution like Tor's authoritative directory servers would work,
+We will treat \(\avail_d\) in \cref{SPORES}.
 
-\commentDaniel{We should describe how to do this selection using a prediction 
-  oracle, then we provide a prediction oracle later.}
-\commentDaniel{The stuff below is just as before, it must be edited.}
-
-\newcommand{\viewsize}{\ensuremath{l_{\text{view}}\xspace}}
-\newcommand{\view}{\ensuremath{\mathcal{V}_{\text{RPS}}\xspace}}
-\NewAlgorithm{\GetRandomNode}{\text{random descriptor from }\view}
-
-To create PORs, devices need to know the address, encryption key, and probability of remaining available of some nodes in the system, to pick them as relays on the route.
-
-To reach this goal, we employ Random Peer Sampling (RPS)~\cite{Voulgaris_Gavidia_van_Steen_2005,Jelasity_Voulgaris_Guerraoui_Kermarrec_van_Steen_2007}.
-Essentially, each node maintains a view \view containing \viewsize other devices' descriptors. 
-This view is periodically updated as follows: a device $d$ pops the oldest descriptor $d'$ from its view, then swaps a predefined number of $l$ elements from \view with $d'$.
-Both devices add a descriptor for themselves to the view exchange.
-If $d'$ was offline, its descriptor is simply removed from the $d$'s view, but \view is otherwise not updated.
-
-This allows for two things: firstly, each device's view contains a constantly changing random sample of the whole set of devices;
-secondly, offline nodes get removed from one's view fairly fast---we can say that a \view contains \emph{mostly} descriptors of online devices.
-
-\NewVariable{\pk}{pk}
-
-% \commentDaniel{%
-%   What is the probability distribution of the peer sample that we get?
-%   Will it be close to uniformly random?
-%   I need this for the security analysis.%
-% }
-
-% Every time a device is online, it participates in the random peer sampling 
-% protocol.
-% If a device is sampled it provides the following information:
-% \begin{itemize}
-%   \item its address, $@_d$;
-%   \item its public key, \(\pk_d\);
-%   \item the probability of being online, $p_d=P\left[d \in O_{t+1} | S_t\right] $.
-% \end{itemize}
-% We will denote this by the following algorithm $(@_d, \pk_d, p_d)\gets 
-%   \GetRandomNode$, which will be used below.
-% The probability of being online, \(p_d\), is inferred as above 
-% (\ref{sub:a_model_of_the_user_s_behavior}).
+When Bob runs \(\CreateReply\) (or Alice runs \(\CreateFwd\)) he must supply a 
+set of nodes for each layer of the route, \(L = \{L_0, \dotsc, L_\nu\}\), where 
+\(|L_i| \leq w_L\) for \(0\leq i\leq \nu\).
+The set \(L_\nu\) contains only one or more of Bob's devices.
+For the other layers, \(L_i\) for \(i < \nu\), Bob will do the following:
+Bob queries \(\GetRandomNode\) \((\nu-1)\cdot w_L\) times to get enough nodes 
+to fill all remaining layers.
+Bob will distribute these nodes across all layers \(L_i\) to maximize \(\min_i 
+  \avail_{L_i}(t)\), where \(\avail_{L_i}(t) = 1-\prod_{l\in L_i} 
+  (1-\avail_l(t))\).
+This means that Bob minimizes the risk of a layer (\ie all nodes in a layer) 
+being unavailable.

### 2018-07-21 paper/squad-overlay-design.tex
Edits intro to SPORES section

--- 2018-05-01 paper/squad-overlay-design.tex
@@
-\subsection{The \squad Overlay} 
+\subsection{\Acf*{SPORES}}%
+\label{SPORES}
 \label{sec:squad_overlay}
+
+So far, we have treated the case where Alice sends \emph{one} message to Bob in 
+\emph{one} round and any one of Bob's devices receives it.
+Now we will consider a slightly different scenario.
+Consider that the message \(m\) that Alice wants to send to Bob is too large to 
+successfully pass every layer of the route.
+\Eg each device goes offline and back online every \(t\) time units, the 
+bandwidth is \(w\) size units per time unit and the message is \(l\) size 
+units; if \(l\geq t w\), then the message \(m\) can never be delivered as any 
+device will go offline before relaying it to the next node.
+The natural solution is to split \(m\) into \(n\) parts, \(m_0, \dotsc, m_n\), 
+where \(l/n\leq w t\).
+The problem now is that \(m_i\) and \(m_j\) (\(i\neq j\)) might end up on 
+different devices.
+In this section we describe two things:
+first, the protocol run by the devices in Alice's and Bob's device squads to 
+compute the function \(\avail\);
+second, the protocol for reassembling a split message where the parts are 
+received by different devices.
+
+\subsubsection{Computing the availability function}
+
+\dots
+
+\subsubsection{Reassembly across the e-squad}
+
+\dots
+
+\endinput
+
+\commentDaniel{The stuff below is Adrien's old stuff.}
 

### 2018-07-21 paper/file-exchange-design.tex
Moves reassembly to file-transfer section

@@
 
-We will now show how to build a file transferring service on top of 
-\ac{SPORES}.
+So far, we have treated the case where Alice sends \emph{one} message to Bob in 
+\emph{one} round and any one of Bob's devices receives it.
+Now we will consider a slightly different scenario, we will show how to build a 
+file transferring service on top of \ac{SPORES}.
+Consider that the message \(m\) that Alice wants to send to Bob is too large to 
+successfully pass every layer of the route.
+\Eg each device goes offline and back online every \(t\) time units, the 
+bandwidth is \(w\) size units per time unit and the message is \(l\) size 
+units; if \(l\geq t w\), then the message \(m\) can never be delivered as any 
+device will go offline before relaying it to the next node.
+The natural solution is to split \(m\) into \(n\) parts, \(m_0, \dotsc, m_n\), 
+where \(l/n\leq w t\).
+The problem now is that \(m_i\) and \(m_j\) (\(i\neq j\)) might end up on 
+different devices.
+In this section we describe two things:
+first, the protocol run by the devices in Alice's and Bob's device squads to 
+compute the function \(\avail\);
+second, the protocol for reassembling a split message where the parts are 
+received by different devices.

### 2018-07-21 paper/design.tex

@@
 
-Finally, we describe the complete \ac{SPORES} protocol (\cref{SPORES}).
-\Ac{SPORES} adds an e-squad protocol to \ac{SPOR}.
-This protocol provides provides each device in the e-squad of a user with 
-prediction of its own and the other devices' availability.
-This availability can then be used by the devices in the e-squad to participate 
-as nodes for the routing of \ac{SPOR}, \ie making it \iac{P2P} system (network 
-structure).
+A device's availability depends on its user's behaviour, hence the device must 
+predict this behaviour.
+This is best done jointly between the user's all devices.
+In \cref{sec:squad_overlay}, we describe a protocol which allows the devices to 
+compute their own availability prediction function based on the observations by 
+all other devices.
 
-\Ac{SPORES} also allows the e-squad to act as one autonomous system, rather 
-than several.
-In particular, the devices will exchange information so that one device can 
-receive an expected message on the behalf of another device, \eg while it is 
-offline.
+Finally, we describe the complete \ac{SPORES} protocol (\cref{SPORES}), which 
+allows the device squad to act as an autonomous system.
+In particular, we introduce a protocol which allows transferring larger 
+messages by fragmentation and reassembly across the devices in the squad.
 

### 2018-07-21 paper/file-exchange-design.tex
Adapts the design intro to reflect changes in the subsections

@@
-\subsection{Transferring files over \acs{SPORES}}%
+\subsection{\acs{SPORES}: fragmentation and reassembly across devices}%
+\label{SPORES}%
 \label{sec:file_exchange}
@@
 different devices.
-In this section we describe two things:
-first, the protocol run by the devices in Alice's and Bob's device squads to 
-compute the function \(\avail\);
-second, the protocol for reassembling a split message where the parts are 
-received by different devices.
+In this section we describe a protocol for reassembling a split message where 
+the parts are received by different devices of the e-squad.
+
+\commentDaniel{I leave it to Adrien, for now, to write this up.}

### 2018-07-21 paper/sphinxes.tex
Adds comment to figure concerning issue #42
Drops POR as scheme in favour of Sphinxes
Moves \New* statements to preamble to fix weird bug
Clarifies what "algorithm fails" means

@@
 (See \cref{fig:OR-POR}.)
+As such, Sphinxes could be described as a bounded random-walk protocol, \ie the 
+each node selects the next node from a set restricted by the source.
 
@@
     and mixing (top) and \ac{POR} (bottom).
+    %\commentDaniel{This figure should be fixed, issue \#42.}
   }
@@
 excellent description in the original Sphinx paper~\cite{Sphinx}.
-
-\NewVariable{\sk}{x}
-\NewVariable{\pk}{X}
 
@@
 
-\NewAlgorithm{\Enc}{Enc}
-
 We will now extend Sphinx to do \ac{POR}: instead of providing only \(d_{i+1}\) 
@@
 
-\NewScheme{\Sphinxes}{POR}
-\NewAlgorithm{\CreateHeader}{\Sphinxes[CreateHeader]}
-\NewAlgorithm{\CreateFwd}{\Sphinxes[CreateForward]}
-\NewAlgorithm{\CreateReply}{\Sphinxes[CreateReply]}
-\NewAlgorithm{\UseReply}{\Sphinxes[UseReply]}
-\NewAlgorithm{\ProcessHeader}{\Sphinxes[ProcessHeader]}
-
 Sphinxes provides the following algorithms:
@@
 \end{itemize}
-
-\NewVariable{\G}{\mathcal{G}}
-\NewVariable*{\mac}{\mu}
-\NewVariable*{\prg}{\rho}
-\NewVariable*{\prp}{\pi}
-\NewVariable{\hash}{h}
-%\NewVariable{\tag}{\tau}
-\NewVariable{\secret}{s}
-\NewVariable{\blind}{b}
-\NewVariable{\N}{\mathcal{N}}
-\NewVariable{\D}{\mathcal{D}}
-\NewVariable*{\nullnode}{\varepsilon}
-\NewVariable{\rdvnode}{*}
 
@@
 \paragraph*{The \(\CreateHeader\) algorithm}
-
-\NewAlgorithm{\ComputeKeys}{ComputeKeys}
-\NewAlgorithm{\ComputePadding}{ComputePadding}
 
@@
 
-\NewVariable{\ProcessMessage}{ProcessMessage}
-
 The algorithm takes as input a header \((M, \delta)\), where \(M = (\alpha, C, 
@@
 If sending to \(n\) fails, choose another node from \(L'\) uniformly at random.
-If all nodes in \(L'\) fails, the algorithm fails.
+If all nodes in \(L'\) fails, the algorithm drops the packet and silently 
+fails.

### 2018-07-21 paper/squad-overlay-design.tex

--- 2018-05-01 paper/squad-overlay-design.tex
@@
-\subsection{The \squad Overlay} 
+\subsection{Predicting device availability}
 \label{sec:squad_overlay}
 
-At the root of \name is predictive routing, based on the concept of Probabilistic Onion Routes (POR).
-To create PORs, as a device's availability strongly depends on the activity of its owner,
- a user's devices (her \squad) must predict the future behavior of their owner. 
-However, one device, belonging to an \squad, can only predict its probability to stay online in the near future
-if it has a global knowledge of the user behavior over the other devices of the \squad it belongs to.
-To reach this aim, \name relies on a overlay, named thereafter the \squad overlay, to share the user's behavior among devices of its \squad.
+A device's availability depends on its user.
+To predict a device's availability, we must predict its user's behaviour.
+A device, belonging to an \squad, can only predict its probability to stay 
+online in the near future if it has global knowledge of the user behaviour over 
+the other devices of the user's \squad.
+We will now describe a protocol which is run by the devices in the squad which 
+allows each device to compute the availability prediction function, \(\avail\).
+
+\commentDaniel{I leave it to Adrien to write this up.
+  The old stuff is commented out below.}
+
+\endinput
 

### 2018-07-22 paper/file-exchange-design.tex
Minor edits in SPORES section

@@
 bandwidth is \(w\) size units per time unit and the message is \(l\) size 
-units; if \(l\geq t w\), then the message \(m\) can never be delivered as any 
+units; if \(l > t w\), then the message \(m\) can never be delivered as any 
 device will go offline before relaying it to the next node.
 The natural solution is to split \(m\) into \(n\) parts, \(m_0, \dotsc, m_n\), 
-where \(l/n\leq w t\).
+where \(l/n\leq t w\).
 The problem now is that \(m_i\) and \(m_j\) (\(i\neq j\)) might end up on 
 different devices.
-In this section we describe a protocol for reassembling a split message where 
-the parts are received by different devices of the e-squad.
+In this section we describe a file-transfer protocol for splitting a large 
+message, sending the fragments using \ac{SPOR} and reassemble them --- even if 
+the fragments are received by different devices of the squad.
 

### 2018-07-22 paper/file-transfer-design.tex
Renames "file exchange" to "file transfer"
Writes up overview of file transfer

--- 2018-07-22 paper/file-exchange-design.tex
@@
 \label{SPORES}%
-\label{sec:file_exchange}
+\label{sec:file_transfer}
 
@@
 successfully pass every layer of the route.
-\Eg each device goes offline and back online every \(t\) time units, the 
-bandwidth is \(w\) size units per time unit and the message is \(l\) size 
-units; if \(l > t w\), then the message \(m\) can never be delivered as any 
-device will go offline before relaying it to the next node.
-The natural solution is to split \(m\) into \(n\) parts, \(m_0, \dotsc, m_n\), 
-where \(l/n\leq t w\).
+\Eg each device goes offline and back online every \(t\) seconds, the bandwidth 
+is \(w\) bits per second and the message is \(|m|\) bits; if \(|m| > t w\), 
+then the message \(m\) can never be delivered as any device will go offline 
+before relaying it to the next node.
+The natural solution is to split \(m\) into \(n\) parts, \(m_0, \dotsc, 
+  m_{n-1}\), where \(|m|/n\leq t w\).
 The problem now is that \(m_i\) and \(m_j\) (\(i\neq j\)) might end up on 
 different devices.
+The parameters \(t\) and \(w\) must be empirically approximated and used as 
+global configuration parameters for the system.
+We run simulations for various values of \(t\) and \(w\) in 
+\cref{PerformanceAnalysis}.
 In this section we describe a file-transfer protocol for splitting a large 
@@
 
-\commentDaniel{I leave it to Adrien, for now, to write this up.}
+Alice wants to send the message \(m\) to Bob, \(m\) is \(|m|\) bits long.
+She splits \(m\) into \(n\) parts \(m_0, \dotsc, m_{n-1}\).
+Alice gives \(|m|\), \(n\), \(\hash(m)\) and \(\hash(m_0), \dotsc, 
+  \hash(m_{n-1})\) to Bob over an out-of-band channel.
+
+Bob runs \(\CreateReply\) \(n\) times, the node sets passed to \(\CreateReply\) 
+are created as in \cref{SPOR}.
+Bob notes the order of the identifiers, \(I\), of each header and sends the 
+headers in that order to Alice.
+
+Alice receives the headers and keeps the order of the headers.
+For each \(0\leq i < n\), she uses \(\UseReply\) with \(m_i\) as payload to get 
+a header \(\hat M_i\).
+Then she constructs the final header \(M_i\) by running \(\CreateFwd\) with 
+\(\hat M_i\) as payload and the final layer set to \(\{\rdvnode\}\) (to 
+indicate to the last node that it is a rendezvous node).
+She then sends \(M_i\) along the route.
+We note that Alice can process all pieces in parallel as long as she uses the 
+headers she got from Bob in the correct order.
+
+When the headers are used in the correct order Bob can use the identifiers from 
+the headers (\(I\)) to correctly reassemble the fragments despite out-of-order 
+delivery.
+
+\commentDaniel{I leave the remaining details for someone else to write up.
+  What we need is the details of how Bob's devices syncs and reassembles files.
+  Maybe this is reduced to Sprinkler or something.}

### 2018-07-22 paper/spor.tex
Adapts the design intro to reflect changes in the subsections

@@
 one expected to come from Bob.
-(This process is illustrated in \cref{fig:file-exchange}.)
+(This process is illustrated in \cref{fig:file-transfer}.)
 Now we will focus on how Alice and Bob choose the nodes that they provide to 
@@
 \begin{figure}
-  \includegraphics[width=\linewidth]{figures/file_exchange_v2.pdf}
-  \caption{\label{fig:file-exchange}%
+  \includegraphics[width=\linewidth]{figures/file_transfer_v2.pdf}
+  \caption{\label{fig:file-transfer}%
     A schematic of Alice and Bob sending a message using \name.
@@
 But even a solution like Tor's authoritative directory servers would work,
-We will treat \(\avail_d\) in \cref{SPORES}.
+We will treat \(\avail_d\) in \cref{sec:squad_overlay}.
 

### 2018-07-23 paper/security-discussion.tex
Writes up SPOR
Writes up SPOR security

@@
 
+The onion route provides unlinkability between Alice and Bob as long as the 
+message passes at least one honest node on the route.
+This means that any adversary, say Eve,  must ensure that the message passes 
+through an adversarial node on each layer.
+The probability of successful attack is proportional to Eve's size in the 
+network, \ie \(f_A = \frac{|D_A|}{|D|}\).
+\commentDaniel{Check that we still use the \(D_i\) notation for the devices in 
+  \(i\)'s squad.}
+If we assume that \(\GetRandomNode\) returns nodes with close to the uniform 
+distribution, then the \(\nu w_L\) nodes selected will contain \(f_A \nu w_L\) 
+nodes controlled by Eve.
+If \(f_A \nu w_L < \nu\), then Eve cannot be present on every layer of the 
+route.
+Considering how \ac{SPOR} distributed the \(\nu w_L\) selected nodes, Eve's 
+best strategy is to have high-availability nodes --- assume that 
+\(\avail_{D_E}(t) = 1\) for all Eve's devices \(D_E\).
+This way, Eve's devices will be distributed evenly across all layers.
+To succeed, Eve must be chosen in the first layer, the probability of which 
+will be \(\frac{f_A}{w_L}\).
+If one of her devices is chosen in the first layer, then she can choose one of 
+her own devices in the next layer.
+Since she is present on every layer, she can ensure she relays the message all 
+the way to Bob.
+
+However, Eve can only be certain that she has relayed the message from Alice to 
+Bob if \(\nu = r\), \ie she receives the message from Alice, relays it \(r-1\) 
+times and lastly sends it to Bob.
+If \(\nu < r\) though, then, due to the indistinguishability and unlinkability 
+properties of Sphinxes (inherited from Sphinx), Eve cannot know for certain if 
+Alice is the first node and Bob is the last node.
+
+\commentDaniel{This must be updated.}
+\commentDaniel{What is the probability of success of the adversary, assuming 
+  \(\GetRandomNode\) returns nodes with uniform probability?
+  We bias the distribution over the layers by using \(\avail\).}
+
 Alice wants to prevent Bob from learning which are her devices (as defined in 
@@
 choice of the encryption scheme \(\Enc*\), used to encrypt the message \(m\). 
-%(see \cref{sec:file_exchange}).
+%(see \cref{sec:file_transfer}).
 

### 2018-07-23 paper/security-discussion.tex
Finalizes edits of security discussion

@@
 
-\commentDaniel{This must be updated.}
-\commentDaniel{What is the probability of success of the adversary, assuming 
-  \(\GetRandomNode\) returns nodes with uniform probability?
-  We bias the distribution over the layers by using \(\avail\).}
-
-Alice wants to prevent Bob from learning which are her devices (as defined in 
-\cref{system-model}).
-Bob is allowed to infer the behaviour of devices in the global set,
-% Global Device Retinue, 
-but a file transfer from Alice should not give Bob any information about which 
-devices are Alice's.
-
-Bob constructs a Sphinxes route that he gives to Alice.
-Due to the properties that Sphinxes inherits from Sphinx, this means that Alice 
-does not learn any of Bob's destination devices.
-When Alice starts sending the message, she will not connect directly to the 
-device at the head of the route, since that device might be under Bob's 
-control.
-Instead, Alice will construct her own Sphinxes route.
-Thus Alice's devices are hidden from Bob's observation and vice versa.
-This assumes that Alice and Bob can sample their nodes uniformly randomly from 
-the \emph{entire} global set of devices.
-If this is true, the probability of successful attack is proportional to the 
-adversary's size in the network, \ie \(\frac{|D_i|}{|D|}\).
-The adversary must be present on each layer and be selected on the first layer 
-(which is lower-bounded by \(\frac{1}{w_L}\)) --- since after that the 
-adversary can select its own nodes in the next layer instead of uniformly at 
-random.
-
-Alice and Bob also want to prevent Carol and David to learn that Alice sent a 
-message to Bob (as defined in \cref{system-model}).
-Alice and Bob construct their \ac{SPOR} route by including devices from the 
-global set %Global Device Retinue
-, which also includes devices from Carol and David.
-If all devices on the route belong to Carol and David, then they can, of course, 
-learn that Alice sent a message to Bob.
-How well they can do if they do not control the entire route, depends on the 
-choice of the encryption scheme \(\Enc*\), used to encrypt the message \(m\). 
-%(see \cref{sec:file_transfer}).
-
-What makes sense is to choose at least an authenticated encryption 
-scheme~\cite{AuthEncryption}.
-(We could also choose a deniable encryption scheme~\cite{DeniableEncryption}, 
-\eg~\cite{OTPKX} which is authenticated and provides deniability under
-surveillance-state attacks.) %is both deniable and authenticated and  provides \ac{DEN-SS}.)
-This would give confidentiality (or deniability) and integrity for the message, 
-but if the first and the last node belong to Carol and David, they can infer 
-that Alice sent a message to Bob.
-Note that as our in-package header is designed, each node on the route can infer 
-its position on the route \emph{relative to the destination}.
-(We discuss how to remedy this below.)
-None of the nodes can know if the previous node is the originator or not, unless 
-they collude with the previous node.
-The last node, however, can know for sure that the next hop is the destination, 
-but not who it belongs to.
-
-If we choose \(\Enc*\) as a universal re-encryption~\cite{UniversalReencryption} 
-scheme (possibly composed with the deniable, authenticated encryption above), 
-then we could also provide bitwise unlinkability for the message between hops on 
-the route.
-%(We would also need to modify \(\SPOR[\Fwd]\), \cref{SPORFwd}, to perform the 
-%re-encryption of \(m\) before forwarding the message to the next hop.)
-Without universal re-encryption, the message \(m\) itself remains constant 
-throughout the route and thus constitutes a tag for tracking.
-As long as \emph{at least one node on the route is honest}, \ie actually 
-performs the re-encryption --- there is no incentive for them to do this, as 
-neither Alice nor Bob can detect cheating without talking directly to each other 
-to compare the ciphertexts --- then the link between Alice and Bob is broken.
-This means that Carol and David must control all nodes on the route to link 
-Alice's transfer to Bob.
-As above, if we assume uniformly random peer sampling, then Carol and David's 
-success probability is proportional to their joint size in the network.
-
-This means that under the assumption of uniformly random peer sampling, we 
-achieve the properties we outlined in \cref{system-model}.
-Additionally, since Alice and Bob choose a new key for every file, we have 
-forward secrecy between files.
-\Eg an adversary who compromises either Alice or Bob cannot determine what Alice 
-sent to Bob, unless it is an ongoing transfer.
-
 \paragraph*{Limitations}%
@@
 
-Many attacks against anonymous communications systems target the peer sampling 
-mechanism, \eg~\cite{%
-  RouteFingerprinting,%
-  EpistemicAttacksOnRouteSelection,%
-}.
-So, even if our system is secure in theory, it will not be secure in practice 
-unless the random peer sampling algorithm returns peers chosen uniformly 
-randomly from the entire global set. %Global Device Retinue.
-
-To prevent attacks on the random peer sampling, some systems have employed 
-techniques to detect colluding nodes, \eg~\cite{%
-  SecurePeerSampling,%
-  MorphMix,%
-}.
-However, as is the case of~\cite{MorphMix}, these can be 
-broken~\cite{BreakingMorphMix}.
-
-There are also other types of attacks, \eg denial of service attacks that can 
-lead to the adversary learning more from the system~\cite{DenialOfSecurity}.
+A global, passive, network-observing adversary can of course do statistical 
+disclosure attacks to eventually learn who communicates with 
+whom~\cite{StatisticalDisclosureAttacks}.
+There are also denial of service attacks that can lead to the adversary 
+learning more from the system~\cite{DenialOfSecurity}.
 It is difficult to say to what extent our system might be vulnerable to this 
 type of attack without a deeper analysis.
-Unfortunately this is outside the scope of this study.
-However, we hypothesize that our stateless and redundant design might have some 
-advantages, \eg no control messages sent back from where the error happened to 
-the source.
+Such an analysis is out of scope of this analysis, here our focus is to protect 
+Alice and Bob from each other and their friends who also participate as nodes 
+in the network, not to protect them from \eg the \ac{NSA}.
+However, we hypothesize that our stateless and redundant design might yield 
+some advantages, \eg no control messages sent from where the adversary have 
+introduced an error back to the source.
 But these advantages will only postpone the success of the attack, eventually 
 even our protocol must resend.
+\commentDaniel{We should look into this denial of security.}
 
-Finally, we would also need the random peer sampling to be privacy preserving.
+Finally, we must point out that the \(\GetRandomNode\) algorithm must be 
+privacy preserving.
 Consider the following scenario.
@@
 encrypt the header.
+(This follows from the fact that Sphinxes is source-routed.)
 \Ie every node on Alice's route would know that Alice is either the source or 
 the destination.
-When running the protocol, Alice only creates one part of the route and Bob 
-creates the other.
-This means that no device knows both ends of the route unless they collude.
-
-% \subsection{Future Work}
-
-% One part that we can directly improve is the header.
-% We see two alternative paths for improving the header.
-% First, we might be able to adapt the Sphinx~\cite{Sphinx} cryptographic packet 
-% format to the routing of \(\SPOR\).
-% Then we could achieve the properties of Sphinx, \eg preventing the last node to 
-% learn the destination, and enjoy provable security.
-
-% The second approach would be to use the technique by \textcite{PPACinPubFS}.
-% They adapt \(\ANOBE\) in such a way that its ciphertexts decrypt to different 
-% things for different recipients.
-% This way we could have one ciphertext encrypted for all the alternative nodes 
-% --- across layers.
-% Then the ciphertext would decrypt to different plaintexts for nodes on different 
-% layers in the route.
-% This would hide the path length (constant-size ciphertexts by padding) and the 
-% position of individual nodes.
-% This approach would probably be the easiest, but would probably not provide all 
-% the properties from Sphinx (\eg resistance to active tagging attacks).
 
@@
   on different devices, squad devices going offline during transfer}
+\commentDaniel{Reordered chunks is not a problem, we handle that.}
 

### 2018-08-01 code/file_exchange/config.py
removed code

@@ -1,26 +1,0 @@
-#!/usr/bin/env python3
-
-from datetime import timedelta
-
-EXPERIMENT_NAME = 'default'
-default = {
-    'ack_size': 0,  # kB
-    'bandwidth': 128,  # kB/s
-    'chunk_max_size': 512,  # kB, will depend on header size later
-    'do_monitor': True,
-    'experiment_id': 0,
-    'experiment_name': EXPERIMENT_NAME,
-    'gossip_size': 20,
-    'header_size': 100,  # kB, will depend on #devices/layers later
-    'layer_threshold': 0.001,
-    'min_file_size': 51200,  # kB
-    'max_file_size': 51200,  # kB
-    'minimum_node_availability': 0,
-    'n_file_exchanges': 10,
-    'n_layers': 3,  # must be odd
-    'n_rounds': 2,
-    'n_users': 20,
-    'output_dir': 'data/'+EXPERIMENT_NAME+'/',
-    'period': timedelta(seconds=1),  # don't put milliseconds!
-    'ping_time': 0.1,  # s
-}

### 2018-08-01 code/file_exchange/monitor.py

@@ -1,51 +1,0 @@
-#!/usr/bin/env python3
-
-import gevent
-import os
-import sys
-import pandas as pd
-
-
-class Monitor:
-    def __init__(self, columns, save_dir, name, do_monitor):
-        self.do_monitor = do_monitor
-        if save_dir is None:
-            self.do_monitor = False
-        if self.do_monitor:
-            self.df = pd.DataFrame(columns=columns)
-            self.save_path = save_dir + name + ".csv"
-            self.lock = gevent.lock.Semaphore()
-            # Better try saving now
-            self.save()
-
-    def save(self):
-        if self.do_monitor:
-            dir_path = os.path.dirname(self.save_path)
-            if not os.path.isdir(dir_path):
-                os.makedirs(dir_path)
-
-            try:
-                self.lock.acquire()
-                self.df.to_csv(self.save_path, index=False)
-                self.lock.release()
-            except:
-                e = sys.exc_info()[0]
-                raise OSError("Could not save to {}: {}".format(
-                    self.save_path, str(e)))
-            # else:
-            #     print("Successfully saved {}. {} lines.".format(
-            #         self.save_path, self.df.shape[0]))
-
-    def put(self, line):
-        if self.do_monitor:
-            if len(line) != len(self.df.columns):
-                print("Columns:", self.df.columns)
-                print("Line:", line)
-                raise ValueError(
-                    "Come back when you learnt to count:"
-                    " invalid columns number")
-
-            new_row = dict(zip(self.df.columns, line))
-            self.lock.acquire()
-            self.df = self.df.append(new_row, ignore_index=True)
-            self.lock.release()

### 2018-08-01 code/file_exchange/peers_view.py

@@ -1,96 +1,0 @@
-#!/usr/bin/env python3
-
-import pandas as pd
-import time
-from . import config
-from gevent.lock import Semaphore
-
-COLUMNS = ["t", "addr", "type", "p"]
-
-
-class PeersView:
-    def __init__(self, conf=config.default):
-        self._view = pd.DataFrame(columns=COLUMNS)
-        self.conf = conf
-        self.lock = Semaphore()
-
-    def put(self, t, addr, typ, p):
-        self.lock.acquire()
-        # Remove previous entry for addr if any
-        self._view = self._view[self._view['addr'] != addr]
-
-        # Add the new line
-        self._view = self._view.append(
-            pd.DataFrame({
-                't': t,
-                'addr': addr,
-                'type': typ,
-                'p': p
-            }, index=[t])
-        )
-
-        # We prune on reads, not writes
-        # self._prune_view()
-        self.lock.release()
-
-    # Items is a dataframe
-    def insert(self, items):
-        if items is None:
-            return
-
-        self.lock.acquire()
-        self._view = self._view.append(items)
-
-        # We prune on reads, not writes
-        # self._prune_view()
-        self.lock.release()
-
-    def get(self):
-        self.lock.acquire()
-        self._prune_view()
-        ret = self._view.copy()
-        self.lock.release()
-        return ret
-
-    def get_sample(self, n=3, exclude_addr=None):
-        self.lock.acquire()
-        self._prune_view()
-        view = self._view[self._view['addr'] != exclude_addr]
-
-        if n > view.shape[0]:
-            n = view.shape[0]
-        if n == 0:
-            self.lock.release()
-            return None
-
-        # Sample returns a copy of df, not a slice
-        ret = view.sample(n=n)
-        self.lock.release()
-
-        return ret
-
-    def snapshot(self, additional_columns=None):
-        self.lock.acquire()
-        self._prune_view()
-        ret = self._view.copy()
-        self.lock.release()
-
-        if additional_columns is None:
-            return ret
-        elif type(additional_columns) is dict:
-            for k, v in additional_columns.items():
-                ret[k] = v
-            return ret
-        else:
-            raise ValueError(
-                "additional_columns must be a dict of 'colname' -> 'value' "
-                "to add the to the view")
-
-    # Must be called inside lock
-    def _prune_view(self):
-        # Time-bound
-        expiration_limit = \
-            time.perf_counter() - self.conf['period'].total_seconds()
-
[…]

### 2018-08-01 code/routes/device.py

@@ -1,154 +1,0 @@
-#!/usr/bin/env python3
-
-from . import config, peers_view
-from datetime import timedelta, datetime
-import numpy as np
-import pandas as pd
-import random
-import string
-
-ADDR_SIZE = 12
-
-DEFAULT_GOSSIP_SIZE = 10
-DEFAULT_EXPIRATION_PERIOD = timedelta(seconds=1)
-MINIMUM_LAYER_PROBA = 1
-
-
-class Device:
-    def __init__(
-            self, owner, global_view, net, device_id, device_type,
-            conf=config.default):
-
-        self.addr = random_string(ADDR_SIZE)
-        self.conf = conf
-        self.device_id = device_id
-        self.global_view = global_view
-        self.gossip_size = conf['gossip_size']
-        self.is_online = False
-        self.net = net
-        self.owner = owner
-        self.peers_view = peers_view.PeersView(conf)
-        self.type = device_type
-
-        net.add_device(self)
-
-    def act(self, is_online):
-        self.is_online = is_online
-        if self.is_online:
-            self.global_view.put(
-                datetime.now(),
-                self.addr,
-                self.type,
-                self.owner.get_prediction(self.device_id)
-            )
-
-    def rps(self):
-        if self.is_online:
-            self.random_peer_sampling()
-
-    def random_peer_sampling(self):
-        self.peers_view.insert(
-            self.global_view.get_sample(
-                n=self.gossip_size,
-                exclude_addr=self.addr))
-        # if len(self.peers_view.view) == 0:
-        #     print("Device's RPS returned 0 devices! Global peers view has {}.".format(
-        #         len(self.global_view.view)))
-        #     expiration_limit = datetime.now() - self.conf['period']
-        #     print("Expiration time:", expiration_limit)
-        #     print(self.global_view.view)
-
-    def build_random_route(self, nodes_per_layer):
-        n_layers = len(nodes_per_layer)
-        route = [pd.DataFrame() for _ in range(n_layers)]
-        view = self.peers_view.view.copy()
-
-        for l_id in range(n_layers):
-            while len(route[l_id]) < nodes_per_layer[l_id]:
-                if len(view) == 0:
-                    raise Exception("Damn, son")
-                # Pick a device from view without replacement
-                d = view.iloc[np.random.choice(len(view))]
-                route[l_id] = route[l_id].append(d)
-                view.drop(d.name, inplace=True)
-
-        return route
-
[…]

### 2018-08-01 code/routes/experiment.py

@@ -1,214 +1,0 @@
-#!/usr/bin/env python3
-
-# import numpy as np
-from datetime import datetime, timedelta
-from . import config
-from .network import Network
-from .peers_view import PeersView
-from .user import User
-import pandas as pd
-import random
-import threading
-import time
-
-
-def run_experiments_set(N_LAYERS, LAYER_THRESHOLD, N_ROUNDS_SINCE_ROUTE,
-                        N_ROUTES, N_EXPERIMENTS, PERIOD):
-    routes_df = pd.DataFrame()
-    layers_df = pd.DataFrame()
-
-    period = PERIOD
-    total_n_experiments = len(N_LAYERS) * len(LAYER_THRESHOLD)
-
-    t_start = time.perf_counter()
-    total_experiment_id = 1
-    for n_layers in N_LAYERS:
-        for layer_threshold in LAYER_THRESHOLD:
-            experiments = [None] * N_EXPERIMENTS
-            for experiment_id in range(N_EXPERIMENTS):
-                n_users = n_layers * 5
-                conf = {
-                    'gossip_size': 10 * n_layers,
-                    'layer_threshold': layer_threshold,
-                    'minimum_node_availability': 0,
-                    'n_layers': n_layers,  # must be odd
-                    'n_rounds': N_ROUNDS_SINCE_ROUTE + 1,
-                    'n_users': n_layers * 5,
-                    'period': period,
-                }
-
-    #             layers, routes = run_experiment(conf, experiment_id,
-    #                                            N_ROUTES,
-    #                                            N_ROUNDS_SINCE_ROUTE)
-
-                experiments[experiment_id] = Experiment(conf, experiment_id,
-                                                        N_ROUTES,
-                                                        N_ROUNDS_SINCE_ROUTE)
-                experiments[experiment_id].start()
-
-            for experiment in experiments:
-                experiment.join()
-                layers_df = layers_df.append(
-                    experiment.layers_df, ignore_index=True)
-                routes_df = routes_df.append(
-                    experiment.routes_df, ignore_index=True)
-                # not sure about this
-                period = max(period, experiment.period)
-
-            time_spent = timedelta(seconds=time.perf_counter() - t_start)
-            print("[{}] Experiment {}/{} done.".format(
-                time_spent, total_experiment_id, total_n_experiments))
-            total_experiment_id += 1
-
-    return layers_df, routes_df
-
-
[…]

### 2018-08-01 code/routes/user.py

@@ -1,55 +1,0 @@
-#!/usr/bin/env python3
-
-import numpy as np
-from . import model, device, config
-
-
-class User:
-    def __init__(self, global_view, net, conf=config.default):
-        self.model = model.get_random()
-
-        # Create devices
-        self.n_devices = self.model.n_obs
-        self.devices = [None] * self.n_devices
-        self.devices_addr = [None] * self.n_devices
-        for d_id in range(self.n_devices):
-            self.devices[d_id] = device.Device(
-                self, global_view, net, d_id,
-                self.model.devices_type[d_id], conf)
-            self.devices_addr[d_id] = self.devices[d_id].addr
-
-        self.conf = conf
-        self.current_round = None
-
-        self.state_history, self.devices_history = self.model.sample(
-            length=conf['n_rounds'])
-
-    def act(self):
-        if self.current_round is None:
-            self.current_round = 0
-        else:
-            self.current_round += 1
-
-        for d_id, is_online in \
-                enumerate(self.devices_history[self.current_round]):
-            self.devices[d_id].act(is_online)
-
-    def rps(self):
-        for d in self.devices:
-            d.rps()
-
-    def has_online_devices(self):
-        return self.devices_history[self.current_round].sum() != 0
-
-    def get_online_device(self):
-        return self.devices[
-            np.random.choice(
-                np.where(
-                    self.devices_history[self.current_round]
-                )[0]
-            )
-        ]
-
-    def get_prediction(self, device_id):
-        return self.model.predict(
-            1, device_id, self.state_history[self.current_round])[0]

### 2018-08-01 paper/abstract.tex
minor in intro

@@
 %problem/topic
-This paper proposes a novel private file sharing service tat avoids any third-party storage or centralized bootstrapping service.
+This paper proposes a novel private file sharing service that avoids any third-party storage or centralized bootstrapping service.
 %research gap
@@
 %approach
-In this paper, we demonstrate that a fully-decentralized data-sharing solution that is  both efficient and strongly private is possible.
-\commentFT{Trying to highlight POR, as likely to be catch people's attention, and contribute to the paper's long-term interest.} At the core of our proposal lies a novel probabilistic onion routing protocol called POR, which exploits decentralized peer sampling, and a probabilistic model of node availability.
+In this paper, we demonstrate that users do not necessarily have to choose between efficiency and strong-privacy when sharing data with others.
+% that is  both efficient and strongly private is possible.
+\commentFT{Trying to highlight POR, as likely to catch people's attention, and contribute to the paper's long-term interest.} At the core of our proposal lies a novel probabilistic onion routing protocol called POR, which exploits decentralized peer sampling, and a probabilistic model of node availability.
 \commentFT{Sharing node availability information freely could potentially disclose private information.

### 2018-08-01 paper/intro.tex
minor in intro

@@
 % -*- tex-main-file: "contents.tex" compile-command: "pdflatex p2p-private-cloud.tex" ispell-dictionary: "american" -*-
+%!TEX root = p2p-private-cloud.tex
 
@@
 in terms of both data \emph{and} metadata. \commentFT{Moving to 3 ideas, to highlight proxemics in its own right} Our proposal hinges on three
-key ideas: \emph{First}, the emergence of \emph{\squad{}s}, the set of connected devices owned and used by one user, 
+key ideas: \emph{Firstly}, the emergence of \emph{\squad{}s}, the set of connected devices owned and used by one user, 
 %% the recent advances of smartphones and other
@@
 alone, thereby reducing one's exposure to security and privacy threats
-from third parties. \emph{Second}, we consider \emph{proxemics relationships} as a key enabler to initiate file
+from third parties. \emph{Secondly}, we consider \emph{proxemics relationships} as a key enabler to initiate file
 transfers. Physical proximity allow users to share
-routing information out-of-band, e.g. from their
-\squad. \commentFT{I did not get what 'from their \squad' mean.} In contrast to state-of-the-art P2P systems, users agree in \name out-of-band to share a file, but
-do not keep it available for anyone else in the future. \emph{Third}, we
+routing information out-of-band.
+%, e.g. from their \squad. \commentFT{I did not get what 'from their \squad' mean.} 
+In contrast to state-of-the-art P2P systems, users of \name agree out-of-band to share a file, but
+do not keep it available for anyone else in the future. \emph{Thirdly}, we
 exploit distributed machine learning techniques to predict the future
 availability of user devices, and use this ability to implement a
-\emph{probabilistic predictive onion routing} (POR) mechanism. The
+\emph{probabilistic predictive onion routing} mechanism. The
 predictive nature of our routing, exploited in a stateless way, allows us to overcome the inherent fragility of pure P2P data-sharing schemes.
@@
 probabilistic node selection, informed by random peer sampling and
-Hidden Markov Model predictions for node availability. 
+Hidden Markov Model predictions for node availability;
 \item  We have demonstrated the successfulness of our approach. Even
@@
 adversary model and the desired privacy properties of \name. Section~\ref{design}
-introduces the design of our proposed solution. Section~\ref{Performance}
-evaluates the proposed approach. In Section~\ref{security-discussion}, we lead a security discussion
-about advantages, and shortcomings of our approach.
+introduces the design of our proposed solution. In Section~\ref{security-discussion}, we lead a security discussion
+about advantages and shortcomings of our approach. Section~\ref{Performance}
+evaluates \name. 
 Finally, Section~\ref{conclusion} discusses future work and conclusions.

### 2018-08-01 paper/system-model.tex
minor system model

@@
 % -*- tex-main-file: "contents.tex" compile-command: "pdflatex -halt-on-error p2p-private-cloud.tex > /dev/null" ispell-dictionary: "american" -*-
+%!TEX root = p2p-private-cloud.tex
 
@@
 to
-highlight some of the desirable privacy properties of a file sharing service, before mapping them into our \changeFT{fully decentralized (a.k.a P2P)}
+highlight some of the desirable privacy properties of a file sharing service, before mapping them into our \changeFT{fully decentralized (a.k.a. P2P)}
 context. 
@@
 \item Except for the cloud provider, Alice and Bob are the only \changeFT{users} who learn 
-about Alice sharing a file with Bob. \sonja{narrow down to users?} \commentFT{Changed to users: we could also use entities/participants}
+about Alice sharing a file with Bob; \sonja{narrow down to users?} \commentFT{Changed to users: we could also use entities/participants}
 \item
@@
 device-unlinkability from the \ac{P2P} requirements, meaning that
-using \name does not reveal the \squad a device belongs to nor the
-owner and can thus not infer anything about a user's behavior such as
-being online.
+using \name does not reveal the \squad a device belongs to nor its
+owner. \changeAL{Thus, no information on the user's behavior (e.g. being online) can be infered through \name.} 
+%and can thus not infer anything about a user's behavior such as being online.
 
-\paragraph*{Adversary model} To assess our approach, we use the adversary model assumed by by Tor \cite{} and
-Sphinx \cite{}: the adversary has complete control over some part of
-the network as well as some of the nodes. We not consider a passive
+\paragraph*{Adversary model} To assess our approach, we use the adversary model assumed by Tor~\cite{Tor} and
+Sphinx~\cite{Sphinx}: the adversary has complete control over some part of
+the network as well as some of the nodes. We do not consider a passive
 global network adversary, against which it is notoriously difficult to

### 2018-08-01 paper/design.tex
Renames "file exchange" to "file transfer"
have it compile: no comment in caption
minor system model
minor design

@@
+%!TEX root = p2p-private-cloud.tex
+
 \section{Design of the \name file transfer system}%
@@
 their smartphones.
-More precisely, they exchange metadata on \(f\), encryption keys, and exchange 
-use-once reply mix-headers.
-They use these reply headers to transfer the file contents of \(f\) over a 
-network of unreliable nodes while also achieving privacy.
+More precisely, they exchange metadata on \(f\), encryption keys, and 
+\changeAL{routing information that they will use to transfer the file's content over \name's network of unreliable nodes.}
+%use-once reply mix-headers.
+%They use these reply headers to transfer the file contents of \(f\) over a network of unreliable nodes while also achieving privacy.
 
@@
   \caption{\label{fig:outline}%
-    \commentDaniel{We must adapt this figure to the text.}
+    %\commentDaniel{We must adapt this figure to the text.}%
     Outline of \name's components. Users squads of devices are circled in gray. 
@@
   \item[Network structure]
-    This describes the characteristics of the anonymous relays, the connections 
+    describes the characteristics of the \changeAL{network nodes}, the connections 
     between them and the underlying topology.
@@
       \item connection type (direction, synchronization),
-      \item symmetry (node roles, node topology for routing, decentralization).
+      \item symmetry (node roles, node topology for routing, decentralization);
     \end{enumerate*}
@@
   \item[Routing information]
-    This describes the network information available to entities deciding on 
-    the route of an anonymous connection.
+    describes the network information available to entities deciding on 
+    the route of an anonymous file exchange.
     The subcategories are
@@
       \item network view necessary for making routing decisions,
-      \item triggers for routing information updates.
+      \item triggers for routing information updates;
     \end{enumerate*}
@@
   \item[Communication model]
-    This describes the entities that make the routing decisions and how they 
+    describes the entities that make the routing decisions and how they 
     make these decisions.
@@
       \item scheduling (traffic prioritization),
-      \item node selection (determinism, selection set, selection probability).
+      \item node selection (determinism, selection set, selection probability);
     \end{enumerate*}
@@
   \item[Performance]
-    This describes things like latency and communication mode.
+    describes things like latency and communication mode.
     The subcategories are
@@
 This focuses on the node selection, \ie adds node selection on top of Sphinxes.
-The \ac{SPOR} protocol assumes a source of random nodes, \eg through 
-\ac{RPS}~\cite[\eg][]{} or \iac{DHT} based scheme~\cite[\eg][]{}.
+%The \ac{SPOR} protocol assumes a source of random nodes, %\eg through \ac{RPS}~\cite[\eg][]{} or \iac{DHT} based scheme~\cite[\eg][]{}.
+The SPOR protocol assumes that each node knows a random subset of the system's participants at all time (\eg through Random-Peer-Sampling \cite{Jelasity_Voulgaris_Guerraoui_Kermarrec_van_Steen_2007}).
 Each node must be associated with a public key and some availability 
@@
 \include*{squad-overlay-design}
-\include*{file-exchange-design}
+\include*{file-transfer-design}

### 2018-08-01 paper/design.tex
minor and my plan, now attacking my parts on the design

@@
 Next, we describe the \ac{SPOR} protocol (\cref{SPOR}).
+\commentAL{A lot of description here, should only come in Section~\ref{sec:squad_overlay}}
 This focuses on the node selection, \ie adds node selection on top of Sphinxes.
@@
 
-A device's availability depends on its user's behaviour, hence the device must 
-predict this behaviour.
+A device's availability depends on its user's behavior, hence the device must 
+predict this behavior.
 This is best done jointly between the user's all devices.
@@
 \include*{spor}
+\commentAL{What I want to do from here:
+(1) The squad overlay, where a user's devices exchange behavioral information;
+(2) Predicting a device's availability;
+(3) What is at the moment III-B SPOR: global overlay (one-liner: ``we use a RPS service'') and nodes selection per layer etc.;
+(4) File exchange.}
 \include*{squad-overlay-design}

### 2018-08-01 paper/squad-overlay-design.tex
added all I could do easily on the system's design

@@
-\subsection{Predicting device availability}
+%!TEX root = p2p-private-cloud.tex
+
+\subsection{The \squad overlay}
 \label{sec:squad_overlay}
 
-A device's availability depends on its user.
-To predict a device's availability, we must predict its user's behaviour.
-A device, belonging to an \squad, can only predict its probability to stay 
-online in the near future if it has global knowledge of the user behaviour over 
-the other devices of the user's \squad.
-We will now describe a protocol which is run by the devices in the squad which 
-allows each device to compute the availability prediction function, \(\avail\).
+A user's devices communicate through an information dissemination protocol (coined \emph{e-squad overlay}) so as to learn the user's behavior.
+The goal is twofold: 
+devices need information on the user to predict their future availability, 
+and they must know which device is responsible for which file exchange to route messages to their recipient in the \squad.
 
-\commentDaniel{I leave it to Adrien to write this up.
-  The old stuff is commented out below.}
+To achieve this goal, we adapt the Cascade protocol~\cite{luxey:cascade} to suit our needs. 
+Using Cascade, participating nodes gossip in a push-pull manner: 
+when a node has new information, it sends it to a fixed-size random subset of its peers; 
+the recipients answer with any information that they believe the sender does not know about, thus reconciling their history.
 
-\endinput
-
-%By sharing information among themselves, a user's devices (her \emph{squad}) can model her behavior.
-
-%In this section, we only take interest in one user (called Alice) and her \squad.
-
-% Each of Alice's (and Bob's) devices will keep track of its own online and 
-% offline behavior.
-% They will use a protocol like Sprinkler~\cite{luxey:hal-01704172} to learn about 
-% each other's online--offline behavior.
-% \commentDaniel{Is that correct?}
-% This allows Alice's device swarm to infer a behavioral model for the device 
-% swarm and do internal scheduling based on the probability of being online.
-
-\subsubsection{Sharing the user's behavior} % (fold)
-\label{sub:sharing_knowledge}
-
-%Online devices want to know whether they are likely to stay online in the near future.
-taken separately, each device can only get local observations, such as when its user used it, and mobility information if it is a handheld device.
-If all these local observations can be combined, a device can infer a refined model of the user’s behavior to predict its future activity in an accurate manner.
-To build such a sequence of observations,
-%a sequence of the user's behavior that is far more complete.
-%For instance, the probability that Alice uses her home computer and workstation simultaneously is null: these devices are too far apart.
-the \squad overlay leverages on a probabilistic dissemination protocol, \textsc{Sprinkler}~\cite{luxey:hal-01704172}.
-it allows one's devices to inform one another every time the user performs an action.
-In our previous work~\cite{luxey:cascade}, we showed that \textsc{Sprinkler} is resilient to devices churn: 
-devices let each other know of what they have missed while offline.
-We thus employ \textsc{Sprinkler} to disseminate the user's activity to its \squad.
-
-% Each device initially only knows when it is connected, which is not sufficient to make reliable predictions on whether it is likely to stay online.
-% If they knew the other devices' connection and disconnection times, they 
-% To make a model of the user's behavior, they need to know the whole observation sequence $O$: which device is online at each time step.
-% To do so, they employ a probabilistic dissemination protocol, 
-% \textsc{Sprinkler}~\cite{luxey:hal-01704172}.
-% This allows devices to gossip any new connection information to random peers in 
-% the local swarm, ensuring that all devices know the full observation sequence 
-% with a very high probability.
-% \textsc{Sprinkler} has shown resilient to device churn~\cite{luxey:cascade}, and 
-% is thus perfectly suited for our purpose, where a user's devices often 
-% disconnect and reconnect.
-
-% subsection sharing_knowledge (end)
-
-% \subsubsection{Other uses of the Squad Overlay} % (fold)
-% \label{ssub:other_uses_of_the_squad_overlay}
-
-\paragraph*{Other uses of the \squad Overlay} In addition to user's behavior, devices use the \squad overlay for several purposes.
-Firstly, they share files location: when Alice wants to share a file $f$ that resides on her home computer, using her smartphone as the exchange initiator, her smartphone knows where $f$ is located and can create the route accordingly.
-Secondly, each device is also informed of its user's ongoing file transfers (which serves the next purpose).
-Finally, because devices can receive messages on behalf of their fellow squad members to ensure reception despite the proper recipient being offline, 
-one's devices can forward messages among the \squad.
-
-% \david{the following paragraph is not clear at all }
-% \name knows two message types (as will be covered in~\ref{sec:file_exchange}): file chunk, and acknowledgment.
-% Alice typically wants to receive a file on one particular device; respectively, only one of her devices is interested in acknowledging reception of the file chunks it is sending.
-\david{what is the relationship with \squad Overlay?}
-% However, \name allows all \squad members to receive messages destined to Alice.
-% Thus, the third complementary purpose of the \Squad Overlay is to relay messages among the squad: when a message is not destined to the device that received it, the receiver forwards the message to its final destination.
-% \david{and then?}
-
-\subsubsection{Modeling the user's behavior}
-\label{sub:a_model_of_the_user_s_behavior}
-
-we need a probabilistic model of the user's behavior to predict its future activity.
-In \name, the only data we collect and share, through the \squad overlay, are the availability times of each device among a \squad.
-In our model, time is discretized, i.e. users periodically change the state availability of their devices in a predefined period.
-We store the availability times in an ever-increasing \emph{sequence} $O=O_1, ..., O_i, ...$ of actions performed at every \emph{round}, that lasts a short period of time $T$. 
-$d \in O_t$ thus means that the device $d$ was online from time $t$ to time $t+T$.
-Our goal is to predict $O_{t+1}$ knowing $O_t$.
-
-To this end, we model the user's behavior as a Hidden Markov Models (HMMs) of order one, with multiple discrete \emph{observable} processes (one per device) stored in $O$. 
-The hidden process $S=S_1, ..., S_i, ...$ represents the user's locations, constituted of a set of $N$ potential locations (e.g. home, work or outside), $N$ being a user-defined parameter.
-A HMM of order one is such that the hidden variable at time $t$, $S_t$, only depends on the hidden variable at $t-1$, $S_{t-1}$.
-The observations at time $t$, $O_t$, depend on the current hidden variable only, $S_t$.
-
-We first formally define our HMM, then show how to predict the future knowing the HMM, then finally present how to infer the model from the observable sequence only.
-
-% In \name, we take interest in users that own several devices, and wish to privately exchange files with each other without revealing .
-% To the best of our knowledge, no real-world traces of multi-devices usage over several days exist, as would be needed for the experimental evaluation of our system.
-% For that reason, we propose a user behavioral model having the following features:
-
-% \begin{itemize}
-% 	\item Each user owns a variable amount of devices. We consider the following device types: mobile, portable, fixed, and server;
-% 	\item The user travels between three ``locations'' according to a simple probabilistic model: her home, her workplace, and outside;
-% 	\item She makes a different use of her devices depending on her location: at home, she will her laptop that at work; she cannot use her workstation at home.
-% \end{itemize}
-
-% To this end, we use a Hidden Markov Model (HMM) of order one, with multiple discrete observation processes. 
-% The hidden Markovian process $S$ represents the user's locations, while the \emph{observable} process $O=O_1, \dots, \O_T$ represents the connection state of her devices (either connected or disconnected at any point in time).
-
-% Such a statistical model is simplistic (e.g. it does not encapsulate date \& time nor location), but it is on purpose: simplicity is bliss.
-% Given the lack of real-world data for our testbed, building a more complex and realistic user model would add no value to our proposal: 
-% our goal is to see devices exhibiting frequent disconnections and reconnections (also called \emph{churn}).
-% Our simple model being able to put extravagant stress on our system, it is sufficient to access \name's resilience.
-
-\paragraph*{Formal definition}
-
-%We consider a single user, owning a set of $\mathcal{D}$ devices.
-%Time is discretized \commentAL{Discretized/synchronous time needs more explanation}.
-Needs, and the devices' observations are independent: Alice can have her laptop and phone connected at the same time.
-The hidden process $S=S_1,\dots,S_i, \dots$ is built from an alphabet of states $\mathcal{S}$, while the observable process $O=O_1, \dots, \O_i, \dots$ contains elements from the alphabet $\mathcal{O}$.
-We define a multivariate HMM $\lambda_N$ as follows:
-
-$$\text{HMM}:\;\lambda_N=(\Pi, A, B)$$
-
-where 
+The exchanged data forms a sequence, ordered by timestamp, populated by three types of information:
 \begin{itemize}
-	\item $N$ is the number of states in the system:
-	$N = \left| \mathcal{S} \right|$;
-
-	\item $\Pi=\left\{ \pi_i\right\}_{i\in\mathcal{S}}$ is the initial state distribution:\\
-	$\pi_i=P[S_1=i]$;
-
-	\item $A = \left\{ a_{i\,j}\right\}_{(i,j)\in\mathcal{S}^2}$ is the state transition matrix:\\
-	$a_{i\,j}=P[S_t=j \mid S_{t-1}=i]$;
-
-	\item $B = \left\{ b_{i\,k}\right\}_{(i,k)\in\mathcal{S}\times\mathcal{D}}$ is the matrix of event emission probabilities for each state:
-	$b_{i\,k} = P[ k \in O_t \mid S_t = i]$.
+	\item \texttt{CONNECTED<$d, t_{step}$>}: Sent by device $d$ when it is used by its user at time step\footnote{As far as devices connections are concerned, time is discretized: we consider that each interaction lasts the same time.} $t_{step}$.
+$d$ is otherwise considered offline at this time.
+Devices use this information to predict their probability of remaining online, as presented in section~\ref{ssec:device_availability};
+	\item \texttt{SENDING<$d, ID_{file}$>}: When the user decides to send a file located on a device $d$, $d$ informs its peers of this fact, and joins the file ID $ID_{file}$.
+Squad members will use this information to forward acknowledgments from the remote to $d$;
+	\item \texttt{RECEIVING<$d, ID_{file}$>}: Reciprocally, when the user starts receiving a file onto a device $d$, $d$ informs its peers of this fact, and joins the file ID $ID_{file}$.
+Squad members will use this information to forward the file's content from the remote to $d$.
 \end{itemize}
 
-In our case, the states $\mathcal{S}$ are the different locations $\mathcal{L}$ where the user is susceptible to go.
-The events represent the devices availability, hence $\mathcal{O} = \mathcal{D}$, where $\mathcal{D}$ is the set of the user's devices.
-Several devices can be available at the same time, such that $O_t$ is a set, and $d \in O_t$ means that device $d$ was available at time $t$. Devices' availability probabilities are independent.
+Given this information dissemination and history reconciliation mechanism, each \squad member knows the full sequence $S$ at all time with an overwhelming probability, even in the face of churn.
 
-% In \cref{fig:hmm}, we show an example HMM of a user's behavioral HMM, along with its graphical representation (the initial state distribution $\Pi$ was left out for simplicity). 
-% The represented user possesses a phone and a laptop, that she carries around with her, a home computer, that is only accessible from her home, and a workstation, located at her workplace.
-She never forgets to turn off her fixed appliances before leaving.
+\subsection{Predicting a device's availability}
+\label{ssec:device_availability}
 
-% Figure~\ref{fig:sample_usage}, shows a possible trace of the user's behavior, using the parameters depicted in figure~\ref{fig:hmm}. 
-% It reads the timeline of $o_{d}$ for each device $d$. On the bottom of the graph, the first letter of the user's location is shown at each time step.
-% We see that devices connections depend on the user's location, and that any number of devices can be connected at the same time.
+The predictive nature of \name lies in the fact that each participating device publicly advertises its probability of being connected in the near future. 
+This information is used when any node needs to create a Probabilistic Onion Route (POR), as will be shown in the next subsection~\ref{ssec:por}.
 
-\paragraph*{Predicting future behavior} 
-\label{para:predicting future behavior}
-As already stated, devices want to predict whether they are likely to be available in the near future.
-This information will be publicly available to enable the intelligent building of routes.
+As described earlier, \squad members know the connection times of all the user's devices, given by the \texttt{CONNECTED} items in the \squad's sequence.
+It can be represented as a 2D sparse matrix of booleans, as shown in the Table~\ref{tab:connection_times} (depicting a user owning a laptop, a phone, and a smart-TV).
 
-Because devices availability only depend on the users location, we can predict the devices availability in $i$ round $O_{t+i}$ given only the model $\lambda_N$ and the current user's location $S_t$.
-We first compute the probability that a device $d$ will be available next turn:
+\begin{table}
+\caption{Matrix representation of an \squad availability over time}
+\centering
+\begin{tabular}{@{}lccccc@{}} \toprule
+		& $\cdots$	& $t_{i-1}$	& $t_i$		& $t_{i+1}$	& $\cdots$ \\ \midrule
+Laptop	& $\cdots$	& 1			& 0			& 0			& $\cdots$ \\
+Phone	& $\cdots$	& 1			& 1			& 1			& $\cdots$ \\
+TV		& $\cdots$	& 0			& 1			& 1			& $\cdots$ \\ \bottomrule
+\end{tabular}
+\label{tab:connection_times}
+\end{table}
 
-$$
-P\left[ d \in O_{t} \mid S_{t-1} = s \right] = 
-\sum\limits_{s' \in \mathcal{S}} 
-a_{s\,s'} * b_{s'\,d}.
-$$
+To predict a device's future availability, we build a Markov representation of the user's activity, 
+where the state $X_i$ represents the availability of the user's devices at time $t_i$.
+The state space $\mathcal{X}$ is the set of possible combinations of the devices' connection.
 
-It is the sum of the probabilities, for each state $s$, that the user switches to $s$ and uses her device.
-Recursively, predicting $i$ turns in advance follows the same logic:
+Given the \squad sequence of connections $S = X_1, \dots, X_i, X_{i+1}, \dots$,
+we can compute the probability of transition from a state $x_1$ to $x_2$ by counting the number of times $x_2$ is seen right after $x_1$ in $S$:
 
-\begin{multline*}
-P\left[ d \in O_{t+i} \mid S_{t} = s \right] = \\
-\sum\limits_{s' \in \mathcal{S}}
-P\left[ S_{t+1} = s' \mid S_t = s \right] * 
-P\left[ d \in O_{t+i} \mid S_{t+1} = s'\right].
-\end{multline*}
+$$P\left[x_1 \rightarrow x_2\right] = \frac{\left| \left\{ X_i = x_1, X_{i+1} = x_2 \right\}_{i \in \left[0, |S| - 1\right]} \right|}{|S| - 1} $$
 
-We show in section~\ref{sub:predictive_onion_routes_creation} that the prediction of devices' availability at $t+1$ is a good enough estimator of their availability state at $t+i$.
-For that reason, devices only compute and publish $P\left[ d \in O_{t+1} \mid S_{t} = s \right]$.
+Each device knows the current state $X=x$ of the Markov chain.
+To predict its probability $P_d$ of remaining online in the next round, 
+a device $d$ simply adds the probabilities that the user switches to a state where $d$ is online next.
+Consider $\mathcal{X}_{d\text{ online}} \subset \mathcal{X}$ the set of states where $d$ is online. Then:
 
-\paragraph*{Inferring the model from the sequence of observations}
+$$ P_d = P\left[d\text{ online next turn} \mid X=x\right] = \sum\limits_{x' \in \mathcal{X}_{d\text{ online}}} P\left[ x \rightarrow x'\right]$$
 
-Given an initial estimate $\lambda_{N}^{(0)}$ of the model, and the sequence of observations $O$, the Baum-Welch algorithm uses Expectation-Maximization to iteratively compute the most likely $S^{(i)}$ and $\lambda_{N}^{(i)}$ until the probability of the observations using the estimated model falls below a predefined threshold: $P[O; \lambda_{N}^{(i)}] < \epsilon$.
-Devices use this algorithm to infer their user's behavioral model from the observations.
+There is a caveat, though.
+While the user acts, $S$ keeps growing, and the Markov chain must be recomputed: their is a probability that the current state $X$ has never been seen before.
+In this case, $\forall X' \in S, P\left[X \rightarrow X'\right] = 0 \implies P_d = 0$.
 
-It needs an initial model, though, with a predefined number of states $N$. 
-$N$ is given by the user, and we set $\lambda_{N}^{(0)}$ to be a uniform model: probabilities of switching to each location are uniform, and all devices have a probability of being online of 0.5.
+To counter this possibility, we propose a fallback:
+when the current state $X=x$ is new, we compute a naive probability $Pf_d$ that $d$ stays online, given only $d$'s previous state:
 
-Baum-Welch usually requires a lot of data to fit the model $\lambda_N$ that generated $O$.
-Indeed, $P[O; \lambda_{N}^{(i)}] < \epsilon$ does not mean that $\lambda_N \simeq \lambda_N^{(i)}$.
-In our case, we do not care as long as the predictions using the estimated model, $P[O_{t+1} \mid S_t; \lambda_N^{(i)}]$, are close to the ground-truth, $P[O_{t+1} \mid S_t; \lambda_N]$.
-%This will be evaluated in section~\ref{sub:devices_predictions_of_the_user_behavior}.
+$$ Pf_d = \frac{\left| \left\{ X_i \in \mathcal{X}_{d\text{ online}}, X_{i+1} \in \mathcal{X}_{d\text{ online}} \right\}_{i \in \left[0, |S| - 1\right]} \right|}{\left| \left\{ X_i \in \mathcal{X}_{d\text{ online}} \right\}_{i \in \left[0, |S| - 1\right]} \right|} $$
+
+$Pf_d$ is an estimator of $d$'s average probability of being online two turns in a row. It will also be used as a baseline in the evaluation.
+
+\subsection{Probabilistic Onion Routes}
+\label{ssec:por}
+
+\commentAL{We need to merge \ref{SPOR} and this section.}
+
+\subsubsection{The global overlay}
+\label{sssec:global_overlay}
+
+Devices need to know the address of SPORES participants in order to craft PORs.
+To this end, we employ a Random Peer Sampling service~\cite{Jelasity_Voulgaris_Guerraoui_Kermarrec_van_Steen_2007} among all nodes in SPORES.
+\commentAL{TODO: cite \cite{Jesi_Montresor_van_Steen_2010} or else for \textbf{secure} RPS}.
+It is a gossip protocol that allows each participant to keep a fixed-size \emph{random} subset of other nodes' descriptor (that we will call the \emph{view}). 
+The view is constantly evolving, as queries are periodically issued between nodes to exchange descriptors between their respective views.
+Finally, offline nodes are quickly evicted from devices' views.
+
+The randomness of the views must be guaranteed: 
+a node that would be present in views too often would become a bottleneck, and could monitor a bigger portion of the network.
+It will be evaluated in section~\commentAL{TODO}.
+
+In SPORES, a descriptor for $d$ contains the following information:
+\begin{itemize}
+  \item \(d\) is the node's identifier (address);
+  \item \(\pk_d\) is the node's public key;
+  \item \(P_d\) is the node's probability of remaining online at the time of the descriptor's creation.
+\end{itemize}
+
+\subsubsection{Routes creation}
+\label{sssec:routes_creation}
+
+\subsection{SPORES: file exchange through probabilistic onion routes}
+\label{ssec:spores_file_exchange_through_probabilistic_onion_routes}

### 2018-08-01 paper/squad-overlay-design.tex
minor

@@
 To counter this possibility, we propose a fallback:
-when the current state $X=x$ is new, we compute a naive probability $Pf_d$ that $d$ stays online, given only $d$'s previous state:
+when the current state $X=x$ is new, we compute a naive probability $P'_d$ that $d$ stays online, given only $d$'s previous state:
 
-$$ Pf_d = \frac{\left| \left\{ X_i \in \mathcal{X}_{d\text{ online}}, X_{i+1} \in \mathcal{X}_{d\text{ online}} \right\}_{i \in \left[0, |S| - 1\right]} \right|}{\left| \left\{ X_i \in \mathcal{X}_{d\text{ online}} \right\}_{i \in \left[0, |S| - 1\right]} \right|} $$
+$$ P'_d = \frac{\left| \left\{ X_i \in \mathcal{X}_{d\text{ online}}, X_{i+1} \in \mathcal{X}_{d\text{ online}} \right\}_{i \in \left[0, |S| - 1\right]} \right|}{\left| \left\{ X_i \in \mathcal{X}_{d\text{ online}} \right\}_{i \in \left[0, |S| - 1\right]} \right|} $$
 
-$Pf_d$ is an estimator of $d$'s average probability of being online two turns in a row. It will also be used as a baseline in the evaluation.
+$P'd$ will be advertised in spite of $P_d$. It will also be used as a baseline in the evaluation.
 

### 2018-08-05 paper/squad-overlay-design.tex
corrections in statistics

@@
 Given the \squad sequence of connections $S = X_1, \dots, X_i, X_{i+1}, \dots$,
-we can compute the probability of transition from a state $x_1$ to $x_2$ by counting the number of times $x_2$ is seen right after $x_1$ in $S$:
+we can compute the probability of transition from a state $X_i=x$ to $X_{i+1}=x'$ by counting\footnote{%
+	Because we work with low-probability events observed with a small amount of data, there is a possibility that an event never occurs in $S$. 
+	To counter that, we apply additive smoothing while computing probabilities. 
+	We left this engineering optimization out of the demonstration for clarity.
+} the number of times $x'$ is seen right after $x$ in $S$:
 
-$$P\left[x_1 \rightarrow x_2\right] = \frac{\left| \left\{ X_i = x_1, X_{i+1} = x_2 \right\}_{i \in \left[0, |S| - 1\right]} \right|}{|S| - 1} $$
+\begin{align*}
+P\left[X_{i+1}=x' \mid X_i=x \right] &= P\left[x \rightarrow x' \right] \\&= \frac{\left| \left\{ X_i = x, X_{i+1} = x' \right\}_{i \in \left[0, |S| - 1\right]} \right|}{\left| \left\{ X_i = x \right\}_{i \in \left[0, |S| - 1\right]} \right|}
+\end{align*}
 
-Each device knows the current state $X=x$ of the Markov chain.
+Each device knows the current state $X_i=x$ of the Markov chain.
 To predict its probability $P_d$ of remaining online in the next round, 
@@
 
-$$ P_d = P\left[d\text{ online next turn} \mid X=x\right] = \sum\limits_{x' \in \mathcal{X}_{d\text{ online}}} P\left[ x \rightarrow x'\right]$$
+\begin{align*}
+P_d & = P\left[d\text{ online at }X_{i+1} \mid X_i=x\right] \\ & = \sum\limits_{x' \in \mathcal{X}_{d\text{ online}}} P\left[ X_{i+1}=x' \mid X_i=x \right]
+\end{align*}
 
 There is a caveat, though.
-While the user acts, $S$ keeps growing, and the Markov chain must be recomputed: their is a probability that the current state $X$ has never been seen before.
-In this case, $\forall X' \in S, P\left[X \rightarrow X'\right] = 0 \implies P_d = 0$.
+While the user acts, $S$ keeps growing, and the Markov chain must be recomputed: there is a probability that the current state $X=x$ has never been seen before.
+In this case, $\forall x' \in \mathcal{X}, P\left[x \rightarrow x'\right]$ is undefined.
 
 To counter this possibility, we propose a fallback:
-when the current state $X=x$ is new, we compute a naive probability $P'_d$ that $d$ stays online, given only $d$'s previous state:
+when the current state is new, we compute a $P'_d$, an estimator of $d$'s average probability of staying online two turns in a row:
 

### 2018-08-05 paper/design.tex
added all I could do easily on the system's design

@@
   section instead of a subsection in the design section.}
-\sonja{remove/update references to building blocks, POR}
-\commentDaniel{I removed the building blocks subsection entirely.}
 
@@
 More precisely, they exchange metadata on \(f\), encryption keys, and 
-\changeAL{routing information that they will use to transfer the file's content over \name's network of unreliable nodes.}
+\changeAL{routing information that they will use to transfer the
+  file's content over \name's network of unreliable nodes.}
+\sonja{here comes more of a solution overview and reference to the outline
+  figure.}
+
+Figure \cref{fig:outline} shows the components needed to obtain this
+routing information.  
 %use-once reply mix-headers.
@@
     %\commentDaniel{We must adapt this figure to the text.}%
-    Outline of \name's components. Users squads of devices are circled in gray. 
+    Outline of \name's components. Users' squads of devices are circled in gray. 
     From top to bottom: a user's devices collaborate through the Squad Overlay 
     (\cref{sec:squad_overlay}); online devices globally share information about 
-    them to random peers (\cref{sec:SPOR}); using the two above 
-    overlays allows for the creation of \ac{SPOR} between sets of devices. 
-    These protocols enables secure file transfer between users 
-    (\cref{SPORES}).}
+    them with random peers (\cref{sec:SPOR}); using the two 
+    overlays above allows for the creation of routes (\ac{SPOR}) between sets of devices. 
+    These protocols enable secure file transfer between users 
+    (\cref{sec:sphinxes}).}
 \end{figure}
 
-This section presents the different parts of the system in detail.
+After the initial, out-of-band setup, file transfer happens along
+onion routes but with the following \name modifications:
+
+\sonja{might need different naming, and deciding about predictive and probabilistic}
+\begin{description}
+\item [Stateless.] There is no mandatory circuit creation, the file transfer can be
+  done in a stateless way. 
+\item [Predictive.] The choice of nodes included in the onion routing
+  layers is based on a predictive model for availability, disseminated
+  according to Figure~\cref{fig:outline}, and queried by random peer sampling.
+\item [Probabilistic.] Instead of source routes with one node per onion layer, each
+  layer consists of a set of nodes and although the source route still
+  determines the sequence of layers, the actual node used for the next
+  hop of forwarding is selected from the set in an ad-hoc way.
+\end{description}
+
+This rest of this section presents the different parts of the system in detail.
 We align the presentation of the system with the taxonomy of 
 \textcite{RoutingSurveyAnonymousProtocols}.
-They categorize anonymous communication protocols using the following 
+They classify anonymous communication protocols using the following 
 categories (see~\cite[Table 1]{RoutingSurveyAnonymousProtocols}):
@@
 \include*{squad-overlay-design}
-\include*{file-transfer-design}
+%\include*{file-transfer-design}

### 2018-08-05 paper/spor.tex
minor design
minor and my plan, now attacking my parts on the design
explaining file exchange

@@
+%!TEX root = p2p-private-cloud.tex
+
 \NewScheme{\SPOR}{SPOR}
@@
 
+\commentAL{I would like to merge that with \ref{ssec:por}.}
+
 Say that Alice wants to send a message \(m\) to Bob.
@@
 over an out-of-band channel.
-We assume that \(m\) is either unavailable when the channel is used or too 
-large to successfully send over the channel directly.
+%We assume that \(m\) is either unavailable when the channel is used or too large to be successfully sent over the channel directly.
 At a later point, Alice attaches a message \(m\) to the reply header using 
 \(\UseReply\), creates a forward header using \(\CreateFwd\) with the prepared 
-reply header as payload.
-Then she sends this packet to the first node, which processes it using 
+reply header as parameter.
+\commentAL{Unclear: she sends? Then it reaches Alice?} Then she sends this packet to the first node, which processes it using 
 \(\ProcessHeader\).

### 2018-08-05 paper/squad-overlay-design.tex
explaining file exchange

@@
 \label{ssec:spores_file_exchange_through_probabilistic_onion_routes}
+
+\newcommand\finfo{\ensuremath{\mathcal{I}_f}}
+\newcommand\filesize{\ensuremath{s_f}\xspace}
+\newcommand\chunksize{\ensuremath{s_{\text{chunk}}}\xspace}
+\newcommand\nchunks{\ensuremath{n_{\text{chunks}}}\xspace}
+\newcommand\hashchunk{\ensuremath{\mathcal{H}_{\text{chunk}}}\xspace}
+\newcommand\hashfile{\ensuremath{\mathcal{H}}\xspace}
+
+We have seen how participants of \name could craft routes to secretly exchange messages.
+We now apply this feature to reliably exchange files between two users.
+
+Our file transfer protocol is loosely based on BitTorrent \cite{bt_bep3}: 
+at initialization, a file $f$ of size \filesize is first cut into chunks of constant size \chunksize by its uploader,
+resulting in $\nchunks = \lceil \filesize / \chunksize \rceil$ chunks.
+A SHA1 hash \hashchunk is computed for each chunk, plus another SHA1 hash \hashfile of the chunks hashes ; that will serve error detection.
+
+In BitTorrent, .torrent files are publicly available on the Web.
+They contain $\finfo = \left(\filesize, \nchunks, \left[\hashchunk\right]_{\text{chunk} \in f}, \hashfile\right)$, 
+along with network information to reach uploaders of $f$ (e.g. the tracker's address).
+Anyone can download a .torrent file and start receiving the file associated to it.
+In \name, we want file exchanges to remain private: these metadata are exchanged out-of-band.
+
+\paragraph{Out-of-band initialization} 
+When Alice wishes to send a file to Bob, she

### 2018-08-05 paper/squad-overlay-design.tex
finished describing file transfer

@@
 %!TEX root = p2p-private-cloud.tex
+
+\newcommand\fileid{\ensuremath{ID_{\text{f}}}}
+\newcommand\sendingdevice{\ensuremath{d^{(s)}_f}}
+\newcommand\recdevice{\ensuremath{d^{(r)}_f}}
 
@@
 Devices use this information to predict their probability of remaining online, as presented in section~\ref{ssec:device_availability};
-	\item \texttt{SENDING<$d, ID_{file}$>}: When the user decides to send a file located on a device $d$, $d$ informs its peers of this fact, and joins the file ID $ID_{file}$.
-Squad members will use this information to forward acknowledgments from the remote to $d$;
-	\item \texttt{RECEIVING<$d, ID_{file}$>}: Reciprocally, when the user starts receiving a file onto a device $d$, $d$ informs its peers of this fact, and joins the file ID $ID_{file}$.
-Squad members will use this information to forward the file's content from the remote to $d$.
+	\item \texttt{SENDING<\sendingdevice, \fileid>}: When the user decides to send a file $f$ located on a device \sendingdevice, \sendingdevice informs its peers of this fact, and joins the file ID \fileid.
+Squad members will use this information to forward acknowledgments from the remote to \sendingdevice;
+	\item \texttt{RECEIVING<\recdevice, \fileid>}: Reciprocally, when the user starts receiving a file $f$ onto a device \recdevice, \recdevice informs its peers of this fact, and joins the file ID \fileid.
+Squad members will use this information to forward the file's content from the remote to \recdevice.
 \end{itemize}
@@
 To this end, we employ a Random Peer Sampling service~\cite{Jelasity_Voulgaris_Guerraoui_Kermarrec_van_Steen_2007} among all nodes in SPORES.
-\commentAL{TODO: cite \cite{Jesi_Montresor_van_Steen_2010} or else for \textbf{secure} RPS}.
+\commentAL{TODO: cite \cite{Jesi_Montresor_van_Steen_2010} for \textbf{secure} RPS}.
 It is a gossip protocol that allows each participant to keep a fixed-size \emph{random} subset of other nodes' descriptor (that we will call the \emph{view}). 
@@
 \newcommand\nchunks{\ensuremath{n_{\text{chunks}}}\xspace}
-\newcommand\hashchunk{\ensuremath{\mathcal{H}_{\text{chunk}}}\xspace}
-\newcommand\hashfile{\ensuremath{\mathcal{H}}\xspace}
+\newcommand\hashchunk{\ensuremath{h_{\text{chunk}}}\xspace}
+\newcommand\hashfile{\ensuremath{h}\xspace}
 
@@
 Anyone can download a .torrent file and start receiving the file associated to it.
+
 In \name, we want file exchanges to remain private: these metadata are exchanged out-of-band.
+In addition, in \name, each file is associated with a random ID \fileid, that is part of \finfo.
 
-\paragraph{Out-of-band initialization} 
-When Alice wishes to send a file to Bob, she
+\paragraph*{Out-of-band initialization} 
+When Alice wishes to send a file $f$ to Bob, she compute \finfo, 
+plus one reply header per chunk, and sends the whole to Bob.
+Still out-of-band, Bob replies with one forward header per chunk.
+
+Alice and Bob now have everything they need to start transferring $f$ in-band.
+
+\newcommand\bitfield{\ensuremath{bf_f}}
+\paragraph*{Chunks and bitfields}
+Alice's file $f$ is located on one of her devices, \sendingdevice. 
+Each chunk $c_i \in f$ is uploaded to Bob through a unique route $\mathcal{H}_{c_i}$.
+When $d_f$ is online, it periodically sends chunks of $f$ to Bob until $f$ is entirely uploaded.
+
+Bob receives $f$ on a device \recdevice. 
+When one of his devices receives a chunk $c_i$ for $f$, it fetches the proper recipient \recdevice by looking into the \squad overlay sequence
+for the line \texttt{RECEIVING<\sendingdevice, \fileid>} and forwards the file chunk to \recdevice.
+Upon reception of the chunk, \recdevice verifies its integrity by computing its SHA1 hash $h_{c_i}$ and comparing it to $\finfo.h_{c_i}$.
+If the chunk is valid, \recdevice updates its \emph{bitfield} \bitfield: this bit-array of size \nchunks is initialized with 0;
+every time Bob successfully receives a chunk $c_i$, \recdevice sets the bit $\bitfield[i]$.
+To acknowledge the chunk's reception, \recdevice sends \bitfield back to Alice, through a unique route $\mathcal{H}'_{c_i}$.
+
+Reciprocally, acknowledgments can arrive to Alice on any on her devices, while only \sendingdevice can process it.
+When one of Alice's devices receive Bob's bitfield \bitfield, 
+it forwards \bitfield to \sendingdevice by looking for the line \texttt{RECEIVING<\sendingdevice, \fileid>} in the \squad overlay's sequence.
+Upon reception of a bitfield \bitfield, \recdevice updates its knowledge of Bob's unreceived chunks of $f$,
+and sends a chunk to Bob among the ones that were not already acknowledged by Bob.
+
+\commentAL{This is a shitty scheduler. Should I mention it? Rephrase? You have a citation to propose instead?}
+Messages in \name might arrive in a wrong order or fail. 
+It is not unlikely that the file exchange stops before its transfer is done.
+As a solution, \sendingdevice will restart periodically sending all chunks that were not acknowledged by Bob if the transfer hangs.
+This solution ensures liveness by increasing network traffic (some chunks might be received several times), as will be seen in the evaluation.
+It nevertheless allows reliable file transfer among a network of poorly connected nodes in a private manner.

### 2018-08-05 paper/evaluation.tex
rewrote beginning of eval

@@
+%!TEX root = p2p-private-cloud.tex
+
 \section{Performance evaluation}%
@@
 
-In the following, we present the evaluation results of \name. 
-We first give precisions on the evaluation testbed and parameters in section~\ref{sub:evaluation_testbed}, before evaluating the PORs creation  in section~\ref{sub:predictive_onion_routes_creation}, to conclude with an overall evaluation of the file transfer performance in section~\ref{sub:file_transfer}.
+To evaluate our protocol, we built a prototype of \name that implements all the features previously described but the encryption processes (Sphinxes).
+It consists of 5400 lines of Go code.
+The users and their behavior (i.e. devices usage and file exchange decisions), on their part, are simulated. 
+Each device is a Docker container that ships the same \name code, and communicates with its peers via TCP connections.
+To allow for realistic simulations (embodying more than 10 users), we distribute the experiments over 5 machines (one with an Intel Xeon E5-2660 CPU (32 cores) and 128GB of RAM, and four having an Intel Xeon E5420 CPU (8 cores) and 32GB of RAM), such that each \squad always resides on the same machine.
+All peers are connected to the same Docker overlay network, and are thus reachable from any other device.
+
+In the following, we first give precisions on the evaluation testbed and parameters in section~\ref{sub:evaluation_testbed}, before evaluating the PORs creation in section~\ref{sub:predictive_onion_routes_creation}, to conclude with an overall evaluation of the file transfer performance in section~\ref{sub:file_transfer}.
 
@@
 
+\newcommand\tuser{\ensuremath{t_{\text{user}}}}
+\newcommand\ndevices{\ensuremath{n_{\text{devices}}}}
+
 To evaluate \name, we take interest in users owning a variable amount of devices of different types, and frequently switching among them.
 To the best of our knowledge, there exists no real-world dataset of the devices connection times of such a user.
-We have thus implemented an evaluation testbed where each user's behavior is simulated  according to the following properties:
+On our testbed, each user's behavior is therefore simulated, according to the following rules:
 \begin{itemize}
@@
 tablet, phone), portable (laptop), fixed (workstation, home computer) and server (such as a NAS, Raspberry Pi or rented appliance);
-	\item She can travel between different locations, say her home, her workplace and and outside;
-	\item She makes a different use of her devices depending on her location: her home computer will only be accessed at home, while her phone can be accessed everywhere (though she tends to use it the most at home, for instance).
+  \item The user always owns a phone;
+	\item The user can travel between different locations;
+	\item The user makes a different use of her devices depending on her location and device type: 
+  her home computer will only be accessed at home, while her phone can be accessed everywhere (though she might tend to use it at home more than at work);
+  \item The user's action are discretized: every action lasts the same amount of time \tuser.
 \end{itemize}
 
-We thus model each user with a Hidden Markov Model, as presented in section~\ref{sub:a_model_of_the_user_s_behavior}.
-We keep the different possible locations $\mathcal{L}$ to $N=3$ and the state transition matrix $A$ to a fixed value (cf figure~\ref{fig:hmm}).
-The number and types of devices per user, along with the matrix of emission probabilities $B$, is determined randomly according to the following rules.
+Towards this goal, we model each user as a discrete time Hidden Markov Model (HMM) of order one. 
+The hidden process $S=S_1, \dots, S_i, \dots$ represents the user's movements from one location from another, 
+taken from the set of possible locations $\mathcal{S}$.
+In our case, there are several independent observation processes (one per device), 
+that form the observation sequence $O= O_1, \dots, O_i, \dots$.
+$O_i[j]=1$ (resp. 0) means that the user's device $d_j$ was online (resp. offline) at time step $t_i$.
 
-A user always has a phone, plus a random number of 2 to 9 devices whose type is decided by a weighted random choice: each device has 30\% chances of being either mobile, portable, or fixed, and only 10\% probability of being a server.
-$B_{*, d}$, the probability that device $d$ is used in each location, depends on $d$'s device type: 
+A HMM of order one is such that the current state $S_i$ (at time $t_i$) only depends on the previous one $S_{i-1}$ (at time $t_{i-1}$).
+The observation at time $t_i$ ($O_i$) only depends on the current state $S_i$.
+
+%locations, constituted of a set of $N$ potential locations (e.g. home, work or outside), $N$ being a user-defined parameter.
+
+%We thus model each user with a Hidden Markov Model, as presented in section~\ref{sub:a_model_of_the_user_s_behavior}.
+In detail, we applied the following rules to our models: 
 \begin{itemize}
-	\item for each location, every mobile device $d_m$ has a random but high probability of being online: $\forall l \in \mathcal{L}, B_{l, d_m} \in [0.6, 1]$;
-	\item a portable device $d_p$ has a much lower probability of being used: $\forall l \in \mathcal{L}, B_{l, d_p} \in [0.2, 0.8]$; 
-	\item a fixed appliance $d_f$ has a non-zero probability of usage in only one location: $\exists l \in \mathcal{L}, B_{l, d_f} \in [0.4, 0.8] \text{ and } \forall l' \neq l, B_{l', d_f} = 0$;
-	\item a server $d_s$ has a very high probability of working, whatever the user's location: $\exists p \in [0.9, 1], \forall l \in \mathcal{L}, B{l, d_s} = p$.
+  \item There are three possible locations $\mathcal{S}=\left\{\text{Home}, \text{Outside}, \text{Work}\right\}$.
+  Each user has transition probabilities from one place to another;
+  one cannot go from work to home without transitionning outside and vice-versa;
+  \item A user always has a phone, plus a random number of 2 to 9 devices which types are decided by a weighted random choice: each device has 30\% chances of being either mobile, portable, or fixed, and only 10\% probability of being a server;
+  \item For each user, device, and location, the probability that a device be used at a location is picked at uniform random according to the following rules:
+  \begin{itemize}
+    \item \emph{Mobiles} can be accessed everywhere with a probability of 60 to 100\%;
+    \item \emph{Portables} can be accessed everywhere with a probability of 20 to 80\%;
+    \item \emph{Fixed} appliances can only be accessed from one single place (never outside) with a probability of 30 to 90\%;
+    \item \emph{Servers} have a constant availability rate between 90 and 100\%.
   \end{itemize}
+\end{itemize}
+
+% we keep the different possible locations $\mathcal{L}$ to $N=3$ and the state transition matrix $A$ to a fixed value (cf figure~\ref{fig:hmm}).
+% The number and types of devices per user, along with the matrix of emission probabilities $B$, is determined randomly according to the following rules.
+
+% A user always has a phone, plus a random number of 2 to 9 devices whose type is decided by a weighted random choice: each device has 30\% chances of being either mobile, portable, or fixed, and only 10\% probability of being a server.
+% $B_{*, d}$, the probability that device $d$ is used in each location, depends on $d$'s device type: 
+% \begin{itemize}
+% 	\item for each location, every mobile device $d_m$ has a random but high probability of being online: $\forall l \in \mathcal{L}, B_{l, d_m} \in [0.6, 1]$;
+% 	\item a portable device $d_p$ has a much lower probability of being used: $\forall l \in \mathcal{L}, B_{l, d_p} \in [0.2, 0.8]$; 
+% 	\item a fixed appliance $d_f$ has a non-zero probability of usage in only one location: $\exists l \in \mathcal{L}, B_{l, d_f} \in [0.4, 0.8] \text{ and } \forall l' \neq l, B_{l', d_f} = 0$;
+% 	\item a server $d_s$ has a very high probability of working, whatever the user's location: $\exists p \in [0.9, 1], \forall l \in \mathcal{L}, B{l, d_s} = p$.
+% \end{itemize}
 
@@
 \centering
-$$A =
-\kbordermatrix{
-      & W   & O   & H   \cr
-    W & 0.6 & 0.4 & 0   \cr
-    O & 0.2 & 0.6 & 0.2 \cr
-    H & 0   & 0.4 & 0.6 \\[0.3em]
-}, \;
-B = 
-\kbordermatrix{
-      & W     & O   & H   \cr
-    p & 0.7 & 0.6 & 0.8 \cr
-    w & 0.7 & 0   & 0   \cr
-    h & 0   & 0   & 0.7 \cr
-    l & 0.2 & 0.4 & 0.6 \\[0.3em]
-}$$
+% $$A =
+% \kbordermatrix{
+%       & W   & O   & H   \cr
+%     W & 0.6 & 0.4 & 0   \cr
+%     O & 0.2 & 0.6 & 0.2 \cr
+%     H & 0   & 0.4 & 0.6 \\[0.3em]
+% }, \;
+% B = 
+% \kbordermatrix{
+%       & W     & O   & H   \cr
+%     p & 0.7 & 0.6 & 0.8 \cr
+%     w & 0.7 & 0   & 0   \cr
+%     h & 0   & 0   & 0.7 \cr
+%     l & 0.2 & 0.4 & 0.6 \\[0.3em]
+%}$$
 
-%\includegraphics[width=0.65\columnwidth]{figures/hmm.pdf}
-%\vspace{2ex}
+\includegraphics[width=0.65\columnwidth]{figures/hmm.pdf}
+\vspace{2ex}
 \includegraphics[width=0.9\columnwidth]{figures/sample_usage.pdf}
 
-\caption{\label{fig:hmm} Example Hidden Markov Model (HMM) of a user's behavior: on top are the HMM parametersand on the bottom is a sample output from the model.}
+\caption{\label{fig:hmm} Example Hidden Markov Model (HMM) of a user's behavior.
+On top: visual representation of the model, with transition probabilities between locations and device usage probabilities at each location.
+On the bottom: Sample output from the HMM, with the initial of the location across time on the x-axis, the initial of each device on the y-axis, and their state across time (gray means online).}
 \end{figure}
 
-HMMs being generative probabilistic models, they allow the generation of observation sequence $O$ given the parameters of the model $\lambda_N$.
-Figure~\ref{fig:hmm} shows a possible outcome of the creation of a user's HMM $\lambda_N$ along with a sample observation sequence $O$ output from the model $\lambda_N$.
+HMMs being generative probabilistic models, they allow the generation of observation sequences given the parameters of the model.
+Figure~\ref{fig:hmm} shows a possible user's model along with a sample observation sequence $O$ generated from it.
 
-Each round lasts $T=10s$ and users start at different times. 
-This way, even though the round period is fixed, devices enter and leave the system at different points in the continuous time.
+Even though each user's behavior is discretized, they start at different times. 
+This way, even though the time step \tuser is fixed, devices enter and leave the system at different points in the continuous time.
 

### 2018-08-06 paper/design.tex
edited solution overview

@@
 When Alice and Bob, two users of our system, want to exchange a file \(f\) 
-through \name; they start by sharing some information out-of-band, \eg from 
+through \name, they start by sharing some information out-of-band, \eg from 
 their smartphones.
 More precisely, they exchange metadata on \(f\), encryption keys, and
+some of
 \changeAL{routing information that they will use to transfer the
-  file's content over \name's network of unreliable nodes.}
+  file's content over \name's network of unreliable nodes.} Namely,
+the recipient provides a \emph{rendezvous point} for the sender to
+initiate the file transfer.
 \sonja{here comes more of a solution overview and reference to the outline
@@
   hop of forwarding is selected from the set in an ad-hoc way.
+\item[Onion Routing.] Put simply, in onion routing, the sender creates
+  a source route and 
+  encapsulates the payload and next-hop information in layers (by
+  encryption), that are \emph{peeled} (decrypted) one by one along the
+  route. By virtue of these layers, the forwarding nodes on the
+  route do not know where on the route they are and thus whether they
+  have received a packet directly from the sender or some other
+  intermediate node. We base our format for layering and peeling on
+  Sphinx~\cite{Sphinx}, with some modification to allow for the
+  changes above, described in \cref{Sphinxes}.
 \end{description}

### 2018-08-06 paper/design.tex
Fixes missing references

--- 2018-08-01 paper/design.tex
@@
-%!TEX root = p2p-private-cloud.tex
-
 \section{Design of the \name file transfer system}%
@@
 their smartphones.
-More precisely, they exchange metadata on \(f\), encryption keys, and 
-\changeAL{routing information that they will use to transfer the file's content over \name's network of unreliable nodes.}
-%use-once reply mix-headers.
-%They use these reply headers to transfer the file contents of \(f\) over a network of unreliable nodes while also achieving privacy.
+More precisely, they exchange metadata on \(f\), encryption keys, and exchange 
+use-once reply mix-headers.
+They use these reply headers to transfer the file contents of \(f\) over a 
+network of unreliable nodes while also achieving privacy.
 
@@
   \caption{\label{fig:outline}%
-    %\commentDaniel{We must adapt this figure to the text.}%
+    \commentDaniel{We must adapt this figure to the text.}
     Outline of \name's components. Users squads of devices are circled in gray. 
@@
   \item[Network structure]
-    describes the characteristics of the \changeAL{network nodes}, the connections 
+    This describes the characteristics of the anonymous relays, the connections 
     between them and the underlying topology.
@@
       \item connection type (direction, synchronization),
-      \item symmetry (node roles, node topology for routing, decentralization);
+      \item symmetry (node roles, node topology for routing, decentralization).
     \end{enumerate*}
@@
   \item[Routing information]
-    describes the network information available to entities deciding on 
-    the route of an anonymous file exchange.
+    This describes the network information available to entities deciding on 
+    the route of an anonymous connection.
     The subcategories are
@@
       \item network view necessary for making routing decisions,
-      \item triggers for routing information updates;
+      \item triggers for routing information updates.
     \end{enumerate*}
@@
   \item[Communication model]
-    describes the entities that make the routing decisions and how they 
+    This describes the entities that make the routing decisions and how they 
     make these decisions.
@@
       \item scheduling (traffic prioritization),
-      \item node selection (determinism, selection set, selection probability);
+      \item node selection (determinism, selection set, selection probability).
     \end{enumerate*}
@@
   \item[Performance]
-    describes things like latency and communication mode.
+    This describes things like latency and communication mode.
     The subcategories are
@@
 Next, we describe the \ac{SPOR} protocol (\cref{SPOR}).
-\commentAL{A lot of description here, should only come in Section~\ref{sec:squad_overlay}}
 This focuses on the node selection, \ie adds node selection on top of Sphinxes.
-%The \ac{SPOR} protocol assumes a source of random nodes, %\eg through \ac{RPS}~\cite[\eg][]{} or \iac{DHT} based scheme~\cite[\eg][]{}.
-The SPOR protocol assumes that each node knows a random subset of the system's participants at all time (\eg through Random-Peer-Sampling \cite{Jelasity_Voulgaris_Guerraoui_Kermarrec_van_Steen_2007}).
+The \ac{SPOR} protocol assumes a source of random nodes, \eg through 
+\ac{RPS}~\cite[\eg][]{BrahmsRPS} or \iac{DHT} based 
+scheme~\cite[\eg][]{Octopus}.
 Each node must be associated with a public key and some availability 
@@
 
-A device's availability depends on its user's behavior, hence the device must 
-predict this behavior.
+A device's availability depends on its user's behaviour, hence the device must 
+predict this behaviour.
 This is best done jointly between the user's all devices.
@@
 \include*{spor}
-\commentAL{What I want to do from here:
-(1) The squad overlay, where a user's devices exchange behavioral information;
-(2) Predicting a device's availability;
-(3) What is at the moment III-B SPOR: global overlay (one-liner: ``we use a RPS service'') and nodes selection per layer etc.;
-(4) File exchange.}
 \include*{squad-overlay-design}

### 2018-08-06 paper/system-model.tex
Fixes missing references

--- 2018-07-17 paper/system-model.tex
@@
 
-\paragraph*{Adversary model} To assess our approach, we use the adversary model assumed by by Tor \cite{} and
-Sphinx \cite{}: the adversary has complete control over some part of
+\paragraph*{Adversary model} To assess our approach, we use the adversary model 
+assumed by by Tor \cite{Tor} and
+Sphinx \cite{Sphinx}: the adversary has complete control over some part of
 the network as well as some of the nodes. We not consider a passive

### 2018-08-06 paper/design.tex

--- 2018-08-06 paper/design.tex
@@
 This focuses on the node selection, \ie adds node selection on top of Sphinxes.
-%The \ac{SPOR} protocol assumes a source of random nodes, %\eg through \ac{RPS}~\cite[\eg][]{} or \iac{DHT} based scheme~\cite[\eg][]{}.
-The SPOR protocol assumes that each node knows a random subset of the system's participants at all time (\eg through Random-Peer-Sampling \cite{Jelasity_Voulgaris_Guerraoui_Kermarrec_van_Steen_2007}).
+The \ac{SPOR} protocol assumes a source of random nodes, \eg through 
+\ac{RPS}~\cite[\eg][]{BrahmsRPS} or \iac{DHT} based 
+scheme~\cite[\eg][]{Octopus}.
 Each node must be associated with a public key and some availability 

### 2018-08-06 paper/sphinxes.tex

@@
+%!TEX root = p2p-private-cloud.tex
+
 \subsection{Sphinxes: the Sphinx header format Extended for Sets of nodes}%
@@
 functionality.
-\Ie, it provides bitwise unlinkability on the forward route, hides the path 
+\Ie, it provides bitwise unlinkability on the forward route \commentAL{Routes must be defined before that point}, hides the path 
 length, makes replies indistinguishable from forward messages and resists 
@@
 We will now give an overview of the Sphinx header format.
-The idea is not to give a detailed description of Sphinx, but to to give the 
+The idea is not to give a detailed description of Sphinx, but to give the 
 reader enough understanding of Sphinx to understand the changes we make to 

### 2018-08-06 paper/squad-overlay-design.tex
finished describing file transfer

@@
 
-\newcommand\fileid{\ensuremath{ID_{\text{f}}}}
-\newcommand\sendingdevice{\ensuremath{d^{(s)}_f}}
-\newcommand\recdevice{\ensuremath{d^{(r)}_f}}
+\newcommand\fileid{\ensuremath{ID_{\text{f}}}\xspace}
+\newcommand\sendingdevice{\ensuremath{d^{(s)}_f}\xspace}
+\newcommand\recdevice{\ensuremath{d^{(r)}_f}\xspace}
 
@@
 In \name, we want file exchanges to remain private: these metadata are exchanged out-of-band.
-In addition, in \name, each file is associated with a random ID \fileid, that is part of \finfo.
+In addition, each file is associated with a random \fileid, that is part of \finfo.
 
 \paragraph*{Out-of-band initialization} 
-When Alice wishes to send a file $f$ to Bob, she compute \finfo, 
+When Alice wishes to send a file $f$ to Bob, she computes \finfo, 
 plus one reply header per chunk, and sends the whole to Bob.
@@
 
-\newcommand\bitfield{\ensuremath{bf_f}}
+\newcommand\bitfield{\ensuremath{bf_f}\xspace}
 \paragraph*{Chunks and bitfields}
@@
 
-Bob receives $f$ on a device \recdevice. 
-When one of his devices receives a chunk $c_i$ for $f$, it fetches the proper recipient \recdevice by looking into the \squad overlay sequence
-for the line \texttt{RECEIVING<\sendingdevice, \fileid>} and forwards the file chunk to \recdevice.
+Bob receives $f$ on a device \recdevice, but a chunk $c_i$ for $f$ might arrive on any of his devices. 
+This device then fetches the address of the proper recipient \recdevice by looking for the line \texttt{RECEIVING<\recdevice, \fileid>} in its squad sequence, 
+and forwards the file chunk to \recdevice.
 Upon reception of the chunk, \recdevice verifies its integrity by computing its SHA1 hash $h_{c_i}$ and comparing it to $\finfo.h_{c_i}$.
@@
 Reciprocally, acknowledgments can arrive to Alice on any on her devices, while only \sendingdevice can process it.
-When one of Alice's devices receive Bob's bitfield \bitfield, 
-it forwards \bitfield to \sendingdevice by looking for the line \texttt{RECEIVING<\sendingdevice, \fileid>} in the \squad overlay's sequence.
+When one of Alice's devices receives Bob's bitfield \bitfield, 
+it forwards \bitfield to \sendingdevice by getting its address on the line \texttt{RECEIVING<\sendingdevice, \fileid>} of the \squad overlay's sequence.
 Upon reception of a bitfield \bitfield, \recdevice updates its knowledge of Bob's unreceived chunks of $f$,
-and sends a chunk to Bob among the ones that were not already acknowledged by Bob.
+and sends a chunk to Bob among the ones that were not already acknowledged by Bob, unless the file has been entirely received.
 
 \commentAL{This is a shitty scheduler. Should I mention it? Rephrase? You have a citation to propose instead?}
-Messages in \name might arrive in a wrong order or fail. 
-It is not unlikely that the file exchange stops before its transfer is done.
-As a solution, \sendingdevice will restart periodically sending all chunks that were not acknowledged by Bob if the transfer hangs.
-This solution ensures liveness by increasing network traffic (some chunks might be received several times), as will be seen in the evaluation.
+Messages in \name might arrive in a wrong order or fail:
+it is not unlikely that the file exchange stops before its transfer is done.
+As a solution, if the transfer hangs, \sendingdevice will restart periodically sending chunks that were not acknowledged by Bob.
+This solution ensures liveness over network efficiency (some chunks might be received several times), as will be seen in the evaluation.
 It nevertheless allows reliable file transfer among a network of poorly connected nodes in a private manner.

### 2018-08-06 paper/system-model.tex

--- 2018-08-01 paper/system-model.tex
@@
 
-\name provides a private and fully decentralized file sharing service by exploiting 
+\name provides a private and fully decentralized file transfer service by exploiting 
 %% is a distributed system made of
-users' devices. 
-We assume any two devices can communicate with one another as soon as one knows the address of the other (\eg using the Internet, \changeFT{possibly extended with NAT traversal techniques}).
-The devices owned by the same user (this user's \squad) know of each other.
-%Thus, the devices from an \squad only know the mapping from devices to users for the devices in 
-% the \squad they belong to.
-We also assume that users can exchange some limited amounts of data 
-out-of-band, \ie through some other channel than the network just mentioned (\eg 
-using \ac{NFC} or QR codes).
-
+users' devices.  We assume any two devices can communicate with one
+another as soon as one knows the address of the other (\eg using the
+Internet, possibly extended with NAT traversal techniques). The
+devices owned by the same user (this user's \squad) know of each
+other. Other users' devices can help transfer the file from one user
+to another but are not needed for storage.  We also assume that users
+can exchange some limited amounts of data out-of-band, \ie through
+some other channel than the network just mentioned (\eg using \ac{NFC}
+or QR codes).
 %system model: explain e-squad, contrast with cloud
@@
 
-In the following, we first describe \changeFT{how file sharing typically occurs when users rely on a cloud storage provider. We use this simple use case}
-%a simple model of data sharing via cloud storage
-to
-highlight some of the desirable privacy properties of a file sharing service, before mapping them into our \changeFT{fully decentralized (a.k.a. P2P)}
-context. 
-We finally consider the additional privacy properties required to protect users from  network traffic analysis, which we propose to address through onion
-routing, and detail our adversary model.
-\commentFT{I wasn't sure how to position onion routing: to me it is more a solution than a problem specification, and since we are describing what we want here (spec./problem space) I wasn't sure how much to highlight onion routing (solution space).} \commentFT{Terminology: Do we use both `fully decentralized' and `P2P', or do we favor one over the other?}
+In the following, we first describe how file transfer typically occurs
+when users rely on a cloud storage provider. We use this simple use
+case to highlight some of the desirable privacy properties of a file
+transfer service, before mapping them into our fully decentralized
+(a.k.a. P2P\footnote{We use the terms \emph{fully decentralized} and
+  \emph{P2P} interchangeably, and preferentially the latter for brevity.})
+context.  We finally consider the additional privacy properties
+required to protect users from inferences such as by network traffic
+analysis and state our adversary model.
 
-% We then add privacy properties and adversary models for onion
-% routing to cover network traffic analysis.
+\subsection{File transfer via a cloud storage provider}
 
-\subsection{File sharing through a cloud storage provider}
-\commentFT{Moving to subsections, to better highlight structure}
-
-When sharing a file with Bob through a cloud provider, Alice only needs to upload this file from one of her devices to the cloud, and \changeFT{share a link to this file with Bob}.
-Bob in turn can download this file through the transmitted link onto one of his devices.
+When sharing a file with Bob through a cloud provider, Alice only
+needs to upload this file from one of her devices to the cloud, and
+share a link to this file with Bob. Bob in turn can download this file
+through the transmitted link onto one of his devices.
 
 The use of the cloud provider, as a third party,
-provides two main privacy properties, which we \changeFT{should preserve} when
+provides two main privacy properties, which we should preserve when
 moving to a \ac{P2P}~\cite{DevilInMetadata} setting:
 \begin{itemize}
-\item Except for the cloud provider, Alice and Bob are the only \changeFT{users} who learn 
-about Alice sharing a file with Bob; \sonja{narrow down to users?} \commentFT{Changed to users: we could also use entities/participants}
-\item
-  The composition and behavior of Alice and Bob's \squad remain hidden to each other, and to other users.
-I.e.
-Alice does not learn which devices Bob owns or uses, let alone how Bob uses them, and reciprocally.
-%%   Alice and Bob learn nothing about each others' devices, \ie 
-%% they cannot map any device as belonging to each other or draw
-%% inferences from their behavior.
-The cloud provider, however, \changeFT{knows this information}. \sonja{expand to other users?} \commentFT{Done}
+\item Alice and Bob are the only users who learn 
+about Alice sharing a file with Bob.
+\item The composition and behavior of Alice and Bob's \squad remain
+  hidden to each other, and to other users. I.e. Alice does not learn
+  which devices Bob owns or uses, let alone how Bob uses them, and
+  reciprocally.
 \end{itemize} 
+The cloud provider, however, has this information and any other
+stemming from the users' interaction with the service, and can draw
+inferences from metadata even when the data itself is encrypted, and
+thus poses a threat to the users' privacy.
 
 \subsection{Moving to a P2P environment}
-A private P2P file sharing solution should retain
-%% We want to keep
-the privacy that
-Alice and Bob already enjoy when a cloud provider functions
-as a gatekeeper towards each other and other users.
-\changeFT{Eschewing a cloud provider, as we propose to do, removes the privacy risks associated with a central brokering entity,}
-% We go a step further by removing the cloud provider that may draw inferences from metadata even when the data itself is encrypted.
-%Unfortunately, removing the cloud provider
-\changeFT{but} also removes the gatekeeping a cloud provider provides, \changeFT{and exposes} users to friendly surveillance~\cite{FriendlySurveillance}
-by other peers (other \name users including Alice and Bob). \sonja{removed: in
-  an honest-but-curious setting}
-\commentFT{Removed, as did not fit with the flow, but probably needed somewhere: `We give the definitions for the
-security and privacy properties of \name in Section~\ref{security-discussion}.'} \changeFT{In particular other users might collude to observe some of the traffic, and gain knowledge regarding Alice's and Bob's interactions, the devices they own, and how they use them.}
+A private P2P file transfer solution should retain the privacy that
+Alice and Bob already enjoy when a cloud provider functions as a
+gatekeeper towards each other and other users.  Eschewing a cloud
+provider, as we propose to do, removes the privacy risks associated
+with a central brokering entity, but also removes the gatekeeping a
+cloud provider provides, and exposes users to friendly
+surveillance~\cite{FriendlySurveillance}, in an honest-but-curious
+setting, by other peers (other \name users including Alice and
+Bob). In particular other users might collude to observe some of the
+traffic, and gain knowledge regarding Alice's and Bob's interactions,
+the devices they own, and how they use them.
 
-%\subsection{Protecting against network traffic analysis in \name}
 \subsection{The privacy properties and adversary model of \name}
@@
 Friendly surveillance can be mitigated by ensuring security properties 
-typically associated with onion routing \cite{CLOnionRouting}: 
+typically associated with onion routing, as defined by Camenisch and Lysianskay~\cite{CLOnionRouting}: 
 % We combine the requirements from
@@
 using \name does not reveal the \squad a device belongs to nor its
-owner. \changeAL{Thus, no information on the user's behavior (e.g. being online) can be infered through \name.} 
-%and can thus not infer anything about a user's behavior such as being online.
+owner. Thus, no information on the user's behavior (e.g. being online)
+can be infered through \name.  \commentFT{Removed, as did not fit with
+  the flow, but probably needed somewhere: `We give the definitions
+  for the security and privacy properties of \name in
+  Section~\ref{security-discussion}.'} \sonja{better here. Need to define
+  device unlinkability, the rest is covered by Camenisch.}
 
-\paragraph*{Adversary model} To assess our approach, we use the adversary model assumed by Tor~\cite{Tor} and
-Sphinx~\cite{Sphinx}: the adversary has complete control over some part of
-the network as well as some of the nodes. We do not consider a passive
-global network adversary, against which it is notoriously difficult to
-achieve security~\cite{SystemsForAnonymousCommunication}.
+\paragraph*{Adversary model} To assess our approach, we use the
+adversary model assumed by Tor~\cite{Tor} and Sphinx~\cite{Sphinx}:
+the adversary has complete control over some part of the network as
+well as some of the nodes. We do not consider a passive global network
+adversary, against which it is notoriously difficult to achieve
+security~\cite{SystemsForAnonymousCommunication}.

### 2018-08-06 paper/design.tex
Design: rejects on and accepts one of Adrien's changes

@@
 More precisely, they exchange metadata on \(f\), encryption keys, and
-some of
-\changeAL{routing information that they will use to transfer the
-  file's content over \name's network of unreliable nodes.} Namely,
-the recipient provides a \emph{rendezvous point} for the sender to
-initiate the file transfer.
-\sonja{here comes more of a solution overview and reference to the outline
+some use-once reply mix-headers.
+They use these reply headers to transfer the file contents of \(f\) over a 
+network of unreliable nodes while also achieving privacy.
+
+\sonja{Here comes more of a solution overview and reference to the outline
   figure.}
-
 Figure \cref{fig:outline} shows the components needed to obtain this
 routing information.
-%use-once reply mix-headers.
-%They use these reply headers to transfer the file contents of \(f\) over a network of unreliable nodes while also achieving privacy.
 
@@
   \item[Network structure]
-    describes the characteristics of the \changeAL{network nodes}, the connections 
-    between them and the underlying topology.
+    describes the characteristics of the network nodes, the connections between 
+    them and the underlying topology.
     The subcategories are

### 2018-08-06 paper/design.tex
proofreading sphinxes, did not dive deep

--- 2018-08-06 paper/design.tex
@@
 
-Figure \cref{fig:outline} shows the components needed to obtain this
+Figure~\ref{fig:outline} shows the components needed to obtain this
 routing information.  
@@
   layers is based on a predictive model for availability, disseminated
-  according to Figure~\cref{fig:outline}, and queried by random peer sampling.
+  according to Figure~\ref{fig:outline}, and queried by random peer sampling.
 \item [Probabilistic.] Instead of source routes with one node per onion layer, each

### 2018-08-06 paper/sphinxes.tex
proofreading sphinxes, did not dive deep

--- 2018-07-21 paper/sphinxes.tex
@@
 128-bit security.
-Sphinx only provides one node per onion layer, in this section we extend Sphinx 
+Sphinx only provides one node per onion layer; in this section we extend Sphinx 
 to Sphinxes, which allows for multiple nodes per onion layer.
 (See \cref{fig:OR-POR}.)
+% AL: Bounded random-walk....
 As such, Sphinxes could be described as a bounded random-walk protocol, \ie the 
@@
 
-The derived shared secret \(s_1\) is then used to derive various keys.
-One of them is the key for the \ac{MAC} (\(gamma_1\)) to verify the integrity 
+The shared secret \(s_1\) is then used to derive various keys.
+One of them is the key for the \ac{MAC} (\(\gamma_1\)) to verify the integrity 
 of the header (\(\beta_1\)).
@@
 We note that \(\beta_i\) is encrypted using a stream cipher.
-Thus we can append zeroes before decryption to keep the ciphertext length 
+Thus we can append zeros before decryption to keep the ciphertext length 
 constant.
-Since we append \emph{before} decryption, those appended zeroes will look 
+Since we append \emph{before} decryption, those appended zeros will look 
 completely random to the next node, thus the position on the path is hidden.
@@
 \(s_1\).
-Then the triple \((\alpha_2, \beta_2, \gamma_2)\) are sent to the node with 
+Then the triple \((\alpha_2, \beta_2, \gamma_2)\) is sent to the node with 
 address \(d_2\).
@@
 We will now extend Sphinx to do \ac{POR}: instead of providing only \(d_{i+1}\) 
-in \(\beta_i\), we will have a set \(\{d_{i+1}^{(0)}, \dotsc, d_{i+1}^{(m)}\}\) 
+in \(\beta_i\), we will have a set \(\{d_{i+1}^{(1)}, \dotsc, d_{i+1}^{(m)}\}\) 
 of \(m\) alternative next nodes.

### 2018-08-06 paper/design.tex

--- 2018-08-06 paper/design.tex
@@
   figure.}
-Figure \cref{fig:outline} shows the components needed to obtain this
+Figure~\ref{fig:outline} shows the components needed to obtain this
 routing information.

### 2018-08-06 paper/system-model.tex
minor edits and added informal definitions of CL properties

@@
 transfer service, before mapping them into our fully decentralized
-(a.k.a. P2P\footnote{We use the terms \emph{fully decentralized} and
-  \emph{P2P} interchangeably, and preferentially the latter for brevity.})
+(a.k.a. peer-to-peer (P2P\footnote{We use the terms \emph{fully decentralized} and
+  \emph{P2P} interchangeably, and preferentially the latter for brevity.}))
 context.  We finally consider the additional privacy properties
-required to protect users from inferences such as by network traffic
-analysis and state our adversary model.
+required to protect users from inferences, such as by network traffic
+analysis, and state our adversary model.
 
@@
 When sharing a file with Bob through a cloud provider, Alice only
-needs to upload this file from one of her devices to the cloud, and
+needs to upload this file from one of her devices to the cloud and
 share a link to this file with Bob. Bob in turn can download this file
@@
 provides two main privacy properties, which we should preserve when
-moving to a \ac{P2P}~\cite{DevilInMetadata} setting:
+moving to a P2P~\cite{DevilInMetadata} setting:
 \begin{itemize}
@@
 stemming from the users' interaction with the service, and can draw
-inferences from metadata even when the data itself is encrypted, and
-thus poses a threat to the users' privacy.
+inferences from metadata even when the data itself is encrypted. The
+provider thus poses a threat to the users' privacy which we remove in
+the P2P scenario.
 
@@
 gatekeeper towards each other and other users.  Eschewing a cloud
-provider, as we propose to do, removes the privacy risks associated
-with a central brokering entity, but also removes the gatekeeping a
-cloud provider provides, and exposes users to friendly
-surveillance~\cite{FriendlySurveillance}, in an honest-but-curious
-setting, by other peers (other \name users including Alice and
-Bob). In particular other users might collude to observe some of the
-traffic, and gain knowledge regarding Alice's and Bob's interactions,
-the devices they own, and how they use them.
+provider, as we propose to do, removes not just the privacy risks
+associated with a central brokering entity but also the benefits from
+gatekeeping and therefore exposes users to friendly
+surveillance~\cite{FriendlySurveillance} by other peers (other \name
+users including Alice and Bob). In particular, in an
+honest-but-curious setting, other users might collude to observe some
+of the traffic, and gain knowledge regarding Alice's and Bob's
+interactions, the devices they own, and how they use them.
 
@@
 Friendly surveillance can be mitigated by ensuring security properties 
-typically associated with onion routing, as defined by Camenisch and Lysianskay~\cite{CLOnionRouting}: 
+typically associated with onion routing, as defined by Camenisch and Lysyanskaya~\cite{CLOnionRouting}: 
 % We combine the requirements from
@@
 % for onion routing:
-correctness, integrity, security (wrap resistance,
-indistinguishability). These properties cover the concerns about
+onion-correctness, integrity, and security %(wrap resistance,
+                                %indistinguishability). 
+Informally, onion-correctness means that if an onion is formed
+correctly, processed by the correct routers in the correct order, then
+the correct message is received by the last router. Onion-integrity
+means that even for an onion created by an adversary, the path length
+is bounded by $N$. Onion-security means that an adversary sending a
+challenge onion to a router and able to see the outcome of how the
+onion is processed, cannot distinguish between whether that onion
+corresponds to a particular message and route or not. This is also
+true for a \emph{re-wrapped} onion, i.e. a challenge onion wrapped in
+another layer. The formal definitions are in~cite{CLOnionRoutin} along
+with a theorem that states that an onion routing scheme satisfying
+these three properties, combined with secure point-to-point channels,
+is UC-secure.
+
+These properties cover the concerns about
 revealing to others that Alice shares a file with Bob in the first
 place. In \name, we additionally derive the property of
-device-unlinkability from the \ac{P2P} requirements, meaning that
+\emph{device-unlinkability} from the \ac{P2P} requirements, meaning that
 using \name does not reveal the \squad a device belongs to nor its
 owner. Thus, no information on the user's behavior (e.g. being online)
-can be infered through \name.  \commentFT{Removed, as did not fit with
+can be infered through \name. \sonja{insert more formal definition
+  here, and perhaps explanation that we need it because we introduce
+  availability information}
+
+ \commentFT{Removed, as did not fit with
   the flow, but probably needed somewhere: `We give the definitions
@@
 the adversary has complete control over some part of the network as
-well as some of the nodes. We do not consider a passive global network
+well as some of the nodes. Like them, we do not consider a passive global network
 adversary, against which it is notoriously difficult to achieve

### 2018-08-06 paper/squad-overlay-design.tex
done with III.E.2

@@
 
+\newcommand\rpsview{\ensuremath{\mathcal{V}}\xspace}
+\newcommand\desc{\ensuremath{{\mathtt{desc}}}\xspace}
+
 Devices need to know the address of SPORES participants in order to craft PORs.
@@
 \commentAL{TODO: cite \cite{Jesi_Montresor_van_Steen_2010} for \textbf{secure} RPS}.
-It is a gossip protocol that allows each participant to keep a fixed-size \emph{random} subset of other nodes' descriptor (that we will call the \emph{view}). 
+It is a gossip protocol that allows each participant to keep a fixed-size \emph{random} subset of other nodes' descriptor (that we will call the \emph{view} \rpsview). 
 The view is constantly evolving, as queries are periodically issued between nodes to exchange descriptors between their respective views.
@@
 
-In SPORES, a descriptor for $d$ contains the following information:
+In SPORES, a descriptor $\desc_d$ describing device $d$ contains the following information:
 \begin{itemize}
@@
 \label{sssec:routes_creation}
+
+\newcommand\layer{\ensuremath{{\mathcal{L}}}\xspace}
+\newcommand\Poff{\ensuremath{P_{\text{off}}}\xspace}
+
+Routes are created via Sphinxes, as described in section~\ref{SPOR}.
+Each layer \layer constituting the route is created by the same \CreateLayer\xspace function.
+
+In \name, we wish to maximize the availability of the route.
+Therefore, each layer \layer is created so as to reach the availability threshold $\theta$, a parameter chosen by the user.
+Note that Sphinxes is agnostic to this use-case: one could want to maximize other characteristics, e.g. the layer's expected bandwidth.
+
+\CreateLayer\xspace iteratively adds random descriptors from the RPS's view \rpsview to the current layer \layer, until the layer's probability of being offline, $\Poff^\layer$, falls below the availability threshold $\theta$:
+
+$$ \Poff^\layer = \sum\limits_{d \in \layer}\desc_d.P_d $$
+
+Recall that each layer in Sphinxes has a constant number of nodes $w_\layer$, that is a Sphinxes parameter.
+If $w_\layer$ is reached before $\Poff^\layer < \theta$, then we early abort \CreateLayer.
+On the other hand, if $|\layer| < w_\layer$, we pad the layer with blank descriptors, such that the header always weighs the same size.
 

### 2018-08-06 paper/conclusion.tex
summarized alternatives in conclusions, framed security discussion, added robustness considerations, rectified typos

@@
 limits of protection against statistical inference.
-%On a related note, it would be interesting to adapt the
-%Sphinx~\cite{Sphinx} cryptographic packet format to the routing of \name as a step toward provable security.
+
+Although we presented a stateless solution, mainly to handle churn in
+a file transfer scenario, \name does not preclude a stateful alternative. 
+Other applications such as web browsing, interaction and
+collaboration or other kind of hidden services might benefit from a stateful, circuit-based approach
+like with traditional onion routing. Prediction of device availability
+could support different goals, for example time of day for delayed
+file transfer for resource optimization.
 

### 2018-08-06 paper/security-discussion.tex

@@
   Our protocol is a \enquote{bounded} random walk, \ie within limits.}
+
+We base our solution on Sphinx, which, when used for onion routing, has been proved to satisfy the
+properties given in ~cite{CLOnionRouting} that were shown to result
+in a UC-secure onion-routing scheme. We thus primarily need to ensure that 
+\begin{enumerate*} \item our extension to Sphinxes preserves these
+  properties, \item the availability information introduced and
+  disseminated to deal with churn satisfies the device-unlinkability
+  property we defined in~\cref{system-model}, and that \item the node
+  selection does not introduce any advantage for the
+  adversary. \end{enumerate*} In terms of general system robustness, a
+stateless routing protocol needs to handle packet re-ordering and
+network failures (links or nodes).
 
@@
 
-\sonja{Failure, exception handling, such as reordered chunks, chunks
-  on different devices, squad devices going offline during transfer}
-\commentDaniel{Reordered chunks is not a problem, we handle that.}
+\paragraph*{Robustness}
 
-\section{Alternatives}%
-\label{Alternatives}
-
-\subsection{Stateful \name}
-\subsection{Beyond file exchange} web browsing, hidden services,
-interaction and collaboration.
-\subsection{Other predictions} time of day?
+Stateless routing can result in re-ordered chunks or packets, and
+chunks received on different devices of a user's squad. From
+Sphinx, we inherit IDs for packets that we we include in the
+out-of-band metadata on the file to be exchanged, as an ordered list,
+that is used to re-order chunks if need be. The squad overlay handles
+inter-squad device coordination. Liveness despite the possibility of squad devices going offline during
+transfer or other node or link failures is ensured by acknowledgments
+and timeouts as detailed in ~\cref{sec:squad_overlay}.

### 2018-08-06 paper/system-model.tex

@@
 true for a \emph{re-wrapped} onion, i.e. a challenge onion wrapped in
-another layer. The formal definitions are in~cite{CLOnionRoutin} along
+another layer. The formal definitions are in~\cite{CLOnionRouting} along
 with a theorem that states that an onion routing scheme satisfying

### 2018-08-06 paper/security-discussion.tex
related work: p2p storage, i2p, uncommented availability modeling

@@
 
-\sonja{will add some framing about us composing and modifying parts that
-  have security proofs for their original and individual versions and needing to evaluate the resulting schemes}
+%\sonja{will add some framing about us composing and modifying parts that
+%  have security proofs for their original and individual versions and needing to evaluate the resulting s%chemes}
 
@@
 
-We base our solution on Sphinx, which, when used for onion routing, has been proved to satisfy the
-properties given in ~cite{CLOnionRouting} that were shown to result
-in a UC-secure onion-routing scheme. We thus primarily need to ensure that 
+We base our solution on Sphinx~\cite{Sphinx}, which, when used for
+onion routing, has been proved to satisfy the properties given
+in~\cite{CLOnionRouting} that were shown to result in a UC-secure
+onion-routing scheme. We thus primarily need to ensure that
 \begin{enumerate*} \item our extension to Sphinxes preserves these
@@
   disseminated to deal with churn satisfies the device-unlinkability
-  property we defined in~\cref{system-model}, and that \item the node
-  selection does not introduce any advantage for the
+  property we defined in~\cref{system-model}, and that \item the
+  resulting node selection does not introduce any advantage for the
   adversary. \end{enumerate*} In terms of general system robustness, a
@@
 one.
-The proofs of Sphinx rests on the results of \textcite{CLOnionRouting}, which 
+The proofs of Sphinx rest on the results of \textcite{CLOnionRouting}, which 
 are results for ordinary \ac{OR} with only one node per layer.
+\sonja{Daniel is working on sketching a proof/rephrasing the following.}
 As long as we output all the nodes in the next layer, the proofs should not 
@@
 
-\paragraph*{Security of \acs*{SPOR}}
+\paragraph*{Security of \acs*{SPOR}, node selection}
 
+\sonja{will motivate using the survey/taxonomy}
 The onion route provides unlinkability between Alice and Bob as long as the 
@@
 Since she is present on every layer, she can ensure she relays the message all 
-the way to Bob.
+the way to Bob. \sonja{compare the chance of being present on every
+  layer AND chosen in the first layer to regular onion routing where she
+  needs to be the (sole) node on each layer. Are we doing
+  better/worse/the same?}
 
@@
 properties of Sphinxes (inherited from Sphinx), Eve cannot know for certain if 
-Alice is the first node and Bob is the last node.
-
-\paragraph*{Limitations}%
-\label{security-limitations}
-
-A global, passive, network-observing adversary can of course do statistical 
-disclosure attacks to eventually learn who communicates with 
-whom~\cite{StatisticalDisclosureAttacks}.
-There are also denial of service attacks that can lead to the adversary 
-learning more from the system~\cite{DenialOfSecurity}.
-It is difficult to say to what extent our system might be vulnerable to this 
-type of attack without a deeper analysis.
-Such an analysis is out of scope of this analysis, here our focus is to protect 
-Alice and Bob from each other and their friends who also participate as nodes 
-in the network, not to protect them from \eg the \ac{NSA}.
-However, we hypothesize that our stateless and redundant design might yield 
-some advantages, \eg no control messages sent from where the adversary have 
-introduced an error back to the source.
-But these advantages will only postpone the success of the attack, eventually 
-even our protocol must resend.
-\commentDaniel{We should look into this denial of security.}
+Alice is the first node and Bob is the last node. \sonja{but what can
+  she learn/guess?}
 
@@
 Stateless routing can result in re-ordered chunks or packets, and
-chunks received on different devices of a user's squad. From
-Sphinx, we inherit IDs for packets that we we include in the
-out-of-band metadata on the file to be exchanged, as an ordered list,
-that is used to re-order chunks if need be. The squad overlay handles
-inter-squad device coordination. Liveness despite the possibility of squad devices going offline during
-transfer or other node or link failures is ensured by acknowledgments
-and timeouts as detailed in ~\cref{sec:squad_overlay}.
+chunks received on different devices of a user's squad. From Sphinx,
+we inherit IDs for packets that we we include in the out-of-band
+metadata on the file to be exchanged, as an ordered list, that is used
+to re-order chunks if need be. The squad overlay handles inter-squad
+device coordination. Liveness despite the possibility of squad devices
+going offline during transfer or other node or link failures is
+ensured by acknowledgments and timeouts as detailed in
+~\cref{sec:squad_overlay}.
+
+\paragraph*{Extended adversary model}%
+\label{security-limitations}
+
+A global, passive, network-observing adversary can of course do
+statistical disclosure attacks to eventually learn who communicates
+with whom~\cite{StatisticalDisclosureAttacks}. \sonja{Daniel: the
+  reference seems to be missing}  There are also denial
+of service attacks that can lead to the adversary learning more from
+the system~\cite{DenialOfSecurity}.  As mentioned in
+\cref{system-model}, we share the adversary model with Tor and Sphinx
+and thus exclude a global passive adversary. Our focus is on
+protecting Alice and Bob from each other and from others who also
+participate as nodes in the network, not on protecting them from
+surveillance. Nevertheless, we offer some reflections on such an
+adversary. We hypothesize that our stateless and redundant design
+might yield some advantages over traditional onion routing. For
+example, no control messages are sent back to the source if the
+adversary has introduced an error.  \sonja{``But these advantages will
+  only postpone the success of the attack, eventually even our
+  protocol must resend.'' why?}  \commentDaniel{We should look into
+  this denial of security.} We would also like to point out that
+vulnerability to a global passive attacker is not inherent in Sphinx
+or Sphinxes, but can be caused by the way they are applied, \ie the
+traffic sent. If performance and resource consumption were not an
+issue, batched and well-timed message or file transfer by all nodes
+would render traffic analysis pointless.

### 2018-08-06 paper/related.tex

@@
 
-There have been several attempts at P2P storage, mostly for backup. Wuala, Farsite, Nebulostore.
-\sonja{will expand and cite}
+There have been several fully implemented attempts at P2P storage, mostly for backup, such as Wuala\footnote{http://www.wuala.com} (later changed to client-server architecture, now closed down), Farsite~\cite{farsite} (no longer in use), Nebulostore~\cite{nebulo} (maintained but not deployed).
+They deliberately use storage and replication on other peers, something we aim to avoid, even though the privacy risk is reduced compared to a central provider.
 
-P2P file sharing has been researched extensively, with respect to aspects such as architecture (starting with the semi-centralized Napster, then decentralized Gnutella), availability and replication~\cite{replica}, scalability (Bittorrent~\cite{bittorrent-incentives}), anonymity (Freenet~\cite{Clarke:2001}, TOR~\cite{Tor}), and distributed hash tables (DHT) such as CAN, Chord, Pastry, and Tapestry (see \cite{dhtchurn} for an overview).
+P2P file sharing has been researched extensively, with respect to aspects such as architecture (starting with the semi-centralized Napster, then decentralized Gnutella), availability and replication~\cite{replica}, scalability (Bittorrent~\cite{bittorrent-incentives}), anonymity (Freenet~\cite{Clarke:2001}, Tor~\cite{Tor}), and distributed hash tables (DHT) such as CAN, Chord, Pastry, and Tapestry (see \cite{dhtchurn} for an overview).
 In contrast to our work, the main goal was to enable dissemination to many users who do not necessarily know each other in person.
-Here, we focus on sharing files in a more deliberate yet ad-hoc manner, i.e., between users that out-of-band agree to share a file but do not keep it available for anyone else in the future.
-TOR~\cite{Tor}, although not designed for file sharing specifically, comes closest in that respect, but does not address the following aspect.
-
-There is a concern shared with traditional P2P file sharing, namely churn~\cite{dhtchurn} and its effect on availability - here in the narrow context of the set of user devices based on user behavior.
-We thus discuss the related work on predicting device availability next, though to the best of our knowledge we are the first to make use of such predictions to cope with churn in interoperating sets of user devices.
+Here, we focus on sharing files in a more deliberate yet ad-hoc manner, \ie between users that out-of-band agree to share a file but do not keep it available for anyone else in the future.
 
@@
 
-Onion routing, with infrastructure and governance (Tor) and without (I2P), are geared toward web browsing. \sonja{will expand and cite}
+Onion routing schemes, with infrastructure and governance (Tor~\cite{Tor}) and without (I2P~\footnote{https://geti2p.net/en/}), though geared toward web browsing, come closest to file transfer without third-party storage.
+They do not, however, allow for unreliable user devices as relay nodes.
+There is a concern shared with traditional P2P file sharing, namely churn~\cite{dhtchurn} and its effect on availability - here in the narrow context of the set of user devices based on user behavior.
+We thus discuss the related work on modeling and predicting device availability next, though to the best of our knowledge we are the first to make use of such predictions to cope with churn in interoperating sets of user devices.
 
-\sonja*{include some on Modeling devices' connection and disconnection}
+%\sonja*{include some on Modeling devices' connection and disconnection}
 
@@
 %\paragraph*{Modeling devices' connection and disconnection} 
-% To simulate users' devices participating in a distributed protocol, we build upon existing literature on two topics: 
-% multi-device interaction, and churn in P2P networks.
+To simulate users' devices participating in a distributed protocol, we build upon existing literature on two topics: 
+multi-device interaction, and churn in P2P networks.
 
-%In our experiments, we simulate users' devices participating in a distributed protocol. We base our modeling of devices' online availability on existing literature such as the following.  
-% Field studies provide \emph{usage and connectivity patterns of users' appliances}.
+In our experiments, we simulate users' devices participating in a distributed protocol. We base our modeling of devices' online availability on existing literature such as the following.  
+Field studies provide \emph{usage and connectivity patterns of users' appliances}.
 Karlson et al.
@@
 \cite{Wagner_Rice_Beresford_2013} conducted a thorough data collection on Android devices via an application called Device Analyzer, that collected metrics on movement patterns, connectivity and energy consumption from 16,000 users.
-% %\commentAL{Conclude: will we use their dataset? Why are these papers useful to us?}
-% Several works point out the emerging trend of \emph{multi-device interaction}.
-% A 2012 Google-led study \cite{google2012} stated that the USA are nowadays ``a nation of multi-screeners''.
+%\commentAL{Conclude: will we use their dataset? Why are these papers useful to us?}
+Several works point out the emerging trend of \emph{multi-device interaction}.
+A 2012 Google-led study \cite{google2012} stated that the USA are nowadays ``a nation of multi-screeners''.
 People switch their attention toward their phone, laptop, tablet or their television depending on the context.
-% M\"uller et al. \cite{Muller_Gove_Webb_Cheang_2015} specifically compared the usage patterns of phones against tablets.
-% Jokela et al. \cite{Jokela_Ojala_Olsson_2015} and \cite{google2012} also differentiated sequential and parallel usage of one's multiple devices.
-% Research in P2P networks observed \cite{Stutzbach_Rejaie_2006} and modeled \cite{Yao_Leonard_Wang_Loguinov_2006} patterns of \emph{churn} (\ie participants moving in and out of a system).
-% We take inspiration from these works in order to establish credible models of user behaviors to evaluate our protocol. 
-% Participants can own several devices: their smartphone is always on, but lacks processing power, while their laptop is rarely online, though it contains better hardware, etc.
+M\"uller et al. \cite{Muller_Gove_Webb_Cheang_2015} specifically compared the usage patterns of phones against tablets.
+Jokela et al. \cite{Jokela_Ojala_Olsson_2015} and \cite{google2012} also differentiated sequential and parallel usage of one's multiple devices.
+Research in P2P networks observed \cite{Stutzbach_Rejaie_2006} and modeled \cite{Yao_Leonard_Wang_Loguinov_2006} patterns of \emph{churn} (\ie participants moving in and out of a system).
+We take inspiration from these works in order to establish credible models of user behaviors to evaluate our protocol. 
+Participants can own several devices: their smartphone is always on, but lacks processing power, while their laptop is rarely online, though it contains better hardware, etc.

### 2018-08-06 paper/sphinxes.tex

@@
     traverse before reaching its destination.
-    Further, let \(w_L\) be the maximum width of a layer, \ie the maximum 
+  % I spent minutes looking for w_L: it deserves its bullet!
+  \item \(w_L\) is the maximum width of a layer, \ie the maximum 
     number of alternative nodes on a layer.
@@
 First we generate all the needed keys.
-We compute \(\nu+1\) tuples
+We compute \(\nu+1\) tuples:
 \begin{align*}
@@
 \end{align*}
-In addition, we compute
+In addition, we compute:
 \begin{align*}
@@
 \]
-We then construct the ciphertexts
+We then construct the ciphertexts:
 \begin{align*}
@@
   \concat \prp'\left(\hash_{\prp'}\left(s_\nu^{(|L_\nu|-1)}\right) 
-    s_\nu\right).
+    s_\nu\right),
 \end{align*}
@@
 Next we need to compute the padding \(\phi_i\) for each layer \(i\).
-We must do this is to predict the padding introduced at each layer so that we 
+We must do this to predict the padding introduced at each layer so that we 
 can compute the correct \acp{MAC} (\(\gamma_i\)).

### 2018-08-06 paper/intro.tex
Updates contributions

@@
 reconstructed frequently, which is particularly costly. By contrast, Tor
-\cite{Dingledine:2004}, one of the most popular anonymous networks,
+\cite{Tor}, one of the most popular anonymous networks,
 trades lower anonymity guaranties for a much better performance. Tor's lower protection arises from
@@
 \begin{itemize}
-\item We have designed \name, a novel fully decentralized, autonomous,
-and self-organizing file sharing service among users based on a novel
-concept named Probabilistic Onion Routes (POR), which combines onion routing with
-probabilistic node selection, informed by random peer sampling and
-Hidden Markov Model predictions for node availability;
-\item  We have demonstrated the successfulness of our approach. Even
-  suboptimal prediction results in successful file transfer with high
-  probability. 
+  \item We provide the Sphinxes mix-header format which extends 
+    Sphinx~\cite{Sphinx} to a source-routed limited random-walk protocol --- 
+    \ie each layer of the onion route contains several alternative next nodes.
+
+  \item We provide the \ac{SPOR} node selection strategy which, given a secure 
+    \ac{RPS} protocol and availability estimates, selects nodes to populate the 
+    layers of Sphinxes to maximize the availability of the route --- this 
+    yields reliable routes even with low-availability nodes.
+
+  \item We provide a protocol for a device swarm to estimate the availabilities 
+    of its own devices.
+    These availabilities can then be used with \ac{SPOR}.
+    \commentDaniel{We should add some more details, maybe.}
+
+  \item We use \ac{SPOR} to design \name: a novel, fully decentralized, 
+    autonomous and self-organizing file transfer service among users.
 \end{itemize}

### 2018-08-06 paper/intro.tex
added sphinxes contribution, rephrased contributions

--- 2018-08-01 paper/intro.tex
@@
 \item We have designed \name, a novel fully decentralized, autonomous,
-and self-organizing file sharing service among users based on a novel
-concept named Probabilistic Onion Routes (POR), which combines onion routing with
+and self-organizing file transfer service among users based on a novel
+concept named Stateless Probabilistic Onion Routes (SPOR), which combines onion routing with
 probabilistic node selection, informed by random peer sampling and
-Hidden Markov Model predictions for node availability;
-\item  We have demonstrated the successfulness of our approach. Even
+predictions for node availability;
+\item We have extended Sphinx~\cite{Sphinx}, a compact and secure
+  message header format for mixnets, to allow for sets of nodes
+  instead of single nodes for onion routing layers, resulting in a
+  hybrid between source routing and ad-hoc node  selection that can
+  deal with unreliable nodes;
+\item  We have demonstrated the feasibility of our approach without
+  third-party storage, both in terms of security and performance . Even
   suboptimal prediction results in successful file transfer with high
@@
 In the following, in Section~\ref{system-model}, we introduce the
-adversary model and the desired privacy properties of \name. Section~\ref{design}
-introduces the design of our proposed solution. In Section~\ref{security-discussion}, we lead a security discussion
-about advantages and shortcomings of our approach. Section~\ref{Performance}
-evaluates \name. 
-Finally, Section~\ref{conclusion} discusses future work and conclusions.
+system and adversary models as well as the desired security and privacy properties of \name. Section~\ref{design}
+introduces the design of our proposed solution. In
+Sections~\ref{security-discussion} and ~\ref{Performance},
+respectively, we evaluate the security and performance of our
+approach. We set \name into context with related work in
+Section~\ref{related-work} and conclude with Section~\ref{conclusion}.
+
 % Cashmere: resilient anonymous routing.

### 2018-08-06 paper/intro.tex

--- 2018-08-06 paper/intro.tex
@@
 \begin{itemize}
+\sonja{commented out my changes, left Daniel's in merge conflict, left
+  my changes on paper outline} 
+% \item We have designed \name, a novel fully decentralized, autonomous,
+% and self-organizing file transfer service among users based on a novel
+% concept named Stateless Probabilistic Onion Routes (SPOR), which combines onion routing with
+% probabilistic node selection, informed by random peer sampling and
+% predictions for node availability;
+% \item We have extended Sphinx~\cite{Sphinx}, a compact and secure
+%   message header format for mixnets, to allow for sets of nodes
+%   instead of single nodes for onion routing layers, resulting in a
+%   hybrid between source routing and ad-hoc node  selection that can
+%   deal with unreliable nodes;
+% \item  We have demonstrated the feasibility of our approach without
+%   third-party storage, both in terms of security and performance . Even
+%   suboptimal prediction results in successful file transfer with high
+%   probability.
+
   \item We provide the Sphinxes mix-header format which extends 
@@
     autonomous and self-organizing file transfer service among users.
+
 \end{itemize}

### 2018-08-06 paper/squad-overlay-design.tex
by luxey et al

@@
 
-To achieve this goal, we adapt the Cascade protocol~\cite{luxey:cascade} to suit our needs. 
-Using Cascade, participating nodes gossip in a push-pull manner: 
+To achieve this goal, we adapt the Sprinkler protocol, proposed by Luxey et al.~\cite{luxey:hal-01704172}, to suit our needs. 
+Using Sprinkler, participating nodes gossip in a push-pull manner: 
 when a node has new information, it sends it to a fixed-size random subset of its peers; 
@@
 
-Given this information dissemination and history reconciliation mechanism, each \squad member knows the full sequence $S$ at all time with an overwhelming probability, even in the face of churn.
+Given this information dissemination and history reconciliation mechanism, each \squad member knows the full sequence $S$ at all time with an overwhelming probability, even in the face of churn~\cite{luxey:cascade}.
 
@@
 \label{ssec:por}
-
-\commentAL{We need to merge \ref{SPOR} and this section.}
 

### 2018-08-06 paper/intro.tex

@@
 
+\sonja{commented out my changes, left Daniel's in merge conflict, left
+  my changes on paper outline} 
 Our contributions are as follows: 
 \begin{itemize}
-\sonja{commented out my changes, left Daniel's in merge conflict, left
-  my changes on paper outline} 
+
 % \item We have designed \name, a novel fully decentralized, autonomous,
@@
 introduces the design of our proposed solution. In
-Sections~\ref{security-discussion} and ~\ref{Performance},
+Sections~\ref{security-discussion} and \ref{Performance},
 respectively, we evaluate the security and performance of our
 approach. We set \name into context with related work in
-Section~\ref{related-work} and conclude with Section~\ref{conclusion}.
+Section~\ref{RelatedWork} and conclude with Section~\ref{conclusion}.
 

### 2018-08-07 paper/evaluation.tex
experiment going on

@@
 
-In the following, we perform two types of experiments: 
-section~\ref{sub:predictive_onion_routes_creation} evaluates the establishment of PORs, while section~\ref{sub:file_transfer} handles file transfer.
-For that reason, they used different parameter sets.
+\newcommand\trps{\ensuremath{t_{\text{RPS}}}}
 
-\paragraph*{PORs creation}
-Figure \ref{fig:success_rate_vs_t} come from the same data, with 10 experiments per set of settings.
-$\theta$, the threshold of the probability that all nodes fail at once, takes the following values: $[0.1, 0.01, 0.001, 0.0001]$.
-$L$, the number of layers constituting a route, takes the following values: $[3, 5, 7]$.
-The time since route establishment goes from 1 to 10 with  unit step.
-It is measured in time periods $T$, the interval at which users change the connection state of their devices.
-An experiment consisted in $L*5$ users, where we randomly picked pairs of users to compute 20 routes.
-Hence, each point on the top of figure~\ref{fig:success_rate_vs_t} is the average of 3000 layers size; 
-each point on the bottom is the availability rate over 200 routes.
+All our experiments were conducted with 25 users participating in \name. 
+The files exchanged are a collection of 12 real ones, ranging from 5KB to 640MB.
 
-\paragraph*{File exchange}
-In section~\ref{sub:file_transfer}, we fix the routes' creation parameters: $\theta=10^-3$, $L=3$.
-The number of users is set to 20, and the number of file exchange per experiment to 10.
-We use a constant file chunk size of 512kB, a constant header size of 100kB, and a constant bandwidth per link of 128kB/s.
+\paragraph*{Random Peer Sampling} It has three parameters: the period between two views exchange \trps, set to 400ms, the size of the exchanged views (6) and the size of the devices' view \view, set to 30.
+Using a bigger view would result in more descriptors choice when crafting routes, but their descriptor would be more stale: descriptors in a view have a lifetime of $|\view| * \trps$ seconds on average.
 
-\subsection{Predictive Onion Routes creation} % (fold)
-\label{sub:predictive_onion_routes_creation}
+\paragraph*{Sprinkler} The \squad overlay has two parameters: the fanout of the gossip exchange when a device has new information to share, set to 3, and the initial length of the sequence $S$ (cf.
+section~\ref{ssec:device_availability}), set to 50.
+The latter provides initial knowledge to \squad members: their peers addresses, among with an estimate of the user's prior behavior.
 
-We first measure the influence of the parameter $\theta$ on the number of nodes per layer on the top of figure~\ref{fig:success_rate_vs_t}, by displaying average and standard deviation of the number of nodes for $\theta=[10^{-4}, 10^{-3}, 10^{-2}, 10^{-1}]$ (the other experiment parameters are listed in section~\ref{ssub:experimental_parameters}).
-As we can see, the number of devices per layer logarithmically decreases as we relax the constraint on the layer's availability.
-The mean number of devices per layer lies between 2 and 6.
-Still, the number of nodes per layer is very variable: at $\theta=10^{-4}$, values range from 2 to 11, with a standard deviation of 1.44.
+\paragraph*{PORs} We used a constant amount of 3 layers per routes (excluding the final, destination layer),
+and a constant number of peers per layer $w_\layer$ of 16.
+The latter heavily influences both the network overhead (the more, the bigger the headers), and the routes' availability (more peers means a better probability that at least one peer is online in a layer).
+The default availability threshold $\theta$ is $10^-3$.
 
-\begin{figure}[t]
-\centering
-\includegraphics[width=0.7\columnwidth]{figures/nodes_per_layer_vs_theta.pdf}
-\vspace{1ex}
-\includegraphics[width=0.9\columnwidth]{figures/success_rate_vs_t.pdf}
-\caption{\label{fig:success_rate_vs_t}On top: Number of nodes per layer of POR as a function of the parameter $\theta$ (the maximal probability that all nodes in a layer fail at once).
+\paragraph*{File transfer} The main parameter here is the chunk size \chunksize, that was set to 512KB, which is considered, in BitTorrent, to be a good trade-off between network efficiency and number of chunks.
+The other parameter, \tupload, was empirically set to 500ms.
+
+\paragraph*{Users' behavior} Finally we set \tuser to 3s.
+
+\trps, \tupload and \tuser are correlated, but otherwise meaningless since \tuser is artificial. 
+Their values were thus empirically chosen to balance efficiency, network traffic and the experiments' duration.
+
+\subsection{File transfer}
+\label{sub:file_transfer}
+
+Using the previous parameters, we performed our experiment 30 times, and combined the results to smooth the results, given the variability of the stochastic processes involved (most notably the devices' churn).
+
+% In the following, we perform two types of experiments: 
+% section~\ref{sub:predictive_onion_routes_creation} evaluates the establishment of PORs, while section~\ref{sub:file_transfer} handles file transfer.
+% For that reason, they used different parameter sets.
+
+% \paragraph*{PORs creation}
+% Figure \ref{fig:success_rate_vs_t} come from the same data, with 10 experiments per set of settings.
+% $\theta$, the threshold of the probability that all nodes fail at once, takes the following values: $[0.1, 0.01, 0.001, 0.0001]$.
+% $L$, the number of layers constituting a route, takes the following values: $[3, 5, 7]$.
+% The time since route establishment goes from 1 to 10 with  unit step.
+% It is measured in time periods $T$, the interval at which users change the connection state of their devices.
+% An experiment consisted in $L*5$ users, where we randomly picked pairs of users to compute 20 routes.
+% Hence, each point on the top of figure~\ref{fig:success_rate_vs_t} is the average of 3000 layers size; 
+% each point on the bottom is the availability rate over 200 routes.
+
+% \paragraph*{File exchange}
+% In section~\ref{sub:file_transfer}, we fix the routes' creation parameters: $\theta=10^-3$, $L=3$.
+% The number of users is set to 20, and the number of file exchange per experiment to 10.
+% We use a constant file chunk size of 512kB, a constant header size of 100kB, and a constant bandwidth per link of 128kB/s.
+
+% \subsection{Predictive Onion Routes creation} % (fold)
+% \label{sub:predictive_onion_routes_creation}
+
+% We first measure the influence of the parameter $\theta$ on the number of nodes per layer on the top of figure~\ref{fig:success_rate_vs_t}, by displaying average and standard deviation of the number of nodes for $\theta=[10^{-4}, 10^{-3}, 10^{-2}, 10^{-1}]$ (the other experiment parameters are listed in section~\ref{ssub:experimental_parameters}).
+% As we can see, the number of devices per layer logarithmically decreases as we relax the constraint on the layer's availability.
+% The mean number of devices per layer lies between 2 and 6.
+% Still, the number of nodes per layer is very variable: at $\theta=10^{-4}$, values range from 2 to 11, with a standard deviation of 1.44.
+
+% \begin{figure}[t]
+% \centering
+% \includegraphics[width=0.7\columnwidth]{figures/nodes_per_layer_vs_theta.pdf}
+% \vspace{1ex}
+% \includegraphics[width=0.9\columnwidth]{figures/success_rate_vs_t.pdf}
+% \caption{\label{fig:success_rate_vs_t}On top: Number of nodes per layer of POR as a function of the parameter $\theta$ (the maximal probability that all nodes in a layer fail at once).
 The number of nodes logarithmically decreases as we relax the $\theta$ constraint.
 On bottom: Availability rate of routes as a function of the time since the route establishment, for several values of the parameters $\theta$ (the maximal probability that all nodes in a layer fail at once) and $L$ (the number of layers in the route).}
-\end{figure}
+% \end{figure}
 
-We now study the influence of the parameters on the future availability of the routes in figure~\ref{fig:success_rate_vs_t}.
-We consider a route available if at least one node per layer is online at this time.
-The plots reads the mean availability of routes as a function of the time since the route's establishment, for every couple of parameters $(\theta, L)$.
-First of all, we observe that time has a negligible impact on the availability of routes. 
-This shows, as was stated in section~\ref{para:predicting future behavior}, that the prediction that devices make of behavior at $t+1$ is a good enough estimator for $t+i$.
-We also see that $\theta$ has a big impact on the mean availability and its variability.
-Still, $\theta\in\{10^-4, 10^-3\}$ allows highly available routes with an average availability of 100\% and 99.5\% respectively.
-Combined with the results from figure~\ref{fig:success_rate_vs_t}, it means that routes will need an average of 5-6 devices per layer to be highly available.
-Finally, increasing $L$ logically hinders the results when using low-availability layers.
-\\
+% We now study the influence of the parameters on the future availability of the routes in figure~\ref{fig:success_rate_vs_t}.
+% We consider a route available if at least one node per layer is online at this time.
+% The plots reads the mean availability of routes as a function of the time since the route's establishment, for every couple of parameters $(\theta, L)$.
+% First of all, we observe that time has a negligible impact on the availability of routes. 
+% This shows, as was stated in section~\ref{para:predicting future behavior}, that the prediction that devices make of behavior at $t+1$ is a good enough estimator for $t+i$.
+% We also see that $\theta$ has a big impact on the mean availability and its variability.
+% Still, $\theta\in\{10^-4, 10^-3\}$ allows highly available routes with an average availability of 100\% and 99.5\% respectively.
+% Combined with the results from figure~\ref{fig:success_rate_vs_t}, it means that routes will need an average of 5-6 devices per layer to be highly available.
+% Finally, increasing $L$ logically hinders the results when using low-availability layers.
+% \\
 
-We showed that creating reliable onion routes using a backbone of unreliable nodes is feasible by using predictive algorithms.
-The counterpart is that messages header size grows with the number of layers and the number of devices per layer.
+% We showed that creating reliable onion routes using a backbone of unreliable nodes is feasible by using predictive algorithms.
+% The counterpart is that messages header size grows with the number of layers and the number of devices per layer.
 
-Considering that most onion routing solutions use a statically defined message size to avoid information leakage, a bigger header means less space for the payload in each message.
+% Considering that most onion routing solutions use a statically defined message size to avoid information leakage, a bigger header means less space for the payload in each message.
 The more reliable the route, the bigger the number of messages per file.
@@
 
-\subsection{File transfer time} % (fold)
-\label{sub:file_transfer}
+% \subsection{File transfer time} % (fold)
+% \label{sub:file_transfer}
 
-To assess the efficiency of \name, we did several file exchanges with fixed parameters and a random file size between 5MB and 500MB.
-By performing 20 experiments using the parameters described in \ref{ssub:experimental_parameters}, we obtained traces for 200 file exchanges.
-All files reached their destination successfully.
+% To assess the efficiency of \name, we did several file exchanges with fixed parameters and a random file size between 5MB and 500MB.
+% By performing 20 experiments using the parameters described in \ref{ssub:experimental_parameters}, we obtained traces for 200 file exchanges.
+% All files reached their destination successfully.
 
-\begin{figure}[t]
-\centering
-\includegraphics[width=0.7\columnwidth]{figures/transfer_time_vs_size.pdf}
+% \begin{figure}[t]
+% \centering
+% \includegraphics[width=0.7\columnwidth]{figures/transfer_time_vs_size.pdf}
 
-\caption{\label{fig:transfer_time_vs_size}Files' transfer time as a function of their size, along with a log-linear regression of the same data.}
-\end{figure}
+% \caption{\label{fig:transfer_time_vs_size}Files' transfer time as a function of their size, along with a log-linear regression of the same data.}
+% \end{figure}
 
-Figure~\ref{fig:transfer_time_vs_size} shows the results of this experiment: it plots the transfer time as a function of the file size.
+% Figure~\ref{fig:transfer_time_vs_size} shows the results of this experiment: it plots the transfer time as a function of the file size.
 File size is binned into 20 bins, making the series of points representing the average transfer time per bin with standard deviation bars.
-We fitted a log-linear regression to this plot, displayed as a curve.
-It shows that transfer time increases less fast that the file size.
+% We fitted a log-linear regression to this plot, displayed as a curve.
+% It shows that transfer time increases less fast that the file size.
 
-Absolute time values are meaningless here: our system was evaluated on a single machine and on a single process.
+% Absolute time values are meaningless here: our system was evaluated on a single machine and on a single process.
 The code execution was not parallel, and only one device was executing at any point in time.
 
-Still, we investigated the message transmission.
+% Still, we investigated the message transmission.
 In this simulation, 145172 chunks were sent, and 141276 ACKs were received: 6.00\% of the chunks were lost in transit.
@@
 
-We now understand the log-linear curve and it's big initial slope: messages spend a long time in transit, but sending messages in parallel does not impact this time.
+% We now understand the log-linear curve and it's big initial slope: messages spend a long time in transit, but sending messages in parallel does not impact this time.
 Even small files thus need a lot of time to transfer, while bigger files do not suffer more than small files from the messages delay.
-\\
+% \\
 
-Overall, we succeeded in creating a reliable and secure file transfer protocol over an underlying network of unreliable, low-end devices.
-Its performance could be enhanced by taking interest in bottlenecks in the messages transmission, i.e. scheduling messages in a similar predictive manner as we planned routes creation.
+% Overall, we succeeded in creating a reliable and secure file transfer protocol over an underlying network of unreliable, low-end devices.
+% Its performance could be enhanced by taking interest in bottlenecks in the messages transmission, i.e. scheduling messages in a similar predictive manner as we planned routes creation.
 

### 2018-08-07 paper/squad-overlay-design.tex
experiment going on

@@
 
-\newcommand\layer{\ensuremath{{\mathcal{L}}}\xspace}
+%\newcommand\layer{\ensuremath{{\mathcal{L}}}\xspace}
+\newcommand\layer{L\xspace}
 \newcommand\Poff{\ensuremath{P_{\text{off}}}\xspace}
@@
 
+When a device creates a layer to reach its user, descriptors are not taken from \rpsview but from the \squad's sequence: all devices in this layer will belong to the user.
+The logic is otherwise the same.
+
 Recall that each layer in Sphinxes has a constant number of nodes $w_\layer$, that is a Sphinxes parameter.
@@
 \newcommand\hashchunk{\ensuremath{h_{\text{chunk}}}\xspace}
-\newcommand\hashfile{\ensuremath{h}\xspace}
+\newcommand\hashfile{h\xspace}
 
@@
 \newcommand\bitfield{\ensuremath{bf_f}\xspace}
+\newcommand\tupload{\ensuremath{t_{\text{upload}}}\xspace}
+
 \paragraph*{Chunks and bitfields}
@@
 Each chunk $c_i \in f$ is uploaded to Bob through a unique route $\mathcal{H}_{c_i}$.
-When $d_f$ is online, it periodically sends chunks of $f$ to Bob until $f$ is entirely uploaded.
+When $d_f$ is online, it periodically sends chunks of $f$ to Bob until $f$ is entirely uploaded, with a period of
 

### 2018-08-07 paper/conclusion.tex
typo in intro, started conclusion edits, more needed

@@
 the future and thus likely improve the throughput. From a security and
-privacy perspective, we were guided by the properties of
-TOR~\cite{Tor}, which we used to provide a modicum of privacy for this
-first investigation of feasibility of file-sharing between two users'
-squads of devices and modified to a stateless protocol to
-accommodate unreliable nodes. While we took the first steps toward
-analyzing the consequences of the modifications on security and
-privacy, more work is needed to provably ensure that the added feature
-of resilience despite unreliable nodes (supported by peer sampling)
-does 
-%and the side effect of enabling more local TOR routing (for example,
-%keeping routes inside a country) do 
-not compromise security. Another
-consideration is the nature of the traffic in this scenario and the
-limits of protection against statistical inference.
+privacy perspective, we were guided by the properties for secure onion
+routing schemes defined by~\cite{CLOnionRouting} and added a property
+for device-unlinkability to prevent inferences from availiability data.
+% TOR~\cite{Tor}, which we used to provide a modicum of privacy for this
+% first investigation of feasibility of file-sharing between two users'
+% squads of devices and modified to a stateless protocol to
+% accommodate unreliable nodes. While we took the first steps toward
+% analyzing the consequences of the modifications on security and
+% privacy, more work is needed to provably ensure that the added feature
+% of resilience despite unreliable nodes (supported by peer sampling)
+% does 
+% %and the side effect of enabling more local TOR routing (for example,
+% %keeping routes inside a country) do 
+% not compromise security. Another
+% consideration is the nature of the traffic in this scenario and the
+% limits of protection against statistical inference.
 

### 2018-08-07 paper/evaluation.tex
figures!

@@
 
-To evaluate our protocol, we built a prototype of \name that implements all the features previously described but the encryption processes (Sphinxes).
-It consists of 5400 lines of Go code.
-The users and their behavior (i.e. devices usage and file exchange decisions), on their part, are simulated.
+To evaluate our protocol, we built a prototype of \name that implements the complete \name protocol in 5400 lines of Go code.
+The users and their behavior (i.e. devices usage and file exchange decisions), on their part, are simulated by 1500 lines of Python.
 Each device is a Docker container that ships the same \name code, and communicates with its peers via TCP connections.
@@
 
-\newcommand\trps{\ensuremath{t_{\text{RPS}}}}
-
 All our experiments were conducted with 25 users participating in \name. 
@@
 
-\paragraph*{Random Peer Sampling} It has three parameters: the period between two views exchange \trps, set to 400ms, the size of the exchanged views (6) and the size of the devices' view \view, set to 30.
-Using a bigger view would result in more descriptors choice when crafting routes, but their descriptor would be more stale: descriptors in a view have a lifetime of $|\view| * \trps$ seconds on average.
+\paragraph*{Random Peer Sampling} It has three parameters: the period between two views exchange \trps, set to 400ms, the size of the exchanged views (6) and the size of the devices' view \rpsview, set to 30.
+Using a bigger view would result in more descriptors choice when crafting routes, but their descriptor would be more stale: descriptors in a view have a lifetime of $|\rpsview| * \trps$ seconds on average.
 
@@
 
+Finally, the experiments had a timeout of 15 minutes. 
+We observed that downloads---however big---usually succeeded long before this time, or did not succeed whatever time was given to them.
+
 \subsection{File transfer}
@@
 
-Using the previous parameters, we performed our experiment 30 times, and combined the results to smooth the results, given the variability of the stochastic processes involved (most notably the devices' churn).
+Using the previous parameters, we performed our experiment 30 times, yielding 360 file exchanges.
+Plots show the aggregation of the results from all experiments, which alleviates the high variability of the stochastic processes involved (most notably the devices' churn).
+
+\begin{figure}[t]
+  \centering
+  %\def\svgwidth{0.8\columnwidth}
+  \includegraphics[width=0.8\columnwidth]{figures/logistic_many_0-001.pdf}
+
+  \caption{\label{fig:logistic}
+  Logistic regression of the success rate as a function of the file size using the default parameters.}
+\end{figure}
+
+Figure~\ref{fig:logistic} shows the logistic regression of the success rate as a function of the files' size. 
+This regression is good candidate to describe binary stochastic processes as a function of a dependent variable,
+and is often used in epidemics prediction, economics, and even marketing.
+Simply put, given $X$ (in our case, the size of each transfered file) and $y$ (the outcome of the transfer: success or failure), 
+the regressor estimates the coefficient $k$ and the mid-point $x_0$ of the logistic function defined as follows:
+
+$$ f(x) = \frac{1}{1 + e^{-k \cdot x + x_0 }} $$
+
+Because it sets the top (100\%) and bottom (0\%) values as asymptotes, 
+logistic regression does not yield very optimistic success rates at the beginning,
+but its midpoint $x_0$ tends to be very accurate even with a low quantity of training samples.
+
+In our case, $f(x)$ reads the probability that a file exchange fails given its size. 
+The plot reads that files below 319MB have more than 90\% chances of being successfully exchanged.
+The probability falls as the file gets bigger, such that a 1,O43MB has 50\% chances of successful transfer (see $x_0$).
+
+\subsection{Shortcomings} % (fold)
+\label{sub:shortcomings}
+
+There are several aspects in \name that can endanger its security or hinder its performance.
+First off, we study the RPS and its capacity to provide a random subset of the whole participants list.
+
+% subsection shortcomings (end)
 

### 2018-08-07 paper/related.tex
taking away related work on prediction, contrasting with replication

--- 2018-07-18 paper/related.tex
@@
 
-Onion routing, with infrastructure and governance (Tor) and without (I2P), are geared toward web browsing. \sonja{will expand and cite}
+Onion routing schemes, with infrastructure and governance (Tor~\cite{Tor}) and without (I2P~\footnote{https://geti2p.net/en/}), though geared toward web browsing, come closest to file transfer without third-party storage.
+They do not, however, allow for unreliable user devices as relay nodes.
 
-\sonja*{include some on Modeling devices' connection and disconnection}
+The main concern, shared with traditional P2P file sharing, is churn~\cite{dhtchurn} and its effect on availability. % - here in the narrow context of the set of user devices based on user behavior. 
+The commonly used approach of replication and redundancy used to handling churn does not work in our case as we prioritize privacy and independence from third-party storage.
 
-%\commentAL{Will need another pass.}
-%\paragraph*{Modeling devices' connection and disconnection} 
+% We thus discuss the related work on modeling and predicting device availability next, though to the best of our knowledge we are the first to make use of such predictions to cope with churn in interoperating sets of user devices.
+
+% %\sonja*{include some on Modeling devices' connection and disconnection}
+
+% %\commentAL{Will need another pass.}
+% %\paragraph*{Modeling devices' connection and disconnection} 
 % To simulate users' devices participating in a distributed protocol, we build upon existing literature on two topics: 
@@
 
-%In our experiments, we simulate users' devices participating in a distributed protocol. We base our modeling of devices' online availability on existing literature such as the following.  
+% In our experiments, we simulate users' devices participating in a distributed protocol. We base our modeling of devices' online availability on existing literature such as the following.  
 % Field studies provide \emph{usage and connectivity patterns of users' appliances}.

### 2018-08-07 paper/evaluation.tex
figures!
removed shortcomings in evaluation

@@
 
+Overall, we saw 94\% of successful file transfer.
+
 \begin{figure}[t]
@@
 but its midpoint $x_0$ tends to be very accurate even with a low quantity of training samples.
+\commentAL{Yes indeed, very pessimistic, where is our 94\%!? I want to make a CDF also.}
 
@@
 
-\subsection{Shortcomings} % (fold)
-\label{sub:shortcomings}
+% \subsection{Shortcomings} % (fold)
+% \label{sub:shortcomings}
 
-There are several aspects in \name that can endanger its security or hinder its performance.
-First off, we study the RPS and its capacity to provide a random subset of the whole participants list.
+% There are several aspects in \name that can endanger its security or hinder its performance.
+% First off, we study the RPS and its capacity to provide a random subset of the whole participants list.
 

### 2018-08-07 paper/security-discussion.tex
rps requirements in security discussion
Adds security of SPORES to discussion

@@
 
+Although the requirements on \ac{RPS} of being uniformly randomly
+distributed and privacy-preserving are not easily met in practice,
+there are some promising candidates~\cite{Octopus, BrahmsRPS}.\name
+does not put any other constraints on the \ac{RPS} used.
+
+\paragraph*{Security of \ac{SPORES}}
+
+\Ac{SPORES} inherits the security properties from Sphinxes and \ac{SPOR}.
+However, both Sphinxes and \ac{SPOR} can be used with any mixing strategy, and 
+the security they provide is as secure as the mixing strategy (or flushing 
+algorithm) allows.
+Since \ac{SPORES} is a fully-fledged system, it must make a concrete choice for 
+the mixing strategy.
+Since \ac{SPORES} aims at low latency, routers do not batch and mix incoming 
+messages; it immediately forwards the messages.
+This puts \ac{SPORES} in the same position as Tor~\cite{Tor}, \ie more 
+vulnerable to traffic analysis than batching 
+mix-nets~\cite{RoutingSurveyAnonymousProtocols} \commentDaniel{we should 
+  probably look for the original papers} --- this vulnerability is inherited 
+from the mixing strategy.
+
+\Ac{SPORES} also inherits a vulnerability from random-walk protocols and the 
+fact that a large message is split into chunks.
+Since the chunks can take several paths from source to destination, the source 
+will send and the destination will receive more traffic than other nodes in the 
+network~\cite{RoutingSurveyAnonymousProtocols} \commentDaniel{we should 
+  probably look for the original papers}.
+However, this is slightly alleviated by the fact that the source and 
+destination can be several different devices --- \ie from the \squad{}s.
+
 \paragraph*{Robustness}

### 2018-08-07 paper/security-discussion.tex
Fixes typos in security discussion

@@
 going offline during transfer or other node or link failures is
-ensured by acknowledgments and timeouts as detailed in
-~\cref{sec:squad_overlay}.
+ensured by acknowledgements and timeouts as detailed in
+\cref{sec:squad_overlay}.
 

### 2018-08-07 paper/evaluation.tex
bandwidth
new figure

@@
 
+\begin{figure}[t]
+  \centering
+  %\def\svgwidth{0.8\columnwidth}
+  \includegraphics[width=\columnwidth]{figures/bw_and_pending_files.pdf}
+
+  \caption{\label{fig:bw_and_pending_files}In gray: number of pending file exchanges; in black: mean outbound traffic (kB) per node per second.}
+\end{figure}
+
+\begin{figure}[t]
+  \centering
+  %\def\svgwidth{0.8\columnwidth}
+  \includegraphics[width=\columnwidth]{figures/bw_and_pending_files_log.pdf}
+
+  \caption{\label{fig:bw_and_pending_files_log}In gray: number of pending file exchanges; in black: mean outbound traffic (kB) per node per second.}
+\end{figure}
+
 % \subsection{Shortcomings} % (fold)

### 2018-08-07 paper/design.tex
Readds Daniel's file transfer description
edits, terminology, comments with questions

@@
 \label{design}
-\sonja{will frame and structure (A) squad overlay (prediction) (B)
-  global overlay (RPS) (C) sphinxes (incl.\ sphinx, onion routing in
-  general) (D) SPOR and SPORES (E) encryption (hybrid, payload, header)
-  if not included earlier (F) out-of-band}
-\commentDaniel{I suggest the following structure:
-  (A) Sphinxes
-  (B) SPOR (global overlay)
-  (C) SPORES (local overlay).
-  My original idea was to make Sphinxes its own section before the design 
-  section instead of a subsection in the design section.}
+% \sonja{will frame and structure (A) squad overlay (prediction) (B)
+%   global overlay (RPS) (C) sphinxes (incl.\ sphinx, onion routing in
+%   general) (D) SPOR and SPORES (E) encryption (hybrid, payload, header)
+%   if not included earlier (F) out-of-band}
+% \commentDaniel{I suggest the following structure:
+%   (A) Sphinxes
+%   (B) SPOR (global overlay)
+%   (C) SPORES (local overlay).
+%   My original idea was to make Sphinxes its own section before the design 
+%   section instead of a subsection in the design section.}
 
-Our goal is to enable private and reliable file exchange between users 
+Our goal is to enable private and reliable file transfer between users 
 participating in the system, by using their respective devices only.
@@
 
-\sonja{Here comes more of a solution overview and reference to the outline
-  figure.}
-Figure~\ref{fig:outline} shows the components needed to obtain this
-routing information.
+Figure~\ref{fig:outline} shows the components needed to obtain the
+routing information for the headers.
 
@@
 
-\sonja{might need different naming, and deciding about predictive and probabilistic}
 \begin{description}
@@
   determines the sequence of layers, the actual node used for the next
-  hop of forwarding is selected from the set in an ad-hoc way.
+  hop of forwarding is selected from the set in an ad-hoc way,
+  resulting in a source-bounded random walk.
 \item[Onion Routing.] Put simply, in onion routing, the sender creates
@@
 \textcite{RoutingSurveyAnonymousProtocols}.
-They classify anonymous communication protocols using the following 
+They characterize anonymous communication protocols using the following 
 categories (see~\cite[Table 1]{RoutingSurveyAnonymousProtocols}):
@@
 
+\sonja{do we apply all categories here?}
 We first describe Sphinxes (\cref{Sphinxes}), which is an adaptation of the 
@@
 message-based (performance) communication.
-But unlike Sphinx, Sphinxes is hybrid source-hop-by-hop routed (communication 
+But unlike Sphinx, Sphinxes is hybrid source-hop-by-hop routed, a
+source-bounded random walk (communication 
 model),
@@
 only a probabilistic selection among already selected nodes and only 
-interesting against passive adversaries (an active adversary can learn the 
+interesting against passive adversaries (an active \sonja{global?} adversary can learn the 
 entire set).
@@
 predict this behavior.
-This is best done jointly between the user's all devices.
+This is best done jointly between all of the user's devices.
 In \cref{sec:squad_overlay}, we describe a protocol which allows the devices to 
@@
 Finally, we describe the complete \ac{SPORES} protocol (\cref{SPORES}), which 
-allows the device squad to act as an autonomous system.
+allows the device \squad to act as an autonomous system.
 In particular, we introduce a protocol which allows transferring larger 
-messages by fragmentation and reassembly across the devices in the squad.
+messages by fragmentation and reassembly across the devices in the \squad.
 
@@
 \include*{squad-overlay-design}
-%\include*{file-transfer-design}
+\include*{file-transfer-design}

### 2018-08-07 paper/sphinxes.tex
more edits, packet to message, sphinxes

@@
 It is also compact with only 224 bytes of header for a five-hop path with 
-128-bit security.
+128-bit security. \sonja{what about the CL properties?}
 Sphinx only provides one node per onion layer; in this section we extend Sphinx 
@@
     Illustration of the conceptual difference between traditional onion routing 
-    and mixing (top) and \ac{POR} (bottom).
+    and mixing (top) and \ac{SPOR} (bottom).
     %\commentDaniel{This figure should be fixed, issue \#42.}
@@
 
-We will now extend Sphinx to do \ac{POR}: instead of providing only \(d_{i+1}\) 
+We will now extend Sphinx to do \ac{SPOR}: instead of providing only \(d_{i+1}\) 
 in \(\beta_i\), we will have a set \(\{d_{i+1}^{(1)}, \dotsc, d_{i+1}^{(m)}\}\) 
@@
 
-\subsubsection{Sphinxes algorithms and \acf*{POR}}
+\subsubsection{Sphinxes algorithms and \acf*{SPOR}}
 
@@
     address.
-    \(\rdvnode\in \N\) is the rendezvous-node identifier, indicating that the 
-    current node is a rendezvous node and that the payload is \iac{POR} route 
-    to forward.
+    \(\rdvnode\in \N\) is the crossover-node identifier, indicating that the 
+    current node is the node at the end of one leg of a route that needs to cross
+   over to another, and that the payload is \iac{SPOR} route 
+    for forwarding.
 
@@
 
+We keep the nomenclature of mix headers and messages from Sphinx for
+clarity but later apply them to onions and file chunks, repectively.
+
 \paragraph*{The \(\CreateHeader\) algorithm}
 
-This algorithm creates a header for \iac{POR}.
+This algorithm creates a header for \iac{SPOR}.
 It is identical to that of Sphinx~\cite[\S 3.2]{Sphinx} except that we use a 
@@
 The last layer, \(L_\nu\), should be either \(\{\nullnode\}\) or 
-\(\{\rdvnode\}\) to terminate the routing.
+\(\{\rdvnode\}\) to terminate the routing. \sonja{define v(nu)}
 
@@
 can compute the correct \acp{MAC} (\(\gamma_i\)).
-The padding for the outmost layer (layer 0) is the empty string, thus \(\phi_0 
+The padding for the outermost layer (layer 0) is the empty string, thus \(\phi_0 
   \gets \epsilon\).
@@
 
-Next we will use the above computations to compute the mix headers \(M_i = 
+Next we will use the above computations to arrive at the mix headers \(M_i = 
   (\alpha_i, \beta_i, \gamma_i)\).
@@
 \(\gamma_i\).
-We must compute \(\beta_i\) in reverse order.
+We must compute \(\beta_i\) in reverse order. \sonja{why? layering?}
 We let \(\beta_{\nu} = I\concat 0_{(w_H r-1)\kappa}\), then, for \(\nu < i\leq 
@@
 If the \ac{MAC} computed correctly, compute \(t\gets \hash_\tau(s_i)\).
-If \(t\) is already in the table of seen packets, drop the packet.
+If \(t\) is already in the table of seen messages, drop the message.
 Otherwise, add \(t\) to the table and decrypt \(\beta\):

### 2018-08-07 paper/system-model.tex
up david

--- 2018-08-06 paper/system-model.tex
@@
 
-\section{System model, adversary model and desired privacy properties}%
+\section{System model, adversary model and desired security and privacy properties}%
 \label{system-model}
@@
 % for onion routing:
-onion-correctness, integrity, and security %(wrap resistance,
-                                %indistinguishability). 
-Informally, onion-correctness means that if an onion is formed
+\textit{onion-correctness, integrity}, and \textit{security}. %(wrap resistance,
+                                %indistinguishability)
+Informally, \textit{onion-correctness} means that if an onion is formed
 correctly, processed by the correct routers in the correct order, then
-the correct message is received by the last router. Onion-integrity
+the correct message is received by the last router. \textit{Onion-integrity}
 means that even for an onion created by an adversary, the path length
-is bounded by $N$. Onion-security means that an adversary sending a
-challenge onion to a router and able to see the outcome of how the
+is bounded by $N$. \textit{Onion-security} means that an adversary sending a
+challenge onion \david{what is a challenge onion?} to a router and able to see the outcome of how the
 onion is processed, cannot distinguish between whether that onion
@@
 true for a \emph{re-wrapped} onion, i.e. a challenge onion wrapped in
-another layer. The formal definitions are in~cite{CLOnionRoutin} along
+another layer. The formal definitions are in~\cite{CLOnionRouting} along
 with a theorem that states that an onion routing scheme satisfying
 these three properties, combined with secure point-to-point channels,
-is UC-secure.
+is UC-secure \david{what does it means, it has never been introduced
+  before, what do you mean?}.
 

### 2018-08-07 paper/system-model.tex

--- 2018-08-06 paper/system-model.tex
@@
 provides two main privacy properties, which we should preserve when
-moving to a P2P~\cite{DevilInMetadata} setting:
+moving to a P2P setting:
 \begin{itemize}
@@
 provider thus poses a threat to the users' privacy which we remove in
-the P2P scenario.
+the P2P scenario~\cite{DevilInMetadata}.
 
@@
 corresponds to a particular message and route or not. This is also
-true for a \emph{re-wrapped} onion, i.e. a challenge onion wrapped in
-another layer. The formal definitions are in~cite{CLOnionRoutin} along
+true for a \emph{re-wrapped} onion, \ie a challenge onion wrapped in
+another layer. The formal definitions are in~\cite{CLOnionRouting} along
 with a theorem that states that an onion routing scheme satisfying
 these three properties, combined with secure point-to-point channels,
-is UC-secure.
+is UC secure.
 
@@
 
- \commentFT{Removed, as did not fit with
-  the flow, but probably needed somewhere: `We give the definitions
-  for the security and privacy properties of \name in
-  Section~\ref{security-discussion}.'} \sonja{better here. Need to define
-  device unlinkability, the rest is covered by Camenisch.}
+ % \commentFT{Removed, as did not fit with
+ %  the flow, but probably needed somewhere: `We give the definitions
+ %  for the security and privacy properties of \name in
+ %  Section~\ref{security-discussion}.'} \sonja{better here. Need to define
+ %  device unlinkability, the rest is covered by Camenisch.}
 

### 2018-08-07 paper/evaluation.tex

--- 2018-08-07 paper/evaluation.tex
@@
 
+\begin{figure}[t]
+  \centering
+  %\def\svgwidth{0.8\columnwidth}
+  \includegraphics[width=0.8\columnwidth]{figures/completion_vs_size.pdf}
+
+  \caption{\label{fig:completion_vs_size}
+  Success rate of the file transfer ordered by size of file.}
+\end{figure}
+
 Using the previous parameters, we performed our experiment 30 times, yielding 360 file exchanges.
@@
 The probability falls as the file gets bigger, such that a 1,O43MB has 50\% chances of successful transfer (see $x_0$).
+
+\begin{figure}[t]
+  \centering
+  %\def\svgwidth{0.8\columnwidth}
+  \includegraphics[width=\columnwidth]{figures/bw_and_pending_files.pdf}
+
+  \caption{\label{fig:bw_and_pending_files}Traffic during one experiment.
+  In gray: number of pending file exchanges; in black: mean outbound traffic (kB) per node per second.}
+\end{figure}
+
+\begin{figure}[t]
+  \centering
+  %\def\svgwidth{0.8\columnwidth}
+  \includegraphics[width=\columnwidth]{figures/bw_and_pending_files_log.pdf}
+
+  \caption{\label{fig:bw_and_pending_files_log}Traffic during one experiment.
+  In gray: number of pending file exchanges; in black: mean outbound traffic (kB) per node per second.}
+\end{figure}
 

### 2018-08-07 paper/design.tex
fixing refs in Figure 1, but no longer fits plan

@@
   \def\svgwidth{0.8\columnwidth}
-  \import{figures/}{outline.pdf_tex}
+  \import{figures/}{outline_figure_only.pdf_tex}
   \caption{\label{fig:outline}%
@@
     (\cref{sec:squad_overlay}); online devices globally share information about 
-    them with random peers (\cref{sec:SPOR}); using the two 
+    them with random peers (\cref{ssec:device_availability}); using the two 
     overlays above allows for the creation of routes (\ac{SPOR}) between sets of devices. 
     These protocols enable secure file transfer between users 
-    (\cref{sec:sphinxes}).}
+    (\cref{ssec:por}).}
 \end{figure}

### 2018-08-07 paper/sphinxes.tex
sphinxes: reinstated packet, some grammar edits

@@
 \begin{figure}
-  \includegraphics[width=\linewidth]{figures/OR-POR.png}
+  \centering
+  %  \includegraphics[width=\linewidth]{figures/OR-POR.png}
+    \includegraphics[width=0.65\linewidth]{figures/principle_SPOR.pdf}
   \caption{\label{fig:OR-POR}%
     Illustration of the conceptual difference between traditional onion routing
-    and mixing (top) and \ac{SPOR} (bottom).
+
+    and mixing (OR, top) and \ac{SPOR} (bottom).
+
     %\commentDaniel{This figure should be fixed, issue \#42.}
@@
 If the \ac{MAC} computed correctly, compute \(t\gets \hash_\tau(s_i)\).
-If \(t\) is already in the table of seen messages, drop the message.
+If \(t\) is already in the table of seen packets, drop the packet.
 Otherwise, add \(t\) to the table and decrypt \(\beta\):
@@
 If sending to \(n\) fails, choose another node from \(L'\) uniformly at random.
-If all nodes in \(L'\) fails, the algorithm drops the packet and silently 
-fails.
+If all nodes in \(L'\) fail, the algorithm drops the packet and fails silently.

### 2018-08-07 paper/design.tex
up

--- 2018-08-06 paper/design.tex
@@
   section instead of a subsection in the design section.}
+
+\subsection{Key features of \name}
 
@@
 After the initial, out-of-band setup, file transfer happens along
-onion routes but with the following \name modifications:
+onion routes but with the following features:
 
@@
 
-This rest of this section presents the different parts of the system in detail.
-We align the presentation of the system with the taxonomy of 
+\subsection{Taxonomy of anonymous communication protocols}
+
+To present the different parts of \name in details, 
+we align the presentation of the system with the taxonomy of 
 \textcite{RoutingSurveyAnonymousProtocols}.
@@
 \begin{description}
-  \item[Network structure]
-    describes the characteristics of the network nodes, the connections between 
+  \item[Network structure.]
+    It describes the characteristics of the network nodes, the connections between 
     them and the underlying topology.
@@
 
-  \item[Routing information]
-    describes the network information available to entities deciding on 
+  \item[Routing information.]
+    It describes the network information available to entities deciding on 
     the route of an anonymous file exchange.
@@
 
-  \item[Communication model]
-    describes the entities that make the routing decisions and how they 
+  \item[Communication model.]
+   It describes the entities that make the routing decisions and how they 
     make these decisions.
@@
 
-  \item[Performance]
-    describes things like latency and communication mode.
+  \item[Performance.]
+    It describes things like latency and communication mode.
     The subcategories are
@@
 
-We first describe Sphinxes (\cref{Sphinxes}), which is an adaptation of the 
+We first describe \sphinxes (\cref{Sphinxes}), which is an adaptation of the 
 Sphinx~\cite{Sphinx} mix-header format.

### 2018-08-07 paper/abstract.tex

@@
 %problem/topic
-This paper proposes a novel private file sharing service that avoids any third-party storage or centralized bootstrapping service.
+This paper proposes a novel private file transfer service that avoids any third-party storage or centralized bootstrapping service.
 %research gap
 Our solution, which adopts a fully decentralized design, overcomes the limitations of cloud file-sharing systems such as Dropbox, which require trust in the service provider and can be monitored, even when their data is encrypted.
-Our proposal also goes beyond existing private peer-to-peer (P2P) solutions that are either particularly inefficient, or must rely on a fixed set of trusted servers for bootstrapping purposes, which limits their level of protection.
+Our proposal also goes beyond existing private peer-to-peer (P2P) solutions that must rely storage replication for efficiency or a fixed set of trusted servers for bootstrapping purposes, which limits their level of protection.
 % We are interested in minimizing the trust needed in other systems and preserving the users' privacy in terms of data and metadata, what they share with whom and when.
@@
 %approach
-In this paper, we demonstrate that users do not necessarily have to choose between efficiency and strong-privacy when sharing data with others.
+In this paper, we demonstrate that users do not necessarily have to choose between efficiency and strong privacy when sharing data with others.
 % that is  both efficient and strongly private is possible.
-\commentFT{Trying to highlight POR, as likely to catch people's attention, and contribute to the paper's long-term interest.} At the core of our proposal lies a novel probabilistic onion routing protocol called POR, which exploits decentralized peer sampling, and a probabilistic model of node availability.
+\commentFT{Trying to highlight POR, as likely to catch people's attention, and contribute to the paper's long-term interest.} At the core of our proposal lies a novel stateless probabilistic onion routing protocol called SPOR, which exploits decentralized peer sampling, and a probabilistic model of node availability.
 \commentFT{Sharing node availability information freely could potentially disclose private information.
@@
 This design makes it possible to exploit transient nodes, without dedicated relays, %take advantage of locality, 
-neither of which is currently the case in TOR.
+neither of which is currently the case in Tor.
+\sonja{say something about security requirements? About sphinxes?}

### 2018-08-07 paper/design.tex

--- 2018-08-07 paper/design.tex
@@
 \label{design}
-% \sonja{will frame and structure (A) squad overlay (prediction) (B)
-%   global overlay (RPS) (C) sphinxes (incl.\ sphinx, onion routing in
-%   general) (D) SPOR and SPORES (E) encryption (hybrid, payload, header)
-%   if not included earlier (F) out-of-band}
-% \commentDaniel{I suggest the following structure:
-%   (A) Sphinxes
-%   (B) SPOR (global overlay)
-%   (C) SPORES (local overlay).
-%   My original idea was to make Sphinxes its own section before the design 
-%   section instead of a subsection in the design section.}
 
-Our goal is to enable private and reliable file transfer between users 
+\sonja{will frame and structure (A) squad overlay (prediction) (B)
+  global overlay (RPS) (C) sphinxes (incl.\ sphinx, onion routing in
+  general) (D) SPOR and SPORES (E) encryption (hybrid, payload, header)
+  if not included earlier (F) out-of-band}
+\commentDaniel{I suggest the following structure:
+  (A) Sphinxes
+  (B) SPOR (global overlay)
+  (C) SPORES (local overlay).
+  My original idea was to make Sphinxes its own section before the design 
+  section instead of a subsection in the design section.}
+
+\subsection{Key features of \name}
+
+Our goal is to enable private and reliable file exchange between users 
 participating in the system, by using their respective devices only.
@@
 
+We first describe \sphinxes (\cref{Sphinxes}), which is an adaptation of the
+
 \sonja{do we apply all categories here?}
-We first describe Sphinxes (\cref{Sphinxes}), which is an adaptation of the 
+
 Sphinx~\cite{Sphinx} mix-header format.

### 2018-08-07 paper/system-model.tex

--- 2018-08-07 paper/system-model.tex
@@
 corresponds to a particular message and route or not. This is also
-true for a \emph{re-wrapped} onion, i.e. a challenge onion wrapped in
+true for a \emph{re-wrapped} onion, \ie a challenge onion wrapped in
 another layer. The formal definitions are in~\cite{CLOnionRouting} along
@@
   before, what do you mean?}.
-
 These properties cover the concerns about

### 2018-08-07 paper/file-transfer-design.tex
Fixes undefined reference
edits throughout

@@
 
+\sonja{to be merged with the previous subsection}
 So far, we have treated the case where Alice sends \emph{one} message to Bob in 
@@
 global configuration parameters for the system.
-We run simulations for various values of \(t\) and \(w\) in 
-\cref{PerformanceAnalysis}.
+We run simulations for various values of \(t\) and \(w\) in \cref{Performance}.
 In this section we describe a file-transfer protocol for splitting a large 
@@
 
-\commentDaniel{I leave the remaining details for someone else to write up.
-  What we need is the details of how Bob's devices syncs and reassembles files.
-  Maybe this is reduced to Sprinkler or something.}
+%\commentDaniel{I leave the remaining details for someone else to write up.
+ % What we need is the details of how Bob's devices syncs and reassembles files.
+ % Maybe this is reduced to Sprinkler or something.}

### 2018-08-07 paper/security-discussion.tex
edits throughout

--- 2018-08-07 paper/security-discussion.tex
@@
 %  have security proofs for their original and individual versions and needing to evaluate the resulting s%chemes}
-
-\commentDaniel{Predecessor attacks: random walk protocols has the problem that 
-  the adversary can see the initiator (statistically) more often than the other 
-  nodes, and can thus identify the 
-  source~\cite{RoutingSurveyAnonymousProtocols}.
-  Our protocol is a \enquote{bounded} random walk, \ie within limits.}
 
@@
 
-\paragraph*{Security of \ac{SPORES}}
-
-\Ac{SPORES} inherits the security properties from Sphinxes and \ac{SPOR}.
-However, both Sphinxes and \ac{SPOR} can be used with any mixing strategy, and 
-the security they provide is as secure as the mixing strategy (or flushing 
-algorithm) allows.
-Since \ac{SPORES} is a fully-fledged system, it must make a concrete choice for 
-the mixing strategy.
-Since \ac{SPORES} aims at low latency, routers do not batch and mix incoming 
-messages; it immediately forwards the messages.
-This puts \ac{SPORES} in the same position as Tor~\cite{Tor}, \ie more 
-vulnerable to traffic analysis than batching 
-mix-nets~\cite{RoutingSurveyAnonymousProtocols} \commentDaniel{we should 
-  probably look for the original papers} --- this vulnerability is inherited 
-from the mixing strategy.
-
-\Ac{SPORES} also inherits a vulnerability from random-walk protocols and the 
-fact that a large message is split into chunks.
-Since the chunks can take several paths from source to destination, the source 
-will send and the destination will receive more traffic than other nodes in the 
-network~\cite{RoutingSurveyAnonymousProtocols} \commentDaniel{we should 
-  probably look for the original papers}.
-However, this is slightly alleviated by the fact that the source and 
-destination can be several different devices --- \ie from the \squad{}s.
-
 \paragraph*{Robustness}
@@
   protocol must resend.'' why?}  \commentDaniel{We should look into
-  this denial of security.} We would also like to point out that
+  this denial of security.} Another example is that the source-bounded
+random walk and different routes for file chunks make tracking more
+difficult than with onion routing circuits. A drawback, however, is
+that since the chunks can take several paths from source to destination, the source 
+will send and the destination will receive more traffic than other nodes in the 
+network~\cite{RoutingSurveyAnonymousProtocols}. However, this is mitigated by the fact that the source and 
+destination can be several different devices --- \ie from the \squads.
+
+We would also like to point out that
 vulnerability to a global passive attacker is not inherent in Sphinx
@@
 issue, batched and well-timed message or file transfer by all nodes
-would render traffic analysis pointless.
+would render traffic analysis pointless. \Ac{SPORES} inherits the security properties from Sphinxes and \ac{SPOR}.
+However, both Sphinxes and \ac{SPOR} can be used with any mixing strategy, and 
+the security they provide is as secure as the mixing strategy (or flushing 
+algorithm) allows.
+Since \ac{SPORES} is a fully-fledged system, it must make a concrete choice for 
+the mixing strategy.
+Since \ac{SPORES} aims at low latency, routers do not batch and mix incoming 
+messages; it immediately forwards the messages.
+This puts \ac{SPORES} in the same position as Tor~\cite{Tor}, \ie more 
+vulnerable to traffic analysis than batching 
+mix-nets~\cite{RoutingSurveyAnonymousProtocols} \commentDaniel{we should 
+  probably look for the original papers} --- this vulnerability is inherited 
+from the mixing strategy.
+
+% \commentDaniel{Predecessor attacks: random walk protocols has the problem that 
+%   the adversary can see the initiator (statistically) more often than the other 
+%   nodes, and can thus identify the 
+%   source~\cite{RoutingSurveyAnonymousProtocols}.
+%   Our protocol is a \enquote{bounded} random walk, \ie within limits.}

### 2018-08-07 paper/spor.tex
(Re-)Adds comments to figures in need on updating
edits throughout

@@
 \(\UseReply\), creates a forward header using \(\CreateFwd\) with the prepared 
-reply header as parameter.
-\commentAL{Unclear: she sends? Then it reaches Alice?} Then she sends this packet to the first node, which processes it using 
+reply header as parameter. \sonja{what about the crossover node and
+  Alice's leg of the route?} 
+Then she sends this packet to the first node, which processes it using 
 \(\ProcessHeader\).
@@
 next node.
-At some point the message will reach Alice who identifies the message as the 
-one expected to come from Bob.
+At some point the message will reach Bob who identifies the message as the 
+one expected to come from Alice.
 (This process is illustrated in \cref{fig:file-transfer}.)
@@
 \end{figure}
+
+\commentAL{When is CreateHeader used?}
 
@@
 The \(\GetRandomNode\) algorithm can be instantiated using \eg
-Octopus~\cite{Octopus}.
-But even a solution like Tor's authoritative directory servers would work,
+Octopus~\cite{Octopus}. Its function is analogous to 
+Tor's authoritative directory servers, but we need a decentralized system. 
 We will treat \(\avail_d\) in \cref{sec:squad_overlay}.

### 2018-08-07 paper/squad-overlay-design.tex
figures!
edits throughout

@@
 %!TEX root = p2p-private-cloud.tex
-
-\newcommand\fileid{\ensuremath{ID_{\text{f}}}\xspace}
-\newcommand\sendingdevice{\ensuremath{d^{(s)}_f}\xspace}
-\newcommand\recdevice{\ensuremath{d^{(r)}_f}\xspace}
 
@@
 	\item \texttt{SENDING<\sendingdevice, \fileid>}: When the user decides to send a file $f$ located on a device \sendingdevice, \sendingdevice informs its peers of this fact, and joins the file ID \fileid.
-Squad members will use this information to forward acknowledgments from the remote to \sendingdevice;
+\Squad members will use this information to forward acknowledgments from the recipient to \sendingdevice;
 	\item \texttt{RECEIVING<\recdevice, \fileid>}: Reciprocally, when the user starts receiving a file $f$ onto a device \recdevice, \recdevice informs its peers of this fact, and joins the file ID \fileid.
-Squad members will use this information to forward the file's content from the remote to \recdevice.
+\Squad members will use this information to forward the file's content from the sender to \recdevice.
 \end{itemize}
 
-Given this information dissemination and history reconciliation mechanism, each \squad member knows the full sequence $S$ at all time with an overwhelming probability, even in the face of churn~\cite{luxey:cascade}.
+Given this information dissemination and history reconciliation mechanism, each \squad member knows the full sequence $S$ at all times with an overwhelming probability, even in the face of churn~\cite{luxey:cascade}.
 
@@
 The predictive nature of \name lies in the fact that each participating device publicly advertises its probability of being connected in the near future. 
-This information is used when any node needs to create a Probabilistic Onion Route (POR), as will be shown in the next subsection~\ref{ssec:por}.
+This information is used when any node needs to create a Stateless Predictive Probabilistic Onion Route (\SPOR), as will be shown in the next subsection~\ref{ssec:por}.
 
@@
 $P'd$ will be advertised in spite of $P_d$. It will also be used as a baseline in the evaluation.
-
-\subsection{Probabilistic Onion Routes}
+\sonja{this and the next subsection seem redundant and need to be merged}
+\subsection{Stateless Predictive Probabilistic Onion Routes}
 \label{ssec:por}
@@
 \label{sssec:global_overlay}
-
-\newcommand\rpsview{\ensuremath{\mathcal{V}}\xspace}
-\newcommand\desc{\ensuremath{{\mathtt{desc}}}\xspace}
 
@@
 
-%\newcommand\layer{\ensuremath{{\mathcal{L}}}\xspace}
-\newcommand\layer{L\xspace}
-\newcommand\Poff{\ensuremath{P_{\text{off}}}\xspace}
-
 Routes are created via Sphinxes, as described in section~\ref{SPOR}.
@@
 
-\newcommand\finfo{\ensuremath{\mathcal{I}_f}}
-\newcommand\filesize{\ensuremath{s_f}\xspace}
-\newcommand\chunksize{\ensuremath{s_{\text{chunk}}}\xspace}
-\newcommand\nchunks{\ensuremath{n_{\text{chunks}}}\xspace}
-\newcommand\hashchunk{\ensuremath{h_{\text{chunk}}}\xspace}
-\newcommand\hashfile{h\xspace}
-
 We have seen how participants of \name could craft routes to secretly exchange messages.
@@
 resulting in $\nchunks = \lceil \filesize / \chunksize \rceil$ chunks.
-A SHA1 hash \hashchunk is computed for each chunk, plus another SHA1 hash \hashfile of the chunks hashes ; that will serve error detection.
+A SHA1 hash \hashchunk is computed for each chunk, plus another SHA1 hash \hashfile of the chunks hashes; that will serve error detection.
 
@@
 
-\newcommand\bitfield{\ensuremath{bf_f}\xspace}
-\newcommand\tupload{\ensuremath{t_{\text{upload}}}\xspace}
-
 \paragraph*{Chunks and bitfields}
@@
 Bob receives $f$ on a device \recdevice, but a chunk $c_i$ for $f$ might arrive on any of his devices. 
-This device then fetches the address of the proper recipient \recdevice by looking for the line \texttt{RECEIVING<\recdevice, \fileid>} in its squad sequence, 
+This device then fetches the address of the proper recipient \recdevice by looking for the line \texttt{RECEIVING<\recdevice, \fileid>} in its \squad sequence, 
 and forwards the file chunk to \recdevice.

### 2018-08-07 paper/design.tex
section 3

@@
 \commentDaniel{I suggest the following structure:
-  (A) Sphinxes
+  (A) \Sphinxes
   (B) SPOR (global overlay)
   (C) SPORES (local overlay).
-  My original idea was to make Sphinxes its own section before the design 
+  My original idea was to make \Sphinxes its own section before the design 
   section instead of a subsection in the design section.}
@@
   Sphinx~\cite{Sphinx}, with some modification to allow for the
-  changes above, described in \cref{Sphinxes}.
+  changes above, described in \cref{\Sphinxes}.
 \end{description}
@@
 
-We first describe \sphinxes (\cref{Sphinxes}), which is an adaptation of the
+We first describe \sphinxes (\cref{\Sphinxes}), which is an adaptation of the
 
@@
 header format, it only imposes some restrictions in the above categories.
-Sphinxes provides, just as Sphinx, unidirectional (network structure), 
+\Sphinxes provides, just as Sphinx, unidirectional (network structure), 
 message-based (performance) communication.
-But unlike Sphinx, Sphinxes is hybrid source-hop-by-hop routed, a
+But unlike Sphinx, \Sphinxes is hybrid source-hop-by-hop routed, a
 source-bounded random walk (communication 
 model),
-Sphinxes relies on a flat routing-topology (network structure) with fair 
+\Sphinxes relies on a flat routing-topology (network structure) with fair 
 scheduling (communication model) --- as all packets are indistinguishable they 
 must be processed on a first-in-first-out basis.
-Sphinxes also introduces some probability to the node selection, but this is 
+\Sphinxes also introduces some probability to the node selection, but this is 
 only a probabilistic selection among already selected nodes and only 
@@
 
-Sphinxes does \emph{not} introduce any restrictions on whether the network 
+\Sphinxes does \emph{not} introduce any restrictions on whether the network 
 topology must be fully connected or not, be asynchronous (as in Tor) or 
@@
 \commentAL{A lot of description here, should only come in Section~\ref{sec:squad_overlay}}
-This focuses on the node selection, \ie adds node selection on top of Sphinxes.
+This focuses on the node selection, \ie adds node selection on top of \Sphinxes.
 The \ac{SPOR} protocol assumes a source of random nodes, \eg through 
@@
 \include*{spor}
-\commentAL{What I want to do from here:
-(1) The squad overlay, where a user's devices exchange behavioral information;
-(2) Predicting a device's availability;
-(3) What is at the moment III-B SPOR: global overlay (one-liner: ``we use a RPS service'') and nodes selection per layer etc.;
-(4) File exchange.}
 \include*{squad-overlay-design}
-\include*{file-transfer-design}
+%\include*{file-transfer-design}

### 2018-08-07 paper/security-discussion.tex
section 3

--- 2018-08-07 paper/security-discussion.tex
@@
 best strategy is to have high-availability nodes --- assume that 
-\(\avail_{D_E}(t) = 1\) for all Eve's devices \(D_E\).
+\(\Pon_{D_E}(t) = 1\) for all Eve's devices \(D_E\).
 This way, Eve's devices will be distributed evenly across all layers.

### 2018-08-07 paper/spor.tex
section 3

--- 2018-08-05 paper/spor.tex
@@
 \label{sec:message_passing}%
-
-\commentAL{I would like to merge that with \ref{ssec:por}.}
 
@@
 
-There are many uses of Sphinxes, many criteria that can be used to select the 
+There are many uses of \Sphinxes, many criteria that can be used to select the 
 nodes in each layer.
@@
 churn, but one could equally well select nodes to maximize, \eg, bandwidth.
-We now describe a protocol, \ac{SPOR}, which uses Sphinxes to transfer messages 
+We now describe a protocol, \ac{SPOR}, which uses \Sphinxes to transfer messages 
 from a source to a destination over a network of nodes with high churn.
 
-\((d, \pk_d, \avail_d)\gets \GetRandomNode\): We assume that there is an 
-algorithm \(\GetRandomNode\) which returns a tuple \((d, \pk_d, \avail_d)\) of 
+\((d, \pk_d, \Pon_d)\gets \GetRandomNode\): We assume that there is an 
+algorithm \(\GetRandomNode\) which returns a tuple \((d, \pk_d, \Pon_d)\) of 
 one uniformly randomly selected node, where.
@@
   \item \(\pk_d\) is the node's public key;
-  \item \(\avail_d(t)\) is the node's probability of being online as a function 
+  \item \(\Pon_d(t)\) is the node's probability of being online as a function 
     of time.
@@
 But even a solution like Tor's authoritative directory servers would work,
-We will treat \(\avail_d\) in \cref{sec:squad_overlay}.
+We will treat \(\Pon_d\) in \cref{sec:squad_overlay}.
 
@@
 Bob will distribute these nodes across all layers \(L_i\) to maximize \(\min_i 
-  \avail_{L_i}(t)\), where \(\avail_{L_i}(t) = 1-\prod_{l\in L_i} 
-  (1-\avail_l(t))\).
+  \Pon_{L_i}(t)\), where \(\Pon_{L_i}(t) = 1-\prod_{l\in L_i} 
+  (1-\Pon_l(t))\).
 This means that Bob minimizes the risk of a layer (\ie all nodes in a layer) 

### 2018-08-07 paper/squad-overlay-design.tex
section 3

@@
 
-The exchanged data forms a sequence, ordered by timestamp, populated by three types of information:
+The exchanged messages form a sequence, ordered by timestamp, populated by three message types:
 \begin{itemize}
@@
 	\item \texttt{SENDING<\sendingdevice, \fileid>}: When the user decides to send a file $f$ located on a device \sendingdevice, \sendingdevice informs its peers of this fact, and joins the file ID \fileid.
-\Squad members will use this information to forward acknowledgments from the recipient to \sendingdevice;
+Squad members will use this information to forward acknowledgments from the remote to \sendingdevice;
 	\item \texttt{RECEIVING<\recdevice, \fileid>}: Reciprocally, when the user starts receiving a file $f$ onto a device \recdevice, \recdevice informs its peers of this fact, and joins the file ID \fileid.
-\Squad members will use this information to forward the file's content from the sender to \recdevice.
+Squad members will use this information to forward the file's content from the remote to \recdevice.
 \end{itemize}
 
-Given this information dissemination and history reconciliation mechanism, each \squad member knows the full sequence $S$ at all times with an overwhelming probability, even in the face of churn~\cite{luxey:cascade}.
+Given this information dissemination (push) and history reconciliation mechanism (pull), each \squad member knows the full sequence $S$ at all time with an overwhelming probability, even in the face of churn~\cite{luxey:cascade}.
 
@@
 The predictive nature of \name lies in the fact that each participating device publicly advertises its probability of being connected in the near future. 
-This information is used when any node needs to create a Stateless Predictive Probabilistic Onion Route (\SPOR), as will be shown in the next subsection~\ref{ssec:por}.
+This information is used when any node needs to create a Probabilistic Onion Route (POR), as will be shown in the next subsection~\ref{ssec:por}.
 
@@
 $P'd$ will be advertised in spite of $P_d$. It will also be used as a baseline in the evaluation.
-\sonja{this and the next subsection seem redundant and need to be merged}
-\subsection{Stateless Predictive Probabilistic Onion Routes}
+
+%\subsection{Probabilistic Onion Routes}
+\subsection{Selection of nodes for routes creation}
 \label{ssec:por}
 
-\subsubsection{The global overlay}
+%\subsubsection{The global overlay}
+\subsubsection{\GetRandomNode}
 \label{sssec:global_overlay}
@@
 Devices need to know the address of SPORES participants in order to craft PORs.
-To this end, we employ a Random Peer Sampling service~\cite{Jelasity_Voulgaris_Guerraoui_Kermarrec_van_Steen_2007} among all nodes in SPORES.
-\commentAL{TODO: cite \cite{Jesi_Montresor_van_Steen_2010} for \textbf{secure} RPS}.
-It is a gossip protocol that allows each participant to keep a fixed-size \emph{random} subset of other nodes' descriptor (that we will call the \emph{view} \rpsview). 
+To this end, we employ a Random Peer Sampling service~\cite{Jelasity_Voulgaris_Guerraoui_Kermarrec_van_Steen_2007,Jesi_Montresor_van_Steen_2010} (RPS) among all nodes in SPORES.
+It is a gossip protocol that allows each participant to keep a fixed-size \emph{random} subset of other nodes' descriptor (that we will call the RPS's \emph{view} \rpsview). 
 The view is constantly evolving, as queries are periodically issued between nodes to exchange descriptors between their respective views.
@@
   \item \(\pk_d\) is the node's public key;
-  \item \(P_d\) is the node's probability of remaining online at the time of the descriptor's creation.
+  \item \(\Pon_d\) is the node's probability of remaining online at the time of the descriptor's creation.
 \end{itemize}
 
-\subsubsection{Routes creation}
+$(d, \pk_d, \Pon_d)= \leftarrow \GetRandomNode$ is the function that takes a node from the RPS's view \rpsview on demand.
+
+%\subsubsection{Routes creation}
+\subsubsection{\CreateLayer}
 \label{sssec:routes_creation}
 
-Routes are created via Sphinxes, as described in section~\ref{SPOR}.
-Each layer \layer constituting the route is created by the same \CreateLayer\xspace function.
+Routes are created via \Sphinxes as described in section~\ref{sec:SPOR}.
+But each layer \layer constituting the route is created by the $\CreateLayer$ function, that is independent from \Sphinxes.
 
@@
 Therefore, each layer \layer is created so as to reach the availability threshold $\theta$, a parameter chosen by the user.
-Note that Sphinxes is agnostic to this use-case: one could want to maximize other characteristics, e.g. the layer's expected bandwidth.
+Note that \Sphinxes is agnostic to this use-case: one could want to maximize other characteristics, e.g. the layer's expected bandwidth.
 
-\CreateLayer\xspace iteratively adds random descriptors from the RPS's view \rpsview to the current layer \layer, until the layer's probability of being offline, $\Poff^\layer$, falls below the availability threshold $\theta$:
+$\CreateLayer$ iteratively calls $\GetRandomNode\xspace$ to add random nodes to the current layer \layer, until the layer's probability of being offline, $\Poff^\layer$, falls below the availability threshold $\theta$:
 
-$$ \Poff^\layer = \sum\limits_{d \in \layer}\desc_d.P_d $$
+$$ \Poff^\layer = \sum\limits_{d \in \layer}(1 - \desc_d.\Pon_d) $$
 
@@
 
-Recall that each layer in Sphinxes has a constant number of nodes $w_\layer$, that is a Sphinxes parameter.
-If $w_\layer$ is reached before $\Poff^\layer < \theta$, then we early abort \CreateLayer.
+Recall that each layer in \Sphinxes has a constant number of nodes $w_\layer$, that is a \Sphinxes parameter.
+If $w_\layer$ is reached before $\Poff^\layer < \theta$, then we early abort $\CreateLayer$.
 On the other hand, if $|\layer| < w_\layer$, we pad the layer with blank descriptors, such that the header always weighs the same size.
@@
 In BitTorrent, .torrent files are publicly available on the Web.
-They contain $\finfo = \left(\filesize, \nchunks, \left[\hashchunk\right]_{\text{chunk} \in f}, \hashfile\right)$, 
+They contain $\finfo = \left(\filesize, \nchunks, \left[\hashchunk\right]_{\chunk \in f}, \hashfile\right)$, 
 along with network information to reach uploaders of $f$ (e.g. the tracker's address).
-Anyone can download a .torrent file and start receiving the file associated to it.
+Anyone can download a .torrent and start receiving the file associated to it.
 
-In \name, we want file exchanges to remain private: these metadata are exchanged out-of-band.
-In addition, each file is associated with a random \fileid, that is part of \finfo.
+In \name, we want file exchanges to remain private: the file's metadata are exchanged out-of-band.
+In addition , each file is associated with a random \fileid, that is part of \finfo.
+
+\newcommand\forwardheader{\ensuremath{\mathcal{H}^{(f)}}}
+\newcommand\backwardheader{\ensuremath{\mathcal{H}^{(b)}}}
 
@@
 When Alice wishes to send a file $f$ to Bob, she computes \finfo, 
-plus one reply header per chunk, and sends the whole to Bob.
+plus one reply header per chunk (as was seen in section~\ref{sec:SPOR}), and sends the whole to Bob.
 Still out-of-band, Bob replies with one forward header per chunk.
+This way, each chunk $\chunk_i$ is associated with a unique route both ways: 
+a forward header $\forwardheader_i$ known by Alice, and a backward header $\backwardheader_i$ known by Bob.
 
@@
 Alice's file $f$ is located on one of her devices, \sendingdevice. 
-Each chunk $c_i \in f$ is uploaded to Bob through a unique route $\mathcal{H}_{c_i}$.
-When $d_f$ is online, it periodically sends chunks of $f$ to Bob until $f$ is entirely uploaded, with a period of
+When $\sendingdevice$ is online, it periodically sends chunks of $f$ to Bob until $f$ is entirely uploaded, with a period of \tupload.
+Each chunk $\chunk_i \in f$ is uploaded to Bob through a unique route $\forwardheader_i$.
 
-Bob receives $f$ on a device \recdevice, but a chunk $c_i$ for $f$ might arrive on any of his devices. 
-This device then fetches the address of the proper recipient \recdevice by looking for the line \texttt{RECEIVING<\recdevice, \fileid>} in its \squad sequence, 
-and forwards the file chunk to \recdevice.
-Upon reception of the chunk, \recdevice verifies its integrity by computing its SHA1 hash $h_{c_i}$ and comparing it to $\finfo.h_{c_i}$.
-If the chunk is valid, \recdevice updates its \emph{bitfield} \bitfield: this bit-array of size \nchunks is initialized with 0;
-every time Bob successfully receives a chunk $c_i$, \recdevice sets the bit $\bitfield[i]$.
-To acknowledge the chunk's reception, \recdevice sends \bitfield back to Alice, through a unique route $\mathcal{H}'_{c_i}$.
+Bob receives $f$ on a single device \recdevice, but chunks for $f$ might arrive on any of his devices.
+Say Bob has received a chunk $\chunk_i$ on $d \neq \recdevice$.
+This device must the address of the file's recipient \recdevice by looking for the line \texttt{RECEIVING<\recdevice, \fileid>} in its squad sequence.
+Having found the address of \recdevice, $d$ forwards the $\chunk_i$ to \recdevice.
+
+Upon reception of a chunk $\chunk_i$, \recdevice verifies its integrity by computing the SHA1 hash $h_{\chunk_i}$ and comparing it to $\finfo.h_{\chunk_i}$.
+If the chunk is valid, Bob must inform Alice that $\chunk_i$ was successfully received.
+We borrow again from the BitTorrent protocol by acknowledging reception with \emph{bitfields}.
+A bitfield \bitfield is bit-array of size \nchunks, such that $\bitfield[i] = 0$ means that Bob lacks the chunk $\chunk_i$, whereas $\bitfield[i] = 1$ means that he successfully received that chunk.
+$\bitfield$ describes the state of the total transfer and not just the current chunk, which is very useful when messages are prone to get lost in transit. 
+This bitfield is sent to Alice using the unique reply route $\backwardheader_i$.
+
+% Every time Bob successfully receives a chunk $\chunk_i$, \recdevice sets the bit $\bitfield[i]$, 
+% To acknowledge the chunk's reception, \recdevice sends \bitfield back to Alice, through a unique route $\mathcal{H}'_{\chunk_i}$.
 
 Reciprocally, acknowledgments can arrive to Alice on any on her devices, while only \sendingdevice can process it.
-When one of Alice's devices receives Bob's bitfield \bitfield, 
-it forwards \bitfield to \sendingdevice by getting its address on the line \texttt{RECEIVING<\sendingdevice, \fileid>} of the \squad overlay's sequence.
-Upon reception of a bitfield \bitfield, \recdevice updates its knowledge of Bob's unreceived chunks of $f$,
-and sends a chunk to Bob among the ones that were not already acknowledged by Bob, unless the file has been entirely received.
+When one of Alice's devices (say $d'$) receives Bob's bitfield \bitfield, 
+$d'$ forwards it to \sendingdevice by getting its address on the line \texttt{RECEIVING<\sendingdevice, \fileid>} of the \squad overlay's sequence.
+
+Once \sendingdevice receives \bitfield, it merges it with its previous knowledge of Bob's reception of $f$.
+If all chunks were acknowledged, the transfer is over.
+Else, \sendingdevice sends a new chunk, among the ones that were not acknowledged by Bob.
 

### 2018-08-07 paper/spor.tex

@@
 The \(\GetRandomNode\) algorithm can be instantiated using \eg
-Octopus~\cite{Octopus}.
-But even a solution like Tor's authoritative directory servers would work,
+Octopus~\cite{Octopus}. Its function is analogous to 
+Tor's authoritative directory servers, but we need a decentralized system. 
 We will treat \(\Pon_d\) in \cref{sec:squad_overlay}.

### 2018-08-07 paper/design.tex
oops

@@
   Sphinx~\cite{Sphinx}, with some modification to allow for the
-  changes above, described in \cref{\Sphinxes}.
+  changes above, described in \cref{{}Sphinxes}.
 \end{description}
@@
 
-We first describe \sphinxes (\cref{\Sphinxes}), which is an adaptation of the
+We first describe \sphinxes (\cref{Sphinxes}), which is an adaptation of the
 

### 2018-08-07 paper/design.tex
oops

@@
   Sphinx~\cite{Sphinx}, with some modification to allow for the
-  changes above, described in \cref{{}Sphinxes}.
+  changes above, described in \cref{Sphinxes}.
 \end{description}

### 2018-08-07 paper/security-discussion.tex
Fixes LaTeX warnings in robustness

--- 2018-08-07 paper/security-discussion.tex
@@
 going offline during transfer or other node or link failures is
-ensured by acknowledgments and timeouts as detailed in
-~\cref{sec:squad_overlay}.
+ensured by acknowledgements and timeouts as detailed in 
+\cref{sec:squad_overlay}.
 

### 2018-08-07 paper/security-discussion.tex
Fixes LaTeX warnings in robustness

--- 2018-08-07 paper/security-discussion.tex
@@
 best strategy is to have high-availability nodes --- assume that 
-\(\Pon_{D_E}(t) = 1\) for all Eve's devices \(D_E\).
+\(\avail_{D_E}(t) = 1\) for all Eve's devices \(D_E\).
 This way, Eve's devices will be distributed evenly across all layers.

### 2018-08-07 paper/security-discussion.tex
Updates security discussion intro

@@
 
-We base our solution on Sphinx~\cite{Sphinx}, which, when used for
-onion routing, has been proved to satisfy the properties given
-in~\cite{CLOnionRouting} that were shown to result in a UC-secure
-onion-routing scheme. We thus primarily need to ensure that
-\begin{enumerate*} \item our extension to Sphinxes preserves these
-  properties, \item the availability information introduced and
-  disseminated to deal with churn satisfies the device-unlinkability
-  property we defined in~\cref{system-model}, and that \item the
-  resulting node selection does not introduce any advantage for the
-  adversary. \end{enumerate*} In terms of general system robustness, a
-stateless routing protocol needs to handle packet re-ordering and
-network failures (links or nodes).
+The \ac{SPORES} system is composed of several parts, each of which requires its 
+own security analysis.
+We thus primarily need to ensure that
+\begin{enumerate*}
+\item Sphinxes (\cref{Sphinxes}) preserves the properties of 
+  \textcite{CLOnionRouting} and \textcite{Sphinx} yielding \ac{UC}-secure 
+  \ac{OR};
+\item the node selection (\ac{SPOR}, \cref{SPOR}) does not introduce any 
+  advantage for the adversary;
+\item the availability information introduced and disseminated to deal with 
+  churn satisfies the device-unlinkability property we defined in 
+  \cref{system-model}; and that
+\item the composed protocol (\ac{SPORES}, \cref{SPORES}) provides the desired 
+  security properties defined in \cref{system-model}, \ie
+  privacy and robustness (packet re-ordering and drops).
+\end{enumerate*}
 

### 2018-08-07 paper/security-discussion.tex
Adds stub for device unlinkability
Adds discussion of bitwise unlinkability of C to security discussion

@@
 We also changed from the classical \ac{OR} of a fixed path with one node per 
-layer to \ac{POR} with several nodes per layer.
+layer to a set of alternative nodes per layer.
 
+The first change:
 The confidentiality of the key previously rested entirely on the \ac{DH} 
@@
 (\(\gamma\) in the header).
+We still achieve the bitwise unlinkability since \(C\) is replaced at each 
+layer and the next \(C\) is hidden inside the header --- which otherwise 
+remains identical to that of Sphinx.
 

### 2018-08-07 paper/security-discussion.tex
WIP on UC simulator argument

@@
 The proofs of Sphinx rest on the results of \textcite{CLOnionRouting}, which 
-are results for ordinary \ac{OR} with only one node per layer.
-\sonja{Daniel is working on sketching a proof/rephrasing the following.}
-As long as we output all the nodes in the next layer, the proofs should not 
-change.
+are results for traditional \ac{OR} with only one node per layer.
+We must thus ensure that the proofs of \citeauthor{CLOnionRouting} also holds 
+for sets of nodes.
+
+Analogously to traditional \ac{OR}, we also reveal the previous and next sets 
+of nodes to the adversary.
 We note that this is actually quite natural as a malicious adversary can drop 
-any incoming traffic to a router and wait for the timeout and retransmission to 
-the next node.
-As such, the adversary can learn all nodes in the layer.
+any incoming traffic to a router and wait for the retransmission, \ie when the 
+node has selected a new node from the next layer and retried sending.
+As such, the adversary can learn all nodes in the layer --- just as for 
+traditional \ac{OR}.
 

### 2018-08-07 paper/design.tex
clarifying adversary effect statement in design overview

@@
 
-\sonja{will frame and structure (A) squad overlay (prediction) (B)
-  global overlay (RPS) (C) sphinxes (incl.\ sphinx, onion routing in
-  general) (D) SPOR and SPORES (E) encryption (hybrid, payload, header)
-  if not included earlier (F) out-of-band}
-\commentDaniel{I suggest the following structure:
-  (A) \Sphinxes
-  (B) SPOR (global overlay)
-  (C) SPORES (local overlay).
-  My original idea was to make \Sphinxes its own section before the design 
-  section instead of a subsection in the design section.}
+% \sonja{will frame and structure (A) squad overlay (prediction) (B)
+%   global overlay (RPS) (C) sphinxes (incl.\ sphinx, onion routing in
+%   general) (D) SPOR and SPORES (E) encryption (hybrid, payload, header)
+%   if not included earlier (F) out-of-band}
+% \commentDaniel{I suggest the following structure:
+%   (A) \Sphinxes
+%   (B) SPOR (global overlay)
+%   (C) SPORES (local overlay).
+%   My original idea was to make \Sphinxes its own section before the design 
+%   section instead of a subsection in the design section.}
 
@@
 
-Figure~\ref{fig:outline} shows the components needed to obtain the
-routing information for the headers.
+% Figure~\ref{fig:outline} shows the components needed to obtain the
+% routing information for the headers.
 
-\begin{figure}[t]
-  \centering
-  \def\svgwidth{0.8\columnwidth}
-  \import{figures/}{outline_figure_only.pdf_tex}
-  \caption{\label{fig:outline}%
-    %\commentDaniel{We must adapt this figure to the text.}%
-    Outline of \name's components. Users' squads of devices are circled in gray. 
-    From top to bottom: a user's devices collaborate through the Squad Overlay 
-    (\cref{sec:squad_overlay}); online devices globally share information about 
-    them with random peers (\cref{ssec:device_availability}); using the two 
-    overlays above allows for the creation of routes (\ac{SPOR}) between sets of devices. 
-    These protocols enable secure file transfer between users 
-    (\cref{ssec:por}).}
-\end{figure}
+% \begin{figure}[t]
+%   \centering
+%   \def\svgwidth{0.8\columnwidth}
+%   \import{figures/}{outline_figure_only.pdf_tex}
+%   \caption{\label{fig:outline}%
+%     %\commentDaniel{We must adapt this figure to the text.}%
+%     Outline of \name's components. Users' squads of devices are circled in gray. 
+%     From top to bottom: a user's devices collaborate through the Squad Overlay 
+%     (\cref{sec:squad_overlay}); online devices globally share information about 
+%     them with random peers (\cref{ssec:device_availability}); using the two 
+%     overlays above allows for the creation of routes (\ac{SPOR}) between sets of devices. 
+%     These protocols enable secure file transfer between users 
+%     (\cref{ssec:por}).}
+% \end{figure}
 
@@
   layers is based on a predictive model for availability, disseminated
-  according to Figure~\ref{fig:outline}, and queried by random peer sampling.
+  by an overlay and queried by random peer sampling.
 \item [Probabilistic.] Instead of source routes with one node per onion layer, each
@@
 
-\subsection{Taxonomy of anonymous communication protocols}
+%\subsection{Taxonomy of anonymous communication protocols}
 
-To present the different parts of \name in details, 
+To present the different parts of \name in detail, 
 we align the presentation of the system with the taxonomy of 
-\textcite{RoutingSurveyAnonymousProtocols}.
+\textcite{RoutingSurveyAnonymousProtocols} .
 They characterize anonymous communication protocols using the following 
@@
 only a probabilistic selection among already selected nodes and only 
-interesting against passive adversaries (an active \sonja{global?} adversary can learn the 
-entire set).
+interesting against passive adversaries (an active adversary can learn the 
+entire set just as she can learn the single node constituting a layer of a
+secure onion-routing scheme without endangering the security
+properties~\cite{CLOnionRouting}).
 

### 2018-08-07 paper/design.tex
New overview figure (Fig 1). Caption still to be added.

--- 2018-08-07 paper/design.tex
@@
   \def\svgwidth{0.8\columnwidth}
-  \import{figures/}{outline_figure_only.pdf_tex}
+  %  \import{figures/}{outline_figure_only.pdf_tex}
+    \includegraphics[width=\columnwidth]{figures/OverviewSPORES_cropped}
   \caption{\label{fig:outline}%
     %\commentDaniel{We must adapt this figure to the text.}%
-    Outline of \name's components. Users' squads of devices are circled in gray. 
-    From top to bottom: a user's devices collaborate through the Squad Overlay 
-    (\cref{sec:squad_overlay}); online devices globally share information about 
-    them with random peers (\cref{ssec:device_availability}); using the two 
-    overlays above allows for the creation of routes (\ac{SPOR}) between sets of devices. 
-    These protocols enable secure file transfer between users 
-    (\cref{ssec:por}).}
+    %% Outline of \name's components. Users' squads of devices are circled in gray. 
+    %% From top to bottom: a user's devices collaborate through the Squad Overlay 
+    %% (\cref{sec:squad_overlay}); online devices globally share information about 
+    %% them with random peers (\cref{ssec:device_availability}); using the two 
+    %% overlays above allows for the creation of routes (\ac{SPOR}) between sets of devices. 
+    %% These protocols enable secure file transfer between users 
+    %% (\cref{ssec:por}).
+    \protect\commentFT{TODO by Francois: describe figure}}
 \end{figure}

### 2018-08-07 paper/security-discussion.tex
added \Sphinxes, some edits in sec discussion

@@
 \begin{enumerate*}
-\item Sphinxes (\cref{Sphinxes}) preserves the properties of 
+\item \Sphinxes (\cref{Sphinxes}) preserves the properties of 
   \textcite{CLOnionRouting} and \textcite{Sphinx} yielding \ac{UC}-secure 
@@
 
-\paragraph*{Security of Sphinxes}
+\paragraph*{Security of \Sphinxes}
 
@@
 are results for ordinary \ac{OR} with only one node per layer.
-\sonja{Daniel is working on sketching a proof/rephrasing the following.}
-As long as we output all the nodes in the next layer, the proofs should not 
-change.
+
+As long as we output all the nodes in the next layer, the results for
+the adversary are the same: the adversary learns the entire
+composition of the layer regardless of whether the set contains a
+single or several nodes.
 We note that this is actually quite natural as a malicious adversary can drop 
@@
 
-With these arguments, we believe that Sphinxes inherits the \ac{UC} security 
-properties of Sphinx, however, this should be formally analysed.
+With these arguments, we believe that \Sphinxes inherits the \ac{UC} security 
+properties of Sphinx. %, however, this should be formally analysed.
 
@@
 Stateless routing can result in re-ordered chunks or packets, and
-chunks received on different devices of a user's squad. From Sphinx,
-we inherit IDs for packets that we we include in the out-of-band
+chunks received on different devices of a user's \squad. From Sphinx,
+we inherit IDs for mix packets that we we include in the out-of-band
 metadata on the file to be exchanged, as an ordered list, that is used
-to re-order chunks if need be. The squad overlay handles inter-squad
-device coordination. Liveness despite the possibility of squad devices
+to re-order chunks if need be. The \squad overlay handles inter-squad
+device coordination. Liveness despite the possibility of \squad devices
 going offline during transfer or other node or link failures is
-ensured by acknowledgements and timeouts as detailed in 
+ensured by acknowledgments and timeouts as detailed in 
 \cref{sec:squad_overlay}.
@@
 statistical disclosure attacks to eventually learn who communicates
-with whom~\cite{StatisticalDisclosureAttacks}. \sonja{Daniel: the
-  reference seems to be missing}  There are also denial
+with whom~\cite{StatisticalDisclosureAttacks}. There are also denial
 of service attacks that can lead to the adversary learning more from
@@
   this denial of security.} Another example is that the source-bounded
-random walk and different routes for file chunks make tracking more
-difficult than with onion routing circuits. A drawback, however, is
+random walk and new routes for file chunks make tracking more
+difficult than with regular onion routing circuits. A drawback, however, is
 that since the chunks can take several paths from source to destination, the source 
@@
 vulnerability to a global passive attacker is not inherent in Sphinx
-or Sphinxes, but can be caused by the way they are applied, \ie the
+or \Sphinxes, but can be caused by the way they are applied, \ie the
 traffic sent. If performance and resource consumption were not an
 issue, batched and well-timed message or file transfer by all nodes
-would render traffic analysis pointless. \Ac{SPORES} inherits the security properties from Sphinxes and \ac{SPOR}.
-However, both Sphinxes and \ac{SPOR} can be used with any mixing strategy, and 
+would render traffic analysis pointless. Concretely, \Ac{SPORES} inherits the security properties from \Sphinxes and \ac{SPOR}.
+However, both \Sphinxes and \ac{SPOR} can be used with any mixing strategy, and 
 the security they provide is as secure as the mixing strategy (or flushing 
@@
 Since \ac{SPORES} aims at low latency, routers do not batch and mix incoming 
-messages; it immediately forwards the messages.
+messages; they immediately forward any messages.
 This puts \ac{SPORES} in the same position as Tor~\cite{Tor}, \ie more 

### 2018-08-07 paper/security-discussion.tex
integrating text from Daniel's uc simulator argument branch

@@
 
-As long as we output all the nodes in the next layer, the results for
-the adversary are the same: the adversary learns the entire
-composition of the layer regardless of whether the set contains a
+Analogously to traditional \ac{OR},  we also reveal the previous and next sets 
+of nodes to the adversary. 
+We note that this is actually quite natural as a malicious adversary can drop 
+any incoming traffic to a router and wait for the timeout and
+retransmission, \ie when the 
+node has selected a new node from the next layer and retried sending.
+As such, the adversary can learn all nodes in the layer --- just as for 
+traditional \ac{OR}, regardless of whether the set making up a layer contains a
 single or several nodes.
-We note that this is actually quite natural as a malicious adversary can drop 
-any incoming traffic to a router and wait for the timeout and retransmission to 
-the next node.
-As such, the adversary can learn all nodes in the layer.
 

### 2018-08-07 paper/security-discussion.tex
Writes up device unlinkability analysis

--- 2018-08-07 paper/security-discussion.tex
@@
 %  have security proofs for their original and individual versions and needing to evaluate the resulting s%chemes}
+
+\commentDaniel{Predecessor attacks: random walk protocols has the problem that 
+  the adversary can see the initiator (statistically) more often than the other 
+  nodes, and can thus identify the 
+  source~\cite{RoutingSurveyAnonymousProtocols}.
+  Our protocol is a \enquote{bounded} random walk, \ie within limits.}
 
@@
 We also changed from the classical \ac{OR} of a fixed path with one node per 
-layer to a set of alternative nodes per layer.
+layer to \ac{POR} with several nodes per layer.
 
-The first change:
 The confidentiality of the key previously rested entirely on the \ac{DH} 
@@
 (\(\gamma\) in the header).
-We still achieve the bitwise unlinkability since \(C\) is replaced at each 
-layer and the next \(C\) is hidden inside the header --- which otherwise 
-remains identical to that of Sphinx.
 
@@
 
+\paragraph*{Device unlinkability}
+
+Alice transfers a file \(f\) to Bob during the time interval 
+\(\interval{t_0}{t_1}\).
+We denote the set of Alice's devices as \(D_A\) and Bob's as \(D_B\).
+Bob wants to compute an estimate \(\hat D_A\) which is as close to \(D_A\) as 
+possible.
+
+At this point, Bob knows that \emph{at least one} of Alice's devices must have 
+been online at any given time in \(\interval{t_0}{t_1}\).
+We can also assume that Bob knows all data from the \ac{RPS}, \ie the \((d, 
+  \pk_d, \avail_d)\) tuple (see \cref{SPOR}) of \emph{every device that was 
+  online at some point during \(\interval{t_0}{t_1}\)}.
+Let \(\A_{\interval{t_0}{t_1}}\subseteq \N\times \G^*\times (\RR\to 
+  \interval{0}{1})\) denote the set of those tuples.
+Thus Bob can approximate \(D_A\) by \(\hat D_A \gets 
+  \A_{\interval{t_0}{t_1}}\cap D_B\).
+
+When Alice and Bob interact the next time, either Alice sends a file \(f'\) to 
+Bob or Bob sends a file \(f'\) to Alice, then Bob can do the same again:
+\(\hat D_A' \gets \A_{\interval{t_0'}{t_1'}} \cap D_B\).
+If at least one of \(d, \pk_d, \avail_d\) remains constant, Bob can use that to 
+improve his approximation.
+Say that \(\avail_d\) remains constant.
+Then Bob can improve his approximation to \(\hat D_A \cap_{\avail_d} 
+  \hat{D}_A'\), where \(\cap_{\avail_d}\) is the intersection which only 
+considers the attribute \(\avail_d\).
+Even if \(\avail_d\) is not constant, its variation might stay inside some 
+\(\epsilon\)-neighbourhood, and if \(\epsilon\) is small enough, \(\avail_d\) 
+might still be used to distinguish Alice.
+The same applies for \(d\).
+(\(\pk_d\) can be regularly updated.)
+
+With an inaccurate availability function, \(\avail\), this will not be a 
+problem as there will be many (as the system scales) that shares the same 
+availability distribution.
+With more accurate availability estimates we would have to employ techniques 
+like \ac{DP}.
+
 \paragraph*{Robustness}
@@
   protocol must resend.'' why?}  \commentDaniel{We should look into
-  this denial of security.} Another example is that the source-bounded
-random walk and different routes for file chunks make tracking more
-difficult than with onion routing circuits. A drawback, however, is
-that since the chunks can take several paths from source to destination, the source 
-will send and the destination will receive more traffic than other nodes in the 
-network~\cite{RoutingSurveyAnonymousProtocols}. However, this is mitigated by the fact that the source and 
-destination can be several different devices --- \ie from the \squads.
-
-We would also like to point out that
+  this denial of security.} We would also like to point out that
 vulnerability to a global passive attacker is not inherent in Sphinx
@@
 issue, batched and well-timed message or file transfer by all nodes
-would render traffic analysis pointless. \Ac{SPORES} inherits the security properties from Sphinxes and \ac{SPOR}.
-However, both Sphinxes and \ac{SPOR} can be used with any mixing strategy, and 
-the security they provide is as secure as the mixing strategy (or flushing 
-algorithm) allows.
-Since \ac{SPORES} is a fully-fledged system, it must make a concrete choice for 
-the mixing strategy.
-Since \ac{SPORES} aims at low latency, routers do not batch and mix incoming 
-messages; it immediately forwards the messages.
-This puts \ac{SPORES} in the same position as Tor~\cite{Tor}, \ie more 
-vulnerable to traffic analysis than batching 
-mix-nets~\cite{RoutingSurveyAnonymousProtocols} \commentDaniel{we should 
-  probably look for the original papers} --- this vulnerability is inherited 
-from the mixing strategy.
-
-% \commentDaniel{Predecessor attacks: random walk protocols has the problem that 
-%   the adversary can see the initiator (statistically) more often than the other 
-%   nodes, and can thus identify the 
-%   source~\cite{RoutingSurveyAnonymousProtocols}.
-%   Our protocol is a \enquote{bounded} random walk, \ie within limits.}
+would render traffic analysis pointless.

### 2018-08-07 paper/design.tex
added caption for overview figure

--- 2018-08-07 paper/design.tex
@@
 
-% Figure~\ref{fig:outline} shows the components needed to obtain the
-% routing information for the headers.
+%% Figure~\ref{fig:outline} shows the components needed to obtain the
+%% routing information for the headers.
 
-% \begin{figure}[t]
-%   \centering
-%   \def\svgwidth{0.8\columnwidth}
+\begin{figure}[t]
+  \centering
+  \def\svgwidth{0.8\columnwidth}
   %  \import{figures/}{outline_figure_only.pdf_tex}
-%   \caption{\label{fig:outline}%
-%     %\commentDaniel{We must adapt this figure to the text.}%
-%     Outline of \name's components. Users' squads of devices are circled in gray. 
-%     From top to bottom: a user's devices collaborate through the Squad Overlay 
-%     (\cref{sec:squad_overlay}); online devices globally share information about 
-%     them with random peers (\cref{ssec:device_availability}); using the two 
-%     overlays above allows for the creation of routes (\ac{SPOR}) between sets of devices. 
-%     These protocols enable secure file transfer between users 
-%     (\cref{ssec:por}).}
-% \end{figure}
+    \includegraphics[width=\columnwidth]{figures/OverviewSPORES_cropped}
+    \caption{Architectural overview of the \ac{SPORES} private file sharing service.
+\ac{SPORES} relies on a predictive and probabilistic onion routing protocol (\ac{SPOR}).
+\ac{SPOR} in turn combines a multi-set mix-header format (\Sphinxes) together with a node selection protocol that exploit decentralized prediction regarding node availability to optimize the reliability of \Sphinxes without jeopardizing its security properties.}
+    \label{fig:outline}
+\end{figure}
 

### 2018-08-07 paper/approach.tex
up

--- 2018-08-07 paper/design.tex
@@
-%!TEX root = p2p-private-cloud.tex
-
-\section{Design of the \name file transfer system}%
-\label{design}
-
-% \sonja{will frame and structure (A) squad overlay (prediction) (B)
-%   global overlay (RPS) (C) sphinxes (incl.\ sphinx, onion routing in
-%   general) (D) SPOR and SPORES (E) encryption (hybrid, payload, header)
-%   if not included earlier (F) out-of-band}
-% \commentDaniel{I suggest the following structure:
-%   (A) \Sphinxes
-%   (B) SPOR (global overlay)
-%   (C) SPORES (local overlay).
-%   My original idea was to make \Sphinxes its own section before the design 
-%   section instead of a subsection in the design section.}
-
-\subsection{Key features of \name}
+\section{Overall approach}%
+\label{approach}
 
@@
 
-\begin{figure}[t]
+\begin{figure}[hbt]
   \centering
@@
     \includegraphics[width=\columnwidth]{figures/OverviewSPORES_cropped}
-    \caption{Architectural overview of the \ac{SPORES} private file sharing service.
-\ac{SPORES} relies on a predictive and probabilistic onion routing protocol (\ac{SPOR}).
-\ac{SPOR} in turn combines a multi-set mix-header format (\Sphinxes) together with a node selection protocol that exploit decentralized prediction regarding node availability to optimize the reliability of \Sphinxes without jeopardizing its security properties.}
-    \label{fig:outline}
+  \caption{\label{fig:outline}%
+    %\commentDaniel{We must adapt this figure to the text.}%
+    %% Outline of \name's components. Users' squads of devices are circled in gray. 
+    %% From top to bottom: a user's devices collaborate through the Squad Overlay 
+    %% (\cref{sec:squad_overlay}); online devices globally share information about 
+    %% them with random peers (\cref{ssec:device_availability}); using the two 
+    %% overlays above allows for the creation of routes (\ac{SPOR}) between sets of devices. 
+    %% These protocols enable secure file transfer between users 
+    %% (\cref{ssec:por}).
+    \protect\commentFT{TODO by Francois: describe figure}}
 \end{figure}
@@
 messages by fragmentation and reassembly across the devices in the \squad.
-
-\include*{sphinxes}
-\include*{spor}
-\include*{squad-overlay-design}
-%\include*{file-transfer-design}

### 2018-08-07 paper/design.tex
up

@@
 
-\subsection{Key features of \name}
-
-Our goal is to enable private and reliable file exchange between users 
-participating in the system, by using their respective devices only.
-When Alice and Bob, two users of our system, want to exchange a file \(f\) 
-through \name, they start by sharing some information out-of-band, \eg from 
-their smartphones.
-More precisely, they exchange metadata on \(f\), encryption keys, and
-some use-once reply mix-headers.
-They use these reply headers to transfer the file contents of \(f\) over a 
-network of unreliable nodes while also achieving privacy.
-
-%% Figure~\ref{fig:outline} shows the components needed to obtain the
-%% routing information for the headers.
-
-\begin{figure}[t]
-  \centering
-  \def\svgwidth{0.8\columnwidth}
-  %  \import{figures/}{outline_figure_only.pdf_tex}
-    \includegraphics[width=\columnwidth]{figures/OverviewSPORES_cropped}
-    \caption{Architectural overview of the \ac{SPORES} private file sharing service.
-\ac{SPORES} relies on a predictive and probabilistic onion routing protocol (\ac{SPOR}).
-\ac{SPOR} in turn combines a multi-set mix-header format (\Sphinxes) together with a node selection protocol that exploit decentralized prediction regarding node availability to optimize the reliability of \Sphinxes without jeopardizing its security properties.}
-    \label{fig:outline}
-\end{figure}
-
-After the initial, out-of-band setup, file transfer happens along
-onion routes but with the following features:
-
-\begin{description}
-\item [Stateless.] There is no mandatory circuit creation, the file transfer can be
-  done in a stateless way. 
-\item [Predictive.] The choice of nodes included in the onion routing
-  layers is based on a predictive model for availability, disseminated
-  by an overlay and queried by random peer sampling.
-\item [Probabilistic.] Instead of source routes with one node per onion layer, each
-  layer consists of a set of nodes and although the source route still
-  determines the sequence of layers, the actual node used for the next
-  hop of forwarding is selected from the set in an ad-hoc way,
-  resulting in a source-bounded random walk.
-\item[Onion Routing.] Put simply, in onion routing, the sender creates
-  a source route and 
-  encapsulates the payload and next-hop information in layers (by
-  encryption), that are \emph{peeled} (decrypted) one by one along the
-  route. By virtue of these layers, the forwarding nodes on the
-  route do not know where on the route they are and thus whether they
-  have received a packet directly from the sender or some other
-  intermediate node. We base our format for layering and peeling on
-  Sphinx~\cite{Sphinx}, with some modification to allow for the
-  changes above, described in \cref{Sphinxes}.
-\end{description}
-
-%\subsection{Taxonomy of anonymous communication protocols}
-
-To present the different parts of \name in detail, 
-we align the presentation of the system with the taxonomy of 
-\textcite{RoutingSurveyAnonymousProtocols} .
-They characterize anonymous communication protocols using the following 
-categories (see~\cite[Table 1]{RoutingSurveyAnonymousProtocols}):
-\begin{description}
-  \item[Network structure.]
-    It describes the characteristics of the network nodes, the connections between 
-    them and the underlying topology.
-    The subcategories are
-    \begin{enumerate*}
-      \item network topology,
-      \item connection type (direction, synchronization),
-      \item symmetry (node roles, node topology for routing, decentralization);
-    \end{enumerate*}
-
-  \item[Routing information.]
-    It describes the network information available to entities deciding on 
-    the route of an anonymous file exchange.
-    The subcategories are
-    \begin{enumerate*}
-      \item network view necessary for making routing decisions,
-      \item triggers for routing information updates;
-    \end{enumerate*}
-
-  \item[Communication model.]
-   It describes the entities that make the routing decisions and how they 
-    make these decisions.
-    The subcategories are
-    \begin{enumerate*}
-      \item routing type (who selects nodes per route),
-      \item scheduling (traffic prioritization),
-      \item node selection (determinism, selection set, selection probability);
-    \end{enumerate*}
-
-  \item[Performance.]
-    It describes things like latency and communication mode.
-    The subcategories are
-    \begin{enumerate*}
-      \item protocol latency,
-      \item communication mode (connection- or message-based).
-    \end{enumerate*}
-\end{description}
-
-We first describe \sphinxes (\cref{Sphinxes}), which is an adaptation of the
-
-\sonja{do we apply all categories here?}
-
-Sphinx~\cite{Sphinx} mix-header format.
-This means that we inherit some properties from Sphinx and due to being only a 
-header format, it only imposes some restrictions in the above categories.
-\Sphinxes provides, just as Sphinx, unidirectional (network structure), 
-message-based (performance) communication.
-But unlike Sphinx, \Sphinxes is hybrid source-hop-by-hop routed, a
-source-bounded random walk (communication 
-model),
-\Sphinxes relies on a flat routing-topology (network structure) with fair 
-scheduling (communication model) --- as all packets are indistinguishable they 
-must be processed on a first-in-first-out basis.
-\Sphinxes also introduces some probability to the node selection, but this is 
-only a probabilistic selection among already selected nodes and only 
-interesting against passive adversaries (an active adversary can learn the 
-entire set just as she can learn the single node constituting a layer of a
-secure onion-routing scheme without endangering the security
-properties~\cite{CLOnionRouting}).
-
-\Sphinxes does \emph{not} introduce any restrictions on whether the network 
-topology must be fully connected or not, be asynchronous (as in Tor) or 
-synchronous (as in mix-nets), whether node selection must be uniformly random 
-or not.
-Just as Sphinx, it can be used in many different settings.
-
-Next, we describe the \ac{SPOR} protocol (\cref{SPOR}).
-\commentAL{A lot of description here, should only come in Section~\ref{sec:squad_overlay}}
-This focuses on the node selection, \ie adds node selection on top of \Sphinxes.
-The \ac{SPOR} protocol assumes a source of random nodes, \eg through 
-\ac{RPS}~\cite[\eg][]{BrahmsRPS} or \iac{DHT} based 
-scheme~\cite[\eg][]{Octopus}.
-Each node must be associated with a public key and some availability 
-prediction.
-\Ac{SPOR} selects nodes for a route uniformly randomly and uses the 
-availability to maximize the availability of the entire route, \ie across 
-layers.
-As \ac{SPOR} assumes this source of random nodes, the network view (routing 
-information) of each node depends on this source of random nodes, as does the 
-fact of how decentralized the scheme becomes and whether the network toppology 
-is fully, mostly or partly connected (network structure).
-As \ac{SPOR} is designed, it selects nodes uniformly among all the nodes 
-(communication model, node selection) that the source of random nodes provides.
-Thus, ultimately, these also depends on the source of random nodes.
-
-A device's availability depends on its user's behavior, hence the device must 
-predict this behavior.
-This is best done jointly between all of the user's devices.
-In \cref{sec:squad_overlay}, we describe a protocol which allows the devices to 
-compute their own availability prediction function based on the observations by 
-all other devices.
-
-Finally, we describe the complete \ac{SPORES} protocol (\cref{SPORES}), which 
-allows the device \squad to act as an autonomous system.
-In particular, we introduce a protocol which allows transferring larger 
-messages by fragmentation and reassembly across the devices in the \squad.
-
-\include*{sphinxes}
+%\include*{sphinxes}
 \include*{spor}
 \include*{squad-overlay-design}
-%\include*{file-transfer-design}
+\include*{file-transfer-design}

### 2018-08-07 paper/intro.tex
typo in intro, started conclusion edits, more needed

@@
 multiple data centers, often in foreign jurisdictions, making it difficult for most users to grasp, review, and assess the privacy, and
-confidentiality guaranties they can expect. In practice, user data hosted in the cloud is routinely harvested, often without explicit
-consent, either by cloud providers or third parties.
+confidentiality guarantees they can expect. In practice, user data hosted in the cloud is routinely harvested, often without explicit
+consent, either by cloud providers or third parties, only partially
+mitigated by legal measures such as the GDPR.
 
@@
 In this model, user devices, masquerading as allies, get turned into %% tracking and/or monitoring \squad{}s, and serve as
-highly efficient spies over their owners.
+highly efficient instruments spying on their owners.
 
@@
 \cite{Tor}, one of the most popular anonymous networks,
-trades lower anonymity guaranties for a much better performance. Tor's lower protection arises from
+trades lower anonymity guarantees for a much better
+performance. \sonja{lower than who?} Tor's lower protection arises from
 a partially centralized design that hinges on a set of \emph{directory
@@
 In this paper, we demonstrate how good performance can be reconciled
-with strong privacy protection in data-sharing systems. We present
+with strong privacy protection in file transfer systems. We present
 \name{}, a novel fully decentralized, autonomous,
 % approach that provides a 
-and self-organizing file sharing service between the \squad{}s of different users that preserves user privacy
+and self-organizing file transfer service between the \squad{}s of different users that preserves user privacy
 in terms of both data \emph{and} metadata. \commentFT{Moving to 3 ideas, to highlight proxemics in its own right} Our proposal hinges on three
@@
 \emph{probabilistic predictive onion routing} mechanism. The
-predictive nature of our routing, exploited in a stateless way, allows us to overcome the inherent fragility of pure P2P data-sharing schemes.
+predictive nature of our routing, exploited in a stateless way, allows
+us to overcome the inherent fragility of pure P2P file transfer schemes.
 
@@
 
-\sonja{commented out my changes, left Daniel's in merge conflict, left
-  my changes on paper outline} 
 Our contributions are as follows: 
@@
 
-  \item We provide the \ac{SPOR} node selection strategy which, given a secure 
+  \item We provide the \ac{SPOR} node selection strategy for routing which, given a secure 
     \ac{RPS} protocol and availability estimates, selects nodes to populate the 
@@
 
-  \item We provide a protocol for a device swarm to estimate the availabilities 
-    of its own devices.
+  \item We provide a protocol for a device squad to estimate the availabilities 
+    of its own devices, based on Markov models and \squad overlays.
     These availabilities can then be used with \ac{SPOR}.
-    \commentDaniel{We should add some more details, maybe.}
+   % \commentDaniel{We should add some more details, maybe.}
 
-  \item We use \ac{SPOR} to design \name: a novel, fully decentralized, 
-    autonomous and self-organizing file transfer service among users.
+  \item We use \ac{SPOR} to design \name \sonja{removed for
+      redundancy, rephrased: a novel, fully decentralized, 
+    autonomous and self-organizing} as a privacy-preserving file transfer service among
+  users without third-party storage.
 
@@
 
-In the following, in Section~\ref{system-model}, we introduce the
+In the following, in Section~\ref{system-model}, we state the
 system and adversary models as well as the desired security and privacy properties of \name. Section~\ref{design}

### 2018-08-07 paper/security-discussion.tex

--- 2018-08-07 paper/security-discussion.tex
@@
 The proofs of Sphinx rest on the results of \textcite{CLOnionRouting}, which 
-are results for ordinary \ac{OR} with only one node per layer.
+are results for traditional \ac{OR} with only one node per layer.
+We must thus ensure that the proofs of \citeauthor{CLOnionRouting} also holds 
+for sets of nodes.
 
@@
 We note that this is actually quite natural as a malicious adversary can drop 
-any incoming traffic to a router and wait for the timeout and
-retransmission, \ie when the 
+any incoming traffic to a router and wait for the retransmission, \ie when the 
 node has selected a new node from the next layer and retried sending.

### 2018-08-07 paper/sphinxes.tex
fixing conflict resolution error
fixing compil error

@@
 
-\subsection{Sphinxes: the Sphinx header format Extended for Sets of nodes}%
+\subsection{\Sphinxes: the Sphinx header format Extended for Sets of nodes}%
 \label{Sphinxes}
@@
 Sphinx only provides one node per onion layer; in this section we extend Sphinx 
-to Sphinxes, which allows for multiple nodes per onion layer.
+to \Sphinxes, which allows for multiple nodes per onion layer.
 (See \cref{fig:OR-POR}.)
 % AL: Bounded random-walk....
-As such, Sphinxes could be described as a bounded random-walk protocol, \ie the 
+As such, \Sphinxes could be described as a bounded random-walk protocol, \ie the 
 each node selects the next node from a set restricted by the source.
@@
     Illustration of the conceptual difference between traditional onion routing 
-
 and mixing (OR, top) and \ac{SPOR} (bottom).
-
     %\commentDaniel{This figure should be fixed, issue \#42.}
@@
 reader enough understanding of Sphinx to understand the changes we make to 
-achieve Sphinxes.
+achieve \Sphinxes.
 For a more detailed understanding of Sphinx, we refer the reader to the 
@@
 
-\subsubsection{The Sphinxes extension for sets of nodes}
+\subsubsection{The \Sphinxes extension for sets of nodes}
 
@@
 
-\subsubsection{Sphinxes algorithms and \acf*{SPOR}}
+\subsubsection{\Sphinxes algorithms and \acf*{SPOR}}
 
-Sphinxes provides the following algorithms:
+\Sphinxes provides the following algorithms:
 \begin{itemize}
@@
 
-If \(L' = \{\rdvnode\}\), the packet payload contains another Sphinxes packet 
+If \(L' = \{\rdvnode\}\), the packet payload contains another \Sphinxes packet 
 to be forwarded.

### 2018-08-07 paper/squad-overlay-design.tex

@@
 	\item \texttt{SENDING<\sendingdevice, \fileid>}: When the user decides to send a file $f$ located on a device \sendingdevice, \sendingdevice informs its peers of this fact, and joins the file ID \fileid.
-Squad members will use this information to forward acknowledgments from the remote to \sendingdevice;
+\Squad members will use this information to forward acknowledgments from the recipient to \sendingdevice;
 	\item \texttt{RECEIVING<\recdevice, \fileid>}: Reciprocally, when the user starts receiving a file $f$ onto a device \recdevice, \recdevice informs its peers of this fact, and joins the file ID \fileid.
-Squad members will use this information to forward the file's content from the remote to \recdevice.
+\Squad members will use this information to forward the file's content from the sender to \recdevice.
 \end{itemize}
@@
 
-% Every time Bob successfully receives a chunk $\chunk_i$, \recdevice sets the bit $\bitfield[i]$, 
-% To acknowledge the chunk's reception, \recdevice sends \bitfield back to Alice, through a unique route $\mathcal{H}'_{\chunk_i}$.
-
 Reciprocally, acknowledgments can arrive to Alice on any on her devices, while only \sendingdevice can process it.

### 2018-08-07 paper/system-model.tex

@@
 means that even for an onion created by an adversary, the path length
-is bounded by $N$. \textit{Onion-security} means that an adversary sending a
-challenge onion \david{what is a challenge onion?} to a router and able to see the outcome of how the
-onion is processed, cannot distinguish between whether that onion
+is bounded by $N$. \textit{Onion-security} means that an adversary sending an
+ onion to a router as a challenge
+ and able to see the response (the outcome of how the
+onion is processed), cannot distinguish between whether that onion
 corresponds to a particular message and route or not. This is also
-true for a \emph{re-wrapped} onion, \ie a challenge onion wrapped in
+true for a \emph{re-wrapped} onion, \ie a challenge (onion) wrapped in
 another layer. The formal definitions are in~\cite{CLOnionRouting} along
@@
 these three properties, combined with secure point-to-point channels,
-is UC-secure \david{what does it means, it has never been introduced
-  before, what do you mean?}.
+is universal composability (UC)-secure, \ie the protocol remains
+secure even if arbitrarily composed with other instances of the same or other protocols.
 These properties cover the concerns about
@@
 place. In \name, we additionally derive the property of
-\emph{device-unlinkability} from the \ac{P2P} requirements, meaning that
+\emph{device-unlinkability} from the \ac{P2P} requirements above, meaning that
 using \name does not reveal the \squad a device belongs to nor its
 owner. Thus, no information on the user's behavior (e.g. being online)
-can be infered through \name. \sonja{insert more formal definition
+can be infered through \name. 
+\sonja{insert more formal definition
   here, and perhaps explanation that we need it because we introduce

### 2018-08-07 paper/approach.tex

--- 2018-08-07 paper/design.tex
@@
-%!TEX root = p2p-private-cloud.tex
-
-\section{Design of the \name file transfer system}%
-\label{design}
-
-% \sonja{will frame and structure (A) squad overlay (prediction) (B)
-%   global overlay (RPS) (C) sphinxes (incl.\ sphinx, onion routing in
-%   general) (D) SPOR and SPORES (E) encryption (hybrid, payload, header)
-%   if not included earlier (F) out-of-band}
-% \commentDaniel{I suggest the following structure:
-%   (A) \Sphinxes
-%   (B) SPOR (global overlay)
-%   (C) SPORES (local overlay).
-%   My original idea was to make \Sphinxes its own section before the design 
-%   section instead of a subsection in the design section.}
-
-\subsection{Key features of \name}
-
+\section{Overall approach}%
+\label{approach}
 Our goal is to enable private and reliable file exchange between users 

### 2018-08-07 paper/security-discussion.tex

@@
 The proofs of Sphinx rest on the results of \textcite{CLOnionRouting}, which 
-are results for traditional \ac{OR} with only one node per layer.
-We must thus ensure that the proofs of \citeauthor{CLOnionRouting} also holds 
-for sets of nodes.
+are results for ordinary \ac{OR} with only one node per layer.
 
@@
 We note that this is actually quite natural as a malicious adversary can drop 
-any incoming traffic to a router and wait for the retransmission, \ie when the 
+any incoming traffic to a router and wait for the timeout and
+retransmission, \ie when the 
 node has selected a new node from the next layer and retried sending.

### 2018-08-07 paper/evaluation.tex
minor eval git submodule update

@@
 \label{ssub:simulating_user_behavior}
-
-\newcommand\tuser{\ensuremath{t_{\text{user}}}}
-\newcommand\ndevices{\ensuremath{n_{\text{devices}}}}
 
@@
 \paragraph*{File transfer} The main parameter here is the chunk size \chunksize, that was set to 512KB, which is considered, in BitTorrent, to be a good trade-off between network efficiency and number of chunks.
-The other parameter, \tupload, was empirically set to 500ms.
+The other parameter, \tupload, that is the period between two chunk sends, was empirically set to 500ms.
 
-\paragraph*{Users' behavior} Finally we set \tuser to 3s.
+\paragraph*{Users' behavior} We set \tuser, the time between two user actions, to 3s.
 
@@
   \caption{\label{fig:bw_and_pending_files}Traffic during one experiment.
-  In gray: number of pending file exchanges; in black: mean outbound traffic (kB) per node per second.}
-\end{figure}
-
-\begin{figure}[t]
-  \centering
-  %\def\svgwidth{0.8\columnwidth}
-  \includegraphics[width=\columnwidth]{figures/bw_and_pending_files_log.pdf}
-
-  \caption{\label{fig:bw_and_pending_files_log}Traffic during one experiment.
   In gray: number of pending file exchanges; in black: mean outbound traffic (kB) per node per second.}

### 2018-08-08 paper/security-discussion.tex
Changes traditional OR to classical OR

@@
 The proofs of Sphinx rest on the results of \textcite{CLOnionRouting}, which 
-are results for ordinary \ac{OR} with only one node per layer.
+are results for classical \ac{OR} with only one node per layer.
 
-Analogously to traditional \ac{OR},  we also reveal the previous and next sets 
-of nodes to the adversary. 
-We note that this is actually quite natural as a malicious adversary can drop 
-any incoming traffic to a router and wait for the timeout and
+Analogously to classical \ac{OR}, we also reveal the previous and next sets of 
+nodes to the adversary. We note that this is actually quite natural as a 
+malicious adversary can drop any incoming traffic to a router and wait for the 
+timeout and
 retransmission, \ie when the 
@@
 As such, the adversary can learn all nodes in the layer --- just as for 
-traditional \ac{OR}, regardless of whether the set making up a layer contains a
+classical \ac{OR}, regardless of whether the set making up a layer contains a
 single or several nodes.

### 2018-08-08 paper/approach.tex

@@
     \includegraphics[width=\columnwidth]{figures/OverviewSPORES_cropped}
-    \caption{Architectural overview of the \ac{SPORES} private file sharing service.
-\ac{SPORES} relies on a predictive and probabilistic onion routing protocol (\ac{SPOR}).
-\ac{SPOR} in turn combines a multi-set mix-header format (\Sphinxes) together with a node selection protocol that exploit decentralized prediction regarding node availability to optimize the reliability of \Sphinxes without jeopardizing its security properties.}
+    \caption{Architectural overview of the \ac{SPORES} private file sharing service.}
     \label{fig:outline}
@@
 After the initial, out-of-band setup, file transfer happens along
-onion routes but with the following features:
-
-\begin{description}
-\item [Stateless.] There is no mandatory circuit creation, the file transfer can be
-  done in a stateless way. 
-\item [Predictive.] The choice of nodes included in the onion routing
+onion routes with the following features:\\
+\textbf{Stateless.} There is no mandatory circuit creation, the file transfer can be
+  done in a stateless way. \\
+\textbf{Predictive.} The choice of nodes included in the onion routing
   layers is based on a predictive model for availability, disseminated
-  by an overlay and queried by random peer sampling.
-\item [Probabilistic.] Instead of source routes with one node per onion layer, each
+  by an overlay and queried by random peer sampling.\\
+ \textbf{Probabilistic.} Instead of source routes with one node per onion layer, each
   layer consists of a set of nodes and although the source route still
@@
   hop of forwarding is selected from the set in an ad-hoc way,
-  resulting in a source-bounded random walk.
-\item[Onion Routing.] Put simply, in onion routing, the sender creates
-  a source route and 
-  encapsulates the payload and next-hop information in layers (by
+  resulting in a source-bounded random walk.\\
+ \textbf{Onion Routing.} Put simply, in onion routing, the sender creates
+  a source route and encapsulates the payload and next-hop information in layers (by
   encryption), that are \emph{peeled} (decrypted) one by one along the
@@
   changes above, described in \cref{Sphinxes}.
-\end{description}
+
+% \begin{description}
+% \item [Stateless.] There is no mandatory circuit creation, the file transfer can be
+%   done in a stateless way. 
+% \item [Predictive.] The choice of nodes included in the onion routing
+%   layers is based on a predictive model for availability, disseminated
+%   by an overlay and queried by random peer sampling.
+% \item [Probabilistic.] Instead of source routes with one node per onion layer, each
+%   layer consists of a set of nodes and although the source route still
+%   determines the sequence of layers, the actual node used for the next
+%   hop of forwarding is selected from the set in an ad-hoc way,
+%   resulting in a source-bounded random walk.
+% \item[Onion Routing.] Put simply, in onion routing, the sender creates
+%   a source route and 
+%   encapsulates the payload and next-hop information in layers (by
+%   encryption), that are \emph{peeled} (decrypted) one by one along the
+%   route. By virtue of these layers, the forwarding nodes on the
+%   route do not know where on the route they are and thus whether they
+%   have received a packet directly from the sender or some other
+%   intermediate node. We base our format for layering and peeling on
+%   Sphinx~\cite{Sphinx}, with some modification to allow for the
+%   changes above, described in \cref{Sphinxes}.
+% \end{description}
 
@@
 we align the presentation of the system with the taxonomy of 
-\textcite{RoutingSurveyAnonymousProtocols} .
+\textcite{RoutingSurveyAnonymousProtocols}.
 They characterize anonymous communication protocols using the following 
-categories (see~\cite[Table 1]{RoutingSurveyAnonymousProtocols}):
-\begin{description}
-  \item[Network structure.]
-    It describes the characteristics of the network nodes, the connections between 
-    them and the underlying topology.
-    The subcategories are
-    \begin{enumerate*}
-      \item network topology,
-      \item connection type (direction, synchronization),
-      \item symmetry (node roles, node topology for routing, decentralization);
-    \end{enumerate*}
+categories: (i) \textit{network structure}, (ii) \textit{routing information},
+(iii) \textit{communication model} and (iv) \textit{performance} (see~\cite[Table 1]{RoutingSurveyAnonymousProtocols}).
 
-  \item[Routing information.]
-    It describes the network information available to entities deciding on 
-    the route of an anonymous file exchange.
-    The subcategories are
-    \begin{enumerate*}
-      \item network view necessary for making routing decisions,
-      \item triggers for routing information updates;
-    \end{enumerate*}
+% \begin{description}
+%   \item[Network structure.]
+%     It describes the characteristics of the network nodes, the connections between 
+%     them and the underlying topology.
+%     The subcategories are
+%     \begin{enumerate*}
+%       \item network topology,
+%       \item connection type (direction, synchronization),
+%       \item symmetry (node roles, node topology for routing, decentralization);
+%     \end{enumerate*}
 
-  \item[Communication model.]
-   It describes the entities that make the routing decisions and how they 
-    make these decisions.
-    The subcategories are
-    \begin{enumerate*}
-      \item routing type (who selects nodes per route),
-      \item scheduling (traffic prioritization),
-      \item node selection (determinism, selection set, selection probability);
-    \end{enumerate*}
+%   \item[Routing information.]
+%     It describes the network information available to entities deciding on 
+%     the route of an anonymous file exchange.
+%     The subcategories are
+%     \begin{enumerate*}
+%       \item network view necessary for making routing decisions,
+%       \item triggers for routing information updates;
+%     \end{enumerate*}
 
-  \item[Performance.]
-    It describes things like latency and communication mode.
-    The subcategories are
-    \begin{enumerate*}
-      \item protocol latency,
-      \item communication mode (connection- or message-based).
-    \end{enumerate*}
-\end{description}
+%   \item[Communication model.]
+%    It describes the entities that make the routing decisions and how they 
+%     make these decisions.
+%     The subcategories are
+%     \begin{enumerate*}
+%       \item routing type (who selects nodes per route),
+%       \item scheduling (traffic prioritization),
+%       \item node selection (determinism, selection set, selection probability);
+%     \end{enumerate*}
 
-We first describe \sphinxes (\cref{Sphinxes}), which is an adaptation of the
+%   \item[Performance.]
+%     It describes things like latency and communication mode.
+%     The subcategories are
+%     \begin{enumerate*}
+%       \item protocol latency,
+%       \item communication mode (connection- or message-based).
+%     \end{enumerate*}
+% \end{description}
 
-\sonja{do we apply all categories here?}
-
-Sphinx~\cite{Sphinx} mix-header format.
+As depicted in Figure~\ref{fig:outline}, \ac{SPORES} relies on a predictive and probabilistic onion routing protocol (\ac{SPOR}).
+\ac{SPOR} in turn combines a multi-set mix-header format (\Sphinxes) together with a node selection protocol that exploit decentralized prediction regarding node availability to optimize the reliability of \Sphinxes without jeopardizing its security properties.
+Particularly, \sphinxes (\cref{Sphinxes}), is an adaptation of the 
+\sonja{do we apply all categories here?} Sphinx~\cite{Sphinx} mix-header format.
 This means that we inherit some properties from Sphinx and due to being only a 
@@
 
-Next, we describe the \ac{SPOR} protocol (\cref{SPOR}).
-\commentAL{A lot of description here, should only come in Section~\ref{sec:squad_overlay}}
-This focuses on the node selection, \ie adds node selection on top of \Sphinxes.
+Further, \ac{SPOR} protocol (\cref{SPOR}) adds node selection on top of \Sphinxes.
 The \ac{SPOR} protocol assumes a source of random nodes, \eg through 

### 2018-08-08 paper/approach.tex
up

@@
 header format, it only imposes some restrictions in the above categories.
-\Sphinxes provides, just as Sphinx, unidirectional (network structure), 
+\Sphinxes (Figure~\ref{fig:outline} \ding{202}) provides, just as Sphinx, unidirectional (network structure), 
 message-based (performance) communication.
-But unlike Sphinx, \Sphinxes is hybrid source-hop-by-hop routed, a
+But unlike Sphinx, \Sphinxes is an hybrid source-hop-by-hop routed, and a
 source-bounded random walk (communication 
-model),
-\Sphinxes relies on a flat routing-topology (network structure) with fair 
+model). \Sphinxes relies on a flat routing-topology (network structure) with fair 
 scheduling (communication model) --- as all packets are indistinguishable they 
@@
 
-Further, \ac{SPOR} protocol (\cref{SPOR}) adds node selection on top of \Sphinxes.
-The \ac{SPOR} protocol assumes a source of random nodes, \eg through 
+Further, \ac{SPOR} protocol (\cref{design}) adds node selection on top of \Sphinxes.
+The \ac{SPOR} protocol (Figure~\ref{fig:outline} \ding{203})  assumes a source of random nodes, \eg through 
 \ac{RPS}~\cite[\eg][]{BrahmsRPS} or \iac{DHT} based 
@@
 A device's availability depends on its user's behavior, hence the device must 
-predict this behavior.
-This is best done jointly between all of the user's devices.
-In \cref{sec:squad_overlay}, we describe a protocol which allows the devices to 
+predict this behavior. This is best done jointly between all of the user's devices.
+%In \cref{sec:squad_overlay}, we describe
+Accordingly we introduce a protocol that allows the devices to 
 compute their own availability prediction function based on the observations by 
@@
 
-Finally, we describe the complete \ac{SPORES} protocol (\cref{SPORES}), which 
-allows the device \squad to act as an autonomous system.
+Finally, we introduce the complete \ac{SPORES} protocol, which 
+allows the device \squad to act as an autonomous system (Figure~\ref{fig:outline} \ding{204}).
 In particular, we introduce a protocol which allows transferring larger 

### 2018-08-08 paper/approach.tex
up

@@
 
-Finally, we introduce the complete \ac{SPORES} protocol, which 
-allows the device \squad to act as an autonomous system (Figure~\ref{fig:outline} \ding{204}).
+Finally, we introduce the complete \ac{SPORES} protocol that acts as a private P2P file transfer. It 
+allows the device \squad to act as an autonomous system.
 In particular, we introduce a protocol which allows transferring larger 
-messages by fragmentation and reassembly across the devices in the \squad.
+messages by fragmentation and reassembly across the devices in the \squad  (Figure~\ref{fig:outline} \ding{204}).

### 2018-08-08 paper/evaluation.tex
eval in progress

@@
 All our experiments were conducted with 25 users participating in \name. 
-The files exchanged are a collection of 12 real ones, ranging from 5KB to 640MB.
+The files exchanged are a collection of 12 real ones, ranging from 6KB to 640MB.
 
@@
 
+\subsubsection{Experimental process} % (fold)
+\label{ssub:experimental_process}
+
+\begin{figure}[t]
+  \centering
+  %\def\svgwidth{0.8\columnwidth}
+  \includegraphics[width=\columnwidth]{figures/bw_and_pending_files.pdf}
+
+  \caption{\label{fig:bw_and_pending_files}Timeline of one experiment's traffic.
+  In gray: number of pending file exchanges; in black: mean outbound traffic (kB) per node per second.}
+\end{figure}
+
+The experiments were conducted as follows: 
+\begin{itemize}
+  \item A first initialization procedure takes care of bootstrapping the users and their devices. 
+  A scheduler is started for each user, that will turn devices on or off throughout the experiment according to the models discussed in~\ref{ssub:simulating_user_behavior};
+  \item The 12 file exchanges are initiated in turn: a couple $(d_s, d_r)$ of online devices from different users is chosen.
+  The sender $d_s$ is requested to initialize file upload
+\end{itemize}
+
+% subsubsection experimental_process (end)
+
 \subsection{File transfer}
@@
 
-Overall, we saw 94\% of successful file transfer.
+Figure~\ref{fig:completion_vs_size} first shows the success rate of each exchanged file over the 30 experiments.
+The dotted black line shows the overall success rate: 94.4\%. 
+Each bar shows the individual success rate of our test files, with their size on the x-axis.
+As one can see, the success rate drops as files get bigger.
+Files bigger than 112MB show a success rate between 80 and 90\%, while all lighter files are successfully transfered in 90\% of the cases at least.
 
-\begin{figure}[t]
-  \centering
-  %\def\svgwidth{0.8\columnwidth}
-  \includegraphics[width=0.8\columnwidth]{figures/logistic_many_0-001.pdf}
+% \begin{figure}[t]
+%   \centering
+%   %\def\svgwidth{0.8\columnwidth}
+%   \includegraphics[width=0.8\columnwidth]{figures/logistic_many_0-001.pdf}
 
-  \caption{\label{fig:logistic}
-  Logistic regression of the success rate as a function of the file size using the default parameters.}
-\end{figure}
+%   \caption{\label{fig:logistic}
+%   Logistic regression of the success rate as a function of the file size using the default parameters.}
+% \end{figure}
 
-Figure~\ref{fig:logistic} shows the logistic regression of the success rate as a function of the files' size. 
-This regression is good candidate to describe binary stochastic processes as a function of a dependent variable,
-and is often used in epidemics prediction, economics, and even marketing.
-Simply put, given $X$ (in our case, the size of each transfered file) and $y$ (the outcome of the transfer: success or failure), 
-the regressor estimates the coefficient $k$ and the mid-point $x_0$ of the logistic function defined as follows:
+% Figure~\ref{fig:logistic} shows the logistic regression of the success rate as a function of the files' size. 
+% This regression is good candidate to describe binary stochastic processes as a function of a dependent variable,
+% and is often used in epidemics prediction, economics, and even marketing.
+% Simply put, given $X$ (in our case, the size of each transfered file) and $y$ (the outcome of the transfer: success or failure), 
+% the regressor estimates the coefficient $k$ and the mid-point $x_0$ of the logistic function defined as follows:
 
-$$ f(x) = \frac{1}{1 + e^{-k \cdot x + x_0 }} $$
+% $$ f(x) = \frac{1}{1 + e^{-k \cdot x + x_0 }} $$
 
-Because it sets the top (100\%) and bottom (0\%) values as asymptotes, 
-logistic regression does not yield very optimistic success rates at the beginning,
-but its midpoint $x_0$ tends to be very accurate even with a low quantity of training samples.
-\commentAL{Yes indeed, very pessimistic, where is our 94\%!? I want to make a CDF also.}
+% Because it sets the top (100\%) and bottom (0\%) values as asymptotes, 
+% logistic regression does not yield very optimistic success rates at the beginning,
+% but its midpoint $x_0$ tends to be very accurate even with a low quantity of training samples.
+% \commentAL{Yes indeed, very pessimistic, where is our 94\%!? I want to make a CDF also.}
 
-In our case, $f(x)$ reads the probability that a file exchange fails given its size. 
-The plot reads that files below 319MB have more than 90\% chances of being successfully exchanged.
-The probability falls as the file gets bigger, such that a 1,O43MB has 50\% chances of successful transfer (see $x_0$).
+% In our case, $f(x)$ reads the probability that a file exchange fails given its size. 
+% The plot reads that files below 319MB have more than 90\% chances of being successfully exchanged.
+% The probability falls as the file gets bigger, such that a 1,O43MB has 50\% chances of successful transfer (see $x_0$).
 
-\begin{figure}[t]
-  \centering
-  %\def\svgwidth{0.8\columnwidth}
-  \includegraphics[width=\columnwidth]{figures/bw_and_pending_files.pdf}
-
-  \caption{\label{fig:bw_and_pending_files}Traffic during one experiment.
-  In gray: number of pending file exchanges; in black: mean outbound traffic (kB) per node per second.}
-\end{figure}
+% ------------------
 

### 2018-08-08 paper/related.tex

@@
 
-Cloud services for availability of files on multiple devices and sharing with others, such as Dropbox, Box, or iCloud, require trust in the service provider, at minimum to keep the service running without changes to the terms of service that would make them unacceptable.
-Alternatively, users could set up their own cloud using a dedicated server or edge device such as a home gateway.
-This would require equipment that users are less likely to already have than laptops or smartphones.
+Cloud services that replicate files across multiple devices and help share them with other users (e.g.
+\emph{Dropbox}, \emph{Box}, or \emph{iCloud}) require trust in the service provider, at a minimum to keep the service running without changes to the terms of service that would make them unacceptable.
+Alternatively, some solutions (such as the \emph{NextCloud} stack, or the \emph{FreedomBox} distribution) allows users to set up their own domestic cloud using a dedicated server or edge device such as a home gateway.
+These approaches however require equipment that users are less likely to possess already compared to laptops or smartphones.
 
-There have been several fully implemented attempts at P2P storage, mostly for backup, such as Wuala\footnote{http://www.wuala.com} (later changed to client-server architecture, now closed down), Farsite~\cite{farsite} (no longer in use), Nebulostore~\cite{nebulo} (maintained but not deployed).
-They deliberately use storage and replication on other peers, something we aim to avoid, even though the privacy risk is reduced compared to a central provider.
+There have been several fully implemented attempts at P2P storage, mostly for backup, such as \emph{Wuala}\footnote{http://www.wuala.com} (later changed to a client-server architecture, now closed down), \emph{Farsite}~\cite{farsite} (no longer in use), \emph{Nebulostore}~\cite{nebulo} (maintained but not deployed).
+They deliberately use storage and replication on other peers.
+Even though the privacy risks of these solutions is reduced compared to central providers, we avoid any form of replication in \ac{SPORES} voluntarily, both to limit unneeded storage overheads, and to increase privacy guarantees.
 
 P2P file sharing has been researched extensively, with respect to aspects such as architecture (starting with the semi-centralized Napster, then decentralized Gnutella), availability and replication~\cite{replica}, scalability (Bittorrent~\cite{bittorrent-incentives}), anonymity (Freenet~\cite{Clarke:2001}, Tor~\cite{Tor}), and distributed hash tables (DHT) such as CAN, Chord, Pastry, and Tapestry (see \cite{dhtchurn} for an overview).
-In contrast to our work, the main goal was to enable dissemination to many users who do not necessarily know each other in person.
-Here, we focus on sharing files in a more deliberate yet ad-hoc manner, \ie between users that out-of-band agree to share a file but do not keep it available for anyone else in the future.
+In contrast to our work, these efforts principally aimed at enabling dissemination to many users who do not necessarily know each other in person.
+With \ac{SPORES}, we focus on sharing files in a more deliberate yet ad-hoc manner, \ie between pairs of users that out-of-band agree to share a file but do not keep it available for anyone else in the future.
 
@@
 
-Onion routing schemes, with infrastructure and governance (Tor~\cite{Tor}) and without (I2P~\footnote{https://geti2p.net/en/}), though geared toward web browsing, come closest to file transfer without third-party storage.
-They do not, however, allow for unreliable user devices as relay nodes.
+Onion routing schemes, with infrastructure and governance (Tor~\cite{Tor}) and without (I2P\footnote{https://geti2p.net/en/}), though geared toward web browsing, come closest to file transfer without third-party storage.
+They do not, however, allow for unreliable user devices as relay nodes, as we do.
 
-The main concern, shared with traditional P2P file sharing, is churn~\cite{dhtchurn} and its effect on availability. % - here in the narrow context of the set of user devices based on user behavior. 
-The commonly used approach of replication and redundancy used to handling churn does not work in our case as we prioritize privacy and independence from third-party storage.
+The main concern arising from unreliable nodes, which is shared with traditional P2P file sharing, is \emph{churn}~\cite{dhtchurn} and its effect on availability.
+% - here in the narrow context of the set of user devices based on user behavior.
+Most P2P approaches have addressed churn in the past by combining in various ways \emph{data replication} (e.g.
+by storing the same file chunk on multiple nodes) and \emph{routing redundancy} (e.g.
+by maintaining multiple independent paths to the same node).
+Data replication does not work in our case as we prioritize privacy and independence from third-party storage.
+The probabilistic onion routing we propose can be interpreted as a form of routing redundancy, albeit one that is built from the ground up to ensure strong privacy guaranties.
+
+% The commonly used approach of replication and redundancy used to handling churn does not work in our case as we prioritize privacy and independence from third-party storage.
 

### 2018-08-08 paper/spor.tex

--- 2018-08-07 paper/spor.tex
@@
 
-\commentAL{When is CreateHeader used?}
-
-There are many uses of Sphinxes, many criteria that can be used to select the 
+There are many uses of \Sphinxes, many criteria that can be used to select the 
 nodes in each layer.
@@
 churn, but one could equally well select nodes to maximize, \eg, bandwidth.
-We now describe a protocol, \ac{SPOR}, which uses Sphinxes to transfer messages 
+We now describe a protocol, \ac{SPOR}, which uses \Sphinxes to transfer messages 
 from a source to a destination over a network of nodes with high churn.

### 2018-08-08 paper/sphinxes.tex
small edits

@@
 
-\subsection{\Sphinxes: the Sphinx header format Extended for Sets of nodes}%
+\section{\Sphinxes: the Sphinx header format Extended for Sets of nodes}%
 \label{Sphinxes}
@@
 For a more detailed understanding of Sphinx, we refer the reader to the 
-excellent description in the original Sphinx paper~\cite{Sphinx}.
+description in the original Sphinx paper~\cite{Sphinx}.
 
@@
 If the \ac{MAC} computed correctly, compute \(t\gets \hash_\tau(s_i)\).
-If \(t\) is already in the table of seen packets, drop the packet.
+If \(t\) is already in the table of seen (mix, not IP) packets, drop the packet.
 Otherwise, add \(t\) to the table and decrypt \(\beta\):

### 2018-08-08 paper/approach.tex
up

@@
 They characterize anonymous communication protocols using the following 
-categories: (i) \textit{network structure}, (ii) \textit{routing information},
-(iii) \textit{communication model} and (iv) \textit{performance} (see~\cite[Table 1]{RoutingSurveyAnonymousProtocols}).
+categories: (i) \textit{network structure}%~\ding{168}
+, (ii) \textit{routing information}%~\ding{169}
+, (iii) \textit{communication model}%~\ding{170}
+, and (iv) \textit{performance}%~\ding{171}
+~(see~\cite[Table 1]{RoutingSurveyAnonymousProtocols}).
 

### 2018-08-08 paper/squad-overlay-design.tex
up

@@
 resulting in $\nchunks = \lceil \filesize / \chunksize \rceil$ chunks.
-A SHA1 hash \hashchunk is computed for each chunk, plus another SHA1 hash \hashfile of the chunks hashes; that will serve error detection.
+A SHA1 hash \hashchunk is computed for each chunk, plus another SHA1 hash \hashfile of the chunks hashes; that will serve as an error detection scheme.
 
-In BitTorrent, .torrent files are publicly available on the Web.
+In BitTorrent, \textit{.torrent} files are publicly available on the Web.
 They contain $\finfo = \left(\filesize, \nchunks, \left[\hashchunk\right]_{\chunk \in f}, \hashfile\right)$, 
 along with network information to reach uploaders of $f$ (e.g. the tracker's address).
-Anyone can download a .torrent and start receiving the file associated to it.
+Anyone can download a \textit{.torrent} and start receiving the file associated to it.
 
@@
 
-\commentAL{This is a shitty scheduler. Should I mention it? Rephrase? You have a citation to propose instead?}
-Messages in \name might arrive in a wrong order or fail:
+%\commentAL{This is a shitty scheduler. Should I mention it? Rephrase? You have a citation to propose instead?}
+
+Naturally, in \name, messages might arrive in a wrong order or fail, e.g.
 it is not unlikely that the file exchange stops before its transfer is done.
-As a solution, if the transfer hangs, \sendingdevice will restart periodically sending chunks that were not acknowledged by Bob.
-This solution ensures liveness over network efficiency (some chunks might be received several times), as will be seen in the evaluation.
-It nevertheless allows reliable file transfer among a network of poorly connected nodes in a private manner.
+Consequently, as a solution, if the transfer hangs, \sendingdevice will restart periodically sending chunks that were not acknowledged by Bob.
+Hence, \name ensures liveness over network efficiency (some chunks might be received several times), as it will be seen in the evaluation.
+Nevertheless, it allows reliable file transfer among a network of poorly connected nodes in a private manner.

### 2018-08-08 paper/squad-overlay-design.tex
commented out former VD (node selection) due to redundancy and outdated content

@@
 %\subsection{Probabilistic Onion Routes}
-\subsection{Selection of nodes for routes creation}
-\label{ssec:por}
+% \subsection{Selection of nodes for routes creation}
+% \label{ssec:por}
 
-%\subsubsection{The global overlay}
-\subsubsection{\GetRandomNode}
-\label{sssec:global_overlay}
+% %\subsubsection{The global overlay}
+% \subsubsection{\GetRandomNode}
+% \label{sssec:global_overlay}
 
-Devices need to know the address of SPORES participants in order to craft PORs.
-To this end, we employ a Random Peer Sampling service~\cite{Jelasity_Voulgaris_Guerraoui_Kermarrec_van_Steen_2007,Jesi_Montresor_van_Steen_2010} (RPS) among all nodes in SPORES.
-It is a gossip protocol that allows each participant to keep a fixed-size \emph{random} subset of other nodes' descriptor (that we will call the RPS's \emph{view} \rpsview). 
-The view is constantly evolving, as queries are periodically issued between nodes to exchange descriptors between their respective views.
-Finally, offline nodes are quickly evicted from devices' views.
+% Devices need to know the address of SPORES participants in order to craft PORs.
+% To this end, we employ a Random Peer Sampling service~\cite{Jelasity_Voulgaris_Guerraoui_Kermarrec_van_Steen_2007,Jesi_Montresor_van_Steen_2010} (RPS) among all nodes in SPORES.
+% It is a gossip protocol that allows each participant to keep a fixed-size \emph{random} subset of other nodes' descriptor (that we will call the RPS's \emph{view} \rpsview). 
+% The view is constantly evolving, as queries are periodically issued between nodes to exchange descriptors between their respective views.
+% Finally, offline nodes are quickly evicted from devices' views.
 
-The randomness of the views must be guaranteed: 
-a node that would be present in views too often would become a bottleneck, and could monitor a bigger portion of the network.
-It will be evaluated in section~\commentAL{TODO}.
+% The randomness of the views must be guaranteed: 
+% a node that would be present in views too often would become a bottleneck, and could monitor a bigger portion of the network.
+% It will be evaluated in section~\commentAL{TODO}.
 
-In SPORES, a descriptor $\desc_d$ describing device $d$ contains the following information:
-\begin{itemize}
-  \item \(d\) is the node's identifier (address);
-  \item \(\pk_d\) is the node's public key;
-  \item \(\Pon_d\) is the node's probability of remaining online at the time of the descriptor's creation.
-\end{itemize}
+% In SPORES, a descriptor $\desc_d$ describing device $d$ contains the following information:
+% \begin{itemize}
+%   \item \(d\) is the node's identifier (address);
+%   \item \(\pk_d\) is the node's public key;
+%   \item \(\Pon_d\) is the node's probability of remaining online at the time of the descriptor's creation.
+% \end{itemize}
 
-$(d, \pk_d, \Pon_d)= \leftarrow \GetRandomNode$ is the function that takes a node from the RPS's view \rpsview on demand.
+% $(d, \pk_d, \Pon_d)= \leftarrow \GetRandomNode$ is the function that takes a node from the RPS's view \rpsview on demand.
 
-%\subsubsection{Routes creation}
-\subsubsection{\CreateLayer}
-\label{sssec:routes_creation}
+% %\subsubsection{Routes creation}
+% \subsubsection{\CreateLayer}
+% \label{sssec:routes_creation}
 
-Routes are created via \Sphinxes as described in section~\ref{sec:SPOR}.
-But each layer \layer constituting the route is created by the $\CreateLayer$ function, that is independent from \Sphinxes.
+% Routes are created via \Sphinxes as described in section~\ref{sec:SPOR}.
+% But each layer \layer constituting the route is created by the $\CreateLayer$ function, that is independent from \Sphinxes.
 
-In \name, we wish to maximize the availability of the route.
-Therefore, each layer \layer is created so as to reach the availability threshold $\theta$, a parameter chosen by the user.
-Note that \Sphinxes is agnostic to this use-case: one could want to maximize other characteristics, e.g. the layer's expected bandwidth.
+% In \name, we wish to maximize the availability of the route.
+% Therefore, each layer \layer is created so as to reach the availability threshold $\theta$, a parameter chosen by the user.
+% Note that \Sphinxes is agnostic to this use-case: one could want to maximize other characteristics, e.g. the layer's expected bandwidth.
 
-$\CreateLayer$ iteratively calls $\GetRandomNode\xspace$ to add random nodes to the current layer \layer, until the layer's probability of being offline, $\Poff^\layer$, falls below the availability threshold $\theta$:
+% $\CreateLayer$ iteratively calls $\GetRandomNode\xspace$ to add random nodes to the current layer \layer, until the layer's probability of being offline, $\Poff^\layer$, falls below the availability threshold $\theta$:
 
-$$ \Poff^\layer = \sum\limits_{d \in \layer}(1 - \desc_d.\Pon_d) $$
+% $$ \Poff^\layer = \sum\limits_{d \in \layer}(1 - \desc_d.\Pon_d) $$
 
-When a device creates a layer to reach its user, descriptors are not taken from \rpsview but from the \squad's sequence: all devices in this layer will belong to the user.
-The logic is otherwise the same.
+% When a device creates a layer to reach its user, descriptors are not taken from \rpsview but from the \squad's sequence: all devices in this layer will belong to the user.
+% The logic is otherwise the same.
 
-Recall that each layer in \Sphinxes has a constant number of nodes $w_\layer$, that is a \Sphinxes parameter.
-If $w_\layer$ is reached before $\Poff^\layer < \theta$, then we early abort $\CreateLayer$.
-On the other hand, if $|\layer| < w_\layer$, we pad the layer with blank descriptors, such that the header always weighs the same size.
+% Recall that each layer in \Sphinxes has a constant number of nodes $w_\layer$, that is a \Sphinxes parameter.
+% If $w_\layer$ is reached before $\Poff^\layer < \theta$, then we early abort $\CreateLayer$.
+% On the other hand, if $|\layer| < w_\layer$, we pad the layer with blank descriptors, such that the header always weighs the same size.
 

### 2018-08-08 paper/conclusion.tex

@@
 We presented \name that, in analogy to its biological
-counterparts, enables dissemination under unfavorable conditions. More
-specifially, the deliberate dissemination of files without using
+counterparts, enables the dissemination of critical data under unfavorable conditions. More
+specifially, \name allows the private dissemination of files between users without relying on
 storage on third-party devices, be they peers or servers in the
-cloud. This constraint results in the unfavorable conditions of
-reduced a-priori availability and therefore unreliable nodes for
-routing. We build resilience to these conditions by using predictive
-modeling for user behavior and the ensuing availability of their
-devices. From our experiments, we find that even suboptimal prediction
-already results in successful file transfer with high probability,
-though often at low speed. More in-depth knowledge of the users'
+cloud.
+This design choice brings unfavorable conditions that our protocol must withstand, in particular the need to route over unreliable and only partially available nodes.
+We overcome this challenge by combining a set-based onion-routing strategy, with {a probabilistic node selection protocol, informed by the on-line prediction of device availability.
+The result is a \emph{predictive and probabilistic onion routing protocol} (\ac{SPOR}), on which we based our private file transfer protocol (\ac{SPORES}).
+Our experiments show that even a suboptimal prediction
+already results in a high success rate of file transfer,
+though often at low speed.
+
+We conjecture that a more in-depth understanding of users'
 behavior would allow us to predict device connectivity farther into
-the future and thus likely improve the throughput. From a security and
+the future, and is thus likely to improve the throughput and reliability of our service. From a security and
 privacy perspective, we were guided by the properties for secure onion
@@
 collaboration or other kind of hidden services might benefit from a stateful, circuit-based approach
-like with traditional onion routing. Prediction of device availability
-could support different goals, for example time of day for delayed
-file transfer for resource optimization.
+such as found in traditional onion routing.
+We could also use our knowledge of future device availability to support a wider range of objectives beyond throughput and rate of success, for instance by delaying
+file transfers to optimize resource usage.
+
+Finally our solution assumes a secure Random Peer Sampling service (RPS), i.e.
+a uniformly random sampling service whose sampling properties are immune to interference by malicious nodes.
+These are strong requirements, that are not easily met in practice.
+Some promising candidates for this service exist however~\cite{Octopus,BrahmsRPS}.
+Further strengthening these solutions seem particularly worthwhile and interesting.
 

### 2018-08-08 paper/evaluation.tex
more eval

@@
 
-Finally, the experiments had a timeout of 15 minutes. 
+Finally, the experiments had a timeout \texp of 15 minutes. 
 We observed that downloads---however big---usually succeeded long before this time, or did not succeed whatever time was given to them.
@@
 \label{ssub:experimental_process}
+
+The experiments are conducted as follows: 
+\begin{itemize}
+  \item A first initialization procedure takes care of bootstrapping the users and their devices. 
+  A scheduler is started for each user, that will turn devices on or off throughout the experiment according to the models discussed in~\ref{ssub:simulating_user_behavior};
+  \item Each file is initiated in turn: a couple $(d_s, d_r)$ of online devices from different users is chosen.
+  The sender $d_s$ is requested to initialize file upload---chunks hashes and routes take some time to compute---and answers with \finfo, including reply headers. 
+  \finfo is given to $d_r$ as it is asked to receive $f$. It replies with forward headers, that are given to $d_s$. The exchange starts;
+  \item We wait for this initialization process to end before starting to send the next file;
+  \item Once all 12 files are initiated; we wait for the \texp timeout, unless all files have successfully completed their transfer, 
+  in which case we early abort. This process takes up to a minute.
+\end{itemize}
 
@@
 
-The experiments were conducted as follows: 
-\begin{itemize}
-  \item A first initialization procedure takes care of bootstrapping the users and their devices. 
-  A scheduler is started for each user, that will turn devices on or off throughout the experiment according to the models discussed in~\ref{ssub:simulating_user_behavior};
-  \item The 12 file exchanges are initiated in turn: a couple $(d_s, d_r)$ of online devices from different users is chosen.
-  The sender $d_s$ is requested to initialize file upload
-\end{itemize}
+Figure~\ref{fig:bw_and_pending_files} reads the timeline of a typical experiment by showing, 
+in gray, the number of simultaneous file exchanges and, in black, the average outbound traffic per node per second.
+The initialization phase is not part of the graph. 
+In this particular experiment, all files were successfully exchanged.
+
+We see that file transfers get started in turn, but that some complete fast, such that the maximum number of simultaneous downloads only rises to 8.
+It quickly drops to 4 at 160s, but the last files take another 300s to finish. 
+Those last files are either the biggest ones, or are exchanged between poorly connected nodes that tend not to be online at the same time.
+
+The dark plot shows that the traffic is uneven, with frequent spikes in the MB/s order. 
+The traffic is obviously dependent on the number of pending exchanges, 
+but remains around 600 kB/s on average, even when 8 files are concurrently downloading.
+Knowing that a chunk message weighs 516 kB, we deduce that nodes exchange an average of one chunk per second when the traffic is substantial.
+We also see that the traffic remains non-null long after the last file finished downloading it. 
+Indeed, some stale messages can remain in the buffers of poorly connected devices for an unbounded period of time.
+This experiment finished early aborting past 600s.
 
@@
   %\def\svgwidth{0.8\columnwidth}
-  \includegraphics[width=0.8\columnwidth]{figures/completion_vs_size.pdf}
+  \includegraphics[width=0.9\columnwidth]{figures/completion_vs_size.pdf}
 
   \caption{\label{fig:completion_vs_size}
-  Success rate of the file transfer ordered by size of file.}
+  Success rate of the file transfer ordered by size of file over 30 experiments.
+  The dotted black line shows the overall success rate of 94.4\%.}
 \end{figure}

### 2018-08-08 paper/squad-overlay-design.tex
more eval

--- 2018-08-07 paper/squad-overlay-design.tex
@@
 When Alice wishes to send a file $f$ to Bob, she computes \finfo, 
-plus one reply header per chunk (as was seen in section~\ref{sec:SPOR}), and sends the whole to Bob.
+including one reply header per chunk (as was seen in section~\ref{sec:SPOR}), and sends the whole to Bob.
 Still out-of-band, Bob replies with one forward header per chunk.

### 2018-08-08 paper/security-discussion.tex

--- 2018-08-07 paper/security-discussion.tex
@@
   \cref{system-model}; and that
-\item the composed protocol (\ac{SPORES}, \cref{SPORES}) provides the desired 
+\item the composed protocol (\ac{SPORES}, \cref{ssec:spores_file_exchange_through_probabilistic_onion_routes}) provides the desired 
   security properties defined in \cref{system-model}, \ie

### 2018-08-08 paper/intro.tex
working through intro

@@
 These devices form a \textit{personal squad} of connected entities (or \emph{\squad} as we shall call them in the remainder of the
-paper), that users rely on for their everyday interactions with the material and digital world, and with their fellow humans.
+paper), that users rely on for their everyday interactions with their fellow humans, as well as with the material and digital worlds.
 The growing importance of these \squad{}s is profoundly modifying how we live~\cite{Dearman:2008, Oh:2017, Sohn:2008,Harper08}, and has opened new areas of research such as \textit{proxemics}, the study of proximity-based interactions in a world of ubiquitous computing
@@
 of personal sharing platforms such as Dropbox, Google Docs,
-OneDrive, Amazon Drive, etc. These solutions allow users to share data between any device, with anyone, almost
-anytime, anywhere. They achieve this feat by relying heavily on
+OneDrive, Amazon Drive, etc. These solutions allow users to share data with anyone, anywhere, at almost
+anytime, between any devices. They achieve this feat by relying heavily on
 \emph{remote cloud services}, which have now become a key enabler of ubiquitous ecosystems. 
@@
 confidentiality guarantees they can expect. In practice, user data hosted in the cloud is routinely harvested, often without explicit
-consent, either by cloud providers or third parties, only partially
+consent, either by cloud providers or third parties, a sad situation that is only partially
 mitigated by legal measures such as the GDPR.
@@
 In this model, user devices, masquerading as allies, get turned into %% tracking and/or monitoring \squad{}s, and serve as
-highly efficient instruments spying on their owners.
+highly efficient monitoring tools spying on their owners.
 
@@
 churn typically experienced by P2P networks, the performance of these systems has been
-discouraging~\cite{LeBlond:2013}; churn causes routes to disappear and be
+discouraging~\cite{LeBlond:2013}, as churn causes routes to disappear and be
 reconstructed frequently, which is particularly costly. By contrast, Tor

### 2018-08-08 paper/security-discussion.tex
Edits security discussion

--- 2018-08-08 paper/security-discussion.tex
@@
 If we assume that \(\GetRandomNode\) returns nodes with close to the uniform 
-distribution, then the \(\nu w_L\) nodes selected will contain \(f_A \nu w_L\) 
-nodes controlled by Eve.
-If \(f_A \nu w_L < \nu\), then Eve cannot be present on every layer of the 
-route.
+distribution, then the \(\nu w_L\) nodes selected is expected to contain \(f_A 
+  \nu w_L\) nodes controlled by Eve.
+If \(f_A \nu w_L < \nu\), then Eve is not expected to be present on every layer 
+of the route.
 Considering how \ac{SPOR} distributed the \(\nu w_L\) selected nodes, Eve's 
@@
 \(\avail_{D_E}(t) = 1\) for all Eve's devices \(D_E\).
-This way, Eve's devices will be distributed evenly across all layers.
+This way, Eve's devices will be distributed evenly across all layers (provided 
+she controls enough of the selected devices).
 To succeed, Eve must be chosen in the first layer, the probability of which 
-will be \(\frac{f_A}{w_L}\).
+will be \(\frac{f_A}{w_L}\) (for a passive adversary and \(1\) for an active).
 If one of her devices is chosen in the first layer, then she can choose one of 
 her own devices in the next layer.
-Since she is present on every layer, she can ensure she relays the message all 
-the way to Bob. \sonja{compare the chance of being present on every
+If she is present on every layer, she can ensure she relays the message all the 
+way to Bob.
+In summary, her probability of success is \(\frac{1}{w_L} (1-(1-f_A)^{(w_L-1) 
+    \nu +1})\) (or without the \(\frac{1}{w_L}\) factor for an active 
+adversary), which can be compared to \((f_A)^\nu\) for classical \ac{OR} (for 
+both active and passive adversaries).
+\sonja{compare the chance of being present on every
   layer AND chosen in the first layer to regular onion routing where she
@@
   better/worse/the same?}
+\commentDaniel{Hard to say at this time of night \dots}
 
@@
   she learn/guess?}
+\commentDaniel{For all she knows there might be another node at either the 
+  beginning or the end, she cannot tell.}
 
@@
 
-Although the requirements on \ac{RPS} of being uniformly randomly
+Although the requirements of the \ac{RPS} being uniformly randomly
 distributed and privacy-preserving are not easily met in practice,
-there are some promising candidates~\cite{Octopus, BrahmsRPS}.\name
-does not put any other constraints on the \ac{RPS} used.
+there are some promising candidates~\cite[\eg][]{Octopus,BrahmsRPS}.
+\name does not put any other constraints on the \ac{RPS} used.
 
@@
 With an inaccurate availability function, \(\avail\), this will not be a 
-problem as there will be many (as the system scales) that shares the same 
-availability distribution.
+problem as there will be many others (as the system scales) that shares the 
+same availability distribution.
 With more accurate availability estimates we would have to employ techniques 
-like \ac{DP}.
+like \ac{DP} to ensure that Alice's availability distribution is not too 
+unique.
 
@@
 chunks received on different devices of a user's \squad. From Sphinx,
-we inherit IDs for mix packets that we we include in the out-of-band
-metadata on the file to be exchanged, as an ordered list, that is used
-to re-order chunks if need be. The \squad overlay handles inter-squad
-device coordination. Liveness despite the possibility of \squad devices
-going offline during transfer or other node or link failures is
-ensured by acknowledgments and timeouts as detailed in 
-\cref{sec:squad_overlay}.
+we inherit unique IDs for each mix packet.
+If we provide the mix packets as an ordered list when we communicate them 
+out-of-band together with the metadata of the file and they are used in that 
+same order, then we can use those IDs to re-order chunks if need be.
+The \squad overlay handles inter-squad \commentDaniel{intra?} device 
+coordination.
+We ensure liveness by acknowledgments and timeouts (as detailed in 
+\cref{sec:squad_overlay}), despite the possibility of \squad devices
+going offline during transfer or other node or link failures.
 
@@
 the system~\cite{DenialOfSecurity}.  As mentioned in
-\cref{system-model}, we share the adversary model with Tor and Sphinx
+\cref{system-model}, we share the adversary model with Tor
+%and Sphinx
 and thus exclude a global passive adversary. Our focus is on
@@
 adversary. We hypothesize that our stateless and redundant design
-might yield some advantages over traditional onion routing. For
+might yield some advantages over classical \ac{OR}. For
 example, no control messages are sent back to the source if the
@@
   only postpone the success of the attack, eventually even our
-  protocol must resend.'' why?}  \commentDaniel{We should look into
+  protocol must resend.'' why?}  \commentDaniel{Due to statistics. We should 
+  also look into
   this denial of security.} Another example is that the source-bounded
-random walk and new routes for file chunks make tracking more
+random-walk and new routes for file chunks make tracking more
 difficult than with regular onion routing circuits. A drawback, however, is
@@
 
-We would also like to point out that
+We would also like to point out that the
 vulnerability to a global passive attacker is not inherent in Sphinx
@@
 issue, batched and well-timed message or file transfer by all nodes
-would render traffic analysis pointless. Concretely, \Ac{SPORES} inherits the security properties from \Sphinxes and \ac{SPOR}.
+would render traffic analysis less efficient. Concretely, \Ac{SPORES} inherits 
+the security properties from \Sphinxes and \ac{SPOR}.
 However, both \Sphinxes and \ac{SPOR} can be used with any mixing strategy, and 

### 2018-08-08 paper/abstract.tex

@@
 %problem/topic
-This paper proposes a novel private file transfer service that avoids any third-party storage or centralized bootstrapping service.
+This paper proposes SP$^2$ORES, a novel private file transfer service that avoids any third-party storage or centralized bootstrapping service.
 %research gap
 Our solution, which adopts a fully decentralized design, overcomes the limitations of cloud file-sharing systems such as Dropbox, which require trust in the service provider and can be monitored, even when their data is encrypted.
-Our proposal also goes beyond existing private peer-to-peer (P2P) solutions that must rely storage replication for efficiency or a fixed set of trusted servers for bootstrapping purposes, which limits their level of protection.
+Our proposal also goes beyond existing private peer-to-peer (P2P) solutions that must rely on storage replication for efficiency or a fixed set of trusted servers for bootstrapping purposes, thus limiting their level of protection.
 % We are interested in minimizing the trust needed in other systems and preserving the users' privacy in terms of data and metadata, what they share with whom and when.
@@
 % that is  both efficient and strongly private is possible.
-\commentFT{Trying to highlight POR, as likely to catch people's attention, and contribute to the paper's long-term interest.} At the core of our proposal lies a novel stateless probabilistic onion routing protocol called SPOR, which exploits decentralized peer sampling, and a probabilistic model of node availability.
+\commentFT{Trying to highlight POR, as likely to catch people's attention, and contribute to the paper's long-term interest.} At the core of our proposal lies a novel stateless probabilistic onion routing protocol called SP$^2$OR, which exploits decentralized peer sampling, a probabilistic model of node availability, and a novel set-based onion routing header format (dubbed SphinxES).
 \commentFT{Sharing node availability information freely could potentially disclose private information.
@@
 neither of which is currently the case in Tor.
-\sonja{say something about security requirements? About sphinxes?}
+\sonja{say something about security requirements? About sphinxes?} \commentFT{Added a mention to SphinxES, not sure if we can discuss security requirements without making the abstract overly long.}

### 2018-08-08 paper/squad-overlay-design.tex

--- 2018-08-08 paper/squad-overlay-design.tex
@@
 The predictive nature of \name lies in the fact that each participating device publicly advertises its probability of being connected in the near future. 
-This information is used when any node needs to create a Stateless Predictive Probabilistic Onion Route (\SPOR), as will be shown in the next subsection~\ref{ssec:por}.
+This information is used when any node needs to create a Stateless Predictive Probabilistic Onion Route (\acs{SPOR}).%, as will be shown in the next subsection~\ref{ssec:por}.
 

### 2018-08-08 paper/spor.tex
introduced theta

@@
   \item \(\pk_d\) is the node's public key;
-  \item \(\avail_d(t)\) is the node's probability of being online as a function 
-    of time.
+  \item \(\avail_d\) is the node's probability of being online in the near future. It computation will be discussed in~\ref{ssec:device_availability}.
 \end{itemize}
@@
 being unavailable.
+
+For the evaluaion of the impact of devices' availability prediction, we introduce a parameter, coined the \emph{availability threshold} $\theta$. 
+\CreateLayer iteratively adds nodes to a layer \layer until its probability of being entirely offline $\Poff^\layer$ falls below $\theta$ or $w_\layer$ is reached:
+
+$$ \Poff^\layer = \sum\limits_{d \in \layer}(1 - \desc_d.\Pon_d) $$
+
+When $|\layer| < w_\layer$, the layer is filled with empty descriptors so as to fill the target number of nodes per layer.
+
+Using $\theta$, \name becomes more conservative than \SPOR, and we can investigate the best number of nodes per layer in regard of its probability of being available.

### 2018-08-08 paper/intro.tex
pass on intro

@@
 availability of user devices, and use this ability to implement a
-\emph{probabilistic predictive onion routing} mechanism. The
-predictive nature of our routing, exploited in a stateless way, allows
-us to overcome the inherent fragility of pure P2P file transfer schemes.
+\emph{probabilistic predictive onion routing} protocol.
+Our protocol exploits a new mix-header format that uses onion layers made of sets of nodes rather single nodes.
+The use of multiple nodes in individual layers, together with our estimation of future device availability, exploited in a stateless way, allows
+us to overcome the inherent fragility of pure P2P file transfer schemes while providing strong privacy properties.
 
@@
 
-  \item We provide the Sphinxes mix-header format which extends 
-    Sphinx~\cite{Sphinx} to a source-routed limited random-walk protocol --- 
-    \ie each layer of the onion route contains several alternative next nodes.
+  \item We propose \Sphinxes, an extension of the
+    Sphinx~\cite{Sphinx} mix-header format to set-based onion routing.
+\Sphinxes allows each layer of an onion route to contain several alternative next nodes, thus realizing a source-routed limited random-walk protocol.
 
-  \item We provide the \ac{SPOR} node selection strategy for routing which, given a secure 
+  \item Building on \Sphinxes, we introduce the \ac{SPOR} %% node selection strategy for routing
+    protocol
+    that, given a secure 
     \ac{RPS} protocol and availability estimates, selects nodes to populate the 
-    layers of Sphinxes to maximize the availability of the route --- this 
-    yields reliable routes even with low-availability nodes.
+    layers of \Sphinxes in order to maximize the availability of the route. This node selection procedure 
+    yields reliable routes even in the presence of low-availability nodes while retaining the strong privacy properties of onion routing.
 
-  \item We provide a protocol for a device squad to estimate the availabilities 
+  \item We provide a protocol for a device \squad to estimate the availabilities 
     of its own devices, based on Markov models and \squad overlays.
-    These availabilities can then be used with \ac{SPOR}.
+    These estimated availabilities can then be exploited by \ac{SPOR} to populate \Sphinxes.
    % \commentDaniel{We should add some more details, maybe.}
 
-  \item We use \ac{SPOR} to design \name \sonja{removed for
+  \item We use \ac{SPOR} to realize \name, \sonja{removed for
       redundancy, rephrased: a novel, fully decentralized, 
-    autonomous and self-organizing} as a privacy-preserving file transfer service among
-  users without third-party storage.
+    autonomous and self-organizing} a privacy-preserving file transfer service among
+  users that eschews any third-party storage or centralized bootstrapping service.
 
@@
 
-In the following, in Section~\ref{system-model}, we state the
+The remainder of this paper is organized as follows. Section~\ref{system-model} presents the
 system and adversary models as well as the desired security and privacy properties of \name. Section~\ref{design}

### 2018-08-08 paper/spor.tex
explained why only scalar prediction

@@
   \item \(\pk_d\) is the node's public key;
-  \item \(\avail_d\) is the node's probability of being online in the near future. It computation will be discussed in~\ref{ssec:device_availability}.
+  \item  \(\avail_d(t)\) is the node's probability of being online as a function of time. 
+  Its computation will be discussed in~\ref{ssec:device_availability}.
 \end{itemize}

### 2018-08-08 paper/squad-overlay-design.tex
explained why only scalar prediction

--- 2018-08-08 paper/squad-overlay-design.tex
@@
 The predictive nature of \name lies in the fact that each participating device publicly advertises its probability of being connected in the near future. 
-This information is used when any node needs to create a Stateless Predictive Probabilistic Onion Route (\SPOR), as will be shown in the next subsection~\ref{ssec:por}.
+This information is used when any node needs to create a Stateless Predictive Probabilistic Onion Route (\acs{SPOR}), as was shown in section~\ref{SPOR}.
+
+In the following, we refer to the node's probability of a node $d$ being online as the scalar $\Pon_d$, because $\forall t, \Pon_d(t) = \Pon_d$.
+The estimate that is made accounts for the next state of the user's behavior in discrete time, and thus approximates the availability of $d$ in the near future.
+The prediction eventually becomes stale, but we count on the fact that stale descriptors are removed fast in most RPS solutions: 
+as a device calls \GetRandomNode, it only gets fresh descriptors.
 

### 2018-08-08 paper/squad-overlay-design.tex
changed X_i to S_i in predictions

@@
 To predict a device's future availability, we build a Markov representation of the user's activity, 
-where the state $X_i$ represents the availability of the user's devices at time $t_i$.
-The state space $\mathcal{X}$ is the set of possible combinations of the devices' connection.
+where the state $S_i$ represents the availability of the user's devices at time $t_i$.
+The state space $\mathcal{S}$ is the set of possible combinations of the devices' connection.
 
-Given the \squad sequence of connections $S = X_1, \dots, X_i, X_{i+1}, \dots$,
-we can compute the probability of transition from a state $X_i=x$ to $X_{i+1}=x'$ by counting\footnote{%
+Given the \squad sequence of connections $S = S_1, \dots, S_i, S_{i+1}, \dots$,
+we can compute the probability of transition from a state $S_i=x$ to $S_{i+1}=x'$ by counting\footnote{%
 	Because we work with low-probability events observed with a small amount of data, there is a possibility that an event never occurs in $S$. 
@@
 \begin{align*}
-P\left[X_{i+1}=x' \mid X_i=x \right] &= P\left[x \rightarrow x' \right] \\&= \frac{\left| \left\{ X_i = x, X_{i+1} = x' \right\}_{i \in \left[0, |S| - 1\right]} \right|}{\left| \left\{ X_i = x \right\}_{i \in \left[0, |S| - 1\right]} \right|}
+P\left[S_{i+1}=x' \mid S_i=x \right] &= P\left[x \rightarrow x' \right] \\&= \frac{\left| \left\{ S_i = x, S_{i+1} = x' \right\}_{i \in \left[0, |S| - 1\right]} \right|}{\left| \left\{ S_i = x \right\}_{i \in \left[0, |S| - 1\right]} \right|}
 \end{align*}
 
-Each device knows the current state $X_i=x$ of the Markov chain.
+Each device knows the current state $S_i=x$ of the Markov chain.
 To predict its probability $P_d$ of remaining online in the next round, 
 a device $d$ simply adds the probabilities that the user switches to a state where $d$ is online next.
-Consider $\mathcal{X}_{d\text{ online}} \subset \mathcal{X}$ the set of states where $d$ is online. Then:
+Consider $\mathcal{S}_{d\text{ online}} \subset \mathcal{S}$ the set of states where $d$ is online. Then:
 
 \begin{align*}
-P_d & = P\left[d\text{ online at }X_{i+1} \mid X_i=x\right] \\ & = \sum\limits_{x' \in \mathcal{X}_{d\text{ online}}} P\left[ X_{i+1}=x' \mid X_i=x \right]
+P_d & = P\left[d\text{ online at }S_{i+1} \mid S_i=x\right] \\ & = \sum\limits_{x' \in \mathcal{S}_{d\text{ online}}} P\left[ S_{i+1}=x' \mid S_i=x \right]
 \end{align*}
@@
 There is a caveat, though.
-While the user acts, $S$ keeps growing, and the Markov chain must be recomputed: there is a probability that the current state $X=x$ has never been seen before.
-In this case, $\forall x' \in \mathcal{X}, P\left[x \rightarrow x'\right]$ is undefined.
+While the user acts, $S$ keeps growing, and the Markov chain must be recomputed: there is a probability that the current state $S_i=x$ has never been seen before.
+In this case, $\forall x' \in \mathcal{S}, P\left[x \rightarrow x'\right]$ is undefined.
 
@@
 
-$$ P'_d = \frac{\left| \left\{ X_i \in \mathcal{X}_{d\text{ online}}, X_{i+1} \in \mathcal{X}_{d\text{ online}} \right\}_{i \in \left[0, |S| - 1\right]} \right|}{\left| \left\{ X_i \in \mathcal{X}_{d\text{ online}} \right\}_{i \in \left[0, |S| - 1\right]} \right|} $$
+$$ P'_d = \frac{\left| \left\{ S_i \in \mathcal{S}_{d\text{ online}}, S_{i+1} \in \mathcal{S}_{d\text{ online}} \right\}_{i \in \left[0, |S| - 1\right]} \right|}{\left| \left\{ S_i \in \mathcal{S}_{d\text{ online}} \right\}_{i \in \left[0, |S| - 1\right]} \right|} $$
 

### 2018-08-08 paper/spor.tex
small error

@@
 
-Using $\theta$, \name becomes more conservative than \SPOR, and we can investigate the best number of nodes per layer in regard of its probability of being available.
+Using $\theta$, \name becomes more conservative than \ac{SPOR}, and we can investigate the best number of nodes per layer in regard of its probability of being available.

### 2018-08-08 paper/evaluation.tex
introduced theta
churnful Tor

@@
 
+\subsubsection{Comparison to churnful Tor} % (fold)
+\label{ssub:comparison_to_churnful_tor}
+
+To demonstrate the need for \iac{SPOR}, 
+we attempt the same experiment as before, but this time using an availability threshold $\theta = 1$ (cf~\ref{SPOR}): 
+layers only contain one random descriptor.
+Over 5 experiments, we observed a file transfer success rate of 41.7\%, which is far below our results when leveraging on \ac{SPOR}.
+
+% subsubsection comparison_to_churnful_tor (end)
+
 % \begin{figure}[t]

### 2018-08-08 paper/system-model.tex
pass on Sec 2

@@
 %% is a distributed system made of
-users' devices.  We assume any two devices can communicate with one
-another as soon as one knows the address of the other (\eg using the
+users' devices.  We assume any pair of devices can communicate with each other as soon as one knows the address of the other (\eg using the
 Internet, possibly extended with NAT traversal techniques). The
 devices owned by the same user (this user's \squad) know of each
-other. Other users' devices can help transfer the file from one user
-to another but are not needed for storage.  We also assume that users
+other. We leverage the the devices of other users to help transfer the file from one user
+to another, but do not use them for storage.  We also assume that users
 can exchange some limited amounts of data out-of-band, \ie through
@@
 transfer service, before mapping them into our fully decentralized
-(a.k.a. peer-to-peer (P2P\footnote{We use the terms \emph{fully decentralized} and
-  \emph{P2P} interchangeably, and preferentially the latter for brevity.}))
+(a.k.a. peer-to-peer, or P2P short short\footnote{We use the terms \emph{fully decentralized} and
+  \emph{P2P} interchangeably, and preferentially the latter for brevity.})
 context.  We finally consider the additional privacy properties
@@
 about Alice sharing a file with Bob.
-\item The composition and behavior of Alice and Bob's \squad remain
+\item The composition and behavior of Alice and Bob's \squad{}s remain
   hidden to each other, and to other users. I.e. Alice does not learn
@@
 place. In \name, we additionally derive the property of
-\emph{device-unlinkability} from the \ac{P2P} requirements above, meaning that
-using \name does not reveal the \squad a device belongs to nor its
+\emph{device-unlinkability} from the \ac{P2P} requirements introduced above, meaning that
+using \name neither reveals the \squad a device belongs to, nor its
 owner. Thus, no information on the user's behavior (e.g. being online)

### 2018-08-08 paper/evaluation.tex
up

--- 2018-08-08 paper/evaluation.tex
@@
 To evaluate \name, we take interest in users owning a variable amount of devices of different types, and frequently switching among them.
-To the best of our knowledge, there exists no real-world dataset of the devices connection times of such a user.
+To the best of our knowledge, there does not exist real-world dataset of the devices connection times of such a user.
 On our testbed, each user's behavior is therefore simulated, according to the following rules:
@@
 
-\paragraph*{Sprinkler} The \squad overlay has two parameters: the fanout of the gossip exchange when a device has new information to share, set to 3, and the initial length of the sequence $S$ (cf.
+\paragraph*{Overlay} The \squad overlay has two parameters: the fanout of the gossip exchange when a device has new information to share, set to 3, and the initial length of the sequence $S$ (cf.
 section~\ref{ssec:device_availability}), set to 50.
@@
 Files bigger than 112MB show a success rate between 80 and 90\%, while all lighter files are successfully transfered in 90\% of the cases at least.
+
+\subsubsection{Comparison to churnful Tor} % (fold)
+\label{ssub:comparison_to_churnful_tor}
+
+To demonstrate the need for
+
+% subsubsection comparison_to_churnful_tor (end)
 

### 2018-08-08 paper/evaluation.tex
up

@@
 
-In the following, we first give precisions on the evaluation testbed and parameters in section~\ref{sub:evaluation_testbed}, before evaluating the PORs creation in section~\ref{sub:predictive_onion_routes_creation}, to conclude with an overall evaluation of the file transfer performance in section~\ref{sub:file_transfer}.
+In the following, we first give precisions on the evaluation testbed and parameters in section~\ref{sub:evaluation_testbed}, before evaluating the file transfer performance in section~\ref{sub:file_transfer}.
 

### 2018-08-08 paper/evaluation.tex
avail experiment

--- 2018-08-08 paper/evaluation.tex
@@
 
-\paragraph*{PORs} We used a constant amount of 3 layers per routes (excluding the final, destination layer),
+\paragraph*{\ac{SPOR}} We used a constant amount of 3 layers per routes (excluding the final, destination layer),
 and a constant number of peers per layer $w_\layer$ of 16.
@@
 % subsubsection comparison_to_churnful_tor (end)
+
+\subsubsection{Traffic and availability} % (fold)
+\label{ssub:traffic_and_availability}
+
+\begin{figure}[t]
+  \centering
+  %\def\svgwidth{0.8\columnwidth}
+  \includegraphics[width=0.9\columnwidth]{figures/avail.pdf}
+
+  \caption{\label{fig:completion_vs_size}
+  Availability of devices and number of messages waiting for reception.}
+\end{figure}
+
+% subsubsection traffic_and_availability (end)
 

### 2018-08-08 paper/approach.tex
Changes use-once reply-block to single-use reply-block

--- 2018-08-08 paper/approach.tex
@@
 More precisely, they exchange metadata on \(f\), encryption keys, and
-some use-once reply mix-headers.
+some single-use reply mix-headers.
 They use these reply headers to transfer the file contents of \(f\) over a 
@@
   done in a stateless way. \\
-\textbf{Predictive.} The choice of nodes included in the onion routing
-  layers is based on a predictive model for availability, disseminated
-  by an overlay and queried by random peer sampling.\\
+ \textbf{Predictive.} The choice of which nodes is placed in which onion routing
+  layer is informed on a predictive model for availability, disseminated
+  by an overlay and queried by random peer sampling (RPS).
+Note that availability predictions only influence how nodes returned by the random peer sampling service are distributed among layers, but have no impact on the overall population of nodes making up the onion route.
+This population is controlled by the random peer sampling service, which we assume is secure.
+This is important to ensure strong privacy protection, and we return to this point in the Security Discussion of Section~\ref{security-discussion}.\\
  \textbf{Probabilistic.} Instead of source routes with one node per onion layer, each
@@
   have received a packet directly from the sender or some other
-  intermediate node. We base our format for layering and peeling on
-  Sphinx~\cite{Sphinx}, with some modification to allow for the
+  intermediate node. We base our format for layering and peeling on the
+  Sphinx~\cite{Sphinx} mix-header format, which we extend to allow for the
   changes above, described in \cref{Sphinxes}.
@@
 They characterize anonymous communication protocols using the following 
-categories: (i) \textit{network structure}, (ii) \textit{routing information},
-(iii) \textit{communication model} and (iv) \textit{performance} (see~\cite[Table 1]{RoutingSurveyAnonymousProtocols}).
+categories: (i) \textit{network structure}%~\ding{168}
+, (ii) \textit{routing information}%~\ding{169}
+, (iii) \textit{communication model}%~\ding{170}
+, and (iv) \textit{performance}%~\ding{171}
+~(see~\cite[Table~1]{RoutingSurveyAnonymousProtocols}).
 
@@
 As depicted in Figure~\ref{fig:outline}, \ac{SPORES} relies on a predictive and probabilistic onion routing protocol (\ac{SPOR}).
-\ac{SPOR} in turn combines a multi-set mix-header format (\Sphinxes) together with a node selection protocol that exploit decentralized prediction regarding node availability to optimize the reliability of \Sphinxes without jeopardizing its security properties.
-Particularly, \sphinxes (\cref{Sphinxes}), is an adaptation of the 
-\sonja{do we apply all categories here?} Sphinx~\cite{Sphinx} mix-header format.
-This means that we inherit some properties from Sphinx and due to being only a 
-header format, it only imposes some restrictions in the above categories.
+\ac{SPOR} in turn combines a multi-set mix-header format (\Sphinxes) together with a node selection protocol that exploits decentralized prediction regarding node availability to optimize the reliability of \Sphinxes without jeopardizing its security properties.
+%% Particularly, \sphinxes (\cref{Sphinxes}), is an adaptation of the 
+%% \sonja{do we apply all categories here?} Sphinx~\cite{Sphinx} mix-header format.
+%% This means that we inherit some properties from Sphinx and due to being only a 
+%% header format, it only imposes some restrictions in the above categories.
 \Sphinxes (Figure~\ref{fig:outline} \ding{202}) provides, just as Sphinx, unidirectional (network structure), 

### 2018-08-08 paper/evaluation.tex

--- 2018-08-08 paper/evaluation.tex
@@
 
-To demonstrate the need for
+To demonstrate the need for \iac{SPOR}, 
+we attempt the same experiment as before, but this time using an availability threshold $\theta = 1$ (cf~\ref{SPOR}): 
+layers only contain one random descriptor.
+Over 5 experiments, we observed a file transfer success rate of 41.7\%, which is far below our results when leveraging on \ac{SPOR}.
 
 % subsubsection comparison_to_churnful_tor (end)
+
+\subsubsection{Traffic and availability} % (fold)
+\label{ssub:traffic_and_availability}
+
+\begin{figure}[t]
+  \centering
+  %\def\svgwidth{0.8\columnwidth}
+  \includegraphics[width=0.9\columnwidth]{figures/avail.pdf}
+
+  \caption{\label{fig:completion_vs_size}
+  Availability of devices and number of messages waiting for reception.}
+\end{figure}
+
+% subsubsection traffic_and_availability (end)
 

### 2018-08-08 paper/evaluation.tex
rephrased churnful Tor, edit, added result

@@
 
-\subsubsection{Comparison to churnful Tor} % (fold)
-\label{ssub:comparison_to_churnful_tor}
+% \subsubsection{Comparison to churnful Tor} % (fold)
+% \label{ssub:comparison_to_churnful_tor}
 
-To demonstrate the need for \iac{SPOR}, 
+To get a rough baseline to evaluate the need for \iac{SPOR}, 
 we attempt the same experiment as before, but this time using an availability threshold $\theta = 1$ (cf~\ref{SPOR}): 
-layers only contain one random descriptor.
+layers only contain one random descriptor, as a naive approximation of
+classical \OR. 
 Over 5 experiments, we observed a file transfer success rate of 41.7\%, which is far below our results when leveraging on \ac{SPOR}.

### 2018-08-08 paper/evaluation.tex
last expe

--- 2018-08-08 paper/evaluation.tex
@@
 
-\subsubsection{Traffic and availability} % (fold)
+\subsubsection{Availability of nodes and messages in transit} % (fold)
 \label{ssub:traffic_and_availability}
@@
 
-  \caption{\label{fig:completion_vs_size}
+  \caption{\label{fig:avail}
   Availability of devices and number of messages waiting for reception.}
 \end{figure}
+
+To assess the performance of \name, another important metric is the rate of online nodes at a time.
+Figure~\ref{fig:avail} shows just that (in gray), along with the number of messages that are in transit at a time (in black). 
+It takes its data from the same experiment as figure~\ref{fig:bw_and_pending_files}.
+The black dotted line is the average number of online nodes throughout the experiment: 15.8\% (it was computed up to the ~500th second where the nodes are killed).
+
+We see that the number of online devices lies around its mean the whole experiment.
+The message curve roughly follows the previous figure~\ref{fig:bw_and_pending_files}'s number of pending file exchanges. 
+Some spikes are created when two devices are online and exchange many chunks in a small amount of time. 
+The spike is shut down when these messages are received by the downloader, or when it suddenly falls offline.
+The curve never goes down below 1000 messages in transit before the end of the experiment: these account for messages in offline devices that took very long to reach their end.
+
+Indeed, it is interesting to look at the transmission times of the messages: their mean time in transit is of 22s in this experiment, which is incredibly long.
+Looking at the standard deviation, that is of 48s, we understand that the dispersion of the transit time is very high, and that the mean is skewed by 
+extremely slow messages (with a maximum transit time of 9m13s).
+In last resort, we compute the median of the messages transfer time: 639ms; it means that half messages spend less that this time in the system.
+
+An obvious direction for future work is to implement at Time To Leave (TTL) or other stale-messages-removal policy.
+
+\\
+To conclude this section, we have seen that \name could empower users to privately exchange files over a challenging network where only 15.8\% of the infrastructure was available at a time.
+Our proposal, \name, allows to nevertheless complete the file exchange with an average probability of 94.4\%, against 41.7\% success rate using classical onion routes
 

### 2018-08-08 paper/evaluation.tex

@@
 
-\subsubsection{Comparison to churnful Tor} % (fold)
-\label{ssub:comparison_to_churnful_tor}
+% \subsubsection{Comparison to churnful Tor} % (fold)
+% \label{ssub:comparison_to_churnful_tor}
 
-To demonstrate the need for \iac{SPOR}, 
+To get a rough baseline to evaluate the need for \iac{SPOR}, 
 we attempt the same experiment as before, but this time using an availability threshold $\theta = 1$ (cf~\ref{SPOR}): 
-layers only contain one random descriptor.
+layers only contain one random descriptor, as a naive approximation of
+classical \acl{OR}. 
 Over 5 experiments, we observed a file transfer success rate of 41.7\%, which is far below our results when leveraging on \ac{SPOR}.

### 2018-08-08 paper/evaluation.tex
ended eval

@@
 In the following, we first give precisions on the evaluation testbed and parameters in section~\ref{sub:evaluation_testbed}, before evaluating the file transfer performance in section~\ref{sub:file_transfer}.
+Finally, we look at the devices availability over time, and at the messages life over the network in \ref{ssub:traffic_and_availability}.
 
@@
 
-\subsubsection{Availability of nodes and messages in transit} % (fold)
+\subsection{Availability of nodes and messages in transit} % (fold)
 \label{ssub:traffic_and_availability}
@@
   \caption{\label{fig:avail}
-  Availability of devices and number of messages waiting for reception.}
+  Availability of devices (in gray) and number of messages waiting for reception (in black) over an experiment. The black dotted line represents the mean rate of online devices: 15.8\%.}
 \end{figure}
@@
 An obvious direction for future work is to implement at Time To Leave (TTL) or other stale-messages-removal policy.
+\\
 
-\\
-To conclude this section, we have seen that \name could empower users to privately exchange files over a challenging network where only 15.8\% of the infrastructure was available at a time.
-Our proposal, \name, allows to nevertheless complete the file exchange with an average probability of 94.4\%, against 41.7\% success rate using classical onion routes
+We have seen that \name could empower users to privately exchange files in a distributed manner over a challenging network where only 15.8\% of the infrastructure is available at a time.
+Our proposal allows to nevertheless complete the file exchange with an average probability of 94.4\%, against 41.7\% success rate using classical onion routes.
 

### 2018-08-08 paper/evaluation.tex

--- 2018-08-08 paper/evaluation.tex
@@
 
-\subsubsection{Availability of nodes and messages in transit} % (fold)
+%\subsubsection{Traffic and availability} % (fold)
 \label{ssub:traffic_and_availability}
@@
 
-  \caption{\label{fig:avail}
+  \caption{\label{fig:completion_vs_size}
   Availability of devices and number of messages waiting for reception.}
 \end{figure}
-
-To assess the performance of \name, another important metric is the rate of online nodes at a time.
-Figure~\ref{fig:avail} shows just that (in gray), along with the number of messages that are in transit at a time (in black). 
-It takes its data from the same experiment as figure~\ref{fig:bw_and_pending_files}.
-The black dotted line is the average number of online nodes throughout the experiment: 15.8\% (it was computed up to the ~500th second where the nodes are killed).
-
-We see that the number of online devices lies around its mean the whole experiment.
-The message curve roughly follows the previous figure~\ref{fig:bw_and_pending_files}'s number of pending file exchanges. 
-Some spikes are created when two devices are online and exchange many chunks in a small amount of time. 
-The spike is shut down when these messages are received by the downloader, or when it suddenly falls offline.
-The curve never goes down below 1000 messages in transit before the end of the experiment: these account for messages in offline devices that took very long to reach their end.
-
-Indeed, it is interesting to look at the transmission times of the messages: their mean time in transit is of 22s in this experiment, which is incredibly long.
-Looking at the standard deviation, that is of 48s, we understand that the dispersion of the transit time is very high, and that the mean is skewed by 
-extremely slow messages (with a maximum transit time of 9m13s).
-In last resort, we compute the median of the messages transfer time: 639ms; it means that half messages spend less that this time in the system.
-
-An obvious direction for future work is to implement at Time To Leave (TTL) or other stale-messages-removal policy.
-
-\\
-To conclude this section, we have seen that \name could empower users to privately exchange files over a challenging network where only 15.8\% of the infrastructure was available at a time.
-Our proposal, \name, allows to nevertheless complete the file exchange with an average probability of 94.4\%, against 41.7\% success rate using classical onion routes
 

### 2018-08-08 paper/approach.tex

@@
 
-Further, \ac{SPOR} protocol (\cref{design}) adds node selection on top of \Sphinxes.
+Further, the \ac{SPOR} protocol (\cref{design}) adds node selection on top of \Sphinxes.
 The \ac{SPOR} protocol (Figure~\ref{fig:outline} \ding{203})  assumes a source of random nodes, \eg through 
@@
 layers.
-As \ac{SPOR} assumes this source of random nodes, the network view (routing 
+\commentFT{What follows seems quite convoluted, with a lot of repetition. Would be nice to revise.} As \ac{SPOR} assumes this source of random nodes, the network view (routing 
 information) of each node depends on this source of random nodes, as does the 

### 2018-08-08 paper/intro.tex

@@
 The remainder of this paper is organized as follows. Section~\ref{system-model} presents the
-system and adversary models as well as the desired security and privacy properties of \name. Section~\ref{design}
-introduces the design of our proposed solution. In
-Sections~\ref{security-discussion} and \ref{Performance},
+system and adversary models as well as the desired security and
+privacy properties of \name. Section~\ref{approach} describes the
+overall approach. In Section~\ref{Sphinxes}, we introduce \sphinxes. 
+Then, in Section~\ref{design}, we introduce the different building
+blocks of \name. In sections~\ref{security-discussion} and \ref{Performance},
 respectively, we evaluate the security and performance of our
 approach. We set \name into context with related work in
-Section~\ref{RelatedWork} and conclude with Section~\ref{conclusion}.
+Section~\ref{RelatedWork}, and finally conclude with Section~\ref{conclusion}.
 

### 2018-08-08 paper/old_squad-overlay-design.tex

%!TEX root = p2p-private-cloud.tex

\subsection{Predicting device availability}
\label{sec:squad_overlay}

A device's availability depends on its user.
To predict a device's availability, we must predict its user's behaviour.
A device, belonging to an \squad, can only predict its probability to stay 
online in the near future if it has global knowledge of the user behaviour over 
the other devices of the user's \squad.
We will now describe a protocol which is run by the devices in the squad which 
allows each device to compute the availability prediction function, \(\avail\).

\commentDaniel{I leave it to Adrien to write this up.
  The old stuff is commented out below.}

\endinput

%By sharing information among themselves, a user's devices (her \emph{squad}) can model her behavior.

%In this section, we only take interest in one user (called Alice) and her \squad.

% Each of Alice's (and Bob's) devices will keep track of its own online and 
% offline behavior.
% They will use a protocol like Sprinkler~\cite{luxey:hal-01704172} to learn about 
% each other's online--offline behavior.
% \commentDaniel{Is that correct?}
% This allows Alice's device swarm to infer a behavioral model for the device 
% swarm and do internal scheduling based on the probability of being online.

\subsubsection{Sharing the user's behavior} % (fold)
\label{sub:sharing_knowledge}

%Online devices want to know whether they are likely to stay online in the near future.
taken separately, each device can only get local observations, such as when its user used it, and mobility information if it is a handheld device.
If all these local observations can be combined, a device can infer a refined model of the user’s behavior to predict its future activity in an accurate manner. To build such a sequence of observations, 
%a sequence of the user's behavior that is far more complete.
%For instance, the probability that Alice uses her home computer and workstation simultaneously is null: these devices are too far apart.
the \squad overlay leverages on a probabilistic dissemination protocol, \textsc{Sprinkler}~\cite{luxey:hal-01704172}.
it allows one's devices to inform one another every time the user performs an action.
In our previous work~\cite{luxey:cascade}, we showed that \textsc{Sprinkler} is resilient to devices churn: 
devices let each other know of what they have missed while offline.
We thus employ \textsc{Sprinkler} to disseminate the user's activity to its \squad.

% Each device initially only knows when it is connected, which is not sufficient to make reliable predictions on whether it is likely to stay online.
% If they knew the other devices' connection and disconnection times, they 
% To make a model of the user's behavior, they need to know the whole observation sequence $O$: which device is online at each time step.
% To do so, they employ a probabilistic dissemination protocol, 
% \textsc{Sprinkler}~\cite{luxey:hal-01704172}.
% This allows devices to gossip any new connection information to random peers in 
% the local swarm, ensuring that all devices know the full observation sequence 
% with a very high probability.
% \textsc{Sprinkler} has shown resilient to device churn~\cite{luxey:cascade}, and 
% is thus perfectly suited for our purpose, where a user's devices often 
% disconnect and reconnect.

% subsection sharing_knowledge (end)

% \subsubsection{Other uses of the Squad Overlay} % (fold)
% \label{ssub:other_uses_of_the_squad_overlay}

\paragraph*{Other uses of the \squad Overlay} In addition to user's behavior, devices use the \squad overlay for several purposes. Firstly, they share files location: when Alice wants to share a file $f$ that resides on her home computer, using her smartphone as the exchange initiator, her smartphone knows where $f$ is located and can create the route accordingly. 
Secondly, each device is also informed of its user's ongoing file transfers (which serves the next purpose).
Finally, because devices can receive messages on behalf of their fellow squad members to ensure reception despite the proper recipient being offline, 
one's devices can forward messages among the \squad.

% \david{the following paragraph is not clear at all }
% \name knows two message types (as will be covered in~\ref{sec:file_transfer}): file chunk, and acknowledgment.
% Alice typically wants to receive a file on one particular device; respectively, only one of her devices is interested in acknowledging reception of the file chunks it is sending. \david{what is the relationship with \squad Overlay?}
% However, \name allows all \squad members to receive messages destined to Alice.
% Thus, the third complementary purpose of the \Squad Overlay is to relay messages among the squad: when a message is not destined to the device that received it, the receiver forwards the message to its final destination.
% \david{and then?}

\subsubsection{Modeling the user's behavior}
\label{sub:a_model_of_the_user_s_behavior}

we need a probabilistic model of the user's behavior to predict its future activity.
In \name, the only data we collect and share, through the \squad overlay, are the availability times of each device among a \squad.
In our model, time is discretized, i.e. users periodically change the state availability of their devices in a predefined period.
We store the availability times in an ever-increasing \emph{sequence} $O=O_1, ..., O_i, ...$ of actions performed at every \emph{round}, that lasts a short period of time $T$. 
$d \in O_t$ thus means that the device $d$ was online from time $t$ to time $t+T$.
Our goal is to predict $O_{t+1}$ knowing $O_t$.

To this end, we model the user's behavior as a Hidden Markov Models (HMMs) of order one, with multiple discrete \emph{observable} processes (one per device) stored in $O$. 
The hidden process $S=S_1, ..., S_i, ...$ represents the user's locations, constituted of a set of $N$ potential locations (e.g. home, work or outside), $N$ being a user-defined parameter.
A HMM of order one is such that the hidden variable at time $t$, $S_t$, only depends on the hidden variable at $t-1$, $S_{t-1}$.
The observations at time $t$, $O_t$, depend on the current hidden variable only, $S_t$.

We first formally define our HMM, then show how to predict the future knowing the HMM, then finally present how to infer the model from the observable sequence only.

% In \name, we take interest in users that own several devices, and wish to privately exchange files with each other without revealing .
% To the best of our knowledge, no real-world traces of multi-devices usage over several days exist, as would be needed for the experimental evaluation of our system.
% For that reason, we propose a user behavioral model having the following features:

% \begin{itemize}
% 	\item Each user owns a variable amount of devices. We consider the following device types: mobile, portable, fixed, and server;
% 	\item The user travels between three ``locations'' according to a simple probabilistic model: her home, her workplace, and outside;
% 	\item She makes a different use of her devices depending on her location: at home, she will her laptop that at work; she cannot use her workstation at home.
% \end{itemize}

% To this end, we use a Hidden Markov Model (HMM) of order one, with multiple discrete observation processes. 
% The hidden Markovian process $S$ represents the user's locations, while the \emph{observable} process $O=O_1, \dots, \O_T$ represents the connection state of her devices (either connected or disconnected at any point in time).

% Such a statistical model is simplistic (e.g. it does not encapsulate date \& time nor location), but it is on purpose: simplicity is bliss.
% Given the lack of real-world data for our testbed, building a more complex and realistic user model would add no value to our proposal: 
% our goal is to see devices exhibiting frequent disconnections and reconnections (also called \emph{churn}).
% Our simple model being able to put extravagant stress on our system, it is sufficient to access \name's resilience.

\paragraph*{Formal definition}

%We consider a single user, owning a set of $\mathcal{D}$ devices.
%Time is discretized \commentAL{Discretized/synchronous time needs more explanation}. Needs, and the devices' observations are independent: Alice can have her laptop and phone connected at the same time.
The hidden process $S=S_1,\dots,S_i, \dots$ is built from an alphabet of states $\mathcal{S}$, while the observable process $O=O_1, \dots, \O_i, \dots$ contains elements from the alphabet $\mathcal{O}$. We define a multivariate HMM $\lambda_N$ as follows:

$$\text{HMM}:\;\lambda_N=(\Pi, A, B)$$

where 
\begin{itemize}
	\item $N$ is the number of states in the system:
	$N = \left| \mathcal{S} \right|$;

	\item $\Pi=\left\{ \pi_i\right\}_{i\in\mathcal{S}}$ is the initial state distribution:\\
	$\pi_i=P[S_1=i]$;

	\item $A = \left\{ a_{i\,j}\right\}_{(i,j)\in\mathcal{S}^2}$ is the state transition matrix:\\
	$a_{i\,j}=P[S_t=j \mid S_{t-1}=i]$;

	\item $B = \left\{ b_{i\,k}\right\}_{(i,k)\in\mathcal{S}\times\mathcal{D}}$ is the matrix of event emission probabilities for each state:
	$b_{i\,k} = P[ k \in O_t \mid S_t = i]$.
\end{itemize}

In our case, the states $\mathcal{S}$ are the different locations $\mathcal{L}$ where the user is susceptible to go.
The events represent the devices availability, hence $\mathcal{O} = \mathcal{D}$, where $\mathcal{D}$ is the set of the user's devices.
Several devices can be available at the same time, such that $O_t$ is a set, and $d \in O_t$ means that device $d$ was available at time $t$. Devices' availability probabilities are independent.

% In \cref{fig:hmm}, we show an example HMM of a user's behavioral HMM, along with its graphical representation (the initial state distribution $\Pi$ was left out for simplicity). 
% The represented user possesses a phone and a laptop, that she carries around with her, a home computer, that is only accessible from her home, and a workstation, located at her workplace. She never forgets to turn off her fixed appliances before leaving.

% Figure~\ref{fig:sample_usage}, shows a possible trace of the user's behavior, using the parameters depicted in figure~\ref{fig:hmm}. 
% It reads the timeline of $o_{d}$ for each device $d$. On the bottom of the graph, the first letter of the user's location is shown at each time step.
% We see that devices connections depend on the user's location, and that any number of devices can be connected at the same time.

\paragraph*{Predicting future behavior} 
\label{para:predicting future behavior}
As already stated, devices want to predict whether they are likely to be available in the near future.
This information will be publicly available to enable the intelligent building of routes.

Because devices availability only depend on the users location, we can predict the devices availability in $i$ round $O_{t+i}$ given only the model $\lambda_N$ and the current user's location $S_t$. We first compute the probability that a device $d$ will be available next turn:

$$
P\left[ d \in O_{t} \mid S_{t-1} = s \right] = 
\sum\limits_{s' \in \mathcal{S}} 
a_{s\,s'} * b_{s'\,d}.
$$

It is the sum of the probabilities, for each state $s$, that the user switches to $s$ and uses her device.
Recursively, predicting $i$ turns in advance follows the same logic:

\begin{multline*}
P\left[ d \in O_{t+i} \mid S_{t} = s \right] = \\
\sum\limits_{s' \in \mathcal{S}}
P\left[ S_{t+1} = s' \mid S_t = s \right] * 
P\left[ d \in O_{t+i} \mid S_{t+1} = s'\right].
\end{multline*}

We show in section~\ref{sub:predictive_onion_routes_creation} that the prediction of devices' availability at $t+1$ is a good enough estimator of their availability state at $t+i$.
For that reason, devices only compute and publish $P\left[ d \in O_{t+1} \mid S_{t} = s \right]$.

\paragraph*{Inferring the model from the sequence of observations}

Given an initial estimate $\lambda_{N}^{(0)}$ of the model, and the sequence of observations $O$, the Baum-Welch algorithm uses Expectation-Maximization to iteratively compute the most likely $S^{(i)}$ and $\lambda_{N}^{(i)}$ until the probability of the observations using the estimated model falls below a predefined threshold: $P[O; \lambda_{N}^{(i)}] < \epsilon$.
Devices use this algorithm to infer their user's behavioral model from the observations.

It needs an initial model, though, with a predefined number of states $N$. 
$N$ is given by the user, and we set $\lambda_{N}^{(0)}$ to be a uniform model: probabilities of switching to each location are uniform, and all devices have a probability of being online of 0.5.

Baum-Welch usually requires a lot of data to fit the model $\lambda_N$ that generated $O$.
Indeed, $P[O; \lambda_{N}^{(i)}] < \epsilon$ does not mean that $\lambda_N \simeq \lambda_N^{(i)}$.
In our case, we do not care as long as the predictions using the estimated model, $P[O_{t+1} \mid S_t; \lambda_N^{(i)}]$, are close to the ground-truth, $P[O_{t+1} \mid S_t; \lambda_N]$.
%This will be evaluated in section~\ref{sub:devices_predictions_of_the_user_behavior}.

### 2018-08-08 paper/related.tex

@@
 Data replication does not work in our case as we prioritize privacy and independence from third-party storage.
-The probabilistic onion routing we propose can be interpreted as a form of routing redundancy, albeit one that is built from the ground up to ensure strong privacy guaranties.
+The probabilistic onion routing we propose can be interpreted as a form of routing redundancy, albeit one that is built from the ground up to ensure strong privacy guarantees.
 

### 2018-08-08 paper/security-discussion.tex

@@
 With an inaccurate availability function, \(\avail\), this will not be a 
-problem as there will be many others (as the system scales) that shares the 
+problem as there will be many others (as the system scales) that share the 
 same availability distribution.
 With more accurate availability estimates we would have to employ techniques 
-like \ac{DP} to ensure that Alice's availability distribution is not too 
+like \ac{DP} to ensure that Alice's availability distribution is not
+(too close to)
 unique.
@@
 same order, then we can use those IDs to re-order chunks if need be.
-The \squad overlay handles inter-squad \commentDaniel{intra?} device 
+The \squad overlay handles intra-squad device 
 coordination.

### 2018-08-09 paper/abstract.tex
Use acro package to handle citation of Tor

@@
-% -*- tex-main-file: "contents.tex" compile-command: "pdflatex p2p-private-cloud.tex" ispell-dictionary: "american" -*-
+% -*- tex-main-file: "contents.tex" compile-command: "pdflatex spores.tex" ispell-dictionary: "american" -*-
 % What's the problem?
@@
 This design makes it possible to exploit transient nodes, without dedicated relays, %take advantage of locality, 
-neither of which is currently the case in Tor.
+neither of which is currently the case in \ac{Tor}.
 \sonja{say something about security requirements? About sphinxes?} \commentFT{Added a mention to SphinxES, not sure if we can discuss security requirements without making the abstract overly long.}

### 2018-08-09 paper/approach.tex
Use acro package to handle citation of Tor

@@
 \Sphinxes does \emph{not} introduce any restrictions on whether the network 
-topology must be fully connected or not, be asynchronous (as in Tor) or 
+topology must be fully connected or not, be asynchronous (as in \ac{Tor}) or 
 synchronous (as in mix-nets), whether node selection must be uniformly random 

### 2018-08-09 paper/intro.tex
Use acro package to handle citation of Tor

@@
-% -*- tex-main-file: "contents.tex" compile-command: "pdflatex p2p-private-cloud.tex" ispell-dictionary: "american" -*-
-%!TEX root = p2p-private-cloud.tex
+% -*- tex-main-file: "contents.tex" compile-command: "pdflatex spores.tex" ispell-dictionary: "american" -*-
+%!TEX root = spores.tex
 
@@
 discouraging~\cite{LeBlond:2013}, as churn causes routes to disappear and be
-reconstructed frequently, which is particularly costly. By contrast, Tor
-\cite{Tor}, one of the most popular anonymous networks,
+reconstructed frequently, which is particularly costly. By contrast, \ac{Tor}, 
+one of the most popular anonymous networks,
 trades lower anonymity guarantees for a much better
-performance. \sonja{lower than who?} Tor's lower protection arises from
+performance. \sonja{lower than who?} \acg{Tor} lower protection arises from
 a partially centralized design that hinges on a set of \emph{directory

### 2018-08-09 paper/security-discussion.tex
Use acro package to handle citation of Tor

@@
 the system~\cite{DenialOfSecurity}.  As mentioned in
-\cref{system-model}, we share the adversary model with Tor
+\cref{system-model}, we share the adversary model with \ac{Tor}
 %and Sphinx
@@
 messages; they immediately forward any messages.
-This puts \ac{SPORES} in the same position as Tor~\cite{Tor}, \ie more 
-vulnerable to traffic analysis than batching 
-mix-nets~\cite{RoutingSurveyAnonymousProtocols} \commentDaniel{we should 
-  probably look for the original papers} --- this vulnerability is inherited 
-from the mixing strategy.
+This puts \ac{SPORES} in the same position as \ac{Tor}, \ie more vulnerable to 
+traffic analysis than batching mix-nets~\cite{RoutingSurveyAnonymousProtocols} 
+\commentDaniel{we should probably look for the original papers} --- this 
+vulnerability is inherited from the mixing strategy.
 

### 2018-08-09 paper/simpleSPOR.tex
Use acro package to handle citation of Tor

@@
 
-Simple Tor:
+Simple \ac{Tor}:
 1) S: get I from directory
@@
 
-Note: need to figure out how Tor sends both return onion and request, then do the same here.
+Note: need to figure out how \ac{Tor} sends both return onion and request, then do the same here.
 
@@
 
-Comparison between Tor and SPOR:
-- SPOR file sharing similar to Tor hidden service
-- Tor web browsing similar to Spor
-- Tor stateful (circuits), SPOR stateless
-- SPOR layers are sets of nodes, Tor layers are single nodes.
-- SPOR allows for parallelism (bottlenecks only at S and D). Whereas Tor bottlenecks at the node in the circuit with the lowest 
+Comparison between \ac{Tor} and SPOR:
+- SPOR file sharing similar to \ac{Tor} hidden service
+- \ac{Tor} web browsing similar to Spor
+- \ac{Tor} stateful (circuits), SPOR stateless
+- SPOR layers are sets of nodes, \ac{Tor} layers are single nodes.
+- SPOR allows for parallelism (bottlenecks only at S and D). Whereas \ac{Tor} bottlenecks at the node in the circuit with the lowest 
 bandwidth.
-- Tor infrastracture, SPOR decentralized
+- \ac{Tor} infrastracture, SPOR decentralized
 - SPOR allows any node intor relay directory. Anyone can enter. Then they receive different ranks based on "good behaviour". They also monitor the nodes and kick out suspicious nodes.
@@
 - SPOR can limit location, e.g. within a country? Would help with availability and uniform distribution of chosen nodes again due to lack of a-priori differences in availability in same time zone.
-- Tor sender anonymity, SPOR file sharing sender-receiver anonymity (ID of device, not user as there's out-of-band communication), but the more fair analogy is probably with hidden services, where there should be sender-receiver anonymity also in Tor.
+- \ac{Tor} sender anonymity, SPOR file sharing sender-receiver anonymity (ID of device, not user as there's out-of-band communication), but the more fair analogy is probably with hidden services, where there should be sender-receiver anonymity also in \ac{Tor}.
 Only sender anonymity when SPOR is used for web browsing.
@@
 This is good for efficiency but opens up for attacks.
-However, the damage of this is not as bad as for mixes (or Tor), since the retransmission will *probably* not take the same route.
+However, the damage of this is not as bad as for mixes (or \ac{Tor}), since the retransmission will *probably* not take the same route.
 Adrien: We take inspiration from BitTorrent. They chunk files in fixed-size

### 2018-08-09 paper/system-model.tex
rm error
Use acro package to handle citation of Tor

@@
-% -*- tex-main-file: "contents.tex" compile-command: "pdflatex -halt-on-error p2p-private-cloud.tex > /dev/null" ispell-dictionary: "american" -*-
-%!TEX root = p2p-private-cloud.tex
+% -*- tex-main-file: "contents.tex" compile-command: "pdflatex -halt-on-error spores.tex > /dev/null" ispell-dictionary: "american" -*-
+%!TEX root = spores.tex
 
@@
 
-%adversary model: remove provider, compensate, results in same as in sphinxOR/Tor?  friends?
+%adversary model: remove provider, compensate, results in same as in sphinxOR/\ac{Tor}?  friends?
 
@@
 transfer service, before mapping them into our fully decentralized
-(a.k.a. peer-to-peer, or P2P short short\footnote{We use the terms \emph{fully decentralized} and
+(a.k.a. P2P\footnote{We use the terms \emph{fully decentralized} and
   \emph{P2P} interchangeably, and preferentially the latter for brevity.})
@@
 \paragraph*{Adversary model} To assess our approach, we use the
-adversary model assumed by Tor~\cite{Tor} and Sphinx~\cite{Sphinx}:
+adversary model assumed by \ac{Tor} and Sphinx~\cite{Sphinx}:
 the adversary has complete control over some part of the network as

### 2018-08-09 paper/approach.tex
Replaces Sphinx~\cite{Sphinx} with \ac{Sphinx}

@@
   intermediate node. We base our format for layering and peeling on the
-  Sphinx~\cite{Sphinx} mix-header format, which we extend to allow for the
+  \ac{Sphinx} mix-header format, which we extend to allow for the
   changes above, described in \cref{Sphinxes}.
@@
 %   intermediate node. We base our format for layering and peeling on
-%   Sphinx~\cite{Sphinx}, with some modification to allow for the
+%   \ac{Sphinx}, with some modification to allow for the
 %   changes above, described in \cref{Sphinxes}.
@@
 %% Particularly, \sphinxes (\cref{Sphinxes}), is an adaptation of the 
-%% \sonja{do we apply all categories here?} Sphinx~\cite{Sphinx} mix-header format.
+%% \sonja{do we apply all categories here?} \ac{Sphinx} mix-header format.
 %% This means that we inherit some properties from Sphinx and due to being only a 

### 2018-08-09 paper/sphinxes.tex
fixed sphinx public key denotation
up
s/p2p-private-cloud/spores/g to replace remaining ones
Replaces Sphinx~\cite{Sphinx} with \ac{Sphinx}

@@
-%!TEX root = p2p-private-cloud.tex
+%!TEX root = spores.tex
 
@@
 Then the triple \((\alpha_2, \beta_2, \gamma_2)\) is sent to the node with 
-address \(d_2\).
-
-When node \(n\) discovers \(d_{n+1} = *\) it knows that the message is intended 
+address \(d_2\). When node \(n\) discovers \(d_{n+1} = *\) it knows that the message is intended 
 for itself and thus stops the forwarding.
@@
 
-In Sphinx we denoted the public key for layer \(i\) as \(\pk_i\).
+In Sphinx, the public key for layer \(i\) is denoted as \(\pk_i\).
 Since we have \(m\) alternative nodes with different keys, let us denote them 
@@
 We will synchronize our detailed descriptions with that of 
-Sphinx~\cite{Sphinx}, hence we will use the following notation:
+\ac{Sphinx}, hence we will use the following notation:
 \begin{itemize}

### 2018-08-09 paper/approach.tex
Changes some Sphinx to \ac{Sphinx}

@@
 %% \sonja{do we apply all categories here?} \ac{Sphinx} mix-header format.
-%% This means that we inherit some properties from Sphinx and due to being only a 
+%% This means that we inherit some properties from \ac{Sphinx} and due to being only a 
 %% header format, it only imposes some restrictions in the above categories.
-\Sphinxes (Figure~\ref{fig:outline} \ding{202}) provides, just as Sphinx, unidirectional (network structure), 
+\Sphinxes (Figure~\ref{fig:outline} \ding{202}) provides, just as \ac{Sphinx}, unidirectional (network structure), 
 message-based (performance) communication.
-But unlike Sphinx, \Sphinxes is an hybrid source-hop-by-hop routed, and a
+But unlike \ac{Sphinx}, \Sphinxes is an hybrid source-hop-by-hop routed, and a
 source-bounded random walk (communication 
@@
 or not.
-Just as Sphinx, it can be used in many different settings.
+Just as \ac{Sphinx}, it can be used in many different settings.
 

### 2018-08-09 paper/sphinxes.tex
Changes some Sphinx to \ac{Sphinx}

@@
 128-bit security. \sonja{what about the CL properties?}
-Sphinx only provides one node per onion layer; in this section we extend Sphinx 
+Sphinx only provides one node per onion layer; in this section we extend \ac{Sphinx} 
 to \Sphinxes, which allows for multiple nodes per onion layer.
@@
 
-We will now give an overview of the Sphinx header format.
-The idea is not to give a detailed description of Sphinx, but to give the 
-reader enough understanding of Sphinx to understand the changes we make to 
+We will now give an overview of the \ac{Sphinx} header format.
+The idea is not to give a detailed description of \ac{Sphinx}, but to give the 
+reader enough understanding of \ac{Sphinx} to understand the changes we make to 
 achieve \Sphinxes.
@@
 
-The Sphinx header (for the first node) is a triple \((\alpha_1, \beta_1, 
+The \ac{Sphinx} header (for the first node) is a triple \((\alpha_1, \beta_1, 
   \gamma_1)\), where \(\alpha_1\) is \iac{DHKE} exponent (\(g^x\), where \(x\) 
@@
 
-We will now extend Sphinx to do \ac{SPOR}: instead of providing only \(d_{i+1}\) 
+We will now extend \ac{Sphinx} to do \ac{SPOR}: instead of providing only \(d_{i+1}\) 
 in \(\beta_i\), we will have a set \(\{d_{i+1}^{(1)}, \dotsc, d_{i+1}^{(m)}\}\) 
@@
 
-In Sphinx, the public key for layer \(i\) is denoted as \(\pk_i\).
+In \ac{Sphinx}, the public key for layer \(i\) is denoted as \(\pk_i\).
 Since we have \(m\) alternative nodes with different keys, let us denote them 
@@
 
-We keep the nomenclature of mix headers and messages from Sphinx for
+We keep the nomenclature of mix headers and messages from \ac{Sphinx} for
 clarity but later apply them to onions and file chunks, repectively.
@@
 This algorithm creates a header for \iac{SPOR}.
-It is identical to that of Sphinx~\cite[\S 3.2]{Sphinx} except that we use a 
+It is identical to that of \ac{Sphinx}~\cite[\S 3.2]{Sphinx} except that we use a 
 set of addresses and keys for each layer instead of only one address and key.

### 2018-08-09 paper/spores.tex

\documentclass[conference]{IEEEtran}
%\documentclass[draftcls]{IEEEtran}
\pagestyle{plain}
\usepackage{import}
\usepackage{capt-of}
\usepackage[noend]{algpseudocode}
\usepackage{pifont}
\errorcontextlines\maxdimen

% begin vertical rule patch for algorithmicx (http://tex.stackexchange.com/questions/144840/vertical-loop-block-lines-in-algorithmicx-with-noend-option)
\makeatletter
% start with some helper code
% This is the vertical rule that is inserted
    \newcommand*{\algrule}[1][\algorithmicindent]{\makebox[#1][l]{\hspace*{.5em}\thealgruleextra\vrule height \thealgruleheight depth \thealgruledepth}}%
% its height and depth need to be adjustable
\newcommand*{\thealgruleextra}{}
\newcommand*{\thealgruleheight}{.75\baselineskip}
\newcommand*{\thealgruledepth}{.25\baselineskip}

\newcount\ALG@printindent@tempcnta
\def\ALG@printindent{%
    \ifnum \theALG@nested>0% is there anything to print
        \ifx\ALG@text\ALG@x@notext% is this an end group without any text?
            % do nothing
        \else
            \unskip
            \addvspace{-1pt}% FUDGE to make the rules line up
            % draw a rule for each indent level
            \ALG@printindent@tempcnta=1
            \loop
                \algrule[\csname ALG@ind@\the\ALG@printindent@tempcnta\endcsname]%
                \advance \ALG@printindent@tempcnta 1
            \ifnum \ALG@printindent@tempcnta<\numexpr\theALG@nested+1\relax% can't do <=, so add one to RHS and use < instead
            \repeat
        \fi
    \fi
    }%
\usepackage{etoolbox}
% the following line injects our new indent handling code in place of the default spacing
\patchcmd{\ALG@doentity}{\noindent\hskip\ALG@tlm}{\ALG@printindent}{}{\errmessage{failed to patch}}
\makeatother

% the required height and depth are set by measuring the content to be shown
% this means that the content is processed twice
\newbox\statebox
\newcommand{\myState}[1]{%
    \setbox\statebox=\vbox{#1}%
    \edef\thealgruleheight{\dimexpr \the\ht\statebox+1pt\relax}%
    \edef\thealgruledepth{\dimexpr \the\dp\statebox+1pt\relax}%
    \ifdim\thealgruleheight<.75\baselineskip
        \def\thealgruleheight{\dimexpr .75\baselineskip+1pt\relax}%
    \fi
    \ifdim\thealgruledepth<.25\baselineskip
        \def\thealgruledepth{\dimexpr .25\baselineskip+1pt\relax}%
    \fi
    %\showboxdepth=100
    %\showboxbreadth=100
    %\showbox\statebox
    \State #1%
    %\State \usebox\statebox
    %\State \unvbox\statebox
    %reset in case the next command is not wrapped in \myState
    \def\thealgruleheight{\dimexpr .75\baselineskip+1pt\relax}%
    \def\thealgruledepth{\dimexpr .25\baselineskip+1pt\relax}%
}
% end vertical rule patch for algorithmicx

\input{preamble.tex}

\begin{document}
\input{contents.tex}
\end{document}

### 2018-10-03 paper/security-discussion.tex

@@
 layer and the next \(C\) is hidden inside the header --- which otherwise 
-remains identical to that of Sphinx.
+remains identical to that of \ac{Sphinx}.
 
@@
 one.
-The proofs of Sphinx rest on the results of \textcite{CLOnionRouting}, which 
+The proofs of \ac{Sphinx} rest on the results of \textcite{CLOnionRouting}, which 
 are results for classical \ac{OR} with only one node per layer.
@@
 With these arguments, we believe that \Sphinxes inherits the \ac{UC} security 
-properties of Sphinx. %, however, this should be formally analysed.
+properties of \ac{Sphinx}. %, however, this should be formally analysed.
 
@@
 If \(\nu < r\) though, then, due to the indistinguishability and unlinkability 
-properties of Sphinxes (inherited from Sphinx), Eve cannot know for certain if 
+properties of Sphinxes (inherited from \ac{Sphinx}), Eve cannot know for certain if 
 Alice is the first node and Bob is the last node. \sonja{but what can
@@
 Stateless routing can result in re-ordered chunks or packets, and
-chunks received on different devices of a user's \squad. From Sphinx,
+chunks received on different devices of a user's \squad. From \ac{Sphinx},
 we inherit unique IDs for each mix packet.

### 2018-10-03 paper/system-model.tex

@@
 \paragraph*{Adversary model} To assess our approach, we use the
-adversary model assumed by \ac{Tor} and Sphinx~\cite{Sphinx}:
+adversary model assumed by \ac{Tor} and \ac{Sphinx}:
 the adversary has complete control over some part of the network as

### 2018-10-03 paper/related.tex

@@
 
-P2P file sharing has been researched extensively, with respect to aspects such as architecture (starting with the semi-centralized Napster, then decentralized Gnutella), availability and replication~\cite{replica}, scalability (Bittorrent~\cite{bittorrent-incentives}), anonymity (Freenet~\cite{Clarke:2001}, Tor~\cite{Tor}), and distributed hash tables (DHT) such as CAN, Chord, Pastry, and Tapestry (see \cite{dhtchurn} for an overview).
-In contrast to our work, these efforts principally aimed at enabling dissemination to many users who do not necessarily know each other in person.
-With \ac{SPORES}, we focus on sharing files in a more deliberate yet ad-hoc manner, \ie between pairs of users that out-of-band agree to share a file but do not keep it available for anyone else in the future.
+P2P file sharing has been researched extensively, with respect to aspects such 
+as architecture (starting with the semi-centralized Napster, then decentralized 
+Gnutella), availability and replication~\cite{replica}, scalability 
+(Bittorrent~\cite{bittorrent-incentives}), anonymity 
+(Freenet~\cite{Clarke:2001}, \ac{Tor}, and \acp{DHT} such as CAN, Chord, 
+Pastry, and Tapestry, see~\cite{dhtchurn} for an overview). In contrast to our 
+work, these efforts principally aimed at enabling dissemination to many users 
+who do not necessarily know each other in person. With \ac{SPORES}, we focus on 
+sharing files in a more deliberate yet ad-hoc manner, \ie between pairs of 
+users that out-of-band agree to share a file but do not keep it available for 
+anyone else in the future.
 
@@
 
-Onion routing schemes, with infrastructure and governance (Tor~\cite{Tor}) and without (I2P\footnote{https://geti2p.net/en/}), though geared toward web browsing, come closest to file transfer without third-party storage.
-They do not, however, allow for unreliable user devices as relay nodes, as we do.
+Onion routing schemes, with infrastructure and governance (\ac{Tor}) and 
+without (I2P\footnote{https://geti2p.net/en/}), though geared toward web 
+browsing, come closest to file transfer without third-party storage. They do 
+not, however, allow for unreliable user devices as relay nodes, as we do.
 

### 2019-02-01 spores-protocol-paper/sphinxes.tex
Adds copy of paper to spores-protocol-paper

--- 2018-08-09 paper/sphinxes.tex
@@
 128-bit security. \sonja{what about the CL properties?}
-Sphinx only provides one node per onion layer; in this section we extend \ac{Sphinx} 
+\Ac{Sphinx} only provides one node per onion layer; in this section we extend \ac{Sphinx} 
 to \Sphinxes, which allows for multiple nodes per onion layer.
@@
 achieve \Sphinxes.
-For a more detailed understanding of Sphinx, we refer the reader to the 
+For a more detailed understanding of \ac{Sphinx}, we refer the reader to the 
 description in the original Sphinx paper~\cite{Sphinx}.
@@
     distributed.
-    (Sphinx made a difference between nodes and destinations, \ie the set 
+    (\Ac{Sphinx} made a difference between nodes and destinations, \ie the set 
     \(\D\) such that \(\D\cap \N = \emptyset\) and \(\D\cup \N\) is prefix 
@@
 This algorithm creates a header for \iac{SPOR}.
-It is identical to that of \ac{Sphinx}~\cite[\S 3.2]{Sphinx} except that we use a 
+It is identical to that of Sphinx~\cite[\S 3.2]{Sphinx} except that we use a 
 set of addresses and keys for each layer instead of only one address and key.

### 2019-02-05 paper/squad-overlay-design.tex
Cuts out prediction etc.

--- 2018-08-08 paper/squad-overlay-design.tex
@@
-%!TEX root = p2p-private-cloud.tex
-
-\subsection{The \squad overlay}
+\subsection{Predicting device availability}
 \label{sec:squad_overlay}
 
-A user's devices communicate through an information dissemination protocol (coined \emph{e-squad overlay}) so as to learn the user's behavior.
-The goal is twofold: 
-devices need information on the user to predict their future availability, 
-and they must know which device is responsible for which file exchange to route messages to their recipient in the \squad.
+A device's availability depends on its user.
+To predict a device's availability, we must predict its user's behaviour.
+A device, belonging to an \squad, can only predict its probability to stay 
+online in the near future if it has global knowledge of the user behaviour over 
+the other devices of the user's \squad.
+We will now describe a protocol which is run by the devices in the squad which 
+allows each device to compute the availability prediction function, \(\avail\).
 
-To achieve this goal, we adapt the Sprinkler protocol, proposed by Luxey et al.~\cite{luxey:hal-01704172}, to suit our needs. 
-Using Sprinkler, participating nodes gossip in a push-pull manner: 
-when a node has new information, it sends it to a fixed-size random subset of its peers; 
-the recipients answer with any information that they believe the sender does not know about, thus reconciling their history.
+\commentDaniel{I leave it to Adrien to write this up.
+  The old stuff is commented out below.}
 
-The exchanged messages form a sequence, ordered by timestamp, populated by three message types:
+\endinput
+
+%By sharing information among themselves, a user's devices (her \emph{squad}) can model her behavior.
+
+%In this section, we only take interest in one user (called Alice) and her \squad.
+
+% Each of Alice's (and Bob's) devices will keep track of its own online and 
+% offline behavior.
+% They will use a protocol like Sprinkler~\cite{luxey:hal-01704172} to learn about 
+% each other's online--offline behavior.
+% \commentDaniel{Is that correct?}
+% This allows Alice's device swarm to infer a behavioral model for the device 
+% swarm and do internal scheduling based on the probability of being online.
+
+\subsubsection{Sharing the user's behavior} % (fold)
+\label{sub:sharing_knowledge}
+
+%Online devices want to know whether they are likely to stay online in the near future.
+taken separately, each device can only get local observations, such as when its user used it, and mobility information if it is a handheld device.
+If all these local observations can be combined, a device can infer a refined model of the user’s behavior to predict its future activity in an accurate manner.
+To build such a sequence of observations,
+%a sequence of the user's behavior that is far more complete.
+%For instance, the probability that Alice uses her home computer and workstation simultaneously is null: these devices are too far apart.
+the \squad overlay leverages on a probabilistic dissemination protocol, \textsc{Sprinkler}~\cite{luxey:hal-01704172}.
+it allows one's devices to inform one another every time the user performs an action.
+In our previous work~\cite{luxey:cascade}, we showed that \textsc{Sprinkler} is resilient to devices churn: 
+devices let each other know of what they have missed while offline.
+We thus employ \textsc{Sprinkler} to disseminate the user's activity to its \squad.
+
+% Each device initially only knows when it is connected, which is not sufficient to make reliable predictions on whether it is likely to stay online.
+% If they knew the other devices' connection and disconnection times, they 
+% To make a model of the user's behavior, they need to know the whole observation sequence $O$: which device is online at each time step.
+% To do so, they employ a probabilistic dissemination protocol, 
+% \textsc{Sprinkler}~\cite{luxey:hal-01704172}.
+% This allows devices to gossip any new connection information to random peers in 
+% the local swarm, ensuring that all devices know the full observation sequence 
+% with a very high probability.
+% \textsc{Sprinkler} has shown resilient to device churn~\cite{luxey:cascade}, and 
+% is thus perfectly suited for our purpose, where a user's devices often 
+% disconnect and reconnect.
+
+% subsection sharing_knowledge (end)
+
+% \subsubsection{Other uses of the Squad Overlay} % (fold)
+% \label{ssub:other_uses_of_the_squad_overlay}
+
+\paragraph*{Other uses of the \squad Overlay} In addition to user's behavior, devices use the \squad overlay for several purposes.
+Firstly, they share files location: when Alice wants to share a file $f$ that resides on her home computer, using her smartphone as the exchange initiator, her smartphone knows where $f$ is located and can create the route accordingly.
+Secondly, each device is also informed of its user's ongoing file transfers (which serves the next purpose).
+Finally, because devices can receive messages on behalf of their fellow squad members to ensure reception despite the proper recipient being offline, 
+one's devices can forward messages among the \squad.
+
+% \david{the following paragraph is not clear at all }
+% \name knows two message types (as will be covered in~\ref{sec:file_transfer}): file chunk, and acknowledgment.
+% Alice typically wants to receive a file on one particular device; respectively, only one of her devices is interested in acknowledging reception of the file chunks it is sending.
+\david{what is the relationship with \squad Overlay?}
+% However, \name allows all \squad members to receive messages destined to Alice.
+% Thus, the third complementary purpose of the \Squad Overlay is to relay messages among the squad: when a message is not destined to the device that received it, the receiver forwards the message to its final destination.
+% \david{and then?}
+
+\subsubsection{Modeling the user's behavior}
+\label{sub:a_model_of_the_user_s_behavior}
+
+we need a probabilistic model of the user's behavior to predict its future activity.
+In \name, the only data we collect and share, through the \squad overlay, are the availability times of each device among a \squad.
+In our model, time is discretized, i.e. users periodically change the state availability of their devices in a predefined period.
+We store the availability times in an ever-increasing \emph{sequence} $O=O_1, ..., O_i, ...$ of actions performed at every \emph{round}, that lasts a short period of time $T$. 
+$d \in O_t$ thus means that the device $d$ was online from time $t$ to time $t+T$.
+Our goal is to predict $O_{t+1}$ knowing $O_t$.
+
+To this end, we model the user's behavior as a Hidden Markov Models (HMMs) of order one, with multiple discrete \emph{observable} processes (one per device) stored in $O$. 
+The hidden process $S=S_1, ..., S_i, ...$ represents the user's locations, constituted of a set of $N$ potential locations (e.g. home, work or outside), $N$ being a user-defined parameter.
+A HMM of order one is such that the hidden variable at time $t$, $S_t$, only depends on the hidden variable at $t-1$, $S_{t-1}$.
+The observations at time $t$, $O_t$, depend on the current hidden variable only, $S_t$.
+
+We first formally define our HMM, then show how to predict the future knowing the HMM, then finally present how to infer the model from the observable sequence only.
+
+% In \name, we take interest in users that own several devices, and wish to privately exchange files with each other without revealing .
+% To the best of our knowledge, no real-world traces of multi-devices usage over several days exist, as would be needed for the experimental evaluation of our system.
+% For that reason, we propose a user behavioral model having the following features:
+
+% \begin{itemize}
+% 	\item Each user owns a variable amount of devices. We consider the following device types: mobile, portable, fixed, and server;
+% 	\item The user travels between three ``locations'' according to a simple probabilistic model: her home, her workplace, and outside;
+% 	\item She makes a different use of her devices depending on her location: at home, she will her laptop that at work; she cannot use her workstation at home.
+% \end{itemize}
+
+% To this end, we use a Hidden Markov Model (HMM) of order one, with multiple discrete observation processes. 
+% The hidden Markovian process $S$ represents the user's locations, while the \emph{observable} process $O=O_1, \dots, \O_T$ represents the connection state of her devices (either connected or disconnected at any point in time).
+
+% Such a statistical model is simplistic (e.g. it does not encapsulate date \& time nor location), but it is on purpose: simplicity is bliss.
+% Given the lack of real-world data for our testbed, building a more complex and realistic user model would add no value to our proposal: 
+% our goal is to see devices exhibiting frequent disconnections and reconnections (also called \emph{churn}).
+% Our simple model being able to put extravagant stress on our system, it is sufficient to access \name's resilience.
+
+\paragraph*{Formal definition}
+
+%We consider a single user, owning a set of $\mathcal{D}$ devices.
+%Time is discretized \commentAL{Discretized/synchronous time needs more explanation}.
+Needs, and the devices' observations are independent: Alice can have her laptop and phone connected at the same time.
+The hidden process $S=S_1,\dots,S_i, \dots$ is built from an alphabet of states $\mathcal{S}$, while the observable process $O=O_1, \dots, \O_i, \dots$ contains elements from the alphabet $\mathcal{O}$.
+We define a multivariate HMM $\lambda_N$ as follows:
+
+$$\text{HMM}:\;\lambda_N=(\Pi, A, B)$$
+
+where 
 \begin{itemize}
-	\item \texttt{CONNECTED<$d, t_{step}$>}: Sent by device $d$ when it is used by its user at time step\footnote{As far as devices connections are concerned, time is discretized: we consider that each interaction lasts the same time.} $t_{step}$.
-$d$ is otherwise considered offline at this time.
-Devices use this information to predict their probability of remaining online, as presented in section~\ref{ssec:device_availability};
-	\item \texttt{SENDING<\sendingdevice, \fileid>}: When the user decides to send a file $f$ located on a device \sendingdevice, \sendingdevice informs its peers of this fact, and joins the file ID \fileid.
-\Squad members will use this information to forward acknowledgments from the recipient to \sendingdevice;
-	\item \texttt{RECEIVING<\recdevice, \fileid>}: Reciprocally, when the user starts receiving a file $f$ onto a device \recdevice, \recdevice informs its peers of this fact, and joins the file ID \fileid.
-\Squad members will use this information to forward the file's content from the sender to \recdevice.
+	\item $N$ is the number of states in the system:
+	$N = \left| \mathcal{S} \right|$;
+
+	\item $\Pi=\left\{ \pi_i\right\}_{i\in\mathcal{S}}$ is the initial state distribution:\\
+	$\pi_i=P[S_1=i]$;
+
+	\item $A = \left\{ a_{i\,j}\right\}_{(i,j)\in\mathcal{S}^2}$ is the state transition matrix:\\
+	$a_{i\,j}=P[S_t=j \mid S_{t-1}=i]$;
+
+	\item $B = \left\{ b_{i\,k}\right\}_{(i,k)\in\mathcal{S}\times\mathcal{D}}$ is the matrix of event emission probabilities for each state:
+	$b_{i\,k} = P[ k \in O_t \mid S_t = i]$.
 \end{itemize}
 
-Given this information dissemination (push) and history reconciliation mechanism (pull), each \squad member knows the full sequence $S$ at all time with an overwhelming probability, even in the face of churn~\cite{luxey:cascade}.
+In our case, the states $\mathcal{S}$ are the different locations $\mathcal{L}$ where the user is susceptible to go.
+The events represent the devices availability, hence $\mathcal{O} = \mathcal{D}$, where $\mathcal{D}$ is the set of the user's devices.
+Several devices can be available at the same time, such that $O_t$ is a set, and $d \in O_t$ means that device $d$ was available at time $t$. Devices' availability probabilities are independent.
 
-\subsection{Predicting a device's availability}
-\label{ssec:device_availability}
+% In \cref{fig:hmm}, we show an example HMM of a user's behavioral HMM, along with its graphical representation (the initial state distribution $\Pi$ was left out for simplicity). 
+% The represented user possesses a phone and a laptop, that she carries around with her, a home computer, that is only accessible from her home, and a workstation, located at her workplace.
+She never forgets to turn off her fixed appliances before leaving.
 
-The predictive nature of \name lies in the fact that each participating device publicly advertises its probability of being connected in the near future. 
-This information is used when any node needs to create a Stateless Predictive Probabilistic Onion Route (\acs{SPOR}).%, as will be shown in the next subsection~\ref{ssec:por}.
+% Figure~\ref{fig:sample_usage}, shows a possible trace of the user's behavior, using the parameters depicted in figure~\ref{fig:hmm}. 
+% It reads the timeline of $o_{d}$ for each device $d$. On the bottom of the graph, the first letter of the user's location is shown at each time step.
+% We see that devices connections depend on the user's location, and that any number of devices can be connected at the same time.
 
-As described earlier, \squad members know the connection times of all the user's devices, given by the \texttt{CONNECTED} items in the \squad's sequence.
-It can be represented as a 2D sparse matrix of booleans, as shown in the Table~\ref{tab:connection_times} (depicting a user owning a laptop, a phone, and a smart-TV).
+\paragraph*{Predicting future behavior} 
+\label{para:predicting future behavior}
+As already stated, devices want to predict whether they are likely to be available in the near future.
+This information will be publicly available to enable the intelligent building of routes.
 
-\begin{table}
-\caption{Matrix representation of an \squad availability over time}
-\centering
-\begin{tabular}{@{}lccccc@{}} \toprule
-		& $\cdots$	& $t_{i-1}$	& $t_i$		& $t_{i+1}$	& $\cdots$ \\ \midrule
-Laptop	& $\cdots$	& 1			& 0			& 0			& $\cdots$ \\
-Phone	& $\cdots$	& 1			& 1			& 1			& $\cdots$ \\
-TV		& $\cdots$	& 0			& 1			& 1			& $\cdots$ \\ \bottomrule
-\end{tabular}
-\label{tab:connection_times}
-\end{table}
+Because devices availability only depend on the users location, we can predict the devices availability in $i$ round $O_{t+i}$ given only the model $\lambda_N$ and the current user's location $S_t$.
+We first compute the probability that a device $d$ will be available next turn:
 
-To predict a device's future availability, we build a Markov representation of the user's activity, 
-where the state $X_i$ represents the availability of the user's devices at time $t_i$.
-The state space $\mathcal{X}$ is the set of possible combinations of the devices' connection.
+$$
+P\left[ d \in O_{t} \mid S_{t-1} = s \right] = 
+\sum\limits_{s' \in \mathcal{S}} 
+a_{s\,s'} * b_{s'\,d}.
+$$
 
-Given the \squad sequence of connections $S = X_1, \dots, X_i, X_{i+1}, \dots$,
-we can compute the probability of transition from a state $X_i=x$ to $X_{i+1}=x'$ by counting\footnote{%
-	Because we work with low-probability events observed with a small amount of data, there is a possibility that an event never occurs in $S$. 
-	To counter that, we apply additive smoothing while computing probabilities. 
-	We left this engineering optimization out of the demonstration for clarity.
-} the number of times $x'$ is seen right after $x$ in $S$:
+It is the sum of the probabilities, for each state $s$, that the user switches to $s$ and uses her device.
+Recursively, predicting $i$ turns in advance follows the same logic:
 
-\begin{align*}
-P\left[X_{i+1}=x' \mid X_i=x \right] &= P\left[x \rightarrow x' \right] \\&= \frac{\left| \left\{ X_i = x, X_{i+1} = x' \right\}_{i \in \left[0, |S| - 1\right]} \right|}{\left| \left\{ X_i = x \right\}_{i \in \left[0, |S| - 1\right]} \right|}
-\end{align*}
+\begin{multline*}
+P\left[ d \in O_{t+i} \mid S_{t} = s \right] = \\
+\sum\limits_{s' \in \mathcal{S}}
+P\left[ S_{t+1} = s' \mid S_t = s \right] * 
+P\left[ d \in O_{t+i} \mid S_{t+1} = s'\right].
+\end{multline*}
 
-Each device knows the current state $X_i=x$ of the Markov chain.
-To predict its probability $P_d$ of remaining online in the next round, 
-a device $d$ simply adds the probabilities that the user switches to a state where $d$ is online next.
-Consider $\mathcal{X}_{d\text{ online}} \subset \mathcal{X}$ the set of states where $d$ is online. Then:
+We show in section~\ref{sub:predictive_onion_routes_creation} that the prediction of devices' availability at $t+1$ is a good enough estimator of their availability state at $t+i$.
+For that reason, devices only compute and publish $P\left[ d \in O_{t+1} \mid S_{t} = s \right]$.
 
-\begin{align*}
-P_d & = P\left[d\text{ online at }X_{i+1} \mid X_i=x\right] \\ & = \sum\limits_{x' \in \mathcal{X}_{d\text{ online}}} P\left[ X_{i+1}=x' \mid X_i=x \right]
-\end{align*}
+\paragraph*{Inferring the model from the sequence of observations}
 
-There is a caveat, though.
-While the user acts, $S$ keeps growing, and the Markov chain must be recomputed: there is a probability that the current state $X=x$ has never been seen before.
-In this case, $\forall x' \in \mathcal{X}, P\left[x \rightarrow x'\right]$ is undefined.
+Given an initial estimate $\lambda_{N}^{(0)}$ of the model, and the sequence of observations $O$, the Baum-Welch algorithm uses Expectation-Maximization to iteratively compute the most likely $S^{(i)}$ and $\lambda_{N}^{(i)}$ until the probability of the observations using the estimated model falls below a predefined threshold: $P[O; \lambda_{N}^{(i)}] < \epsilon$.
+Devices use this algorithm to infer their user's behavioral model from the observations.
 
-To counter this possibility, we propose a fallback:
-when the current state is new, we compute a $P'_d$, an estimator of $d$'s average probability of staying online two turns in a row:
+It needs an initial model, though, with a predefined number of states $N$. 
+$N$ is given by the user, and we set $\lambda_{N}^{(0)}$ to be a uniform model: probabilities of switching to each location are uniform, and all devices have a probability of being online of 0.5.
 
-$$ P'_d = \frac{\left| \left\{ X_i \in \mathcal{X}_{d\text{ online}}, X_{i+1} \in \mathcal{X}_{d\text{ online}} \right\}_{i \in \left[0, |S| - 1\right]} \right|}{\left| \left\{ X_i \in \mathcal{X}_{d\text{ online}} \right\}_{i \in \left[0, |S| - 1\right]} \right|} $$
-
-$P'd$ will be advertised in spite of $P_d$. It will also be used as a baseline in the evaluation.
-
-%\subsection{Probabilistic Onion Routes}
-% \subsection{Selection of nodes for routes creation}
-% \label{ssec:por}
-
-% %\subsubsection{The global overlay}
-% \subsubsection{\GetRandomNode}
-% \label{sssec:global_overlay}
-
-% Devices need to know the address of SPORES participants in order to craft PORs.
-% To this end, we employ a Random Peer Sampling service~\cite{Jelasity_Voulgaris_Guerraoui_Kermarrec_van_Steen_2007,Jesi_Montresor_van_Steen_2010} (RPS) among all nodes in SPORES.
-% It is a gossip protocol that allows each participant to keep a fixed-size \emph{random} subset of other nodes' descriptor (that we will call the RPS's \emph{view} \rpsview). 
-% The view is constantly evolving, as queries are periodically issued between nodes to exchange descriptors between their respective views.
-% Finally, offline nodes are quickly evicted from devices' views.
-
-% The randomness of the views must be guaranteed: 
-% a node that would be present in views too often would become a bottleneck, and could monitor a bigger portion of the network.
-% It will be evaluated in section~\commentAL{TODO}.
-
-% In SPORES, a descriptor $\desc_d$ describing device $d$ contains the following information:
-% \begin{itemize}
-%   \item \(d\) is the node's identifier (address);
-%   \item \(\pk_d\) is the node's public key;
-%   \item \(\Pon_d\) is the node's probability of remaining online at the time of the descriptor's creation.
-% \end{itemize}
-
-% $(d, \pk_d, \Pon_d)= \leftarrow \GetRandomNode$ is the function that takes a node from the RPS's view \rpsview on demand.
-
-% %\subsubsection{Routes creation}
-% \subsubsection{\CreateLayer}
-% \label{sssec:routes_creation}
-
-% Routes are created via \Sphinxes as described in section~\ref{sec:SPOR}.
-% But each layer \layer constituting the route is created by the $\CreateLayer$ function, that is independent from \Sphinxes.
-
-% In \name, we wish to maximize the availability of the route.
-% Therefore, each layer \layer is created so as to reach the availability threshold $\theta$, a parameter chosen by the user.
-% Note that \Sphinxes is agnostic to this use-case: one could want to maximize other characteristics, e.g. the layer's expected bandwidth.
-
-% $\CreateLayer$ iteratively calls $\GetRandomNode\xspace$ to add random nodes to the current layer \layer, until the layer's probability of being offline, $\Poff^\layer$, falls below the availability threshold $\theta$:
-
-% $$ \Poff^\layer = \sum\limits_{d \in \layer}(1 - \desc_d.\Pon_d) $$
-
-% When a device creates a layer to reach its user, descriptors are not taken from \rpsview but from the \squad's sequence: all devices in this layer will belong to the user.
-% The logic is otherwise the same.
-
-% Recall that each layer in \Sphinxes has a constant number of nodes $w_\layer$, that is a \Sphinxes parameter.
-% If $w_\layer$ is reached before $\Poff^\layer < \theta$, then we early abort $\CreateLayer$.
-% On the other hand, if $|\layer| < w_\layer$, we pad the layer with blank descriptors, such that the header always weighs the same size.
-
-\subsection{SPORES: file exchange through probabilistic onion routes}
-\label{ssec:spores_file_exchange_through_probabilistic_onion_routes}
-
-We have seen how participants of \name could craft routes to secretly exchange messages.
-We now apply this feature to reliably exchange files between two users.
-
-Our file transfer protocol is loosely based on BitTorrent \cite{bt_bep3}: 
-at initialization, a file $f$ of size \filesize is first cut into chunks of constant size \chunksize by its uploader,
-resulting in $\nchunks = \lceil \filesize / \chunksize \rceil$ chunks.
-A SHA1 hash \hashchunk is computed for each chunk, plus another SHA1 hash \hashfile of the chunks hashes; that will serve as an error detection scheme.
-
-In BitTorrent, \textit{.torrent} files are publicly available on the Web.
-They contain $\finfo = \left(\filesize, \nchunks, \left[\hashchunk\right]_{\chunk \in f}, \hashfile\right)$, 
-along with network information to reach uploaders of $f$ (e.g. the tracker's address).
-Anyone can download a \textit{.torrent} and start receiving the file associated to it.
-
-In \name, we want file exchanges to remain private: the file's metadata are exchanged out-of-band.
-In addition , each file is associated with a random \fileid, that is part of \finfo.
-
-\newcommand\forwardheader{\ensuremath{\mathcal{H}^{(f)}}}
-\newcommand\backwardheader{\ensuremath{\mathcal{H}^{(b)}}}
-
-\paragraph*{Out-of-band initialization} 
-When Alice wishes to send a file $f$ to Bob, she computes \finfo, 
-including one reply header per chunk (as was seen in section~\ref{sec:SPOR}), and sends the whole to Bob.
-Still out-of-band, Bob replies with one forward header per chunk.
-This way, each chunk $\chunk_i$ is associated with a unique route both ways: 
-a forward header $\forwardheader_i$ known by Alice, and a backward header $\backwardheader_i$ known by Bob.
-
-Alice and Bob now have everything they need to start transferring $f$ in-band.
-
-\paragraph*{Chunks and bitfields}
-Alice's file $f$ is located on one of her devices, \sendingdevice. 
-When $\sendingdevice$ is online, it periodically sends chunks of $f$ to Bob until $f$ is entirely uploaded, with a period of \tupload.
-Each chunk $\chunk_i \in f$ is uploaded to Bob through a unique route $\forwardheader_i$.
-
-Bob receives $f$ on a single device \recdevice, but chunks for $f$ might arrive on any of his devices.
-Say Bob has received a chunk $\chunk_i$ on $d \neq \recdevice$.
-This device must the address of the file's recipient \recdevice by looking for the line \texttt{RECEIVING<\recdevice, \fileid>} in its squad sequence.
-Having found the address of \recdevice, $d$ forwards the $\chunk_i$ to \recdevice.
-
-Upon reception of a chunk $\chunk_i$, \recdevice verifies its integrity by computing the SHA1 hash $h_{\chunk_i}$ and comparing it to $\finfo.h_{\chunk_i}$.
-If the chunk is valid, Bob must inform Alice that $\chunk_i$ was successfully received.
-We borrow again from the BitTorrent protocol by acknowledging reception with \emph{bitfields}.
-A bitfield \bitfield is bit-array of size \nchunks, such that $\bitfield[i] = 0$ means that Bob lacks the chunk $\chunk_i$, whereas $\bitfield[i] = 1$ means that he successfully received that chunk.
-$\bitfield$ describes the state of the total transfer and not just the current chunk, which is very useful when messages are prone to get lost in transit. 
-This bitfield is sent to Alice using the unique reply route $\backwardheader_i$.
-
-Reciprocally, acknowledgments can arrive to Alice on any on her devices, while only \sendingdevice can process it.
-When one of Alice's devices (say $d'$) receives Bob's bitfield \bitfield, 
-$d'$ forwards it to \sendingdevice by getting its address on the line \texttt{RECEIVING<\sendingdevice, \fileid>} of the \squad overlay's sequence.
-
-Once \sendingdevice receives \bitfield, it merges it with its previous knowledge of Bob's reception of $f$.
-If all chunks were acknowledged, the transfer is over.
-Else, \sendingdevice sends a new chunk, among the ones that were not acknowledged by Bob.
-
-%\commentAL{This is a shitty scheduler. Should I mention it? Rephrase? You have a citation to propose instead?}
-
-Naturally, in \name, messages might arrive in a wrong order or fail, e.g.
-it is not unlikely that the file exchange stops before its transfer is done.
-Consequently, as a solution, if the transfer hangs, \sendingdevice will restart periodically sending chunks that were not acknowledged by Bob.
-Hence, \name ensures liveness over network efficiency (some chunks might be received several times), as it will be seen in the evaluation.
-Nevertheless, it allows reliable file transfer among a network of poorly connected nodes in a private manner.
+Baum-Welch usually requires a lot of data to fit the model $\lambda_N$ that generated $O$.
+Indeed, $P[O; \lambda_{N}^{(i)}] < \epsilon$ does not mean that $\lambda_N \simeq \lambda_N^{(i)}$.
+In our case, we do not care as long as the predictions using the estimated model, $P[O_{t+1} \mid S_t; \lambda_N^{(i)}]$, are close to the ground-truth, $P[O_{t+1} \mid S_t; \lambda_N]$.
+%This will be evaluated in section~\ref{sub:devices_predictions_of_the_user_behavior}.

### 2019-05-10 swits/abstract.tex
Adds abstract for SWITS

% What's the problem?
SPORES is a protocol that provides a file transfer service that does not rely 
on a central service but provides strong privacy guarantees.

% Why is it a problem? Research gap left by other approaches?
% Not really covered: Why is it important? Why care?
Consider that Alice wants to share a file with Bob.
She uploads the file to \enquote{the Cloud} (someone else's computer) and sends 
a link to Bob.
Bob fetches the file from the third-party storage.
This allows the third party to infer much information.
SPORES changes this.

% What's the approach? How to solve the problem?
Alice has several devices (laptop, smartphone, etc.) with varying 
online--offline patterns, we call these devices her device squad.
The squad knows which device has which files and each device of the squad has a 
model of the other devices' online--offline patterns.
Alice's devices can coordinate the sending of the file.
Similarly, Bob also has a device squad, and his squad can coordinate receiving 
the file.
Instead of Alice giving Bob a link to the file in the Cloud, Bob gives Alice a 
route where the destination is his squad (\ie the \emph{set} of Bob's devices).

% What's the findings? How was it evaluated, what are the results, limitations, 
% what remains to be done?
At the core of our proposal lies a stateless, probabilistic onion-routing 
protocol called SPOR\@.
SPOR relies on a set-based mix-header format based on Sphinx~\cite{Sphinx} (we 
dubb this extension SphinxES, for Sphinx Extended for Sets).
Given an algorithm for secure peer sampling, a probabilistic model of node 
availability, SPOR will populate the layers of SphinxES with sets of devices to 
reliably deliver packets from one set of devices to another over a network of 
mix-nodes with high churn.

This yields several interesting properties, among others: SPOR can provide 
connections over a network of unreliable devices, unlike Tor's network of 
dedicated, always online devices; SPOR removes the weakest-link bandwidth 
problem present in Tor, sets of nodes at each layer provides a wider path and 
thus more bandwidth; at the same time, SPOR still provides privacy guarantees 
en par with Tor.

### 2019-05-21 spores-protocol-paper/sphinxes.tex
Adds acro adjective, adverb forms from bibsp

@@
 
-\Textcite{Sphinx} designed \iac{UC} secure message format for mixes, called 
+\Textcite{Sphinx} designed \iacadv{UC} secure message format for mixes, called 
 Sphinx.
-Since it is \ac{UC} secure, it provably implements an ideal onion routing 
+Since it is \acadv{UC} secure, it provably implements an ideal onion routing 
 functionality.

### 2019-05-23 spores-protocol-paper/approach.tex
Changes back from \ac{Tor} to Tor

--- 2018-08-09 paper/approach.tex
@@
 \Sphinxes does \emph{not} introduce any restrictions on whether the network 
-topology must be fully connected or not, be asynchronous (as in \ac{Tor}) or 
+topology must be fully connected or not, be asynchronous (as in Tor) or 
 synchronous (as in mix-nets), whether node selection must be uniformly random 

### 2019-05-23 spores-protocol-paper/intro.tex
Changes back from \ac{Tor} to Tor

--- 2018-08-09 paper/intro.tex
@@
 discouraging~\cite{LeBlond:2013}, as churn causes routes to disappear and be
-reconstructed frequently, which is particularly costly. By contrast, \ac{Tor}, 
-one of the most popular anonymous networks,
+reconstructed frequently, which is particularly costly. By contrast, 
+Tor~\cite{Tor}, one of the most popular anonymous networks,
 trades lower anonymity guarantees for a much better
@@
 % predictions for node availability;
-% \item We have extended Sphinx~\cite{Sphinx}, a compact and secure
+% \item We have extended \ac{Sphinx}, a compact and secure
 %   message header format for mixnets, to allow for sets of nodes
@@
   \item We propose \Sphinxes, an extension of the
-    Sphinx~\cite{Sphinx} mix-header format to set-based onion routing.
+    \ac{Sphinx} mix-header format to set-based onion routing.
 \Sphinxes allows each layer of an onion route to contain several alternative next nodes, thus realizing a source-routed limited random-walk protocol.

### 2019-05-23 spores-protocol-paper/security-discussion.tex
Changes back from \ac{Tor} to Tor

--- 2018-10-03 paper/security-discussion.tex
@@
 the system~\cite{DenialOfSecurity}.  As mentioned in
-\cref{system-model}, we share the adversary model with \ac{Tor}
+\cref{system-model}, we share the adversary model with Tor
 %and Sphinx
@@
 messages; they immediately forward any messages.
-This puts \ac{SPORES} in the same position as \ac{Tor}, \ie more vulnerable to 
+This puts \ac{SPORES} in the same position as Tor, \ie more vulnerable to 
 traffic analysis than batching mix-nets~\cite{RoutingSurveyAnonymousProtocols} 
-\commentDaniel{we should probably look for the original papers} --- this 
+\daniel{we should probably look for the original papers} --- this 
 vulnerability is inherited from the mixing strategy.
 
-% \commentDaniel{Predecessor attacks: random walk protocols has the problem that 
+% \daniel{Predecessor attacks: random walk protocols has the problem that 
 %   the adversary can see the initiator (statistically) more often than the other 

### 2019-05-23 spores-protocol-paper/system-model.tex
Changes back from \ac{Tor} to Tor

--- 2018-10-03 paper/system-model.tex
@@
 
-%adversary model: remove provider, compensate, results in same as in sphinxOR/\ac{Tor}?  friends?
+%adversary model: remove provider, compensate, results in same as in sphinxOR/Tor?  friends?
 
@@
 \paragraph*{Adversary model} To assess our approach, we use the
-adversary model assumed by \ac{Tor} and \ac{Sphinx}:
+adversary model assumed by Tor and \ac{Sphinx}:
 the adversary has complete control over some part of the network as

### 2019-05-23 spores-protocol-paper/security-discussion.tex
Enables comments again, changes commentDaniel to daniel

@@
 network, \ie \(f_A = \frac{|D_A|}{|D|}\).
-\commentDaniel{Check that we still use the \(D_i\) notation for the devices in 
+\daniel{Check that we still use the \(D_i\) notation for the devices in 
   \(i\)'s squad.}
@@
   better/worse/the same?}
-\commentDaniel{Hard to say at this time of night \dots}
+\daniel{Hard to say at this time of night \dots}
 
@@
   she learn/guess?}
-\commentDaniel{For all she knows there might be another node at either the 
+\daniel{For all she knows there might be another node at either the 
   beginning or the end, she cannot tell.}
@@
   only postpone the success of the attack, eventually even our
-  protocol must resend.'' why?}  \commentDaniel{Due to statistics. We should 
+  protocol must resend.'' why?}  \daniel{Due to statistics. We should 
   also look into

### 2019-05-23 spores-protocol-paper/intro.tex
Enables comments again, changes commentDaniel to daniel
Edits intro

@@
 arbitrary device to another~\cite{Dearman:2008}, as they
-would have a few years ago with an USB key or an email.
+would have a few years ago with a USB key, an email or, nowadays, the Cloud.
 
 This thirst for seamless sharing explains the rise and ongoing popularity
-of personal sharing platforms such as Dropbox, Google Docs,
-OneDrive, Amazon Drive, etc. These solutions allow users to share data with anyone, anywhere, at almost
+of personal sharing platforms such as Dropbox, Google Drive,
+OneDrive, Amazon Drive, \etc.
+These solutions allow users to share data with anyone, anywhere, at almost
 anytime, between any devices. They achieve this feat by relying heavily on
@@
 multiple data centers, often in foreign jurisdictions, making it difficult for most users to grasp, review, and assess the privacy, and
-confidentiality guarantees they can expect. In practice, user data hosted in the cloud is routinely harvested, often without explicit
+confidentiality guarantees they can expect.
+\daniel{We need a reference for this strong statement.}
+In practice, user data hosted in the cloud is routinely harvested, often 
+without explicit
 consent, either by cloud providers or third parties, a sad situation that is only partially
@@
 %  because it does not protect meta-data information
-The exposure of metadata seriously weakens user privacy, as famously emphasized by a former NSA and CIA director: "\emph{We kill people based on metadata.}''~\cite{NaughtonTheGuardian2016} 
-In this model, user devices, masquerading as allies, get turned into %% tracking and/or monitoring \squad{}s, and serve as
+The exposure of metadata seriously weakens user privacy, as famously emphasized 
+by a former NSA and CIA director: \textcquote{NaughtonTheGuardian2016}{We kill 
+  people based on metadata}. In this model, user devices, masquerading as 
+allies, get turned into %% tracking and/or monitoring \squad{}s, and serve as
 highly efficient monitoring tools spying on their owners.
@@
 with strong privacy protection in file transfer systems. We present
-\name{}, a novel fully decentralized, autonomous,
+\name{}, a fully decentralized, autonomous,
 % approach that provides a 
@@
 alone, thereby reducing one's exposure to security and privacy threats
-from third parties. \emph{Secondly}, we consider \emph{proxemics relationships} as a key enabler to initiate file
-transfers. Physical proximity allow users to share
-routing information out-of-band.
-%, e.g. from their \squad. \commentFT{I did not get what 'from their \squad' mean.} 
-In contrast to state-of-the-art P2P systems, users of \name agree out-of-band to share a file, but
+from third parties. \emph{Secondly}, just as users must exchange links (URLs) 
+that point to the files in the Cloud, we can encode mix-net headers and 
+meta-data as links to exchange instead.
+In contrast to state-of-the-art P2P systems, users of \name agree out-of-band 
+to share a file, but
 do not keep it available for anyone else in the future. \emph{Thirdly}, we
-exploit distributed machine learning techniques to predict the future
-availability of user devices, and use this ability to implement a
-\emph{probabilistic predictive onion routing} protocol.
-Our protocol exploits a new mix-header format that uses onion layers made of sets of nodes rather single nodes.
-The use of multiple nodes in individual layers, together with our estimation of future device availability, exploited in a stateless way, allows
+implement a \emph{stateless probabilistic onion routing} protocol. Our protocol 
+exploits a new mix-header format that uses onion layers made of sets of nodes 
+rather single nodes. The use of multiple nodes in individual layers, exploited 
+in a stateless way, allows
 us to overcome the inherent fragility of pure P2P file transfer schemes while providing strong privacy properties.
@@
   \item We propose \Sphinxes, an extension of the
-    \ac{Sphinx} mix-header format to set-based onion routing.
-\Sphinxes allows each layer of an onion route to contain several alternative next nodes, thus realizing a source-routed limited random-walk protocol.
+    \ac{Sphinx} mix-header format to set-based onion routing. \Sphinxes allows 
+    each layer of an onion route to contain several alternative next nodes, 
+    thus realizing a source-routed bounded random-walk protocol.
 
@@
     protocol
-    that, given a secure 
-    \ac{RPS} protocol and availability estimates, selects nodes to populate the 
-    layers of \Sphinxes in order to maximize the availability of the route. This node selection procedure 
-    yields reliable routes even in the presence of low-availability nodes while retaining the strong privacy properties of onion routing.
+    that, given a secure \ac{RPS} protocol and a probability distribution, 
+    selects nodes to populate the layers of \Sphinxes in order to maximize a 
+    desired property of the route.
+    \daniel{We must reconsider this phrasing.}
+    This node selection procedure yields reliable routes even in the presence 
+    of low-availability nodes while retaining the strong privacy properties of 
+    onion routing.
 
-  \item We provide a protocol for a device \squad to estimate the availabilities 
-    of its own devices, based on Markov models and \squad overlays.
-    These estimated availabilities can then be exploited by \ac{SPOR} to populate \Sphinxes.
-   % \commentDaniel{We should add some more details, maybe.}
+  \item \daniel{Protocol for syncing devices? Or just refer to Cascade?}
 
-  \item We use \ac{SPOR} to realize \name, \sonja{removed for
-      redundancy, rephrased: a novel, fully decentralized, 
-    autonomous and self-organizing} a privacy-preserving file transfer service among
+  \item We use \ac{SPOR} to realize \name, a privacy-preserving file transfer 
+    service among
   users that eschews any third-party storage or centralized bootstrapping service.
@@
 system and adversary models as well as the desired security and
-privacy properties of \name. Section~\ref{approach} describes the
-overall approach. In Section~\ref{Sphinxes}, we introduce \sphinxes. 
-Then, in Section~\ref{design}, we introduce the different building
-blocks of \name. In sections~\ref{security-discussion} and \ref{Performance},
-respectively, we evaluate the security and performance of our
-approach. We set \name into context with related work in
-Section~\ref{RelatedWork}, and finally conclude with Section~\ref{conclusion}.
+privacy properties of \name.
+\Cref{approach} describes the overall approach.
+In \cref{Sphinxes}, we introduce \sphinxes.
+Then, in \cref{design}, we introduce the different building blocks of \name.
+In \cref{security-discussion}, we evaluate the security of our approach.
+We set \name into context with related work in \cref{RelatedWork} and, finally, 
+conclude with \cref{conclusion}.
 

### 2019-06-03 swits/contents.tex
Adds slides for SWITS

\title{%
  SPORES: Transferring files as spores through the wind instead of up in the Cloud
}
\author{Daniel Bosk\thanks{%
    Joint work with Sonja Buchegger (KTH), Adrien Luxey, David Bromberg, 
    François Taîani (INRIA/IRISA Rennes, France)
  }}
\institute{%
  KTH EECS\\
  \email{dbosk@kth.se}
}

\mode<article>{\maketitle}
\mode<presentation>{%
  \begin{frame}
    \maketitle
  \end{frame}
}

\mode*

\section{Introduction}

\subsection{What's the problem?}

\begin{frame}
  \begin{block}{The problem}
    \begin{itemize}
      \item Users have multiple devices: laptop, smartphone, \dots
      \item Files are spread among devices: documents on laptop, photos on phone, 
        \dots

        \pause

      \item Users want to share files.
    \end{itemize}
  \end{block}
\end{frame}

\subsection{Why is it a problem?}
% Why is it a problem? Research gap left by other approaches?
% Why is it important, why care?

\begin{frame}
  \begin{example}[Current practice]
    \begin{itemize}
      \item Alice wants to share a file with Bob.
      \item Alice copies it to Someone Else's computer (a.k.a.\ the Cloud).
      \item She sends a URL to Bob (email, instant message, \dots)
      \item Bob fetches the file from Someone Else's computer.
    \end{itemize}
  \end{example}
\end{frame}

\begin{frame}
  \begin{remark}
    \begin{itemize}
      \item Alice and Bob have privacy against each other.
      \item Someone Else can see everything.
    \end{itemize}
  \end{remark}

  \pause

  \begin{question}
    \begin{itemize}
      \item Can we remove Someone Else's central position?
      \item And still have privacy?
    \end{itemize}
  \end{question}
\end{frame}

\section{The solution}

\subsection{What's the approach?}
% What's the approach? How to solve the problem?

\begin{frame}
  \begin{block}{Goals}
  \begin{itemize}
    \item We want end-to-end encryption for data.
    \item Alice and Bob should only learn that the other has at least one 
      device online.
    \item Someone Else should not learn that Alice and Bob exchange files.
    \end{itemize}
  \end{block}

  \pause

  \begin{idea}
    \begin{itemize}
      \item We leverage that each user have multiple devices.
      \item Although these devices have varying availability.
    \end{itemize}
  \end{idea}
\end{frame}

\begin{frame}
  \begin{block}{Idea}
    \begin{itemize}
      \item We use onion routing with a rendezvous point for privacy.
    \end{itemize}
  \end{block}

  \includegraphics[width=0.48\textwidth]{fig/tor.png}
  \hfill
  \includegraphics[width=0.48\textwidth]{fig/tor-hs.png}

  \pause

  \begin{remark}
    \begin{itemize}
      \item Our devices are not as reliable as Tor nodes.
    \end{itemize}
  \end{remark}
\end{frame}

\begin{frame}
  \begin{center}
    \includegraphics[height=0.5\textheight]{fig/principle-SPOR.pdf}
  \end{center}

  \pause

  \begin{block}{Approach}
    \begin{itemize}
      \item We adapt the Sphinx mix-header format.
      \item Still universally composable.
    \end{itemize}
  \end{block}
\end{frame}

\begin{frame}
  \begin{example}[Scenario]
    \begin{itemize}
      \item Alice wants to send a file to Bob.
      \item \emph{Bob} encodes a SPOR route as a URL and sends to Alice.
      \item Alice \enquote{wraps} a route around Bob's.
      \item She sends the file over the route.
    \end{itemize}
  \end{example}

  \pause

  \begin{remark}
    \begin{itemize}
      \item Bob's set of devices (a squad) must coordinate to reassemble the 
        file.
      \item Alice's squad can coordinate too to send the file.
    \end{itemize}
  \end{remark}
\end{frame}

\subsection{What are the findings?}
% What's the findings? How was it evaluated, what are the results, limitations, 
% what remains to be done?

\begin{frame}
  \begin{block}{Interesting properties}
    \begin{itemize}
      \item Source-bounded random walk
      \item Sender and recipient are sets --- avoids random-walk problems.
      \item Can optimize redundancy for various attributes: availability, 
        bandwidth, \dots
    \end{itemize}
  \end{block}
\end{frame}

\section{Summary}

\begin{frame}
  \begin{block}{Take away}
    \begin{itemize}
      \item Sphinx Extended for Sets (Sphixes)
      \item Onion routing over unreliable nodes.
      \item Alice and Bob can transfer files without Someone Else learning about 
        it.
      \item They reveal minimal information to each other.
    \end{itemize}
  \end{block}
\end{frame}

%%% REFERENCES %%%

\begin{frame}[allowframebreaks]
  \printbibliography
\end{frame}

### 2019-06-12 short-talk/contents.tex
Improves short talk slides

--- 2019-06-03 swits/contents.tex
@@
     \begin{itemize}
-      \item Alice and Bob have privacy against each other.
+      \item Alice and Bob enjoy privacy against each other.
       \item Someone Else can see everything.
@@
       \item Can we remove Someone Else's central position?
-      \item And still have privacy?
+      \item And still enjoy privacy?
     \end{itemize}
@@
   \end{block}
+\end{frame}
 
-  \pause
+\begin{frame}
+%  \begin{idea}
+%    \begin{itemize}
+%      \item We leverage that each user have multiple devices.
+%      \item Some subset of devices is online at any given time.
+%      \item Alice and Bob will use Carol's and David's devices for relaying.
+%    \end{itemize}
+%  \end{idea}
 
-  \begin{idea}
-    \begin{itemize}
-      \item We leverage that each user have multiple devices.
-      \item Although these devices have varying availability.
-    \end{itemize}
-  \end{idea}
+  \begin{center}
+    \includegraphics[height=0.6\textheight]{spores-squads.png}
+  \end{center}
 \end{frame}
@@
   \begin{center}
-    \includegraphics[height=0.5\textheight]{fig/principle-SPOR.pdf}
+    \includegraphics[height=0.25\textheight]{sphinx-route.png}
   \end{center}
 
-  \pause
-
-  \begin{block}{Approach}
-    \begin{itemize}
-      \item We adapt the Sphinx mix-header format.
-      \item Still universally composable.
-    \end{itemize}
-  \end{block}
+  \begin{center}
+    \includegraphics[height=0.4\textheight]{sphinxes-route.png}
+  \end{center}
 \end{frame}
@@
       \item Alice wants to send a file to Bob.
-      \item \emph{Bob} encodes a SPOR route as a URL and sends to Alice.
+      \item \emph{Bob} encodes a route as a URL and sends to Alice.
       \item Alice \enquote{wraps} a route around Bob's.
-      \item She sends the file over the route.
+      \item She sends the file (chunks) over the route.
     \end{itemize}

### 2020-03-23 paper/spores.tex
Changes to plain article format

@@
-\documentclass[conference]{IEEEtran}
-%\documentclass[draftcls]{IEEEtran}
-\pagestyle{plain}
-\usepackage{import}
-\usepackage{capt-of}
-\usepackage[noend]{algpseudocode}
-\usepackage{pifont}
-\errorcontextlines\maxdimen
-
-% begin vertical rule patch for algorithmicx (http://tex.stackexchange.com/questions/144840/vertical-loop-block-lines-in-algorithmicx-with-noend-option)
-\makeatletter
-% start with some helper code
-% This is the vertical rule that is inserted
-    \newcommand*{\algrule}[1][\algorithmicindent]{\makebox[#1][l]{\hspace*{.5em}\thealgruleextra\vrule height \thealgruleheight depth \thealgruledepth}}%
-% its height and depth need to be adjustable
-\newcommand*{\thealgruleextra}{}
-\newcommand*{\thealgruleheight}{.75\baselineskip}
-\newcommand*{\thealgruledepth}{.25\baselineskip}
-
-\newcount\ALG@printindent@tempcnta
-\def\ALG@printindent{%
-    \ifnum \theALG@nested>0% is there anything to print
-        \ifx\ALG@text\ALG@x@notext% is this an end group without any text?
-            % do nothing
-        \else
-            \unskip
-            \addvspace{-1pt}% FUDGE to make the rules line up
-            % draw a rule for each indent level
-            \ALG@printindent@tempcnta=1
-            \loop
-                \algrule[\csname ALG@ind@\the\ALG@printindent@tempcnta\endcsname]%
-                \advance \ALG@printindent@tempcnta 1
-            \ifnum \ALG@printindent@tempcnta<\numexpr\theALG@nested+1\relax% can't do <=, so add one to RHS and use < instead
-            \repeat
-        \fi
-    \fi
-    }%
-\usepackage{etoolbox}
-% the following line injects our new indent handling code in place of the default spacing
-\patchcmd{\ALG@doentity}{\noindent\hskip\ALG@tlm}{\ALG@printindent}{}{\errmessage{failed to patch}}
-\makeatother
-
-% the required height and depth are set by measuring the content to be shown
-% this means that the content is processed twice
-\newbox\statebox
-\newcommand{\myState}[1]{%
-    \setbox\statebox=\vbox{#1}%
-    \edef\thealgruleheight{\dimexpr \the\ht\statebox+1pt\relax}%
-    \edef\thealgruledepth{\dimexpr \the\dp\statebox+1pt\relax}%
-    \ifdim\thealgruleheight<.75\baselineskip
-        \def\thealgruleheight{\dimexpr .75\baselineskip+1pt\relax}%
-    \fi
-    \ifdim\thealgruledepth<.25\baselineskip
-        \def\thealgruledepth{\dimexpr .25\baselineskip+1pt\relax}%
-    \fi
-    %\showboxdepth=100
-    %\showboxbreadth=100
-    %\showbox\statebox
-    \State #1%
-    %\State \usebox\statebox
-    %\State \unvbox\statebox
-    %reset in case the next command is not wrapped in \myState
-    \def\thealgruleheight{\dimexpr .75\baselineskip+1pt\relax}%
-    \def\thealgruledepth{\dimexpr .25\baselineskip+1pt\relax}%
-}
-% end vertical rule patch for algorithmicx
-
+\documentclass{article}
 \input{preamble.tex}
+\usepackage{authblk}
 
 \begin{document}
+\title{%
+  \acs*{SPORES}: \acl*{SPORES}%
+  %\name: Stateless Predictive Onion Routing for E-Squads%
+  %% From the IEEE template
+  % \thanks{Identify applicable funding agency here. If none, delete this.}
+  % \thanks{%
+  %   Daniel Bosk and Sonja Buchegger were funded by
+  %   the Swedish Foundation for Strategic Research grant SSF FFL09-0086.
+  %   Research done while Daniel Bosk visited the WIDE team at INRIA/IRISA Rennes, 
+  %   France.
+  % }
+}
+
+\author[1]{Daniel Bosk\thanks{%
+  Research done while the author visited the WIDE team at INRIA/IRISA Rennes, 
+  France.
+}}
+\affil[1]{KTH Royal Institute of Technology\\\email{daniel@bosk.se}}
+\author[1]{Sonja Buchegger}
+\author[2]{Adrien Luxey}
+\affil[2]{Univ.\ de Rennes, INRIA, CNRS, IRISA\\\email{Adrien.Luxey@irisa.fr}}
+\author[2]{Yérom-David Bromberg}
+\author[2]{François Taïani}
+
+\mode<article>{\maketitle}
+\mode<presentation>{%
+  \begin{frame}
+    \maketitle
+  \end{frame}
+}
+
+\begin{abstract}
+  \input{abstract.tex}
+\end{abstract}
+
 \input{contents.tex}

### 2020-03-23 paper/evaluation.tex
Removes performance eval (heavy on prediction)

@@
 
-To evaluate our protocol, we built a prototype of \name that implements the complete \name protocol in 5400 lines of Go code.
-The users and their behavior (i.e. devices usage and file exchange decisions), on their part, are simulated by 1500 lines of Python.
-Each device is a Docker container that ships the same \name code, and communicates with its peers via TCP connections.
-To allow for realistic simulations (embodying more than 10 users), we distribute the experiments over 5 machines (one with an Intel Xeon E5-2660 CPU (32 cores) and 128GB of RAM, and four having an Intel Xeon E5420 CPU (8 cores) and 32GB of RAM), such that each \squad always resides on the same machine.
-All peers are connected to the same Docker overlay network, and are thus reachable from any other device.
-
-In the following, we first give precisions on the evaluation testbed and parameters in section~\ref{sub:evaluation_testbed}, before evaluating the file transfer performance in section~\ref{sub:file_transfer}.
-
-\subsection{Evaluation testbed} % (fold)
-\label{sub:evaluation_testbed}
-
-\subsubsection{Simulating user behavior} % (fold)
-\label{ssub:simulating_user_behavior}
-
-To evaluate \name, we take interest in users owning a variable amount of devices of different types, and frequently switching among them.
-To the best of our knowledge, there does not exist real-world dataset of the devices connection times of such a user.
-On our testbed, each user's behavior is therefore simulated, according to the following rules:
-\begin{itemize}
-  \item The user owns a variable amount of devices.
-We consider the following device types: mobile (e.g.
-tablet, phone), portable (laptop), fixed (workstation, home computer) and server (such as a NAS, Raspberry Pi or rented appliance);
-  \item The user always owns a phone;
-	\item The user can travel between different locations;
-	\item The user makes a different use of her devices depending on her location and device type: 
-  her home computer will only be accessed at home, while her phone can be accessed everywhere (though she might tend to use it at home more than at work);
-  \item The user's action are discretized: every action lasts the same amount of time \tuser.
-\end{itemize}
-
-Towards this goal, we model each user as a discrete time Hidden Markov Model (HMM) of order one. 
-The hidden process $S=S_1, \dots, S_i, \dots$ represents the user's movements from one location from another, 
-taken from the set of possible locations $\mathcal{S}$.
-In our case, there are several independent observation processes (one per device), 
-that form the observation sequence $O= O_1, \dots, O_i, \dots$.
-$O_i[j]=1$ (resp. 0) means that the user's device $d_j$ was online (resp. offline) at time step $t_i$.
-
-A HMM of order one is such that the current state $S_i$ (at time $t_i$) only depends on the previous one $S_{i-1}$ (at time $t_{i-1}$).
-The observation at time $t_i$ ($O_i$) only depends on the current state $S_i$.
-
-%locations, constituted of a set of $N$ potential locations (e.g. home, work or outside), $N$ being a user-defined parameter.
-
-%We thus model each user with a Hidden Markov Model, as presented in section~\ref{sub:a_model_of_the_user_s_behavior}.
-In detail, we applied the following rules to our models: 
-\begin{itemize}
-  \item There are three possible locations $\mathcal{S}=\left\{\text{Home}, \text{Outside}, \text{Work}\right\}$.
-  Each user has transition probabilities from one place to another;
-  one cannot go from work to home without transitionning outside and vice-versa;
-  \item A user always has a phone, plus a random number of 2 to 9 devices which types are decided by a weighted random choice: each device has 30\% chances of being either mobile, portable, or fixed, and only 10\% probability of being a server;
-  \item For each user, device, and location, the probability that a device be used at a location is picked at uniform random according to the following rules:
-  \begin{itemize}
-    \item \emph{Mobiles} can be accessed everywhere with a probability of 60 to 100\%;
-    \item \emph{Portables} can be accessed everywhere with a probability of 20 to 80\%;
-    \item \emph{Fixed} appliances can only be accessed from one single place (never outside) with a probability of 30 to 90\%;
-    \item \emph{Servers} have a constant availability rate between 90 and 100\%.
-  \end{itemize}
-\end{itemize}
-
-% we keep the different possible locations $\mathcal{L}$ to $N=3$ and the state transition matrix $A$ to a fixed value (cf figure~\ref{fig:hmm}).
-% The number and types of devices per user, along with the matrix of emission probabilities $B$, is determined randomly according to the following rules.
-
-% A user always has a phone, plus a random number of 2 to 9 devices whose type is decided by a weighted random choice: each device has 30\% chances of being either mobile, portable, or fixed, and only 10\% probability of being a server.
-% $B_{*, d}$, the probability that device $d$ is used in each location, depends on $d$'s device type: 
-% \begin{itemize}
-% 	\item for each location, every mobile device $d_m$ has a random but high probability of being online: $\forall l \in \mathcal{L}, B_{l, d_m} \in [0.6, 1]$;
-% 	\item a portable device $d_p$ has a much lower probability of being used: $\forall l \in \mathcal{L}, B_{l, d_p} \in [0.2, 0.8]$; 
-% 	\item a fixed appliance $d_f$ has a non-zero probability of usage in only one location: $\exists l \in \mathcal{L}, B_{l, d_f} \in [0.4, 0.8] \text{ and } \forall l' \neq l, B_{l', d_f} = 0$;
-% 	\item a server $d_s$ has a very high probability of working, whatever the user's location: $\exists p \in [0.9, 1], \forall l \in \mathcal{L}, B{l, d_s} = p$.
-% \end{itemize}
-
-\begin{figure}[t]
-\centering
-\vspace{-1em}
-\footnotesize
-\centering
-% $$A =
-% \kbordermatrix{
-%       & W   & O   & H   \cr
-%     W & 0.6 & 0.4 & 0   \cr
-%     O & 0.2 & 0.6 & 0.2 \cr
-%     H & 0   & 0.4 & 0.6 \\[0.3em]
-% }, \;
-% B = 
-% \kbordermatrix{
-%       & W     & O   & H   \cr
-%     p & 0.7 & 0.6 & 0.8 \cr
-%     w & 0.7 & 0   & 0   \cr
-%     h & 0   & 0   & 0.7 \cr
-%     l & 0.2 & 0.4 & 0.6 \\[0.3em]
-%}$$
-
-\includegraphics[width=0.65\columnwidth]{figures/hmm.pdf}
-\vspace{2ex}
-\includegraphics[width=0.9\columnwidth]{figures/sample_usage.pdf}
-
-\caption{\label{fig:hmm} Example Hidden Markov Model (HMM) of a user's behavior.
-On top: visual representation of the model, with transition probabilities between locations and device usage probabilities at each location.
-On the bottom: Sample output from the HMM, with the initial of the location across time on the x-axis, the initial of each device on the y-axis, and their state across time (gray means online).}
-\end{figure}
-
-HMMs being generative probabilistic models, they allow the generation of observation sequences given the parameters of the model.
-Figure~\ref{fig:hmm} shows a possible user's model along with a sample observation sequence $O$ generated from it.
-
-Even though each user's behavior is discretized, they start at different times. 
-This way, even though the time step \tuser is fixed, devices enter and leave the system at different points in the continuous time.
-
-\subsubsection{Experimental parameters} % (fold)
-\label{ssub:experimental_parameters}
-
-All our experiments were conducted with 25 users participating in \name. 
-The files exchanged are a collection of 12 real ones, ranging from 6KB to 640MB.
-
-\paragraph*{Random Peer Sampling} It has three parameters: the period between two views exchange \trps, set to 400ms, the size of the exchanged views (6) and the size of the devices' view \rpsview, set to 30.
-Using a bigger view would result in more descriptors choice when crafting routes, but their descriptor would be more stale: descriptors in a view have a lifetime of $|\rpsview| * \trps$ seconds on average.
-
-\paragraph*{Overlay} The \squad overlay has two parameters: the fanout of the gossip exchange when a device has new information to share, set to 3, and the initial length of the sequence $S$ (cf.
-section~\ref{ssec:device_availability}), set to 50.
-The latter provides initial knowledge to \squad members: their peers addresses, among with an estimate of the user's prior behavior.
-
-\paragraph*{\ac{SPOR}} We used a constant amount of 3 layers per routes (excluding the final, destination layer),
-and a constant number of peers per layer $w_\layer$ of 16.
-The latter heavily influences both the network overhead (the more, the bigger the headers), and the routes' availability (more peers means a better probability that at least one peer is online in a layer).
-The default availability threshold $\theta$ is $10^-3$.
-
-\paragraph*{File transfer} The main parameter here is the chunk size \chunksize, that was set to 512KB, which is considered, in BitTorrent, to be a good trade-off between network efficiency and number of chunks.
-The other parameter, \tupload, that is the period between two chunk sends, was empirically set to 500ms.
-
-\paragraph*{Users' behavior} We set \tuser, the time between two user actions, to 3s.
-
-\trps, \tupload and \tuser are correlated, but otherwise meaningless since \tuser is artificial. 
-Their values were thus empirically chosen to balance efficiency, network traffic and the experiments' duration.
-
-Finally, the experiments had a timeout \texp of 15 minutes. 
-We observed that downloads---however big---usually succeeded long before this time, or did not succeed whatever time was given to them.
-
-\subsubsection{Experimental process} % (fold)
-\label{ssub:experimental_process}
-
-The experiments are conducted as follows: 
-\begin{itemize}
-  \item A first initialization procedure takes care of bootstrapping the users and their devices. 
-  A scheduler is started for each user, that will turn devices on or off throughout the experiment according to the models discussed in~\ref{ssub:simulating_user_behavior};
-  \item Each file is initiated in turn: a couple $(d_s, d_r)$ of online devices from different users is chosen.
-  The sender $d_s$ is requested to initialize file upload---chunks hashes and routes take some time to compute---and answers with \finfo, including reply headers. 
-  \finfo is given to $d_r$ as it is asked to receive $f$. It replies with forward headers, that are given to $d_s$. The exchange starts;
-  \item We wait for this initialization process to end before starting to send the next file;
-  \item Once all 12 files are initiated; we wait for the \texp timeout, unless all files have successfully completed their transfer, 
-  in which case we early abort. This process takes up to a minute.
-\end{itemize}
-
-\begin{figure}[t]
-  \centering
-  %\def\svgwidth{0.8\columnwidth}
-  \includegraphics[width=\columnwidth]{figures/bw_and_pending_files.pdf}
-
-  \caption{\label{fig:bw_and_pending_files}Timeline of one experiment's traffic.
-  In gray: number of pending file exchanges; in black: mean outbound traffic (kB) per node per second.}
-\end{figure}
-
-Figure~\ref{fig:bw_and_pending_files} reads the timeline of a typical experiment by showing, 
-in gray, the number of simultaneous file exchanges and, in black, the average outbound traffic per node per second.
-The initialization phase is not part of the graph. 
-In this particular experiment, all files were successfully exchanged.
-
-We see that file transfers get started in turn, but that some complete fast, such that the maximum number of simultaneous downloads only rises to 8.
-It quickly drops to 4 at 160s, but the last files take another 300s to finish. 
-Those last files are either the biggest ones, or are exchanged between poorly connected nodes that tend not to be online at the same time.
-
-The dark plot shows that the traffic is uneven, with frequent spikes in the MB/s order. 
-The traffic is obviously dependent on the number of pending exchanges, 
-but remains around 600 kB/s on average, even when 8 files are concurrently downloading.
-Knowing that a chunk message weighs 516 kB, we deduce that nodes exchange an average of one chunk per second when the traffic is substantial.
-We also see that the traffic remains non-null long after the last file finished downloading it. 
-Indeed, some stale messages can remain in the buffers of poorly connected devices for an unbounded period of time.
-This experiment finished early aborting past 600s.
-
-% subsubsection experimental_process (end)
-
-\subsection{File transfer}
-\label{sub:file_transfer}
-
-\begin{figure}[t]
-  \centering
-  %\def\svgwidth{0.8\columnwidth}
-  \includegraphics[width=0.9\columnwidth]{figures/completion_vs_size.pdf}
-
-  \caption{\label{fig:completion_vs_size}
-  Success rate of the file transfer ordered by size of file over 30 experiments.
-  The dotted black line shows the overall success rate of 94.4\%.}
-\end{figure}
-
-Using the previous parameters, we performed our experiment 30 times, yielding 360 file exchanges.
-Plots show the aggregation of the results from all experiments, which alleviates the high variability of the stochastic processes involved (most notably the devices' churn).
-
-Figure~\ref{fig:completion_vs_size} first shows the success rate of each exchanged file over the 30 experiments.
-The dotted black line shows the overall success rate: 94.4\%. 
-Each bar shows the individual success rate of our test files, with their size on the x-axis.
-As one can see, the success rate drops as files get bigger.
-Files bigger than 112MB show a success rate between 80 and 90\%, while all lighter files are successfully transfered in 90\% of the cases at least.
-
-% \subsubsection{Comparison to churnful Tor} % (fold)
-% \label{ssub:comparison_to_churnful_tor}
-
-To get a rough baseline to evaluate the need for \iac{SPOR}, 
-we attempt the same experiment as before, but this time using an availability threshold $\theta = 1$ (cf~\ref{SPOR}): 
-layers only contain one random descriptor, as a naive approximation of
-classical \acl{OR}. 
-Over 5 experiments, we observed a file transfer success rate of 41.7\%, which is far below our results when leveraging on \ac{SPOR}.
-
-% subsubsection comparison_to_churnful_tor (end)
-
-%\subsubsection{Traffic and availability} % (fold)
-\label{ssub:traffic_and_availability}
-
-\begin{figure}[t]
-  \centering
-  %\def\svgwidth{0.8\columnwidth}
-  \includegraphics[width=0.9\columnwidth]{figures/avail.pdf}
-
-  \caption{\label{fig:completion_vs_size}
-  Availability of devices and number of messages waiting for reception.}
-\end{figure}
-
-% subsubsection traffic_and_availability (end)
-
-% \begin{figure}[t]
-%   \centering
-%   %\def\svgwidth{0.8\columnwidth}
-%   \includegraphics[width=0.8\columnwidth]{figures/logistic_many_0-001.pdf}
-
-%   \caption{\label{fig:logistic}
-%   Logistic regression of the success rate as a function of the file size using the default parameters.}
-% \end{figure}
-
-% Figure~\ref{fig:logistic} shows the logistic regression of the success rate as a function of the files' size. 
-% This regression is good candidate to describe binary stochastic processes as a function of a dependent variable,
-% and is often used in epidemics prediction, economics, and even marketing.
-% Simply put, given $X$ (in our case, the size of each transfered file) and $y$ (the outcome of the transfer: success or failure), 
-% the regressor estimates the coefficient $k$ and the mid-point $x_0$ of the logistic function defined as follows:
-
-% $$ f(x) = \frac{1}{1 + e^{-k \cdot x + x_0 }} $$
-
-% Because it sets the top (100\%) and bottom (0\%) values as asymptotes, 
-% logistic regression does not yield very optimistic success rates at the beginning,
-% but its midpoint $x_0$ tends to be very accurate even with a low quantity of training samples.
-% \commentAL{Yes indeed, very pessimistic, where is our 94\%!? I want to make a CDF also.}
-
-% In our case, $f(x)$ reads the probability that a file exchange fails given its size. 
-% The plot reads that files below 319MB have more than 90\% chances of being successfully exchanged.
-% The probability falls as the file gets bigger, such that a 1,O43MB has 50\% chances of successful transfer (see $x_0$).
-
-% ------------------
-
-% \subsection{Shortcomings} % (fold)
-% \label{sub:shortcomings}
-
-% There are several aspects in \name that can endanger its security or hinder its performance.
-% First off, we study the RPS and its capacity to provide a random subset of the whole participants list.
-
-% subsection shortcomings (end)
-
-% In the following, we perform two types of experiments: 
-% section~\ref{sub:predictive_onion_routes_creation} evaluates the establishment of PORs, while section~\ref{sub:file_transfer} handles file transfer.
-% For that reason, they used different parameter sets.
-
-% \paragraph*{PORs creation}
-% Figure \ref{fig:success_rate_vs_t} come from the same data, with 10 experiments per set of settings.
-% $\theta$, the threshold of the probability that all nodes fail at once, takes the following values: $[0.1, 0.01, 0.001, 0.0001]$.
-% $L$, the number of layers constituting a route, takes the following values: $[3, 5, 7]$.
-% The time since route establishment goes from 1 to 10 with  unit step.
-% It is measured in time periods $T$, the interval at which users change the connection state of their devices.
-% An experiment consisted in $L*5$ users, where we randomly picked pairs of users to compute 20 routes.
-% Hence, each point on the top of figure~\ref{fig:success_rate_vs_t} is the average of 3000 layers size; 
-% each point on the bottom is the availability rate over 200 routes.
-
-% \paragraph*{File exchange}
-% In section~\ref{sub:file_transfer}, we fix the routes' creation parameters: $\theta=10^-3$, $L=3$.
-% The number of users is set to 20, and the number of file exchange per experiment to 10.
-% We use a constant file chunk size of 512kB, a constant header size of 100kB, and a constant bandwidth per link of 128kB/s.
-
-% \subsection{Predictive Onion Routes creation} % (fold)
-% \label{sub:predictive_onion_routes_creation}
-
-% We first measure the influence of the parameter $\theta$ on the number of nodes per layer on the top of figure~\ref{fig:success_rate_vs_t}, by displaying average and standard deviation of the number of nodes for $\theta=[10^{-4}, 10^{-3}, 10^{-2}, 10^{-1}]$ (the other experiment parameters are listed in section~\ref{ssub:experimental_parameters}).
-% As we can see, the number of devices per layer logarithmically decreases as we relax the constraint on the layer's availability.
-% The mean number of devices per layer lies between 2 and 6.
-% Still, the number of nodes per layer is very variable: at $\theta=10^{-4}$, values range from 2 to 11, with a standard deviation of 1.44.
-
-% \begin{figure}[t]
-% \centering
-% \includegraphics[width=0.7\columnwidth]{figures/nodes_per_layer_vs_theta.pdf}
-% \vspace{1ex}
-% \includegraphics[width=0.9\columnwidth]{figures/success_rate_vs_t.pdf}
-% \caption{\label{fig:success_rate_vs_t}On top: Number of nodes per layer of POR as a function of the parameter $\theta$ (the maximal probability that all nodes in a layer fail at once).
-The number of nodes logarithmically decreases as we relax the $\theta$ constraint.
-On bottom: Availability rate of routes as a function of the time since the route establishment, for several values of the parameters $\theta$ (the maximal probability that all nodes in a layer fail at once) and $L$ (the number of layers in the route).}
-% \end{figure}
-
-% We now study the influence of the parameters on the future availability of the routes in figure~\ref{fig:success_rate_vs_t}.
-% We consider a route available if at least one node per layer is online at this time.
-% The plots reads the mean availability of routes as a function of the time since the route's establishment, for every couple of parameters $(\theta, L)$.
-% First of all, we observe that time has a negligible impact on the availability of routes. 
-% This shows, as was stated in section~\ref{para:predicting future behavior}, that the prediction that devices make of behavior at $t+1$ is a good enough estimator for $t+i$.
-% We also see that $\theta$ has a big impact on the mean availability and its variability.
-% Still, $\theta\in\{10^-4, 10^-3\}$ allows highly available routes with an average availability of 100\% and 99.5\% respectively.
-% Combined with the results from figure~\ref{fig:success_rate_vs_t}, it means that routes will need an average of 5-6 devices per layer to be highly available.
-% Finally, increasing $L$ logically hinders the results when using low-availability layers.
-% \\
-
-% We showed that creating reliable onion routes using a backbone of unreliable nodes is feasible by using predictive algorithms.
-% The counterpart is that messages header size grows with the number of layers and the number of devices per layer.
-
-% Considering that most onion routing solutions use a statically defined message size to avoid information leakage, a bigger header means less space for the payload in each message.
-The more reliable the route, the bigger the number of messages per file.
-There is a trade-off between route reliability and network traffic.
-
-% \subsection{File transfer time} % (fold)
-% \label{sub:file_transfer}
-
-% To assess the efficiency of \name, we did several file exchanges with fixed parameters and a random file size between 5MB and 500MB.
-% By performing 20 experiments using the parameters described in \ref{ssub:experimental_parameters}, we obtained traces for 200 file exchanges.
-% All files reached their destination successfully.
-
-% \begin{figure}[t]
-% \centering
-% \includegraphics[width=0.7\columnwidth]{figures/transfer_time_vs_size.pdf}
-
-% \caption{\label{fig:transfer_time_vs_size}Files' transfer time as a function of their size, along with a log-linear regression of the same data.}
-% \end{figure}
-
-% Figure~\ref{fig:transfer_time_vs_size} shows the results of this experiment: it plots the transfer time as a function of the file size.
-File size is binned into 20 bins, making the series of points representing the average transfer time per bin with standard deviation bars.
-% We fitted a log-linear regression to this plot, displayed as a curve.
-% It shows that transfer time increases less fast that the file size.
-
-% Absolute time values are meaningless here: our system was evaluated on a single machine and on a single process.
-The code execution was not parallel, and only one device was executing at any point in time.
-
-% Still, we investigated the message transmission.
-In this simulation, 145172 chunks were sent, and 141276 ACKs were received: 6.00\% of the chunks were lost in transit.
-A chunk took an average of 56s $\pm$ 36s to reach its destination, while ACKs to 48s $\pm$ 33s to do so.
-This is explained mostly by devices falling offline between the time they receive a message and the time they forward it.
-
-% We now understand the log-linear curve and it's big initial slope: messages spend a long time in transit, but sending messages in parallel does not impact this time.
-Even small files thus need a lot of time to transfer, while bigger files do not suffer more than small files from the messages delay.
-% \\
-
-% Overall, we succeeded in creating a reliable and secure file transfer protocol over an underlying network of unreliable, low-end devices.
-% Its performance could be enhanced by taking interest in bottlenecks in the messages transmission, i.e. scheduling messages in a similar predictive manner as we planned routes creation.
-
-% subsection file_transfer (end)
+\dots

### 2020-03-23 paper/intro.tex
Kills abstract, to-the-point intro, better title

@@
 % What's the problem?
+
+First, we provide an extension to the Sphinx mix-header format~\cite{Sphinx} 
+that adds several nodes per layer.
+We call this extension SphinxES.
+In essence, this makes it a source-routed random-walk.
+
+The sender can populate the layers according to different optimizations.
+For instance, the sender can populate the layers to minimize the risk of 
+failure of a complete layer to minimize the impact of high churn in a 
+network.
+Another example is that the sender distribute nodes over the layers to maximize 
+the sum of bandwidth over the nodes of each layer.
+This would optimize for throughput.
+
+Second, we provide a way for messaging services, like Signal, to use SphinxES 
+to relay messages over the devices in \iac{P2P} network with high churn.
+We call this the \ac{SPOR} protocol.
+
+Third, we provide a higher-level protocol\footnote{%
+  If SphinxES is IP, this protocol would be TCP.
+} for file transfers.
+We call this the \ac{SPORES} protocol.
+
+\endinput
 

### 2020-03-24 paper/security-discussion.tex
Edits sphinxes and sphinxes-security

@@
 \end{enumerate*}
-
-\paragraph*{Security of \Sphinxes}
-
-There are two changes that we have made that must be analysed.
-We changed the key agreement from a pure \ac{DHKE}, \ie based on the \ac{DH} 
-assumption, to one containing an indirection.
-We also changed from the classical \ac{OR} of a fixed path with one node per 
-layer to a set of alternative nodes per layer.
-
-The first change:
-The confidentiality of the key previously rested entirely on the \ac{DH} 
-assumption (\(\alpha\) in the header).
-Now it also rests on the security of the \ac{PRP} \(\prp'\) (\(C\) in the 
-header).
-The integrity is still reduced to the security of the \ac{MAC} \(\mac\) 
-(\(\gamma\) in the header).
-We still achieve the bitwise unlinkability since \(C\) is replaced at each 
-layer and the next \(C\) is hidden inside the header --- which otherwise 
-remains identical to that of \ac{Sphinx}.
-
-The second change is that we use several nodes per layer as opposed to only 
-one.
-The proofs of \ac{Sphinx} rest on the results of \textcite{CLOnionRouting}, which 
-are results for classical \ac{OR} with only one node per layer.
-
-Analogously to classical \ac{OR}, we also reveal the previous and next sets of 
-nodes to the adversary. We note that this is actually quite natural as a 
-malicious adversary can drop any incoming traffic to a router and wait for the 
-timeout and
-retransmission, \ie when the 
-node has selected a new node from the next layer and retried sending.
-As such, the adversary can learn all nodes in the layer --- just as for 
-classical \ac{OR}, regardless of whether the set making up a layer contains a
-single or several nodes.
-
-With these arguments, we believe that \Sphinxes inherits the \ac{UC} security 
-properties of \ac{Sphinx}. %, however, this should be formally analysed.
 

### 2020-03-24 paper/sphinxes-security.tex
Edits sphinxes and sphinxes-security

--- 2019-05-23 spores-protocol-paper/security-discussion.tex
@@
-\section{Security Discussion}%
-\label{security-discussion}
-
-%\sonja{will add some framing about us composing and modifying parts that
-%  have security proofs for their original and individual versions and needing to evaluate the resulting s%chemes}
-
-The \ac{SPORES} system is composed of several parts, each of which requires its 
-own security analysis.
-We thus primarily need to ensure that
-\begin{enumerate*}
-\item \Sphinxes (\cref{Sphinxes}) preserves the properties of 
-  \textcite{CLOnionRouting} and \textcite{Sphinx} yielding \ac{UC}-secure 
-  \ac{OR};
-\item the node selection (\ac{SPOR}, \cref{SPOR}) does not introduce any 
-  advantage for the adversary;
-\item the availability information introduced and disseminated to deal with 
-  churn satisfies the device-unlinkability property we defined in 
-  \cref{system-model}; and that
-\item the composed protocol (\ac{SPORES}, \cref{ssec:spores_file_exchange_through_probabilistic_onion_routes}) provides the desired 
-  security properties defined in \cref{system-model}, \ie
-  privacy and robustness (packet re-ordering and drops).
-\end{enumerate*}
-
-\paragraph*{Security of \Sphinxes}
+\section{SphinxES security analysis}%
+\label{SphinxES-security}
 
@@
 
-With these arguments, we believe that \Sphinxes inherits the \ac{UC} security 
+With these arguments, we believe that SphinxES inherits the \ac{UC} security 
 properties of \ac{Sphinx}. %, however, this should be formally analysed.
-
-\paragraph*{Security of \acs*{SPOR}, node selection}
-
-\sonja{will motivate using the survey/taxonomy}
-The onion route provides unlinkability between Alice and Bob as long as the 
-message passes at least one honest node on the route.
-This means that any adversary, say Eve,  must ensure that the message passes 
-through an adversarial node on each layer.
-The probability of successful attack is proportional to Eve's size in the 
-network, \ie \(f_A = \frac{|D_A|}{|D|}\).
-\daniel{Check that we still use the \(D_i\) notation for the devices in 
-  \(i\)'s squad.}
-If we assume that \(\GetRandomNode\) returns nodes with close to the uniform 
-distribution, then the \(\nu w_L\) nodes selected is expected to contain \(f_A 
-  \nu w_L\) nodes controlled by Eve.
-If \(f_A \nu w_L < \nu\), then Eve is not expected to be present on every layer 
-of the route.
-Considering how \ac{SPOR} distributed the \(\nu w_L\) selected nodes, Eve's 
-best strategy is to have high-availability nodes --- assume that 
-\(\avail_{D_E}(t) = 1\) for all Eve's devices \(D_E\).
-This way, Eve's devices will be distributed evenly across all layers (provided 
-she controls enough of the selected devices).
-To succeed, Eve must be chosen in the first layer, the probability of which 
-will be \(\frac{f_A}{w_L}\) (for a passive adversary and \(1\) for an active).
-If one of her devices is chosen in the first layer, then she can choose one of 
-her own devices in the next layer.
-If she is present on every layer, she can ensure she relays the message all the 
-way to Bob.
-In summary, her probability of success is \(\frac{1}{w_L} (1-(1-f_A)^{(w_L-1) 
-    \nu +1})\) (or without the \(\frac{1}{w_L}\) factor for an active 
-adversary), which can be compared to \((f_A)^\nu\) for classical \ac{OR} (for 
-both active and passive adversaries).
-\sonja{compare the chance of being present on every
-  layer AND chosen in the first layer to regular onion routing where she
-  needs to be the (sole) node on each layer. Are we doing
-  better/worse/the same?}
-\daniel{Hard to say at this time of night \dots}
-
-However, Eve can only be certain that she has relayed the message from Alice to 
-Bob if \(\nu = r\), \ie she receives the message from Alice, relays it \(r-1\) 
-times and lastly sends it to Bob.
-If \(\nu < r\) though, then, due to the indistinguishability and unlinkability 
-properties of Sphinxes (inherited from \ac{Sphinx}), Eve cannot know for certain if 
-Alice is the first node and Bob is the last node. \sonja{but what can
-  she learn/guess?}
-\daniel{For all she knows there might be another node at either the 
-  beginning or the end, she cannot tell.}
-
-Finally, we must point out that the \(\GetRandomNode\) algorithm must be 
-privacy preserving.
-Consider the following scenario.
-Alice requests a set of peers, say \(\{d_1, \dotsc, d_n\}\).
-If \(d_i\) interacts in each sampling operation resulting in \(d_i\) being in 
-the sample, then \(d_i\) can generate a new public key \(\pk_d^{(j)}\) for each 
-sample \(j\).
-This means that, if Alice sampled \(d_i\), she knows the public key 
-\(\pk_i^{(j)}\), and if \(d_i\) knows it is included in Alice's sample, then it 
-will also know a route belongs to Alice whenever \(\pk_i^{(j)}\) is used to 
-encrypt the header.
-(This follows from the fact that Sphinxes is source-routed.)
-\Ie every node on Alice's route would know that Alice is either the source or 
-the destination.
-
-Although the requirements of the \ac{RPS} being uniformly randomly
-distributed and privacy-preserving are not easily met in practice,
-there are some promising candidates~\cite[\eg][]{Octopus,BrahmsRPS}.
-\name does not put any other constraints on the \ac{RPS} used.
-
-\paragraph*{Device unlinkability}
-
-Alice transfers a file \(f\) to Bob during the time interval 
-\(\interval{t_0}{t_1}\).
-We denote the set of Alice's devices as \(D_A\) and Bob's as \(D_B\).
-Bob wants to compute an estimate \(\hat D_A\) which is as close to \(D_A\) as 
-possible.
-
-At this point, Bob knows that \emph{at least one} of Alice's devices must have 
-been online at any given time in \(\interval{t_0}{t_1}\).
-We can also assume that Bob knows all data from the \ac{RPS}, \ie the \((d, 
-  \pk_d, \avail_d)\) tuple (see \cref{SPOR}) of \emph{every device that was 
-  online at some point during \(\interval{t_0}{t_1}\)}.
-Let \(\A_{\interval{t_0}{t_1}}\subseteq \N\times \G^*\times (\RR\to 
-  \interval{0}{1})\) denote the set of those tuples.
-Thus Bob can approximate \(D_A\) by \(\hat D_A \gets 
-  \A_{\interval{t_0}{t_1}}\cap D_B\).
-
-When Alice and Bob interact the next time, either Alice sends a file \(f'\) to 
-Bob or Bob sends a file \(f'\) to Alice, then Bob can do the same again:
-\(\hat D_A' \gets \A_{\interval{t_0'}{t_1'}} \cap D_B\).
-If at least one of \(d, \pk_d, \avail_d\) remains constant, Bob can use that to 
-improve his approximation.
-Say that \(\avail_d\) remains constant.
-Then Bob can improve his approximation to \(\hat D_A \cap_{\avail_d} 
-  \hat{D}_A'\), where \(\cap_{\avail_d}\) is the intersection which only 
-considers the attribute \(\avail_d\).
-Even if \(\avail_d\) is not constant, its variation might stay inside some 
-\(\epsilon\)-neighbourhood, and if \(\epsilon\) is small enough, \(\avail_d\) 
-might still be used to distinguish Alice.
-The same applies for \(d\).
-(\(\pk_d\) can be regularly updated.)
-
-With an inaccurate availability function, \(\avail\), this will not be a 
-problem as there will be many others (as the system scales) that share the 
-same availability distribution.
-With more accurate availability estimates we would have to employ techniques 
-like \ac{DP} to ensure that Alice's availability distribution is not
-(too close to)
-unique.
-
-\paragraph*{Robustness}
-
-Stateless routing can result in re-ordered chunks or packets, and
-chunks received on different devices of a user's \squad. From \ac{Sphinx},
-we inherit unique IDs for each mix packet.
-If we provide the mix packets as an ordered list when we communicate them 
-out-of-band together with the metadata of the file and they are used in that 
-same order, then we can use those IDs to re-order chunks if need be.
-The \squad overlay handles intra-squad device 
-coordination.
-We ensure liveness by acknowledgments and timeouts (as detailed in 
-\cref{sec:squad_overlay}), despite the possibility of \squad devices
-going offline during transfer or other node or link failures.
-
-\paragraph*{Extended adversary model}%
-\label{security-limitations}
-
-A global, passive, network-observing adversary can of course do
-statistical disclosure attacks to eventually learn who communicates
-with whom~\cite{StatisticalDisclosureAttacks}. There are also denial
-of service attacks that can lead to the adversary learning more from
-the system~\cite{DenialOfSecurity}.  As mentioned in
-\cref{system-model}, we share the adversary model with Tor
-%and Sphinx
-and thus exclude a global passive adversary. Our focus is on
-protecting Alice and Bob from each other and from others who also
-participate as nodes in the network, not on protecting them from
-surveillance. Nevertheless, we offer some reflections on such an
-adversary. We hypothesize that our stateless and redundant design
-might yield some advantages over classical \ac{OR}. For
-example, no control messages are sent back to the source if the
-adversary has introduced an error.  \sonja{``But these advantages will
-  only postpone the success of the attack, eventually even our
-  protocol must resend.'' why?}  \daniel{Due to statistics. We should 
-  also look into
-  this denial of security.} Another example is that the source-bounded
-random-walk and new routes for file chunks make tracking more
-difficult than with regular onion routing circuits. A drawback, however, is
-that since the chunks can take several paths from source to destination, the source 
-will send and the destination will receive more traffic than other nodes in the 
-network~\cite{RoutingSurveyAnonymousProtocols}. However, this is mitigated by the fact that the source and 
-destination can be several different devices --- \ie from the \squads.
-
-We would also like to point out that the
-vulnerability to a global passive attacker is not inherent in Sphinx
-or \Sphinxes, but can be caused by the way they are applied, \ie the
-traffic sent. If performance and resource consumption were not an
-issue, batched and well-timed message or file transfer by all nodes
-would render traffic analysis less efficient. Concretely, \Ac{SPORES} inherits 
-the security properties from \Sphinxes and \ac{SPOR}.
-However, both \Sphinxes and \ac{SPOR} can be used with any mixing strategy, and 
-the security they provide is as secure as the mixing strategy (or flushing 
-algorithm) allows.
-Since \ac{SPORES} is a fully-fledged system, it must make a concrete choice for 
-the mixing strategy.
-Since \ac{SPORES} aims at low latency, routers do not batch and mix incoming 
-messages; they immediately forward any messages.
-This puts \ac{SPORES} in the same position as Tor, \ie more vulnerable to 
-traffic analysis than batching mix-nets~\cite{RoutingSurveyAnonymousProtocols} 
-\daniel{we should probably look for the original papers} --- this 
-vulnerability is inherited from the mixing strategy.
-
-% \daniel{Predecessor attacks: random walk protocols has the problem that 
-%   the adversary can see the initiator (statistically) more often than the other 
-%   nodes, and can thus identify the 
-%   source~\cite{RoutingSurveyAnonymousProtocols}.
-%   Our protocol is a \enquote{bounded} random walk, \ie within limits.}

### 2020-03-24 paper/approach.tex
Edits all forms of SphinxES, \Sphinxes, \ac{Sphinx} etc.

@@
   \ac{Sphinx} mix-header format, which we extend to allow for the
-  changes above, described in \cref{Sphinxes}.
+  changes above, described in \cref{SphinxES}.
 
@@
 %   \ac{Sphinx}, with some modification to allow for the
-%   changes above, described in \cref{Sphinxes}.
+%   changes above, described in \cref{SphinxES}.
 % \end{description}
@@
 As depicted in Figure~\ref{fig:outline}, \ac{SPORES} relies on a predictive and probabilistic onion routing protocol (\ac{SPOR}).
-\ac{SPOR} in turn combines a multi-set mix-header format (\Sphinxes) together with a node selection protocol that exploits decentralized prediction regarding node availability to optimize the reliability of \Sphinxes without jeopardizing its security properties.
-%% Particularly, \sphinxes (\cref{Sphinxes}), is an adaptation of the 
+\ac{SPOR} in turn combines a multi-set mix-header format (SphinxES) together with a node selection protocol that exploits decentralized prediction regarding node availability to optimize the reliability of SphinxES without jeopardizing its security properties.
+%% Particularly, \sphinxes (\cref{SphinxES}), is an adaptation of the 
 %% \sonja{do we apply all categories here?} \ac{Sphinx} mix-header format.
@@
 %% header format, it only imposes some restrictions in the above categories.
-\Sphinxes (Figure~\ref{fig:outline} \ding{202}) provides, just as \ac{Sphinx}, unidirectional (network structure), 
+SphinxES (Figure~\ref{fig:outline} \ding{202}) provides, just as \ac{Sphinx}, unidirectional (network structure), 
 message-based (performance) communication.
-But unlike \ac{Sphinx}, \Sphinxes is an hybrid source-hop-by-hop routed, and a
+But unlike \ac{Sphinx}, SphinxES is an hybrid source-hop-by-hop routed, and a
 source-bounded random walk (communication 
-model). \Sphinxes relies on a flat routing-topology (network structure) with fair 
+model). SphinxES relies on a flat routing-topology (network structure) with fair 
 scheduling (communication model) --- as all packets are indistinguishable they 
 must be processed on a first-in-first-out basis.
-\Sphinxes also introduces some probability to the node selection, but this is 
+SphinxES also introduces some probability to the node selection, but this is 
 only a probabilistic selection among already selected nodes and only 
@@
 
-\Sphinxes does \emph{not} introduce any restrictions on whether the network 
+SphinxES does \emph{not} introduce any restrictions on whether the network 
 topology must be fully connected or not, be asynchronous (as in \ac{Tor}) or 
@@
 
-Further, the \ac{SPOR} protocol (\cref{design}) adds node selection on top of \Sphinxes.
+Further, the \ac{SPOR} protocol (\cref{design}) adds node selection on top of SphinxES.
 The \ac{SPOR} protocol (Figure~\ref{fig:outline} \ding{203})  assumes a source of random nodes, \eg through 

### 2020-03-24 paper/intro.tex
Edits sphinxes and sphinxes-security
Edits all forms of SphinxES, \Sphinxes, \ac{Sphinx} etc.

@@
 that adds several nodes per layer.
-We call this extension SphinxES.
+We call this extension SphinxES and describe it in detail in \cref{SphinxES}.
 In essence, this makes it a source-routed random-walk.
@@
 
-  \item We propose \Sphinxes, an extension of the
+  \item We propose SphinxES, an extension of the
     \ac{Sphinx} mix-header format to set-based onion routing.
-\Sphinxes allows each layer of an onion route to contain several alternative next nodes, thus realizing a source-routed limited random-walk protocol.
+SphinxES allows each layer of an onion route to contain several alternative next nodes, thus realizing a source-routed limited random-walk protocol.
 
-  \item Building on \Sphinxes, we introduce the \ac{SPOR} %% node selection strategy for routing
+  \item Building on SphinxES, we introduce the \ac{SPOR} %% node selection strategy for routing
     protocol
@@
     \ac{RPS} protocol and availability estimates, selects nodes to populate the 
-    layers of \Sphinxes in order to maximize the availability of the route. This node selection procedure 
+    layers of SphinxES in order to maximize the availability of the route. This node selection procedure 
     yields reliable routes even in the presence of low-availability nodes while retaining the strong privacy properties of onion routing.
@@
     of its own devices, based on Markov models and \squad overlays.
-    These estimated availabilities can then be exploited by \ac{SPOR} to populate \Sphinxes.
+    These estimated availabilities can then be exploited by \ac{SPOR} to populate SphinxES.
    % \commentDaniel{We should add some more details, maybe.}
@@
 privacy properties of \name. Section~\ref{approach} describes the
-overall approach. In Section~\ref{Sphinxes}, we introduce \sphinxes. 
+overall approach. In Section~\ref{SphinxES}, we introduce \sphinxes. 
 Then, in Section~\ref{design}, we introduce the different building

### 2020-03-24 paper/spor.tex
Edits all forms of SphinxES, \Sphinxes, \ac{Sphinx} etc.

@@
 
-There are many uses of \Sphinxes, many criteria that can be used to select the 
+There are many uses of SphinxES, many criteria that can be used to select the 
 nodes in each layer.
@@
 churn, but one could equally well select nodes to maximize, \eg, bandwidth.
-We now describe a protocol, \ac{SPOR}, which uses \Sphinxes to transfer messages 
+We now describe a protocol, \ac{SPOR}, which uses SphinxES to transfer messages 
 from a source to a destination over a network of nodes with high churn.
@@
 The \(\GetRandomNode\) algorithm can be instantiated using \eg
-Octopus~\cite{Octopus}. Its function is analogous to 
-Tor's authoritative directory servers, but we need a decentralized system. 
-We will treat \(\avail_d\) in \cref{sec:squad_overlay}.
+Octopus~\cite{Octopus}. Its function is analogous to \acg{Tor} authoritative 
+directory servers, but we need a decentralized system. We will treat 
+\(\avail_d\) in \cref{sec:squad_overlay}.
 

### 2020-03-24 paper/spor-security.tex
Moves SPOR up to after SphinxES

--- 2020-03-24 paper/security-discussion.tex
@@
-\section{Security Discussion}%
-\label{security-discussion}
+\section{\acs*{SPOR} security analysis}%
+\label{spor-security}
 
-%\sonja{will add some framing about us composing and modifying parts that
-%  have security proofs for their original and individual versions and needing to evaluate the resulting s%chemes}
-
-The \ac{SPORES} system is composed of several parts, each of which requires its 
-own security analysis.
-We thus primarily need to ensure that
-\begin{enumerate*}
-\item \Sphinxes (\cref{Sphinxes}) preserves the properties of 
-  \textcite{CLOnionRouting} and \textcite{Sphinx} yielding \ac{UC}-secure 
-  \ac{OR};
-\item the node selection (\ac{SPOR}, \cref{SPOR}) does not introduce any 
-  advantage for the adversary;
-\item the availability information introduced and disseminated to deal with 
-  churn satisfies the device-unlinkability property we defined in 
-  \cref{system-model}; and that
-\item the composed protocol (\ac{SPORES}, \cref{ssec:spores_file_exchange_through_probabilistic_onion_routes}) provides the desired 
-  security properties defined in \cref{system-model}, \ie
-  privacy and robustness (packet re-ordering and drops).
-\end{enumerate*}
-
-\paragraph*{Security of \acs*{SPOR}, node selection}
+\paragraph*{Node selection}
 
@@
 If \(\nu < r\) though, then, due to the indistinguishability and unlinkability 
-properties of Sphinxes (inherited from \ac{Sphinx}), Eve cannot know for certain if 
+properties of SphinxES (inherited from \ac{Sphinx}), Eve cannot know for certain if 
 Alice is the first node and Bob is the last node. \sonja{but what can
@@
 encrypt the header.
-(This follows from the fact that Sphinxes is source-routed.)
+(This follows from the fact that SphinxES is source-routed.)
 \Ie every node on Alice's route would know that Alice is either the source or 
@@
 vulnerability to a global passive attacker is not inherent in Sphinx
-or \Sphinxes, but can be caused by the way they are applied, \ie the
+or SphinxES, but can be caused by the way they are applied, \ie the
 traffic sent. If performance and resource consumption were not an
@@
 would render traffic analysis less efficient. Concretely, \Ac{SPORES} inherits 
-the security properties from \Sphinxes and \ac{SPOR}.
-However, both \Sphinxes and \ac{SPOR} can be used with any mixing strategy, and 
+the security properties from SphinxES and \ac{SPOR}.
+However, both SphinxES and \ac{SPOR} can be used with any mixing strategy, and 
 the security they provide is as secure as the mixing strategy (or flushing 

### 2020-03-27 spores-protocol-paper/reviews/rebuttal-ndss.md

We would like to thank the reviewers for their constructive reviews. We structured our response by topic, referring to reviewers as RA and RB.

We agree with your joint suggestions for presentation (operational diagram, roles of protocols/subsystems; overview in text, details in appendix) and reference to Weiser; we will update the paper accordingly.

Regarding the concern about privacy threats from availability prediction data: @RB the data used for prediction is stored locally, only the predicted availability can be sampled. 
@RA leaks from prediction are analyzed in Section VI  (Device unlinkability), albeit for the worst case of extremely detailed availability data. In practice, leaks are constrained by separate address spaces (NFC for the out-of-band set-up step, and IP for availability sampling), public keys which can be replaced regularly, and availability prediction being coarse-grained and thus not unique. There are corner cases that allow for a link between IP addresses and devices and then potentially owners; for example when the adversary is behind the same NAT as the target, but even those are short-lived due to the coarse-grained prediction.

@RB on onion routing without circuits: this is likely a terminology issue. Onion routing is associated with circuits as Tor uses them, but it is not included in the definition in reference [21].  While Tor establishes circuits by maintaining a routing table at relays according to the onion layers, SphinxES (and Sphinx) defines a header format that encapsulates the routing information, hence the statelessness of SP²ORES.

@RB about global v. local sampling, we sample globally to achieve anonymity: if we only used our own devices, we would expose whom we are communicating with through our network metadata and Alice would reveal her devices to Bob.

Both reviewers expressed concerns regarding the realism of our evaluation. We have considered data collections such as Crawdad, but the data sets are not applicable as-is to our problem. Mobility is not a direct estimator of availability (e.g. mobile phones are available even during transitions), and it does not capture the interaction of a user with several of her devices, an emergent domain for which field data does not exist yet. We will keep an eye on data collections for any more directly applicable traces or empirical studies on availability of devices and their relation to data on mobility and other traces.

In the absence of data, HMM are commonly used for simulating user behavior. Should user behavior diverge markedly, however, the prediction module we use (based on plain Markov Chains) could be exchanged for one adapted to the scenario, for instance using privacy-preserving decentralized machine learning [Bellet, Guerraoui, et al, 2018].

@RB We agree that adapting our Docker setup to emulate more complex network properties and energy constraints could enrich our model. Our choice was to fold issues of network reliability and device resources together with device availability, considering that a poorly connected device is in effect only intermittently available. We believe that this provides an appropriate approximation for our experimental aims.

#Wannabe final version:

We would like to thank the reviewers for their constructive reviews. We structured our response by topic, referring to reviewers as RA and RB.

We agree with your joint suggestions for presentation (operational diagram, roles of protocols/subsystems; overview in text, details in appendix) and reference to Weiser; we will update the paper accordingly.

Regarding the concern about privacy threats from availability prediction data: @RB the data used for prediction is stored locally, only the predicted availability can be sampled. 
@RA leaks from prediction are analyzed in Section VI  (Device unlinkability), albeit for the worst case of extremely detailed availability data. In practice, leaks are constrained by separate address spaces (NFC for the out-of-band set-up step, and IP for availability sampling), public keys which can be replaced with configurable frequency, and availability prediction being coarse-grained and thus not unique. There are corner cases that allow for a link between IP addresses and devices and then potentially owners; for example when the adversary is behind the same NAT as the target, but even those are short-lived.

@RB on onion routing without circuits: this is likely a terminology issue. Onion routing is associated with circuits as Tor uses them, but it is not included in the definition in reference [21].  While Tor establishes circuits by maintaining a routing table at relays according to the onion layers, SphinxES defines a header format that encapsulates the routing information, hence the statelessness of SP²ORES.

@RB about global v. local sampling, we sample globally to achieve anonymity: if we only used our own devices, we would expose whom we are communicating with through our network metadata.

Both reviewers expressed concerns regarding the realism of our evaluation. We have considered data collections such as Crawdad, but the data sets are not applicable as-is to our problem. Mobility is not a direct estimator of availability (e.g. mobile phones are available even during transitions), and it does not capture the interaction of a user with several of her devices, an emergent domain for which field data does not exist yet. We will keep an eye on data collections for any more directly applicable traces or empirical studies on availability of devices and their relation to data on mobility and other traces.

In the absence of data, HMM are commonly used for simulating user behavior. Should user behavior diverge markedly, however, the prediction module we use (based on plain Markov Chains) could be exchanged for one adapted to the scenario, for instance using privacy-preserving decentralized machine learning [Bellet, Guerraoui, et al, 2018].

@RB We agree that adapting our Docker setup to emulate more complex network properties and energy constraints could enrich our model. Our choice was to fold issues of network reliability and device resources together with device availability, considering that a poorly connected device is in effect only intermittently available. We believe that this provides an appropriate approximation for our experimental aims.

-------------

[If room: In addition, devices in proximity can more easily be controlled by the same entity, thus they can more easily collude to de-anonymize the connections.]

Both reviewers expressed concerns regarding the realism of our evaluation. Mobility/connectivity datasets are not applicable as-is to our study, because they do not capture the interaction of a user with many of her devices, an emergent domain for which field data does not exist yet.
There are not a direct mapping between mobility and availability.... Mobility is not a direct indicator about availability ... Mobility is not a direct estimator of availability 
 Still, we thank you for the Crawdad pointer. OR We keep an eye on Crawdad in the hope that some dataset would be directly applicable to our work.
 [If room: we would need to make our own empirical study/a contribution.]

@RA <insert separated address spaces, short-lived public keys, coarse-grained availability, point to device unlinkability, still corner cases left that can link IP to device/owner [We must state clearly that most of the time [we don't know if it's most of the time], we **cannot** link IP to owner]>.

In the absence of data, HMM are commonly used for simulating user behavior. Should user behavior diverge markedly, however, the prediction module we use (based on plain Markov Chains) would be enriched, for instance using privacy-preserving decentralized machine learning [Bellet, Guerraoui, et al, 2018].

@RB on onion routing without circuits: this is likely a terminology issue. Onion routing is associated with circuits as Tor uses them, but it is not included in the definition in reference [CL]. Sphinx is a header format for mix networks, and SP2ORES is technically a source-bounded random walk that adapts sphinx headers for encapsulating routing information (onion routing) per packet (SP2ORES, not IP) and not per connection (circuit).
but it is not mandatory according to [CL]. While Tor pre-establishes circuits by maintaining a routing table at relays, Sphinxes defines a header format that contains all the routing information, hence the statelessness of SP²ORES.
[Encrypted Tor packets == *cells*]

We therefore simulated user behavior using Hidden Markov chains, because of [versatile/widely used/ simplicity and realism [Gambs, Killijian, Núñez del Prado Cortez, 2012]

#Answers to questions

We merged all these issues by exhibiting different levels of availability.

###- Q1,RA: Location privacy, how much info is leaked by the published prediction?

We have an implicit assumption that when Alice and Bob communicate
out-of-band they use local addresses which are unlinkable to the
addresses used on the global network (\ie where they advertise P'd).

I remember this as being emphasized in the paper, but now that I read
the system model it's very implicit. This should be fine: they use IP
for global communication and bluetooth or NFC for out-of-band. These are
different address spaces, hence according to our assumption.

We also (implicitly) assume that the network addresses are independent
of the owner's attributes --- this should be emphasized in the paper!

This is not the case for IP: GeoIP services work for this reason. \Eg if
Bob knows where Alice lives he can use GeoIP to look for IPs that are
likely Alice's. Also if Alice and Bob are on the same NATed LAN, they
will have the same global address. Then Bob can read out every entry in
the RPS that has the same IP as himself. If there are only two and he
knows that Alice is also using the service (likely if she's exchanging
out-of-band data with him), then he can be quite certain that that's
Alice. Then if the probability is quite unique he can use that as
Alice's identifier, \ie he can track her addresses later (and use GeoIP
to follow her location).

In that sense, it's better for Alice to use her 4G connection instead of
local WiFi. Since then Bob cannot know her address on the global network
--- only that she's online (this case is analysed in the security
discussion, see "Device unlinkability" there). Of course, then her
ISP/phone carrier can learn her online behaviour, but they do that
anyway. Maybe the device-to-device of 5G will break this property for
Alice.

###- Q2,RB: It's unclear how onion routing is used without circuits:

This is a problem with terminology. There's first that CL called it
onion routing. Sphinx is a mixnet header. SphinxES is too. Technically,
routing is something stateless: there are no circuits in IP. We route
packets through multiple layers, using multiple layers of encryption,
hence onion routing. The problem is that, right now, onion routing is
synonymous to Tor. Tor sets up a state at each
node, \ie the circuit setup. We contain all that data in the header of
each packet, this is inherited from mixes. This gives us larger overhead
than Tor, as Tor can send just data without headers after the circuit
setup.

So we're correct in calling it onion routing. On the other hand we're
closer to a mix-cascade in that sense, except we don't do batching,
which is characteristic for mixes. Strictly speaking, using that survey
I used to characterize our work (of which I'm not sure how much remains
in the paper), we're technically a "source-routed bounded random-walk",
or maybe "source-bounded random-walk" is better.

###- Q3,RB: How are the overheads in terms of data transmitted and power used by this system for the small personal devices people keep with them?

I don't think processing one packet is much more expensive than an HTTPS handshake. But it's of course better to know, or at least make the estimate more explicit.

###Q4,RB: Why have a global DHT with all devices instead of choosing locally?

We use  a global DHT to achieve anonymity: if we only used our own devices, we would expose whom we are communicating with through our network metadata. In addition, devices in proximity can more easily be controlled by the same entity, thus they can more easily collude to de-anonymize the connections.

###- Q5,RB: Isn't the data needed for the prediction privacy sensitive, wouldn't the system endager users' privacy?
The data doesn't leave the user's own devices. The only data that leaves is in "aggregate from" in terms of the prediction. This information can be very coarse-grained, which it is in our evaluation.

###- Q6, RA, RB:  Both reviewers expressed concerns regarding the realism of our evaluation.

(See text above)

----
v2:
We use a general model for our predictions: a Markov chain (not Hidden) where states are the bitarray denoting which devices are connected: our prediction of a future device's availability solely depends on which devices are online now, given the history of the user's behavior. Our argument is that prediction enables onion routing. If we had field data, we would choose another prediction model, e.g. Recurrent Neural Networks, that are good candidates for classifying patterns in time series.
For the evaluation, we introduced the user's location (leading to a HMM), which enabled to model fixed appliances tied to a location (i.e. more realistic connection traces than mere random).
Despite the location transition matrix being fixed for all users, devices' connectivity traces exhibit much diversity, because the number, type and connection probability of devices are all different for each user.

Our study did not consider connection unreliability or devices' scarce resources, because we collapsed these concepts with device availability: a user carrying their phone outside would have e.g. 65% of availability, because the phone's connection often drops and its resources are constrained. Using Docker to limit the resources of devices, or simulate an unreliable network with high latency would still benefit the soundness of our experiments, but certainly field data would be best.
Mobility/connectivity datasets are not applicable as-is for our study, because they do not capture the interaction of a user with many of their devices; we would need to engage in empirical experiments to get data on the emerging trend of e-squads.
Still, studies about user mobility prediction (like \url{https://crawdad.org/yonsei/lifemap/20120103/)} or connectivity over time are of interest to us, and we thank you for pointing us to Crawdad.

-----
v1:
We use a general model for our predictions: a Markov chain (not Hidden) where state are the bitarray stating which devices are connected:
our prediction of a future device's availability solely depends on which devices are online now, given the history of the user's behavior.
For the evaluation, we introduced a second stochastic process, the user's location, which enabled to model fixed appliances tied to a location.
Despite the location transition matrix being fixed for all users, devices' connectivity traces exhibit much diversity, because the number, type and connection probability of devices are all different for each user. 
We picked a Markov prediction model because it fits the simulated users behavior. If we had field  but we would strengthen our prediction with a more complex model if we had different (real world) traces of human behavior (e.g. Recurrent Neural Networks are good candidates for classifying patterns in time series).
Which leads to the question of ground data being absent from our experiments.
Mobility/connectivity datasets are not applicable as-is for our study, because they do not capture the interaction of a user with many of their devices; we would need to engage in empirical experiments to get data on the emerging trend of e-squads.
Still, studies about user mobility prediction (like \url{https://crawdad.org/yonsei/lifemap/20120103/)} or connectivity over time are of interest to us, and we thank you for pointing us to Crawdad.
Lastly, our study did not consider connection unreliability or devices' scarce resources, because we collapsed these concepts with the availability: 
a user carrying their phone outside would have e.g. 65% of availability, because the phone's connection is often dropping and its resources are constrained.
Using Docker to limit the resources of devices, or simulate an unreliable network with high latency would still benefit the soundness of our experiments.

#Adrien V1

Dear Reviewers,

Thank you for valuable comments! Notably, we understand that the relationship between SP²ORES' building blocks must be better explained (with a figure), that putting SphinxES details (Section IV) in an appendix would facilitate the presentation, and that we need to address the security risks of publicly advertising the devices' predicted availability.

We will develop on two other points: the statelessness of SP²ORES, and our evaluation testbed.

Reviewer B observed the following: "It is not clear how you use onion routing without circuits". 
In Tor, Alice creates onion routes by iteratively contacting her designated relays. The Onion Routers (OR) along the path must remember where to forward each received stream (i.e. they maintain a routing table).
Unlike it, SP²ORES builds routes by crafting a self-sufficient header beforehand, such that each OR will know where to forward each packet by simply decrypting the header.
// To enjoy sender-receiver anonymity in SP²ORES, both ends of the circuit must exchange their headers out-of-band.

You coined our evaluation optimistic, and doubted its realism. It is true that we only employ fabricated user traces (furthermore, using the same stochastic model as our prediction engine).
We aim to show that, assuming information on personal devices (such as timestamped connection/disconnection), it is possible to infer their future availability by modeling the user's behavior. 
Alas, real-world data that would fit our purpose is cruelly lacking (at least for academia). Adapting data such as wireless connectivity traces to fit our purpose (multi-device interaction over time) would by itself constitute a legitimate contribution: we firmly envisage to tackle it in the near future.

##Quotes from reviewers

###On the evaluation.

since human movements are emulated in the evaluation via a Hidden Markov Model
(HMM) and HMMs also serve as the models as to how SP$^2$ORES forms
predictive behavior.  In other words, the evaluation uses a model
that's assumed by the implementation, and thus misses how actual human
behavior (which doesn't strictly conform to HMMs) affects performance.
# @B Section VII I wonder how realistic the performance 
evaluation is. I would have liked some discussion of how the Docker instances 
can be limited to emulate lower powered devices. Also, how do you distribute 
the user's e-squads over the five machines in your evaluation. I feel like 
putting these all on the same machine will hide impacts of unreliable wireless 
channels on your results. 
# @B Section VII It would have been nice to see models of user 
mobility that are available in existing traces vs. a totally simulated 
mobility/usage pattern here. E.g., traces from CRAWDAD (\url{https://crawdad.org/)} 
may be a good starting point to create more realistic user models.

### 2020-03-27 paper/UCOR.tex

\section{\Acladj*{UC} \acl*{OR}}%
\label{UCOR}

\dots

### 2020-03-27 paper/sphinxes.tex

--- 2018-08-09 paper/sphinxes.tex
@@
 
-\section{\Sphinxes: the Sphinx header format Extended for Sets of nodes}%
-\label{Sphinxes}
+\section{SphinxES: the Sphinx header format Extended for Sets of nodes}%
+\label{SphinxES}
 
-\Textcite{Sphinx} designed \iac{UC} secure message format for mixes, called 
+\Textcite{Sphinx} designed \iacadv{UC} secure message format for mixes, called 
 Sphinx.
@@
 Sphinx only provides one node per onion layer; in this section we extend Sphinx 
-to \Sphinxes, which allows for multiple nodes per onion layer.
-(See \cref{fig:OR-POR}.)
-% AL: Bounded random-walk....
-As such, \Sphinxes could be described as a bounded random-walk protocol, \ie the 
-each node selects the next node from a set restricted by the source.
+to SphinxES, which allows for multiple nodes per onion layer.
+As such, SphinxES could be described as a source-bounded random-walk protocol, 
+\ie the each node selects the next node randomly from a set restricted by the 
+source.
 
-\begin{figure}
-  \centering
-  %  \includegraphics[width=\linewidth]{figures/OR-POR.png}
-    \includegraphics[width=0.65\linewidth]{figures/principle_SPOR.pdf}
-  \caption{\label{fig:OR-POR}%
-    Illustration of the conceptual difference between traditional onion routing 
-and mixing (OR, top) and \ac{SPOR} (bottom).
-    %\commentDaniel{This figure should be fixed, issue \#42.}
-  }
-\end{figure}
-
-\subsubsection{Overview of the Sphinx header format}
+\subsection{Overview of the Sphinx header format}
 
@@
 reader enough understanding of Sphinx to understand the changes we make to 
-achieve \Sphinxes.
+achieve SphinxES.
 For a more detailed understanding of Sphinx, we refer the reader to the 
@@
 
-\subsubsection{The \Sphinxes extension for sets of nodes}
+\subsection{The SphinxES extension for sets of nodes}
 
@@
 
-\subsubsection{\Sphinxes algorithms and \acf*{SPOR}}
+\subsection{SphinxES algorithms}
 
-\Sphinxes provides the following algorithms:
+SphinxES provides the following algorithms:
 \begin{itemize}
@@
 We will synchronize our detailed descriptions with that of 
-\ac{Sphinx}, hence we will use the following notation:
+Sphinx, hence we will use the following notation:
 \begin{itemize}
@@
 
-If \(L' = \{\rdvnode\}\), the packet payload contains another \Sphinxes packet 
+If \(L' = \{\rdvnode\}\), the packet payload contains another SphinxES packet 
 to be forwarded.

### 2020-03-27 spores-protocol-paper/abstract.tex

% -*- tex-main-file: "contents.tex" compile-command: "pdflatex spores.tex" ispell-dictionary: "american" -*-

% What's the problem?
% Why is it a problem? Research gap left by other approaches?
% Why is it important? Why care?
% What's the approach? How to solve the problem?
% What's the findings? How was it evaluated, what are the results, limitations, 
% what remains to be done?

\acs{SPORES} is a protocol that provides a file transfer service that does not
rely on a central service but provides strong privacy guarantees.

Consider that Alice wants to share a file with Bob. She uploads the file
to \enquote{the Cloud} (someone else's computer) and sends a link to Bob. Bob
fetches the file from the third-party storage. This allows the third
party to infer much information. \Ac{SPORES} changes this.

Alice has several devices (laptop, smartphone, etc.) with varying
online--offline patterns, we call these devices her device squad. The
squad knows which device has which files and each device of the squad
has a model of the other devices' online--offline patterns. Alice's
devices can coordinate the sending of the file. Similarly, Bob also has
a device squad, and his squad can coordinate receiving the file. Instead
of Alice giving Bob a link to the file in the Cloud, Bob gives Alice a
route where the destination is his squad (the \emph{set} of Bob's devices).

At the core of our proposal lies a stateless, probabilistic
onion-routing protocol called \ac{SPOR}. \Ac{SPOR} relies on a set-based
mix-header format based on Sphinx~\cite{Sphinx} (we dubb this extension
SphinxES, for Sphinx Extended for Sets). Given an algorithm for secure
peer sampling, a probabilistic model of node availability, \ac{SPOR} will
populate the layers of SphinxES with sets of devices to reliably deliver
packets from one set of devices to another over a network of mix-nodes
with high churn.

This yields several interesting properties, among others: \ac{SPOR} can
provide connections over a network of unreliable devices, unlike 
Tor's~\cite{Tor} network of dedicated, always online devices; \ac{SPOR} removes 
the weakest-link bandwidth problem present in Tor, sets of nodes at each
layer provides a wider path and thus more bandwidth; at the same time,
\ac{SPOR} still provides privacy guarantees en par with Tor.

### 2020-03-27 spores-protocol-paper/approach.tex

@@
 When Alice and Bob, two users of our system, want to exchange a file \(f\) 
-through \name, they start by sharing some information out-of-band, \eg from 
-their smartphones.
+through \name, they start by sharing some information out-of-band, comparable 
+to links for sharing a file in the Cloud.
 More precisely, they exchange metadata on \(f\), encryption keys, and
@@
 
-%% Figure~\ref{fig:outline} shows the components needed to obtain the
-%% routing information for the headers.
-
-\begin{figure}[t]
-  \centering
-  \def\svgwidth{0.8\columnwidth}
-  %  \import{figures/}{outline_figure_only.pdf_tex}
-    \includegraphics[width=\columnwidth]{figures/OverviewSPORES_cropped}
-    \caption{Architectural overview of the \ac{SPORES} private file sharing service.}
-    \label{fig:outline}
-\end{figure}
-
 After the initial, out-of-band setup, file transfer happens along
 onion routes with the following features:\\
-\textbf{Stateless.} There is no mandatory circuit creation, the file transfer can be
-  done in a stateless way. \\
- \textbf{Predictive.} The choice of which nodes is placed in which onion routing
-  layer is informed on a predictive model for availability, disseminated
-  by an overlay and queried by random peer sampling (RPS).
-Note that availability predictions only influence how nodes returned by the random peer sampling service are distributed among layers, but have no impact on the overall population of nodes making up the onion route.
-This population is controlled by the random peer sampling service, which we assume is secure.
-This is important to ensure strong privacy protection, and we return to this point in the Security Discussion of Section~\ref{security-discussion}.\\
- \textbf{Probabilistic.} Instead of source routes with one node per onion layer, each
-  layer consists of a set of nodes and although the source route still
-  determines the sequence of layers, the actual node used for the next
-  hop of forwarding is selected from the set in an ad-hoc way,
-  resulting in a source-bounded random walk.\\
- \textbf{Onion Routing.} Put simply, in onion routing, the sender creates
-  a source route and encapsulates the payload and next-hop information in layers (by
-  encryption), that are \emph{peeled} (decrypted) one by one along the
-  route. By virtue of these layers, the forwarding nodes on the
-  route do not know where on the route they are and thus whether they
-  have received a packet directly from the sender or some other
-  intermediate node. We base our format for layering and peeling on the
-  \ac{Sphinx} mix-header format, which we extend to allow for the
-  changes above, described in \cref{Sphinxes}.
+\begin{description}
+  \item[Stateless] There is no circuit creation.
+    The protocol is stateless up to remembering previously seen packets to 
+    prevent replay attacks.
+    (There is no relation between packets.)
+
+  \item[Probabilistic] Instead of source routes with one node per onion layer, 
+    each layer consists of a set of nodes and although the source route still 
+    determines the sequence of layers, the actual node used for the next hop of 
+    forwarding is selected from the set in an ad-hoc way\daniel{%
+      What is \enquote{ad-hoc way}?}, resulting in a source-bounded random 
+    walk.
+
+  \item[Onion Routing] Put simply, in onion routing, the sender creates a 
+    source route and encapsulates the payload and next-hop information in 
+    layers (by encryption), that are \emph{peeled} (decrypted) one by one along 
+    the route. By virtue of these layers, the forwarding nodes on the route do 
+    not know where on the route they are and thus whether they have received a 
+    packet directly from the sender or some other intermediate node. We base 
+    our format for layering and peeling on the \ac{Sphinx} mix-header format, 
+    which we extend to allow for sets of nodes in each layer.
+\end{description}
 
@@
 
-As depicted in Figure~\ref{fig:outline}, \ac{SPORES} relies on a predictive and probabilistic onion routing protocol (\ac{SPOR}).
-\ac{SPOR} in turn combines a multi-set mix-header format (\Sphinxes) together with a node selection protocol that exploits decentralized prediction regarding node availability to optimize the reliability of \Sphinxes without jeopardizing its security properties.
+As depicted in \cref{fig:outline}, \ac{SPORES} relies on a probabilistic onion 
+routing protocol (\ac{SPOR}). \Ac{SPOR} in turn combines a set-based mix-header 
+format (\Sphinxes) together with a node selection protocol.
 %% Particularly, \sphinxes (\cref{Sphinxes}), is an adaptation of the 
@@
 %% header format, it only imposes some restrictions in the above categories.
-\Sphinxes (Figure~\ref{fig:outline} \ding{202}) provides, just as \ac{Sphinx}, unidirectional (network structure), 
-message-based (performance) communication.
-But unlike \ac{Sphinx}, \Sphinxes is an hybrid source-hop-by-hop routed, and a
-source-bounded random walk (communication 
-model). \Sphinxes relies on a flat routing-topology (network structure) with fair 
+\Sphinxes (Figure~\ref{fig:outline} \ding{202}, \cref{Sphinxes}) provides, just 
+as \ac{Sphinx}, unidirectional (network structure), message-based (performance) 
+communication.
+But unlike \ac{Sphinx}, \Sphinxes is a hybrid: source-hop-by-hop routed, 
+essentially a source-bounded random walk (communication model).
+\Sphinxes relies on a flat routing-topology (network structure) with fair 
 scheduling (communication model) --- as all packets are indistinguishable they 
@@
 entire set just as she can learn the single node constituting a layer of a
-secure onion-routing scheme without endangering the security
+secure onion-routing scheme, this does not endanger the security
 properties~\cite{CLOnionRouting}).
+
+\begin{figure}[t]
+  \centering
+  \def\svgwidth{0.8\columnwidth}
+  %  \import{figures/}{outline_figure_only.pdf_tex}
+    \includegraphics[width=\columnwidth]{figures/OverviewSPORES_cropped}
+    \caption{%
+      Architectural overview of the \ac{SPORES} private file sharing service.
+      \daniel{This figure must be updated.}
+    }
+    \label{fig:outline}
+\end{figure}
 
@@
 scheme~\cite[\eg][]{Octopus}.
-Each node must be associated with a public key and some availability 
-prediction.
-\Ac{SPOR} selects nodes for a route uniformly randomly and uses the 
-availability to maximize the availability of the entire route, \ie across 
-layers.
-\commentFT{What follows seems quite convoluted, with a lot of repetition. Would be nice to revise.} As \ac{SPOR} assumes this source of random nodes, the network view (routing 
-information) of each node depends on this source of random nodes, as does the 
-fact of how decentralized the scheme becomes and whether the network toppology 
-is fully, mostly or partly connected (network structure).
+The choice of this source of random nodes affects the network view (routing 
+information) of each node, as well as how decentralized the scheme becomes and 
+whether the network topology is fully, mostly or partly connected (network 
+structure).
+
+Each node must be associated with a public key and some prediction function.
+\Ac{SPOR} selects nodes for a route uniformly randomly and uses the prediction 
+function to optimize the properties of the entire route, \ie across layers.
 As \ac{SPOR} is designed, it selects nodes uniformly among all the nodes 
@@
 
-A device's availability depends on its user's behavior, hence the device must 
-predict this behavior. This is best done jointly between all of the user's devices.
-%In \cref{sec:squad_overlay}, we describe
-Accordingly we introduce a protocol that allows the devices to 
-compute their own availability prediction function based on the observations by 
-all other devices.
-
-Finally, we introduce the complete \ac{SPORES} protocol that acts as a private P2P file transfer. It 
-allows the device \squad to act as an autonomous system.
-In particular, we introduce a protocol which allows transferring larger 
-messages by fragmentation and reassembly across the devices in the \squad  (Figure~\ref{fig:outline} \ding{204}).
+Finally, we introduce the complete \ac{SPORES} protocol that allows 
+transferring larger messages by fragmentation and reassembly across the devices 
+in the \squad  (Figure~\ref{fig:outline} \ding{204}).

### 2020-03-27 spores-protocol-paper/related.tex

--- 2018-10-03 paper/related.tex
@@
 (Bittorrent~\cite{bittorrent-incentives}), anonymity 
-(Freenet~\cite{Clarke:2001}, \ac{Tor}, and \acp{DHT} such as CAN, Chord, 
+(Freenet~\cite{Clarke:2001}, Tor, and \acp{DHT} such as CAN, Chord, 
 Pastry, and Tapestry, see~\cite{dhtchurn} for an overview). In contrast to our 
@@
 
-Onion routing schemes, with infrastructure and governance (\ac{Tor}) and 
+Onion routing schemes, with infrastructure and governance (Tor) and 
 without (I2P\footnote{https://geti2p.net/en/}), though geared toward web 

### 2020-03-27 spores-protocol-paper/system-model.tex

@@
 
-\name provides a private and fully decentralized file transfer service by exploiting 
-%% is a distributed system made of
-users' devices.  We assume any pair of devices can communicate with each other as soon as one knows the address of the other (\eg using the
-Internet, possibly extended with NAT traversal techniques). The
-devices owned by the same user (this user's \squad) know of each
-other. We leverage the the devices of other users to help transfer the file from one user
-to another, but do not use them for storage.  We also assume that users
-can exchange some limited amounts of data out-of-band, \ie through
-some other channel than the network just mentioned (\eg using \ac{NFC}
-or QR codes).
 %system model: explain e-squad, contrast with cloud
@@
   \emph{P2P} interchangeably, and preferentially the latter for brevity.})
-context.  We finally consider the additional privacy properties
+context.
+We finally consider the additional privacy properties
 required to protect users from inferences, such as by network traffic
@@
 \begin{itemize}
-\item Alice and Bob are the only users who learn 
-about Alice sharing a file with Bob.
+\item Alice and Bob are the only \emph{users} who learn about Alice sharing a 
+  file with Bob.
 \item The composition and behavior of Alice and Bob's \squad{}s remain
@@
 stemming from the users' interaction with the service, and can draw
-inferences from metadata even when the data itself is encrypted. The
-provider thus poses a threat to the users' privacy which we remove in
-the P2P scenario~\cite{DevilInMetadata}.
+inferences from metadata even when the data itself is encrypted.
 
 \subsection{Moving to a P2P environment}
+
 A private P2P file transfer solution should retain the privacy that
@@
 associated with a central brokering entity but also the benefits from
-gatekeeping and therefore exposes users to friendly
-surveillance~\cite{FriendlySurveillance} by other peers (other \name
-users including Alice and Bob). In particular, in an
+gatekeeping~\cite{DevilInMetadata} and therefore exposes users to friendly
+surveillance~\cite{FriendlySurveillance} by other peers (\name
+users including Alice and Bob themselves). In particular, in an
 honest-but-curious setting, other users might collude to observe some
@@
 
-\subsection{The privacy properties and adversary model of \name}
+\subsection{Basic assumptions}
+
+We assume any pair of devices can communicate with each other as soon as one 
+knows the address of the other (\eg using the Internet, possibly extended with 
+NAT traversal techniques).
+The devices owned by the same user (this user's \squad) know of each
+other and their addresses.
+We also assume there exists some protocol which allows them to synchronize 
+their knowledge~\cite[\eg][]{luxey:cascade}.
+
+We also assume that users can exchange some limited amounts of data 
+out-of-band, \ie through some other channel --- \eg using \ac{NFC}, QR codes or 
+simply send a link through instant messaging or email.
+
+\subsection{Privacy properties and adversary model of \name}
+
+\daniel{This section doesn't really say what the privacy properties are.}
+
+\paragraph*{Privacy properties}
 
 Friendly surveillance can be mitigated by ensuring security properties 
-typically associated with onion routing, as defined by Camenisch and Lysyanskaya~\cite{CLOnionRouting}: 
+typically associated with onion routing.
+\Textcite{CLOnionRouting} define security properties for onion routing as 
 % We combine the requirements from
@@
 these three properties, combined with secure point-to-point channels,
-is universal composability (UC)-secure, \ie the protocol remains
+is \acadv{UC} secure, \ie the protocol remains
 secure even if arbitrarily composed with other instances of the same or other protocols.
@@
 
-\paragraph*{Adversary model} To assess our approach, we use the
+\paragraph*{Adversary model}
+
+To assess our approach, we use the
 adversary model assumed by Tor and \ac{Sphinx}:

### 2020-04-02 paper/UCOR.tex
Added summary of the ideal fuinctionality and properties which we will use to prove the secorutiy of spores. They are currently in written in an inexact manner

@@
 \label{UCOR}
+The Universal Composability framework (which we will call UC or
+UC-framework) is a mathematical framework that can be summarized in
+two ideas, first, that there exists a stringent and well defined idea
+about what a protocol needs to do, its functionality. Secondly, that
+any two protocols that fulfill this idea should be {\it
+  indistinguishable\/} in the sense that they should perform the exact
+same service. If the protocol is regarded as a black box, this means
+that any input into to the two different boxes should result in the
+exact same output.
 
-\dots
+The second idea also means that any two protocols, with well defined
+functionalities, should not interefere with one another if they are
+are used in parallel or one after the other, as long as their inputs
+are correct. That is, they are composable.
+
+The underlying framework is quite technical and requires one to handle
+a computational model with what the original author %TODO: Insert reference
+called Interactive Turing Machines and on top of this designed the
+Universal Composability theorem. However, the most important part of
+this framework is what is known as an {\bf Ideal Functionality}, which
+can be thought of as a black box that fulfills some well-defined
+functionality. The idea behind the UC-framework is then that we ought
+to define a protocol which we must then prove simulates the ideal
+functionality, so that distinghuising between the ideal functionality
+and the real protocol becomes infeasible.
+
+However, this is not necessarily the way one must go about working in
+the framework. We will, for example, instead utilise the fact that one
+may prove some sufficient conditions that if fulfilled means that the
+protocol must simulate the ideal functionality.
+
+One of the first succesful uses of the UC-framework was a model
+created by Jan Camenish and Anna Lysyanskaya (a mode we will call the
+CL-model). This model was an attempt at formalising the concept of
+onion routing using the UC-framework. It relied on an ideal
+functionality, and 5 properties that ensured a protocol would properly
+simulate the ideal functionality.
+
+The ideal functionality itself works through messages, and is
+designed around 4 different functions, each activated by a specific
+message.
+\begin{Itemize}
+  \item{{\tt Process_New_Onion} When an onion is received, either
+    reject if faulty or proceed with}
+  \item{{\tt Process_Next_step} Creates a temporary id for the onion
+    and informs the adversary of onion (this emulates the fact that
+    the adversary controls the network). If the router itself is
+    adversial, it also tells the adversary which route it was part
+    of. }
+  \item{{\tt Deliver_Message} Is actually sent by the adversary, but
+    simply informs the router to send the onion to the next step in
+    its path.}
+  \item{{\tt Forward_Onion} Tells the ideal functionality to send the
+    message to the next router and the step {\tt Process_Next_Step} is
+    once again taken.}
+\end{Itemize}
+
+To prove that a protocol properly simulates this ideal functionality,
+the CL-model, as mentioned above, defined five sufficient properties.
+
+\begin{enumerate}
+  \item{{\bf Onion routing scheme I/O.} The protocol should have a key
+  generation algorithm for assymetric encryption, be able to form an
+  onion from a message and a list of routers and their public
+  keys. Lastly, the protocol should also be able to process the onion,
+  that is, peel a lay off of it and deliver it to the next router.}
+
+  \item{{\bf Onion evolution, path and layering.} Each onion should
+    have a pair of idenifiers, that is the onion itself and its
+    router. Then the evolution is the ordered set of such pairs, the path is
+    the set of routers and the layering is the set of onions.}
+
+  \item{{\bf Onion-correctness.} This is the simple condition that if a
+  correctly formed onion is processed correctly and by the correct
+  routers, then the correct message is received by the last router.}
+
+  \item{{\bf Onion-integrity} This is the requirement that the path of
+  an onion is limited by some integer N, that is, no matter how an
+  onion is manipulated, the path may never have a length that is
+  larger than N.}
+
+  \item{{\bf Onion-security.} A protocol has the property of
+    onion-security if an adversary can not guess the message nor add
+    an extra onion-layer to any onion.}
+
+\end{enumerate}
+
+However, while these definitions are useful, newer work have found
+that they were not sufficient and added two new properties, which has
+since been proven to fulfill the security properties of the ideal
+functionality. The properties were:
+
+\begin{enumerate}
+  \setcounter{enumi}{6}
+  \item{{\bf Tail indistinguishability against a corrupted receiver.}
+    An adversary that reads after the last honest relay should not be
+    able to distinguish between two onions who follow the same path
+    after the last honest router, but differ before it.}
+
+  \item{{\bf Layer-Unlinkability against bypassing honest nodes.} An
+    adversary should not be able to distinguish between an onion for
+    which the adversary chooses the path up to an honest router, and
+    an onion which contains this path as a subpath.}
+\end{enumerate}
+
+With these properties and the Spores protocol, we wish to prove that
+spores does indeed have these properties, and thus fulfills the
+security properties of the ideal functionality.

### 2020-04-02 paper/spor.tex
Revises SPOR protocol

@@
 
-\subsection{\Acf*{SPOR}}%
+\section{\Acf*{SPOR}}%
 \label{SPOR}%
@@
 Bob creates a reply header using \(\CreateReply\) and gives the output to Alice 
-over an out-of-band channel.
-%We assume that \(m\) is either unavailable when the channel is used or too large to be successfully sent over the channel directly.
+over an out-of-band channel\footnote{%
+  There can be many reasons for this and many ways to solve it.
+  \Eg \(m\) might be unavailable at the time.
+  Signal creates \ac{DH} exponents in advance (before \(m\) is known) and 
+  publishes on the Signal servers, so Alice would fetch one of Bob's when she 
+  has a message to send.
+  We will treat this in more detail later.
+}.
 At a later point, Alice attaches a message \(m\) to the reply header using 
@@
 one expected to come from Alice.
-(This process is illustrated in \cref{fig:file-transfer}.)
+%(This process is illustrated in \cref{fig:file-transfer}.)
 Now we will focus on how Alice and Bob choose the nodes that they provide to 
@@
 
-\begin{figure}
-  \includegraphics[width=\linewidth]{figures/file_transfer_v2.pdf}
-  \caption{\label{fig:file-transfer}%
-    A schematic of Alice and Bob sending a message using \name.
-    \ding{182} illustrates the layer of the headers that Alice and Bob create.
-    In \ding{183}, Alice and Bob exchange the headers out-of-band.
-    In \ding{184}, Alice and Bob use two \ac{SPOR} routes, one for messages and 
-    one for acknowledgements.
-  }
-\end{figure}
+%\begin{figure}
+%  \includegraphics[width=\linewidth]{figures/file_transfer_v2.pdf}
+%  \caption{\label{fig:file-transfer}%
+%    A schematic of Alice and Bob sending a message using \name.
+%    \ding{182} illustrates the layer of the headers that Alice and Bob create.
+%    In \ding{183}, Alice and Bob exchange the headers out-of-band.
+%    In \ding{184}, Alice and Bob use two \ac{SPOR} routes, one for messages and 
+%    one for acknowledgements.
+%  }
+%\end{figure}
 
@@
 nodes in each layer.
-We will focus on maximizing availability when routing in a network with high 
-churn, but one could equally well select nodes to maximize, \eg, bandwidth.
-We now describe a protocol, \ac{SPOR}, which uses SphinxES to transfer messages 
-from a source to a destination over a network of nodes with high churn.
+We will now describe the protocol~\(\SPOR\), which uses SphinxES to transfer 
+messages from a source to a destination.
+It chooses nodes to optimize for availability of each layer.
+It also chooses them uniformly randomly from the entire set of 
+devices~\(\devices\).
 
-\((d, \pk_d, \avail_d)\gets \GetRandomNode\): We assume that there is an 
-algorithm \(\GetRandomNode\) which returns a tuple \((d, \pk_d, \avail_d)\) of 
-one uniformly randomly selected node, where.
+\((d, \pk_d, a_d)\gets \GetNode\): The algorithm~\(\GetNode\) returns a tuple 
+\((d, \pk_d, a_d)\) of one selected node, where
 \begin{itemize}
@@
   \item \(\pk_d\) is the node's public key;
-  \item  \(\avail_d(t)\) is the node's probability of being online as a function of time. 
-  Its computation will be discussed in~\ref{ssec:device_availability}.
+  \item \(a_d\gets \avail(d)\) is the availability of device~\(d\), where the 
+    function~\(\avail\colon \devices\to \interval{0}{1}\) maps a device to its 
+    availability (0 is always offline, 1 is always online).
 \end{itemize}
-The \(\GetRandomNode\) algorithm can be instantiated using \eg
-Octopus~\cite{Octopus}. Its function is analogous to \acg{Tor} authoritative 
-directory servers, but we need a decentralized system. We will treat 
-\(\avail_d\) in \cref{sec:squad_overlay}.
+We note that the function~\(\avail\) does note necessarily have to return the 
+exact availability of \(d\), \eg it can provide \(k\)-anonymity by mapping the 
+\(d\)'s availability to the closest of some predefined availability values, 
+such as \(\{0.25, 0.5, 0.75, 1\}\).
 
-When Bob runs \(\CreateReply\) (or Alice runs \(\CreateFwd\)) he must supply a 
-set of nodes for each layer of the route, \(L = \{L_0, \dotsc, L_\nu\}\), where 
-\(|L_i| \leq w_L\) for \(0\leq i\leq \nu\).
+The \(\GetNode\) algorithm can be instantiated using \eg
+Octopus~\cite{Octopus}, which would yield a near uniform distribution of nodes 
+under adversarial conditions.
+Another instantiation would be Tor's authoritative directory servers.
+However, exactly how the \(\GetNode\) algorithm is implemented is not our 
+concern at the moment.
+
+When Bob runs \(\CreateReply\) he must supply a set of nodes for each layer of 
+the route, \(L = \{L_0, \dotsc, L_\nu\}\), where \(|L_i| \leq w_L\) for \(0\leq 
+i\leq \nu\).
 The set \(L_\nu\) contains only one or more of Bob's devices.
 For the other layers, \(L_i\) for \(i < \nu\), Bob will do the following:
-Bob queries \(\GetRandomNode\) \((\nu-1)\cdot w_L\) times to get enough nodes 
-to fill all remaining layers.
-Bob will distribute these nodes across all layers \(L_i\) to maximize \(\min_i 
-  \avail_{L_i}(t)\), where \(\avail_{L_i}(t) = 1-\prod_{l\in L_i} 
-  (1-\avail_l(t))\).
-This means that Bob minimizes the risk of a layer (\ie all nodes in a layer) 
-being unavailable.
-
-For the evaluaion of the impact of devices' availability prediction, we introduce a parameter, coined the \emph{availability threshold} $\theta$. 
-\CreateLayer iteratively adds nodes to a layer \layer until its probability of being entirely offline $\Poff^\layer$ falls below $\theta$ or $w_\layer$ is reached:
-
-$$ \Poff^\layer = \sum\limits_{d \in \layer}(1 - \desc_d.\Pon_d) $$
-
-When $|\layer| < w_\layer$, the layer is filled with empty descriptors so as to fill the target number of nodes per layer.
-
-Using $\theta$, \name becomes more conservative than \ac{SPOR}, and we can investigate the best number of nodes per layer in regard of its probability of being available.
+Bob makes \((\nu-1)\cdot w_L\) queries to \(\GetNode\) to get enough nodes to 
+fill all remaining layers.
+Bob will distribute these nodes across all layers~\(L_i\) to maximize the 
+availability~\[
+  a_{L_i} = 1 - \prod_{d\in L_i} (1-a_d)
+\] of every layer (or equivalently, minimizing the risk that every node in a 
+layer is offline at the same time).

### 2020-04-02 paper/UCOR.tex
Added references to the section. Now ready for review.

@@
   indistinguishable\/} in the sense that they should perform the exact
-same service. If the protocol is regarded as a black box, this means
+same service\cite{UC-framework}. If the protocol is regarded as a black box, this means
 that any input into to the two different boxes should result in the
@@
 are used in parallel or one after the other, as long as their inputs
-are correct. That is, they are composable.
+are correct. That is, they are composable\cite{UC-framework}.
 
@@
 called Interactive Turing Machines and on top of this designed the
-Universal Composability theorem. However, the most important part of
+Universal Composability theorem \cite{UC-framework}. However, the most important part of
 this framework is what is known as an {\bf Ideal Functionality}, which
 can be thought of as a black box that fulfills some well-defined
-functionality. The idea behind the UC-framework is then that we ought
+functionality\cite{UC-framework}. The idea behind the UC-framework is then that we ought
 to define a protocol which we must then prove simulates the ideal
@@
 functionality, and 5 properties that ensured a protocol would properly
-simulate the ideal functionality.
+simulate the ideal functionality\cite{CL-model}.
 
@@
 designed around 4 different functions, each activated by a specific
-message.
-\begin{Itemize}
+message\cite{CL-model}.
+\begin{itemize}
   \item{{\tt Process_New_Onion} When an onion is received, either
@@
     once again taken.}
-\end{Itemize}
+\end{itemize}
 
 To prove that a protocol properly simulates this ideal functionality,
-the CL-model, as mentioned above, defined five sufficient properties.
+the CL-model, as mentioned above, defined five sufficient properties\cite{CL-model}.
 
@@
 
-  \item{{\bf Onion-integrity} This is the requirement that the path of
+  \item{{\bf Onion-integrity.} This is the requirement that the path of
   an onion is limited by some integer N, that is, no matter how an
@@
     an extra onion-layer to any onion.}
-
 \end{enumerate}
@@
 since been proven to fulfill the security properties of the ideal
-functionality. The properties were:
+functionality\cite{kuhn}. The properties were:
 
 \begin{enumerate}
-  \setcounter{enumi}{6}
+  \setcounter{enumi}{5}
   \item{{\bf Tail indistinguishability against a corrupted receiver.}

### 2020-04-06 paper/UCOR.tex
Spelling, grammar, references and proper placements by dbosk
Co-Authored-By: dbosk <dbosk@users.noreply.github.com>

--- 2020-03-27 paper/UCOR.tex
@@
 \label{UCOR}
+The \ac{UC} framework is a mathematical framework that can be summarized in
+two ideas, first, that there exists a stringent and well defined idea
+about what a protocol needs to do, its functionality. Secondly, that
+any two protocols that fulfill this idea should be {\it
+  indistinguishable\/} in the sense that they should perform the exact
+same service~\cite{UniversalComposability}. If the protocol is regarded as a black box, this means
+that any input into the two different boxes should result in the
+exact same output.
 
-\dots
+The second idea also means that any two protocols, with well defined
+functionalities, should not interefere with one another if they are
+are used in parallel or one after the other, as long as their inputs
+are correct. That is, they are composable~\cite{UniversalComposability}.
+
+The underlying framework is quite technical and requires one to handle
+a computational model with what the original author %TODO: Insert reference
+called Interactive Turing Machines and on top of this designed the
+Universal Composability theorem \cite{UniversalComposability}. However, the most important part of
+this framework is what is known as an {\bf Ideal Functionality}, which
+can be thought of as a black box that fulfills some well-defined
+functionality\cite{UniversalComposability}. The idea behind the \ac{UC} framework is then that we ought
+to define a protocol which we must then prove simulates the ideal
+functionality, so that distinghuising between the ideal functionality
+and the real protocol becomes infeasible.
+
+However, this is not necessarily the way one must go about working in
+the framework. We will, for example, instead utilise the fact that one
+may prove some sufficient conditions that if fulfilled means that the
+protocol must simulate the ideal functionality.
+
+One of the first successful uses of the \ac{UC} framework was a model
+created by Jan Camenish and Anna Lysyanskaya (a mode we will call the
+CL-model). This model was an attempt at formalising the concept of
+onion routing using the UC-framework. It relied on an ideal
+functionality, and 5 properties that ensured a protocol would properly
+simulate the ideal functionality~\cite{CL-model}.
+
+The ideal functionality itself works through messages, and is
+designed around 4 different functions, each activated by a specific
+message~\cite{CL-model}.
+\begin{itemize}
+  \item{{\tt Process_New_Onion} When an onion is received, either
+    reject if faulty or proceed with}
+  \item{{\tt Process_Next_Step} Creates a temporary id for the onion
+    and informs the adversary of onion (this emulates the fact that
+    the adversary controls the network). If the router itself is
+    adversial, it also tells the adversary which route it was part
+    of. }
+  \item{{\tt Deliver_Message} Is actually sent by the adversary, but
+    simply informs the router to send the onion to the next step in
+    its path.}
+  \item{{\tt Forward_Onion} Tells the ideal functionality to send the
+    message to the next router and the step {\tt Process_Next_Step} is
+    once again taken.}
+\end{itemize}
+
+To prove that a protocol properly simulates this ideal functionality,
+the CL-model, as mentioned above, defined five sufficient properties~\cite{CL-model}.
+
+\begin{enumerate}
+  \item{{\bf Onion routing scheme I/O.} The protocol should have a key
+  generation algorithm for asymetric encryption, be able to form an
+  onion from a message and a list of routers and their public
+  keys. Lastly, the protocol should also be able to process the onion,
+  that is, peel a layer off of it and deliver it to the next router.}
+
+  \item{{\bf Onion evolution, path and layering.} Each onion should
+    have a pair of idenifiers, that is the onion itself and its
+    router. Then the evolution is the ordered set of such pairs, the path is
+    the set of routers and the layering is the set of onions.}
+
+  \item{{\bf Onion-correctness.} This is the simple condition that if a
+  correctly formed onion is processed correctly and by the correct
+  routers, then the correct message is received by the last router.}
+
+  \item{{\bf Onion-integrity.} This is the requirement that the path of
+  an onion is limited by some integer N, that is, no matter how an
+  onion is manipulated, the path may never have a length that is
+  larger than N.}
+
+  \item{{\bf Onion-security.} A protocol has the property of
+    onion-security if an adversary can not guess the message nor add
+    an extra onion-layer to any onion.}
+\end{enumerate}
+
+However, while these definitions are useful, newer work have found
+that they were not sufficient and added two new properties, which has
+since been proven to fulfill the security properties of the ideal
+functionality~\cite{kuhn}. The properties were:
+
+\begin{enumerate}
+  \setcounter{enumi}{5}
+  \item{{\bf Tail indistinguishability against a corrupted receiver.}
+    An adversary that reads after the last honest relay should not be
+    able to distinguish between two onions who follow the same path
+    after the last honest router, but differ before it.}
+
+  \item{{\bf Layer-Unlinkability against bypassing honest nodes.} An
+    adversary should not be able to distinguish between an onion for
+    which the adversary chooses the path up to an honest router, and
+    an onion which contains this path as a subpath.}
+\end{enumerate}
+
+With these properties and the SphinxES protocol, we wish to prove that
+SphinxES does indeed have these properties, and thus fulfills the
+security properties of the ideal functionality.

### 2020-04-06 paper/spor.tex
Revises the security analysis of SPOR

@@
 
-\((d, \pk_d, a_d)\gets \GetNode\): The algorithm~\(\GetNode\) returns a tuple 
-\((d, \pk_d, a_d)\) of one selected node, where
+\((d, \pk_d, a_d)\gets \GetNode\): We assume that there exists an 
+algorithm~\(\GetNode\) which returns a tuple \((d, \pk_d, a_d)\) of one 
+selected node, where
 \begin{itemize}
@@
 
-When Bob runs \(\CreateReply\) he must supply a set of nodes for each layer of 
-the route, \(L = \{L_0, \dotsc, L_\nu\}\), where \(|L_i| \leq w_L\) for \(0\leq 
-i\leq \nu\).
-The set \(L_\nu\) contains only one or more of Bob's devices.
-For the other layers, \(L_i\) for \(i < \nu\), Bob will do the following:
-Bob makes \((\nu-1)\cdot w_L\) queries to \(\GetNode\) to get enough nodes to 
-fill all remaining layers.
-Bob will distribute these nodes across all layers~\(L_i\) to maximize the 
-availability~\[
+Now we can construct the layers of Bob's reply block that Alice can use to send 
+him a message.
+We provide the algorithm \(\CreateLayers\), which populates the layers~\(L_0, 
+\dotsc, L_{\nu-1}\) that Bob must provide to \(\CreateReply\).
+(Bob will create \(L_\nu\) himself by filling it with his devices.)
+
+\((L_0, \dotsc, L_{\nu-1}) \gets \CreateLayers\):
+The algorithm first makes \(\nu\cdot w_L\) queries to \(\GetNode\) to get 
+enough nodes to fill all layers.
+These nodes are distributed across all layers~\(L_i\), for \(0\leq i < \nu\), 
+to maximize the availability~\[
   a_{L_i} = 1 - \prod_{d\in L_i} (1-a_d)
 \] of every layer (or equivalently, minimizing the risk that every node in a 
-layer is offline at the same time).
+layer is offline at the same time) while keeping \(|L_i| = w_L\).

### 2020-04-08 paper/UCOR.tex
Added Kuhn properties, a description of the ideal functionality

@@
 \label{UCOR}
-The \ac{UC} framework is a mathematical framework that can be summarized in
+The \ac{UC} framework is a mathematical framework that can be summarised in
 two ideas, first, that there exists a stringent and well defined idea
 about what a protocol needs to do, its functionality. Secondly, that
-any two protocols that fulfill this idea should be {\it
+any two protocols that fulfil this idea should be {\it
   indistinguishable\/} in the sense that they should perform the exact
@@
 The second idea also means that any two protocols, with well defined
-functionalities, should not interefere with one another if they are
+functionalities, should not interfere with one another if they are
 are used in parallel or one after the other, as long as their inputs
@@
 this framework is what is known as an {\bf Ideal Functionality}, which
-can be thought of as a black box that fulfills some well-defined
+can be thought of as a black box that fulfils some well-defined
 functionality\cite{UniversalComposability}. The idea behind the \ac{UC} framework is then that we ought
 to define a protocol which we must then prove simulates the ideal
-functionality, so that distinghuising between the ideal functionality
+functionality, so that distinguishing between the ideal functionality
 and the real protocol becomes infeasible.
@@
 One of the first successful uses of the \ac{UC} framework was a model
-created by Jan Camenish and Anna Lysyanskaya (a mode we will call the
+created by Jan Camenish and Anna Lysyanskaya (a model we will call the
 CL-model). This model was an attempt at formalising the concept of
 onion routing using the UC-framework. It relied on an ideal
-functionality, and 5 properties that ensured a protocol would properly
-simulate the ideal functionality~\cite{CL-model}.
+functionality, and five properties that ensured a protocol would properly
+simulate the ideal functionality~\cite{CL-model}. We will however not
+use these five original properties, rather opting to use three newer
+properties~\cite{kuhn}.
 
-The ideal functionality itself works through messages, and is
-designed around 4 different functions, each activated by a specific
-message~\cite{CL-model}.
+We begin by describing the ideal functionality, and it can be
+described as consisting of two parts, the internal data structure and
+the set of instructions in the form of messages. We begin with the
+data structure, describing what parties and information we have.
+
+\subsubsection*{Ideal Onion Routing Functionality: Internal Data Structure.}
 \begin{itemize}
-  \item{{\tt Process_New_Onion} When an onion is received, either
-    reject if faulty or proceed with}
-  \item{{\tt Process_Next_Step} Creates a temporary id for the onion
-    and informs the adversary of onion (this emulates the fact that
-    the adversary controls the network). If the router itself is
-    adversial, it also tells the adversary which route it was part
-    of. }
-  \item{{\tt Deliver_Message} Is actually sent by the adversary, but
-    simply informs the router to send the onion to the next step in
-    its path.}
-  \item{{\tt Forward_Onion} Tells the ideal functionality to send the
-    message to the next router and the step {\tt Process_Next_Step} is
-    once again taken.}
+\item{The set {\it Bad\/} of  parties controlled by the adversary \(S\).}
+
+\item{An onion \(O\) is stored in the a tuple on the form \((sid, P_s,
+  P_r, m, n, \mathcal{P}, i)\) where: \(sid\) is the
+  identifier,\(P_s\)is the sender, \(P_r\) is the recipient, \(m\) is
+  the message sent through the onion routers, \(n < N\) is the length
+  of the onion path, \(\mathcal{P} (P_{o_1},\ldots, P_{o_n})\) is the
+  path over which the message is sent (by convention,\(P_{o_0}=P_s\),
+  and \(P_{o_{n+1}}=P_r\)),\(i\) indicates how much of the path the
+  message has already traversed (\(i= 0\) when the onion is at
+  \(P_s\)). We know that the onion has reached its destination when
+  \(i=n+ 1\).
+}
+
+\item{ A list \(L\) of onions that the adversarial routers are
+  currently processing. Each entry of the list is in the form of a
+  tuple \((temp, O, j)\), where \(temp\) is the temporary id provided
+  by the ideal functionality, while \(O= (sid, P_s, P_r, m, n,
+  \mathcal{P}, i) \) is the onion itself, and \(j\) is the entry in
+  \(\mathcal{P}\) that indicates where the onion should go next (the
+  adversary does not get to see \(O\)and \(j\)). Remark: Entries will
+  never be removed from \(L\). This allows us to model the replay
+  attack for the ideal adversary.
+}
+
+\item{ For each honest party \(P_i\), there is a buffer \(B_i\) of
+  onions that are currently being held by \(P_i\). Each entry consists
+  of \((temp', O)\), where \(temp'\) is the temporary id that the
+  ideal functionality provides, so that the router may process the
+  onion and \(O = (sid, P_s, P_r, m, n, P, i)\) is the onion itself
+  (\(O\) is hidden from the honest party). Entries are removed from
+  this buffer if an honest party informs the ideal functionality that
+  it wishes to send the corresponding onion to the next party.
+}
+
+\end{itemize}
+
+Every party gets its instructions by way of messages sent between
+them, and for this we define 4 messages.
+
+The parties involved receives their instructions from messages that
+they send between them, and the ideal functionality have four
+messages.
+
+\subsubsection*{Ideal Onion Routing Functionality: Instructions.}
+
+\begin{itemize}
+
+\item{({\texttt Process_New_Onion}, \(P_r, m, n, \mathcal{P}\)). When
+  receiving a message of this form from \(P_s\), where \(m\in
+  \{0,1\}^{l_m}\cup\{\bot\}\), do.}
+  \begin{enumerate}
+  \item{If \(|\mathcal{P}| \geq N\), reject.}
+  \item{Otherwise, create a new session id \(sid\), and let \(O =
+    (sid, P, P_r, m, n, \mathcal{P}, 0)\). Send the message
+    ({\texttt Process_Next_Step}, \(O\)) to itself.}
+  \end{enumerate}
+
+\item{({\texttt Process_Next_Step}, \(O\)). Suppose \(O = (sid, P_s,
+  P_r, m, n, \mathcal{P}, i)\). The ideal functionality now looks at
+  the next part of the path. The router \(P_{o_i}\) is passing the
+  onion to the router \(P_{o_{i+1}}\). Depending on which routers are
+  honest and which ones are adversarial, two different steps may be
+  taken, an honest and an adversarial one:
+
+  \begin{enumerate}
+
+  \item{{\bf Honest next}.if the next node, \(P_{o_{i+1}}\), is
+    honest.Here, the ideal functionality creates a new random temporary id
+    \(temp\) for this onion and sends it to \(S\) (since \(S\) controls
+    the network, it decides which messages get delivered): ``Onion
+    \(temp\) from \(P_{o_i}\) to \(P_{o_{i+1}}\)''. It adds the entry
+    \((temp, O, i+1)\) to the list \(L\). (See ({\texttt Deliver_Message},
+    \(temp\)) for the next step.)}
+
+  \item{{\bf Adversary next}.Suppose that \(P_{o_{i+1}}\)is
+    adversarial. Then there are two cases:
+    \begin{itemize}
+    \item{There is an honest router remaining on the path to the
+      recipient. Let \(P_{o_j}\)be the next honest router. In this
+      case, the ideal functionality creates a random temporary id
+      \(temp\) for this onion, and sends the message ``Onion \(temp\)
+      from \(P_{o_i}\), routed through \((P_{o_{i+1}}, \ldots,
+      P_{o_{j-1}})\) to \(P_{o_j}\)'' to the ideal adversary \(S\),
+      and stores \((temp, O, j) \) in the list \(L\).}
+
+    \item{ \(P_{o_i}\)is the last honest router on the path; in
+      particular, this means that \(P_r\) is adversarial as well. In
+      this case, the ideal functionality sends the message``Onion from
+      \(P_{o_i}\) with message \(m\) for \(P_r\) routed through
+      \((P_{o_{i+1}}, \ldots,P_{o_n})\)'' to the adversary \(S\).}
+    \end{itemize}
+  }    
+  \end{enumerate}
+}
+
+\item{({\texttt Deliver_Message}, \(temp\)). This is a message of
+  confirmation from
+  \(S\) that it sends to the ideal process to notify it that it agrees that
+  the onion with temporary id \(temp\) should be delivered to its
+  intended destination. To process this message, the functionality
+  checks if the temporary identifier \(temp\) corresponds to any onion
+  \(O\) on the list \(L\). If it does, it retrieves the corresponding
+  record\((temp, O, j)\) and update the onion: if \(O= (sid, P_s, P_r,
+  m, n, \mathcal{P}, i)\), it replaces \(i\) with \(j\) to indicate
+  that we have reached the \(j\)'th router on the path of this
+  onion. If \(j < n+ 1\), it generates a temporary identifier
+  \(temp'\), sends ``Onion \(temp'\) received'' to party \(P_{o_j}\),
+  and stores the resulting pair(\(temp', O= (sid, P_s, P_r, m, n,
+  \mathcal{P}, j)\)) in the buffer \(B_{o_j}\) of party
+  \(P_{o_j}\). Otherwise, \(j=n+ 1\), so the onion has reached its
+  destination: if \(m \neq \bot\)it sends ``Message \(m\) received''
+  to router \(P_r\): otherwise no message is delivered.
+}
+
+\item{({\texttt Forward_Onion}, \(temp'\)). This is a message from an
+  honest ideal router \(P_i\) notifying the ideal process that it is
+  ready to send the onion with id \(temp'\) to the next hop. In
+  response, the ideal functionality
+
+  \begin{itemize}
+
+  \item{Checks if the temporary identifier \(temp'\) corresponds to
+    any entry in \(B_i\). If it does, it retrieves the corresponding
+    record \((temp', O)\).
+  }
+
+  \item{ Sends itself the message ({\texttt Process_Next_Step},
+    \(O\)).
+  }
+
+  \item{ Removes \((temp', O)\) from \(B_i\).
+  }
+  \end{itemize}
+}
 \end{itemize}
@@
 the CL-model, as mentioned above, defined five sufficient properties~\cite{CL-model}.
+However, later research has found that there exists three properties
+that provide the same thing, making the model slightly easier to
+describe~\cite{kuhn}.
+
+\begin{definition}{Onion-Correctness.}
+  Let \((G, \text{FormOnion}, \text{ProcOnion})\) be an Onion Routing
+  scheme with maximal path length \(N\). Then for all polynomial
+  numbers of routers \(P_i\), for all settings of the public
+  parameters \(p\), for all \((PK(P), SK(P))\) generated by
+  \(G(1^\lambda, p, P)\) for all \(n < N\), for all messages \(m \in
+  \mathcal{M}\) and for all onions \(O_1\) formed as \((O_1, \ldots,
+  O_{n+1}) \leftarrow
+  \text{FormOnion}(m,(P_1,\ldots,P_{n+1}),(PK(P_1),\ldots,PK(P_{n+1})))\)
+  the following is true:
 
   \begin{enumerate}
-  \item{{\bf Onion routing scheme I/O.} The protocol should have a key
-  generation algorithm for asymetric encryption, be able to form an
-  onion from a message and a list of routers and their public
-  keys. Lastly, the protocol should also be able to process the onion,
-  that is, peel a layer off of it and deliver it to the next router.}
+    \item{Correct path: \(\Pr[\mathcal{P}(O_1, P_1) = (P_1, \ldots,
+      P_{n+1})] \geq 1 - negl(\lambda).\)}
+    \item{Correct layering: \(\Pr[\mathcal{L}(O_1, P_1) = (O_1, \ldots,
+        O_{n+1})] \geq 1 - negl(\lambda).\)}
+    \item{Correct decryption: \(\Pr[(m,\bot) =
+        \text{ProcOnion}(SK(P_{n+1}), O_{n+1}, P_{n+1}) \geq 1 -
+        negl(\lambda). ]\)}
+  \end{enumerate}
+\end{definition}
 
-  \item{{\bf Onion evolution, path and layering.} Each onion should
-    have a pair of idenifiers, that is the onion itself and its
-    router. Then the evolution is the ordered set of such pairs, the path is
-    the set of routers and the layering is the set of onions.}
+\begin{definition}{Tail-Indistinguishability TI.}
+  \begin{enumerate}
+    \item{The adversary receives as input the challenge public key
+      \(PK\), chosen by the challenger by letting \((PK,SK) \leftarrow
+      G(1^\lambda, p, P_j)\) and the router name \(P_j\).}
+    \item{The adversary may submit any number of onions \(O_i\) of her
+      choice to the challenger. The challenger sends the output of
+      \(\text{ProcOnion}(SK, O_i, P_j)\) to the adversary.}
+    \item{The adversary submits a message \(m\), a path \(\mathcal{P}
+      = (P_1, \ldots, P_j, \ldots, P_{n+1})\) with the honest node at
+      position \(j, 1\leq j \leq n+1\) of her choice and key pairs for
+      all nodes \((PK_i,SK_i)\) (\(1\leq i \leq n+1\) for the nodes on
+      the path and \(n+1\) for the other relays).}
+    \item{The challenger checks that the router names are valid, that
+      the public keys correspond to the secret keys and that the same
+      key pair is chose if the router names are equal, and if so, sets
+      \(PK_j = PK\) and sets bit \(b\) at random.}
+    \item{The challenger create the onion with the adversary's input
+      choice:
+      \[ (O_1, \ldots, O_{n+1}) \leftarrow \text{FormOnion}(m,
+      \mathcal{P}, (PK)_{\mathcal{P}})
+      \]
+      and a random onion with a randomly chosen path
+      \(\bar{\mathcal{P}} = (\bar{P}_1, \ldots, \bar{P}_k = P_j,
+      \ldots, \bar{P}_{n+1} = P_{n+1})\), that includes the subpath
+      from the honest relay to the corrupted receiver starting at
+      position \(k\) ending at \(\bar{n} +1 \):
+      \[ (\bar{O}_1, \ldots, \bar{O}_{n+1} \leftarrow
+      \text{FormOnion}(m, \bar{\mathcal{P}}, (PK)_{\mathcal{P}})).
+      \]}
+    \item{
+      \begin{itemize}
+        \item{If \(b = 0\), the challenger gives \((O_{j+1},
+          P_{j+1})\) to the adversary.}
+        \item{Otherwise, the challenger gives, \((\bar{O}_{k+1},
+          \bar{P}_{j+1})\) to the adversary.}
+      \end{itemize}
+    }
+    \item{ The adversary may submit any number of onions \(O_i\) of
+      her choice to the challenger. The challenger sends the output of
+      \(\text{ProcOnion}(SK,O_i, P_j)\) to the adversary.}
+    \item{The adversary produces guess \(b'\).}
+  \end{enumerate}
+  TI is achieved if any PPT adversary \(\mathcal{A}\) cannot guess
+  \(b' = b\) with a probability non-neglibly better than \(\frac{1}{2}\).
+\end{definition}
 
-  \item{{\bf Onion-correctness.} This is the simple condition that if a
-  correctly formed onion is processed correctly and by the correct
-  routers, then the correct message is received by the last router.}
-
-  \item{{\bf Onion-integrity.} This is the requirement that the path of
-  an onion is limited by some integer N, that is, no matter how an
-  onion is manipulated, the path may never have a length that is
-  larger than N.}
-
-  \item{{\bf Onion-security.} A protocol has the property of
-    onion-security if an adversary can not guess the message nor add
-    an extra onion-layer to any onion.}
+\begin{definition}{Layer-Unlinkability LU}
+  \begin{enumerate}
+  \item - 4 are the same as in the definition of TI.
+    \setcounter{enumi}{4}
+  \item{The challenger creates the onion with the adversary's input
+    choice:
+    \[(O_1, \ldots, O_{n+1} \leftarrow \text{FormOnion}(m,
+    \mathcal{P}, (PK)_{\mathcal{P}}))    
+    \]
+    and a random onion with a randomly chosen path \(\bar{\mathcal{P}}
+    = (\bar{P}_1, \ldots, \bar{P}_k = P_1, \ldots, \bar{P}_{k+j} =
+    P_j, \bar{P}_{k+j+1}, \ldots, \bar{P}_{n+1})\), that includes the
+    subpath from the honest node of \(\mathcal{P}\) starting at
+    position \(k\) ending at \(k+j\) (with \(1 \leq j+k \leq \bar{n}
+    +1 \leq N\)), and a random message \(m' \in \mathcal{M}\):
+    \[ (\bar{O}_1, \ldots, \bar{O}_{\bar{n} + 1}) \leftarrow
+    \text{FormOnion}(m', \bar{\mathcal{P}}, (PK)_{\bar{\mathcal{P}}}).
+    \]
+  }
+  \item{
+    \begin{itemize}
+      \item{If \(b = 0\), the challenger gives \((O_1,
+        \text{ProcOnion(O_j)})\) to the adversary.}
+      \item{Otherwise, the challenger gives \((\bar{O}_k,
+        \text{ProcOnion(O_j)})\) to the adversary.}
+    \end{itemize}
+  }
+  \item{The adversary may submit any number of onions \(O_i,\, O_i
+    \neq O_j,\, O_i \neq \bar{O}_{k+j}\) of her choice to the
+    challenger. The challenger sends the output of
+    \(\text{ProcOnion}(SK, O_i, P_j)\) to the adversary.}
+  \item{The adversary produces guess \(b'\).}
   \end{enumerate}
-
-However, while these definitions are useful, newer work have found
-that they were not sufficient and added two new properties, which has
-since been proven to fulfill the security properties of the ideal
-functionality~\cite{kuhn}. The properties were:
-
-\begin{enumerate}
-  \setcounter{enumi}{5}
-  \item{{\bf Tail indistinguishability against a corrupted receiver.}
-    An adversary that reads after the last honest relay should not be
-    able to distinguish between two onions who follow the same path
-    after the last honest router, but differ before it.}
-
-  \item{{\bf Layer-Unlinkability against bypassing honest nodes.} An
-    adversary should not be able to distinguish between an onion for
-    which the adversary chooses the path up to an honest router, and
-    an onion which contains this path as a subpath.}
-\end{enumerate}
+  LU is achieved if any PPT adversary \(\mathcal{A}\) cannot guess
+  \(b' = b\) with a probability non-negligibly better than \(\frac{1}{2}\).
+\end{definition}
 
 With these properties and the SphinxES protocol, we wish to prove that
-SphinxES does indeed have these properties, and thus fulfills the
+SphinxES does indeed have these properties, and thus fulfils the
 security properties of the ideal functionality.

### 2020-04-08 paper/UCOR.tex
Changed 'One of the first...'

@@
 
-One of the first successful uses of the \ac{UC} framework was a model
+One  successful use of the \ac{UC} framework is a model
 created by Jan Camenish and Anna Lysyanskaya (a model we will call the
-CL-model). This model was an attempt at formalising the concept of
-onion routing using the UC-framework. It relied on an ideal
-functionality, and five properties that ensured a protocol would properly
+CL-model). This model is an attempt at formalising the concept of
+onion routing using the UC-framework. It relies on an ideal
+functionality, and five properties that ensures a protocol would properly
 simulate the ideal functionality~\cite{CL-model}. We will however not

### 2020-04-08 paper/spores-security.tex
Reorganizes files to have SPORES in spores.tex

--- 2020-03-24 paper/security-discussion.tex
@@
 \begin{enumerate*}
-\item \Sphinxes (\cref{Sphinxes}) preserves the properties of 
+\item SphinxES (\cref{SphinxES}) preserves the properties of 
   \textcite{CLOnionRouting} and \textcite{Sphinx} yielding \ac{UC}-secure 

### 2020-04-08 paper/spores.tex
Reorganizes files to have SPORES in spores.tex

@@
-\documentclass{article}
-\input{preamble.tex}
-\usepackage{authblk}
+%!TEX root = spores.tex
 
-\begin{document}
-\title{%
-  \acs*{SPORES}: \acl*{SPORES}%
-  %\name: Stateless Predictive Onion Routing for E-Squads%
-  %% From the IEEE template
-  % \thanks{Identify applicable funding agency here. If none, delete this.}
-  % \thanks{%
-  %   Daniel Bosk and Sonja Buchegger were funded by
-  %   the Swedish Foundation for Strategic Research grant SSF FFL09-0086.
-  %   Research done while Daniel Bosk visited the WIDE team at INRIA/IRISA Rennes, 
-  %   France.
-  % }
-}
+\section{Design of the \name file transfer system}%
+\label{design}
 
-\author[1]{Daniel Bosk\thanks{%
-  Research done while the author visited the WIDE team at INRIA/IRISA Rennes, 
-  France.
-}}
-\affil[1]{KTH Royal Institute of Technology\\\email{daniel@bosk.se}}
-\author[1]{Sonja Buchegger}
-\author[2]{Adrien Luxey}
-\affil[2]{Univ.\ de Rennes, INRIA, CNRS, IRISA\\\email{Adrien.Luxey@irisa.fr}}
-\author[2]{Yérom-David Bromberg}
-\author[2]{François Taïani}
+% \sonja{will frame and structure (A) squad overlay (prediction) (B)
+%   global overlay (RPS) (C) sphinxes (incl.\ sphinx, onion routing in
+%   general) (D) SPOR and SPORES (E) encryption (hybrid, payload, header)
+%   if not included earlier (F) out-of-band}
+% \commentDaniel{I suggest the following structure:
+%   (A) SphinxES
+%   (B) SPOR (global overlay)
+%   (C) SPORES (local overlay).
+%   My original idea was to make SphinxES its own section before the design 
+%   section instead of a subsection in the design section.}
 
-\mode<article>{\maketitle}
-\mode<presentation>{%
-  \begin{frame}
-    \maketitle
-  \end{frame}
-}
-
-\begin{abstract}
-  \input{abstract.tex}
-\end{abstract}
-
-\input{contents.tex}
-\end{document}
+%\include*{spor}
+%\include*{squad-overlay-design}
+\include*{file-transfer-design}

### 2020-04-14 paper/intro.tex

@@
 
-Second, we provide a way for messaging services, like Signal, to use SphinxES 
-to relay messages over the devices in \iac{P2P} network with high churn.
-We call this the \ac{SPOR} protocol.
+Second, we provide a protocol, \ac{SPOR}, which optimizes the layers for 
+availability.
+See \cref{SPOR} for details.
+We use a wide definition of churn, a node that is available is online and not 
+congested.
+This allows systems to relay messages in a \ac{P2P} network with high churn.
+For instance, one could convert Signal to use \ac{SPOR} for message delivery.
+We use this as the scenario for our performance evaluation.
 

### 2020-04-14 paper/spor-security.tex

@@
 
-\paragraph*{Node selection}
+\paragraph*{If Eve is in the layers}
 
 \sonja{will motivate using the survey/taxonomy}
-The onion route provides unlinkability between Alice and Bob as long as the 
-message passes at least one honest node on the route.
-This means that any adversary, say Eve,  must ensure that the message passes 
-through an adversarial node on each layer.
+The security of SphinxES rests on the fact that the message must pass at least 
+one honest node.
+Phrasing it in terms of what the adversary~Eve must accomplish, she must ensure 
+that the message passes through an adversarial node.
+Now that we have some node selection, we can reason about the likelihood of 
+that.
+
 The probability of successful attack is proportional to Eve's size in the 
-network, \ie \(f_A = \frac{|D_A|}{|D|}\).
-\commentDaniel{Check that we still use the \(D_i\) notation for the devices in 
-  \(i\)'s squad.}
-If we assume that \(\GetRandomNode\) returns nodes with close to the uniform 
-distribution, then the \(\nu w_L\) nodes selected is expected to contain \(f_A 
+network, \ie \(q_A = \frac{|\devices_A|}{|\devices|}\).
+\commentDaniel{Check that we still use the \(\devices_i\) notation for the 
+devices in \(i\)'s squad.}
+If we assume that \(\GetNode\) returns nodes with close to the uniform 
+distribution, then the \(\nu w_L\) nodes selected is expected to contain \(q_A 
 \nu w_L\) nodes controlled by Eve.
-If \(f_A \nu w_L < \nu\), then Eve is not expected to be present on every layer 
+If \(q_A \nu w_L < \nu\), then Eve is not expected to be present on every layer 
 of the route.
+
 Considering how \ac{SPOR} distributed the \(\nu w_L\) selected nodes, Eve's 
 best strategy is to have high-availability nodes --- assume that 
-\(\avail_{D_E}(t) = 1\) for all Eve's devices \(D_E\).
+\(\avail[\devices_E] = 1\) for all Eve's devices \(\devices_E\).
 This way, Eve's devices will be distributed evenly across all layers (provided 
 she controls enough of the selected devices).
-To succeed, Eve must be chosen in the first layer, the probability of which 
-will be \(\frac{f_A}{w_L}\) (for a passive adversary and \(1\) for an active).
+
+To link Alice and Bob, Eve must be chosen in the first layer and the route must 
+contain the maximum number of layers~\(r\).
+(Remember, we chose \(\nu+1\leq r\) in \cref{SphinxEScreate}.)
+The probability for Eve to be chosen in the first layer will be 
+\(\frac{q_A}{w_L}\) (for a passive adversary and \(1\) for an active).
 If one of her devices is chosen in the first layer, then she can choose one of 
@@
 way to Bob.
-In summary, her probability of success is \(\frac{1}{w_L} (1-(1-f_A)^{(w_L-1) 
-    \nu +1})\) (or without the \(\frac{1}{w_L}\) factor for an active 
-adversary), which can be compared to \((f_A)^\nu\) for classical \ac{OR} (for 
-both active and passive adversaries).
-\sonja{compare the chance of being present on every
-  layer AND chosen in the first layer to regular onion routing where she
-  needs to be the (sole) node on each layer. Are we doing
-  better/worse/the same?}
-\commentDaniel{Hard to say at this time of night \dots}
+In summary, her probability of success is \(
+  \frac{1}{w_L} (1-(1-q_A)^{(w_L-1) \nu +1})
+\) (or without the \(\frac{1}{w_L}\) factor for an active adversary), which can 
+be compared to \((q_A)^\nu\) for classical \ac{OR} (for both active and passive 
+adversaries).
 
 However, Eve can only be certain that she has relayed the message from Alice to 
-Bob if \(\nu = r\), \ie she receives the message from Alice, relays it \(r-1\) 
-times and lastly sends it to Bob.
-If \(\nu < r\) though, then, due to the indistinguishability and unlinkability 
-properties of SphinxES (inherited from \ac{Sphinx}), Eve cannot know for certain if 
-Alice is the first node and Bob is the last node. \sonja{but what can
-  she learn/guess?}
-\commentDaniel{For all she knows there might be another node at either the 
-  beginning or the end, she cannot tell.}
+Bob if \(\nu+1 = r\), \ie she receives the message from Alice, relays it 
+\(r-1\) times and lastly sends it to Bob.
+If \(\nu+1 = r-1\), then Eve learns that either Alice must be the sender or Bob 
+must be the recipient.
+(This is due to the indistinguishability and unlinkability properties of the 
+ideal functionality.)
+If \(\nu+1 \leq r-2\), then Eve cannot certainly tell whether Alice and Bob are 
+end points of simply honest relays for someone else.
 
-Finally, we must point out that the \(\GetRandomNode\) algorithm must be 
-privacy preserving.
+That reasoning is only valid when there is more than one node in a layer.
+If Eve learns that there is only one node in the next layer, it is likely the 
+recipient node.
+
+\paragraph*{Privacy of \(\GetNode\)}
+
+The \(\GetNode\) algorithm must be privacy preserving.
 Consider the following scenario.
-Alice requests a set of peers, say \(\{d_1, \dotsc, d_n\}\).
+Alice requests a set of peers, say \(\{d_0, \dotsc, d_{n-1}\}\).
 If \(d_i\) interacts in each sampling operation resulting in \(d_i\) being in 
@@
 encrypt the header.
-(This follows from the fact that SphinxES is source-routed.)
-\Ie every node on Alice's route would know that Alice is either the source or 
-the destination.
+(This follows from the fact that the ideal functionality is source-routed.)
+\Ie every node on Alice's route would know that Alice is either the source 
+(forward header) or the destination (reply header).
 
-Although the requirements of the \ac{RPS} being uniformly randomly
-distributed and privacy-preserving are not easily met in practice,
-there are some promising candidates~\cite[\eg][]{Octopus,BrahmsRPS}.
-\name does not put any other constraints on the \ac{RPS} used.
+\paragraph*{Distributions in layers}
+
+The output of Alice's query to \(\GetNode\) must only be learned by Alice.
+Again, Alice requests a set of peers~\(\{d_0, \dotsc, d_{\nu w_L}\}\).
+Say that Eve observes all of Alice's requests.
+Now, both Alice and Eve can compute the output of \(\CreateLayers\) 
+(deterministic).
+Now, if Eve is on that path, say in layer~\(L_i\), she can recognize Alice's 
+onions by the composition of the next layer~\(L_{i+1}\).
+The likelihood that Bob has a layer \(L_j = L_{i+1}\) is small.
+Consider normal onion routing, there the probability that Alice and Bob both 
+chose node \(N\) is \(\frac{1}{|\devices|}\).
+Here, however, it is \((\frac{1}{|\devices|})^{w_L}\), for large sets of 
+devices~\(\devices\).
+
+Consider a node controlled by Eve.
+Given the low probability of \(\frac{1}{|\devices|^{w_L}}\) that a combination 
+of nodes appear as a layer, the combination Alice's own devices in the final 
+layer will have a higher probability of appearing.
+Thus, any more frequently appearing combination of nodes is with high 
+likelihood the recipient devices of a user.
+(This is all the more true when there is only one device in a layer.)
 
@@
 
-Alice transfers a file \(f\) to Bob during the time interval 
+Alice sends the message \(m\) to Bob during the time interval 
 \(\interval{t_0}{t_1}\).
-We denote the set of Alice's devices as \(D_A\) and Bob's as \(D_B\).
-Bob wants to compute an estimate \(\hat D_A\) which is as close to \(D_A\) as 
-possible.
+We denote the set of Alice's devices as \(\devices_A\) and Bob's as 
+\(\devices_B\).
+Bob wants to compute an estimate \(\hat \devices_A\) which is as close to 
+\(\devices_A\) as possible.
 
@@
 We can also assume that Bob knows all data from the \ac{RPS}, \ie the \((d, 
-  \pk_d, \avail_d)\) tuple (see \cref{SPOR}) of \emph{every device that was 
+\pk_d, a_d)\) tuple (see \cref{SPOR}) of \emph{every device~\(d\) that was 
 online at some point during \(\interval{t_0}{t_1}\)}.
-Let \(\A_{\interval{t_0}{t_1}}\subseteq \N\times \G^*\times (\RR\to 
-  \interval{0}{1})\) denote the set of those tuples.
-Thus Bob can approximate \(D_A\) by \(\hat D_A \gets 
-  \A_{\interval{t_0}{t_1}}\cap D_B\).
+Let \(\A_{\interval{t_0}{t_1}}\subseteq \N\times \G^*\times \interval{0}{1}\) 
+denote the set of those tuples.
+Thus Bob can approximate \(\devices_A\) by \(\hat \devices_A \gets 
+\A_{\interval{t_0}{t_1}}\cap \devices_B\).
 
-When Alice and Bob interact the next time, either Alice sends a file \(f'\) to 
-Bob or Bob sends a file \(f'\) to Alice, then Bob can do the same again:
-\(\hat D_A' \gets \A_{\interval{t_0'}{t_1'}} \cap D_B\).
-If at least one of \(d, \pk_d, \avail_d\) remains constant, Bob can use that to 
+When Alice and Bob interact the next time, either Alice sends a message \(m'\) 
+to Bob or Bob sends a file \(m'\) to Alice, then Bob can do the same again:
+\(\hat \devices_A' \gets \A_{\interval{t_0'}{t_1'}} \cap \devices_B\).
+If at least one of \(d, \pk_d, a_d\) remains constant, Bob can use that to 
 improve his approximation.
-Say that \(\avail_d\) remains constant.
-Then Bob can improve his approximation to \(\hat D_A \cap_{\avail_d} 
-  \hat{D}_A'\), where \(\cap_{\avail_d}\) is the intersection which only 
-considers the attribute \(\avail_d\).
-Even if \(\avail_d\) is not constant, its variation might stay inside some 
-\(\epsilon\)-neighbourhood, and if \(\epsilon\) is small enough, \(\avail_d\) 
-might still be used to distinguish Alice.
-The same applies for \(d\).
-(\(\pk_d\) can be regularly updated.)
+Say that \(a_d\) remains constant.
+Then Bob can improve his approximation to \(
+  \hat \devices_A \cap_{a_d} \hat \devices_A',
+\) where \(\cap_{a_d}\) is the intersection which only considers the attribute 
+\(a_d\).
+Even if \(a_d\) is not constant, its variation might stay inside some 
+\(\epsilon\)-neighbourhood, and if \(\epsilon\) is small enough, \(a_d\) might 
+still be used to distinguish Alice.
+The same applies for \(d\) and \(\pk_d\).
 
-With an inaccurate availability function, \(\avail\), this will not be a 
-problem as there will be many others (as the system scales) that share the 
-same availability distribution.
-With more accurate availability estimates we would have to employ techniques 
-like \ac{DP} to ensure that Alice's availability distribution is not
-(too close to)
-unique.
-
-\paragraph*{Robustness}
-
-Stateless routing can result in re-ordered chunks or packets, and
-chunks received on different devices of a user's \squad. From \ac{Sphinx},
-we inherit unique IDs for each mix packet.
-If we provide the mix packets as an ordered list when we communicate them 
-out-of-band together with the metadata of the file and they are used in that 
-same order, then we can use those IDs to re-order chunks if need be.
-The \squad overlay handles intra-squad device 
-coordination.
-We ensure liveness by acknowledgments and timeouts (as detailed in 
-\cref{sec:squad_overlay}), despite the possibility of \squad devices
-going offline during transfer or other node or link failures.
-
-\paragraph*{Extended adversary model}%
-\label{security-limitations}
-
-A global, passive, network-observing adversary can of course do
-statistical disclosure attacks to eventually learn who communicates
-with whom~\cite{StatisticalDisclosureAttacks}. There are also denial
-of service attacks that can lead to the adversary learning more from
-the system~\cite{DenialOfSecurity}.  As mentioned in
-\cref{system-model}, we share the adversary model with \ac{Tor}
-%and Sphinx
-and thus exclude a global passive adversary. Our focus is on
-protecting Alice and Bob from each other and from others who also
-participate as nodes in the network, not on protecting them from
-surveillance. Nevertheless, we offer some reflections on such an
-adversary. We hypothesize that our stateless and redundant design
-might yield some advantages over classical \ac{OR}. For
-example, no control messages are sent back to the source if the
-adversary has introduced an error.  \sonja{``But these advantages will
-  only postpone the success of the attack, eventually even our
-  protocol must resend.'' why?}  \commentDaniel{Due to statistics. We should 
-  also look into
-  this denial of security.} Another example is that the source-bounded
-random-walk and new routes for file chunks make tracking more
-difficult than with regular onion routing circuits. A drawback, however, is
-that since the chunks can take several paths from source to destination, the source 
-will send and the destination will receive more traffic than other nodes in the 
-network~\cite{RoutingSurveyAnonymousProtocols}. However, this is mitigated by the fact that the source and 
-destination can be several different devices --- \ie from the \squads.
-
-We would also like to point out that the
-vulnerability to a global passive attacker is not inherent in Sphinx
-or SphinxES, but can be caused by the way they are applied, \ie the
-traffic sent. If performance and resource consumption were not an
-issue, batched and well-timed message or file transfer by all nodes
-would render traffic analysis less efficient. Concretely, \Ac{SPORES} inherits 
-the security properties from SphinxES and \ac{SPOR}.
-However, both SphinxES and \ac{SPOR} can be used with any mixing strategy, and 
-the security they provide is as secure as the mixing strategy (or flushing 
-algorithm) allows.
-Since \ac{SPORES} is a fully-fledged system, it must make a concrete choice for 
-the mixing strategy.
-Since \ac{SPORES} aims at low latency, routers do not batch and mix incoming 
-messages; they immediately forward any messages.
-This puts \ac{SPORES} in the same position as \ac{Tor}, \ie more vulnerable to 
-traffic analysis than batching mix-nets~\cite{RoutingSurveyAnonymousProtocols} 
-\commentDaniel{we should probably look for the original papers} --- this 
-vulnerability is inherited from the mixing strategy.
-
-% \commentDaniel{Predecessor attacks: random walk protocols has the problem that 
-%   the adversary can see the initiator (statistically) more often than the other 
-%   nodes, and can thus identify the 
-%   source~\cite{RoutingSurveyAnonymousProtocols}.
-%   Our protocol is a \enquote{bounded} random walk, \ie within limits.}
+With an inaccurate availability function~\(\avail\) (\eg \(k\)-anonymous, as 
+mentioned above) this will not be a problem as there will be many others (as 
+the system scales) that share the same availability distribution.
+The public key~\(\pk\) can be refreshed regularly.
+The main problem is any persistent identifier (address) \(d\).

### 2020-04-14 paper/spores.tex

@@
-%!TEX root = spores.tex
+\section{\Acf*{SPORES}}%
+\label{SPORES}%
 
-\section{Design of the \name file transfer system}%
-\label{design}
+We will now extend \ac{SPOR} into \ac{SPORES}.
+It is becoming more and more common that people own more than one online device 
+(\eg a laptop and a smartphone).
+We will utilize this in the construction of \ac{SPORES}.
+Thus \ac{SPORES} is different in two aspects:
+First, the recipient layer consists of several devices instead of only one.
+These devices, the e-squad of Bob, will then coordinate to ensure the relevant 
+device gets the message.
+We assume there is a protocol which solves this problem.
+For instance, \textcite{luxey:cascade} introduce a protocol that allows the 
+devices of an e-squad to coordinate user sessions in the face of churn.
 
-% \sonja{will frame and structure (A) squad overlay (prediction) (B)
-%   global overlay (RPS) (C) sphinxes (incl.\ sphinx, onion routing in
-%   general) (D) SPOR and SPORES (E) encryption (hybrid, payload, header)
-%   if not included earlier (F) out-of-band}
-% \commentDaniel{I suggest the following structure:
-%   (A) SphinxES
-%   (B) SPOR (global overlay)
-%   (C) SPORES (local overlay).
-%   My original idea was to make SphinxES its own section before the design 
-%   section instead of a subsection in the design section.}
+Second, we will introduce how to do fragmentation and reassembly for large 
+messages.
+Consider that the message \(m\) that Alice wants to send to Bob is too large to 
+successfully pass every layer of the route.
+\Eg each device goes offline and back online every \(t\) seconds, the bandwidth 
+is \(w\) bits per second and the message is \(|m|\) bits; if \(|m| > t w\), 
+then the message \(m\) can never be delivered as any device will go offline 
+before relaying it to the next node.
+The natural solution is to split \(m\) into \(n\) parts, \(m_0, \dotsc, 
+  m_{n-1}\), where \(|m|/n\leq t w\).
+The problem now is that \(m_i\) and \(m_j\) (\(i\neq j\)) might end up on 
+different devices.
+But that problem is solved by the protocol mentioned above.
+This allows us to send large messages, such as videos, more efficiently.
 
-%\include*{spor}
-%\include*{squad-overlay-design}
-\include*{file-transfer-design}
+The parameters \(t\) and \(w\) must be empirically approximated and used as 
+global configuration parameters for the system.
+We run simulations for various values of \(t\) and \(w\) in \cref{Performance}.
+In this section we describe a file-transfer protocol for splitting a large 
+message, sending the fragments using \ac{SPOR} and reassemble them --- even if 
+the fragments are received by different devices of the squad.
+
+\subsection{Fragmentation and reassembly}%
+\label{sec:file_transfer}
+
+Alice wants to send the message \(m\) to Bob, \(m\) is \(|m|\) bits long.
+Bob creates a reply header and gives it to Alice.
+Alice splits \(m\) into \(n\) parts \(m_0, \dotsc, m_{n-1}\).
+Alice sends \(|m|\), \(n\), \(\hash(m)\), \(\hash(m_0), \dotsc, 
+\hash(m_{n-1})\) to Bob using \ac{SPOR} and Bob's reply header.
+(Remember, this means that Bob receives a reply header with the data, so that 
+he can later reply to Alice.)
+
+Bob runs \(\CreateReply\) \(n\) times, the node sets passed to \(\CreateReply\) 
+are created as in \cref{SPOR}, but all of Bob's devices populate the recipient 
+set.
+Bob notes the order of the identifiers, \(I\), of each header and sends the 
+headers in that order to Alice (using Alice's reply header).
+
+Alice receives the headers and keeps the order of the headers.
+For each \(0\leq i < n\), she uses \(\UseReply\) with \(m_i\) as payload to get 
+a header \(\hat M_i\).
+Then she constructs the final header \(M_i\) by running \(\CreateFwd\) with 
+\(\hat M_i\) as payload and the final layer set to \(\{\rdvnode\}\) (to 
+indicate to the last node that it is a rendezvous node).
+She then sends \(M_i\) along the route.
+We note that Alice can process all pieces in parallel as long as she uses the 
+headers she got from Bob in the correct order --- \ie \(M_i\) contains \(m_i\) 
+as payload.
+
+When the headers are used in the correct order Bob can use the identifiers from 
+the headers (\(I\)) to correctly reassemble the fragments despite out-of-order 
+delivery.
+
+As above, each payload also contains a reply header for Bob, these can be used 
+by Bob to inform Alice at regular time intervals about which chunks have been 
+received and which are missing.
+
+%\commentDaniel{I leave the remaining details for someone else to write up.
+ % What we need is the details of how Bob's devices syncs and reassembles files.
+ % Maybe this is reduced to Sprinkler or something.}

### 2020-04-14 paper/spor.tex

@@
 %!TEX root = spores.tex
-
-\NewScheme{\SPOR}{SPOR}
 
@@
 \(\UseReply\), creates a forward header using \(\CreateFwd\) with the prepared 
-reply header as parameter. \sonja{what about the crossover node and
-  Alice's leg of the route?} 
+reply header as parameter.
 Then she sends this packet to the first node, which processes it using 
@@
 %(This process is illustrated in \cref{fig:file-transfer}.)
-Now we will focus on how Alice and Bob choose the nodes that they provide to 
-\(\CreateReply\) and \(\CreateFwd\).
+Now we will focus on two problems that Alice and Bob have:
+first, how Alice and Bob choose the nodes that they provide to \(\CreateReply\) 
+and \(\CreateFwd\);
+second, how Alice and Bob can reduce the use of the out-of-band channel.
 
@@
 %\end{figure}
+
+\subsection{Selecting nodes}
 
@@
 layer is offline at the same time) while keeping \(|L_i| = w_L\).
+
+\subsection{Reducing the use of the out-of-band channel}
+
+It is desirable for Alice and Bob to use out-of-band communication as little as 
+possible.
+To do this, we define \ac{SPOR} to let the first part of the payload to be a 
+reply header that the recipient can use to reply.

### 2020-04-16 paper/UCOR.tex

@@
 Universal Composability theorem \cite{UniversalComposability}. However, the most important part of
-this framework is what is known as an {\bf Ideal Functionality}, which
+this framework is what is known as an \emph{ideal functionality}, which
 can be thought of as a black box that fulfils some well-defined
